### 2022-01-21 ARSimulation.Rmd
Added ARSimulation.Rmd

---
title: "Block Bootstrap for Time Series"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r simulation, echo=FALSE}
# simulates, prints, and plots auto-regressive process of order 1 with ar = 0.5 and size = 100
ts.sim <- arima.sim(list(order = c(1,0,0), ar = 0.5), n = 100) 
ts.sim
plot(ts.sim)
# splits time series into ten blocks of size 10 and stores them in a list
ts.blocks <- list(ts.sim[c(1:10)], ts.sim[c(11:20)], ts.sim[c(21:30)], ts.sim[c(31:40)], ts.sim[c(41:50)], ts.sim[c(51:60)], ts.sim[c(61:70)], ts.sim[c(71:80)], ts.sim[c(81:90)], ts.sim[c(91:100)])
ts.blocks
# randomly samples 10 non-overlapping blocks (with replacement) from ts.blocks, creating a single bootstrapped time series
ts.boot1 <- sample(ts.blocks, 10, replace = T)
ts.boot1
class(ts.boot1)
# ts.boot1 is a list of vectors and does not work with the plot() function, so ts.boot2 is a simpler numeric vector
ts.boot2 <- c()
for(i in 1:10) {
  for(j in 1: 10) {
    ts.boot2 <- c(ts.boot2, ts.boot1[[i]][[j]])
  }
}
ts.boot2
class(ts.boot2)
#ts.boot2 is plotted
plot(ts.boot2, type = "l")

```

### 2022-01-26 ARSimulation.Rmd
Made Style Changes

@@
 
-```{r simulation, echo=FALSE}
-# simulates, prints, and plots auto-regressive process of order 1 with ar = 0.5 and size = 100
-ts.sim <- arima.sim(list(order = c(1,0,0), ar = 0.5), n = 100) 
+Simulates, prints, and plots auto-regressive process of order 1 with ar = 0.5 and size = 100
+```{r, echo = FALSE}
+ts.sim <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 100) 
 ts.sim
 plot(ts.sim)
-# splits time series into ten blocks of size 10 and stores them in a list
+```
+
+Splits time series into ten blocks of size 10 and stores them in a list
+```{r, echo = False}
 ts.blocks <- list(ts.sim[c(1:10)], ts.sim[c(11:20)], ts.sim[c(21:30)], ts.sim[c(31:40)], ts.sim[c(41:50)], ts.sim[c(51:60)], ts.sim[c(61:70)], ts.sim[c(71:80)], ts.sim[c(81:90)], ts.sim[c(91:100)])
 ts.blocks
-# randomly samples 10 non-overlapping blocks (with replacement) from ts.blocks, creating a single bootstrapped time series
+```
+
+Randomly samples 10 non-overlapping blocks (with replacement) from ts.blocks, creating a single bootstrapped time series
+```{r, echo = False}
 ts.boot1 <- sample(ts.blocks, 10, replace = T)
@@
 class(ts.boot1)
-# ts.boot1 is a list of vectors and does not work with the plot() function, so ts.boot2 is a simpler numeric vector
+```
+
+ts.boot1 is a list of vectors and does not work with the plot() function, so we use a nested loop to store the values in ts.boot2, a simpler numeric vector
+```{r, echo = False}
 ts.boot2 <- c()
@@
 class(ts.boot2)
-#ts.boot2 is plotted
+```
+
+Ts.boot2 is plotted
+```{r, echo = False}
 plot(ts.boot2, type = "l")
-
 ```

### 2022-01-28 ARSimulation.Rmd
Began Writing Function
Randomly Select Single Point

@@
 ```
+We need to start with a sample of a certain size B of consecutive points from a time series ts.series.
+First we need to randomly select a single point in the time series, and we can do this by selecting a number between 1 and 100.
+
+```{r, echo = False}
+ts.sim <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 100) 
+single_point <- function(ts.series, B, b, overlap)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  print(point1)
+}
+bootstrap(ts.sim, 0, 0, F)
+```

### 2022-01-28 ARSimulation.Rmd
Starting Sample

@@
 ts.sim <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 100) 
-single_point <- function(ts.series, B, b, overlap)
+single_point <- function(ts.series)
 {
@@
 }
-bootstrap(ts.sim, 0, 0, F)
+single_point(ts.sim)
 ```
+one_sample creates the sample that we'll be working with now
+```{r, echo = False}
+one_sample <- function(ts.series, B)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  samp1 <- c()
+  for(i in 1:B)
+  {
+    samp1 <- c(samp1, ts.sim[point1 + i - 1])
+  }
+  print(ts.sim)
+  print(point1)
+  print(samp1)
+}
+one_sample(ts.sim, 10)
+```

### 2022-01-29 ARSimulation.Rmd
Added Plots

--- 2022-01-28 ARSimulation.Rmd
@@
 ts.sim <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 100) 
-single_point <- function(ts.series, B, b, overlap)
+single_point <- function(ts.series)
 {
   point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  print(ts.sim)
   print(point1)
 }
-bootstrap(ts.sim, 0, 0, F)
+single_point(ts.sim)
 ```
+one_sample creates the sample that we'll be working with now
+```{r, echo = False}
+one_sample <- function(ts.series, B)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  ts.samp1 <- c()
+  for(i in 1:B)
+  {
+    ts.samp1 <- c(ts.samp1, ts.sim[point1 + i - 1])
+  }
+  print(ts.sim)
+  plot(ts.sim)
+  print(point1)
+  print(ts.samp1)
+  plot(ts.samp1, type = 'l')
+}
+one_sample(ts.sim, 10)
+```

### 2022-01-29 ARSimulation.Rmd
Split Series into Blocks

--- 2022-01-28 ARSimulation.Rmd
@@
 ts.sim <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 100) 
-single_point <- function(ts.series, B, b, overlap)
+single_point <- function(ts.series)
 {
   point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  print(ts.sim)
   print(point1)
 }
-bootstrap(ts.sim, 0, 0, F)
+single_point(ts.sim)
 ```
+one_sample creates the sample that we'll be working with now
+```{r, echo = False}
+one_sample <- function(ts.series, B)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  ts.samp1 <- c()
+  for(i in 1 : B)
+  {
+    ts.samp1 <- c(ts.samp1, ts.sim[point1 + i - 1])
+  }
+  print(ts.sim)
+  plot(ts.sim)
+  print(point1)
+  print(ts.samp1)
+  plot(ts.samp1, type = 'l')
+}
+one_sample(ts.sim, 10)
+```
+Now we need to separate the sample into blocks of size b.
+```{r, echo == False}
+blocks <- function(ts.series, B, b)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  ts.samp1 <- c()
+  for(i in 1 : B)
+  {
+    ts.samp1 <- c(ts.samp1, ts.sim[point1 + i - 1])
+  }
+  print(ts.sim)
+  plot(ts.sim)
+  print(point1)
+  print(ts.samp1)
+  i <- 1
+  ts.block_list <- list()
+  while(i < B)
+  {
+    x <- list(ts.samp1[i : (i + b - 1)])
+    ts.block_list <- append(ts.block_list, x)
+    i = i + b
+  }
+  print(ts.block_list)
+  plot(ts.samp1, type = 'l')
+}
+blocks(ts.sim, 20, 4)
+```

### 2022-01-29 ARSimulation.Rmd
Sample Blocks into Bootstrap

@@
 ```
+
 one_sample creates the sample that we'll be working with now
+
 ```{r, echo = False}
@@
 ```
-Now we need to separate the sample into blocks of size b.
+
+Now we need to separate the sample into blocks of size b. We are assuming that B is divisible by b.
+
 ```{r, echo == False}
@@
 ```
+
+Randomly samples B/b non-overlapping blocks (with replacement) from ts.block_list, creating a single bootstrapped time series. 
+```{r, echo = False}
+blocks <- function(ts.series, B, b)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  ts.samp1 <- c()
+  for(i in 1 : B)
+  {
+    ts.samp1 <- c(ts.samp1, ts.sim[point1 + i - 1])
+  }
+  print(ts.sim)
+  plot(ts.sim)
+  print(point1)
+  print(ts.samp1)
+  plot(ts.samp1, type = 'l')
+  i <- 1
+  ts.block_list <- list()
+  while(i < B)
+  {
+    x <- list(ts.samp1[i : (i + b - 1)])
+    ts.block_list <- append(ts.block_list, x)
+    i = i + b
+  }
+  print(ts.block_list)
+  ts.bootstrap_1 <- sample(ts.block_list, B/b, replace = T)
+  print(ts.bootstrap_1)
+  class(ts.boot1)
+}
+blocks(ts.sim, 20, 4)
+
+```

### 2022-01-29 ARSimulation.Rmd
Improved Bootstrap

@@
 ```{r, echo = False}
-ts.blocks <- list(ts.sim[c(1:10)], ts.sim[c(11:20)], ts.sim[c(21:30)], ts.sim[c(31:40)], ts.sim[c(41:50)], ts.sim[c(51:60)], ts.sim[c(61:70)], ts.sim[c(71:80)], ts.sim[c(81:90)], ts.sim[c(91:100)])
+ts.blocks <- list(ts.sim[c(1 : 10)], ts.sim[c(11 : 20)], ts.sim[c(21 : 30)], ts.sim[c(31 : 40)], ts.sim[c(41 : 50)], ts.sim[c(51 : 60)], ts.sim[c(61 : 70)], ts.sim[c(71 : 80)], ts.sim[c(81 : 90)], ts.sim[c(91 : 100)])
 ts.blocks
@@
 ts.boot2 <- c()
-for(i in 1:10) {
-  for(j in 1: 10) {
+for(i in 1 : 10) {
+  for(j in 1 : 10) {
     ts.boot2 <- c(ts.boot2, ts.boot1[[i]][[j]])
@@
 ```{r, echo = False}
-blocks <- function(ts.series, B, b)
+bootstrap_samp1 <- function(ts.series, B, b)
 {
@@
 }
-blocks(ts.sim, 20, 4)
+bootstrap_samp1(ts.sim, 20, 4)
+```
 
+ts.bootstrap_1 is a list of lists and will be difficult to work with, so we use a nested loop to store the values in ts.bootstrap_2, a simpler numeric vector
+
+```{r, echo = False}
+bootstrap_samp2 <- function(ts.series, B, b)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  ts.samp1 <- c()
+  for(i in 1 : B)
+  {
+    ts.samp1 <- c(ts.samp1, ts.sim[point1 + i - 1])
+  }
+  print(ts.sim)
+  plot(ts.sim)
+  print(point1)
+  print(ts.samp1)
+  plot(ts.samp1, type = 'l')
+  i <- 1
+  ts.block_list <- list()
+  while(i < B)
+  {
+    x <- list(ts.samp1[i : (i + b - 1)])
+    ts.block_list <- append(ts.block_list, x)
+    i = i + b
+  }
+  print(ts.block_list)
+  ts.bootstrap_1 <- sample(ts.block_list, B/b, replace = T)
+  print(ts.bootstrap_1)
+  class(ts.boot1)
+  ts.bootstrap_2 <- c()
+  for(i in 1 : (B/b)) {
+    for(j in 1 : b) {
+      ts.bootstrap_2 <- c(ts.bootstrap_2, ts.bootstrap_1[[i]][[j]])
+    }
+  }
+  print(ts.bootstrap_2)
+  class(ts.bootstrap_2)
+}
+bootstrap_samp2(ts.sim, 20, 4)
 ```

### 2022-01-31 ARSimulation.Rmd
Added Plot of Bootstrap

@@
   class(ts.bootstrap_2)
+  plot(ts.bootstrap_2, type = 'l')
 }

### 2022-01-31 ARSimulation.Rmd
Sampling Distribution of Means

--- 2022-01-29 ARSimulation.Rmd
@@
 ```
+Now we can find the mean of this bootstrap, repeat the process many times, and find the point estimate for the mean and the standard error of the distribution.
+```{r, echo = False}
+bootstrap_samp2 <- function(ts.series, B, b)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  ts.samp1 <- c()
+  for(i in 1 : B)
+  {
+    ts.samp1 <- c(ts.samp1, ts.sim[point1 + i - 1])
+  }
+  print(ts.sim)
+  plot(ts.sim)
+  print(point1)
+  print(ts.samp1)
+  plot(ts.samp1, type = 'l')
+  i <- 1
+  ts.block_list <- list()
+  while(i < B)
+  {
+    x <- list(ts.samp1[i : (i + b - 1)])
+    ts.block_list <- append(ts.block_list, x)
+    i = i + b
+  }
+  print(ts.block_list)
+  samp_mean <- c()
+  for(i in 1 : 1000)
+  {
+    ts.bootstrap_1 <- sample(ts.block_list, B/b, replace = T)
+    ts.bootstrap_2 <- c()
+    for(i in 1 : (B/b)) {
+      for(j in 1 : b) {
+        ts.bootstrap_2 <- c(ts.bootstrap_2, ts.bootstrap_1[[i]][[j]])
+      }
+    }
+    samp_mean <- c(samp_mean, mean(ts.bootstrap_2))
+  }
+  print(samp_mean)
+
+}
+bootstrap_samp2(ts.sim, 20, 4)
+```

### 2022-01-31 ARSimulation.Rmd
Return Mean and Standard Error

--- 2022-01-29 ARSimulation.Rmd
@@
 ```
+Now we can find the mean of this bootstrap, repeat the process many times, and find the point estimate for the mean and the standard error of the distribution (or the standard deviation of the sample mean).
+```{r, echo = False}
+samp_dist <- function(ts.series, B, b)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  ts.samp1 <- c()
+  for(i in 1 : B)
+  {
+    ts.samp1 <- c(ts.samp1, ts.sim[point1 + i - 1])
+  }
+  print(ts.sim)
+  plot(ts.sim)
+  print(point1)
+  print(ts.samp1)
+  plot(ts.samp1, type = 'l')
+  i <- 1
+  ts.block_list <- list()
+  while(i < B)
+  {
+    x <- list(ts.samp1[i : (i + b - 1)])
+    ts.block_list <- append(ts.block_list, x)
+    i = i + b
+  }
+  print(ts.block_list)
+  samp_mean <- c()
+  for(i in 1 : 1000)
+  {
+    ts.bootstrap_1 <- sample(ts.block_list, B/b, replace = T)
+    ts.bootstrap_2 <- c()
+    for(i in 1 : (B/b)) {
+      for(j in 1 : b) {
+        ts.bootstrap_2 <- c(ts.bootstrap_2, ts.bootstrap_1[[i]][[j]])
+      }
+    }
+    samp_mean <- c(samp_mean, mean(ts.bootstrap_2))
+  }
+  print(samp_mean)
+  return(c(mean(samp_mean), sd(samp_mean)))
+
+}
+print(samp_dist(ts.sim, 20, 4))
+```

### 2022-01-31 ARSimulation.Rmd
Tried with Larger Time Series and Sample Size

--- 2022-01-31 ARSimulation.Rmd
@@
   point1 <- sample(c(1:length(ts.series)), 1, replace = T)
-  print(ts.sim)
+  print(ts.series)
   print(point1)
@@
   }
-  print(ts.sim)
-  plot(ts.sim)
+  print(ts.series)
+  plot(ts.series)
   print(point1)
@@
   {
-    ts.samp1 <- c(ts.samp1, ts.sim[point1 + i - 1])
+    ts.samp1 <- c(ts.samp1, ts.series[point1 + i - 1])
   }
-  print(ts.sim)
-  plot(ts.sim)
+  print(ts.series)
+  plot(ts.series)
   print(point1)
@@
 ```
+Now we can find the mean of this bootstrap, repeat the process many times, and find the point estimate for the mean and the standard error of the distribution (or the standard deviation of the sample mean).
+```{r, echo = False}
+samp_dist <- function(ts.series, B, b)
+{
+  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
+  ts.samp1 <- c()
+  for(i in 1 : B)
+  {
+    ts.samp1 <- c(ts.samp1, ts.series[point1 + i - 1])
+  }
+  plot(ts.series)
+  plot(ts.samp1, type = 'l')
+  i <- 1
+  ts.block_list <- list()
+  while(i < B)
+  {
+    x <- list(ts.samp1[i : (i + b - 1)])
+    ts.block_list <- append(ts.block_list, x)
+    i = i + b
+  }
+  samp_mean <- c()
+  for(i in 1 : 1000)
+  {
+    ts.bootstrap_1 <- sample(ts.block_list, B/b, replace = T)
+    ts.bootstrap_2 <- c()
+    for(i in 1 : (B/b)) {
+      for(j in 1 : b) {
+        ts.bootstrap_2 <- c(ts.bootstrap_2, ts.bootstrap_1[[i]][[j]])
+      }
+    }
+    samp_mean <- c(samp_mean, mean(ts.bootstrap_2))
+  }
+  return(c(mean(samp_mean), sd(samp_mean)))
+
+}
+print(samp_dist(ts.sim, 20, 4))
+```
+
+Let's test how well the function works now with a larger time series and a larger sample size:
+```{r, echo = False}
+ts.sim1 <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 1000)
+print(samp_dist(ts.sim1, 100, 10))
+print(mean(ts.sim1))
+```

### 2022-01-31 ARSimulation.Rmd
Removed Some Code from Beginning

@@
 
-Simulates, prints, and plots auto-regressive process of order 1 with ar = 0.5 and size = 100
-```{r, echo = FALSE}
-ts.sim <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 100) 
-ts.sim
-plot(ts.sim)
-```
-
-Splits time series into ten blocks of size 10 and stores them in a list
-```{r, echo = False}
-ts.blocks <- list(ts.sim[c(1 : 10)], ts.sim[c(11 : 20)], ts.sim[c(21 : 30)], ts.sim[c(31 : 40)], ts.sim[c(41 : 50)], ts.sim[c(51 : 60)], ts.sim[c(61 : 70)], ts.sim[c(71 : 80)], ts.sim[c(81 : 90)], ts.sim[c(91 : 100)])
-ts.blocks
-```
-
-Randomly samples 10 non-overlapping blocks (with replacement) from ts.blocks, creating a single bootstrapped time series
-```{r, echo = False}
-ts.boot1 <- sample(ts.blocks, 10, replace = T)
-ts.boot1
-class(ts.boot1)
-```
-
-ts.boot1 is a list of vectors and does not work with the plot() function, so we use a nested loop to store the values in ts.boot2, a simpler numeric vector
-```{r, echo = False}
-ts.boot2 <- c()
-for(i in 1 : 10) {
-  for(j in 1 : 10) {
-    ts.boot2 <- c(ts.boot2, ts.boot1[[i]][[j]])
-  }
-}
-ts.boot2
-class(ts.boot2)
-```
-
-Ts.boot2 is plotted
-```{r, echo = False}
-plot(ts.boot2, type = "l")
-```
 We need to start with a sample of a certain size B of consecutive points from a time series ts.series.

### 2022-02-21 Simulation_Study.Rmd
Added Simulation_Study

---
title: "Simulation_Study"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We need all necessary functions:

```{r functions, echo = FALSE}
nmblk <- function(n, l) {
  b <- n / l # assuming that is an integer
  idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE) # Sample between 1 and n - l + 1, 
  # separating by l, b times
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points 
  # decided by idx
}

mvblk <- function(n, l) {
  b <- n / l
  idx <- sample(1:(n - l + 1), b, replace = TRUE) # Sample any starting point between 1 and n - 1 + 1
  # they can overlap
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points
  # decided by idx
}

blkboot <- function(tseries, statistic, R, l) {
  n <- length(tseries) 
  ## observed statistic
  stat <- statistic(tseries) #stat stores a certain statistic of tseries using a function
  ## nonmoving block bootstrap
  nm.stat <- replicate(R, statistic(tseries[nmblk(n, l)])) # finds the statistic of nm bootstrap and repeats R times
  ## moving block bootstrap
  mv.stat <- replicate(R, statistic(tseries[mvblk(n, l)])) # finds the statistic of mv bootstrap and repeats R times
  list(stat = stat, nm.stat = nm.stat, mv.stat = mv.stat) # returns list of three values
}

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n, sd = sd)
  bt <- blkboot(x, statistic, 1000, l) 
  nm_interval = c(bt$stat - 1.96*sd(bt$nm.stat), bt$stat + 1.96*sd(bt$nm.stat))
  mv_interval = c(bt$stat - 1.96*sd(bt$mv.stat), bt$stat + 1.96*sd(bt$mv.stat))
  if (0.5 >)
  c(bt$stat, sd(bt$nm.stat), sd(bt$mv.stat), nm_interval, mv_interval) 
    # returns statistics and sd's for nm and mv respectively

}
```

Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1

```{r functions, echo = False}
ar1 <- function(x) cor(x[-1], x[-length(x)])
sim <- replicate(100, do1rep(100, 0.5, 0.1, 10, ar1))
print(sim)

```

### 2022-02-22 Simulation_Study.Rmd
Simulation Study for n = 100

@@
   mv_interval = c(bt$stat - 1.96*sd(bt$mv.stat), bt$stat + 1.96*sd(bt$mv.stat))
-  if (0.5 >)
-  c(bt$stat, sd(bt$nm.stat), sd(bt$mv.stat), nm_interval, mv_interval) 
+  nm_chi = c(999 * var(bt$nm.stat) / qchisq(p = .025, df = 999, lower.tail = FALSE), 999 * var(bt$nm.stat) / qchisq(p = .975, df = 999, lower.tail = FALSE))
+  mv_chi = c(999 * var(bt$mv.stat) / qchisq(p = .025, df = 999, lower.tail = FALSE), 999 * var(bt$mv.stat) / qchisq(p = .975, df = 999, lower.tail = FALSE))
+  nm_contains = FALSE
+  if (nm_interval[1] < theta && nm_interval[2] > theta)
+  {
+    nm_contains = TRUE
+  }
+  mv_contains = FALSE
+  if (mv_interval[1] < theta && mv_interval[2] > theta)
+  {
+    mv_contains = TRUE
+  }
+  nm_chi_contains = FALSE
+  if (nm_chi[1] < sd**2 && nm_chi[2] > sd**2)
+  {
+    nm_chi_contains = TRUE
+  }
+  mv_chi_contains = FALSE
+  if (mv_chi[1] < sd**2 && mv_chi[2] > sd**2)
+  {
+    mv_chi_contains = TRUE
+  }
+
+  c(bt$stat, sd(bt$nm.stat), sd(bt$mv.stat), nm_interval, mv_interval, nm_contains, mv_contains, nm_chi, mv_chi, nm_chi_contains, mv_chi_contains) 
     # returns statistics and sd's for nm and mv respectively
@@
 
-Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1
+Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1 (var = 0.01)
 
 ```{r functions, echo = False}
+options(max.print = 1000000)
 ar1 <- function(x) cor(x[-1], x[-length(x)])
-sim <- replicate(100, do1rep(100, 0.5, 0.1, 10, ar1))
+nmcount = 0
+mvcount = 0
+nmchicount = 0
+mvchicount = 0
+sim <- replicate(100, do1rep(100, 0.7, 0.3, 10, ar1))
 print(sim)
+for(i in sim[8,])
+{
+  if(i == 1)
+  {
+    nmcount = nmcount + 1
+  }
+}
+for(i in sim[9,])
+{
+  if(i == 1)
+  {
+    mvcount = mvcount + 1
+  }
+}
+for(i in sim[14,])
+{
+  if(i == 1)
+  {
+    nmchicount = nmchicount + 1
+  }
+}
+for(i in sim[15,])
+{
+  if(i == 1)
+  {
+    mvchicount = mvchicount + 1
+  }
+}
+c(nmcount, mvcount, nmchicount, mvchicount)
 

### 2022-02-28 Simulation_Study.Rmd
Quantile Interval

--- 2022-02-21 Simulation_Study.Rmd
@@
 do1rep <- function(n, theta, sd, l, statistic) {
-  x <- arima.sim(list(ar = theta), n, sd = sd)
+  x <- arima.sim(list(ar = theta), n = n, sd = sd) 
+  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)
+
   bt <- blkboot(x, statistic, 1000, l)
-  nm_interval = c(bt$stat - 1.96*sd(bt$nm.stat), bt$stat + 1.96*sd(bt$nm.stat))
-  mv_interval = c(bt$stat - 1.96*sd(bt$mv.stat), bt$stat + 1.96*sd(bt$mv.stat))
-  if (0.5 >)
-  c(bt$stat, sd(bt$nm.stat), sd(bt$mv.stat), nm_interval, mv_interval) 
-    # returns statistics and sd's for nm and mv respectively
+
+  # Variance Stuff that isn't working
+  # 95 % Confidence Interval for Variance -> Lower bound: (n - 1) * sample_variance(X_t) / chisq(.025, n - 1)
+  # Upper bound: (n - 1) * sample_variance(X_t) / chisq(.975, n - 1)
+  # sample_variance(X_t) = se^2 * n
+
+ # nm_lower_bound with quantile function
+
+  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
+  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))
+
+  nm_contains = FALSE
+  if (nm_interval[1] < 0 && nm_interval[2] > 0)
+  {
+    nm_contains = TRUE
+  }
+  mv_contains = FALSE
+  if (mv_interval[1] < 0 && mv_interval[2] > 0)
+  {
+    mv_contains = TRUE
+  }
+
+  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)
+
+    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
 
@@
 
-Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1
+Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1 (var = 0.01)
 
 ```{r functions, echo = False}
+options(max.print = 1000000)
 ar1 <- function(x) cor(x[-1], x[-length(x)])
-sim <- replicate(100, do1rep(100, 0.5, 0.1, 10, ar1))
+m1 <- function(x) mean(x)
+nmcount = 0
+mvcount = 0
+nmchicount = 0
+mvchicount = 0
+
+sim <- replicate(100, do1rep(100, 0.1, 0.1, 10, m1))
+
+my_summary <- function(x)
+{
+  c(rowMeans(x), sd(x[1,]))
+}
+my_summary(sim)
 print(sim)
 
+#Counts how many times the true statistic was found in the interval
+
 ```

### 2022-03-06 Simulation_Study.Rmd
Vary Sample Size with Same Block Length

@@
   x <- arima.sim(list(ar = theta), n = n, sd = sd)
+
   # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)
@@
   bt <- blkboot(x, statistic, 1000, l)
-
-  # Variance Stuff that isn't working
-  # 95 % Confidence Interval for Variance -> Lower bound: (n - 1) * sample_variance(X_t) / chisq(.025, n - 1)
-  # Upper bound: (n - 1) * sample_variance(X_t) / chisq(.975, n - 1)
-  # sample_variance(X_t) = se^2 * n
 
@@
 m1 <- function(x) mean(x)
-nmcount = 0
-mvcount = 0
-nmchicount = 0
-mvchicount = 0
-
-sim <- replicate(100, do1rep(100, 0.1, 0.1, 10, m1))
 
@@
 {
-  c(rowMeans(x), sd(x[1,]))
+  rm = rowMeans(x)
+  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]))
 }
-my_summary(sim)
-print(sim)
-
-#Counts how many times the true statistic was found in the interval
 
 ```
+
+```{r functions, echo = False}
+sim <- replicate(100, do1rep(100, 0.5, 0.1, 10, m1))
+
+n_100 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(200, 0.5, 0.1, 10, m1))
+
+n_200 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(300, 0.5, 0.1, 10, m1))
+
+n_300 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(400, 0.5, 0.1, 10, m1))
+
+n_400 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(500, 0.5, 0.1, 10, m1))
+
+n_500 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(600, 0.5, 0.1, 10, m1))
+
+n_600 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(700, 0.5, 0.1, 10, m1))
+
+n_700 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(800, 0.5, 0.1, 10, m1))
+
+n_800 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(900, 0.5, 0.1, 10, m1))
+
+n_900 <- my_summary(sim)
+
+sim <- replicate(100, do1rep(1000, 0.5, 0.1, 10, m1))
+
+n_1000 <- my_summary(sim)
+
+n_constant_l.data <- data.frame(
+   n = c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000),
+   ar = c(0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
+   sigma = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1),
+   l = c(10, 10, 10, 10, 10, 10, 10, 10, 10, 10),
+   mean = c(n_100[1], n_200[1], n_300[1], n_400[1], n_500[1], n_600[1], n_700[1], n_800[1], n_900[1], n_1000[1]), 
+   nm_se = c(n_100[2], n_200[2], n_300[2], n_400[2], n_500[2], n_600[2], n_700[2], n_800[2], n_900[2], n_1000[2]),
+   nm_lower = c(n_100[3], n_200[3], n_300[3], n_400[3], n_500[3], n_600[3], n_700[3], n_800[3], n_900[3], n_1000[3]), 
+   nm_upper = c(n_100[4], n_200[4], n_300[4], n_400[4], n_500[4], n_600[4], n_700[4], n_800[4], n_900[4], n_1000[4]),
+   nm_success = c(n_100[5], n_200[5], n_300[5], n_400[5], n_500[5], n_600[5], n_700[5], n_800[5], n_900[5], n_1000[5]),
+   mv_se = c(n_100[6], n_200[6], n_300[6], n_400[6], n_500[6], n_600[6], n_700[6], n_800[6], n_900[6], n_1000[6]),
+   mv_lower = c(n_100[7], n_200[7], n_300[7], n_400[7], n_500[7], n_600[7], n_700[7], n_800[7], n_900[7], n_1000[7]), 
+   mv_upper = c(n_100[8], n_200[8], n_300[8], n_400[8], n_500[8], n_600[8], n_700[8], n_800[8], n_900[8], n_1000[8]),
+   mv_success = c(n_100[9], n_200[9], n_300[9], n_400[9], n_500[9], n_600[9], n_700[9], n_800[9], n_900[9], n_1000[9]),
+   true_se = c(n_100[10], n_200[10], n_300[10], n_400[10], n_500[10], n_600[10], n_700[10], n_800[10], n_900[10], n_1000[10]),
+   nm_diff = c(n_100[11], n_200[11], n_300[11], n_400[11], n_500[11], n_600[11], n_700[11], n_800[11], n_900[11], n_1000[11]),
+   mv_diff = c(n_100[12], n_200[12], n_300[12], n_400[12], n_500[12], n_600[12], n_700[12], n_800[12], n_900[12], n_1000[12]),
+   nm_percent_change = c(n_100[13], n_200[13], n_300[13], n_400[13], n_500[13], n_600[13], n_700[13], n_800[13], n_900[13], n_1000[13]),
+   mv_percent_change = c(n_100[14], n_200[14], n_300[14], n_400[14], n_500[14], n_600[14], n_700[14], n_800[14], n_900[14], n_1000[14])
+)
+print(n_constant_l.data)
+```

### 2022-03-07 Simulation_Study.Rmd
Plots for Simulation

--- 2022-02-28 Simulation_Study.Rmd
@@
 {
-  c(rowMeans(x), sd(x[1,]))
+  rm = rowMeans(x)
+  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]))
 }
-my_summary(sim)
-print(sim)
-
-#Counts how many times the true statistic was found in the interval
 
 ```
+
+```{r functions, echo = False}
+n_constant_l.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_change = c(m[13]),
+     mv_percent_change = c(m[14])
+    )
+    n_constant_l.data = rbind(n_constant_l.data, tobind.data)
+  }
+}
+
+print(n_constant_l.data)
+```
+
+```{r functions, echo = False}
+
+plot(n_constant_l.data$n, n_constant_l.data$nm_success, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+```
+
+```{r functions, echo = False}
+
+plot(n_constant_l.data$n, n_constant_l.data$mv_success, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+```
+
+```{r functions, echo = False}
+
+plot(n_constant_l.data$n, n_constant_l.data$nm_diff, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+```
+
+```{r functions, echo = False}
+
+plot(n_constant_l.data$n, n_constant_l.data$mv_diff, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+```
+
+```{r functions, echo = False}
+
+plot(n_constant_l.data$n, n_constant_l.data$nm_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+```
+
+```{r functions, echo = False}
+
+plot(n_constant_l.data$n, n_constant_l.data$mv_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+```
+
+```{r functions, echo = False}
+
+plot(n_constant_l.data$n, n_constant_l.data$mv_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+```

### 2022-03-12 Simulation_Study.Rmd
Added Some Tests

@@
 ```{r functions, echo = False}
-n_constant_l.data <- data.frame(
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+install.packages("ggplot2")
+library(ggplot2)
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
 
@@
   {
-    sim <- replicate(100, do1rep(n, 0.5, 0.1, 10, m1))
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, 10, m1))
     m <- my_summary(sim)
@@
      n = c(n),
-     ar = c(0.5),
+     ar = c(0.1),
      sigma = c(0.1),
@@
      mv_diff = c(m[12]),
-     nm_percent_change = c(m[13]),
-     mv_percent_change = c(m[14])
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
     )
-    n_constant_l.data = rbind(n_constant_l.data, tobind.data)
+    test.data = rbind(test.data, tobind.data)
   }
@@
 
-print(n_constant_l.data)
+print(test.data)
 ```
@@
 ```{r functions, echo = False}
+install.packages("ggplot2")
+library(ggplot2)
 
-plot(n_constant_l.data$n, n_constant_l.data$nm_success, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
 ```
@@
 ```{r functions, echo = False}
+install.packages("ggplot2")
+library(ggplot2)
 
-plot(n_constant_l.data$n, n_constant_l.data$mv_success, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
 ```
@@
 ```{r functions, echo = False}
+install.packages("ggplot2")
+library(ggplot2)
 
-plot(n_constant_l.data$n, n_constant_l.data$nm_diff, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
 ```
-
-```{r functions, echo = False}
-
-plot(n_constant_l.data$n, n_constant_l.data$mv_diff, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
-```
-
-```{r functions, echo = False}
-
-plot(n_constant_l.data$n, n_constant_l.data$nm_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
-```
-
-```{r functions, echo = False}
-
-plot(n_constant_l.data$n, n_constant_l.data$mv_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
-```
-
-```{r functions, echo = False}
-
-plot(n_constant_l.data$n, n_constant_l.data$mv_percent_change, pch = 19, col = rgb(red = 0.2, green = 0.2, blue = 0.2, alpha = 0.3))
-```

### 2022-03-12 Simulation_Study.Rmd
Added Some Tests for Constant N/L Ratio

@@
 
-Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1 (var = 0.01)
+Let's conduct a simulation study with n = 100, ar = 0.1, and sd = 0.1 (var = 0.01)
 
@@
 ```{r functions, echo = False}
-install.packages("ggplot2")
-library(ggplot2)
 
@@
 ```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```

### 2022-03-13 Simulation_Study.Rmd
Tests for Different Block Lengths

@@
 ```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 8, 27, 64, 125, 216, 343, 512, 729, 1000, 1331, 1728, 2197, 2744, 3375))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, n**(1/3), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(n**(1/3)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 16, 81, 256, 625, 1296, 2401, 4096))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, n**(1/4), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(n**(1/4)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 32, 243, 1024, 3125, 7776))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.1, 0.1, n**(1/5), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.1),
+     sigma = c(0.1),
+     l = c(n**(1/5)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```

### 2022-03-15 Simulation_Study.Rmd
Tests for AR = 0.5

@@
 
+Let's first do this while keeping l = 10 constant.
+
 ```{r functions, echo = False}
@@
 ```
+There doesn't seem to be any clear pattern when looking at these larger sample sizes. Let's zoom in a little.
 
@@
 ```
+The pattern is not super clear, although it seems to begin to increasingly underestimate somewhere around n = 200.
 
@@
 ```
+For these smaller sample sizes, it seems to have a tendency to increasingly underestimate as n decreases. A notable drop occurs around n = 40.
 
@@
 ```
+Again, for these smaller sample sizes, it seems to have a tendency to increasingly underestimate as n decreases. Notable drops occur around n = 50 and n = 20.
 
@@
 ```
+Let's try this while keeping the ratio n/l = 10 constant.
 
@@
 ```
+There is no pattern for these larger sample sizes, let's zoom in.
 
@@
 ```
+Again, there is really no pattern here.
 
@@
 ```
+No pattern.
 
@@
 ```
+No pattern, it seems that changing the sample size while keeping the ratio constant has no effect on the variance estimation.
+However it appears that on average, using this ratio results in a slight underestimation of the variance, regardless of the sample size.
 
@@
 ```
+Let's try it while setting l equal n^(1/3).
+
 ```{r functions, echo = False}
@@
 ```
+It seems to begin to clearly underestimate around n = 27.
 
@@
 ```
+Let's try it while setting l equal n^(1/4).
+
 ```{r functions, echo = False}
@@
 ```
+There seems to be a more steady increase in underestimation, until it drops to -1 when n = 1.
 
@@
 ```
+It is difficult to discern a pattern until it drops to -1 when n = 1. However, even at the higher n's, it seems to be somewhat underestimating the variance.
 
@@
 ```
+Let's conduct a simulation study with n = 100, ar = 0.1, and sd = 0.1 (var = 0.01)
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```

### 2022-03-20 Simulation_Study.Rmd
Tests for ar = 0.1, 0.5, and 0.9

@@
 ```
-Let's conduct a simulation study with n = 100, ar = 0.1, and sd = 0.1 (var = 0.01)
+Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1 (var = 0.01). Let's first do this while keeping l = 10 constant.
 
@@
 ```
-
-```{r functions, echo = False}
+No clear pattern, but it seems to significantly underestimate the variance on average.
+
+```{r functions, echo = False}
+install.packages("ggplot2")
+library(ggplot2)
 
@@
 ```
+
 ```{r functions, echo = False}
@@
 ```
+Again, no super clear pattern but it seems to underestimate the variance on average at this range of sample sizes.
 
@@
 
+The underestimation begins to become far more noticeable around n = 80.
+
 ```{r functions, echo = False}
@@
 
+At this range, there seems to be a drop either at n = 70 or n = 50.
+
 ```{r functions, echo = False}
@@
 ```
+
+Let's try this while keeping the ratio n/l = 10 constant.
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 8, 27, 64, 125, 216, 343, 512, 729, 1000, 1331, 1728, 2197, 2744, 3375))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, n**(1/3), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(n**(1/3)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 16, 81, 256, 625, 1296, 2401, 4096))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, n**(1/4), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(n**(1/4)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 32, 243, 1024, 3125, 7776))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.5, 0.1, n**(1/5), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.5),
+     sigma = c(0.1),
+     l = c(n**(1/5)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, 10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+install.packages("ggplot2")
+library(ggplot2)
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700, 1800, 1900, 2000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(50, 100, 150, 200, 250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 950, 1000))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(20, 40, 60, 80, 100, 120, 140, 160, 180, 200, 220, 240, 260, 280, 300, 320, 340, 360, 380, 400, 420, 440, 460, 480, 500))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150, 160, 170, 180, 190, 200, 210, 220, 230, 240, 250))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, n/10, m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(n/10),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+install.packages("ggplot2")
+library(ggplot2)
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 8, 27, 64, 125, 216, 343, 512, 729, 1000, 1331, 1728, 2197, 2744, 3375))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, n**(1/3), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(n**(1/3)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+install.packages("ggplot2")
+library(ggplot2)
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 16, 81, 256, 625, 1296, 2401, 4096))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, n**(1/4), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(n**(1/4)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```
+
+```{r functions, echo = False}
+test.data <- data.frame(
+
+   n = c(),
+   ar = c(),
+   sigma = c(),
+   l = c(),
+   mean = c(), 
+   nm_se = c(),
+   nm_lower = c(), 
+   nm_upper = c(),
+   nm_success = c(),
+   mv_se = c(),
+   mv_lower = c(), 
+   mv_upper = c(),
+   mv_success = c(),
+   true_se = c(),
+   nm_diff = c(),
+   mv_diff = c(),
+   nm_percent_change = c(),
+   mv_percent_change = c()
+)
+
+for(n in c(1, 32, 243, 1024, 3125, 7776))
+{
+  for(i in 1:3)
+  {
+    sim <- replicate(100, do1rep(n, 0.9, 0.1, n**(1/5), m1))
+    m <- my_summary(sim)
+    tobind.data <- data.frame(
+     n = c(n),
+     ar = c(0.9),
+     sigma = c(0.1),
+     l = c(n**(1/5)),
+     mean = c(m[1]), 
+     nm_se = c(m[2]),
+     nm_lower = c(m[3]), 
+     nm_upper = c(m[4]),
+     nm_success = c(m[5]),
+     mv_se = c(m[6]),
+     mv_lower = c(m[7]), 
+     mv_upper = c(m[8]),
+     mv_success = c(m[9]),
+     true_se = c(m[10]),
+     nm_diff = c(m[11]),
+     mv_diff = c(m[12]),
+     nm_percent_diff = c(m[13]),
+     mv_percent_diff = c(m[14])
+    )
+    test.data = rbind(test.data, tobind.data)
+  }
+}
+
+print(test.data)
+```
+
+```{r functions, echo = False}
+
+test_reshaped <- data.frame(x = test.data$n,                           
+                       y = c(test.data$nm_percent_diff, test.data$mv_percent_diff),
+                       group = c(rep("Non-moving Percent Difference", nrow(test.data)),
+                                 rep("Moving Percent Difference", nrow(test.data))))
+
+ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
+
+```

### 2022-03-27 AR_=_0.2.Rmd
Added Test for AR = 0.2

---
title: "Tests for AR = 0.2"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We need all necessary functions:

```{r functions, echo = FALSE}
nmblk <- function(n, l) {
  b <- n / l # assuming that is an integer
  idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE) # Sample between 1 and n - l + 1, 
  # separating by l, b times
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points 
  # decided by idx
}

mvblk <- function(n, l) {
  b <- n / l
  idx <- sample(1:(n - l + 1), b, replace = TRUE) # Sample any starting point between 1 and n - 1 + 1
  # they can overlap
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points
  # decided by idx
}

blkboot <- function(tseries, statistic, R, l) {
  n <- length(tseries) 
  ## observed statistic
  stat <- statistic(tseries) #stat stores a certain statistic of tseries using a function
  ## nonmoving block bootstrap
  nm.stat <- replicate(R, statistic(tseries[nmblk(n, l)])) # finds the statistic of nm bootstrap and repeats R times
  ## moving block bootstrap
  mv.stat <- replicate(R, statistic(tseries[mvblk(n, l)])) # finds the statistic of mv bootstrap and repeats R times
  list(stat = stat, nm.stat = nm.stat, mv.stat = mv.stat) # returns list of three values
}

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n = n, sd = sd)

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  if (nm_interval[1] < 0 && nm_interval[2] > 0)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < 0 && mv_interval[2] > 0)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

}
```

```{r functions, echo = False}
options(max.print = 1000000)
ar1 <- function(x) cor(x[-1], x[-length(x)])
m1 <- function(x) mean(x)

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]))
}

```

Let's start with n = 400. We want l to decrease as n decreases, but we also want the ratio k (l / n) to increase, so we can set l = sqrt(n). For n = 400, l = 20. We can do 3 trials each for 3 different sigmas.

```{r functions, echo = False}
t1 <- replicate(3, my_summary(replicate(100, do1rep(400, 0.2, 0.1, 20, m1))))
print(t1)
```

```{r functions, echo = False}
t2 <- replicate(3, my_summary(replicate(100, do1rep(400, 0.2, 1, 20, m1))))
print(t2)
```

```{r functions, echo = False}
t3 <- replicate(3, my_summary(replicate(100, do1rep(400, 0.2, 10, 20, m1))))
print(t3)
```

As expected, the coverage rates for 95% confidence intervals at this sample size are generally close to 95%. We also observe that this is true regardless of sigma.

Now let's try it with n = 361 and l = 19.
```{r functions, echo = False}
t4 <- replicate(3, my_summary(replicate(100, do1rep(361, 0.2, 0.1, 19, m1))))
print(t4)
```

```{r functions, echo = False}
t5 <- replicate(3, my_summary(replicate(100, do1rep(324, 0.2, 0.1, 18, m1))))
print(t5)
```

```{r functions, echo = False}
t6 <- replicate(3, my_summary(replicate(100, do1rep(289, 0.2, 0.1, 17, m1))))
print(t6)
```

At this n, we begin to observe more coverage rates below .90. The highest observation is .90 for the trial 2 moving block bootstrap, and the lowest observation is .85 for the trial 3 non-moving block bootstrap. Until now, we have only observed coverage rates above .87. If we run it again, we observe acceptable coverage rates. Still, this shows that even at this sample size, we can observe success rates that are not acceptable. Let's go to the next lowest n that is a square of some l.

```{r functions, echo = False}
tt <- replicate(3, my_summary(replicate(100, do1rep(289, 0.2, 0.1, 17, m1))))
print(tt)
```

```{r functions, echo = False}
t7 <- replicate(3, my_summary(replicate(100, do1rep(256, 0.2, 0.1, 16, m1))))
print(t7)
```

At this n, the coverage rates seem to be generally close to .95, so it seems like the trials for n = 289 may just have been a bit unlucky.

```{r functions, echo = False}
t8 <- replicate(3, my_summary(replicate(100, do1rep(225, 0.2, 0.1, 15, m1))))
print(t8)
```

```{r functions, echo = False}
t9 <- replicate(3, my_summary(replicate(100, do1rep(196, 0.2, 0.1, 14, m1))))
print(t9)
```

```{r functions, echo = False}
t10 <- replicate(3, my_summary(replicate(100, do1rep(169, 0.2, 0.1, 13, m1))))
print(t10)
```

At this n, 4 of the 6 coverage rates observed are below .90. This is first sample size at which we have observed a coverage rate below .85. The highest coverage rate observed is .93.

```{r functions, echo = False}
t11 <- replicate(3, my_summary(replicate(100, do1rep(144, 0.2, 0.1, 12, m1))))
print(t11)
```

These coverage rates seem to be better than those for n = 163, although it is not great, with two success rates below .90.

```{r functions, echo = False}
t12 <- replicate(3, my_summary(replicate(100, do1rep(121, 0.2, 0.1, 11, m1))))
print(t12)
```

Three coverage rates below .90, and only one above .90.

```{r functions, echo = False}
t13 <- replicate(3, my_summary(replicate(100, do1rep(100, 0.2, 0.1, 10, m1))))
print(t13)
```

four coverage rates below .90.

```{r functions, echo = False}
t14 <- replicate(3, my_summary(replicate(100, do1rep(81, 0.2, 0.1, 9, m1))))
print(t14)
```

Four coverage rates below .90. Highest coverage rate is .94.

```{r functions, echo = False}
t15 <- replicate(3, my_summary(replicate(100, do1rep(64, 0.2, 0.1, 8, m1))))
print(t15)
```

Five coverage rates below .90, and one below .85.

So it seems that the coverage rates are now clearly below .95, so the question is at what range of sample sizes do the coverage rates become unacceptable. When n was 289, we observed 5 coverage rates below .90, but for n's below that we observed acceptable coverage rates. Still, the fact that we observed such low coverage rates for this sample size shows that the variance can be heavily underestimated for sample sizes of this size. Once n hit 169, at least 2 coverage rates were below .90 for each sample size after that.

### 2022-04-17 Block-Bootstrap.Rmd
New Tests

---
title: "More Tests" 
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We need all necessary functions:

```{r functions, echo = FALSE}
nmblk <- function(n, l) {
  b <- n / l # assuming that is an integer
  idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE) # Sample between 1 and n - l + 1, 
  # separating by l, b times
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points 
  # decided by idx
}

mvblk <- function(n, l) {
  b <- n / l
  idx <- sample(1:(n - l + 1), b, replace = TRUE) # Sample any starting point between 1 and n - 1 + 1
  # they can overlap
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points
  # decided by idx
}

blkboot <- function(tseries, statistic, R, l) {
  n <- length(tseries) 
  ## observed statistic
  stat <- statistic(tseries) #stat stores a certain statistic of tseries using a function
  ## nonmoving block bootstrap
  nm.stat <- replicate(R, statistic(tseries[nmblk(n, l)])) # finds the statistic of nm bootstrap and repeats R times
  ## moving block bootstrap
  mv.stat <- replicate(R, statistic(tseries[mvblk(n, l)])) # finds the statistic of mv bootstrap and repeats R times
  list(stat = stat, nm.stat = nm.stat, mv.stat = mv.stat) # returns list of three values
}

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n = n, sd = sd)

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  if (nm_interval[1] < 0 && nm_interval[2] > 0)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < 0 && mv_interval[2] > 0)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

}
```

```{r more_functions, echo = False}
options(max.print = 1000000)
ar1 <- function(x) cor(x[-1], x[-length(x)])
m1 <- function(x) mean(x)

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]))
}

```

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 20, m1)))
root_0.2_1 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_1 <- cbind(root_0.2_1, c(n, l, t))

}

print(root_0.2_1)
```
```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(225, 0.2, 0.1, 15, m1)))
root_0.2_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_2 <- cbind(root_0.2_2, c(n, l, t))
}

print(root_0.2_2)
```
Observed coverage rates seem to be lower, when n was 169 and 144, coverage rates below .90 were recorded for the non-moving method.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
root_0.2_3 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_3 <- cbind(root_0.2_3, c(n, l, t))
}

print(root_0.2_3)
```
For all n's at or below 100, the coverage rates are below .90.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(625, 0.4, 0.1, 25, m1)))
root_0.4_1 <- data.frame(c(625, 25, o))
for(l in 24:21)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_1 <- cbind(root_0.4_1, c(n, l, t))

}

print(root_0.4_1)
```

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 20, m1)))
root_0.4_2 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_2 <- cbind(root_0.4_2, c(n, l, t))

}

print(root_0.4_2)
```

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(225, 0.4, 0.1, 15, m1)))
root_0.4_3 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_3 <- cbind(root_0.4_3, c(n, l, t))

}

print(root_0.4_3)
```

Observed coverage rates seem to be lower, when n was 144 and 121, both coverage rates recorded were below .90.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
root_0.4_4 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_4 <- cbind(root_0.4_4, c(n, l, t))

}

print(root_0.4_4)
```

For all n's at or below 100, the coverage rates are below .90.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 30, m1)))
root_0.6_1 <- data.frame(c(900, 30, o))
for(l in 29:26)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_1 <- cbind(root_0.6_1, c(n, l, t))

}

print(root_0.6_1)
```

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(625, 0.6, 0.1, 25, m1)))
root_0.6_2 <- data.frame(c(625, 25, o))
for(l in 24:21)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_2 <- cbind(root_0.6_2, c(n, l, t))

}

print(root_0.6_2)
```
Observed coverage rates seem to be lower, when n was 529, a coverage rate below .90 was recorded for the non-moving method.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(400, 0.6, 0.1, 20, m1)))
root_0.6_3 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_3 <- cbind(root_0.6_3, c(n, l, t))

}

print(root_0.6_3)
```

Observed coverage rates seem to be lower, when n was 324 and 256, coverage rate below .90 was recorded for the non-moving methods.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(225, 0.6, 0.1, 15, m1)))
root_0.6_4 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_4 <- cbind(root_0.6_4, c(n, l, t))

}

print(root_0.6_4)
```
9 out of the 10 coverage rates are below .90.

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(1600, 0.8, 0.1, 40, m1)))
root_0.8_1 <- data.frame(c(1600, 40, o))
for(l in 39:36)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.8, 0.1, l, m1)))
  root_0.8_1 <- cbind(root_0.8_1, c(n, l, t))

}

print(root_0.8_1)
```

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(1225, 0.8, 0.1, 35, m1)))
root_0.8_2 <- data.frame(c(1225, 35, o))
for(l in 34:31)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.8, 0.1, l, m1)))
  root_0.8_2 <- cbind(root_0.8_2, c(n, l, t))

}

print(root_0.8_2)
```
```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(900, 0.8, 0.1, 30, m1)))
root_0.8_3 <- data.frame(c(900, 30, o))
for(l in 29:26)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.8, 0.1, l, m1)))
  root_0.8_3 <- cbind(root_0.8_3, c(n, l, t))

}

print(root_0.8_3)
```
Observed coverage rates seem to be lower, when n was 676, coverage rates below .90 was recorded for both methods

```{r functions, echo = False}
o = my_summary(replicate(1000, do1rep(625, 0.8, 0.1, 25, m1)))
root_0.8_4 <- data.frame(c(625, 25, o))
for(l in 24:21)
{
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.8, 0.1, l, m1)))
  root_0.8_4 <- cbind(root_0.8_4, c(n, l, t))

}

print(root_0.8_4)
```
All of the coverage rates are below .90.

### 2022-04-26 blkboot_function.R
Test Remove File

@@ -1,66 +1,0 @@
-n <- 200
-x <- stats::arima.sim(list(ar = 0.5), n) + 2
-
-nmblk <- function(n, l) {
-  b <- n / l # assuming that is an integer
-  idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE) # Sample between 1 and n - l + 1, 
-  # separating by l, b times
-  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points 
-  # decided by idx
-}
-
-nmblk(n, 10)
-
-#idc <- sample(seq(1, 191, by = 10), 20, replace = TRUE)
-#print(idc)
-#outer(0:9, idc)
-#c(outer(0:9, idc, '+'))
-
-mvblk <- function(n, l) {
-  b <- n / l
-  idx <- sample(1:(n - l + 1), b, replace = TRUE) # Sample any starting point between 1 and n - 1 + 1
-  # they can overlap
-  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points
-  # decided by idx
-}
-
-mvblk(n, 10)
-
-#idk <- sample(1:191, 20, replace = TRUE)
-#print(idk)
-#outer(0:9, idk)
-#c(outer(0:9, idk, '+'))
-
-blkboot <- function(tseries, statistic, R, l) {
-  n <- length(tseries) 
-  ## observed statistic
-  stat <- statistic(tseries) #stat stores a certain statistic of tseries using a function
-  ## nonmoving block bootstrap
-  nm.stat <- replicate(R, statistic(tseries[nmblk(n, l)])) # finds the statistic of nm bootstrap and repeats R times
-  ## moving block bootstrap
-  mv.stat <- replicate(R, statistic(tseries[mvblk(n, l)])) # finds the statistic of mv bootstrap and repeats R times
-  list(stat = stat, nm.stat = nm.stat, mv.stat = mv.stat) # returns list of three values
-}
-
-## an experiment
-ar1 <- function(x) cor(x[-1], x[-length(x)]) # correlation of series without the first entry vs series without the last entry
-m1 <- function(x) mean(x)
-m2 <- function(x) median(x)
-
-y <- c(0, 1, 3, 5)
-y[-1]
-y[-length(y)]
-cor(y[-1], y[-length(y)])
-
-blkboot(x, ar1, 1000, 10)
-
[…]

### 2022-04-27 Manuscript/Block-Bootstrap.Rmd
Two Directories

--- 2022-04-26 Data/Block-Bootstrap.Rmd
@@
 ```
-Observed coverage rates seem to be lower, when n was 169 and 144, coverage rates below .90 were recorded for the non-moving method.
+Observed coverage rates seem to be lower...
 
@@
 ```
+Coverage for n = 256 below .90.
 
@@
 
-Observed coverage rates seem to be lower, when n was 144 and 121, both coverage rates recorded were below .90.
+Observed coverage rates seem to be lower, when n was 144 and 121, both coverage rates recorded were below .90. For n = 225, coverage rate below .90 recorded for moving method.
 
@@
 ```
-Observed coverage rates seem to be lower, when n was 529, a coverage rate below .90 was recorded for the non-moving method.
 
@@
 
-Observed coverage rates seem to be lower, when n was 324 and 256, coverage rate below .90 was recorded for the non-moving methods.
+Observed coverage rates seem to be lower, when n was 324 and 256, coverage rate below .90 was recorded for the moving methods.
 
@@
 ```
-Observed coverage rates seem to be lower, when n was 676, coverage rates below .90 was recorded for both methods
+Observed coverage rates seem to be lower, when n was 841 and 784, coverage rates below .90 were recorded for non-moving method, and when n was 900, coverage rate fro moving method was below .90.
 
@@
 ```
-All of the coverage rates are below .90.
+All but 3 of the coverage rates are below .90.

### 2022-08-30 Manuscript/manuscript.tex
Latex file

% Created by Bonita Graham
% Last update: December 2019 By Kestutis Bendinskas

% Authors: 
% Please do not make changes to the preamble until after the solid line of %s.

\documentclass[10pt]{article}
\usepackage[explicit]{titlesec}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\usepackage{hyphenat}
\usepackage{ragged2e}
\RaggedRight

% % These commands change the font. If you do not have Garamond on your computer, you will need to install it.
% \usepackage{garamondx}
% \usepackage[T1]{fontenc}
% \usepackage{amsmath, amsthm}
% \usepackage{graphicx}
% \usepackage{hyperref}
% \usepackage{xcolor}
% \newcommand{\jy}[1]{\textcolor{orange}{JY: (#1)}}
% \usepackage{booktabs}

% This adjusts the underline to be in keeping with word processors.
\usepackage{soul}
\setul{.6pt}{.4pt}

% The following sets margins to 1 in. on top and bottom and .75 in on left and right, and remove page numbers.
\usepackage{geometry}
\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{gobble}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}

% These Commands create the label style for tables, figures and equations.
\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
\captionsetup{labelformat=simple, labelsep=period}
\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
\renewcommand{\theequation}{\arabic{equation}}
\makeatletter
\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
\makeatother
\setlength{\intextsep}{10pt}
\setlength{\abovecaptionskip}{2pt}
\setlength{\belowcaptionskip}{-10pt}

\renewcommand{\textfraction}{0.10}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.90}

% These commands set the paragraph and line spacing
\titleformat{\section}
  {\normalfont}{\thesection}{1em}{\MakeUppercase{\textbf{#1}}}
\titlespacing\section{0pt}{0pt}{-10pt}
\titleformat{\subsection}
  {\normalfont}{\thesubsection}{1em}{\textit{#1}}
\titlespacing\subsection{0pt}{0pt}{-8pt}
\renewcommand{\baselinestretch}{1.15}

% This designs the title display style for the maketitle command
\makeatletter
\newcommand\sixteen{\@setfontsize\sixteen{17pt}{6}}
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
\sixteen\bfseries \@title
\medskip
\end{flushleft}
\textit{\@author}
\egroup}
\makeatother

% This styles the bibliography and citations.
%\usepackage[biblabel]{cite}
\usepackage[sort&compress]{natbib}
\setlength\bibindent{2em}
\makeatletter
\renewcommand\@biblabel[1]{\textbf{#1.}\hfill}
\makeatother
\renewcommand{\citenumfont}[1]{\textbf{#1}}
\bibpunct{}{}{,~}{s}{,}{,}
\setlength{\bibsep}{0pt plus 0.3ex}

\usepackage{float}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Authors: Add additional packages and new commands here.  
% Limit your use of new commands and special formatting.

% Place your title below. Use Title Capitalization.
\title{Time Series Length at Which Block Bootstrapping is Effective for Estimation of a Statistic}

% Add author information below. Communicating author is indicated by an asterisk, the affiliation is shown by superscripted lower case letter if several affiliations need to be noted.
\author{
Mathew Chandy*, Jun Yan \\ \medskip 
Department of Statistics, University of Connecticut, Storrs, CT  \\  \medskip 
Students: mathew.chandy@uconn.edu* \\
Mentor: jun.yan@uconn.edu 
}

\pagestyle{empty}

\begin{document}

% Makes the title and author information appear.
\vspace*{.01 in}
\maketitle
\vspace{.12 in}

% Abstracts are required.
\section*{abstract}

Block bootstrapping is a method that can be used for estimating a statistic of a time series. It involves splitting a series into blocks (in order to account for the time factor) and re-sampling the blocks to create many new bootstrapped time series. This method becomes more effective as the length of the time series increases. The question for this study is how does one determine at what length the block bootstrap method stops being an effective method to estimate a statistic of a time series.

% Keywords are required.
\section*{keywords} 
Block Bootstrap

\vspace{.12 in}

% Start the main part of the manuscript here.
% Comment out section headings if inappropriate to your discipline.
% If you add additional section or subsection headings, use an asterisk * to avoid numbering.

\section{Introduction}

For this study, many block bootstrap simulations were conducted with R. At the base level, we are block-bootstrapping an auto-regressive process with true mean 0. Bootstrapping is the term for creating new samples of the same size by re-sampling from the original sample with replacement. Many bootstrapped samples are used to create a distribution of sampling means to estimate mean and variance. This works for samples that are not dependent. However, for a time series such as an auto-regressive process, a different procedure is required to account for the time dependence. In such a case, the series is split into blocks that may overlap (moving block bootstrap) or may not overlap (non-moving block bootstrap). These blocks are then re-sampled to create new bootstrapped time series.

In our experiment, we find the means of a 1000 block-bootstrapped time series, and create a 95 \% confidence interval of the means. We replicate this 1000 times, and record the proportion of confidence intervals that recover the true mean (coverage rate). We are effectively observing how successful the bootstrapping process is at estimating the mean and variance. The key variable being observed was n, the length of the time series, or the size of the sample. It is known that as n increases, block bootstrapping will become a less accurate method for estimation (the coverage rates will decrease). The question is at what range of n values does this start to become a problem.

In this experiment, there are certain factors that are expected to affect the coverage rates. As the AR coefficient (the time dependence) of the time series increases, we expect the coverage rates of the confidence intervals to decrease. The coverage rates are also affected by the size of the blocks - more specifically, the ratio of the size of the blocks (l) to the size of the time series (L) - and whether or not they overlap.

So to solve the question of what n is necessary for effective block bootstrapping, while still accounting for all these factors, the simulations were repeated for multiple combinations of AR coefficient and l:L ratios. In addition, the coverage rates for both the non-moving and moving methods were recorded.

\section{Literature Review}

\section{Data}

\section{Methods}

\section{Results}

\section{Discussion}

\bibliographystyle{chicago}
\bibliography{citations.bib}

% \section*{acknowledgements}
% The authors thank the University of Connecticut and the UConn Department of Statistics.
%Note correct LaTeX quotations above. Do not use the " symbol, but rather double ` followed by double '

% The About the Student Author section is NOT optional.  Write a paragraph about the student; see previous journal editions for examples.
% If there is more than one student author, you must move the comment below.
\section*{about the student author}
%\section*{about the student authors}

% The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
\section*{press summary}

\end{document}

### 2022-09-12 Manuscript/manuscript.tex
Format change
Makefile and manuscript update

@@
-% Created by Bonita Graham
-% Last update: December 2019 By Kestutis Bendinskas
+\documentclass[12pt, letterpaper, titlepage]{article}
 
-% Authors: 
-% Please do not make changes to the preamble until after the solid line of %s.
+\usepackage{amsmath}
+\usepackage{booktabs}
+\usepackage{amsthm}
+\usepackage{graphicx}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
+\usepackage{natbib}
+\usepackage{enumitem}
+\usepackage{setspace}
 
-\documentclass[10pt]{article}
-\usepackage[explicit]{titlesec}
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{1em}
-\usepackage{hyphenat}
-\usepackage{ragged2e}
-\RaggedRight
+\usepackage[pagewise]{lineno}
+%\linenumbers*[1]
+% %% patches to make lineno work better with amsmath
+\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
+ \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
+ \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
+ \renewenvironment{#1}%
+ {\linenomath\csname old#1\endcsname}%
+ {\csname oldend#1\endcsname\endlinenomath}}%
+\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
+ \patchAmsMathEnvironmentForLineno{#1}%
+ \patchAmsMathEnvironmentForLineno{#1*}}%
 
-% % These commands change the font. If you do not have Garamond on your computer, you will need to install it.
-% \usepackage{garamondx}
-% \usepackage[T1]{fontenc}
-% \usepackage{amsmath, amsthm}
-% \usepackage{graphicx}
-% \usepackage{hyperref}
-% \usepackage{xcolor}
-% \newcommand{\jy}[1]{\textcolor{orange}{JY: (#1)}}
-% \usepackage{booktabs}
-
-% This adjusts the underline to be in keeping with word processors.
-\usepackage{soul}
-\setul{.6pt}{.4pt}
-
-% The following sets margins to 1 in. on top and bottom and .75 in on left and right, and remove page numbers.
-\usepackage{geometry}
-\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\pagenumbering{gobble}
-\renewcommand{\headrulewidth}{0.0pt}
-\renewcommand{\footrulewidth}{0.0pt}
-
-% These Commands create the label style for tables, figures and equations.
-\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
-\captionsetup{labelformat=simple, labelsep=period}
-\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
-\renewcommand{\theequation}{\arabic{equation}}
-\makeatletter
-\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
-\makeatother
-\setlength{\intextsep}{10pt}
-\setlength{\abovecaptionskip}{2pt}
-\setlength{\belowcaptionskip}{-10pt}
-
-\renewcommand{\textfraction}{0.10}
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\bottomfraction}{0.85}
-\renewcommand{\floatpagefraction}{0.90}
-
-% These commands set the paragraph and line spacing
-\titleformat{\section}
-  {\normalfont}{\thesection}{1em}{\MakeUppercase{\textbf{#1}}}
-\titlespacing\section{0pt}{0pt}{-10pt}
-\titleformat{\subsection}
-  {\normalfont}{\thesubsection}{1em}{\textit{#1}}
-\titlespacing\subsection{0pt}{0pt}{-8pt}
-\renewcommand{\baselinestretch}{1.15}
-
-% This designs the title display style for the maketitle command
-\makeatletter
-\newcommand\sixteen{\@setfontsize\sixteen{17pt}{6}}
-\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
-\begin{flushleft}
-\sixteen\bfseries \@title
-\medskip
-\end{flushleft}
-\textit{\@author}
-\egroup}
-\makeatother
-
-% This styles the bibliography and citations.
-%\usepackage[biblabel]{cite}
-\usepackage[sort&compress]{natbib}
-\setlength\bibindent{2em}
-\makeatletter
-\renewcommand\@biblabel[1]{\textbf{#1.}\hfill}
-\makeatother
-\renewcommand{\citenumfont}[1]{\textbf{#1}}
-\bibpunct{}{}{,~}{s}{,}{,}
-\setlength{\bibsep}{0pt plus 0.3ex}
-
-\usepackage{float}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Authors: Add additional packages and new commands here.  
-% Limit your use of new commands and special formatting.
-
-% Place your title below. Use Title Capitalization.
-\title{Time Series Length at Which Block Bootstrapping is Effective for Estimation of a Statistic}
-
-% Add author information below. Communicating author is indicated by an asterisk, the affiliation is shown by superscripted lower case letter if several affiliations need to be noted.
-\author{
-Mathew Chandy*, Jun Yan \\ \medskip 
-Department of Statistics, University of Connecticut, Storrs, CT  \\  \medskip 
-Students: mathew.chandy@uconn.edu* \\
-Mentor: jun.yan@uconn.edu 
+\AtBeginDocument{%
+ \patchBothAmsMathEnvironmentsForLineno{equation}%
+ \patchBothAmsMathEnvironmentsForLineno{align}%
+ \patchBothAmsMathEnvironmentsForLineno{flalign}%
+ \patchBothAmsMathEnvironmentsForLineno{alignat}%
+ \patchBothAmsMathEnvironmentsForLineno{gather}%
+ \patchBothAmsMathEnvironmentsForLineno{multline}%
 }
 
-\pagestyle{empty}
+% control floats
+\renewcommand\floatpagefraction{.9}
+\renewcommand\topfraction{.9}
+\renewcommand\bottomfraction{.9}
+\renewcommand\textfraction{.1}
+\setcounter{totalnumber}{50}
+\setcounter{topnumber}{50}
+\setcounter{bottomnumber}{50}
+
+\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
+\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
+
+\title{Time Series Length at Which Block Bootstrapping is Effective for Estimation of Variance}
+
+\author{Mathew Chandy\\
+%   \href{mailto:mathew.chandy@uconn.edu}
+% {\nolinkurl{mathew.chandy@uconn.edu}}\\
+  Jun Yan\\[1ex]
+  Department of Statistics, University of Connecticut\\
+}
+\date{}
 
 \begin{document}
+\maketitle
 
-% Makes the title and author information appear.
-\vspace*{.01 in}
-\maketitle
-\vspace{.12 in}
+\doublespace
 
-% Abstracts are required.
-\section*{abstract}
+\begin{abstract}
+Block bootstrapping is a method that can be used for estimating a statistic of a time
+series. It involves splitting a series into blocks (in order to account for the time
+factor) and re-sampling the blocks to create many new bootstrapped time series.
+This method becomes more effective as the length of the time series increases. 
+The question for this study is how does one determine at what length the block
+bootstrap method stops being an effective method to estimate a statistic of a time
+series.
 
-Block bootstrapping is a method that can be used for estimating a statistic of a time series.
-It involves splitting a series into blocks (in order to account for the time factor) and re-sampling the blocks to create many new bootstrapped time series.
-This method becomes more effective as the length of the time series increases.
-The question for this study is how does one determine at what length the block bootstrap method stops being an effective method to estimate a statistic of a time series.
-
-% Keywords are required.
-\section*{keywords} 
-Block Bootstrap
-
-\vspace{.12 in}
-
-% Start the main part of the manuscript here.
-% Comment out section headings if inappropriate to your discipline.
-% If you add additional section or subsection headings, use an asterisk * to avoid numbering.
+\bigskip
+\noindent\sc{Keywords}:
+block bootstrap;
+\end{abstract}
 
 \section{Introduction}
+\label{sec:intro}
 
-For this study, many block bootstrap simulations were conducted with R.
-At the base level, we are block-bootstrapping an auto-regressive process with true mean 0.
-Bootstrapping is the term for creating new samples of the same size by re-sampling from the original sample with replacement.
-Many bootstrapped samples are used to create a distribution of sampling means to estimate mean and variance.
-This works for samples that are not dependent.
-However, for a time series such as an auto-regressive process, a different procedure is required to account for the time dependence.
-In such a case, the series is split into blocks that may overlap (moving block bootstrap) or may not overlap (non-moving block bootstrap).
-These blocks are then re-sampled to create new bootstrapped time series.
+For this study, many block bootstrap simulations were conducted with R. At the base
+level, we are block-bootstrapping an auto-regressive process with true mean 0.
+Bootstrapping is the term for creating new samples of the same size by re-sampling from
+the original sample with replacement. Many bootstrapped samples are used to create a
+distribution of sampling means to estimate mean and variance. This works for samples
+that are not dependent. However, for a time series such as an auto-regressive process,
+a different procedure is required to account for the time dependence. In such a case,
+the series is split into blocks that may overlap (moving block bootstrap) or may not
+overlap (non-moving block bootstrap). These blocks are then re-sampled to create new
+bootstrapped time series.
 
-In our experiment, we find the means of a 1000 block-bootstrapped time series, and create a 95 \% confidence interval of the means.
-We replicate this 1000 times, and record the proportion of confidence intervals that recover the true mean (coverage rate).
-We are effectively observing how successful the bootstrapping process is at estimating the mean and variance.
-The key variable being observed was n, the length of the time series, or the size of the sample.
-It is known that as n increases, block bootstrapping will become a less accurate method for estimation (the coverage rates will decrease).
-The question is at what range of n values does this start to become a problem.
+In our experiment, we find the means of a 1000 block-bootstrapped time series, 
+and create a 95 \% confidence interval of the means. We replicate this 1000 times, 
+and record the proportion of confidence intervals that recover the true mean 
+(coverage rate). We are effectively observing how successful the bootstrapping process
+is at estimating the mean and variance. The key variable being observed was n, 
+the length of the time series, or the size of the sample. It is known that as n
+increases, block bootstrapping will become a less accurate method for estimation
+(the coverage rates will decrease). The question is at what range of n values does this
+start to become a problem.
 
-In this experiment, there are certain factors that are expected to affect the coverage rates.
-As the AR coefficient (the time dependence) of the time series increases, we expect the coverage rates of the confidence intervals to decrease.
-The coverage rates are also affected by the size of the blocks - more specifically, the ratio of the size of the blocks (l) to the size of the time series (L) - and whether or not they overlap.
+In this experiment, there are certain factors that are expected to affect the coverage
+rates. As the AR coefficient (the time dependence) of the time series increases,
+we expect the coverage rates of the confidence intervals to decrease.
+The coverage rates are also affected by the size of the blocks - more specifically,
+the ratio of the size of the blocks (l) to the size of the time series (L) - 
+and whether or not they overlap.
 
-So to solve the question of what n is necessary for effective block bootstrapping, while still accounting for all these factors, the simulations were repeated for multiple combinations of AR coefficient and l:L ratios.
-In addition, the coverage rates for both the non-moving and moving methods were recorded.
+So to solve the question of what n is necessary for effective block bootstrapping,
+while still accounting for all these factors, the simulations were repeated for
+multiple combinations of AR coefficient and l:L ratios. In addition, the coverage rates
+for both the non-moving and moving methods were recorded.
 
 \section{Literature Review}
+\label{sec:litreview}
 
 \section{Data}
+\label{sec:data}
 
 \section{Methods}
+\label{sec:methods}
 
 \section{Results}
+\label{sec:results}
 
 \section{Discussion}
+\label{sec:discuss}
 
@@
 
-% \section*{acknowledgements}
-% The authors thank the University of Connecticut and the UConn Department of Statistics.
-%Note correct LaTeX quotations above. Do not use the " symbol, but rather double ` followed by double '
-
-% The About the Student Author section is NOT optional.  Write a paragraph about the student; see previous journal editions for examples.
-% If there is more than one student author, you must move the comment below.
-\section*{about the student author}
-%\section*{about the student authors}
-
-% The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
-\section*{press summary}
-
 \end{document}

### 2022-09-13 Manuscript/manuscript.tex
Started Methods

@@
 In this experiment, there are certain factors that are expected to affect the coverage
-rates. As the AR coefficient (the time dependence) of the time series increases,
+rates. As the Auto-Regressive (AR) coefficient (the time dependence) of the time series increases,
 we expect the coverage rates of the confidence intervals to decrease.
 The coverage rates are also affected by the size of the blocks - more specifically,
-the ratio of the size of the blocks (l) to the size of the time series (L) - 
+how the size of the blocks (l) relates to the size of the time series (n) - 
 and whether or not they overlap.
@@
 while still accounting for all these factors, the simulations were repeated for
-multiple combinations of AR coefficient and l:L ratios. In addition, the coverage rates
+multiple combinations of AR coefficient and the function of n used to decide l. In addition, the coverage rates
 for both the non-moving and moving methods were recorded.
@@
 
+A simulation of an autoregressive integrated moving average (ARIMA) process was run repeatedly with varying parameters. 
+The mean and standard deviation of the time series was held constant at 0 and 0.1, whereas the sample size and AR Coefficient
+ were varied. The AR Coefficients that were used were 0.2, 0.4, and 0.6. The sample sizes that were used depended on the AR
+ Coefficient, and the function used to compute l. For each of these variations, 1000 confidence intervals are created using
+ the block bootstrap method, and the proportion of these intervals that recover the true mean (0) is recorded as the coverage
+ rate. The block bootstrap method has different settings that were varied in this study: non-moving vs moving, 
+and the function for block length - the two used were a constant block length of 10 and the square root of n.
+
+For the simulations using a constant block length of 10, the sample size was gradually lowered by increments of 20 to see when
+the block bootstrap would begin to consistently return coverage rates below .90. For AR = 0.2 using a constant l, results for
+sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, results for sample sizes ranging from 600
+to 20 were observed.
+For AR = 0.6, using a constant l, results for sample sizes ranging from 900 to 220 were observed.
+For the simulations in which the block length was the square root of the time series length, the only sample sizes used were perfect squares so that the blocks would have whole number lengths.
+For AR = 0.2 using l = sqrt{n}, results for sample sizes ranging from 625 to 36 were observed.
+For AR = 0.4 using sqrt{n}, results for sample sizes ranging from 900 to 121 were observed.
+For AR = 0.6 using l = sqrt{n}, results for sample sizes ranging from 1600 to 121 were observed.
+
 \section{Results}
+
+As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was required for effective block bootstrap estimation.
+
+\begin{figure}[]
+  \centering
+  \includegraphics[width=\textwidth]{constant_0.2}
+  \caption{}
+  \label{fig:constant_0.2}
+\end{figure}
+
 \label{sec:results}

### 2022-09-14 Manuscript/manuscript.tex
Update

@@
 For the simulations using a constant block length of 10, the sample size was gradually lowered by increments of 20 to see when
-the block bootstrap would begin to consistently return coverage rates below .90. For AR = 0.2 using a constant l, results for
+the block bootstrap would begin to consistently return low coverage rates. For AR = 0.2 using a constant l, results for
 sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, results for sample sizes ranging from 600
@@
 As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was required for effective block bootstrap estimation.
+With l = sqrt{n} and AR = 0.2, all observed coverage rates are lower than .92 for n <= 225.
+For all n's <= 100, all observed coverage rates were below .90.
+With l = sqrt{n} and AR = 0.4, all observed coverage rates were below .92 for n <= 441.
+For all n's <= 144, all observed coverage rates were below .90.
+With l = sqrt{n} and AR = 0.6, all observed coverage rates were below .92 for n <= 400.
+For all n's <= 196, all observed coverage rates were below .90.
+
+With a constant l and AR = 0.2, for n <= 180, all observed coverage rates were below .92.
+For all n's <= 60, all observed coverage rates were below .90.
+With a constant l and AR = 0.4, for n <= 160, all observed coverage rates were below .91.
+For all n's <= 80, all observed coverage rates were below .90.
+With a constant l and AR = 0.6, for n <= 380, all observed coverage rates were below .92.
+For all n's <= 240, all observed coverage rates were below .90.
 

### 2022-09-18 Manuscript/Block-Bootstrap.Rmd
Set Random Seed

@@
 We need all necessary functions:
+
+```{r}
+set.seed(5)
+```
 
@@
 ```
-Observed coverage rates seem to be lower...
+Observed coverage rates seem to be lower, all are lower than .92 for n <= 225.
 
@@
 ```
-Coverage for n = 256 below .90.
+All coverage rates below .92 for n <= 441. Coverage for n = 256 below .90 for both methods.
 
@@
 ```
+Coverage rates seem pretty good at this range of n values.
 
@@
 ```
+Coverage rates are still pretty good.
 
@@
 
-Observed coverage rates seem to be lower, when n was 324 and 256, coverage rate below .90 was recorded for the moving methods.
+Observed coverage rates seem to be lower, when n was 324, a coverage rate below .90 was recorded for the moving method.
+When n was 256, both coverage rates were below .90.
+All coverage rates are below .92.
 
@@
 ```
-9 out of the 10 coverage rates are below .90.
+8 out of the 10 coverage rates are below .90.
 
@@
 ```
+Coverage rates generally seem good at this range.
 
@@
 ```
+Coverage rates still seem pretty good.
 
@@
 ```
-Observed coverage rates seem to be lower, when n was 841 and 784, coverage rates below .90 were recorded for non-moving method, and when n was 900, coverage rate fro moving method was below .90.
+Observed coverage rates seem to be lower, when n was 841 and 784, coverage rates below .90 were recorded for non-moving method, and when n was 900, coverage rate for moving method was below .90.
+All coverage rates below .92.
 
@@
 All but 3 of the coverage rates are below .90.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 10, m1)))
+constant_0.2_1 <- data.frame(c(400, 10, o))
+for(m in 19:16)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  constant_0.2_1 <- cbind(constant_0.2_1, c(n, 10, t))
+
+}
+
+print(constant_0.2_1)
+```
+Coverage rates are good.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(300, 0.2, 0.1, 10, m1)))
+constant_0.2_2 <- data.frame(c(300, 10, o))
+for(m in 14:11)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  constant_0.2_2 <- cbind(constant_0.2_2, c(n, 10, t))
+
+}
+
+print(constant_0.2_2)
+```
+Coverage rates are still good.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(200, 0.2, 0.1, 10, m1)))
+constant_0.2_3 <- data.frame(c(200, 10, o))
+for(m in 9:6)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  constant_0.2_3 <- cbind(constant_0.2_3, c(n, 10, t))
+
+}
+
+print(constant_0.2_3)
+```
+For n <= 180, coverage rates are below .92. For n = 140, both coverage rates are below .90, and the moving method has a coverage rate below .90 for n = 120.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
+constant_0.2_4 <- data.frame(c(100, 10, o))
+for(m in 4:1)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  constant_0.2_4 <- cbind(constant_0.2_4, c(n, 10, t))
+
+}
+
+print(constant_0.2_4)
+```
+Coverage rates are poor.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(600, 0.4, 0.1, 10, m1)))
+constant_0.4_1 <- data.frame(c(600, 10, o))
+for(m in 29:26)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_1 <- cbind(constant_0.4_1, c(n, 10, t))
+
+}
+
+print(constant_0.4_1)
+```
+Good coverage rates.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(500, 0.4, 0.1, 10, m1)))
+constant_0.4_2 <- data.frame(c(500, 10, o))
+for(m in 24:21)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_2 <- cbind(constant_0.4_2, c(n, 10, t))
+
+}
+
+print(constant_0.4_2)
+```
+
+Good coverage rates.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 10, m1)))
+constant_0.4_3 <- data.frame(c(400, 10, o))
+for(m in 19:16)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_3 <- cbind(constant_0.4_3, c(n, 10, t))
+
+}
+
+print(constant_0.4_3)
+```
+
+Still good.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(300, 0.4, 0.1, 10, m1)))
+constant_0.4_4 <- data.frame(c(300, 10, o))
+for(m in 14:11)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_4 <- cbind(constant_0.4_4, c(n, 10, t))
+
+}
+
+print(constant_0.4_4)
+```
+
+Coverage rates still pretty good.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(200, 0.4, 0.1, 10, m1)))
+constant_0.4_5 <- data.frame(c(200, 10, o))
+for(m in 9:6)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_5 <- cbind(constant_0.4_5, c(n, 10, t))
+
+}
+
+print(constant_0.4_5)
+```
+
+Non-moving method resulted in coverage rate below .90 for n = 200. All coverage rates for n = 140 and 120 are below .90.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
+constant_0.4_6 <- data.frame(c(100, 10, o))
+for(m in 4:1)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_6 <- cbind(constant_0.4_6, c(n, 10, t))
+
+}
+
+print(constant_0.4_6)
+```
+
+Poor coverage rates.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 10, m1)))
+constant_0.6_1 <- data.frame(c(900, 10, o))
+for(m in 44:41)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_1 <- cbind(constant_0.6_1, c(n, 10, t))
+
+}
+
+print(constant_0.6_1)
+```
+
+All coverage rates below .92.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(800, 0.6, 0.1, 10, m1)))
+constant_0.6_2 <- data.frame(c(800, 10, o))
+for(m in 39:36)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_2 <- cbind(constant_0.6_2, c(n, 10, t))
+
+}
+
+print(constant_0.6_2)
+```
+
+Moving coverage rate for n = 760 is below .90.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(700, 0.6, 0.1, 10, m1)))
+constant_0.6_3 <- data.frame(c(700, 10, o))
+for(m in 34:31)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_3 <- cbind(constant_0.6_3, c(n, 10, t))
+
+}
+
+print(constant_0.6_3)
+```
+All coverage rates below .92 except those for n = 680.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(600, 0.6, 0.1, 10, m1)))
+constant_0.6_4 <- data.frame(c(600, 10, o))
+for(m in 29:26)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_4 <- cbind(constant_0.6_4, c(n, 10, t))
+
+}
+
+print(constant_0.6_4)
+```
+
+All coverage rates below .92 except those for n = 540.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(500, 0.6, 0.1, 10, m1)))
+constant_0.6_5 <- data.frame(c(500, 10, o))
+for(m in 24:21)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_5 <- cbind(constant_0.6_5, c(n, 10, t))
+
+}
+
+print(constant_0.6_5)
+```
+
+Coverage rates are generally good.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(400, 0.6, 0.1, 10, m1)))
+constant_0.6_6 <- data.frame(c(400, 10, o))
+for(m in 19:16)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_6 <- cbind(constant_0.6_6, c(n, 10, t))
+
+}
+
+print(constant_0.6_6)
+```
+
+All coverage rates below .92 for n <= 380. Coverage rates below .90 for n = 360 and 340.
+
+```{r functions, echo = False}
+o = my_summary(replicate(1000, do1rep(300, 0.6, 0.1, 10, m1)))
+constant_0.6_7 <- data.frame(c(300, 10, o))
+for(m in 14:11)
+{
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_7 <- cbind(constant_0.6_7, c(n, 10, t))
+
+}
+
+print(constant_0.6_7)
+```
+```{r} 
+colnames(root_0.2_1) <- NULL
+colnames(root_0.2_2) <- NULL
+colnames(root_0.2_3) <- NULL
+root_0.2_3
+```
+
+```{r}
+
+root_0.2 <- data.frame(rbind(t(root_0.2_1[c(1, 2, 7),]), t(root_0.2_1[c(1, 2, 11),]), t(root_0.2_2[c(1, 2, 7),]), t(root_0.2_2[c(1, 2, 11),]), t(root_0.2_3[c(1, 2, 7),]), t(root_0.2_3[c(1, 2, 11),])))
+rownames(root_0.2) <- NULL
+colnames(root_0.2) <- c("n", "l", 'ci')
+root_0.2['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_0.2
+```
+```{r}
+library(ggplot2)
+ggplot(root_0.2, aes(x = n, y = ci, color = method)) +
+  geom_line() +
+  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
+ggsave('root_0.2.pdf')
+```
+```{r}
+root_0.4 <- data.frame(rbind(t(root_0.4_1[c(1, 2, 7),]), t(root_0.4_1[c(1, 2, 11),]), t(root_0.4_2[c(1, 2, 7),]), t(root_0.4_2[c(1, 2, 11),]), t(root_0.4_3[c(1, 2, 7),]), t(root_0.4_3[c(1, 2, 11),]), t(root_0.4_4[c(1, 2, 7),]), t(root_0.4_4[c(1, 2, 11),])))
+rownames(root_0.4) <- NULL
+colnames(root_0.4) <- c("n", "l", 'ci')
+root_0.4['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_0.4
+```
+```{r}
+library(ggplot2)
+ggplot(root_0.4, aes(x = n, y = ci, color = method)) +
+  geom_line() +
+  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
+ggsave('root_0.4.pdf')
+```
+```{r}
+root_0.6 <- data.frame(rbind(t(root_0.6_1[c(1, 2, 7),]), t(root_0.6_1[c(1, 2, 11),]), t(root_0.6_2[c(1, 2, 7),]), t(root_0.6_2[c(1, 2, 11),]), t(root_0.6_3[c(1, 2, 7),]), t(root_0.6_3[c(1, 2, 11),]), t(root_0.6_4[c(1, 2, 7),]), t(root_0.6_4[c(1, 2, 11),])))
+rownames(root_0.6) <- NULL
+colnames(root_0.6) <- c("n", "l", 'ci')
+root_0.6['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_0.6
+```
+
+```{r}
+library(ggplot2)
+ggplot(root_0.6, aes(x = n, y = ci, color = method)) +
+  geom_line() +
+  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
+ggsave('root_0.6.pdf') 
+```
+```{r}
+root_0.8 <- data.frame(rbind(t(root_0.8_1[c(1, 2, 7),]), t(root_0.8_1[c(1, 2, 11),]), t(root_0.8_2[c(1, 2, 7),]), t(root_0.8_2[c(1, 2, 11),]), t(root_0.8_3[c(1, 2, 7),]), t(root_0.8_3[c(1, 2, 11),]), t(root_0.8_4[c(1, 2, 7),]), t(root_0.8_4[c(1, 2, 11),])))
+rownames(root_0.8) <- NULL
+colnames(root_0.8) <- c("n", "l", 'ci')
+root_0.8['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_0.8
+```
+
+```{r}
+library(ggplot2)
+ggplot(root_0.8, aes(x = n, y = ci, color = method)) +
+  geom_line() +
+  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
+ggsave('root_0.8.pdf') 
+```
+```{r}
+constant_0.2 <- data.frame(rbind(t(constant_0.2_1[c(1, 2, 7),]), t(constant_0.2_1[c(1, 2, 11),]), t(constant_0.2_2[c(1, 2, 7),]), t(constant_0.2_2[c(1, 2, 11),]), t(constant_0.2_3[c(1, 2, 7),]), t(constant_0.2_3[c(1, 2, 11),]), t(constant_0.2_4[c(1, 2, 7),]), t(constant_0.2_4[c(1, 2, 11),])))
+rownames(constant_0.2) <- NULL
+colnames(constant_0.2) <- c("n", "l", 'ci')
+constant_0.2['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_0.2
+```
+
+```{r}
+library(ggplot2)
+ggplot(constant_0.2, aes(x = n, y = ci, color = method)) +
+  geom_line() +
+  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
+ggsave('constant_0.2.pdf')  
+```
+```{r}
+constant_0.4 <- data.frame(rbind(t(constant_0.4_1[c(1, 2, 7),]), t(constant_0.4_1[c(1, 2, 11),]), t(constant_0.4_2[c(1, 2, 7),]), t(constant_0.4_2[c(1, 2, 11),]), t(constant_0.4_3[c(1, 2, 7),]), t(constant_0.4_3[c(1, 2, 11),]), t(constant_0.4_4[c(1, 2, 7),]), t(constant_0.4_4[c(1, 2, 11),]), t(constant_0.4_5[c(1, 2, 7),]), t(constant_0.4_5[c(1, 2, 11),]), t(constant_0.4_6[c(1, 2, 7),]), t(constant_0.4_6[c(1, 2, 11),])))
+rownames(constant_0.4) <- NULL
+colnames(constant_0.4) <- c("n", "l", 'ci')
+constant_0.4['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_0.4
+```
+
+```{r}
+library(ggplot2)
+ggplot(constant_0.4, aes(x = n, y = ci, color = method)) +
+  geom_line() +
+  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
+ggsave('constant_0.4.pdf')  
+```
+```{r}
+constant_0.6 <- data.frame(rbind(t(constant_0.6_1[c(1, 2, 7),]), t(constant_0.6_1[c(1, 2, 11),]), t(constant_0.6_2[c(1, 2, 7),]), t(constant_0.6_2[c(1, 2, 11),]), t(constant_0.6_3[c(1, 2, 7),]), t(constant_0.6_3[c(1, 2, 11),]), t(constant_0.6_4[c(1, 2, 7),]), t(constant_0.6_4[c(1, 2, 11),]), t(constant_0.6_5[c(1, 2, 7),]), t(constant_0.6_5[c(1, 2, 11),]), t(constant_0.6_6[c(1, 2, 7),]), t(constant_0.6_6[c(1, 2, 11),]), t(constant_0.6_7[c(1, 2, 7),]), t(constant_0.6_7[c(1, 2, 11),])))
+rownames(constant_0.6) <- NULL
+colnames(constant_0.6) <- c("n", "l", 'ci')
+constant_0.6['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_0.6
+```
+
+```{r}
+library(ggplot2)
+ggplot(constant_0.6, aes(x = n, y = ci, color = method)) +
+  geom_line() +
+  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
+ggsave('constant_0.6.pdf')  
+```
+
+```{r}
+constant_0.8 <- data.frame(rbind(t(constant_0.8_1[c(1, 2, 7),]), t(constant_0.8_1[c(1, 2, 11),])))
+rownames(constant_0.8) <- NULL
+colnames(constant_0.8) <- c("n", "l", 'ci')
+constant_0.8['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_0.8
+```
+
+```{r}
+library(ggplot2)
+ggplot(constant_0.8, aes(x = n, y = ci, color = method)) +
+  geom_line() +
+  labs(x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate',  color = 'Method')
+ggsave('constant_0.8.pdf')  
+```

### 2022-09-22 Manuscript/manuscript.tex
Update
References

--- 2022-09-13 Manuscript/manuscript.tex
@@
 
+Block bootstrapping is a widely used method in Statistics. The concept for block 
+bootstrapping was developed independently by. It has been applied to a variety of 
+different fields such 
+as econometrics \citep{MacKinnon} and meteorology \citep{Varga}. It can be used for 
+situations in which there is temporal dependence and the goal is estimation or hypothesis 
+testing. It is useful for a variety of applicationsAssuming that the sample is infinitely 
+large, the method will work perfectly. However, for a finite sample size, the method will 
+not work as well as expected. It may be necessary (in order to plan an applied 
+statistical 
+procedure) to know at which sample size the method stops working at an acceptable level. 
+The goal of this study is to find a threshold or range of sample sizes at block bootstrap 
+is no longer an effective method for estimating variance.
+
+\citet{Nevitt} find that a sample size of 200-1000 is usually sufficient for standard 
+bootstrap estimation. However, block bootstrapping is a different situation especially in 
+the context of time series because the sample is split into blocks and there is a time 
+dependence factor.
+
 For this study, many block bootstrap simulations were conducted with R. At the base
@@
 In this experiment, there are certain factors that are expected to affect the coverage
-rates. As the Auto-Regressive (AR) coefficient (the time dependence) of the time series increases,
+rates. As the Auto-Regressive (AR) coefficient (the time dependence) of the time series 
+increases,
 we expect the coverage rates of the confidence intervals to decrease.
@@
 how the size of the blocks (l) relates to the size of the time series (n) - 
-and whether or not they overlap.
+and whether or not they overlap. It is known that as the size of the time series 
+increases, the optimal block length should increase, and the ratio of the block length to 
+the time series length should decrease. l = (n)(1/3) is typically considered the optimal 
+block length according to asymptotic theory. If only perfect cubes are used for the time 
+series length, n gets too large when l increases by relatively little. An alternative 
+would be to use smaller time series, find the cube root, and set the block length to the 
+nearest whole number. However, in this study l = sqrt{n} is used, as it allows for smaller 
+sample sizes, but it still follows the aforementioned principle.
 
@@
 while still accounting for all these factors, the simulations were repeated for
-multiple combinations of AR coefficient and the function of n used to decide l. In addition, the coverage rates
+multiple combinations of AR coefficient and the function of n used to decide l. In 
+addition, the coverage rates
 for both the non-moving and moving methods were recorded.
@@
 
-A simulation of an autoregressive integrated moving average (ARIMA) process was run repeatedly with varying parameters. 
-The mean and standard deviation of the time series was held constant at 0 and 0.1, whereas the sample size and AR Coefficient
- were varied. The AR Coefficients that were used were 0.2, 0.4, and 0.6. The sample sizes that were used depended on the AR
- Coefficient, and the function used to compute l. For each of these variations, 1000 confidence intervals are created using
- the block bootstrap method, and the proportion of these intervals that recover the true mean (0) is recorded as the coverage
- rate. The block bootstrap method has different settings that were varied in this study: non-moving vs moving, 
-and the function for block length - the two used were a constant block length of 10 and the square root of n.
+Before each simulation, the random seed was set to 5 so that the randomized results can be 
+reproduced.
 
-For the simulations using a constant block length of 10, the sample size was gradually lowered by increments of 20 to see when
-the block bootstrap would begin to consistently return coverage rates below .90. For AR = 0.2 using a constant l, results for
-sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, results for sample sizes ranging from 600
-to 20 were observed.
-For AR = 0.6, using a constant l, results for sample sizes ranging from 900 to 220 were observed.
-For the simulations in which the block length was the square root of the time series length, the only sample sizes used were perfect squares so that the blocks would have whole number lengths.
-For AR = 0.2 using l = sqrt{n}, results for sample sizes ranging from 625 to 36 were observed.
-For AR = 0.4 using sqrt{n}, results for sample sizes ranging from 900 to 121 were observed.
-For AR = 0.6 using l = sqrt{n}, results for sample sizes ranging from 1600 to 121 were observed.
+A simulation of an autoregressive integrated moving average (ARIMA) process was run 
+repeatedly with varying parameters. 
+The mean and standard deviation of the time series was held constant at 0 and 0.1, whereas 
+the sample size and AR Coefficient
+ were varied. The AR Coefficients that were used were 0.2, 0.4, and 0.6. The sample sizes 
+ that were used depended on the AR
+ Coefficient, and the function used to compute l. For each of these variations, 1000 
+ confidence intervals are created using
+ the block bootstrap method, and the proportion of these intervals that recover the true 
+ mean (0) is recorded as the coverage
+ rate. The block bootstrap method has different settings that were varied in this study: 
+ non-moving vs moving, 
+and the function for block length - the two used were a constant block length of 10 and 
+the square root of n.
+
+For the simulations using a constant block length of 10, the sample size was gradually 
+lowered by increments of 20 to see when
+the block bootstrap would begin to consistently return low coverage rates. For AR = 0.2 
+using a constant l, results for
+sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, 
+results for sample sizes ranging from 600
+to 20 were observed. For AR = 0.6, using a constant l, results for sample sizes ranging 
+from 900 to 220 were observed. For the simulations in which the block length was the 
+square root of the time series length, the only sample sizes used were perfect squares so 
+that the blocks would have whole number lengths. For AR = 0.2 using l = sqrt{n}, results 
+for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using sqrt{n}, results 
+for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = sqrt{n}, 
+results for sample sizes ranging from 1600 to 121 were observed.
 
 \section{Results}
+\label{sec:results}
 
-As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was required for effective block bootstrap estimation.
+As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was 
+required for effective block bootstrap estimation. With l = sqrt{n} and AR = 0.2, all 
+observed coverage rates were lower than .92 for n <= 144. For all n's <= 49, all observed 
+coverage rates were below .90. A coverage rate of .895 was recorded for the non-moving 
+method when n = 196, indicating that even at such a sample size, a coverage rate below .90 
+is possible. A coverage rate below .90 (.895) was recorded for the moving method at a 
+sample size as large as n = 144. With l = sqrt{n} and AR = 0.4, all observed coverage 
+rates were below .91 for n <= 169. For all n's <= 100, all observed coverage rates were 
+below .90. A coverage rate of .897 was recorded for the non-moving method when n = 400, 
+indicating that even at such a sample size, a coverage rate below .90 is possible. A 
+coverage rate below .90 (.897) was recorded for the moving method at a sample size as 
+large as n = 169. With l = sqrt{n} and AR = 0.6, all observed coverage rates were below 
+.91 for n <= 361. For all n's <= 225, all observed coverage rates were below .90. A 
+coverage rate of .896 was recorded for the moving method when n = 361, indicating that 
+even at such a sample size, a coverage rate below .90 is possible. A coverage rate below 
+.90 (.891) was recorded for the non-moving method at a sample size as large as n = 225.
 
-\begin{figure}[]
+With a constant l and AR = 0.2, for n <= 180, all observed coverage rates were below .92. 
+For all n's <= 100, all observed coverage rates were below .90. A coverage rate of .899 
+was recorded for the non-moving method when n = 140, indicating that even at such a sample 
+size, a coverage rate below .90 is possible. A coverage rate below .90 (.899) was recorded 
+for the moving method at a sample size as large as n = 100. With a constant l and AR = 
+0.4, for n <= 280, all observed coverage rates were below .92. For all n's <= 120, all 
+observed coverage rates were below .90. A coverage rate of .892 was recorded for the 
+moving method when n = 260, indicating that even at such a sample size, a coverage rate 
+below .90 is possible. A coverage rate below .90 (.896) was recorded for the non-moving 
+method at a sample size as large as n = 160. With a constant l and AR = 0.6.
+
+\begin{figure}[tbp]
   \centering

### 2022-09-22 Manuscript/manuscript.tex
9/22 Notes

@@
 Block bootstrapping is a widely used method in Statistics. The concept for block 
-bootstrapping was developed independently by. It has been applied to a variety of 
+bootstrapping was developed independently by \citet{Hall}, \citet{Carlstein}, and 
+\citet{Kunsch}. \citet{Radovanov} It has been applied to a variety of 
 different fields such 
@@
 \citet{Nevitt} find that a sample size of 200-1000 is usually sufficient for standard 
-bootstrap estimation. However, block bootstrapping is a different situation especially in 
-the context of time series because the sample is split into blocks and there is a time 
-dependence factor.
+bootstrap estimation. However, block bootstrapping is a different situation because the 
+sample is split into blocks.
+
+\citet{Goncalves} found that standard error estimates from block bootstrapping small 
+samples 
+may be significantly more accurate than inference from closed-form asymptotic estimates. 
+This however, works only under the assumption of low dependence and heterogeneity. In the
+context of a time series, it becomes more complicated.
 
@@
 increases, the optimal block length should increase, and the ratio of the block length to 
-the time series length should decrease. l = (n)(1/3) is typically considered the optimal 
-block length according to asymptotic theory. If only perfect cubes are used for the time 
+the time series length should decrease. l = n$^3$ is typically considered the optimal 
+block length according to asymptotic theory. \citep{Buhlmann} If only perfect cubes are used for the time 
 series length, n gets too large when l increases by relatively little. An alternative 

### 2022-09-25 Manuscript/Block-Bootstrap.Rmd
Error Bars

--- 2022-04-27 Manuscript/Block-Bootstrap.Rmd
@@
   rm = rowMeans(x)
-  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]))
+  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]), rm[5] + qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 1000), rm[5] - qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 1000),  rm[9] + qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 1000), rm[9] - qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 1000))
 }
@@
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 20, m1)))
@@
 {
+  set.seed(5)
   n = l^2
@@
 ```
+
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(225, 0.2, 0.1, 15, m1)))
@@
 ```
-Observed coverage rates seem to be lower...
+Observed coverage rates seem to be lower, all are lower than .92 for n <= 225.
 
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
@@
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(625, 0.4, 0.1, 25, m1)))
@@
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 20, m1)))
@@
 ```
-Coverage for n = 256 below .90.
+All coverage rates below .92 for n <= 441. Coverage for n = 256 below .90 for both methods.
 
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(225, 0.4, 0.1, 15, m1)))
@@
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
@@
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 30, m1)))
@@
 ```
+Coverage rates seem pretty good at this range of n values.
 
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(625, 0.6, 0.1, 25, m1)))
@@
 ```
+Coverage rates are still pretty good.
 
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(400, 0.6, 0.1, 20, m1)))
@@
 
-Observed coverage rates seem to be lower, when n was 324 and 256, coverage rate below .90 was recorded for the moving methods.
+Observed coverage rates seem to be lower, when n was 324, a coverage rate below .90 was recorded for the moving method.
+When n was 256, both coverage rates were below .90.
+All coverage rates are below .92.
 
 ```{r functions, echo = False}
+set.seed(5)
 o = my_summary(replicate(1000, do1rep(225, 0.6, 0.1, 15, m1)))
@@
 ```
-9 out of the 10 coverage rates are below .90.
+8 out of the 10 coverage rates are below .90.
 
 ```{r functions, echo = False}
-o = my_summary(replicate(1000, do1rep(1600, 0.8, 0.1, 40, m1)))
-root_0.8_1 <- data.frame(c(1600, 40, o))
-for(l in 39:36)
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 10, m1)))
+constant_0.2_1 <- data.frame(c(400, 10, o))
+for(m in 19:16)
 {
-  n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.8, 0.1, l, m1)))
-  root_0.8_1 <- cbind(root_0.8_1, c(n, l, t))
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  constant_0.2_1 <- cbind(constant_0.2_1, c(n, 10, t))
 
@@
 
-print(root_0.8_1)
+print(constant_0.2_1)
+```
+Coverage rates are good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(300, 0.2, 0.1, 10, m1)))
+constant_0.2_2 <- data.frame(c(300, 10, o))
+for(m in 14:11)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  constant_0.2_2 <- cbind(constant_0.2_2, c(n, 10, t))
+
+}
+
+print(constant_0.2_2)
+```
+Coverage rates are still good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(200, 0.2, 0.1, 10, m1)))
+constant_0.2_3 <- data.frame(c(200, 10, o))
+for(m in 9:6)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  constant_0.2_3 <- cbind(constant_0.2_3, c(n, 10, t))
+
+}
+
+print(constant_0.2_3)
+```
+For n <= 180, coverage rates are below .92. For n = 140, both coverage rates are below .90, and the moving method has a coverage rate below .90 for n = 120.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
+constant_0.2_4 <- data.frame(c(100, 10, o))
+for(m in 4:1)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  constant_0.2_4 <- cbind(constant_0.2_4, c(n, 10, t))
+
+}
+
+print(constant_0.2_4)
+```
+Coverage rates are poor.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(600, 0.4, 0.1, 10, m1)))
+constant_0.4_1 <- data.frame(c(600, 10, o))
+for(m in 29:26)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_1 <- cbind(constant_0.4_1, c(n, 10, t))
+
+}
+
+print(constant_0.4_1)
+```
+Good coverage rates.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(500, 0.4, 0.1, 10, m1)))
+constant_0.4_2 <- data.frame(c(500, 10, o))
+for(m in 24:21)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_2 <- cbind(constant_0.4_2, c(n, 10, t))
+
+}
+
+print(constant_0.4_2)
+```
+
+Good coverage rates.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 10, m1)))
+constant_0.4_3 <- data.frame(c(400, 10, o))
+for(m in 19:16)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_3 <- cbind(constant_0.4_3, c(n, 10, t))
+
+}
+
+print(constant_0.4_3)
+```
+
+Still good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(300, 0.4, 0.1, 10, m1)))
+constant_0.4_4 <- data.frame(c(300, 10, o))
+for(m in 14:11)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_4 <- cbind(constant_0.4_4, c(n, 10, t))
+
+}
+
+print(constant_0.4_4)
+```
+
+Coverage rates still pretty good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(200, 0.4, 0.1, 10, m1)))
+constant_0.4_5 <- data.frame(c(200, 10, o))
+for(m in 9:6)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_5 <- cbind(constant_0.4_5, c(n, 10, t))
+
+}
+
+print(constant_0.4_5)
+```
+
+Non-moving method resulted in coverage rate below .90 for n = 200. All coverage rates for n = 140 and 120 are below .90.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
+constant_0.4_6 <- data.frame(c(100, 10, o))
+for(m in 4:1)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  constant_0.4_6 <- cbind(constant_0.4_6, c(n, 10, t))
+
+}
+
+print(constant_0.4_6)
+```
+
+Poor coverage rates.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 10, m1)))
+constant_0.6_1 <- data.frame(c(900, 10, o))
+for(m in 44:41)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_1 <- cbind(constant_0.6_1, c(n, 10, t))
+
+}
+
+print(constant_0.6_1)
+```
+
+All coverage rates below .92.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(800, 0.6, 0.1, 10, m1)))
+constant_0.6_2 <- data.frame(c(800, 10, o))
+for(m in 39:36)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_2 <- cbind(constant_0.6_2, c(n, 10, t))
+
+}
+
+print(constant_0.6_2)
+```
+
+Moving coverage rate for n = 760 is below .90.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(700, 0.6, 0.1, 10, m1)))
+constant_0.6_3 <- data.frame(c(700, 10, o))
+for(m in 34:31)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_3 <- cbind(constant_0.6_3, c(n, 10, t))
+
+}
+
+print(constant_0.6_3)
+```
+All coverage rates below .92 except those for n = 680.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(600, 0.6, 0.1, 10, m1)))
+constant_0.6_4 <- data.frame(c(600, 10, o))
+for(m in 29:26)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_4 <- cbind(constant_0.6_4, c(n, 10, t))
+
+}
+
+print(constant_0.6_4)
+```
+
+All coverage rates below .92 except those for n = 540.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(500, 0.6, 0.1, 10, m1)))
+constant_0.6_5 <- data.frame(c(500, 10, o))
+for(m in 24:21)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_5 <- cbind(constant_0.6_5, c(n, 10, t))
+
+}
+
+print(constant_0.6_5)
+```
+
+Coverage rates are generally good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(400, 0.6, 0.1, 10, m1)))
+constant_0.6_6 <- data.frame(c(400, 10, o))
+for(m in 19:16)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_6 <- cbind(constant_0.6_6, c(n, 10, t))
+
+}
+
+print(constant_0.6_6)
+```
+
+All coverage rates below .92 for n <= 380. Coverage rates below .90 for n = 360 and 340.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(300, 0.6, 0.1, 10, m1)))
+constant_0.6_7 <- data.frame(c(300, 10, o))
+for(m in 14:11)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_7 <- cbind(constant_0.6_7, c(n, 10, t))
+
+}
+
+print(constant_0.6_7)
 ```
@@
 ```{r functions, echo = False}
-o = my_summary(replicate(1000, do1rep(1225, 0.8, 0.1, 35, m1)))
-root_0.8_2 <- data.frame(c(1225, 35, o))
-for(l in 34:31)
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(200, 0.6, 0.1, 10, m1)))
+constant_0.6_8 <- data.frame(c(200, 10, o))
+for(m in 9:6)
 {
-  n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.8, 0.1, l, m1)))
-  root_0.8_2 <- cbind(root_0.8_2, c(n, l, t))
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  constant_0.6_8 <- cbind(constant_0.6_8, c(n, 10, t))
 
@@
 
-print(root_0.8_2)
+print(constant_0.6_8)
 ```
 
-```{r functions, echo = False}
-o = my_summary(replicate(1000, do1rep(900, 0.8, 0.1, 30, m1)))
-root_0.8_3 <- data.frame(c(900, 30, o))
-for(l in 29:26)
-{
-  n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.8, 0.1, l, m1)))
-  root_0.8_3 <- cbind(root_0.8_3, c(n, l, t))
+```{r} 
+colnames(root_0.2_1) <- NULL
+colnames(root_0.2_2) <- NULL
+colnames(root_0.2_3) <- NULL
+root_0.2_3
+```
 
-}
+```{r}
 
-print(root_0.8_3)
+root_0.2 <- data.frame(rbind(t(root_0.2_1[c(1, 2, 7, 18, 17),]), t(root_0.2_1[c(1, 2, 11, 20, 19),]), t(root_0.2_2[c(1, 2, 7, 18, 17),]), t(root_0.2_2[c(1, 2, 11, 20, 19),]), t(root_0.2_3[c(1, 2, 7, 18, 17),]), t(root_0.2_3[c(1, 2, 11, 20, 19),])))
+rownames(root_0.2) <- NULL
+colnames(root_0.2) <- c("n", "l", 'coverage_rate', 'lb', 'ub')
+root_0.2['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_0.2[order(-root_0.2$n), ]
 ```
-Observed coverage rates seem to be lower, when n was 841 and 784, coverage rates below .90 were recorded for non-moving method, and when n was 900, coverage rate fro moving method was below .90.
+```{r}
+library(ggplot2)
+ggplot(root_0.2, aes(x = n, y = coverage_rate, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = ' * sqrt(n) * ', AR = 0.2'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('root_0.2.pdf')
+```
 
-```{r functions, echo = False}
-o = my_summary(replicate(1000, do1rep(625, 0.8, 0.1, 25, m1)))
-root_0.8_4 <- data.frame(c(625, 25, o))
-for(l in 24:21)
-{
-  n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.8, 0.1, l, m1)))
-  root_0.8_4 <- cbind(root_0.8_4, c(n, l, t))
+```{r}
+root_0.4 <- data.frame(rbind(t(root_0.4_1[c(1, 2, 7, 18, 17),]), t(root_0.4_1[c(1, 2, 11, 20, 19),]), t(root_0.4_2[c(1, 2, 7, 18, 17),]), t(root_0.4_2[c(1, 2, 11, 20, 19),]), t(root_0.4_3[c(1, 2, 7, 18, 17),]), t(root_0.4_3[c(1, 2, 11, 20, 19),]), t(root_0.4_4[c(1, 2, 7, 18, 17),]), t(root_0.4_4[c(1, 2, 11, 20, 19),])))
+rownames(root_0.4) <- NULL
+colnames(root_0.4) <- c("n", "l", 'ci', 'lb', 'ub')
+root_0.4['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_0.4[order(-root_0.4$n), ]
+```
+```{r}
+library(ggplot2)
+ggplot(root_0.4, aes(x = n, y = ci, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = ' * sqrt(n) * ', AR = 0.4'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('root_0.4.pdf')
+```
+```{r}
+root_0.6 <- data.frame(rbind(t(root_0.6_1[c(1, 2, 7, 18, 17),]), t(root_0.6_1[c(1, 2, 11, 20, 19),]), t(root_0.6_2[c(1, 2, 7, 18, 17),]), t(root_0.6_2[c(1, 2, 11, 20, 19),]), t(root_0.6_3[c(1, 2, 7, 18, 17),]), t(root_0.6_3[c(1, 2, 11, 20, 19),]), t(root_0.6_4[c(1, 2, 7, 18, 17),]), t(root_0.6_4[c(1, 2, 11, 20, 19),])))
+rownames(root_0.6) <- NULL
+colnames(root_0.6) <- c("n", "l", 'ci', 'lb', 'ub')
+root_0.6['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_0.6[order(-root_0.6$n), ]
+```
 
-}
+```{r}
+library(ggplot2)
+ggplot(root_0.6, aes(x = n, y = ci, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = ' * sqrt(n) * ', AR = 0.6'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('root_0.6.pdf')
+```
 
-print(root_0.8_4)
+```{r}
+constant_0.2 <- data.frame(rbind(t(constant_0.2_1[c(1, 2, 7, 18, 17),]), t(constant_0.2_1[c(1, 2, 11, 20, 19),]), t(constant_0.2_2[c(1, 2, 7, 18, 17),]), t(constant_0.2_2[c(1, 2, 11, 20, 19),]), t(constant_0.2_3[c(1, 2, 7, 18, 17),]), t(constant_0.2_3[c(1, 2, 11, 20, 19),]), t(constant_0.2_4[c(1, 2, 7, 18, 17),]), t(constant_0.2_4[c(1, 2, 11, 20, 19),])))
+rownames(constant_0.2) <- NULL
+colnames(constant_0.2) <- c("n", "l", 'ci', 'lb', 'ub')
+constant_0.2['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_0.2[order(-constant_0.2$n), ]
 ```
-All but 3 of the coverage rates are below .90.
+
+```{r}
+library(ggplot2)
+ggplot(constant_0.2, aes(x = n, y = ci, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = 10, AR = 0.2'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('constant_0.2.pdf')
+```
+
+```{r}
+constant_0.4 <- data.frame(rbind(t(constant_0.4_1[c(1, 2, 7, 18, 17),]), t(constant_0.4_1[c(1, 2, 11, 20, 19),]), t(constant_0.4_2[c(1, 2, 7, 18, 17),]), t(constant_0.4_2[c(1, 2, 11, 20, 19),]), t(constant_0.4_3[c(1, 2, 7, 18, 17),]), t(constant_0.4_3[c(1, 2, 11, 20, 19),]), t(constant_0.4_4[c(1, 2, 7, 18, 17),]), t(constant_0.4_4[c(1, 2, 11, 20, 19),]), t(constant_0.4_5[c(1, 2, 7, 18, 17),]), t(constant_0.4_5[c(1, 2, 11, 20, 19),]), t(constant_0.4_6[c(1, 2, 7, 18, 17),]), t(constant_0.4_6[c(1, 2, 11, 20, 19),])))
+rownames(constant_0.4) <- NULL
+colnames(constant_0.4) <- c("n", "l", 'ci', 'lb', 'ub')
+constant_0.4['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_0.4[order(-constant_0.4$n), ]
+```
+
+```{r}
+library(ggplot2)
+ggplot(constant_0.4, aes(x = n, y = ci, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = 10, AR = 0.4'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('constant_0.4.pdf')
+```
+
+```{r}
+constant_0.6 <- data.frame(rbind(t(constant_0.6_1[c(1, 2, 7, 18, 17),]), t(constant_0.6_1[c(1, 2, 11, 20, 19),]), t(constant_0.6_2[c(1, 2, 7, 18, 17),]), t(constant_0.6_2[c(1, 2, 11, 20, 19),]), t(constant_0.6_3[c(1, 2, 7, 18, 17),]), t(constant_0.6_3[c(1, 2, 11, 20, 19),]), t(constant_0.6_4[c(1, 2, 7, 18, 17),]), t(constant_0.6_4[c(1, 2, 11, 20, 19),]), t(constant_0.6_5[c(1, 2, 7, 18, 17),]), t(constant_0.6_5[c(1, 2, 11, 20, 19),]), t(constant_0.6_6[c(1, 2, 7, 18, 17),]), t(constant_0.6_6[c(1, 2, 11, 20, 19),]), t(constant_0.6_7[c(1, 2, 7, 18, 17),]), t(constant_0.6_7[c(1, 2, 11, 20, 19),]), t(constant_0.6_8[c(1, 2, 7, 18, 17),]), t(constant_0.6_8[c(1, 2, 11, 20, 19),])))
+rownames(constant_0.6) <- NULL
+colnames(constant_0.6) <- c("n", "l", 'ci', 'lb', 'ub')
+constant_0.6['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_0.6[order(-constant_0.6$n), ]
+```
+
+```{r}
+library(ggplot2)
+ggplot(constant_0.6, aes(x = n, y = ci, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = 10, AR = 0.6'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('constant_0.6.pdf')
+```

### 2022-09-28 Manuscript/Block-Bootstrap.Rmd
Update

@@
 ggplot(root_0.4, aes(x = n, y = ci, color = method)) +
-  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=10) +
   geom_line() +
@@
 ggplot(root_0.6, aes(x = n, y = ci, color = method)) +
-  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=15) +
   geom_line() +
@@
 ggplot(constant_0.4, aes(x = n, y = ci, color = method)) +
-  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=10) +
   geom_line() +
@@
 ggplot(constant_0.6, aes(x = n, y = ci, color = method)) +
-  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=15) +
   geom_line() +

### 2022-09-28 Manuscript/manuscript.tex
Update

--- 2022-09-14 Manuscript/manuscript.tex
@@
 
+Block bootstrapping is a widely used method in Statistics. The concept for block 
+bootstrapping was developed independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
+\citet{kunsch1989jackknife}. \citet{radovanov2014comparison} It has been applied to a variety of 
+different fields such 
+as econometrics \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}. It can be used for 
+situations in which there is temporal dependence and the goal is estimation or hypothesis 
+testing. Assuming that the sample is infinitely 
+large, the method will work perfectly. However, for a finite sample size, the method will 
+not work as well as expected. It may be necessary (in order to plan an applied 
+statistical 
+procedure) to know at which sample size the method stops working at an acceptable level. 
+The goal of this study is to find a threshold or range of sample sizes at block bootstrap 
+is no longer an effective method for estimating variance.
+
+\citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for standard 
+bootstrap estimation. However, block bootstrapping is a different situation because the 
+sample is split into blocks.
+
+\citet{goncalves2005bootstrap} found that standard error estimates from block bootstrapping small 
+samples 
+may be significantly more accurate than inference from closed-form asymptotic estimates.
+That study focused on variance estimation within the context of linear regression.
+Still, the rate at which confidence intervals recover the true variance for small sample sizes wasn't very close to the confidence level of the intervals.
+This study aims to find how small the sample size can be for time series (which has a dependence factor which can be compared to a linear regression) in order for the coverage rate to be close to the confidence level.
+
 For this study, many block bootstrap simulations were conducted with R. At the base
@@
 how the size of the blocks (l) relates to the size of the time series (n) - 
-and whether or not they overlap.
+and whether or not they overlap. It is known that as the size of the time series 
+increases, the optimal block length should increase, and the ratio of the block length to 
+the time series length should decrease. l = n$^3$ is typically considered the optimal 
+block length according to asymptotic theory. \citep{buhlmann1999block} If only perfect cubes are used for the time 
+series length, n gets too large when l increases by relatively little. An alternative 
+would be to use smaller time series, find the cube root, and set the block length to the 
+nearest whole number. However, in this study l = sqrt{n} is used, as it allows for smaller 
+sample sizes, but it still follows the aforementioned principle.
 
@@
 while still accounting for all these factors, the simulations were repeated for
-multiple combinations of AR coefficient and the function of n used to decide l. In addition, the coverage rates
+multiple combinations of AR coefficient and the function of n used to decide l. In 
+addition, the coverage rates
 for both the non-moving and moving methods were recorded.
 
-\section{Literature Review}
-\label{sec:litreview}
+\section{Review of Block Bootstrap}
+\label{sec:blkbootreview}
 
-\section{Data}
-\label{sec:data}
+Block bootstrapping is a method that can be applied to time series to estimate a parameter and it's variance.
+Suppose that a sample of size n of a time series is given.
+In order to account for the temporal dependence, the time series can be split into blocks, typically of the same size.
+The block should be of size l large enough to include time dependence, yet small enough to include some variance.
+The designer of the study can choose whether the blocks overlap or not.
+If the bloc(Figure here) A bootstrapped sample is created by taking a sample of n / l blocks with replacement to create a new series of size n.
+An estimator of the parameter is computed from the sample.
+This procedure can be repeated many times to create a sampling distribution if the distribution is unknown.
+Using this sampling distribution, a confidence interval for the parameter can be created using the alpha/2 and 1 - alpha/2 percentiles.
+
+\section{Simulation Study Design}
+\label{sec:simdesign}
+
+The basic objective of the study was to assess how well block bootstrap estimates the variance for an autoregressive process.
+In the previous section, the process for creating a confidence interval using the block bootstrap method is described.
+This process is applied to a simulation of an autoregressive integrated moving average (ARIMA) with sigma = 0.1 to create a confidence interval of the mean of the process.
+For a certain AR coefficient, a block bootstrap 95\% confidence interval is replicated 1000 times at a starting sample size at which block bootstrap is expected to be very effective.
+For each individual confidence interval, it can be recorded whether or not the interval includes the true mean (0).
+The coverage rate, or the proportion of intervals that include the mean, can then be recorded.
+If the variance is being properly estimated by the block bootstrap, the coverage rate should reflect this by being close to the confidence level of 95\%.
+If this is not the case, the method is not working as well as it should.
+Since the coverage rate is a proportion, a 95\% confidence interval of the coverage rate can also be created.
 
@@
 
-A simulation of an autoregressive integrated moving average (ARIMA) process was run repeatedly with varying parameters. 
-The mean and standard deviation of the time series was held constant at 0 and 0.1, whereas the sample size and AR Coefficient
- were varied. The AR Coefficients that were used were 0.2, 0.4, and 0.6. The sample sizes that were used depended on the AR
- Coefficient, and the function used to compute l. For each of these variations, 1000 confidence intervals are created using
- the block bootstrap method, and the proportion of these intervals that recover the true mean (0) is recorded as the coverage
- rate. The block bootstrap method has different settings that were varied in this study: non-moving vs moving, 
-and the function for block length - the two used were a constant block length of 10 and the square root of n.
+Before each simulation, the random seed was set to 5 so that the randomized results can be 
+reproduced.
 
-For the simulations using a constant block length of 10, the sample size was gradually lowered by increments of 20 to see when
-the block bootstrap would begin to consistently return low coverage rates. For AR = 0.2 using a constant l, results for
-sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, results for sample sizes ranging from 600
-to 20 were observed.
-For AR = 0.6, using a constant l, results for sample sizes ranging from 900 to 220 were observed.
-For the simulations in which the block length was the square root of the time series length, the only sample sizes used were perfect squares so that the blocks would have whole number lengths.
-For AR = 0.2 using l = sqrt{n}, results for sample sizes ranging from 625 to 36 were observed.
-For AR = 0.4 using sqrt{n}, results for sample sizes ranging from 900 to 121 were observed.
-For AR = 0.6 using l = sqrt{n}, results for sample sizes ranging from 1600 to 121 were observed.
+A simulation of an autoregressive integrated moving average (ARIMA) process was run 
+repeatedly with varying parameters. 
+The mean and standard deviation of the time series was held constant at 0 and 0.1, whereas 
+the sample size and AR Coefficient
+ were varied. The AR Coefficients that were used were 0.2, 0.4, and 0.6. The sample sizes 
+ that were used depended on the AR
+ Coefficient, and the function used to compute l. For each of these variations, 1000 
+ confidence intervals are created using
+ the block bootstrap method, and the proportion of these intervals that recover the true 
+ mean (0) is recorded as the coverage
+ rate. The block bootstrap method has different settings that were varied in this study: 
+ non-moving vs moving, 
+and the function for block length - the two used were a constant block length of 10 and 
+the square root of n.
+
+For the simulations using a constant block length of 10, the sample size was gradually 
+lowered by increments of 20 to see when
+the block bootstrap would begin to consistently return low coverage rates. For AR = 0.2 
+using a constant l, results for
+sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, 
+results for sample sizes ranging from 600
+to 20 were observed. For AR = 0.6, using a constant l, results for sample sizes ranging 
+from 900 to 120 were observed. For the simulations in which the block length was the 
+square root of the time series length, the only sample sizes used were perfect squares so 
+that the blocks would have whole number lengths. For AR = 0.2 using l = sqrt{n}, results 
+for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using sqrt{n}, results 
+for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = sqrt{n}, 
+results for sample sizes ranging from 1600 to 121 were observed.
 
 \section{Results}
+\label{sec:results}
 
-As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was required for effective block bootstrap estimation.
-With l = sqrt{n} and AR = 0.2, all observed coverage rates are lower than .92 for n <= 225.
-For all n's <= 100, all observed coverage rates were below .90.
-With l = sqrt{n} and AR = 0.4, all observed coverage rates were below .92 for n <= 441.
-For all n's <= 144, all observed coverage rates were below .90.
-With l = sqrt{n} and AR = 0.6, all observed coverage rates were below .92 for n <= 400.
-For all n's <= 196, all observed coverage rates were below .90.
+As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was 
+required for effective block bootstrap estimation.
 
-With a constant l and AR = 0.2, for n <= 180, all observed coverage rates were below .92.
-For all n's <= 60, all observed coverage rates were below .90.
-With a constant l and AR = 0.4, for n <= 160, all observed coverage rates were below .91.
-For all n's <= 80, all observed coverage rates were below .90.
-With a constant l and AR = 0.6, for n <= 380, all observed coverage rates were below .92.
-For all n's <= 240, all observed coverage rates were below .90.
-
-\begin{figure}[]
+\begin{figure}[tbp]
   \centering
@@
   \label{fig:constant_0.2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{constant_0.4}
+  \caption{}
+  \label{fig:constant_0.4}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{constant_0.6}
+  \caption{}
+  \label{fig:constant_0.6}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{root_0.2}
+  \caption{}
+  \label{fig:root_0.2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{root_0.4}
+  \caption{}
+  \label{fig:root_0.4}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{root_0.6}
+  \caption{}
+  \label{fig:root_0.6}
 \end{figure}

### 2022-10-06 Manuscript/Block-Bootstrap.Rmd
Manuscript Update

@@
 do1rep <- function(n, theta, sd, l, statistic) {
-  x <- arima.sim(list(ar = theta), n = n, sd = sd)
+  x <- arima.sim(list(ar = theta), n = n, sd = sqrt((sd^2)*(1-theta^2)))
+
+  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)
+
+  bt <- blkboot(x, statistic, 1000, l)
+
+ # nm_lower_bound with quantile function
+
+  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
+  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))
+
+  nm_contains = FALSE
+  if (nm_interval[1] < 0 && nm_interval[2] > 0)
+  {
+    nm_contains = TRUE
+  }
+  mv_contains = FALSE
+  if (mv_interval[1] < 0 && mv_interval[2] > 0)
+  {
+    mv_contains = TRUE
+  }
+
+  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)
+
+    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
+
+}
+
+do1rep2 <- function(n, theta, sd, l, statistic) {
+  x <- rnorm(n = n, sd = sd)
 
@@
 
+```
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep2(400, 0, 0.1, 20, m1)))
+root_norm_1 <- data.frame(c(400, 20, o))
+for(l in 19:16)
+{
+  set.seed(5)
+  n = l^2
+  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
+  root_norm_1 <- cbind(root_norm_1, c(n, l, t))
+
+}
+
+print(root_norm_1)
+```
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep2(225, 0, 0.1, 15, m1)))
+root_norm_2 <- data.frame(c(225, 15, o))
+for(l in 14:11)
+{
+  set.seed(5)
+  n = l^2
+  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
+  root_norm_2 <- cbind(root_norm_2, c(n, l, t))
+
+}
+
+print(root_norm_2)
+```
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep2(100, 0, 0.1, 10, m1)))
+root_norm_3 <- data.frame(c(100, 10, o))
+for(l in 9:6)
+{
+  set.seed(5)
+  n = l^2
+  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
+  root_norm_3 <- cbind(root_norm_3, c(n, l, t))
+
+}
+
+print(root_norm_3)
+```
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(400, 0, 0.1, 20, m1)))
+root_0_1 <- data.frame(c(400, 20, o))
+for(l in 19:16)
+{
+  set.seed(5)
+  n = l^2
+  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
+  root_0_1 <- cbind(root_0_1, c(n, l, t))
+
+}
+
+print(root_0_1)
+```
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(225, 0, 0.1, 15, m1)))
+root_0_2 <- data.frame(c(225, 15, o))
+for(l in 14:11)
+{
+  set.seed(5)
+  n = l^2
+  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
+  root_0_2 <- cbind(root_0_2, c(n, l, t))
+
+}
+
+print(root_0_2)
+```
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(100, 0, 0.1, 10, m1)))
+root_0_3 <- data.frame(c(100, 10, o))
+for(l in 9:6)
+{
+  set.seed(5)
+  n = l^2
+  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
+  root_0_3 <- cbind(root_0_3, c(n, l, t))
+
+}
+
+print(root_0_3)
 ```
@@
 8 out of the 10 coverage rates are below .90.
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep2(400, 0, 0.1, 10, m1)))
+constant_norm_1 <- data.frame(c(400, 10, o))
+for(m in 19:16)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
+  constant_norm_1 <- cbind(constant_norm_1, c(n, 10, t))
+
+}
+
+print(constant_norm_1)
+```
+Coverage rates are good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep2(300, 0, 0.1, 10, m1)))
+constant_norm_2 <- data.frame(c(300, 10, o))
+for(m in 14:11)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
+  constant_norm_2 <- cbind(constant_norm_2, c(n, 10, t))
+
+}
+
+print(constant_norm_2)
+```
+Coverage rates are still good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep2(200, 0, 0.1, 10, m1)))
+constant_norm_3 <- data.frame(c(200, 10, o))
+for(m in 9:6)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
+  constant_norm_3 <- cbind(constant_norm_3, c(n, 10, t))
+
+}
+
+print(constant_norm_3)
+```
+For n <= 180, coverage rates are below .92. For n = 140, both coverage rates are below .90, and the moving method has a coverage rate below .90 for n = 120.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep2(100, 0, 0.1, 10, m1)))
+constant_norm_4 <- data.frame(c(100, 10, o))
+for(m in 4:1)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
+  constant_norm_4 <- cbind(constant_norm_4, c(n, 10, t))
+
+}
+
+print(constant_norm_4)
+```
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(400, 0, 0.1, 10, m1)))
+constant_0_1 <- data.frame(c(400, 10, o))
+for(m in 19:16)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
+  constant_0_1 <- cbind(constant_0_1, c(n, 10, t))
+
+}
+
+print(constant_0_1)
+```
+Coverage rates are good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(300, 0, 0.1, 10, m1)))
+constant_0_2 <- data.frame(c(300, 10, o))
+for(m in 14:11)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
+  constant_0_2 <- cbind(constant_0_2, c(n, 10, t))
+
+}
+
+print(constant_0_2)
+```
+Coverage rates are still good.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(200, 0, 0.1, 10, m1)))
+constant_0_3 <- data.frame(c(200, 10, o))
+for(m in 9:6)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
+  constant_0_3 <- cbind(constant_0_3, c(n, 10, t))
+
+}
+
+print(constant_0_3)
+```
+For n <= 180, coverage rates are below .92. For n = 140, both coverage rates are below .90, and the moving method has a coverage rate below .90 for n = 120.
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(1000, do1rep(100, 0, 0.1, 10, m1)))
+constant_0_4 <- data.frame(c(100, 10, o))
+for(m in 4:1)
+{
+  set.seed(5)
+  n = 20 * m
+  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
+  constant_0_4 <- cbind(constant_0_4, c(n, 10, t))
+
+}
+
+print(constant_0_4)
+```
 
@@
 ```
+```{r}
+
+root_norm <- data.frame(rbind(t(root_norm_1[c(1, 2, 7, 18, 17),]), t(root_norm_1[c(1, 2, 11, 20, 19),]), t(root_norm_2[c(1, 2, 7, 18, 17),]), t(root_norm_2[c(1, 2, 11, 20, 19),]), t(root_norm_3[c(1, 2, 7, 18, 17),]), t(root_norm_3[c(1, 2, 11, 20, 19),])))
+rownames(root_norm) <- NULL
+colnames(root_norm) <- c("n", "l", 'coverage_rate', 'lb', 'ub')
+root_norm['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_norm[order(-root_norm$n), ]
+```
+
+```{r}
+library(ggplot2)
+ggplot(root_norm, aes(x = n, y = coverage_rate, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = ' * sqrt(n) * ', AR = 0'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('root_norm.pdf')
+```
+
+```{r}
+
+root_0 <- data.frame(rbind(t(root_0_1[c(1, 2, 7, 18, 17),]), t(root_0_1[c(1, 2, 11, 20, 19),]), t(root_0_2[c(1, 2, 7, 18, 17),]), t(root_0_2[c(1, 2, 11, 20, 19),]), t(root_0_3[c(1, 2, 7, 18, 17),]), t(root_0_3[c(1, 2, 11, 20, 19),])))
+rownames(root_0) <- NULL
+colnames(root_0) <- c("n", "l", 'coverage_rate', 'lb', 'ub')
+root_0['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+root_0[order(-root_0$n), ]
+```
+
+```{r}
+library(ggplot2)
+ggplot(root_0, aes(x = n, y = coverage_rate, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = ' * sqrt(n) * ', AR = 0'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('root_0.pdf')
+```
 
@@
 ```
+
 ```{r}
@@
 ggsave('root_0.6.pdf')
+```
+```{r}
+constant_norm <- data.frame(rbind(t(constant_norm_1[c(1, 2, 7, 18, 17),]), t(constant_norm_1[c(1, 2, 11, 20, 19),]), t(constant_norm_2[c(1, 2, 7, 18, 17),]), t(constant_norm_2[c(1, 2, 11, 20, 19),]), t(constant_norm_3[c(1, 2, 7, 18, 17),]), t(constant_norm_3[c(1, 2, 11, 20, 19),]), t(constant_norm_4[c(1, 2, 7, 18, 17),]), t(constant_norm_4[c(1, 2, 11, 20, 19),])))
+rownames(constant_norm) <- NULL
+colnames(constant_norm) <- c("n", "l", 'ci', 'lb', 'ub')
+constant_norm['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_norm[order(-constant_norm$n), ]
+```
+
+```{r}
+library(ggplot2)
+ggplot(constant_norm, aes(x = n, y = ci, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = 10, AR = 0'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('constant_norm.pdf')
+```
+
+```{r}
+constant_0 <- data.frame(rbind(t(constant_0_1[c(1, 2, 7, 18, 17),]), t(constant_0_1[c(1, 2, 11, 20, 19),]), t(constant_0_2[c(1, 2, 7, 18, 17),]), t(constant_0_2[c(1, 2, 11, 20, 19),]), t(constant_0_3[c(1, 2, 7, 18, 17),]), t(constant_0_3[c(1, 2, 11, 20, 19),]), t(constant_0_4[c(1, 2, 7, 18, 17),]), t(constant_0_4[c(1, 2, 11, 20, 19),])))
+rownames(constant_0) <- NULL
+colnames(constant_0) <- c("n", "l", 'ci', 'lb', 'ub')
+constant_0['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
+constant_0[order(-constant_0$n), ]
+```
+
+```{r}
+library(ggplot2)
+ggplot(constant_0, aes(x = n, y = ci, color = method)) +
+  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(~method, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'))) +
+  labs(title = expression('l = 10, AR = 0'), x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
+ggsave('constant_0.pdf')
 ```

### 2022-10-06 Manuscript/manuscript.tex
Manuscript Update

@@
 \begin{abstract}
-Block bootstrapping is a method that can be used for estimating a statistic of a time
+Block bootstrapping is a method that can be used for estimating a parameter of a time
 series. It involves splitting a series into blocks (in order to account for the time
@@
 The question for this study is how does one determine at what length the block
-bootstrap method stops being an effective method to estimate a statistic of a time
+bootstrap method stops being an effective method to estimate a parameter of a time
 series.
@@
 
-Block bootstrapping is a method that can be applied to time series to estimate a parameter and it's variance.
+Block bootstrapping is a method that can be applied to a time series (or any sample of data for that matter) to estimate a parameter and its variance.
 Suppose that a sample of size n of a time series is given.
-In order to account for the temporal dependence, the time series can be split into blocks, typically of the same size.
+In regular bootstrap procedure, the new sample of the same size as the original would just be created by resampling observations with replacement.
+In the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size.
 The block should be of size l large enough to include time dependence, yet small enough to include some variance.
+A bootstrapped sample is created by taking a sample of n / l blocks with replacement to create a new series of size n.
 The designer of the study can choose whether the blocks overlap or not.
-If the bloc(Figure here) A bootstrapped sample is created by taking a sample of n / l blocks with replacement to create a new series of size n.
-An estimator of the parameter is computed from the sample.
-This procedure can be repeated many times to create a sampling distribution if the distribution is unknown.
-Using this sampling distribution, a confidence interval for the parameter can be created using the alpha/2 and 1 - alpha/2 percentiles.
+If the blocks can never overlap, it is called a non-moving block bootstrap.
+In this case, the original sample is split evenly into n / l blocks, and the same number of blocks is sampled without replacement to create a bootstrapped sample.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{orig_ts}
+  \caption{}
+  \label{fig:orig_ts}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{nm_ts}
+  \caption{}
+  \label{fig:nm_ts}
+\end{figure}
+
+If the block do overlap, it is called a moving block bootstrap. n / l samples are taken randomly from the original sample, but they do not have to be from a group of evenly spaced blocks.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{orig_ts_2}
+  \caption{}
+  \label{fig:orig_ts_2}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{mv_ts}
+  \caption{}
+  \label{fig:mv_ts}
+\end{figure}
+
+An estimator of the parameter is computed from the bootstrapped sample. This procedure can be repeated many times to create a sampling distribution of the estimator.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{nm_dist}
+  \caption{}
+  \label{fig:nm_dist}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{mv_dist}
+  \caption{}
+  \label{fig:mv_dist}
+\end{figure}
+
+Using this distribution of estimators, a confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles.
 
@@
 
-The basic objective of the study was to assess how well block bootstrap estimates the variance for an autoregressive process.
-In the previous section, the process for creating a confidence interval using the block bootstrap method is described.
-This process is applied to a simulation of an autoregressive integrated moving average (ARIMA) with sigma = 0.1 to create a confidence interval of the mean of the process.
-For a certain AR coefficient, a block bootstrap 95\% confidence interval is replicated 1000 times at a starting sample size at which block bootstrap is expected to be very effective.
+The central objective of the study was to assess at which sample size block bootstrap no longer estimates the variance well for an autoregressive process.
+The method will work better as sample size goes to infinity, but the goal is to see what is the smallest sample size that is acceptable.
+To achieve this, simulations must first be conducted with a larger sample size in order to compare to results with a smaller n.
+In the previous section, the procedure for creating a confidence interval using the block bootstrap method is described.
+This process is applied to a simulation of an autoregressive integrated moving average (ARIMA) with standard deviation = 0.1 to create a confidence interval of the mean of the process.
+R has a built in ARIMA simulation which allows you to set the AR coefficient and the standard deviation of the error term.
+Using the equation below, the sigma of the error term can be decided so that the standard deviation of Y is constant (0.1, Variance = 0.01).
+
+\[ \sigma_{x}^{2}=\sigma_{\eta}^{2}/\left( 1-\phi^2 \right)\]
+\[\sigma_{\eta}=\sqrt{\sigma_{x}^{2}*\left( 1-\phi^2 \right)}\]
+
+For a certain AR coefficient, a block bootstrap 95\% confidence interval is replicated 1000 times at a starting sample size at which block bootstrap is expected to be very effective (a relatively large sample).
 For each individual confidence interval, it can be recorded whether or not the interval includes the true mean (0).
@@
 Since the coverage rate is a proportion, a 95\% confidence interval of the coverage rate can also be created.
+Once the simulation is done for the starting n, the sample size can gradually be lowered until the coverage rates and their respective confidence intervals indicate that the method no longer functions well.
 
@@
 
-Before each simulation, the random seed was set to 5 so that the randomized results can be 
+Before each simulation (1000 replications of confidence intervals from block bootstrapped sample mean distributions), the random seed was set to 5 so that the randomized results can be 
 reproduced.
@@
 repeatedly with varying parameters. 
-The mean and standard deviation of the time series was held constant at 0 and 0.1, whereas 
+The mean and standard deviation of the time series was held constant at 0 and 0.1, respectively, whereas 
 the sample size and AR Coefficient
- were varied. The AR Coefficients that were used were 0.2, 0.4, and 0.6. The sample sizes 
+ were varied. The AR Coefficients that were used were 0 (or a regular sample with no temporal dependence) 0.2, 0.4, and 0.6. The sample sizes 
  that were used depended on the AR
@@
 lowered by increments of 20 to see when
-the block bootstrap would begin to consistently return low coverage rates. For AR = 0.2 
+the block bootstrap would begin to consistently return low coverage rates. For both AR = 0 and AR = 0.2 
 using a constant l, results for
@@
 square root of the time series length, the only sample sizes used were perfect squares so 
-that the blocks would have whole number lengths. For AR = 0.2 using l = sqrt{n}, results 
-for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using sqrt{n}, results 
-for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = sqrt{n}, 
+that the blocks would have whole number lengths. For AR = 0.2 using l = $\sqrt{n}$, results 
+for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using $\sqrt{n}$, results 
+for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = $\sqrt{n}$, 
 results for sample sizes ranging from 1600 to 121 were observed.
@@
 required for effective block bootstrap estimation.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{constant_0}
+  \caption{}
+  \label{fig:constant_0}
+\end{figure}
 
@@
   \label{fig:constant_0.6}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{root_0}
+  \caption{}
+  \label{fig:root_0}
 \end{figure}

### 2022-10-13 Manuscript/manuscript.tex
Updated Plots

@@
 block length according to asymptotic theory. \citep{buhlmann1999block} If only perfect cubes are used for the time 
-series length, n gets too large when l increases by relatively little. An alternative 
+series length, n gets quite large when l increases by relatively little. An alternative 
 would be to use smaller time series, find the cube root, and set the block length to the 
 nearest whole number. However, in this study l = sqrt{n} is used, as it allows for smaller 
-sample sizes, but it still follows the aforementioned principle.
+sample sizes while still using perfect squares.
 
@@
 In this case, the original sample is split evenly into n / l blocks, and the same number of blocks is sampled without replacement to create a bootstrapped sample.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{orig_ts}
-  \caption{}
-  \label{fig:orig_ts}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{nm_ts}
-  \caption{}
-  \label{fig:nm_ts}
-\end{figure}
-
-If the block do overlap, it is called a moving block bootstrap. n / l samples are taken randomly from the original sample, but they do not have to be from a group of evenly spaced blocks.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{orig_ts_2}
-  \caption{}
-  \label{fig:orig_ts_2}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{mv_ts}
-  \caption{}
-  \label{fig:mv_ts}
-\end{figure}
-
-An estimator of the parameter is computed from the bootstrapped sample. This procedure can be repeated many times to create a sampling distribution of the estimator.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{nm_dist}
-  \caption{}
-  \label{fig:nm_dist}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{mv_dist}
-  \caption{}
-  \label{fig:mv_dist}
-\end{figure}
-
+If the blocks do overlap, it is called a moving block bootstrap.
+n / l samples are taken randomly from the original sample, but they do not have to be from a group of evenly spaced blocks.
+An estimator of the parameter is computed from the bootstrapped sample.
+This procedure can be repeated many times to create a sampling distribution of the estimator.
 Using this distribution of estimators, a confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles.
@@
 
-For a certain AR coefficient, a block bootstrap 95\% confidence interval is replicated 1000 times at a starting sample size at which block bootstrap is expected to be very effective (a relatively large sample).
+For a certain AR coefficient, a block bootstrap 95\% confidence interval is replicated 4000 times at a starting sample size at which block bootstrap is expected to be very effective (a relatively large sample).
 For each individual confidence interval, it can be recorded whether or not the interval includes the true mean (0).
@@
 If this is not the case, the method is not working as well as it should.
-Since the coverage rate is a proportion, a 95\% confidence interval of the coverage rate can also be created.
+Since the coverage rate is a proportion based on many replication of independent Bernoulli outcomes, a 95\% confidence interval of the coverage rate at that sample size can also be created.
 Once the simulation is done for the starting n, the sample size can gradually be lowered until the coverage rates and their respective confidence intervals indicate that the method no longer functions well.
@@
 
-Before each simulation (1000 replications of confidence intervals from block bootstrapped sample mean distributions), the random seed was set to 5 so that the randomized results can be 
+Before each simulation (4000 replications of confidence intervals from block bootstrapped sample mean distributions), the random seed was set to 5 so that the randomized results can be 
 reproduced.
@@
 the sample size and AR Coefficient
- were varied. The AR Coefficients that were used were 0 (or a regular sample with no temporal dependence) 0.2, 0.4, and 0.6. The sample sizes 
+ were varied. The AR Coefficients that were used were 0 (or a sample from a normal distribution with no temporal dependence) 0.2, 0.4, and 0.6. The sample sizes 
  that were used depended on the AR
@@
 required for effective block bootstrap estimation.
+When AR = 0.2, n = 225, and l = $\sqrt{n}$, we are 95\% confident that the coverage rate given an infinite number of replications is within the interval \[0.907, 0.940\] for the non-moving method and \[0.916, 0.932\] for the moving method.
+When AR = 0.2, n = 225, and l = $\sqrt{n}$, we are 95\% confident that the coverage rate given an infinite number of replications is within the interval \[0.888, 0.925\] for the non-moving method and \[0.900, 0.918\] for the moving method.
+When AR = 0.2, n = 100, and l = $\sqrt{n}$, we are 95\% confident that the coverage rate given an infinite number of replications is within the interval \[0.883, 0.920\].
 
@@
   \caption{}
-  \label{fig:constant_0}
+  \label{fig:constant_norm}
 \end{figure}
@@
   \caption{}
-  \label{fig:root_0}
+  \label{fig:root_norm}
 \end{figure}

### 2022-10-27 Manuscript/manuscript.tex
New Plot

@@
 large, the method will work perfectly. However, for a finite sample size, the method will 
-not work as well as expected. It may be necessary (in order to plan an applied 
+not work as well as expected.
+\citet{hesterberg2015teachers} notes that while intervals based on the percentiles from nonparametric bootstrapping are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
+It may be necessary (in order to plan an applied
 statistical 
@@
 increases, the optimal block length should increase, and the ratio of the block length to 
-the time series length should decrease. l = n$^3$ is typically considered the optimal 
-block length according to asymptotic theory. \citep{buhlmann1999block} If only perfect cubes are used for the time 
-series length, n gets quite large when l increases by relatively little. An alternative 
-would be to use smaller time series, find the cube root, and set the block length to the 
-nearest whole number. However, in this study l = sqrt{n} is used, as it allows for smaller 
-sample sizes while still using perfect squares.
+the time series length should decrease. l = n$^{1/3}$ is typically considered the optimal 
+block length according to asymptotic theory.
+\citep{buhlmann1999block} The effect of this relation on the block bootstrap method was observed in this study.
+Simulations were conducted with a constant l, l = $\sqrt{n}$, and l = n$^{1/3}$.
 
@@
 The block should be of size l large enough to include time dependence, yet small enough to include some variance.
+As n increases, an ideal l should also increase, but the ratio of l to n should decrease.
+To achieve this, l is often assigned a value as a function of n.
+A common function that is considered the best by much previous literature is l = n$^{1/3}$.
+However not all n sizes are perfect squares, and l must be a whole number, so the ceiling of this function must be used.
+The same can be done for the $\sqrt{n}$.
 A bootstrapped sample is created by taking a sample of n / l blocks with replacement to create a new series of size n.
@@
 An estimator of the parameter is computed from the bootstrapped sample.
-This procedure can be repeated many times to create a sampling distribution of the estimator.
+This procedure can be repeated many times (typically 1000) to create a sampling distribution of the estimator.
 Using this distribution of estimators, a confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles.
@@
 The coverage rate, or the proportion of intervals that include the mean, can then be recorded.
-If the variance is being properly estimated by the block bootstrap, the coverage rate should reflect this by being close to the confidence level of 95\%.
+If the parameter and its variance are being properly estimated by the block bootstrap, the coverage rate should reflect this by being close to the confidence level of 95\%.
 If this is not the case, the method is not working as well as it should.
+The width of the confidence interval for each replication is dependent on the variance of the means of the bootstrapped samples.
+If the interval is not wide enough to capture the mean at the expected rate of 95\%, it indicates that the variance of the parameter (which will be estimated from the variance of the means of the bootstrapped samples) will be underestimated.
 Since the coverage rate is a proportion based on many replication of independent Bernoulli outcomes, a 95\% confidence interval of the coverage rate at that sample size can also be created.
@@
 
-Before each simulation (4000 replications of confidence intervals from block bootstrapped sample mean distributions), the random seed was set to 5 so that the randomized results can be 
+Before each set of 4000 replications of confidence intervals from block bootstrapped sample mean distributions, the random seed was set to 5 so that the randomized results can be 
 reproduced.
@@
 The mean and standard deviation of the time series was held constant at 0 and 0.1, respectively, whereas 
-the sample size and AR Coefficient
- were varied. The AR Coefficients that were used were 0 (or a sample from a normal distribution with no temporal dependence) 0.2, 0.4, and 0.6. The sample sizes 
+the sample length and AR Coefficient
+ were varied.
+The AR Coefficients that were observed with were 0.2, 0.4, and 0.6.
+Normally distributed samples, in other words, samples with AR Coefficients of 0, were also experimented with as a control group to compare against.
+The sample lengths
  that were used depended on the AR
- Coefficient, and the function used to compute l. For each of these variations, 1000 
- confidence intervals are created using
- the block bootstrap method, and the proportion of these intervals that recover the true 
- mean (0) is recorded as the coverage
- rate. The block bootstrap method has different settings that were varied in this study: 
- non-moving vs moving, 
-and the function for block length - the two used were a constant block length of 10 and 
-the square root of n.
+ Coefficient and the function used to compute l.
 
-For the simulations using a constant block length of 10, the sample size was gradually 
-lowered by increments of 20 to see when
-the block bootstrap would begin to consistently return low coverage rates. For both AR = 0 and AR = 0.2 
-using a constant l, results for
-sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, 
-results for sample sizes ranging from 600
-to 20 were observed. For AR = 0.6, using a constant l, results for sample sizes ranging 
-from 900 to 120 were observed. For the simulations in which the block length was the 
-square root of the time series length, the only sample sizes used were perfect squares so 
-that the blocks would have whole number lengths. For AR = 0.2 using l = $\sqrt{n}$, results 
-for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using $\sqrt{n}$, results 
-for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = $\sqrt{n}$, 
-results for sample sizes ranging from 1600 to 121 were observed.
+ The block bootstrap method has different settings that were varied in this study: 
+ non-moving vs moving, and the function for block length - the three functions used were l = 10 and 
+the l = f(n) = $\lceil \sqrt{n} \rceil$, and l = f(n) = $\lceil n^{1/3} \rceil$. That means six variations of the block bootstrap method.
+
+For each simulated ARIMA process, the block bootstrap method with each of these six variations was applied to the sample.
+4000 replications were conducted, meaning that 4000 samples of the same size from a process with the same parameters were simulated.
+For each sample, a 95\% confidence interval was created, and for each block bootstrap variation, the proportion of all 4000 intervals (created using that variation) that recovered the true mean (0) was recorded as the coverage
+ rate for that specific variation. 95\% confidence intervals for these proportions were also computed.
+
+For each AR coefficient, a starting sample size was decided based on expectations of how the bootstrap method would perform. Then, the sample size was gradually lowered by increments of 20 to see when
+the block bootstrap would begin to consistently return low coverage rates.
+
+For both AR = 0 and AR = 0.2, results for sample sizes ranging from 400 to 20 were observed.
+For AR = 0.4, results for sample sizes ranging from 600 to 20 were observed.
+For AR = 0.6, results for sample sizes ranging from 900 to 20 were observed.
 
@@
 required for effective block bootstrap estimation.
-When AR = 0.2, n = 225, and l = $\sqrt{n}$, we are 95\% confident that the coverage rate given an infinite number of replications is within the interval \[0.907, 0.940\] for the non-moving method and \[0.916, 0.932\] for the moving method.
-When AR = 0.2, n = 225, and l = $\sqrt{n}$, we are 95\% confident that the coverage rate given an infinite number of replications is within the interval \[0.888, 0.925\] for the non-moving method and \[0.900, 0.918\] for the moving method.
-When AR = 0.2, n = 100, and l = $\sqrt{n}$, we are 95\% confident that the coverage rate given an infinite number of replications is within the interval \[0.883, 0.920\].
+The tables below for each corresponding block length function and AR Coefficient display information about the length of the sample of the ARIMA process, the block length used in bootstrap, the method (non-moving or moving), and the proportion of 95\% confidence intervals produced by each of 4000 block bootstrap replications that recover the mean, as well as an interval in which we can be 95\% confident that the true coverage rate given an infinite number of replications is contained.
+As shown in the plots, as n decreases, the coverage rate decreases.
+As AR increases, not only is a larger sample size required for effective bootstrap estimation, but the level of noise also increases.
+The best block length function, as shown in previous literature, is l = n$^{1/3}$, as it yields the most consistently high coverage rates even for samples as small as n = 20.
+For the larger sample sizes, there does not appear to be a significant difference in results for moving method vs non-moving method.
+However, block bootstrap with moving method appears to perform better for smaller sample sizes than block bootstrap with non-moving method.
 
-\begin{figure}[tbp]
+\begin{figure}[p]
   \centering
-  \includegraphics[width=\textwidth]{constant_0}
+  \includegraphics[width=\textwidth]{norm}
   \caption{}
-  \label{fig:constant_norm}
+  \label{fig:norm}
 \end{figure}
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{constant_0.2}
-  \caption{}
-  \label{fig:constant_0.2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{constant_0.4}
-  \caption{}
-  \label{fig:constant_0.4}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{constant_0.6}
-  \caption{}
-  \label{fig:constant_0.6}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{root_0}
-  \caption{}
-  \label{fig:root_norm}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{root_0.2}
-  \caption{}
-  \label{fig:root_0.2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{root_0.4}
-  \caption{}
-  \label{fig:root_0.4}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{root_0.6}
-  \caption{}
-  \label{fig:root_0.6}
-\end{figure}
-
-\label{sec:results}
+%\begin{figure}[p]
+%  \centering
+%  \includegraphics[width=\textwidth]{ar_0.2}
+%  \caption{}
+%  \label{fig:ar_0.2}
+%\end{figure}
+%
+%\begin{figure}[p]
+%  \centering
+%  \includegraphics[width=\textwidth]{ar_0.4}
+%  \caption{}
+%  \label{fig:ar_0.4}
+%\end{figure}
+%
+%\begin{figure}[p]
+%  \centering
+%  \includegraphics[width=\textwidth]{ar_0.6}
+%  \caption{}
+%  \label{fig:ar_0.6}
+%\end{figure}
 
@@
 
+This study finds that as the AR coefficient increases, the sample size necessary for good block bootstrap estimation must be larger.
+
 \bibliographystyle{chicago}
-\bibliography{citations.bib}
+\bibliography{citations.bib}[tp]
 

### 2022-10-27 Manuscript/manuscript.tex
Fix?
manuscript.tex

@@
 As AR increases, not only is a larger sample size required for effective bootstrap estimation, but the level of noise also increases.
-The best block length function, as shown in previous literature, is l = n$^{1/3}$, as it yields the most consistently high coverage rates even for samples as small as n = 20.
+The best block length function, as shown in previous literature, \citep{buhlmann1999block} is l = n$^{1/3}$, as it yields the most consistently high coverage rates even for samples as small as n = 20.
+l = 10 seems to perform better than l = $\sqrt{n}$ for higher sample sizes, but the coverage rates for l = 10 drop down much more for small sample sizes than l = $\sqrt{n}$.
 For the larger sample sizes, there does not appear to be a significant difference in results for moving method vs non-moving method.
@@
 \bibliographystyle{chicago}
-\bibliography{citations.bib}[tp]
+\bibliography{citations}[tp]
 

### 2022-11-10 Manuscript/manuscript.tex
New Figures
Update Manuscript

--- 2022-10-27 Manuscript/manuscript.tex
@@
 The question for this study is how does one determine at what length the block
-bootstrap method stops being an effective method to estimate a parameter of a time
+bootstrap method stops being effective to estimate a parameter of a time
 series.
@@
 as econometrics \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}. It can be used for 
-situations in which there is temporal dependence and the goal is estimation or hypothesis 
-testing. Assuming that the sample is infinitely 
+situations in which there is temporal dependence, and the goal is the estimation or testing a hypothesis about a parameter. Assuming that the sample is infinitely 
 large, the method will work perfectly. However, for a finite sample size, the method will 
@@
 \citet{hesterberg2015teachers} notes that while intervals based on the percentiles from nonparametric bootstrapping are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
-It may be necessary (in order to plan an applied
-statistical 
-procedure) to know at which sample size the method stops working at an acceptable level. 
-The goal of this study is to find a threshold or range of sample sizes at block bootstrap 
+In the context of planning an applied
+statistical procedure, for which a large sample size is not always practical, it may be helpful to know at which sample size the method stops working at an acceptable level. 
+The goal of this study is to find a threshold or range of sample sizes at whichblock bootstrap 
 is no longer an effective method for estimating variance.
 
-\citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for standard 
-bootstrap estimation. However, block bootstrapping is a different situation because the 
-sample is split into blocks.
+\citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for estimation using the bootstrap method (simple resampling with no blocks involved).
+However, block bootstrapping is a different situation altogether because the sample is split into blocks.
 
@@
 may be significantly more accurate than inference from closed-form asymptotic estimates.
-That study focused on variance estimation within the context of linear regression.
-Still, the rate at which confidence intervals recover the true variance for small sample sizes wasn't very close to the confidence level of the intervals.
-This study aims to find how small the sample size can be for time series (which has a dependence factor which can be compared to a linear regression) in order for the coverage rate to be close to the confidence level.
+That study focused on the estimation of a parameter within the context of linear regression.
+Still, the block bootstrap percentile confidence intervals under covered even for n = 1024.
+This study aims to find how small the sample size can be for time series (which has a dependence factor which can be compared to that of a linear regression) in order for the coverage rate to be close to the confidence level.
 
-For this study, many block bootstrap simulations were conducted with R. At the base
+For this study, many block bootstrap simulations were conducted with RStudio. At the base
 level, we are block-bootstrapping an auto-regressive process with true mean 0.
 Bootstrapping is the term for creating new samples of the same size by re-sampling from
-the original sample with replacement. Many bootstrapped samples are used to create a
-distribution of sampling means to estimate mean and variance. This works for samples
-that are not dependent. However, for a time series such as an auto-regressive process,
+the original sample with replacement. The means of many bootstrapped samples are used to create a
+distribution of sampling means to estimate mean and variance. This works well for samples
+that are do not have a dependence factor. However, for a time series such as an auto-regressive process,
 a different procedure is required to account for the time dependence. In such a case,
-the series is split into blocks that may overlap (moving block bootstrap) or may not
-overlap (non-moving block bootstrap). These blocks are then re-sampled to create new
-bootstrapped time series.
+the series is split into blocks that can overlap (moving block bootstrap) or not(non-moving block bootstrap). These blocks are then re-sampled to create a new
+bootstrapped time series sample.
 
@@
 block length according to asymptotic theory.
-\citep{buhlmann1999block} The effect of this relation on the block bootstrap method was observed in this study.
-Simulations were conducted with a constant l, l = $\sqrt{n}$, and l = n$^{1/3}$.
+\citep{buhlmann1999block} The effect of the block function on the performance block bootstrap method was observed in this study.
+Simulations were conducted using block functions of l = 10 and l = n$^{1/3}$.
 
-So to solve the question of what n is necessary for effective block bootstrapping,
+In order to solve the question of what n is necessary for effective block bootstrapping,
 while still accounting for all these factors, the simulations were repeated for
-multiple combinations of AR coefficient and the function of n used to decide l. In 
-addition, the coverage rates
-for both the non-moving and moving methods were recorded.
+various combinations of AR coefficients, block length functions, and non-moving vs moving method. For each of these combinations, coverage rates were recorded for a wide range of sample sizes.
 
@@
 However not all n sizes are perfect squares, and l must be a whole number, so the ceiling of this function must be used.
-The same can be done for the $\sqrt{n}$.
 A bootstrapped sample is created by taking a sample of n / l blocks with replacement to create a new series of size n.
@@
 If the blocks do overlap, it is called a moving block bootstrap.
-n / l samples are taken randomly from the original sample, but they do not have to be from a group of evenly spaced blocks.
+n / l samples are taken randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
 An estimator of the parameter is computed from the bootstrapped sample.
 This procedure can be repeated many times (typically 1000) to create a sampling distribution of the estimator.
-Using this distribution of estimators, a confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles.
+Using this distribution of estimators, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles.
 
@@
 
-The central objective of the study was to assess at which sample size block bootstrap no longer estimates the variance well for an autoregressive process.
-The method will work better as sample size goes to infinity, but the goal is to see what is the smallest sample size that is acceptable.
-To achieve this, simulations must first be conducted with a larger sample size in order to compare to results with a smaller n.
+The central objective of the study was to assess at which sample size the block bootstrap method no longer estimates the variance well for an autoregressive process.
+The method will work better as the sample size goes to infinity, but the goal is to see what is the smallest sample size that is acceptable.
+To achieve this, simulations must first be conducted with a larger sample size in order to compare to results with a smaller sample size.
 In the previous section, the procedure for creating a confidence interval using the block bootstrap method is described.
@@
  that were used depended on the AR
- Coefficient and the function used to compute l.
+ Coefficient, but the lowest sample length observed was always n = 20.
 
  The block bootstrap method has different settings that were varied in this study: 
- non-moving vs moving, and the function for block length - the three functions used were l = 10 and 
-the l = f(n) = $\lceil \sqrt{n} \rceil$, and l = f(n) = $\lceil n^{1/3} \rceil$. That means six variations of the block bootstrap method.
+ non-moving vs moving, and the function for block length - the three functions used were l = 10 and l = f(n) = $\lceil n^{1/3} \rceil$. That means six variations of the block bootstrap method.
 
@@
 As AR increases, not only is a larger sample size required for effective bootstrap estimation, but the level of noise also increases.
-The best block length function, as shown in previous literature, is l = n$^{1/3}$, as it yields the most consistently high coverage rates even for samples as small as n = 20.
+The best block length function, as shown in previous literature \citep{buhlmann1999block}, is l = n$^{1/3}$, as it yields the most consistently high coverage rates even for samples as small as n = 20.
+l = 10 seems to perform almost as well as l = n$^{1/3}$ for higher sample sizes, but the coverage rates for l = 10 drop down much more for small sample sizes.
 For the larger sample sizes, there does not appear to be a significant difference in results for moving method vs non-moving method.
@@
 
-\begin{figure}[p]
+\begin{figure}[tbp]
+\caption{The figure below demonstrates how block bootstrap performs at estimating the mean of a normal population.
+As shown in the plots, even for a sample with no time dependency, a very large sample size is needed to even approach a coverage rate of 95\%.
+While for large sample sizes (approximately greater than 300), the performance for l = 10 is comparable to the performance for l = n$^{1/3}$, the performance with l = 10 is much worse than that for l = n$^{1/3}$ when using very small sample sizes (approximately less than 100).
+The moving method seems to have a similar performance to the non-moving method, although it appears to perform slightly better for very low sample sizes regardless of the block length function.}
   \centering
@@
 
-%\begin{figure}[p]
-%  \centering
-%  \includegraphics[width=\textwidth]{ar_0.2}
-%  \caption{}
-%  \label{fig:ar_0.2}
-%\end{figure}
-%
-%\begin{figure}[p]
-%  \centering
-%  \includegraphics[width=\textwidth]{ar_0.4}
-%  \caption{}
-%  \label{fig:ar_0.4}
-%\end{figure}
-%
-%\begin{figure}[p]
-%  \centering
-%  \includegraphics[width=\textwidth]{ar_0.6}
-%  \caption{}
-%  \label{fig:ar_0.6}
-%\end{figure}
+\begin{figure}[tbp]
+\caption{The figure below demonstrates how block bootstrap performs at estimating the mean of a AR = 0.2 process.
+As shown in the plots, even for a sample with relatively low dependency, a very large sample size is needed to even approach a coverage rate of 95\%.
+While for large sample sizes (approximately greater than 200), the performance for l = 10 is comparable to the performance for l = n$^{1/3}$, the performance with l = 10 is much worse than that for l = n$^{1/3}$ when using small sample sizes (approximately less than 100).
+Again, the moving method seems to have a similar performance overall to the non-moving method, but the coverage rates drop off slightly more for non-moving method when using smaller sample sizes.}
+  \centering
+  \includegraphics[width=\textwidth]{ar_0.2}
+  \caption{}
+  \label{fig:ar_0.2}
+\end{figure}
+
+\begin{figure}[tbp]
+\caption{The figure below demonstrates how block bootstrap performs at estimating the mean of a AR = 0.4 process.
+As shown in the plots, even for a sample of size 600, the block bootstrap method fails to adequately capture the mean at a rate of \%.
+While for large sample sizes, the performance for l = 10 is comparable to the performance for l = n$^{1/3}$, the performance with l = 10 is much worse than that for l = n$^{1/3}$ when using small sample sizes.
+Again, the moving method seems to have a similar performance overall to the non-moving method, but the coverage rates drop off slightly more for non-moving method when using smaller sample sizes.}
+  \centering
+  \includegraphics[width=\textwidth]{ar_0.4}
+  \caption{}
+  \label{fig:ar_0.4}
+\end{figure}
+
+\begin{figure}[tbp]
+\caption{The figure below demonstrates how block bootstrap performs at estimating the mean of a AR = 0.6 process.
+As shown in the plots, even for a sample of size 900, the block bootstrap method fails to adequately capture the mean at a rate of 95\%.
+While for large sample sizes, the performance for l = 10 is comparable to the performance for l = n$^{1/3}$, the performance with l = 10 is much worse than that for l = n$^{1/3}$ when using small sample sizes.
+Again, the moving method seems to have a similar performance overall to the non-moving method, but the coverage rates drop off slightly more for non-moving method when using smaller sample sizes, although the difference is less noticeable than for samples with lesser time dependence.}
+  \centering
+  \includegraphics[width=\textwidth]{ar_0.6}
+  \caption{}
+  \label{fig:ar_0.6}
+\end{figure}
 
@@
 
-This study finds that as the AR coefficient increases, the sample size necessary for good block bootstrap estimation must be larger.
+This study finds that as the AR coefficient increases, the sample size necessary for effective block bootstrap estimation must be larger.
+When implementing the block bootstrap method using a block length function of l = n$^{1/3}$ results in the highest coverage rates overall (indicating a more accurate estimation of a parameter and its variance), but using l = 10 results in similar performance for large sample sizes.
+It is important to note that a different constant block length will perform differently for different ranges of sample sizes.
+While the moving-method and non-moving method yield similar coverage rates, the non-moving method performs slightly worse when using very small sample sizes.
 
 \bibliographystyle{chicago}
-\bibliography{citations.bib}[tp]
+\bibliography{citations}[tp]
 

### 2022-11-17 Manuscript/UpdatedBlockBootstrap.Rmd
Updated Block Bootstrap

```{r functions, echo = FALSE}
nmblk <- function(n, l) {
  b <- n / l # assuming that is an integer
  idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE) # Sample between 1 and n - l + 1, 
  # separating by l, b times
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points 
  # decided by idx
}

mvblk <- function(n, l) {
  b <- n / l
  idx <- sample(1:(n - l + 1), b, replace = TRUE) # Sample any starting point between 1 and n - 1 + 1
  # they can overlap
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points
  # decided by idx
}

blkboot <- function(tseries, statistic, R, l) {
  n <- length(tseries) 
  ## observed statistic
  stat <- statistic(tseries) #stat stores a certain statistic of tseries using a function
  ## nonmoving block bootstrap
  nm.stat <- replicate(R, statistic(tseries[nmblk(n, l)])) # finds the statistic of nm bootstrap and repeats R times
  ## moving block bootstrap
  mv.stat <- replicate(R, statistic(tseries[mvblk(n, l)])) # finds the statistic of mv bootstrap and repeats R times
  list(stat = stat, nm.stat = nm.stat, mv.stat = mv.stat) # returns list of three values
}

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n = n, sd = sqrt((sd^2)*(1-theta^2)))

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  value = 0
  if (identical(statistic, ar1))
  {
    value = theta
  }
  if (nm_interval[1] < value && nm_interval[2] > value)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < value && mv_interval[2] > value)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

}

do1rep2 <- function(n, theta, sd, l, statistic) {
  x <- rnorm(n = n, sd = sd)

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  value = 0
  if (identical(statistic, ar1))
  {
    value = theta
  }

  if (nm_interval[1] < value && nm_interval[2] > value)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < value && mv_interval[2] > value)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

}
```

```{r more_functions, echo = False}
options(max.print = 1000000)
ar1 <- function(x) cor(x[-1], x[-length(x)])
#ar1 <- function(x) acf(x, plot = FALSE, lag.max = 1)$acf[2]
m1 <- function(x) mean(x)

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]), rm[5] + qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 4000), rm[5] - qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 4000),  rm[9] + qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 4000), rm[9] - qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 4000))
}

```

```{r Normal Sample n = 32}
set.seed(5)
(m_norm_32 = my_summary(replicate(4000, do1rep2(32, 0, 0.1, ceiling(32**(1/3)), m1))))
set.seed(5)
(ar_norm_32 = my_summary(replicate(4000, do1rep2(32, 0, 0.1, ceiling(32**(1/3)), ar1))))
```

```{r Normal Sample n = 64}
set.seed(5)
(m_norm_64 = my_summary(replicate(4000, do1rep2(64, 0, 0.1, ceiling(64**(1/3)), m1))))
set.seed(5)
(ar_norm_64 = my_summary(replicate(4000, do1rep2(64, 0, 0.1, ceiling(64**(1/3)), ar1))))
```

```{r Normal Sample n = 128}
set.seed(5)
(m_norm_128 = my_summary(replicate(4000, do1rep2(128, 0, 0.1, ceiling(128**(1/3)), m1))))
set.seed(5)
(ar_norm_128 = my_summary(replicate(4000, do1rep2(128, 0, 0.1, ceiling(128**(1/3)), ar1))))
```

```{r Normal Sample n = 256}
set.seed(5)
(m_norm_256 = my_summary(replicate(4000, do1rep2(256, 0, 0.1, ceiling(256**(1/3)), m1))))
set.seed(5)
(ar_norm_256 = my_summary(replicate(4000, do1rep2(256, 0, 0.1, ceiling(256**(1/3)), ar1))))
```

```{r Normal Sample n = 512}
set.seed(5)
(m_norm_512 = my_summary(replicate(4000, do1rep2(512, 0, 0.1, ceiling(512**(1/3)), m1))))
set.seed(5)
(ar_norm_512 = my_summary(replicate(4000, do1rep2(512, 0, 0.1, ceiling(512**(1/3)), ar1))))
```

```{r Normal Sample n = 1024}
set.seed(5)
(m_norm_1024 = my_summary(replicate(4000, do1rep2(1024, 0, 0.1, ceiling(1024**(1/3)), m1))))
```

```{r Normal Sample n = 2048}
set.seed(5)
(m_norm_2048 = my_summary(replicate(4000, do1rep2(2048, 0, 0.1, ceiling(2048**(1/3)), m1))))
```

```{r AR = 0.2 Sample n = 32}
set.seed(5)
(m_0.2_32 = my_summary(replicate(4000, do1rep(32, 0.2, 0.1, ceiling(32**(1/3)), m1))))
set.seed(5)
(ar_0.2_32 = my_summary(replicate(4000, do1rep(32, 0.2, 0.1, ceiling(32**(1/3)), ar1))))
```

```{r AR = 0.2 Sample n = 64}
set.seed(5)
(m_0.2_64 = my_summary(replicate(4000, do1rep(64, 0.2, 0.1, ceiling(64**(1/3)), m1))))
set.seed(5)
(ar_0.2_64 = my_summary(replicate(4000, do1rep(64, 0.2, 0.1, ceiling(64**(1/3)), ar1))))
```

```{r AR = 0.2 Sample n = 128}
set.seed(5)
(m_0.2_128 = my_summary(replicate(4000, do1rep(128, 0.2, 0.1, ceiling(128**(1/3)), m1))))
set.seed(5)
(ar_0.2_128 = my_summary(replicate(4000, do1rep(128, 0.2, 0.1, ceiling(128**(1/3)), ar1))))
```

```{r AR = 0.2 Sample n = 256}
set.seed(5)
(m_0.2_256 = my_summary(replicate(4000, do1rep(256, 0.2, 0.1, ceiling(256**(1/3)), m1))))
set.seed(5)
(ar_0.2_256 = my_summary(replicate(4000, do1rep(256, 0.2, 0.1, ceiling(256**(1/3)), ar1))))
```

```{r AR = 0.2 Sample n = 512}
set.seed(5)
(m_0.2_512 = my_summary(replicate(4000, do1rep(512, 0.2, 0.1, ceiling(512**(1/3)), m1))))
set.seed(5)
(ar_0.2_512 = my_summary(replicate(4000, do1rep(512, 0.2, 0.1, ceiling(512**(1/3)), ar1))))
```

```{r AR = 0.2 Sample n = 1024}
set.seed(5)
(m_0.2_1024 = my_summary(replicate(4000, do1rep(1024, 0.2, 0.1, ceiling(1024**(1/3)), m1))))
set.seed(5)
(ar_0.2_1024 = my_summary(replicate(4000, do1rep(1024, 0.2, 0.1, ceiling(1024**(1/3)), ar1))))
```

```{r AR = 0.2 Sample n = 2048}
set.seed(5)
(m_0.2_2048 = my_summary(replicate(4000, do1rep(2048, 0.2, 0.1, ceiling(2048**(1/3)), m1))))
set.seed(5)
(ar_0.2_2048 = my_summary(replicate(4000, do1rep(2048, 0.2, 0.1, ceiling(2048**(1/3)), ar1))))
```

```{r AR = 0.4 Sample n = 32}
set.seed(5)
(m_0.4_32 = my_summary(replicate(4000, do1rep(32, 0.4, 0.1, ceiling(32**(1/3)), m1))))
set.seed(5)
(ar_0.4_32 = my_summary(replicate(4000, do1rep(32, 0.4, 0.1, ceiling(32**(1/3)), ar1))))
```

```{r AR = 0.4 Sample n = 64}
set.seed(5)
(m_0.4_64 = my_summary(replicate(4000, do1rep(64, 0.4, 0.1, ceiling(64**(1/3)), m1))))
set.seed(5)
(ar_0.4_64 = my_summary(replicate(4000, do1rep(64, 0.4, 0.1, ceiling(64**(1/3)), ar1))))
```

```{r AR = 0.4 Sample n = 128}
set.seed(5)
(m_0.4_128 = my_summary(replicate(4000, do1rep(128, 0.4, 0.1, ceiling(128**(1/3)), m1))))
set.seed(5)
(ar_0.4_128 = my_summary(replicate(4000, do1rep(128, 0.4, 0.1, ceiling(128**(1/3)), ar1))))
```

```{r AR = 0.4 Sample n = 256}
set.seed(5)
(m_0.4_256 = my_summary(replicate(4000, do1rep(256, 0.4, 0.1, ceiling(256**(1/3)), m1))))
set.seed(5)
(ar_0.4_256 = my_summary(replicate(4000, do1rep(256, 0.4, 0.1, ceiling(256**(1/3)), ar1))))
```

```{r AR = 0.4 Sample n = 512}
set.seed(5)
(m_0.4_512 = my_summary(replicate(4000, do1rep(512, 0.4, 0.1, ceiling(512**(1/3)), m1))))
set.seed(5)
(ar_0.4_512 = my_summary(replicate(4000, do1rep(512, 0.4, 0.1, ceiling(512**(1/3)), ar1))))
```

```{r AR = 0.4 Sample n = 1024}
set.seed(5)
(m_0.4_1024 = my_summary(replicate(4000, do1rep(1024, 0.4, 0.1, ceiling(1024**(1/3)), m1))))
set.seed(5)
(ar_0.4_1024 = my_summary(replicate(4000, do1rep(1024, 0.4, 0.1, ceiling(1024**(1/3)), ar1))))
```

```{r AR = 0.4 Sample n = 2048}
set.seed(5)
(m_0.4_2048 = my_summary(replicate(4000, do1rep(2048, 0.4, 0.1, ceiling(2048**(1/3)), m1))))
set.seed(5)
(ar_0.4_2048 = my_summary(replicate(4000, do1rep(2048, 0.4, 0.1, ceiling(2048**(1/3)), ar1))))
```

```{r AR = 0.4 Sample n = 4096}
set.seed(5)
(m_0.4_4096 = my_summary(replicate(4000, do1rep(4096, 0.4, 0.1, ceiling(4096**(1/3)), m1))))
set.seed(5)
(ar_0.4_4096 = my_summary(replicate(4000, do1rep(4096, 0.4, 0.1, ceiling(4096**(1/3)), ar1))))
```

```{r}
#m_norm_1024 <- c(1024, m_norm_1024)
```

```{r}
m_norm <- data.frame(rbind(t(m_norm_32[c(1, 6, 17, 16)]), t(m_norm_32[c(1, 10, 19, 18)]), t(m_norm_64[c(1, 6, 17, 16)]), t(m_norm_64[c(1, 10, 19, 18)]), t(m_norm_128[c(1, 6, 17, 16)]), t(m_norm_128[c(1, 10, 19, 18)]), t(m_norm_256[c(1, 6, 17, 16)]), t(m_norm_256[c(1, 10, 19, 18)]), t(m_norm_512[c(1, 6, 17, 16)]), t(m_norm_512[c(1, 10, 19, 18)]), t(m_norm_1024[c(1, 6, 17, 16)]), t(m_norm_1024[c(1, 10, 19, 18)])))
rownames(m_norm) <- NULL
colnames(m_norm) <- c("n", 'coverage_rate', 'lb', 'ub')
m_norm['method'] <- c('nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv')
library(dplyr)
m_norm[order(-m_norm$n), ]
```

```{r}
ggplot(m_norm, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(~ method) +
  labs(title = 'AR = 0', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  scale_x_continuous(trans='log2') +
  theme(legend.position="none")
```

```{r}
ar_norm <- data.frame(rbind(t(ar_norm_32[c(1, 6, 17, 16)]), t(ar_norm_32[c(1, 10, 19, 18)]), t(ar_norm_64[c(1, 6, 17, 16)]), t(ar_norm_64[c(1, 10, 19, 18)]), t(ar_norm_128[c(1, 6, 17, 16)]), t(ar_norm_128[c(1, 10, 19, 18)]), t(ar_norm_256[c(1, 6, 17, 16)]), t(ar_norm_256[c(1, 10, 19, 18)]), t(ar_norm_512[c(1, 6, 17, 16)]), t(ar_norm_512[c(1, 10, 19, 18)])))
rownames(ar_norm) <- NULL
colnames(ar_norm) <- c("n", 'coverage_rate', 'lb', 'ub')
ar_norm['method'] <- c('nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv')
library(dplyr)
ar_norm[order(-ar_norm$n), ]
```

```{r}
ggplot(ar_norm, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(~ method) +
  labs(title = 'AR = 0', x = 'Time Series Length', y = 'Confidence Interval AR(1) Coefficient Recovery Rate') +
  scale_x_continuous(trans='log2') +
  theme(legend.position="none")
```

```{r}
m_0.2 <- data.frame(rbind(t(m_0.2_32[c(1, 6, 17, 16)]), t(m_0.2_32[c(1, 10, 19, 18)]), t(m_0.2_64[c(1, 6, 17, 16)]), t(m_0.2_64[c(1, 10, 19, 18)]), t(m_0.2_128[c(1, 6, 17, 16)]), t(m_0.2_128[c(1, 10, 19, 18)]), t(m_0.2_256[c(1, 6, 17, 16)]), t(m_0.2_256[c(1, 10, 19, 18)]), t(m_0.2_512[c(1, 6, 17, 16)]), t(m_0.2_512[c(1, 10, 19, 18)]), t(m_0.2_1024[c(1, 6, 17, 16)]), t(m_0.2_1024[c(1, 10, 19, 18)])))
rownames(m_0.2) <- NULL
colnames(m_0.2) <- c("n", 'coverage_rate', 'lb', 'ub')
m_0.2['method'] <- c('nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv')
library(dplyr)
m_0.2[order(-m_0.2$n), ]
```

```{r}
ggplot(m_0.2, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(~ method) +
  labs(title = 'AR = 0.2', x = 'Time Series Length', y = 'Confidence Interval AR(1) Coefficient Recovery Rate') +
  scale_x_continuous(trans='log2') +
  theme(legend.position="none")
```

```{r}
ar_0.2 <- data.frame(rbind(t(ar_0.2_32[c(1, 6, 17, 16)]), t(ar_0.2_32[c(1, 10, 19, 18)]), t(ar_0.2_64[c(1, 6, 17, 16)]), t(ar_0.2_64[c(1, 10, 19, 18)]), t(ar_0.2_128[c(1, 6, 17, 16)]), t(ar_0.2_128[c(1, 10, 19, 18)]), t(ar_0.2_256[c(1, 6, 17, 16)]), t(ar_0.2_256[c(1, 10, 19, 18)]), t(ar_0.2_512[c(1, 6, 17, 16)]), t(ar_0.2_512[c(1, 10, 19, 18)]), t(ar_0.2_1024[c(1, 6, 17, 16)]), t(ar_0.2_1024[c(1, 10, 19, 18)])))
rownames(ar_0.2) <- NULL
colnames(ar_0.2) <- c("n", 'coverage_rate', 'lb', 'ub')
ar_0.2['method'] <- c('nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv')
library(dplyr)
ar_0.2[order(-ar_0.2$n), ]
```
```{r}
ggplot(ar_0.2, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(~ method) +
  labs(title = 'AR = 0.2', x = 'Time Series Length', y = 'Confidence Interval AR(1) Coefficient Recovery Rate') +
  scale_x_continuous(trans='log2') +
  theme(legend.position="none")
```

```{r}
m_0.4 <- data.frame(rbind(t(m_0.4_32[c(1, 6, 17, 16)]), t(m_0.4_32[c(1, 10, 19, 18)]), t(m_0.4_64[c(1, 6, 17, 16)]), t(m_0.4_64[c(1, 10, 19, 18)]), t(m_0.4_128[c(1, 6, 17, 16)]), t(m_0.4_128[c(1, 10, 19, 18)]), t(m_0.4_256[c(1, 6, 17, 16)]), t(m_0.4_256[c(1, 10, 19, 18)]), t(m_0.4_512[c(1, 6, 17, 16)]), t(m_0.4_512[c(1, 10, 19, 18)]), t(m_0.4_1024[c(1, 6, 17, 16)]), t(m_0.4_1024[c(1, 10, 19, 18)]), t(m_0.4_2048[c(1, 6, 17, 16)]), t(m_0.4_2048[c(1, 10, 19, 18)])))
rownames(m_0.4) <- NULL
colnames(m_0.4) <- c("n", 'coverage_rate', 'lb', 'ub')
m_0.4['method'] <- c('nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv')
library(dplyr)
m_0.4[order(-m_0.4$n), ]
```

```{r}
ggplot(m_0.4, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(~ method) +
  labs(title = 'AR = 0.4', x = 'Time Series Length', y = 'Confidence Interval AR(1) Coefficient Recovery Rate') +
  scale_x_continuous(trans='log2') +
  theme(legend.position="none")
```

```{r}
ar_0.4 <- data.frame(rbind(t(ar_0.4_32[c(1, 6, 17, 16)]), t(ar_0.4_32[c(1, 10, 19, 18)]), t(ar_0.4_64[c(1, 6, 17, 16)]), t(ar_0.4_64[c(1, 10, 19, 18)]), t(ar_0.4_128[c(1, 6, 17, 16)]), t(ar_0.4_128[c(1, 10, 19, 18)]), t(ar_0.4_256[c(1, 6, 17, 16)]), t(ar_0.4_256[c(1, 10, 19, 18)]), t(ar_0.4_512[c(1, 6, 17, 16)]), t(ar_0.4_512[c(1, 10, 19, 18)]), t(ar_0.4_1024[c(1, 6, 17, 16)]), t(ar_0.4_1024[c(1, 10, 19, 18)]), t(ar_0.4_2048[c(1, 6, 17, 16)]), t(ar_0.4_2048[c(1, 10, 19, 18)])))
rownames(ar_0.4) <- NULL
colnames(ar_0.4) <- c("n", 'coverage_rate', 'lb', 'ub')
ar_0.4['method'] <- c('nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv', 'nm', 'mv')
library(dplyr)
ar_0.4[order(-ar_0.4$n), ]
```
```{r}
ggplot(ar_0.4, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(~ method) +
  labs(title = 'AR = 0.4', x = 'Time Series Length', y = 'Confidence Interval AR(1) Coefficient Recovery Rate') +
  scale_x_continuous(trans='log2') +
  theme(legend.position="none")
```

### 2022-11-17 Manuscript/UpdatedBlockBootstrap.Rmd

@@
 
-do1rep <- function(n, theta, sd, l, statistic) {
-  x <- arima.sim(list(ar = theta), n = n, sd = sqrt((sd^2)*(1-theta^2)))
+do1rep <- function(n, theta, sigma,
+                   target,
+                   len, statistic, B = 1000) {
+  x <- arima.sim(list(ar = theta), n = n, sd = sigma * sqrt(1-theta^2))
+  ## sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)
+  bt <- blkboot(x, statistic, B, len)
 
-  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)
+  ## two intervals  
+  nm = quantile(bt$nm.stat, probs = c(0.025, 0.975))
+  mv = quantile(bt$mv.stat, probs = c(0.025, 0.975))
 
-  bt <- blkboot(x, statistic, 1000, l)
+  nm.cov <- nm[1] < target && target < nm[2]
+  mv.cov <- mv[1] < target && target < mv[2]
 
- # nm_lower_bound with quantile function
+  ## c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)
 
-  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
-  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))
-
-  nm_contains = FALSE
-  value = 0
-  if (identical(statistic, ar1))
-  {
-    value = theta
-  }
-  if (nm_interval[1] < value && nm_interval[2] > value)
-  {
-    nm_contains = TRUE
-  }
-  mv_contains = FALSE
-  if (mv_interval[1] < value && mv_interval[2] > value)
-  {
-    mv_contains = TRUE
+  ## returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
+  c(nm.cov, mv.cov)
 }
 
-  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)
-
-    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
-
-}
-
-do1rep2 <- function(n, theta, sd, l, statistic) {
-  x <- rnorm(n = n, sd = sd)
-
-  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)
-
-  bt <- blkboot(x, statistic, 1000, l)
-
- # nm_lower_bound with quantile function
-
-  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
-  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))
-
-  nm_contains = FALSE
-  value = 0
-  if (identical(statistic, ar1))
-  {
-    value = theta
-  }
-
-  if (nm_interval[1] < value && nm_interval[2] > value)
-  {
-    nm_contains = TRUE
-  }
-  mv_contains = FALSE
-  if (mv_interval[1] < value && mv_interval[2] > value)
-  {
-    mv_contains = TRUE
-  }
-
-  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)
-
-    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
-
-}
 ```
@@
 #m_norm_1024 <- c(1024, m_norm_1024)
+# Save the simulation results to an external file
 ```
@@
 ```{r}
+## put the processing of the results in a separate script
+## load the simulation results
 m_norm <- data.frame(rbind(t(m_norm_32[c(1, 6, 17, 16)]), t(m_norm_32[c(1, 10, 19, 18)]), t(m_norm_64[c(1, 6, 17, 16)]), t(m_norm_64[c(1, 10, 19, 18)]), t(m_norm_128[c(1, 6, 17, 16)]), t(m_norm_128[c(1, 10, 19, 18)]), t(m_norm_256[c(1, 6, 17, 16)]), t(m_norm_256[c(1, 10, 19, 18)]), t(m_norm_512[c(1, 6, 17, 16)]), t(m_norm_512[c(1, 10, 19, 18)]), t(m_norm_1024[c(1, 6, 17, 16)]), t(m_norm_1024[c(1, 10, 19, 18)])))

### 2022-11-23 Code/Block-Bootstrap.Rmd
Code

--- 2022-10-06 Manuscript/Block-Bootstrap.Rmd
@@
   rm = rowMeans(x)
-  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]), rm[5] + qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 1000), rm[5] - qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 1000),  rm[9] + qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 1000), rm[9] - qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 1000))
-}
-
-```
-
-```{r functions, echo = False}
-set.seed(5)
-o = my_summary(replicate(1000, do1rep2(400, 0, 0.1, 20, m1)))
+  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]), rm[5] + qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 4000), rm[5] - qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 4000),  rm[9] + qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 4000), rm[9] - qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 4000))
+}
+
+```
+
+```{r functions, echo = False}
+set.seed(5)
+o = my_summary(replicate(4000, do1rep2(400, 0, 0.1, 20, m1)))
 root_norm_1 <- data.frame(c(400, 20, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, l, m1)))
   root_norm_1 <- cbind(root_norm_1, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep2(225, 0, 0.1, 15, m1)))
+o = my_summary(replicate(4000, do1rep2(225, 0, 0.1, 15, m1)))
 root_norm_2 <- data.frame(c(225, 15, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, l, m1)))
   root_norm_2 <- cbind(root_norm_2, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep2(100, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep2(100, 0, 0.1, 10, m1)))
 root_norm_3 <- data.frame(c(100, 10, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, l, m1)))
   root_norm_3 <- cbind(root_norm_3, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(400, 0, 0.1, 20, m1)))
+o = my_summary(replicate(4000, do1rep(400, 0, 0.1, 20, m1)))
 root_0_1 <- data.frame(c(400, 20, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, l, m1)))
   root_0_1 <- cbind(root_0_1, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(225, 0, 0.1, 15, m1)))
+o = my_summary(replicate(4000, do1rep(225, 0, 0.1, 15, m1)))
 root_0_2 <- data.frame(c(225, 15, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, l, m1)))
   root_0_2 <- cbind(root_0_2, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(100, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(100, 0, 0.1, 10, m1)))
 root_0_3 <- data.frame(c(100, 10, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, l, m1)))
   root_0_3 <- cbind(root_0_3, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 20, m1)))
+o = my_summary(replicate(4000, do1rep(400, 0.2, 0.1, 20, m1)))
 root_0.2_1 <- data.frame(c(400, 20, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, l, m1)))
   root_0.2_1 <- cbind(root_0.2_1, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(225, 0.2, 0.1, 15, m1)))
+o = my_summary(replicate(4000, do1rep(225, 0.2, 0.1, 15, m1)))
 root_0.2_2 <- data.frame(c(225, 15, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, l, m1)))
   root_0.2_2 <- cbind(root_0.2_2, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(100, 0.2, 0.1, 10, m1)))
 root_0.2_3 <- data.frame(c(100, 10, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, l, m1)))
   root_0.2_3 <- cbind(root_0.2_3, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(625, 0.4, 0.1, 25, m1)))
+o = my_summary(replicate(4000, do1rep(625, 0.4, 0.1, 25, m1)))
 root_0.4_1 <- data.frame(c(625, 25, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, l, m1)))
   root_0.4_1 <- cbind(root_0.4_1, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 20, m1)))
+o = my_summary(replicate(4000, do1rep(400, 0.4, 0.1, 20, m1)))
 root_0.4_2 <- data.frame(c(400, 20, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, l, m1)))
   root_0.4_2 <- cbind(root_0.4_2, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(225, 0.4, 0.1, 15, m1)))
+o = my_summary(replicate(4000, do1rep(225, 0.4, 0.1, 15, m1)))
 root_0.4_3 <- data.frame(c(225, 15, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, l, m1)))
   root_0.4_3 <- cbind(root_0.4_3, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(100, 0.4, 0.1, 10, m1)))
 root_0.4_4 <- data.frame(c(100, 10, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, l, m1)))
   root_0.4_4 <- cbind(root_0.4_4, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 30, m1)))
+o = my_summary(replicate(4000, do1rep(900, 0.6, 0.1, 30, m1)))
 root_0.6_1 <- data.frame(c(900, 30, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, l, m1)))
   root_0.6_1 <- cbind(root_0.6_1, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(625, 0.6, 0.1, 25, m1)))
+o = my_summary(replicate(4000, do1rep(625, 0.6, 0.1, 25, m1)))
 root_0.6_2 <- data.frame(c(625, 25, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, l, m1)))
   root_0.6_2 <- cbind(root_0.6_2, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(400, 0.6, 0.1, 20, m1)))
+o = my_summary(replicate(4000, do1rep(400, 0.6, 0.1, 20, m1)))
 root_0.6_3 <- data.frame(c(400, 20, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, l, m1)))
   root_0.6_3 <- cbind(root_0.6_3, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(225, 0.6, 0.1, 15, m1)))
+o = my_summary(replicate(4000, do1rep(225, 0.6, 0.1, 15, m1)))
 root_0.6_4 <- data.frame(c(225, 15, o))
@@
   n = l^2
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, l, m1)))
   root_0.6_4 <- cbind(root_0.6_4, c(n, l, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep2(400, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep2(400, 0, 0.1, 10, m1)))
 constant_norm_1 <- data.frame(c(400, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, 10, m1)))
   constant_norm_1 <- cbind(constant_norm_1, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep2(300, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep2(300, 0, 0.1, 10, m1)))
 constant_norm_2 <- data.frame(c(300, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, 10, m1)))
   constant_norm_2 <- cbind(constant_norm_2, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep2(200, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep2(200, 0, 0.1, 10, m1)))
 constant_norm_3 <- data.frame(c(200, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, 10, m1)))
   constant_norm_3 <- cbind(constant_norm_3, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep2(100, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep2(100, 0, 0.1, 10, m1)))
 constant_norm_4 <- data.frame(c(100, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, 10, m1)))
   constant_norm_4 <- cbind(constant_norm_4, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(400, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(400, 0, 0.1, 10, m1)))
 constant_0_1 <- data.frame(c(400, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, 10, m1)))
   constant_0_1 <- cbind(constant_0_1, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(300, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(300, 0, 0.1, 10, m1)))
 constant_0_2 <- data.frame(c(300, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, 10, m1)))
   constant_0_2 <- cbind(constant_0_2, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(200, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(200, 0, 0.1, 10, m1)))
 constant_0_3 <- data.frame(c(200, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, 10, m1)))
   constant_0_3 <- cbind(constant_0_3, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(100, 0, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(100, 0, 0.1, 10, m1)))
 constant_0_4 <- data.frame(c(100, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, 10, m1)))
   constant_0_4 <- cbind(constant_0_4, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(400, 0.2, 0.1, 10, m1)))
 constant_0.2_1 <- data.frame(c(400, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, 10, m1)))
   constant_0.2_1 <- cbind(constant_0.2_1, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(300, 0.2, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(300, 0.2, 0.1, 10, m1)))
 constant_0.2_2 <- data.frame(c(300, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, 10, m1)))
   constant_0.2_2 <- cbind(constant_0.2_2, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(200, 0.2, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(200, 0.2, 0.1, 10, m1)))
 constant_0.2_3 <- data.frame(c(200, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, 10, m1)))
   constant_0.2_3 <- cbind(constant_0.2_3, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(100, 0.2, 0.1, 10, m1)))
 constant_0.2_4 <- data.frame(c(100, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, 10, m1)))
   constant_0.2_4 <- cbind(constant_0.2_4, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(600, 0.4, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(600, 0.4, 0.1, 10, m1)))
 constant_0.4_1 <- data.frame(c(600, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
   constant_0.4_1 <- cbind(constant_0.4_1, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(500, 0.4, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(500, 0.4, 0.1, 10, m1)))
 constant_0.4_2 <- data.frame(c(500, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
   constant_0.4_2 <- cbind(constant_0.4_2, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(400, 0.4, 0.1, 10, m1)))
 constant_0.4_3 <- data.frame(c(400, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
   constant_0.4_3 <- cbind(constant_0.4_3, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(300, 0.4, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(300, 0.4, 0.1, 10, m1)))
 constant_0.4_4 <- data.frame(c(300, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
   constant_0.4_4 <- cbind(constant_0.4_4, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(200, 0.4, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(200, 0.4, 0.1, 10, m1)))
 constant_0.4_5 <- data.frame(c(200, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
   constant_0.4_5 <- cbind(constant_0.4_5, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(100, 0.4, 0.1, 10, m1)))
 constant_0.4_6 <- data.frame(c(100, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
   constant_0.4_6 <- cbind(constant_0.4_6, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(900, 0.6, 0.1, 10, m1)))
 constant_0.6_1 <- data.frame(c(900, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
   constant_0.6_1 <- cbind(constant_0.6_1, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(800, 0.6, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(800, 0.6, 0.1, 10, m1)))
 constant_0.6_2 <- data.frame(c(800, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
   constant_0.6_2 <- cbind(constant_0.6_2, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(700, 0.6, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(700, 0.6, 0.1, 10, m1)))
 constant_0.6_3 <- data.frame(c(700, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
   constant_0.6_3 <- cbind(constant_0.6_3, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(600, 0.6, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(600, 0.6, 0.1, 10, m1)))
 constant_0.6_4 <- data.frame(c(600, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
   constant_0.6_4 <- cbind(constant_0.6_4, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(500, 0.6, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(500, 0.6, 0.1, 10, m1)))
 constant_0.6_5 <- data.frame(c(500, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
   constant_0.6_5 <- cbind(constant_0.6_5, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(400, 0.6, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(400, 0.6, 0.1, 10, m1)))
 constant_0.6_6 <- data.frame(c(400, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
   constant_0.6_6 <- cbind(constant_0.6_6, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(300, 0.6, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(300, 0.6, 0.1, 10, m1)))
 constant_0.6_7 <- data.frame(c(300, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
   constant_0.6_7 <- cbind(constant_0.6_7, c(n, 10, t))
@@
 set.seed(5)
-o = my_summary(replicate(1000, do1rep(200, 0.6, 0.1, 10, m1)))
+o = my_summary(replicate(4000, do1rep(200, 0.6, 0.1, 10, m1)))
 constant_0.6_8 <- data.frame(c(200, 10, o))
@@
   n = 20 * m
-  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
+  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
   constant_0.6_8 <- cbind(constant_0.6_8, c(n, 10, t))
@@
 ```
+```{r}
+library(xtable)
+table_root_norm <- root_norm
+table_root_norm$lb <- format(round(table_root_norm$lb, 5), 5)
+table_root_norm$ub <- format(round(table_root_norm$ub, 5), 5)
+table_root_norm$coverage_rate <- format(table_root_norm$coverage_rate, 5)
+table_root_norm$interval <- paste(table_root_norm$coverage_rate, '(', table_root_norm$lb, ',', table_root_norm$ub, ')')
+table_root_norm = subset(table_root_norm, select = -c(coverage_rate, lb, ub) )
+colnames(table_root_norm) <- c("Sample Size, "Block Length", 'Method', 'Coverage Rate')
+table_root_norm <- table_root_norm[order(-table_root_norm$`Time Series Length`), ]
+row.names(table_root_norm) <- NULL
+table_root_norm
+xtable(table_root_norm)
+```
+```{r}
+library(xtable)
+table_root_0.2 <- root_0.2
+table_root_0.2$lb <- format(round(table_root_0.2$lb, 5), 5)
+table_root_0.2$ub <- format(round(table_root_0.2$ub, 5), 5)
+table_root_0.2$coverage_rate <- format(table_root_0.2$coverage_rate, 5)
+table_root_0.2$interval <- paste(table_root_0.2$coverage_rate, '(', table_root_0.2$lb, ',', table_root_0.2$ub, ')')
+table_root_0.2 = subset(table_root_0.2, select = -c(coverage_rate, lb, ub) )
+colnames(table_root_0.2) <- c("Sample Size", "Block Length", 'Method', 'Coverage Rate')
+table_root_0.2 <- table_root_0.2[order(-table_root_0.2$`Time Series Length`), ]
+row.names(table_root_0.2) <- NULL
+table_root_0.2
+xtable(table_root_0.2)
+```
+```{r}
+library(xtable)
+table_root_0.4 <- root_0.4
+table_root_0.4$lb <- format(round(table_root_0.4$lb, 5), 5)
+table_root_0.4$ub <- format(round(table_root_0.4$ub, 5), 5)
+table_root_0.4$ci <- format(table_root_0.4$ci, 5)
+table_root_0.4$interval <- paste(table_root_0.4$ci, '(', table_root_0.4$lb, ',', table_root_0.4$ub, ')')
+table_root_0.4 = subset(table_root_0.4, select = -c(ci, lb, ub) )
+colnames(table_root_0.4) <- c("Sample Size", "Block Length", 'Method', 'Coverage Rate')
+table_root_0.4 <- table_root_0.4[order(-table_root_0.4$`Time Series Length`), ]
+row.names(table_root_0.4) <- NULL
+table_root_0.4
+xtable(table_root_0.4)
+```
+```{r}
+library(xtable)
+table_root_0.6 <- root_0.6
+table_root_0.6$lb <- format(round(table_root_0.6$lb, 5), 5)
+table_root_0.6$ub <- format(round(table_root_0.6$ub, 5), 5)
+table_root_0.6$ci <- format(table_root_0.6$ci, 5)
+table_root_0.6$interval <- paste(table_root_0.6$ci, '(', table_root_0.6$lb, ',', table_root_0.6$ub, ')')
+table_root_0.6 = subset(table_root_0.6, select = -c(ci, lb, ub) )
+colnames(table_root_0.6) <- c("Sample Size", "Block Length", 'Method', 'Coverage Rate')
+table_root_0.6 <- table_root_0.6[order(-table_root_0.6$`Time Series Length`), ]
+row.names(table_root_0.6) <- NULL
+table_root_0.6
+xtable(table_root_0.6)
+```
+```{r}
+library(xtable)
+table_constant_norm <- constant_norm
+table_constant_norm$lb <- format(round(table_constant_norm$lb, 5), 5)
+table_constant_norm$ub <- format(round(table_constant_norm$ub, 5), 5)
+table_constant_norm$ci <- format(table_constant_norm$ci, 5)
+table_constant_norm$interval <- paste(table_constant_norm$ci, '(', table_constant_norm$lb, ',', table_constant_norm$ub, ')')
+table_constant_norm = subset(table_constant_norm, select = -c(ci, lb, ub) )
+colnames(table_constant_norm) <- c("Sample Size", "Block Length", 'Method', 'Coverage Rate')
+table_constant_norm <- table_constant_norm[order(-table_constant_norm$`Sample Size`), ]
+row.names(table_constant_norm) <- NULL
+table_constant_norm
+xtable(table_constant_norm)
+```
+
+```{r}
+library(xtable)
+table_constant_0.2 <- constant_0.2
+table_constant_0.2$lb <- format(round(table_constant_0.2$lb, 5), 5)
+table_constant_0.2$ub <- format(round(table_constant_0.2$ub, 5), 5)
+table_constant_0.2$ci <- format(table_constant_0.2$ci, 5)
+table_constant_0.2$interval <- paste(table_constant_0.2$ci, '(', table_constant_0.2$lb, ',', table_constant_0.2$ub, ')')
+table_constant_0.2 = subset(table_constant_0.2, select = -c(ci, lb, ub) )
+colnames(table_constant_0.2) <- c("Sample Length", "Block Length", 'Method', 'Coverage Rate')
+table_constant_0.2 <- table_constant_0.2[order(-table_constant_0.2$`Sample Length`), ]
+row.names(table_constant_0.2) <- NULL
+table_constant_0.2
+xtable(table_constant_0.2)
+```
+```{r}
+library(xtable)
+table_constant_0.4 <- constant_0.4
+table_constant_0.4$lb <- format(round(table_constant_0.4$lb, 5), 5)
+table_constant_0.4$ub <- format(round(table_constant_0.4$ub, 5), 5)
+table_constant_0.4$ci <- format(table_constant_0.4$ci, 5)
+table_constant_0.4$interval <- paste(table_constant_0.4$ci, '(', table_constant_0.4$lb, ',', table_constant_0.4$ub, ')')
+table_constant_0.4 = subset(table_constant_0.4, select = -c(ci, lb, ub) )
+colnames(table_constant_0.4) <- c("Sample Length", "Block Length", 'Method', 'Coverage Rate')
+table_constant_0.4 <- table_constant_0.4[order(-table_constant_0.4$`Sample Length`), ]
+row.names(table_constant_0.4) <- NULL
+table_constant_0.4
+xtable(table_constant_0.4)
+```
+```{r}
+library(xtable)
+table_constant_0.6 <- constant_0.6
+table_constant_0.6$lb <- format(round(table_constant_0.6$lb, 5), 5)
+table_constant_0.6$ub <- format(round(table_constant_0.6$ub, 5), 5)
+table_constant_0.6$ci <- format(table_constant_0.6$ci, 5)
+table_constant_0.6$interval <- paste(table_constant_0.6$ci, '(', table_constant_0.6$lb, ',', table_constant_0.6$ub, ')')
+table_constant_0.6 = subset(table_constant_0.6, select = -c(ci, lb, ub) )
+colnames(table_constant_0.6) <- c("Sample Length", "Block Length", 'Method', 'Coverage Rate')
+table_constant_0.6 <- table_constant_0.6[order(-table_constant_0.6$`Sample Length`), ]
+row.names(table_constant_0.6) <- NULL
+table_constant_0.6
+xtable(table_constant_0.6)
+```

### 2022-11-23 Code/New-Block-Bootstrap.Rmd
Code

```{r functions, echo = FALSE}
nmblk <- function(n, l) {
  b <- n / l # assuming that is an integer
  idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE) # Sample between 1 and n - l + 1, 
  # separating by l, b times
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points 
  # decided by idx
}

mvblk <- function(n, l) {
  b <- n / l
  idx <- sample(1:(n - l + 1), b, replace = TRUE) # Sample any starting point between 1 and n - 1 + 1
  # they can overlap
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points
  # decided by idx
}

blkboot <- function(tseries, statistic, R, l) {
  n <- length(tseries) 
  ## observed statistic
  stat <- statistic(tseries) #stat stores a certain statistic of tseries using a function
  ## nonmoving block bootstrap
  nm.stat <- replicate(R, statistic(tseries[nmblk(n, l)])) # finds the statistic of nm bootstrap and repeats R times
  ## moving block bootstrap
  mv.stat <- replicate(R, statistic(tseries[mvblk(n, l)])) # finds the statistic of mv bootstrap and repeats R times
  list(stat = stat, nm.stat = nm.stat, mv.stat = mv.stat) # returns list of three values
}

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n = n, sd = sqrt((sd^2)*(1-theta^2)))

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  if (nm_interval[1] < 0 && nm_interval[2] > 0)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < 0 && mv_interval[2] > 0)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

}

do1rep2 <- function(n, theta, sd, l, statistic) {
  x <- rnorm(n = n, sd = sd)

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

  bt <- blkboot(x, statistic, 1000, l)

 # nm_lower_bound with quantile function

  nm_interval = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv_interval = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm_contains = FALSE
  if (nm_interval[1] < 0 && nm_interval[2] > 0)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < 0 && mv_interval[2] > 0)
  {
    mv_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

    # returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)

}
```

```{r more_functions, echo = False}
options(max.print = 1000000)
ar1 <- function(x) cor(x[-1], x[-length(x)])
m1 <- function(x) mean(x)

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]), rm[5] + qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 4000), rm[5] - qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 4000),  rm[9] + qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 4000), rm[9] - qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 4000))
}

```

```{r functions, echo = False}
set.seed(5)
o1 = my_summary(replicate(10, do1rep2(100, 0, 0.1, 10, m1)))
set.seed(5)
o2 = my_summary(replicate(10, do1rep2(100, 0, 0.1, ceiling(sqrt(100)), m1)))
set.seed(5)
o3 = my_summary(replicate(10, do1rep2(100, 0, 0.1, ceiling(100**(1/3)), m1)))
o = c(o1, o2, o3)
test <- data.frame(c(100, 10, ceiling(sqrt(100)), ceiling(100**(1/3)), o))
for(m in 4:1)
{
  n = 20 * m
  l1 = 10
  l2 = ceiling(sqrt(n))
  l3 = ceiling(n**(1/3))
  set.seed(5)
  t1 = my_summary(replicate(10, do1rep2(n, 0, 0.1, l1, m1)))
  set.seed(5)
  t2 = my_summary(replicate(10, do1rep2(n, 0, 0.1, l2, m1)))
  set.seed(5)
  t3 = my_summary(replicate(10, do1rep2(n, 0, 0.1, l3, m1)))
  t = c(t1, t2, t3)
  test <- cbind(test, c(n, l1, l2, l3, t))

}

print(test)
```
```{r}
five_sims <- function(N, f, R, AR) {
  set.seed(5)
  o1 = my_summary(replicate(R, f(N, AR, 0.1, 10, m1)))
  set.seed(5)
  o2 = my_summary(replicate(R, f(N, AR, 0.1, ceiling(sqrt(N)), m1)))
  set.seed(5)
  o3 = my_summary(replicate(R, f(N, AR, 0.1, ceiling(N**(1/3)), m1)))
  o = c(o1, o2, o3)
  test <- data.frame(c(N, 10, ceiling(sqrt(N)), ceiling(N**(1/3)), o))
  for(m in ((N/20) - 1):((N/20) - 4))
  {
    n = 20 * m
    l1 = 10
    l2 = ceiling(sqrt(n))
    l3 = ceiling(n**(1/3))
    set.seed(5)
    t1 = my_summary(replicate(R, f(n, AR, 0.1, l1, m1)))
    set.seed(5)
    t2 = my_summary(replicate(R, f(n, AR, 0.1, l2, m1)))
    set.seed(5)
    t3 = my_summary(replicate(R, f(n, AR, 0.1, l3, m1)))
    t = c(t1, t2, t3)
    test <- cbind(test, c(n, l1, l2, l3, t))

  }
  return(data.frame(test))
}
```

```{r}
print(five_sims(100, do1rep2, 10, 0))
```

```{r Normal, 400 - 320, echo = False}
(norm_1 <- five_sims(400, do1rep2, 4000, 0))
```

```{r Normal, 300 - 220, echo = False}
(norm_2 <- five_sims(300, do1rep2, 4000, 0))
```

```{r Normal, 200 - 120, echo = False}
(norm_3 <- five_sims(200, do1rep2, 4000, 0))
```

```{r Normal, 100 - 20, echo = False}
(norm_4 <- five_sims(100, do1rep2, 4000, 0))
```

```{r AR = 0.2, 400 - 320, echo = False}
(ar_0.2_1 <- five_sims(400, do1rep, 4000, 0.2))
```

```{r AR = 0.2, 300 - 220, echo = False}
(ar_0.2_2 <- five_sims(300, do1rep, 4000, 0.2))
```

```{r AR = 0.2, 200 - 120, echo = False}
(ar_0.2_3 <- five_sims(200, do1rep, 4000, 0.2))
```

```{r AR = 0.2, 100 - 20, echo = False}
(ar_0.2_4 <- five_sims(100, do1rep, 4000, 0.2))
```

```{r AR = 0.4, 600 - 520, echo = False}
(ar_0.4_1 <- five_sims(600, do1rep, 4000, 0.4))
```

```{r AR = 0.4, 500 - 420, echo = False}
(ar_0.4_2 <- five_sims(500, do1rep, 4000, 0.4))
```

```{r AR = 0.4, 400 - 320, echo = False}
(ar_0.4_3 <- five_sims(400, do1rep, 4000, 0.4))
```

```{r AR = 0.4, 300 - 220, echo = False}
(ar_0.4_4 <- five_sims(300, do1rep, 4000, 0.4))
```

```{r AR = 0.4, 200 - 120, echo = False}
(ar_0.4_5 <- five_sims(200, do1rep, 4000, 0.4))
```

```{r AR = 0.4, 100 - 20, echo = False}
(ar_0.4_6 <- five_sims(100, do1rep, 4000, 0.4))
```

```{r AR = 0.6, 900 - 820, echo = False}
(ar_0.6_1 <- five_sims(900, do1rep, 4000, 0.6))
```

```{r AR = 0.6, 800 - 720, echo = False}
(ar_0.6_2 <- five_sims(800, do1rep, 4000, 0.6))
```

```{r AR = 0.6, 700 - 620, echo = False}
(ar_0.6_3 <- five_sims(700, do1rep, 4000, 0.6))
```

```{r AR = 0.6, 600 - 520, echo = False}
(ar_0.6_4 <- five_sims(600, do1rep, 4000, 0.6))
```

```{r AR = 0.6, 500 - 420, echo = False}
(ar_0.6_5 <- five_sims(500, do1rep, 4000, 0.6))
```

```{r AR = 0.6, 400 - 320, echo = False}
(ar_0.6_6 <- five_sims(400, do1rep, 4000, 0.6))
```

```{r AR = 0.6, 300 - 220, echo = False}
(ar_0.6_7 <- five_sims(300, do1rep, 4000, 0.6))
```

```{r AR = 0.6, 200 - 120, echo = False}
(ar_0.6_8 <- five_sims(200, do1rep, 4000, 0.6))
```

```{r AR = 0.6, 100 - 20, echo = False}
(ar_0.6_9 <- five_sims(100, do1rep, 4000, 0.6))
```
```{r}
norm <- data.frame(rbind(t(norm_1[c(1, 2, 9, 20, 19),]), t(norm_1[c(1, 2, 13, 22, 21),]), t(norm_2[c(1, 2, 9, 20, 19),]), t(norm_2[c(1, 2, 13, 22, 21),]), t(norm_3[c(1, 2, 9, 20, 19),]), t(norm_3[c(1, 2, 13, 22, 21),]), t(norm_4[c(1, 2, 9, 20, 19),]), t(norm_4[c(1, 2, 13, 22, 21),]), t(norm_1[c(1, 4, 45, 56, 55),]), t(norm_1[c(1, 4, 49, 58, 57),]), t(norm_2[c(1, 4, 45, 56, 55),]), t(norm_2[c(1, 4, 49, 58, 57),]), t(norm_3[c(1, 4, 45, 56, 55),]), t(norm_3[c(1, 4, 49, 58, 57),]), t(norm_4[c(1, 4, 45, 56, 55),]), t(norm_4[c(1, 4, 49, 58, 57),])))
rownames(norm) <- NULL
colnames(norm) <- c("n", "l", 'coverage_rate', 'lb', 'ub')
norm['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
library(dplyr)
norm <- tibble::rowid_to_column(norm, "index")
norm <- norm %>%
  mutate(l_func = case_when(
    index < 41 ~ "c",
    index > 40 & index < 81 ~ "cbrt",
    index > 80 ~ "cbrt"
    ))
norm[order(-norm$n), ]
```

```{r}
library(ggplot2)
ggplot(norm, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(method ~ l_func, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'), l_func = c(c = 'l = 10', sqrt = 'l = sqrt(n)', cbrt = 'l = n^(1/3)'))) +
  labs(title = 'AR = 0', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
  theme(legend.position="none") +
  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
ggsave('norm.pdf', height = 5)
```
```{r}
ar_0.2 <- data.frame(rbind(t(ar_0.2_1[c(1, 2, 9, 20, 19),]), t(ar_0.2_1[c(1, 2, 13, 22, 21),]), t(ar_0.2_2[c(1, 2, 9, 20, 19),]), t(ar_0.2_2[c(1, 2, 13, 22, 21),]), t(ar_0.2_3[c(1, 2, 9, 20, 19),]), t(ar_0.2_3[c(1, 2, 13, 22, 21),]), t(ar_0.2_4[c(1, 2, 9, 20, 19),]), t(ar_0.2_4[c(1, 2, 13, 22, 21),]), t(ar_0.2_1[c(1, 4, 45, 56, 55),]), t(ar_0.2_1[c(1, 4, 49, 58, 57),]), t(ar_0.2_2[c(1, 4, 45, 56, 55),]), t(ar_0.2_2[c(1, 4, 49, 58, 57),]), t(ar_0.2_3[c(1, 4, 45, 56, 55),]), t(ar_0.2_3[c(1, 4, 49, 58, 57),]), t(ar_0.2_4[c(1, 4, 45, 56, 55),]), t(ar_0.2_4[c(1, 4, 49, 58, 57),])))
rownames(ar_0.2) <- NULL
colnames(ar_0.2) <- c("n", "l", 'coverage_rate', 'lb', 'ub')
ar_0.2['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
library(dplyr)
ar_0.2 <- tibble::rowid_to_column(ar_0.2, "index")
ar_0.2 <- ar_0.2 %>%
  mutate(l_func = case_when(
    index < 41 ~ "c",
    index > 40 & index < 81 ~ "cbrt",
    index > 80 ~ "cbrt"
    ))
ar_0.2[order(-ar_0.2$n), ]
```

```{r}
ggplot(ar_0.2, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=5) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(method ~ l_func, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'), l_func = c(c = 'l = 10', sqrt = 'l = sqrt(n)', cbrt = 'l = n^(1/3)'))) +
  labs(title = 'AR = 0.2', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
  theme(legend.position="none") +
  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
ggsave('ar_0.2.pdf', height = 5)
```

```{r}
ar_0.4 <- data.frame(rbind(t(ar_0.4_1[c(1, 2, 9, 20, 19),]), t(ar_0.4_1[c(1, 2, 13, 22, 21),]), t(ar_0.4_2[c(1, 2, 9, 20, 19),]), t(ar_0.4_2[c(1, 2, 13, 22, 21),]), t(ar_0.4_3[c(1, 2, 9, 20, 19),]), t(ar_0.4_3[c(1, 2, 13, 22, 21),]), t(ar_0.4_4[c(1, 2, 9, 20, 19),]), t(ar_0.4_4[c(1, 2, 13, 22, 21),]), t(ar_0.4_5[c(1, 2, 9, 20, 19),]), t(ar_0.4_5[c(1, 2, 13, 22, 21),]), t(ar_0.4_6[c(1, 2, 9, 20, 19),]), t(ar_0.4_6[c(1, 2, 13, 22, 21),]), t(ar_0.4_1[c(1, 4, 45, 56, 55),]), t(ar_0.4_1[c(1, 4, 49, 58, 57),]), t(ar_0.4_2[c(1, 4, 45, 56, 55),]), t(ar_0.4_2[c(1, 4, 49, 58, 57),]), t(ar_0.4_3[c(1, 4, 45, 56, 55),]), t(ar_0.4_3[c(1, 4, 49, 58, 57),]), t(ar_0.4_4[c(1, 4, 45, 56, 55),]), t(ar_0.4_4[c(1, 4, 49, 58, 57),]), t(ar_0.4_5[c(1, 4, 45, 56, 55),]), t(ar_0.4_5[c(1, 4, 49, 58, 57),]), t(ar_0.4_6[c(1, 4, 45, 56, 55),]), t(ar_0.4_6[c(1, 4, 49, 58, 57),])))
rownames(ar_0.4) <- NULL
colnames(ar_0.4) <- c("n", "l", 'coverage_rate', 'lb', 'ub')
ar_0.4['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
library(dplyr)
ar_0.4 <- tibble::rowid_to_column(ar_0.4, "index")
ar_0.4 <- ar_0.4 %>%
  mutate(l_func = case_when(
    index < 61 ~ "c",
    index > 60 & index < 121  ~ "cbrt",
    index > 120 ~ "cbrt"
    ))
ar_0.4[order(-ar_0.4$n), ]
```

```{r}
ggplot(ar_0.4, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=7.5) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(method ~ l_func, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'), l_func = c(c = 'l = 10', sqrt = 'l = sqrt(n)', cbrt = 'l = n^(1/3)'))) +
  labs(title = 'AR = 0.4', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
  theme(legend.position="none") +
  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
ggsave('ar_0.4.pdf', height = 5)
```
```{r}
ar_0.6 <- data.frame(rbind(t(ar_0.6_1[c(1, 2, 9, 20, 19),]), t(ar_0.6_1[c(1, 2, 13, 22, 21),]), t(ar_0.6_2[c(1, 2, 9, 20, 19),]), t(ar_0.6_2[c(1, 2, 13, 22, 21),]), t(ar_0.6_3[c(1, 2, 9, 20, 19),]), t(ar_0.6_3[c(1, 2, 13, 22, 21),]), t(ar_0.6_4[c(1, 2, 9, 20, 19),]), t(ar_0.6_4[c(1, 2, 13, 22, 21),]), t(ar_0.6_5[c(1, 2, 9, 20, 19),]), t(ar_0.6_5[c(1, 2, 13, 22, 21),]), t(ar_0.6_6[c(1, 2, 9, 20, 19),]), t(ar_0.6_6[c(1, 2, 13, 22, 21),]), t(ar_0.6_7[c(1, 2, 9, 20, 19),]), t(ar_0.6_7[c(1, 2, 13, 22, 21),]), t(ar_0.6_8[c(1, 2, 9, 20, 19),]), t(ar_0.6_8[c(1, 2, 13, 22, 21),]), t(ar_0.6_9[c(1, 2, 9, 20, 19),]), t(ar_0.6_9[c(1, 2, 13, 22, 21),]), t(ar_0.6_1[c(1, 4, 45, 56, 55),]), t(ar_0.6_1[c(1, 4, 49, 58, 57),]), t(ar_0.6_2[c(1, 4, 45, 56, 55),]), t(ar_0.6_2[c(1, 4, 49, 58, 57),]), t(ar_0.6_3[c(1, 4, 45, 56, 55),]), t(ar_0.6_3[c(1, 4, 49, 58, 57),]), t(ar_0.6_4[c(1, 4, 45, 56, 55),]), t(ar_0.6_4[c(1, 4, 49, 58, 57),]), t(ar_0.6_5[c(1, 4, 45, 56, 55),]), t(ar_0.6_5[c(1, 4, 49, 58, 57),]), t(ar_0.6_6[c(1, 4, 45, 56, 55),]), t(ar_0.6_6[c(1, 4, 49, 58, 57),]), t(ar_0.6_7[c(1, 4, 45, 56, 55),]), t(ar_0.6_7[c(1, 4, 49, 58, 57),]), t(ar_0.6_8[c(1, 4, 45, 56, 55),]), t(ar_0.6_8[c(1, 4, 49, 58, 57),]), t(ar_0.6_9[c(1, 4, 45, 56, 55),]), t(ar_0.6_9[c(1, 4, 49, 58, 57),])))
rownames(ar_0.6) <- NULL
colnames(ar_0.6) <- c("n", "l", 'coverage_rate', 'lb', 'ub')
ar_0.6['method'] <- c('nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv', 'nm', 'nm', 'nm', 'nm', 'nm', 'mv', 'mv', 'mv', 'mv', 'mv')
library(dplyr)
ar_0.6 <- tibble::rowid_to_column(ar_0.6, "index")
ar_0.6 <- ar_0.6 %>%
  mutate(l_func = case_when(
    index < 91 ~ "c",
    index > 90 & index < 181  ~ "cbrt",
    index > 180 ~ "cbrt"
    ))
ar_0.6[order(-ar_0.6$n), ]
```

```{r}
ggplot(ar_0.6, aes(x = n, y = coverage_rate, color = method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=lb, ymax=ub), colour="black", width=10) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(method ~ l_func, labeller=labeller(method = c(mv = 'Moving Method', nm = 'Non-Moving Method'), l_func = c(c = 'l = 10', sqrt = 'l = sqrt(n)', cbrt = 'l = n^(1/3)'))) +
  labs(title = 'AR = 0.6', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
  theme(legend.position="none") +
  scale_color_manual(labels = c("Moving Method", "Non-Moving Method"), values = c("blue", "red"))
ggsave('ar_0.6.pdf', height = 5)
```

### 2022-11-23 Code/UpdatedBlockBootstrap.Rmd
Code

```{r}
numeric2 <- function(theta) {
  if (theta == 0) {
    c(numeric(0))
  }
  else {
    c(theta)
  }
}
numeric2(0)
numeric2(0.2)
```

```{r functions, echo = FALSE}
nmblk <- function(n, l) {
  b <- n / l # assuming that is an integer
  idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE) # Sample between 1 and n - l + 1, 
  # separating by l, b times
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points 
  # decided by idx
}

mvblk <- function(n, l) {
  b <- n / l
  idx <- sample(1:(n - l + 1), b, replace = TRUE) # Sample any starting point between 1 and n - 1 + 1
  # they can overlap
  c(outer(0:(l - 1), idx, "+")) # Creates a vector listing random blocks of size l with starting points
  # decided by idx
}

blkboot <- function(tseries, statistic, R, l) {
  n <- length(tseries) 
  ## observed statistic
  stat <- statistic(tseries) #stat stores a certain statistic of tseries using a function
  ## nonmoving block bootstrap
  nm.stat <- replicate(R, statistic(tseries[nmblk(n, l)])) # finds the statistic of nm bootstrap and repeats R times
  ## moving block bootstrap
  mv.stat <- replicate(R, statistic(tseries[mvblk(n, l)])) # finds the statistic of mv bootstrap and repeats R times
  list(stat = stat, nm.stat = nm.stat, mv.stat = mv.stat) # returns list of three values
}

do1rep <- function(n, theta, sigma,
                   target,
                   len, statistic, B = 1000) {
  x <- arima.sim(list(ar = numeric2(theta)), n = n, sd = sigma * sqrt(1-theta^2))
  ## sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)
  bt <- blkboot(x, statistic, B, len)

  ## two intervals  
  nm = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm.cov <- nm[1] < target && target < nm[2]
  mv.cov <- mv[1] < target && target < mv[2]

  ## c(bt$stat, sd(bt$nm.stat), nm_interval, nm_contains, sd(bt$mv.stat), mv_interval, mv_contains)

  ## returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
  c(nm.cov, mv.cov)
}

```

```{r more_functions, echo = False}
options(max.print = 1000000)
#ar1 <- function(x) cor(x[-1], x[-length(x)])
ar1 <- function(x) acf(x, plot = FALSE, lag.max = 1)$acf[2]
m1 <- function(x) mean(x)

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, rm[1] - qnorm(.975) * sqrt((rm[1] * (1 - rm[1])) / 4000), rm[1] + qnorm(.975) * sqrt((rm[1] * (1 - rm[1])) / 4000),  rm[2] - qnorm(.975) * sqrt((rm[2] * (1 - rm[2])) / 4000), rm[2] + qnorm(.975) * sqrt((rm[2] * (1 - rm[2])) / 4000))
}

```

```{r}
asdf <- c(32, my_summary(replicate(200, do1rep(n = 32, theta = 0.2, sigma = 0.1, target = 0, len = ceiling(32**(1/3)), statistic = m1))))
```

```{r}
qwer <- c(64, my_summary(replicate(200, do1rep(n = 64, theta = 0.4, sigma = 0.1, target = 0.4, len = ceiling(64**(1/3)), statistic = ar1))))
```

```{r}
do1rep(n = 64, theta = 0.4, sigma = 0.1, target = 0.4, len = ceiling(64**(1/3)), statistic = ar1)
```

```{r}
zxcv <- data.frame(rbind(asdf, qwer))
colnames(zxcv) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
zxcv
```

```{r Normal Sample n = 32}
set.seed(1)
(m_norm_32 = c(32, my_summary(replicate(4000, do1rep(32, 0, 0.1, 0, ceiling(32**(1/3)), m1)))))
set.seed(1)
(ar_norm_32 = c(32, my_summary(replicate(4000, do1rep(32, 0, 0.1, 0, ceiling(32**(1/3)), ar1)))))
```

```{r Normal Sample n = 64}
set.seed(5)
(m_norm_64 = c(64, my_summary(replicate(4000, do1rep(64, 0, 0.1, 0, ceiling(64**(1/3)), m1)))))
set.seed(5)
(ar_norm_64 = c(64, my_summary(replicate(4000, do1rep(64, 0, 0.1, 0, ceiling(64**(1/3)), ar1)))))
```

```{r Normal Sample n = 128}
set.seed(10)
(m_norm_128 = c(128, my_summary(replicate(4000, do1rep(128, 0, 0.1, 0, ceiling(128**(1/3)), m1)))))
set.seed(10)
(ar_norm_128 = c(128, my_summary(replicate(4000, do1rep(128, 0, 0.1, 0, ceiling(128**(1/3)), ar1)))))
```

```{r Normal Sample n = 256}
set.seed(50)
(m_norm_256 = c(256, my_summary(replicate(4000, do1rep(256, 0, 0.1, 0, ceiling(256**(1/3)), m1)))))
set.seed(50)
(ar_norm_256 = c(256, my_summary(replicate(4000, do1rep(256, 0, 0.1, 0, ceiling(256**(1/3)), ar1)))))
```

```{r Normal Sample n = 512}
set.seed(100)
(m_norm_512 = c(512, my_summary(replicate(4000, do1rep(512, 0, 0.1, 0, ceiling(512**(1/3)), m1)))))
set.seed(100)
(ar_norm_512 = c(512, my_summary(replicate(4000, do1rep(512, 0, 0.1, 0, ceiling(512**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 32}
set.seed(1)
(m_0.2_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.2, 0.1, 0, ceiling(32**(1/3)), m1)))))
set.seed(1)
(ar_0.2_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.2, 0.1, 0.2, ceiling(32**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 64}
set.seed(5)
(m_0.2_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.2, 0.1, 0, ceiling(64**(1/3)), m1)))))
set.seed(5)
(ar_0.2_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.2, 0.1, 0.2, ceiling(64**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 128}
set.seed(10)
(m_0.2_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.2, 0.1, 0, ceiling(128**(1/3)), m1)))))
set.seed(10)
(ar_0.2_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.2, 0.1, 0.2, ceiling(128**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 256}
set.seed(50)
(m_0.2_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.2, 0.1, 0, ceiling(256**(1/3)), m1)))))
set.seed(50)
(ar_0.2_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.2, 0.1, 0.2, ceiling(256**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 512}
set.seed(100)
(m_0.2_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.2, 0.1, 0, ceiling(512**(1/3)), m1)))))
set.seed(100)
(ar_0.2_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.2, 0.1, 0.2, ceiling(512**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 1024}
set.seed(500)
(m_0.2_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.2, 0.1, 0, ceiling(1024**(1/3)), m1)))))
set.seed(500)
(ar_0.2_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.2, 0.1, 0.2, ceiling(1024**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 2048}
set.seed(1000)
(m_0.2_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.2, 0.1, 0, ceiling(2048**(1/3)), m1)))))
set.seed(1000)
(ar_0.2_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.2, 0.1, 0.2, ceiling(2048**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 4096}
set.seed(5000)
(m_0.2_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.2, 0.1, 0, ceiling(4096**(1/3)), m1)))))
set.seed(5000)
(ar_0.2_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.2, 0.1, 0.2, ceiling(4096**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 32}
set.seed(1)
(m_0.4_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.4, 0.1, 0, ceiling(32**(1/3)), m1)))))
set.seed(1)
(ar_0.4_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.4, 0.1, 0.4, ceiling(32**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 64}
set.seed(5)
(m_0.4_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.4, 0.1, 0, ceiling(64**(1/3)), m1)))))
set.seed(5)
(ar_0.4_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.4, 0.1, 0.4, ceiling(64**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 128}
set.seed(10)
(m_0.4_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.4, 0.1, 0, ceiling(128**(1/3)), m1)))))
set.seed(10)
(ar_0.4_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.4, 0.1, 0.4, ceiling(128**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 256}
set.seed(50)
(m_0.4_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.4, 0.1, 0, ceiling(256**(1/3)), m1)))))
set.seed(50)
(ar_0.4_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.4, 0.1, 0.4, ceiling(256**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 512}
set.seed(100)
(m_0.4_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.4, 0.1, 0, ceiling(512**(1/3)), m1)))))
set.seed(100)
(ar_0.4_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.4, 0.1, 0.4, ceiling(512**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 1024}
set.seed(500)
(m_0.4_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.4, 0.1, 0, ceiling(1024**(1/3)), m1)))))
set.seed(500)
(ar_0.4_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.4, 0.1, 0.4, ceiling(1024**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 2048}
set.seed(1000)
(m_0.4_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.4, 0.1, 0, ceiling(2048**(1/3)), m1)))))
set.seed(1000)
(ar_0.4_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.4, 0.1, 0.4, ceiling(2048**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 4096}
set.seed(5000)
(m_0.4_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.4, 0.1, 0, ceiling(4096**(1/3)), m1)))))
set.seed(5000)
(ar_0.4_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.4, 0.1, 0.4, ceiling(4096**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 8192}
set.seed(10000)
(m_0.4_8192 = c(8192, my_summary(replicate(4000, do1rep(8192, 0.4, 0.1, 0, ceiling(8192**(1/3)), m1)))))
set.seed(10000)
(ar_0.4_8192 = c(8192, my_summary(replicate(4000, do1rep(8192, 0.4, 0.1, 0.4, ceiling(8192**(1/3)), ar1)))))
```

```{r}
m_0 <- data.frame(rbind(m_norm_32, m_norm_64, m_norm_128, m_norm_256, m_norm_512))
ar_0 <- data.frame(rbind(ar_norm_32, ar_norm_64, ar_norm_128, ar_norm_256, ar_norm_512))
m_0.2 <- data.frame(rbind(m_0.2_32, m_0.2_64, m_0.2_128, m_0.2_256, m_0.2_512, m_0.2_1024, m_0.2_2048, m_0.2_4096))
ar_0.2 <- data.frame(rbind(ar_0.2_32, ar_0.2_64, ar_0.2_128, ar_0.2_256, ar_0.2_512, ar_0.2_1024, ar_0.2_2048, ar_0.2_4096))
m_0.4 <- data.frame(rbind(m_0.4_32, m_0.4_64, m_0.4_128, m_0.4_256, m_0.4_512, m_0.4_1024, m_0.4_2048, m_0.4_4096, m_0.4_8192))
ar_0.4 <- data.frame(rbind(ar_0.4_32, ar_0.4_64, ar_0.4_128, ar_0.4_256, ar_0.4_512, ar_0.4_1024, ar_0.4_2048, ar_0.4_4096, ar_0.4_8192))
colnames(m_0) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(ar_0) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(m_0.2) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(ar_0.2) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(m_0.4) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(ar_0.4) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
m_0
ar_0
m_0.2
ar_0.2
m_0.4
ar_0.4
write.csv(m_0,"../Data/m_0.csv", row.names = FALSE)
write.csv(ar_0,"../Data/ar_0.csv", row.names = FALSE)
write.csv(m_0.2,"../Data/m_0.2.csv", row.names = FALSE)
write.csv(ar_0.2,"../Data/ar_0.2.csv", row.names = FALSE)
write.csv(m_0.4,"../Data/m_0.4.csv", row.names = FALSE)
write.csv(ar_0.4,"../Data/ar_0.4.csv", row.names = FALSE)
```

### 2022-11-23 Code/Visualizations.Rmd
Code

---
title: "Visualization"
output: html_document
date: "2022-09-30"
---

```{r}
set.seed(5)
(x <- arima.sim(list(ar = 0.2), n = 50, sd = 1)) 
pdf("orig_ts.pdf", width = 15)
plot.ts(x)
text(x=c(5, 15, 25), y=c(2, 2, 2), labels=c("Block 3, 5", "Block 1", "Block 2, 4"), col="blue")
rect(1, -3, 10, 3, col= rgb(0,0,0,alpha=0.25))
rect(11, -3, 20, 3, col= rgb(0,0,1,alpha=0.25))
rect(21, -3, 30, 3, col= rgb(0,1,0,alpha=0.25))
rect(31, -3, 40, 3, col= rgb(0,1,1,alpha=0))
rect(41, -3, 50, 3, col= rgb(1,0,0,alpha=0))
dev.off()
```

```{r}
set.seed(5)
(y1 <- x[nmblk(50, 10)])
pdf("nm_ts.pdf", width = 15)
plot.ts(y1)
text(x=c(5, 15, 25, 35, 45), y=c(2, 2, 2, 2, 2), labels=c("Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), col="blue")
rect(1, -3, 10, 3, col= rgb(0,0,1,alpha=0.25))
rect(11, -3, 20, 3, col= rgb(0,1,0,alpha=0.25))
rect(21, -3, 30, 3, col= rgb(0,0,0,alpha=0.25))
rect(31, -3, 40, 3, col= rgb(0,1,0,alpha=0.25))
rect(41, -3, 50, 3, col= rgb(0,0,0,alpha=0.25))
dev.off()
```
```{r}
set.seed(5)
(y2 <- x[mvblk(50, 10)])
pdf("mv_ts.pdf", width = 15)
plot.ts(y2)
text(x=c(5, 15, 25, 35, 45), y=c(2, 2, 2, 2, 2), labels=c("Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), col="blue")
rect(1, -3, 10, 3, col= rgb(0,0,0,alpha=0.25))
rect(11, -3, 20, 3, col= rgb(0,0,1,alpha=0.25))
rect(21, -3, 30, 3, col= rgb(0,1,0,alpha=0.25))
rect(31, -3, 40, 3, col= rgb(0,1,1,alpha=0.25))
rect(41, -3, 50, 3, col= rgb(1,0,0,alpha=0.25))
dev.off()
```
```{r}
pdf("orig_ts_2.pdf", width = 15)
plot.ts(x)
rect(2, -3, 11, 3, col= rgb(0,0,0,alpha=0.25))
rect(15, -3, 24, 3, col= rgb(0,0,1,alpha=0.5))
rect(11, -3, 20, 3, col= rgb(0,1,0,alpha=0.25))
rect(41, -3, 50, 3, col= rgb(0,1,1,alpha=0.25))
rect(21, -3, 30, 3, col= rgb(1,0,0,alpha=0.25))
text(x=c(6, 19, 15, 45, 25), y=c(2, -2, 2, 2, 2), labels=c("Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), col="blue")
dev.off()
```
```{r}
set.seed(5)
data <- blkboot(x, m1, 1000, 10)
library(ggplot2)
pdf('nm_dist.pdf')
hist(data$nm.stat, main = 'Distribution of Sample Means from Non-Moving Block Bootstrap', xlab = 'Sample Mean')
dev.off()
pdf('mv_dist.pdf')
hist(data$mv.stat, main = 'Distribution of Sample Means from Moving Block Bootstrap', xlab = 'Sample Mean')
dev.off()
```

### 2022-11-25 Code/UpdatedBlockBootstrap.Rmd
Update to Manuscript

@@
 }
-numeric2(0)
-numeric2(0.2)
+numeric2(0) # Returns numeric (0) when theta is 0
+numeric2(0.2) # Returns theta when theta is not 0, this ensures that the arima simulation runs without a warning
 ```
@@
 
-```
-
-```{r}
-asdf <- c(32, my_summary(replicate(200, do1rep(n = 32, theta = 0.2, sigma = 0.1, target = 0, len = ceiling(32**(1/3)), statistic = m1))))
-```
-
-```{r}
-qwer <- c(64, my_summary(replicate(200, do1rep(n = 64, theta = 0.4, sigma = 0.1, target = 0.4, len = ceiling(64**(1/3)), statistic = ar1))))
-```
-
-```{r}
-do1rep(n = 64, theta = 0.4, sigma = 0.1, target = 0.4, len = ceiling(64**(1/3)), statistic = ar1)
-```
-
-```{r}
-zxcv <- data.frame(rbind(asdf, qwer))
-colnames(zxcv) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
-zxcv
 ```

### 2022-11-25 Manuscript/manuscript.tex
Update to Manuscript

@@
 statistical procedure, for which a large sample size is not always practical, it may be helpful to know at which sample size the method stops working at an acceptable level. 
-The goal of this study is to find a threshold or range of sample sizes at whichblock bootstrap 
-is no longer an effective method for estimating variance.
+The goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
+is no longer an effective method for estimating variance of a parameter.
 
@@
 For this study, many block bootstrap simulations were conducted with RStudio. At the base
-level, we are block-bootstrapping an auto-regressive process with true mean 0.
+level, we are block-bootstrapping an auto-regressive process with true mean 0, and some AR(1) coefficient.
 Bootstrapping is the term for creating new samples of the same size by re-sampling from
-the original sample with replacement. The means of many bootstrapped samples are used to create a
-distribution of sampling means to estimate mean and variance. This works well for samples
+the original sample with replacement. Estimates of two parameters (the mean and the AR(1) coefficient) from many bootstrapped samples are used to create a
+distribution to estimate the parameter and its variance. This works well for samples
 that are do not have a dependence factor. However, for a time series such as an auto-regressive process,
@@
 
-In our experiment, we find the means of a 1000 block-bootstrapped time series, 
-and create a 95 \% confidence interval of the means. We replicate this 1000 times, 
-and record the proportion of confidence intervals that recover the true mean 
+In our experiment, we find the mean and auto-correlation function estimatesof a 1000 block-bootstrapped time series, 
+and create 95\% confidence intervals of these paramters We replicate this 1000 times, 
+and record the proportion of confidence intervals that recover the true known parameter 
 (coverage rate). We are effectively observing how successful the bootstrapping process
-is at estimating the mean and variance. The key variable being observed was n, 
+is at estimating a parameter and its variance. The key variable being observed was n, 
 the length of the time series, or the size of the sample. It is known that as n
@@
 (the coverage rates will decrease). The question is at what range of n values does this
-start to become a problem.
+start to become a problem and what range of n values is necessary to reach a coverage rate of 95\%.
 
@@
 the time series length should decrease. l = n$^{1/3}$ is typically considered the optimal 
-block length according to asymptotic theory.
-\citep{buhlmann1999block} The effect of the block function on the performance block bootstrap method was observed in this study.
-Simulations were conducted using block functions of l = 10 and l = n$^{1/3}$.
+block length according to asymptotic theory. \citep{buhlmann1999block} Simulations were conducted using this optimal function of l = n$^{1/3}$.
 
@@
 n / l samples are taken randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
-An estimator of the parameter is computed from the bootstrapped sample.
+An estimate of the parameter is computed from the bootstrapped sample.
 This procedure can be repeated many times (typically 1000) to create a sampling distribution of the estimator.
-Using this distribution of estimators, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles.
+Using this distribution of estimates, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles.
 
@@
 
-The central objective of the study was to assess at which sample size the block bootstrap method no longer estimates the variance well for an autoregressive process.
+The central objective of the study was to assess what sample size is necessary for the the block bootstrap method to estimate a parameter of an autoregressive process.
 The method will work better as the sample size goes to infinity, but the goal is to see what is the smallest sample size that is acceptable.
-To achieve this, simulations must first be conducted with a larger sample size in order to compare to results with a smaller sample size.
-In the previous section, the procedure for creating a confidence interval using the block bootstrap method is described.
-This process is applied to a simulation of an autoregressive integrated moving average (ARIMA) with standard deviation = 0.1 to create a confidence interval of the mean of the process.
-R has a built in ARIMA simulation which allows you to set the AR coefficient and the standard deviation of the error term.
-Using the equation below, the sigma of the error term can be decided so that the standard deviation of Y is constant (0.1, Variance = 0.01).
+The sample size is acceptable if many 1 - $\alpha$/2 confidence intervals for that sample size recover the parameter at a rate of 1 - $\alpha$/2.
+In the previous section, the procedure for creating a confidence interval of a parameter using the block bootstrap method is described.
+This process is applied to a simulation of an autoregressive integrated moving average (ARIMA) process to create a confidence interval of a certain parameter (could be the mean or the AR(1) coefficient).
+R has a built in ARIMA simulation which allows you to set the mean, AR(1) coefficient, and the standard deviation of the error term.
+Using the equation below, the standard deviation of the error term can be set so that the standard deviation of Y is constant (0.1, Variance = 0.01).
 
@@
 
-For a certain AR coefficient, a block bootstrap 95\% confidence interval is replicated 4000 times at a starting sample size at which block bootstrap is expected to be very effective (a relatively large sample).
-For each individual confidence interval, it can be recorded whether or not the interval includes the true mean (0).
-The coverage rate, or the proportion of intervals that include the mean, can then be recorded.
+For all simulation studies, the mean can be kept at 0, but the AR(1) Coefficient is the main factor that makes block bootstrap less effective, so its impact on the method's performance should be analyzed.
+For a certain variation of the ARIMA process, a block bootstrap 95\% confidence interval for a sample of length 32 is replicated 4000 times.
+For each individual confidence interval, it can be recorded whether or not the interval includes the true parameter.
+The coverage rate, or the proportion of intervals that include the true parameter, can then be recorded.
 If the parameter and its variance are being properly estimated by the block bootstrap, the coverage rate should reflect this by being close to the confidence level of 95\%.
 If this is not the case, the method is not working as well as it should.
-The width of the confidence interval for each replication is dependent on the variance of the means of the bootstrapped samples.
-If the interval is not wide enough to capture the mean at the expected rate of 95\%, it indicates that the variance of the parameter (which will be estimated from the variance of the means of the bootstrapped samples) will be underestimated.
+The width of the confidence interval for each replication is dependent on the variance of the parameter of the time series.
+If the interval is on average not wide enough to capture the parameter at the expected rate of 95\%, it indicates that the variance of the parameter (which will be estimated from the standard error of the parameter estimates from the bootstrapped samples) will be underestimated.
+If the interval is too wide and captures the parameter at a rate above 95\%, it indicates that the variance of the parameter will be overestimated.
 Since the coverage rate is a proportion based on many replication of independent Bernoulli outcomes, a 95\% confidence interval of the coverage rate at that sample size can also be created.
-Once the simulation is done for the starting n, the sample size can gradually be lowered until the coverage rates and their respective confidence intervals indicate that the method no longer functions well.
+We can be 95\% confident that the true expected coverage rate is included in this interval, so if .95 is included in the interval, this indicates that the block bootstrap method is working well.
+Once the simulation is done for this sample size, the process can be run again with a sample twice as big.
+This can be continued until the method is determined to be working acceptably (.95 is included within the confidence interval of the coverage rate).
 
@@
 
-Before each set of 4000 replications of confidence intervals from block bootstrapped sample mean distributions, the random seed was set to 5 so that the randomized results can be 
-reproduced.
+12 variations of simulation studies were analyzed based on factors that might affect the results of the block bootstrap method.
+Simulation studies were conducted for an autoregressive process with AR = 0, an autoregressive process with AR = 0.2, and an autoregressive process with AR = 0.4.
+For each of these AR(1) coefficient values, separate simulation studies were conducted for the mean and AR(1) coefficient.
+For each of these variations, the non-moving block bootstrap method as well as the moving block bootstrap method were applied to estimate the respective parameter.
 
-A simulation of an autoregressive integrated moving average (ARIMA) process was run 
-repeatedly with varying parameters. 
-The mean and standard deviation of the time series was held constant at 0 and 0.1, respectively, whereas 
-the sample length and AR Coefficient
- were varied.
-The AR Coefficients that were observed with were 0.2, 0.4, and 0.6.
-Normally distributed samples, in other words, samples with AR Coefficients of 0, were also experimented with as a control group to compare against.
-The sample lengths
- that were used depended on the AR
- Coefficient, but the lowest sample length observed was always n = 20.
-
- The block bootstrap method has different settings that were varied in this study: 
- non-moving vs moving, and the function for block length - the three functions used were l = 10 and l = f(n) = $\lceil n^{1/3} \rceil$. That means six variations of the block bootstrap method.
-
-For each simulated ARIMA process, the block bootstrap method with each of these six variations was applied to the sample.
-4000 replications were conducted, meaning that 4000 samples of the same size from a process with the same parameters were simulated.
-For each sample, a 95\% confidence interval was created, and for each block bootstrap variation, the proportion of all 4000 intervals (created using that variation) that recovered the true mean (0) was recorded as the coverage
- rate for that specific variation. 95\% confidence intervals for these proportions were also computed.
-
-For each AR coefficient, a starting sample size was decided based on expectations of how the bootstrap method would perform. Then, the sample size was gradually lowered by increments of 20 to see when
-the block bootstrap would begin to consistently return low coverage rates.
-
-For both AR = 0 and AR = 0.2, results for sample sizes ranging from 400 to 20 were observed.
-For AR = 0.4, results for sample sizes ranging from 600 to 20 were observed.
-For AR = 0.6, results for sample sizes ranging from 900 to 20 were observed.
+The goal was to determine what range sample sizes was acceptable for each of these variations of simulation studies.
 

### 2022-11-28 Code/Plots.Rmd
Plots

```{r}
(m_0 <- read.csv('../Data/m_0.csv'))
```
```{r}
(m_0.2 <- read.csv('../Data/m_0.2.csv'))
```
```{r}
(m_0.4 <- read.csv('../Data/m_0.4.csv'))
```
```{r}
(ar_0 <- read.csv('../Data/ar_0.csv'))
```
```{r}
(ar_0.2 <- read.csv('../Data/ar_0.2.csv'))
```
```{r}
(ar_0.4 <- read.csv('../Data/ar_0.4.csv'))
```
```{r}
library(ggplot2)
library(gridExtra)
m_0_nm <- ggplot(m_0, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0, Non-Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") + 
  scale_x_continuous(trans='log2')
m_0_nm
```
```{r}
m_0_m <- ggplot(m_0, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0, Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") + 
  scale_x_continuous(trans='log2')
grid.arrange(m_0_nm, m_0_m, ncol=2)
```
```{r}
ggplot(m_0.2, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0.2, Non-Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
ggplot(m_0.2, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0.2, Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
ggplot(m_0.4, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0.4, Non-Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
ggplot(ar_0, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0, Non-Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
ggplot(ar_0, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0, Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
ggplot(ar_0.2, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0.2, Non-Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
ggplot(ar_0.2, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0.2, Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
ggplot(ar_0.4, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0.4, Non-Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
ggplot(ar_0.4, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  labs(title = 'Theta = 0.4, Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
```
```{r}
(df <- read.csv('../Data/df.csv'))
```
```{r}
library(ggplot2)
ggplot(df[df$Theta == 0, ], aes(x = Sample.Length, y = Coverage.Rate, color = Method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Lower.Bound, ymax=Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(Method ~ Target) +
  labs(title = 'Theta = 0', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
ggsave('../Manuscript/theta_0.pdf', height = 5)
```
```{r}
library(ggplot2)
ggplot(df[df$Theta == 0.2, ], aes(x = Sample.Length, y = Coverage.Rate, color = Method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Lower.Bound, ymax=Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(Method ~ Target) +
  labs(title = 'Theta = 0.2', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
ggsave('../Manuscript/theta_0.2.pdf', height = 5)
```
```{r}
library(ggplot2)
ggplot(df[df$Theta == 0.4, ], aes(x = Sample.Length, y = Coverage.Rate, color = Method)) +
  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
  geom_errorbar(aes(ymin=Lower.Bound, ymax=Upper.Bound), colour="black", width=0.1) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_grid(Method ~ Target) +
  labs(title = 'Theta = 0.4', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
  theme(legend.position="none") +
  scale_x_continuous(trans='log2')
ggsave('../Manuscript/theta_0.4.pdf', height = 5)
```

### 2022-11-28 Code/UpdatedBlockBootstrap.Rmd
Plots

@@
 ```
+
+```{r}
+tf <- function(df, target, theta) {
+  library(reshape2)
+  library(dplyr)
+  d1 <- melt(df[1:3], id.vars = 'Sample.Length', variable.name = 'Method', value.name = 'Coverage.Rate')
+  levels(d1$Method) <- list(Non.Moving  = "Non.Moving.Coverage.Rate", Moving = "Moving.Coverage.Rate")
+  d2 <- melt(df[c(1, 4, 6)], id.vars = 'Sample.Length', variable.name = 'Method', value.name = 'Lower.Bound')
+  levels(d2$Method) <- list(Non.Moving  = "Non.Moving.Lower.Bound", Moving = "Moving.Lower.Bound")
+  d3 <- melt(df[c(1, 5, 7)], id.vars = 'Sample.Length', variable.name = 'Method', value.name= 'Upper.Bound')
+  levels(d3$Method) <- list(Non.Moving  = "Non.Moving.Upper.Bound", Moving = "Moving.Upper.Bound")
+  z <- merge(x=d1,y=d2)
+  z <- merge(x=z,y=d3)
+  z %>%
+    mutate(Target = target) %>%
+    mutate(Theta = theta)
+}
+df <- rbind(tf(m_0, 'Mean', 0), tf(m_0.2, 'Mean', 0.2), tf(m_0.4, 'Mean', 0.4), tf(ar_0, 'Theta', 0), tf(ar_0.2, 'Theta', 0.2), tf(ar_0.4, 'Theta', 0.4))
+write.csv(df,"../Data/df.csv", row.names = FALSE)
+```

### 2022-11-28 Manuscript/manuscript.tex
Plots

@@
 
-The goal was to determine what range sample sizes was acceptable for each of these variations of simulation studies.
+The goal was to determine what range of sample sizes was acceptable for each of these variations of simulation studies.
 
@@
 
-As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was 
-required for effective block bootstrap estimation.
-The tables below for each corresponding block length function and AR Coefficient display information about the length of the sample of the ARIMA process, the block length used in bootstrap, the method (non-moving or moving), and the proportion of 95\% confidence intervals produced by each of 4000 block bootstrap replications that recover the mean, as well as an interval in which we can be 95\% confident that the true coverage rate given an infinite number of replications is contained.
-As shown in the plots, as n decreases, the coverage rate decreases.
-As AR increases, not only is a larger sample size required for effective bootstrap estimation, but the level of noise also increases.
-The best block length function, as shown in previous literature \citep{buhlmann1999block}, is l = n$^{1/3}$, as it yields the most consistently high coverage rates even for samples as small as n = 20.
-l = 10 seems to perform almost as well as l = n$^{1/3}$ for higher sample sizes, but the coverage rates for l = 10 drop down much more for small sample sizes.
-For the larger sample sizes, there does not appear to be a significant difference in results for moving method vs non-moving method.
-However, block bootstrap with moving method appears to perform better for smaller sample sizes than block bootstrap with non-moving method.
+As the AR(1) coefficient increases, it was found unsurprisingly that a large sample size was needed for the block bootstrap method to work.
+When the target for estimation was the mean of the process, moving block bootstrap generally had a similar performance to non-moving block bootstrap.
+However when the target for estimation was the AR(1) coefficient of the process, moving block bootstrap noticeably recovered the parameter at a greater rate than non-moving block bootstrap.
+When the target was the mean and theta was more than 0, the coverage rate was generally much higher than that for when the target was the AR(1) coefficient.
+However when theta was 0, the AR(1) coefficient was recovered at a greater rate than the mean.
 
 \begin{figure}[tbp]
-\caption{The figure below demonstrates how block bootstrap performs at estimating the mean of a normal population.
-As shown in the plots, even for a sample with no time dependency, a very large sample size is needed to even approach a coverage rate of 95\%.
-While for large sample sizes (approximately greater than 300), the performance for l = 10 is comparable to the performance for l = n$^{1/3}$, the performance with l = 10 is much worse than that for l = n$^{1/3}$ when using very small sample sizes (approximately less than 100).
-The moving method seems to have a similar performance to the non-moving method, although it appears to perform slightly better for very low sample sizes regardless of the block length function.}
+\caption{The figure below shows results for block bootstrap estimation when theta is 0.
+When the target was the mean and the moving method was used, the coverage rate confidence interval included .95 when the sample length was 512, indicating that even for a sample with no temporal dependence, a very large sample length of around 500 is necessary to get an accurate estimation of the mean.
+Similarly, when the target was the mean and the non-moving method was used, the coverage rate confidence interval included .95 when the sample length was 512, showing that a sample size of around 500 is necessary for good block bootstrap estimation.
+When the target was the AR(1) coefficient and the moving method was used, the parameter was over-covered - all of the coverage rate confidence interval lower bounds were greater than .95 - for all sample sizes that were observed (32, 64, 128, 256, and 512).
+This indicates that the variance of the parameter is being overestimated.
+When the target was the AR(1) coefficient and the non-moving method was used, the parameter was under-covered when the sample length was 32 and slightly over-covered when the sample length was 256.
+For sample lengths 64, 128, and 512, the non-moving method recovered the parameter well.}
   \centering
-  \includegraphics[width=\textwidth]{norm}
+  \includegraphics[width=\textwidth]{theta_0}
   \caption{}
-  \label{fig:norm}
+  \label{fig:theta_0}
 \end{figure}
@@
 \begin{figure}[tbp]
-\caption{The figure below demonstrates how block bootstrap performs at estimating the mean of a AR = 0.2 process.
-As shown in the plots, even for a sample with relatively low dependency, a very large sample size is needed to even approach a coverage rate of 95\%.
-While for large sample sizes (approximately greater than 200), the performance for l = 10 is comparable to the performance for l = n$^{1/3}$, the performance with l = 10 is much worse than that for l = n$^{1/3}$ when using small sample sizes (approximately less than 100).
-Again, the moving method seems to have a similar performance overall to the non-moving method, but the coverage rates drop off slightly more for non-moving method when using smaller sample sizes.}
+\caption{The figure below shows results for block bootstrap estimation when theta is 0.2.
+When the target was the mean and the moving method was used, the coverage rate confidence interval included .95 when the sample length was 2048 and 4096, indicating that even for a sample with relatively low temporal dependence, a very large sample of around 2000 is necessary to get an accurate estimation of the mean.
+Similarly, when the target was the mean and the non-moving method was used, the coverage rate confidence interval included .95 when the sample length was 2048 and 4096, showing that a sample size of around 2000 is necessary for good block bootstrap estimation.
+When the target was the AR(1) coefficient, for both methods, the parameter was under-covered for sample lengths as large as 4096, although the moving method appeared to perform better for all sample sizes.
+}
   \centering
-  \includegraphics[width=\textwidth]{ar_0.2}
+  \includegraphics[width=\textwidth]{theta_0.2}
   \caption{}
-  \label{fig:ar_0.2}
+  \label{fig:theta_0.2}
 \end{figure}
@@
 \begin{figure}[tbp]
-\caption{The figure below demonstrates how block bootstrap performs at estimating the mean of a AR = 0.4 process.
-As shown in the plots, even for a sample of size 600, the block bootstrap method fails to adequately capture the mean at a rate of \%.
-While for large sample sizes, the performance for l = 10 is comparable to the performance for l = n$^{1/3}$, the performance with l = 10 is much worse than that for l = n$^{1/3}$ when using small sample sizes.
-Again, the moving method seems to have a similar performance overall to the non-moving method, but the coverage rates drop off slightly more for non-moving method when using smaller sample sizes.}
+\caption{The figure below shows results for block bootstrap estimation when theta is 0.4.
+When the target was the mean, for both methods, the coverage rate was under-covered for sample sizes as large as 8192.
+When the target was the AR(1) coefficient, for both methods, the parameter was under-covered for sample lengths as large as 4096, although the moving method appeared to perform better for smaller sample sizes.
+}
   \centering
-  \includegraphics[width=\textwidth]{ar_0.4}
+  \includegraphics[width=\textwidth]{theta_0.4}
   \caption{}
-  \label{fig:ar_0.4}
-\end{figure}
-
-\begin{figure}[tbp]
-\caption{The figure below demonstrates how block bootstrap performs at estimating the mean of a AR = 0.6 process.
-As shown in the plots, even for a sample of size 900, the block bootstrap method fails to adequately capture the mean at a rate of 95\%.
-While for large sample sizes, the performance for l = 10 is comparable to the performance for l = n$^{1/3}$, the performance with l = 10 is much worse than that for l = n$^{1/3}$ when using small sample sizes.
-Again, the moving method seems to have a similar performance overall to the non-moving method, but the coverage rates drop off slightly more for non-moving method when using smaller sample sizes, although the difference is less noticeable than for samples with lesser time dependence.}
-  \centering
-  \includegraphics[width=\textwidth]{ar_0.6}
-  \caption{}
-  \label{fig:ar_0.6}
+  \label{fig:theta_0.4}
 \end{figure}
@@
 This study finds that as the AR coefficient increases, the sample size necessary for effective block bootstrap estimation must be larger.
-When implementing the block bootstrap method using a block length function of l = n$^{1/3}$ results in the highest coverage rates overall (indicating a more accurate estimation of a parameter and its variance), but using l = 10 results in similar performance for large sample sizes.
-It is important to note that a different constant block length will perform differently for different ranges of sample sizes.
-While the moving-method and non-moving method yield similar coverage rates, the non-moving method performs slightly worse when using very small sample sizes.
+When implementing the block bootstrap method to estimate the mean of an autoregressive process, the non-moving method and moving method perform about the same.
+However, when estimating the AR(1) coefficient, the non-moving method performs noticeably worse than the moving method, which still covers the coefficient poorly when theta is greater than 0.
 

### 2022-11-30 Manuscript/manuscript.tex
Update to Manuscript

@@
 
-\title{Time Series Length at Which Block Bootstrapping is Effective for Estimation of Variance}
+\title{Time Series Length at Which Block Bootstrapping is Effective for Estimation of Parameter and Its Variance}
 
@@
 \citet{kunsch1989jackknife}. \citet{radovanov2014comparison} It has been applied to a variety of 
-different fields such 
+different domains such 
 as econometrics \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}. It can be used for 
-situations in which there is temporal dependence, and the goal is the estimation or testing a hypothesis about a parameter. Assuming that the sample is infinitely 
+situations in which there is temporal dependence within a population, and the goal is the estimation or testing a hypothesis about a parameter. Assuming that the sample is infinitely 
 large, the method will work perfectly. However, for a finite sample size, the method will 
@@
 In the context of planning an applied
-statistical procedure, for which a large sample size is not always practical, it may be helpful to know at which sample size the method stops working at an acceptable level. 
+statistical procedure, for which a large sample size is not always practical, it may be helpful to know which sample size is necessary for the method to work at an acceptable level. 
 The goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
-is no longer an effective method for estimating variance of a parameter.
+is an effective method for estimating a parameter and its variance.
+This is true if 1 - $\alpha$/2 \% (for some predetermined $\alpha$) of confidence intervals created from samples of the same size recover the parameter.
 
@@
 may be significantly more accurate than inference from closed-form asymptotic estimates.
-That study focused on the estimation of a parameter within the context of linear regression.
-Still, the block bootstrap percentile confidence intervals under covered even for n = 1024.
-This study aims to find how small the sample size can be for time series (which has a dependence factor which can be compared to that of a linear regression) in order for the coverage rate to be close to the confidence level.
+That study focused on the estimation of a coefficient parameter within the context of linear regression.
+Still, the block bootstrap percentile confidence intervals under-covered the parameter even for n = 1024.
+This study aims to find how small the sample size can be for time series (which has a time dependence factor which can be compared to a coefficient of a linear regression) in order for the coverage rate to be close to the confidence level.
 
@@
 Bootstrapping is the term for creating new samples of the same size by re-sampling from
-the original sample with replacement. Estimates of two parameters (the mean and the AR(1) coefficient) from many bootstrapped samples are used to create a
-distribution to estimate the parameter and its variance. This works well for samples
+the original sample with replacement. Basic bootstrapping works well for samples
 that are do not have a dependence factor. However, for a time series such as an auto-regressive process,
@@
 the series is split into blocks that can overlap (moving block bootstrap) or not(non-moving block bootstrap). These blocks are then re-sampled to create a new
-bootstrapped time series sample.
+bootstrapped time series sample. Point estimates of a parameter from many block bootstrapped samples are used to create a distribution to create an interval estimation of the parameter.
 
-In our experiment, we find the mean and auto-correlation function estimatesof a 1000 block-bootstrapped time series, 
-and create 95\% confidence intervals of these paramters We replicate this 1000 times, 
-and record the proportion of confidence intervals that recover the true known parameter 
-(coverage rate). We are effectively observing how successful the bootstrapping process
-is at estimating a parameter and its variance. The key variable being observed was n, 
+In this experiment, the mean and auto-correlation function (with a maximum lag of 1) of a 1000 block-bootstrapped time series samples are computed, 
+and a 95\% confidence intervals of these parameters is created. This is replicated 4000 times, 
+and the proportion of confidence intervals that recover the true known parameter 
+(coverage rate) is recorded. The goal of this is to observe how successful the bootstrapping process
+is at estimating a parameter and its variance. The key variable being observed was, 
 the length of the time series, or the size of the sample. It is known that as n
 increases, block bootstrapping will become a less accurate method for estimation
-(the coverage rates will decrease). The question is at what range of n values does this
-start to become a problem and what range of n values is necessary to reach a coverage rate of 95\%.
+(the coverage rates will decrease). The question is at what range of sample lengths does this
+start to become a problem and what range of sample lengths is necessary to reach a coverage rate of 95\%.
 
@@
 while still accounting for all these factors, the simulations were repeated for
-various combinations of AR coefficients, block length functions, and non-moving vs moving method. For each of these combinations, coverage rates were recorded for a wide range of sample sizes.
+variations of the AR coefficient, target parameter, and non-moving vs moving method. For each of these combinations, block bootstrap results were recorded for a wide range of sample sizes.
 
@@
 This procedure can be repeated many times (typically 1000) to create a sampling distribution of the estimator.
-Using this distribution of estimates, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles.
+Using this distribution of estimates, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles of sample estimates.
 
@@
 For all simulation studies, the mean can be kept at 0, but the AR(1) Coefficient is the main factor that makes block bootstrap less effective, so its impact on the method's performance should be analyzed.
-For a certain variation of the ARIMA process, a block bootstrap 95\% confidence interval for a sample of length 32 is replicated 4000 times.
+For a certain variation of the ARIMA process, a block bootstrap 95\% confidence interval for a sample of length 32 is replicated 4000 times (each replication of the method is applied to a newly generated ARIMA simulation).
 For each individual confidence interval, it can be recorded whether or not the interval includes the true parameter.
@@
 The goal was to determine what range of sample sizes was acceptable for each of these variations of simulation studies.
+For theta = 0, results for five sample sizes (32, 64, 128, 256, 512) were observed.
+For theta = 0.2, results for eight sample sizes (32,  64, 128, 256, 512, 1024, 2048, 4096) were observed.
+For theta = 0.4, results for nine sample sizes (32, 64, 128, 256, 512, 1024, 2048, 4096, 8192) were observed.
 

### 2022-12-08 Code/Plots.Rmd
Repo Update

@@
+---
+output:
+  pdf_document: default
+  html_document: default
+---
 ```{r}
-(m_0 <- read.csv('../Data/m_0.csv'))
+df <- read.csv('../Data/df.csv')
 ```
 ```{r}
-(m_0.2 <- read.csv('../Data/m_0.2.csv'))
+(df <- read.csv('../Data/summary.df.csv'))
 ```
-```{r}
-(m_0.4 <- read.csv('../Data/m_0.4.csv'))
-```
-```{r}
-(ar_0 <- read.csv('../Data/ar_0.csv'))
-```
-```{r}
-(ar_0.2 <- read.csv('../Data/ar_0.2.csv'))
-```
-```{r}
-(ar_0.4 <- read.csv('../Data/ar_0.4.csv'))
-```
+
 ```{r}
 library(ggplot2)
-library(gridExtra)
-m_0_nm <- ggplot(m_0, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
+ggplot(df[df$theta == 0, ], aes(x = n, y = cov, color = method)) +
   geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
+  geom_errorbar(aes(ymin=lower, ymax=upper), colour="black", width=0.1) +
   geom_line() +
   geom_point(size = 0.5) +
-  labs(title = 'Theta = 0, Non-Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") + 
-  scale_x_continuous(trans='log2')
-m_0_nm
-```
-```{r}
-m_0_m <- ggplot(m_0, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0, Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") + 
-  scale_x_continuous(trans='log2')
-grid.arrange(m_0_nm, m_0_m, ncol=2)
-```
-```{r}
-ggplot(m_0.2, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0.2, Non-Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-ggplot(m_0.2, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0.2, Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-ggplot(m_0.4, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0.4, Non-Moving Method for Mean', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-ggplot(ar_0, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0, Non-Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-ggplot(ar_0, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0, Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-ggplot(ar_0.2, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0.2, Non-Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-ggplot(ar_0.2, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0.2, Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-ggplot(ar_0.4, aes(x = Sample.Length, y = Non.Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Non.Moving.Lower.Bound, ymax=Non.Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0.4, Non-Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-ggplot(ar_0.4, aes(x = Sample.Length, y = Moving.Coverage.Rate)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Moving.Lower.Bound, ymax=Moving.Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  labs(title = 'Theta = 0.4, Moving Method for AR(1) Coefficient', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate') +
-  theme(legend.position="none") +
-  scale_x_continuous(trans='log2')
-```
-```{r}
-(df <- read.csv('../Data/df.csv'))
-```
-```{r}
-library(ggplot2)
-ggplot(df[df$Theta == 0, ], aes(x = Sample.Length, y = Coverage.Rate, color = Method)) +
-  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Lower.Bound, ymax=Upper.Bound), colour="black", width=0.1) +
-  geom_line() +
-  geom_point(size = 0.5) +
-  facet_grid(Method ~ Target) +
+  facet_grid(method ~ target) +
   labs(title = 'Theta = 0', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
@@
   scale_x_continuous(trans='log2')
-ggsave('../Manuscript/theta_0.pdf', height = 5)
 ```
@@
 library(ggplot2)
-ggplot(df[df$Theta == 0.4, ], aes(x = Sample.Length, y = Coverage.Rate, color = Method)) +
+ggplot(df[df$theta == 0.2, ], aes(x = n, y = cov, color = method)) +
   geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
-  geom_errorbar(aes(ymin=Lower.Bound, ymax=Upper.Bound), colour="black", width=0.1) +
+  geom_errorbar(aes(ymin=lower, ymax=upper), colour="black", width=0.1) +
   geom_line() +
   geom_point(size = 0.5) +
-  facet_grid(Method ~ Target) +
+  facet_grid(method ~ target) +
+  labs(title = 'Theta = 0.2', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
+  theme(legend.position="none") +
+  scale_x_continuous(trans='log2')
+```
+
+```{r}
+library(ggplot2)
+ggplot(df[df$theta == 0.4, ], aes(x = n, y = cov, color = method)) +
+  geom_hline(yintercept = .95, linetype = 'dashed', color = 'orange') + 
+  geom_errorbar(aes(ymin=lower, ymax=upper), colour="black", width=0.1) +
+  geom_line() +
+  geom_point(size = 0.5) +
+  facet_grid(method ~ target) +
   labs(title = 'Theta = 0.4', x = 'Time Series Length', y = 'Confidence Interval Mean Recovery Rate', color = 'Method') +
@@
   scale_x_continuous(trans='log2')
-ggsave('../Manuscript/theta_0.4.pdf', height = 5)
 ```

### 2022-12-08 Code/UpdatedBlockBootstrap.Rmd
Repo Update

--- 2022-11-25 Code/UpdatedBlockBootstrap.Rmd
@@
 
-  ## two intervals  
-  nm = quantile(bt$nm.stat, probs = c(0.025, 0.975))
-  mv = quantile(bt$mv.stat, probs = c(0.025, 0.975))
-
-  nm.cov <- nm[1] < target && target < nm[2]
-  mv.cov <- mv[1] < target && target < mv[2]
+  ## two intervals for each statistic
+  ret <- c()
+  num <- dim(bt$nm.stat)[1]
+  for (s in 1:num) {
+    nm = quantile(bt$nm.stat[s,], probs = c(0.025, 0.975))
+    ret <- append(ret, nm[1] < target[s] && target[s] < nm[2])
+    mv = quantile(bt$mv.stat[s,], probs = c(0.025, 0.975))
+    ret <- append(ret, mv[1] < target[s] && target[s] < mv[2])
+  }
 
@@
   ## returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
-  c(nm.cov, mv.cov)
+  #c(nm.cov, mv.cov)
+  c(ret)
 }
@@
 #ar1 <- function(x) cor(x[-1], x[-length(x)])
-ar1 <- function(x) acf(x, plot = FALSE, lag.max = 1)$acf[2]
+ar1 <- function(x) c(acf(x, plot = FALSE, lag.max = 1)$acf)[2]
 m1 <- function(x) mean(x)
+s1 <- function(x) c(mean(x), acf(x, plot = FALSE, lag.max = 1)$acf[2], var(x))
 
-my_summary <- function(x)
+my_summary <- function(x, alpha = .05)
 {
+  n = dim(x)[2]
+  ret <- c()
   rm = rowMeans(x)
-  c(rm, rm[1] - qnorm(.975) * sqrt((rm[1] * (1 - rm[1])) / 4000), rm[1] + qnorm(.975) * sqrt((rm[1] * (1 - rm[1])) / 4000),  rm[2] - qnorm(.975) * sqrt((rm[2] * (1 - rm[2])) / 4000), rm[2] + qnorm(.975) * sqrt((rm[2] * (1 - rm[2])) / 4000))
+  for (s in rm) {
+    ret = append(ret, c(s, s - qnorm(1 - alpha/2) * sqrt((s * (1 - s)) / n), s + qnorm(1 - alpha/2) * sqrt((s * (1 - s)) / n)))
+  }
+  c(ret)
 }
@@
 
-```{r Normal Sample n = 32}
+```{r Theta = 0, Sigma = 0.1, n = 32}
+my.summary <- data.frame(matrix(ncol = 21, nrow = 0))
+colnames(my.summary) <- c('theta', 'sigma', 'n', 'nm.cov.mu', 'nm.lower.mu', 'nm.upper.mu', 'mv.cov.mu', 'mv.lower.mu', 'mv.upper.mu', 'nm.cov.theta', 'nm.lower.theta', 'nm.upper.theta', 'mv.cov.theta', 'mv.lower.theta', 'mv.upper.theta', 'nm.cov.sigsq', 'nm.lower.sigsq', 'nm.upper.sigsq', 'mv.cov.sigsq', 'mv.lower.sigsq', 'mv.upper.sigsq')
+nrep <- 4000
+statistic <- s1
+mu <- 0
+theta <- 0
+sigma <- 0.1
 set.seed(1)
-(m_norm_32 = c(32, my_summary(replicate(4000, do1rep(32, 0, 0.1, 0, ceiling(32**(1/3)), m1)))))
-set.seed(1)
-(ar_norm_32 = c(32, my_summary(replicate(4000, do1rep(32, 0, 0.1, 0, ceiling(32**(1/3)), ar1)))))
+n <- 32
+d_0_0.1_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_32)))
 ```
 
-```{r Normal Sample n = 64}
+```{r Theta = 0, Sigma = 0.1, n = 64}
 set.seed(5)
-(m_norm_64 = c(64, my_summary(replicate(4000, do1rep(64, 0, 0.1, 0, ceiling(64**(1/3)), m1)))))
-set.seed(5)
-(ar_norm_64 = c(64, my_summary(replicate(4000, do1rep(64, 0, 0.1, 0, ceiling(64**(1/3)), ar1)))))
+n <- 64
+d_0_0.1_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_64)))
 ```
 
-```{r Normal Sample n = 128}
-set.seed(10)
-(m_norm_128 = c(128, my_summary(replicate(4000, do1rep(128, 0, 0.1, 0, ceiling(128**(1/3)), m1)))))
-set.seed(10)
-(ar_norm_128 = c(128, my_summary(replicate(4000, do1rep(128, 0, 0.1, 0, ceiling(128**(1/3)), ar1)))))
+```{r Theta = 0, Sigma = 0.1, n = 128}
+set.seed(25)
+n <- 128
+d_0_0.1_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_128)))
 ```
 
-```{r Normal Sample n = 256}
-set.seed(50)
-(m_norm_256 = c(256, my_summary(replicate(4000, do1rep(256, 0, 0.1, 0, ceiling(256**(1/3)), m1)))))
-set.seed(50)
-(ar_norm_256 = c(256, my_summary(replicate(4000, do1rep(256, 0, 0.1, 0, ceiling(256**(1/3)), ar1)))))
+```{r Theta = 0, Sigma = 0.1, n = 256}
+set.seed(125)
+n <- 256
+d_0_0.1_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_256)))
 ```
 
-```{r Normal Sample n = 512}
-set.seed(100)
-(m_norm_512 = c(512, my_summary(replicate(4000, do1rep(512, 0, 0.1, 0, ceiling(512**(1/3)), m1)))))
-set.seed(100)
-(ar_norm_512 = c(512, my_summary(replicate(4000, do1rep(512, 0, 0.1, 0, ceiling(512**(1/3)), ar1)))))
+```{r Theta = 0, Sigma = 0.1, n = 512}
+set.seed(625)
+n <- 512
+d_0_0.1_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_512)))
 ```
 
-```{r AR = 0.2 Sample n = 32}
-set.seed(1)
-(m_0.2_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.2, 0.1, 0, ceiling(32**(1/3)), m1)))))
-set.seed(1)
-(ar_0.2_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.2, 0.1, 0.2, ceiling(32**(1/3)), ar1)))))
+```{r Theta = 0, Sigma = 0.1, n = 1024}
+set.seed(3125)
+n <- 1024
+d_0_0.1_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_1024)))
 ```
 
-```{r AR = 0.2 Sample n = 64}
-set.seed(5)
-(m_0.2_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.2, 0.1, 0, ceiling(64**(1/3)), m1)))))
-set.seed(5)
-(ar_0.2_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.2, 0.1, 0.2, ceiling(64**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 32}
+theta <- 0.2
+set.seed(3)
+n <- 32
+d_0.2_0.1_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_32)))
 ```
 
-```{r AR = 0.2 Sample n = 128}
-set.seed(10)
-(m_0.2_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.2, 0.1, 0, ceiling(128**(1/3)), m1)))))
-set.seed(10)
-(ar_0.2_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.2, 0.1, 0.2, ceiling(128**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 64}
+set.seed(15)
+n <- 64
+d_0.2_0.1_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_64)))
 ```
 
-```{r AR = 0.2 Sample n = 256}
-set.seed(50)
-(m_0.2_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.2, 0.1, 0, ceiling(256**(1/3)), m1)))))
-set.seed(50)
-(ar_0.2_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.2, 0.1, 0.2, ceiling(256**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 128}
+set.seed(75)
+n <- 128
+d_0.2_0.1_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_128)))
 ```
 
-```{r AR = 0.2 Sample n = 512}
-set.seed(100)
-(m_0.2_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.2, 0.1, 0, ceiling(512**(1/3)), m1)))))
-set.seed(100)
-(ar_0.2_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.2, 0.1, 0.2, ceiling(512**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 256}
+set.seed(375)
+n <- 256
+d_0.2_0.1_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_256)))
 ```
 
-```{r AR = 0.2 Sample n = 1024}
-set.seed(500)
-(m_0.2_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.2, 0.1, 0, ceiling(1024**(1/3)), m1)))))
-set.seed(500)
-(ar_0.2_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.2, 0.1, 0.2, ceiling(1024**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 512}
+set.seed(1875)
+n <- 512
+d_0.2_0.1_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_512)))
 ```
 
-```{r AR = 0.2 Sample n = 2048}
-set.seed(1000)
-(m_0.2_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.2, 0.1, 0, ceiling(2048**(1/3)), m1)))))
-set.seed(1000)
-(ar_0.2_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.2, 0.1, 0.2, ceiling(2048**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 1024}
+set.seed(9375)
+n <- 1024
+d_0.2_0.1_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_1024)))
 ```
 
-```{r AR = 0.2 Sample n = 4096}
-set.seed(5000)
-(m_0.2_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.2, 0.1, 0, ceiling(4096**(1/3)), m1)))))
-set.seed(5000)
-(ar_0.2_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.2, 0.1, 0.2, ceiling(4096**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 2048}
+set.seed(46875)
+n <- 2048
+d_0.2_0.1_2048 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_2048)))
 ```
 
-```{r AR = 0.4 Sample n = 32}
-set.seed(1)
-(m_0.4_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.4, 0.1, 0, ceiling(32**(1/3)), m1)))))
-set.seed(1)
-(ar_0.4_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.4, 0.1, 0.4, ceiling(32**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 4096}
+set.seed(234375)
+n <- 4096
+d_0.2_0.1_4096 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_4096)))
 ```
 
-```{r AR = 0.4 Sample n = 64}
-set.seed(5)
-(m_0.4_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.4, 0.1, 0, ceiling(64**(1/3)), m1)))))
-set.seed(5)
-(ar_0.4_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.4, 0.1, 0.4, ceiling(64**(1/3)), ar1)))))
+```{r Theta = 0.2, Sigma = 0.1, n = 8192}
+set.seed(1171875)
+n <- 8192
+d_0.2_0.1_8192 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_8192)))
 ```
 
-```{r AR = 0.4 Sample n = 128}
-set.seed(10)
-(m_0.4_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.4, 0.1, 0, ceiling(128**(1/3)), m1)))))
-set.seed(10)
-(ar_0.4_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.4, 0.1, 0.4, ceiling(128**(1/3)), ar1)))))
+```{r Theta = 0.4, Sigma = 0.1, n = 32}
+theta <- 0.4
+set.seed(5)
+n <- 32
+d_0.4_0.1_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_32)))
 ```
 
-```{r AR = 0.4 Sample n = 256}
-set.seed(50)
-(m_0.4_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.4, 0.1, 0, ceiling(256**(1/3)), m1)))))
-set.seed(50)
-(ar_0.4_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.4, 0.1, 0.4, ceiling(256**(1/3)), ar1)))))
+```{r Theta = 0.4, Sigma = 0.1, n = 64}
+set.seed(25)
+n <- 64
+d_0.4_0.1_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_64)))
 ```
 
-```{r AR = 0.4 Sample n = 512}
-set.seed(100)
-(m_0.4_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.4, 0.1, 0, ceiling(512**(1/3)), m1)))))
-set.seed(100)
-(ar_0.4_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.4, 0.1, 0.4, ceiling(512**(1/3)), ar1)))))
+```{r Theta = 0.4, Sigma = 0.1, n = 128}
+set.seed(125)
+n <- 128
+d_0.4_0.1_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_128)))
 ```
 
-```{r AR = 0.4 Sample n = 1024}
-set.seed(500)
-(m_0.4_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.4, 0.1, 0, ceiling(1024**(1/3)), m1)))))
-set.seed(500)
-(ar_0.4_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.4, 0.1, 0.4, ceiling(1024**(1/3)), ar1)))))
+```{r Theta = 0.4, Sigma = 0.1, n = 256}
+set.seed(625)
+n <- 256
+d_0.4_0.1_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_256)))
 ```
 
-```{r AR = 0.4 Sample n = 2048}
-set.seed(1000)
-(m_0.4_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.4, 0.1, 0, ceiling(2048**(1/3)), m1)))))
-set.seed(1000)
-(ar_0.4_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.4, 0.1, 0.4, ceiling(2048**(1/3)), ar1)))))
+```{r Theta = 0.4, Sigma = 0.1, n = 512}
+set.seed(3125)
+n <- 512
+d_0.4_0.1_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_512)))
 ```
 
-```{r AR = 0.4 Sample n = 4096}
-set.seed(5000)
-(m_0.4_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.4, 0.1, 0, ceiling(4096**(1/3)), m1)))))
-set.seed(5000)
-(ar_0.4_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.4, 0.1, 0.4, ceiling(4096**(1/3)), ar1)))))
+```{r Theta = 0.4, Sigma = 0.1, n = 1024}
+set.seed(15625)
+n <- 1024
+d_0.4_0.1_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_1024)))
 ```
 
-```{r AR = 0.4 Sample n = 8192}
-set.seed(10000)
-(m_0.4_8192 = c(8192, my_summary(replicate(4000, do1rep(8192, 0.4, 0.1, 0, ceiling(8192**(1/3)), m1)))))
-set.seed(10000)
-(ar_0.4_8192 = c(8192, my_summary(replicate(4000, do1rep(8192, 0.4, 0.1, 0.4, ceiling(8192**(1/3)), ar1)))))
+```{r Theta = 0.4, Sigma = 0.1, n = 2048}
+set.seed(78125)
+n <- 2048
+d_0.4_0.1_2048 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_2048)))
+```
+
+```{r Theta = 0.4, Sigma = 0.1, n = 4096}
+set.seed(390625)
+n <- 4096
+d_0.4_0.1_4096 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_4096)))
+```
+
+```{r Theta = 0.4, Sigma = 0.1, n = 8192}
+set.seed(1953125)
+n <- 8192
+d_0.4_0.1_8192 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_8192)))
+```
+
+```{r Theta = 0.4, Sigma = 0.1, n = 16384}
+set.seed(9765625)
+n <- 16384
+d_0.4_0.1_16384 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_16384)))
+```
+
+```{r Theta = 0, Sigma = 0.5, n = 32}
+theta <- 0
+sigma <- 0.5
+set.seed(1)
+n <- 32
+d_0_0.5_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_32)))
+```
+
+```{r Theta = 0, Sigma = 0.5, n = 64}
+set.seed(5)
+n <- 64
+d_0_0.5_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_64)))
+```
+
+```{r Theta = 0, Sigma = 0.5, n = 128}
+set.seed(25)
+n <- 128
+d_0_0.5_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_128)))
+```
+
+```{r Theta = 0, Sigma = 0.5, n = 256}
+set.seed(125)
+n <- 256
+d_0_0.5_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_256)))
+```
+
+```{r Theta = 0, Sigma = 0.5, n = 512}
+set.seed(625)
+n <- 512
+d_0_0.5_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_512)))
+```
+
+```{r Theta = 0, Sigma = 0.5, n = 1024}
+set.seed(3125)
+n <- 1024
+d_0_0.5_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_1024)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 32}
+theta <- 0.2
+set.seed(3)
+n <- 32
+d_0.2_0.5_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_32)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 64}
+set.seed(15)
+n <- 64
+d_0.2_0.5_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_64)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 128}
+set.seed(75)
+n <- 128
+d_0.2_0.5_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_128)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 256}
+set.seed(375)
+n <- 256
+d_0.2_0.5_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_256)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 512}
+set.seed(1875)
+n <- 512
+d_0.2_0.5_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_512)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 1024}
+set.seed(9375)
+n <- 1024
+d_0.2_0.5_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_1024)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 2048}
+set.seed(46875)
+n <- 2048
+d_0.2_0.5_2048 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_2048)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 4096}
+set.seed(234375)
+n <- 4096
+d_0.2_0.5_4096 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_4096)))
+```
+
+```{r Theta = 0.2, Sigma = 0.5, n = 8192}
+set.seed(1171875)
+n <- 8192
+d_0.2_0.5_8192 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_8192)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 32}
+theta <- 0.4
+set.seed(5)
+n <- 32
+d_0.4_0.5_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_32)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 64}
+set.seed(25)
+n <- 64
+d_0.4_0.5_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_64)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 128}
+set.seed(125)
+n <- 128
+d_0.4_0.5_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_128)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 256}
+set.seed(625)
+n <- 256
+d_0.4_0.5_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_256)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 512}
+set.seed(3125)
+n <- 512
+d_0.4_0.5_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_512)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 1024}
+set.seed(15625)
+n <- 1024
+d_0.4_0.5_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_1024)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 2048}
+set.seed(78125)
+n <- 2048
+d_0.4_0.5_2048 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_2048)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 4096}
+set.seed(390625)
+n <- 4096
+d_0.4_0.5_4096 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_4096)))
+```
+
+```{r Theta = 0.4, Sigma = 0.5, n = 8192}
+set.seed(1953125)
+n <- 8192
+d_0.4_0.5_8192 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
+(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_8192)))
 ```
@@
 ```{r}
-m_0 <- data.frame(rbind(m_norm_32, m_norm_64, m_norm_128, m_norm_256, m_norm_512))
-ar_0 <- data.frame(rbind(ar_norm_32, ar_norm_64, ar_norm_128, ar_norm_256, ar_norm_512))
-m_0.2 <- data.frame(rbind(m_0.2_32, m_0.2_64, m_0.2_128, m_0.2_256, m_0.2_512, m_0.2_1024, m_0.2_2048, m_0.2_4096))
-ar_0.2 <- data.frame(rbind(ar_0.2_32, ar_0.2_64, ar_0.2_128, ar_0.2_256, ar_0.2_512, ar_0.2_1024, ar_0.2_2048, ar_0.2_4096))
-m_0.4 <- data.frame(rbind(m_0.4_32, m_0.4_64, m_0.4_128, m_0.4_256, m_0.4_512, m_0.4_1024, m_0.4_2048, m_0.4_4096, m_0.4_8192))
-ar_0.4 <- data.frame(rbind(ar_0.4_32, ar_0.4_64, ar_0.4_128, ar_0.4_256, ar_0.4_512, ar_0.4_1024, ar_0.4_2048, ar_0.4_4096, ar_0.4_8192))
-colnames(m_0) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
-colnames(ar_0) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
-colnames(m_0.2) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
-colnames(ar_0.2) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
-colnames(m_0.4) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
-colnames(ar_0.4) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
+my.summary
+```
+
+```{r}
+library(tidyr)
+(summary.df <- my.summary %>%
+  pivot_longer(
+    cols = nm.cov.mu:mv.upper.sigsq,
+    names_to = c('method', '.value', 'target'),
+    names_pattern = "(.*)\\.(.*)\\.(.*)"
+  ))
+write.csv(summary.df,"../Data/summary.df.csv", row.names = FALSE)
+```
+
+```{r}
+write.csv(my.summary,"../Data/my.summary.csv", row.names = FALSE)
+```
+
+```{r}
+write.csv(d_0_0.1_32,"../Data/Raw/d_0_0.1_32.csv", row.names = FALSE)
+write.csv(d_0_0.1_64,"../Data/Raw/d_0_0.1_64.csv", row.names = FALSE)
+write.csv(d_0_0.1_128,"../Data/Raw/d_0_0.1_128.csv", row.names = FALSE)
+write.csv(d_0_0.1_256,"../Data/Raw/d_0_0.1_256.csv", row.names = FALSE)
+write.csv(d_0_0.1_512,"../Data/Raw/d_0_0.1_512.csv", row.names = FALSE)
+write.csv(d_0_0.1_1024,"../Data/Raw/d_0_0.1_1024.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_32,"../Data/Raw/d_0.2_0.1_32.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_64,"../Data/Raw/d_0.2_0.1_64.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_128,"../Data/Raw/d_0.2_0.1_128.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_256,"../Data/Raw/d_0.2_0.1_256.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_512,"../Data/Raw/d_0.2_0.1_512.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_1024,"../Data/Raw/d_0.2_0.1_1024.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_2048,"../Data/Raw/d_0.2_0.1_2048.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_4096,"../Data/Raw/d_0.2_0.1_4096.csv", row.names = FALSE)
+write.csv(d_0.2_0.1_8192,"../Data/Raw/d_0.2_0.1_8192.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_32,"../Data/Raw/d_0.4_0.1_32.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_64,"../Data/Raw/d_0.4_0.1_64.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_128,"../Data/Raw/d_0.4_0.1_128.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_256,"../Data/Raw/d_0.4_0.1_256.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_512,"../Data/Raw/d_0.4_0.1_512.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_1024,"../Data/Raw/d_0.4_0.1_1024.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_2048,"../Data/Raw/d_0.4_0.1_2048.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_4096,"../Data/Raw/d_0.4_0.1_4096.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_8192,"../Data/Raw/d_0.4_0.1_8192.csv", row.names = FALSE)
+write.csv(d_0.4_0.1_16384,"../Data/Raw/d_0.4_0.1_16384.csv", row.names = FALSE)
+write.csv(d_0_0.5_32,"../Data/Raw/d_0_0.5_32.csv", row.names = FALSE)
+write.csv(d_0_0.5_64,"../Data/Raw/d_0_0.5_64.csv", row.names = FALSE)
+write.csv(d_0_0.5_128,"../Data/Raw/d_0_0.5_128.csv", row.names = FALSE)
+write.csv(d_0_0.5_256,"../Data/Raw/d_0_0.5_256.csv", row.names = FALSE)
+write.csv(d_0_0.5_512,"../Data/Raw/d_0_0.5_512.csv", row.names = FALSE)
+write.csv(d_0_0.5_1024,"../Data/Raw/d_0_0.5_1024.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_32,"../Data/Raw/d_0.2_0.5_32.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_64,"../Data/Raw/d_0.2_0.5_64.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_128,"../Data/Raw/d_0.2_0.5_128.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_256,"../Data/Raw/d_0.2_0.5_256.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_512,"../Data/Raw/d_0.2_0.5_512.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_1024,"../Data/Raw/d_0.2_0.5_1024.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_2048,"../Data/Raw/d_0.2_0.5_2048.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_4096,"../Data/Raw/d_0.2_0.5_4096.csv", row.names = FALSE)
+write.csv(d_0.2_0.5_8192,"../Data/Raw/d_0.2_0.5_8192.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_32,"../Data/Raw/d_0.4_0.5_32.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_64,"../Data/Raw/d_0.4_0.5_64.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_128,"../Data/Raw/d_0.4_0.5_128.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_256,"../Data/Raw/d_0.4_0.5_256.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_512,"../Data/Raw/d_0.4_0.5_512.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_1024,"../Data/Raw/d_0.4_0.5_1024.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_2048,"../Data/Raw/d_0.4_0.5_2048.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_4096,"../Data/Raw/d_0.4_0.5_4096.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_8192,"../Data/Raw/d_0.4_0.5_8192.csv", row.names = FALSE)
+write.csv(d_0.4_0.5_16384,"../Data/Raw/d_0.4_0.5_16384.csv", row.names = FALSE)
+
+```
+
+```{r}
+tf <- function(df, target, theta) {
+  library(reshape2)
+  library(dplyr)
+  d1 <- melt(df[1:3], id.vars = 'n', variable.name = 'Method', value.name = 'Coverage.Rate')
+  levels(d1$Method) <- list(Non.Moving  = "Non.Moving.Coverage.Rate", Moving = "Moving.Coverage.Rate")
+  d2 <- melt(df[c(1, 4, 6)], id.vars = 'n', variable.name = 'Method', value.name = 'Lower.Bound')
+  levels(d2$Method) <- list(Non.Moving  = "Non.Moving.Lower.Bound", Moving = "Moving.Lower.Bound")
+  d3 <- melt(df[c(1, 5, 7)], id.vars = 'nh', variable.name = 'Method', value.name= 'Upper.Bound')
+  levels(d3$Method) <- list(Non.Moving  = "Non.Moving.Upper.Bound", Moving = "Moving.Upper.Bound")
+  z <- merge(x=d1,y=d2)
+  z <- merge(x=z,y=d3)
+  z %>%
+    mutate(Target = target) %>%
+    mutate(Theta = theta)
+}
+df <- rbind(tf(m_0, 'Mean', 0), tf(m_0.2, 'Mean', 0.2), tf(m_0.4, 'Mean', 0.4), tf(ar_0, 'Theta', 0), tf(ar_0.2, 'Theta', 0.2), tf(ar_0.4, 'Theta', 0.4))
+write.csv(df,"../Data/df.csv", row.names = FALSE)
+```
+
+```{r}
 m_0
-ar_0
-m_0.2
-ar_0.2
-m_0.4
-ar_0.4
-write.csv(m_0,"../Data/m_0.csv", row.names = FALSE)
-write.csv(ar_0,"../Data/ar_0.csv", row.names = FALSE)
-write.csv(m_0.2,"../Data/m_0.2.csv", row.names = FALSE)
-write.csv(ar_0.2,"../Data/ar_0.2.csv", row.names = FALSE)
-write.csv(m_0.4,"../Data/m_0.4.csv", row.names = FALSE)
-write.csv(ar_0.4,"../Data/ar_0.4.csv", row.names = FALSE)
 ```

### 2022-12-08 Manuscript/manuscript.tex
Repo Update

@@
 
-In this experiment, the mean and auto-correlation function (with a maximum lag of 1) of a 1000 block-bootstrapped time series samples are computed, 
+In this experiment, the mean, auto-correlation function (with a maximum lag of 1), and variance of a 1000 block-bootstrapped time series samples are computed, 
 and a 95\% confidence intervals of these parameters is created. This is replicated 4000 times, 
@@
 For all simulation studies, the mean can be kept at 0, but the AR(1) Coefficient is the main factor that makes block bootstrap less effective, so its impact on the method's performance should be analyzed.
-For a certain variation of the ARIMA process, a block bootstrap 95\% confidence interval for a sample of length 32 is replicated 4000 times (each replication of the method is applied to a newly generated ARIMA simulation).
+For a certain variation of the ARIMA process, block bootstrap 95\% confidence intervals for each of 3 parameters (mean, AR(1) Coefficient, and sigma-squared) for a sample of length 32 is replicated 4000 times (each replication of the method is applied to a newly generated ARIMA simulation).
 For each individual confidence interval, it can be recorded whether or not the interval includes the true parameter.
@@
 
-12 variations of simulation studies were analyzed based on factors that might affect the results of the block bootstrap method.
+6 variations of simulation studies were analyzed based on factors that might affect the results of the block bootstrap method.
 Simulation studies were conducted for an autoregressive process with AR = 0, an autoregressive process with AR = 0.2, and an autoregressive process with AR = 0.4.
@@
 As the AR(1) coefficient increases, it was found unsurprisingly that a large sample size was needed for the block bootstrap method to work.
-When the target for estimation was the mean of the process, moving block bootstrap generally had a similar performance to non-moving block bootstrap.
+When the target for estimation was the mean or the variance of the process, moving block bootstrap generally had a similar performance to non-moving block bootstrap.
 However when the target for estimation was the AR(1) coefficient of the process, moving block bootstrap noticeably recovered the parameter at a greater rate than non-moving block bootstrap.
-When the target was the mean and theta was more than 0, the coverage rate was generally much higher than that for when the target was the AR(1) coefficient.
-However when theta was 0, the AR(1) coefficient was recovered at a greater rate than the mean.
+When the target was the mean or the variance and theta was more than 0, the coverage rate was generally much higher than that for when the target was the AR(1) coefficient.
+However when theta was 0, the AR(1) coefficient was recovered at a greater rate than the mean or variance .
 
@@
 This study finds that as the AR coefficient increases, the sample size necessary for effective block bootstrap estimation must be larger.
-When implementing the block bootstrap method to estimate the mean of an autoregressive process, the non-moving method and moving method perform about the same.
+When implementing the block bootstrap method to estimate the mean or variance of an autoregressive process, the non-moving method and moving method perform about the same.
 However, when estimating the AR(1) coefficient, the non-moving method performs noticeably worse than the moving method, which still covers the coefficient poorly when theta is greater than 0.
+Whereas the performance improves as sample length increases when the target is the mean or variance, the performance decays as sample length increases when the target is the AR(1) coefficient.
 

### 2022-12-22 Code/demo2.Rmd
Demo with Empirical Bootstrap

```{r}
mystat <- function(x) {
    c(mean(x),
      sd(x),
      cor(x[-1], x[-length(x)]))
      # acf(x, lag.max = 1, plot = FALSE)$acf[2])
}

x <- arima.sim(list(ma = .3), n = 1000) / sqrt(1 + .3^2)
mystat(x)
```

```{r}
do1rep <- function(n, theta, statistic, blksize, R = 1000) {
    x <- arima.sim(list(ma = theta), n = n) / sqrt(1 + theta^2)
    bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
    ## returns a vector with length twice of that of mystat's returned values
    ## each pair forms an interval for one target
    delta <- sweep(asdf$t, 2, mystat(x)) 
    # Subtract vector from each row of mystat(x) delta = pseudosample mean - original sample mean
    percentile <- apply(bts$t, 2, quantile, prob = c(.025, .975))
    empirical <- rep(mystat(x), each = 2) - apply(delta, 2, quantile, prob = c(.975, .025))
    # Subtract 97.5 percentile delta from statistic for lower bound, and 2.5 percentile delta from statistic for upper bound
    c(percentile, empirical)
}
do1rep(1000, .3, mystat, 10)
```

```{r}
mychk <- function(sim, target) {
    t <- rep(target, 2) # Iterate through statistic twice
    ret <- rep(NA, length(t))
    for (i in seq_along(t)) {
        ii <- (i - 1) * 2
        ret[i] <- mean(sim[ii + 1,] < t[i] & t[i] < sim[ii + 2,])
    }
    c(ret)
}
y <- replicate(5, do1rep(1000, .3, mystat, 10))
mychk(y, target = c(0, 1, .3 / (1 + .3^2)))
```

```{r}
#### simulation
nrep <- 1000
```

```{r}
## n = 1000
n <- 1000
blksize <- 10
theta <- .3
sim_.3_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.3_1k, target = c(0, 1, theta / (1 + theta^2)))
```

```{r}
## n = 8000
n <- 8000
blksize <- 20
theta <- .3
sim_.3_8k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.3_8k, target = c(0, 1, theta / (1 + theta^2)))
```

### 2022-12-30 Code/demo2.Rmd
Changed variable name

@@
     ## each pair forms an interval for one target
-    delta <- sweep(asdf$t, 2, mystat(x)) 
+    delta <- sweep(bts$t, 2, mystat(x)) 
     # Subtract vector from each row of mystat(x) delta = pseudosample mean - original sample mean

### 2023-01-07 Code/simulation.Rmd
New Code

```{r functions}
## This note checks the empirical coverage rate of CIs constructed from
## block bootstrap with series generated from an MA process

mystat <- function(x) {
    c(mean(x),
      sd(x),
      cor(x[-1], x[-length(x)]))
      # acf(x, lag.max = 1, plot = FALSE)$acf[2])
}

do1rep <- function(n, theta, statistic, blksize, R = 1000, level = .95) {
    x <- arima.sim(list(ma = theta), n = n) / sqrt(1 + theta^2)
    bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
    alpha <- 1 - level
    ## returns a vector with length twice of that of mystat's returned values
    ## each pair forms an interval for one target
    pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
    empCI <- matrix(2 * bts$t0, 2, length(bts$t0), byrow = TRUE) - pctCI[c(2, 1),]
    ## BCa interval
    z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
    ## thetajack <- sapply(1:n, function(i) statistic(x[-i]))
    thetajack <- sapply(1: (n / blksize),
                        function(i) statistic(x[ - ((i - 1) * blksize + 1:blksize)]))
    a <- apply(thetajack, 1, e1071::skewness) / 6
    alpha1 <- pnorm(z0 + (z0 + qnorm(alpha/2)) / (1 - a * (z0 + qnorm(alpha/2))))
    alpha2 <- pnorm(z0 + (z0 + qnorm(1 - alpha/2)) / (1 - a * (z0 + qnorm(1 - alpha/2))))
    bcaCI <- sapply(1:length(bts$t0),
                    function(i) quantile(bts$t[,i], prob = c(alpha1[i], alpha2[i])))
    ## return all intervals
    c(pctCI, empCI, bcaCI)
}

mychk <- function(sim, target) {
    p <- nrow(sim) / length(target) / 2
    target <- rep(target, p)
    ret <- rep(NA, length(target))
    for (i in seq_along(ret)) {
        ii <- (i - 1) * 2
        ret[i] <- mean(sim[ii + 1,] < target[i] & target[i] < sim[ii + 2,])
    }
    ret
}
```

```{r simulation}
nrep <- 4000
```

```{r ma = .3, n = 125}
n <- 125
blksize <- 5
theta <- .3
target <- c(0, 1, theta / (1 + theta^2))
set.seed(1234)
sim_.3_125 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.3_125, target)
```

```{r ma = .3, n = 1000}
n <- 1000
blksize <- 10
theta <- .3
target <- c(0, 1, theta / (1 + theta^2))
set.seed(2345)
sim_.3_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.3_1k, target)
```

```{r ma = .3, n = 3375}
n <- 3375
blksize <- 15
theta <- .3
target <- c(0, 1, theta / (1 + theta^2))
set.seed(3456)
sim_.3_3375 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.3_3375, target)
```

```{r ma = .3, n = 8000}
n <- 8000
blksize <- 20
theta <- .3
target <- c(0, 1, theta / (1 + theta^2))
set.seed(4567)
sim_.3_8k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.3_8k, target)
```

### 2023-01-07 Manuscript/manuscript.tex
New Code

@@
 
-\title{Time Series Length at Which Block Bootstrapping is Effective for Estimation of Parameter and Its Variance}
+\title{Sample Length at Which Block Bootstrapping is Effective for Estimation of Parameter of Time Series}
 
@@
 Block bootstrapping is a method that can be used for estimating a parameter of a time
-series. It involves splitting a series into blocks (in order to account for the time
-factor) and re-sampling the blocks to create many new bootstrapped time series.
+series. It involves splitting a series into blocks (in order to account for the temporal dependence
+factor) and re-sampling the blocks to create many new bootstrapped pseudo-samples of the time series.
 This method becomes more effective as the length of the time series increases. 
-The question for this study is how does one determine at what length the block
-bootstrap method stops being effective to estimate a parameter of a time
+The question that this study seeks to answer is what sample length is necessary for the block
+bootstrap method to be effective in estimating a parameter of a time
 series.
@@
 not work as well as expected.
-\citet{hesterberg2015teachers} notes that while intervals based on the percentiles from nonparametric bootstrapping are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
+\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from nonparametric bootstrapping are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
 In the context of planning an applied
-statistical procedure, for which a large sample size is not always practical, it may be helpful to know which sample size is necessary for the method to work at an acceptable level. 
+statistical procedure, for which a large sample size is not always practical, it may be helpful to know how large the sample must be for the method to work at an acceptable level. 
 The goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
-is an effective method for estimating a parameter and its variance.
-This is true if 1 - $\alpha$/2 \% (for some predetermined $\alpha$) of confidence intervals created from samples of the same size recover the parameter.
+is an effective method for estimating a parameter.
+The method is effective if approximately 1 - $\alpha$/2 \% (for some predetermined significance level $\alpha$) of confidence intervals created from samples of the same size recover the parameter.
 
 \citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for estimation using the bootstrap method (simple resampling with no blocks involved).
-However, block bootstrapping is a different situation altogether because the sample is split into blocks.
+However, in this study, the focus is block bootstrapping a temporally dependent sample.This is a different situation altogether, first, because the sample has a dependence factor that must be accounted for, and second because block bootstrapping involves splitting the sample into blocks.
 
@@
 Still, the block bootstrap percentile confidence intervals under-covered the parameter even for n = 1024.
-This study aims to find how small the sample size can be for time series (which has a time dependence factor which can be compared to a coefficient of a linear regression) in order for the coverage rate to be close to the confidence level.
+This study aims to find how small the sample size can be for a time series (which has a time dependence factor comparable to a coefficient of a linear regression) in order for the coverage rate to be close to the confidence level.
 
-For this study, many block bootstrap simulations were conducted with RStudio. At the base
-level, we are block-bootstrapping an auto-regressive process with true mean 0, and some AR(1) coefficient.
-Bootstrapping is the term for creating new samples of the same size by re-sampling from
-the original sample with replacement. Basic bootstrapping works well for samples
-that are do not have a dependence factor. However, for a time series such as an auto-regressive process,
-a different procedure is required to account for the time dependence. In such a case,
-the series is split into blocks that can overlap (moving block bootstrap) or not(non-moving block bootstrap). These blocks are then re-sampled to create a new
-bootstrapped time series sample. Point estimates of a parameter from many block bootstrapped samples are used to create a distribution to create an interval estimation of the parameter.
+For this study, the block bootstrap method was applied to time series simulations in R.
 
-In this experiment, the mean, auto-correlation function (with a maximum lag of 1), and variance of a 1000 block-bootstrapped time series samples are computed, 
-and a 95\% confidence intervals of these parameters is created. This is replicated 4000 times, 
+%At the base level, we are block-bootstrapping an auto-regressive process with true mean 0, and some AR(1) coefficient.
+
+Bootstrapping is the procedure of creating new pseudo-samples of the same size by resampling observations with replacement from
+the original sample. Basic bootstrapping works well for samples
+that are do not have a dependence factor. However, for a time series such as an auto-regressive or moving-average process,
+a different procedure is required to account for the time dependence.
+In such a situation, instead of resampling observations, blocks of the original sample can be resampled (these blocks must be of a certain length by which the sample length is divisible) to create a pseudo-sample.
+Point estimates of a parameter calculated from many block bootstrapped pseudo-samples are then used to create a distribution to create an interval estimation of the parameter.
+
+%In this experiment, the mean, auto-correlation function (with a maximum lag of 1), and variance of a 1000 block-bootstrapped time series samples are computed, and 95\% confidence intervals of these parameters is created.
+
+The various ways which these intervals can be constructed are described in \citet{diciccio1996bootstrap} and \citet{rice2006mathematical}.
+They will be discussed later in a review of the block bootstrap method.
+For the purposes of this study (in which the true parameters are known), in order to establish whether or not the method is effective, the block bootstrapping of a simulated sample can be replicated many times,
 and the proportion of confidence intervals that recover the true known parameter 
-(coverage rate) is recorded. The goal of this is to observe how successful the bootstrapping process
-is at estimating a parameter and its variance. The key variable being observed was, 
-the length of the time series, or the size of the sample. It is known that as n
-increases, block bootstrapping will become a less accurate method for estimation
-(the coverage rates will decrease). The question is at what range of sample lengths does this
-start to become a problem and what range of sample lengths is necessary to reach a coverage rate of 95\%.
+(coverage rate) is recorded. The goal of this is simply to observe how successful the block bootstrapping procedure
+is at estimating a parameter. The key variable being observed was, the sample length (n). It is known that as n
+increases, block bootstrapping should become a more accurate and precise method for estimation
+(the coverage rates will approach the theoretical confidence level and the interval widths will decrease).
+The question is what is the minimum sample length necessary to reach a coverage rate of 1 - $\alpha$/2 \%.
 
-In this experiment, there are certain factors that are expected to affect the coverage
-rates. As the Auto-Regressive (AR) coefficient (the time dependence) of the time series 
-increases,
-we expect the coverage rates of the confidence intervals to decrease.
+In this experiment, there are certain variables that are expected to affect the performance of block bootstrap. As the the time dependence (AR or MA coefficient) of the time series 
+increases, we expect the coverage rates of the confidence intervals to decrease.
 The coverage rates are also affected by the size of the blocks - more specifically,
@@
 the time series length should decrease. l = n$^{1/3}$ is typically considered the optimal 
-block length according to asymptotic theory. \citep{buhlmann1999block} Simulations were conducted using this optimal function of l = n$^{1/3}$.
+block length according to asymptotic theory. \citep{buhlmann1999block} Therefore, simulations in this study were conducted using this optimal function of l = n$^{1/3}$.
 
-In order to solve the question of what n is necessary for effective block bootstrapping,
-while still accounting for all these factors, the simulations were repeated for
-variations of the AR coefficient, target parameter, and non-moving vs moving method. For each of these combinations, block bootstrap results were recorded for a wide range of sample sizes.
+%In order to solve the question of what sample length is necessary for effective block bootstrapping while still accounting for all these factors, the simulations were repeated for different variations of the MA coefficient, target parameter, and non-moving vs moving method.
+
+For each of these variations, results for block bootstrap estimation of mean, MA coefficient, and standard deviation were recorded for a wide range of sample length.
 
@@
 
-Block bootstrapping is a method that can be applied to a time series (or any sample of data for that matter) to estimate a parameter and its variance.
-Suppose that a sample of size n of a time series is given.
-In regular bootstrap procedure, the new sample of the same size as the original would just be created by resampling observations with replacement.
+Block bootstrapping is a method that can be applied to a non-stationary process to estimate a parameter.
+Suppose that a sample of length n of a time series is given.
+In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the with replacement.
 In the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size.
 The block should be of size l large enough to include time dependence, yet small enough to include some variance.
+l should also divide n.
 As n increases, an ideal l should also increase, but the ratio of l to n should decrease.
@@
 A common function that is considered the best by much previous literature is l = n$^{1/3}$.
-However not all n sizes are perfect squares, and l must be a whole number, so the ceiling of this function must be used.
-A bootstrapped sample is created by taking a sample of n / l blocks with replacement to create a new series of size n.
+To make things sample for this study, only perfect cubes were used for the sample length.
+A bootstrapped sample is created by taking a sample of n / l blocks with replacement to create a new pseudo-sample of size n.
 The designer of the study can choose whether the blocks overlap or not.
 If the blocks can never overlap, it is called a non-moving block bootstrap.
-In this case, the original sample is split evenly into n / l blocks, and the same number of blocks is sampled without replacement to create a bootstrapped sample.
+In this case, the original sample is split evenly into n / l blocks, and the same number of blocks are sampled with replacement to create a bootstrapped pseudo-sample.
 If the blocks do overlap, it is called a moving block bootstrap.
 n / l samples are taken randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
-An estimate of the parameter is computed from the bootstrapped sample.
-This procedure can be repeated many times (typically 1000) to create a sampling distribution of the estimator.
-Using this distribution of estimates, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created using the $\alpha$/2 and 1 - $\alpha$/2 percentiles of sample estimates.
+An estimate of the parameter (or parameters) is computed from the bootstrapped sample.
+This procedure can be repeated many times to create a sampling distribution of the estimator.
+In this study, 1000 bootstrapped pseudo-samples were created for each simulation.
+Using this distribution of point estimates, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created.
+The most simplistic method for constructing this interval is the percentile confidence interval.
+For a parameter $\theta$, the percentile confidence interval takes the form: \[ [ ]\].
+Another method for constructing this interval is the empirical confidence interval, which takes the form: \[ [ ]\].
+The last method used in this study is the bias-corrected and accelerated
+(BCA) confidence interval, which takes the form: \[ [ ]\].
 

### 2023-01-08 Code/simulation.Rmd
New Data

@@
 ```
+```{r}
+write.csv(sim_.3_125,"../Data/Raw/sim_.3_125.csv", row.names = FALSE)
+write.csv(sim_.3_1k,"../Data/Raw/sim_.3_1k.csv", row.names = FALSE)
+write.csv(sim_.3_3375,"../Data/Raw/sim_.3_3375.csv", row.names = FALSE)
+write.csv(sim_.3_8k,"../Data/Raw/sim_.3_8k.csv", row.names = FALSE)
+```

### 2023-01-11 Code/simulation.Rmd
Clean Folders

--- 2023-01-07 Code/simulation.Rmd
@@
 
+```{r ma = .1, n = 125}
+n <- 125
+blksize <- 5
+theta <- .1
+target <- c(0, 1, theta / (1 + theta^2))
+set.seed(1234)
+sim_.1_125 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+mychk(sim_.1_125, target)
+```
+
+```{r ma = .1, n = 1000}
+n <- 1000
+blksize <- 10
+theta <- .1
+target <- c(0, 1, theta / (1 + theta^2))
+set.seed(2345)
+sim_.1_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+mychk(sim_.1_1k, target)
+```
+
+```{r ma = .1, n = 3375}
+n <- 3375
+blksize <- 15
+theta <- .1
+target <- c(0, 1, theta / (1 + theta^2))
+set.seed(3456)
+sim_.1_3375 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+mychk(sim_.1_3375, target)
+```
+
 ```{r ma = .3, n = 125}
@@
 ```
+
+```{r ma = .5, n = 3375}
+n <- 3375
+blksize <- 15
+theta <- .5
+target <- c(0, 1, theta / (1 + theta^2))
+set.seed(3456)
+sim_.5_3375 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+mychk(sim_.5_3375, target)
+```
+
+```{r ma = .5, n = 8000}
+n <- 8000
+blksize <- 20
+theta <- .5
+target <- c(0, 1, theta / (1 + theta^2))
+set.seed(4567)
+sim_.5_8k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+mychk(sim_.5_8k, target)
+```
+
+```{r}
+write.csv(sim_.1_125,"../Data/Raw/sim_.1_125.csv", row.names = FALSE)
+write.csv(sim_.1_1k,"../Data/Raw/sim_.1_1k.csv", row.names = FALSE)
+write.csv(sim_.3_125,"../Data/Raw/sim_.3_125.csv", row.names = FALSE)
+write.csv(sim_.3_1k,"../Data/Raw/sim_.3_1k.csv", row.names = FALSE)
+write.csv(sim_.3_3375,"../Data/Raw/sim_.3_3375.csv", row.names = FALSE)
+write.csv(sim_.3_8k,"../Data/Raw/sim_.3_8k.csv", row.names = FALSE)
+```

### 2023-01-11 Code/demo.R
stat centered first as suggested by Xianyang Zheng

@@ -14,7 +14,10 @@ do1rep <- function(n, theta, statistic, blksize, R = 1000, level = .95) {
     alpha <- 1 - level
     ## returns a vector with length twice of that of mystat's returned values
     ## each pair forms an interval for one target
-    pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
+    ## pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
+    mbts <- apply(bts$t, 2, mean)
+    crit <- apply(abs(t(t(bts$t) - mbts)), 2, quantile, prob = level)
+    pctCI <- rbind(bts$t0 - crit, bts$t0 + crit)  
     empCI <- matrix(2 * bts$t0, 2, length(bts$t0), byrow = TRUE) - pctCI[c(2, 1),]
     ## BCa interval
     z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))

### 2023-01-17 Manuscript/manuscript.tex
Clean Manuscript Folder

@@
 n / l samples are taken randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
-An estimate of the parameter (or parameters) is computed from the bootstrapped sample.
-This procedure can be repeated many times to create a sampling distribution of the estimator.
+An estimate of the parameter (or parameters) $\hat{\theta}_{b}$ is computed from the bootstrapped sample.
+This procedure can be repeated many times to create a distribution of $\hat{\theta}_{b}$.
 In this study, 1000 bootstrapped pseudo-samples were created for each simulation.
-Using this distribution of point estimates, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created.
+Using this distribution of $\hat{\theta}_{b}$, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created.
 The most simplistic method for constructing this interval is the percentile confidence interval.
-For a parameter $\theta$, the percentile confidence interval takes the form: \[ [ ]\].
-Another method for constructing this interval is the empirical confidence interval, which takes the form: \[ [ ]\].
-The last method used in this study is the bias-corrected and accelerated
-(BCA) confidence interval, which takes the form: \[ [ ]\].
+For a parameter $\theta$, the percentile confidence interval takes the form: \[ [\hat{\theta}_{b, .025}, \hat{\theta}_{b, .975}].\] Another method is the bias-corrected and accelerated
+(BCA) confidence interval, which takes the form: \[ [\hat{\theta}_{b, \alpha_{L}}, \hat{\theta}_{b, \alpha_{U}}].\] $\alpha{L}$ and $\alpha{U}$ are the cumulative probability of $z{L}$ and $z{U}$, respectively, where:
+\[z_{L} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} + z_{0}\] and
+\[z_{U} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} + z_{0}.\] 
+	Both of these intervals are good at recovering the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as n increases.
+A potential solution to this issue is to center the intervals around either the original sample estimate $\hat{\theta}$ or the mean of all $\hat{\theta}_{b}$.
 
@@
 The method will work better as the sample size goes to infinity, but the goal is to see what is the smallest sample size that is acceptable.
-The sample size is acceptable if many 1 - $\alpha$/2 confidence intervals for that sample size recover the parameter at a rate of 1 - $\alpha$/2.
-In the previous section, the procedure for creating a confidence interval of a parameter using the block bootstrap method is described.
-This process is applied to a simulation of an autoregressive integrated moving average (ARIMA) process to create a confidence interval of a certain parameter (could be the mean or the AR(1) coefficient).
-R has a built in ARIMA simulation which allows you to set the mean, AR(1) coefficient, and the standard deviation of the error term.
-Using the equation below, the standard deviation of the error term can be set so that the standard deviation of Y is constant (0.1, Variance = 0.01).
+The sample size is acceptable if many 1 - $\alpha$/2 confidence intervals for that sample size recover the parameter at a rate of 1 - $\alpha$/2 \%.
+In the previous section, the procedures for creating three types of confidence interval of a parameter using the block bootstrap method are described.
 
-\[ \sigma_{x}^{2}=\sigma_{\eta}^{2}/\left( 1-\phi^2 \right)\]
-\[\sigma_{\eta}=\sqrt{\sigma_{x}^{2}*\left( 1-\phi^2 \right)}\]
+%These procedures are applied to a simulation of an autoregressive integrated moving average (ARIMA) process to create three confidence interval of certain parameters (the mean, the AR(1) coefficient, the MA(1) coefficient, the standard deviation, etc.).
 
-For all simulation studies, the mean can be kept at 0, but the AR(1) Coefficient is the main factor that makes block bootstrap less effective, so its impact on the method's performance should be analyzed.
-For a certain variation of the ARIMA process, block bootstrap 95\% confidence intervals for each of 3 parameters (mean, AR(1) Coefficient, and sigma-squared) for a sample of length 32 is replicated 4000 times (each replication of the method is applied to a newly generated ARIMA simulation).
+R has a built in ARIMA simulation function which allows you to set the mean, AR and MA coefficients, and the standard deviation of the error term $\epsilon$.
+The standard deviation $\sigma_{\epsilon}$ of a AR(1) process with mean 0 can be written as a function of $\sigma_{x}$ and the AR(1) coefficient $\theta$.
+\[X_{t} = \epsilon_{t} + \theta*X_{t-1}\]
+\[Var(X_{t}) = Var(\epsilon_{t} + \theta*X_{t-1})\]
+\[\sigma^2_{x} = \sigma^2_{\epsilon} + \theta^2*\sigma^2_{x}\]
+\[\sigma^2_{x}(1 - \theta^2) = \sigma^2_{\epsilon}\]
+\[\sigma_{\epsilon} = \sigma_{x}\sqrt{1 - \theta^2}\]
+
+For the purposes of this study, $\mu$ should be fixed at 0, and $\sigma_{x}$ at 1.
+By default, $\mu$ is 0 and $\sigma_{\epsilon}$ is 1, so the observations can be multiplied by $\sqrt{1 - \theta^2}$ so that the theoretical $\sigma_{x}$ is equivalent to 1.
+
+For all simulation studies, , but $\mu$ and $\sigma_{x}$ can be kept constant, but increasing temporal dependence factors such as AR and MA Coefficients can make block bootstrap less effective in estimation, so its impact on the method's performance should be analyzed.
+For a certain variation of an AR(1) process, block bootstrap 95\% confidence intervals for each of 3 parameters ($\mu$, $\sigma_{x}$, and the autocorrelation function$\rho$) can be replicated for 1000 simulated samples of a certain length.
 For each individual confidence interval, it can be recorded whether or not the interval includes the true parameter.
 The coverage rate, or the proportion of intervals that include the true parameter, can then be recorded.
-If the parameter and its variance are being properly estimated by the block bootstrap, the coverage rate should reflect this by being close to the confidence level of 95\%.
+If the parameter is being properly estimated by the block bootstrap, the coverage rate should reflect this by being close to the confidence level of 95\%.
 If this is not the case, the method is not working as well as it should.
-The width of the confidence interval for each replication is dependent on the variance of the parameter of the time series.
-If the interval is on average not wide enough to capture the parameter at the expected rate of 95\%, it indicates that the variance of the parameter (which will be estimated from the standard error of the parameter estimates from the bootstrapped samples) will be underestimated.
-If the interval is too wide and captures the parameter at a rate above 95\%, it indicates that the variance of the parameter will be overestimated.
-Since the coverage rate is a proportion based on many replication of independent Bernoulli outcomes, a 95\% confidence interval of the coverage rate at that sample size can also be created.
-We can be 95\% confident that the true expected coverage rate is included in this interval, so if .95 is included in the interval, this indicates that the block bootstrap method is working well.
-Once the simulation is done for this sample size, the process can be run again with a sample twice as big.
-This can be continued until the method is determined to be working acceptably (.95 is included within the confidence interval of the coverage rate).
+The width of the confidence interval for each replication is dependent on the variability of the parameter of the time series.
+If the interval is on average not wide enough to capture the parameter at the expected rate of 95\%, it indicates that the variability of the parameter is underestimated.
+If the interval is too wide and captures the parameter at a rate above 95\%, it indicates that the variability of the parameter is overestimated.
+Since the coverage rate is a proportion based on 1000 independent binary outcomes (the interval recovers the parameter or it doesn't), a 95\% confidence interval of the coverage rate for each parameter can also be created.
+The inclusion of .95 in the interval indicates that the block bootstrap method is working well for its respective parameter.
+If this is not the case for this sample length, the procedure can be conducted again with a larger sample length.
+This can be repeated until the method is determined to be working acceptably, meaning that .95 is included in the 95\% confidence interval of the coverage rate of the parameter.
 
@@
 
-6 variations of simulation studies were analyzed based on factors that might affect the results of the block bootstrap method.
-Simulation studies were conducted for an autoregressive process with AR = 0, an autoregressive process with AR = 0.2, and an autoregressive process with AR = 0.4.
-For each of these AR(1) coefficient values, separate simulation studies were conducted for the mean and AR(1) coefficient.
-For each of these variations, the non-moving block bootstrap method as well as the moving block bootstrap method were applied to estimate the respective parameter.
-
-The goal was to determine what range of sample sizes was acceptable for each of these variations of simulation studies.
-For theta = 0, results for five sample sizes (32, 64, 128, 256, 512) were observed.
-For theta = 0.2, results for eight sample sizes (32,  64, 128, 256, 512, 1024, 2048, 4096) were observed.
-For theta = 0.4, results for nine sample sizes (32, 64, 128, 256, 512, 1024, 2048, 4096, 8192) were observed.
+1000 replicates of length-n random samples of an AR(1) process with theoretical $\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1 were simulated using R.
+For each of three target parameters ($\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1, three types of block bootstrap (with block length l) confidence intervals (percentile, empirical, and BCA) were constructed for each replicate sample.
+The statistic used to estimate $\mu$ is the sample mean $\bar{x}$, the statistic used to estimate $\sigma$ is the sample standard deviation $S^2$, and the statistic used to estimate $\theta$ is the auto-correlation function of the sample.
+For each of these nine categories of confidence intervals, the coverage rate of its respective parameter was computed, along with a 95\% confidence interval of the proportion given 4000 trials.
+For a certain variation of the process, the study was repeated for n = 125, 1000, 3375, and 8000.
+The only parameter of the process that was varied was $\theta$, and 0.1, 0.3, and 0.5 were the values used.
 
@@
 \label{sec:results}
-
-As the AR(1) coefficient increases, it was found unsurprisingly that a large sample size was needed for the block bootstrap method to work.
-When the target for estimation was the mean or the variance of the process, moving block bootstrap generally had a similar performance to non-moving block bootstrap.
-However when the target for estimation was the AR(1) coefficient of the process, moving block bootstrap noticeably recovered the parameter at a greater rate than non-moving block bootstrap.
-When the target was the mean or the variance and theta was more than 0, the coverage rate was generally much higher than that for when the target was the AR(1) coefficient.
-However when theta was 0, the AR(1) coefficient was recovered at a greater rate than the mean or variance .
 

### 2023-01-18 Code/NewPlots.Rmd
Manuscript Change

```{r}
graph_bts <- function(cov, theta, target, width, nrep = 1000, sizes = c(100, 500, 1000), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'theta'), level = .95) {
  n <- rep(sizes, each = length(types) * length(parameters))
  CI <- rep(types, times = length(sizes), each = length(parameters))
  t <- rep(parameters, times = length(sizes) * length(types))
  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
  UB <-sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])

  df <- data.frame(n, CI, t, cov, LB, UB)
  library(ggplot2)
  ggplot(df, aes(x = n, y = cov)) +
    geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
    geom_line() +
    geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
    facet_grid(t ~ CI)
}
```

```{r}
theta <- 0.1
target <- c(0, 1, theta)
cov <- c(mychk(sim_.1_1h, target), mychk(sim_.1_5h, target), mychk(sim_.1_1k, target))

graph_bts(cov, theta, target, width = 50)
ggsave('../Manuscript/plot_.1.pdf')
```
```{r}
theta <- 0.3
target <- c(0, 1, theta)
cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))

graph_bts(cov, theta, target, width = 25)
ggsave('../Manuscript/plot_.3.pdf')
```
```{r}
theta <- 0.5
target <- c(0, 1, theta)
cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))

graph_bts(cov, theta, target, width = 10)
ggsave('../Manuscript/plot_.5.pdf')
```

### 2023-01-18 Code/simulation.Rmd
Manuscript Change

--- 2023-01-07 Code/simulation.Rmd
@@
 ## This note checks the empirical coverage rate of CIs constructed from
-## block bootstrap with series generated from an MA process
+## block bootstrap with series generated from an AR process
 
@@
 do1rep <- function(n, theta, statistic, blksize, R = 1000, level = .95) {
-    x <- arima.sim(list(ma = theta), n = n) / sqrt(1 + theta^2)
+    x <- arima.sim(list(ar = theta), n = n) * sqrt(1 - theta^2)
     bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
     alpha <- 1 - level
-    ## returns a vector with length twice of that of mystat's returned values
-    ## each pair forms an interval for one target
-    pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
-    empCI <- matrix(2 * bts$t0, 2, length(bts$t0), byrow = TRUE) - pctCI[c(2, 1),]
+
+    ## Percentile interval
+    mbts <- apply(bts$t, 2, mean)
+    crit <- 
+      apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
+    ## alpha/2 and 1 - alpha/2 critical values 
+    ## of pseudo-estimate - mean of pseudo-estimates
+    crit2 <- 
+      apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
+    ## alpha/2 and 1 - alpha/2 critical values 
+    ## of pseudo-estimate - original estimate
+
+    ## interval centered around...
+    estCI <- sweep(crit, 2, bts$t0, FUN = '+') # original estimate
+    ## LB: bts$t0 + alpha/2 crit, UB: bts$t0 + (1 - alpha/2) crit
+    mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
+    ## LB: mbts + alpha/2 crit2, UB: mbts + (1 - alpha/2) crit2
+    altCI <- sweep(-crit[order(2:1),], 2, bts$t0, FUN = '+') # both
+    ## LB: bts$t0 - (1 - alpha/2) crit, UB: bts$t0 - alpha/2 crit and
+    ## LB: mbts - (1 - alpha/2) crit2, UB: mbts - alpha/2 crit2
+
     ## BCa interval
     z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
-    ## thetajack <- sapply(1:n, function(i) statistic(x[-i]))
     thetajack <- sapply(1: (n / blksize), 
-                        function(i) statistic(x[ - ((i - 1) * blksize + 1:blksize)]))
+                        function(i) 
+                          statistic(x[ - ((i - 1) * blksize + 1:blksize)]))
     a <- apply(thetajack, 1, e1071::skewness) / 6
-    alpha1 <- pnorm(z0 + (z0 + qnorm(alpha/2)) / (1 - a * (z0 + qnorm(alpha/2))))
-    alpha2 <- pnorm(z0 + (z0 + qnorm(1 - alpha/2)) / (1 - a * (z0 + qnorm(1 - alpha/2))))
-    bcaCI <- sapply(1:length(bts$t0),
-                    function(i) quantile(bts$t[,i], prob = c(alpha1[i], alpha2[i])))
+    alpha1 <- pnorm(
+      z0 + (z0 + qnorm(alpha/2)) / (1 - a * (z0 + qnorm(alpha/2))))
+    alpha2 <- pnorm(
+      z0 + (z0 + qnorm(1 - alpha/2)) / (1 - a * (z0 + qnorm(1 - alpha/2))))
+    crit3 <- sapply(1:length(bts$t0), function(i) 
+      quantile(t(t(bts$t[,i]) - mbts[i]), prob = c(alpha1[i], alpha2[i]))) 
+    ## alpha1 and alpha2 critical values 
+    ## of pseudo-estimate - mean of pseudo-estimates
+    crit4 <- sapply(1:length(bts$t0), function(i) 
+      quantile(t(t(bts$t[,i]) - bts$t0[i]), prob = c(alpha1[i], alpha2[i])))
+    ## alpha1 and alpha2 critical values 
+    ## of pseudo-estimate - original estimate
+
+    ## interval centered around...
+    bcaCIest <- sweep(crit3, 2, bts$t0, FUN = '+') # original estimate
+    ## LB: bts$t0 + alpha1 crit3, UB: bts$t0 + alpha2 crit3
+    bcaCImbt <- sweep(crit4, 2, mbts, FUN = '+') # mean of pseudo-estimates
+    ## LB: mbts + alpha1 crit4, UB: mbts + alpha2 crit4
+    bcaCIalt <- sweep(-crit3[order(2:1),], 2, bts$t0, FUN = '+') # both
+    ## LB: bts$t0 - alpha2 crit3, UB: bts$t0 - alpha1 crit3 and
+    ## LB: mbts - alpha2 crit4, UB: mbts - alpha1 crit4
+
     ## return all intervals
-    c(pctCI, empCI, bcaCI)
+    c(estCI, mbtCI, altCI, bcaCIest, bcaCImbt, bcaCIalt)
 }
@@
 ```{r simulation}
-nrep <- 4000
+nrep <- 1000
 ```
 
-```{r ma = .3, n = 125}
-n <- 125
+```{r ma = .1, n = 100}
+n <- 100
+blksize <- 5
+theta <- .1
+target <- c(0, 1, theta)
+set.seed(1234)
+sim_.1_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.1_1h,"../Data/Raw/sim_.1_1h.csv", row.names = FALSE)
+mychk(sim_.1_1h, target)
+```
+```{r ma = .1, n = 500}
+n <- 500
+blksize <- 8
+theta <- .1
+target <- c(0, 1, theta)
+set.seed(2345)
+sim_.1_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.1_5h,"../Data/Raw/sim_.1_5h.csv", row.names = FALSE)
+mychk(sim_.1_5h, target)
+```
+```{r ma = .1, n = 1000}
+n <- 1000
+blksize <- 10
+theta <- .1
+target <- c(0, 1, theta)
+set.seed(3456)
+sim_.1_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.1_1k,"../Data/Raw/sim_.1_1k.csv", row.names = FALSE)
+mychk(sim_.1_1k, target)
+```
+```{r ma = .3, n = 100}
+n <- 100
 blksize <- 5
 theta <- .3
-target <- c(0, 1, theta / (1 + theta^2))
+target <- c(0, 1, theta)
 set.seed(1234)
-sim_.3_125 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-mychk(sim_.3_125, target)
+sim_.3_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.3_1h,"../Data/Raw/sim_.3_1h.csv", row.names = FALSE)
+mychk(sim_.3_1h, target)
 ```
-
+```{r ma = .3, n = 500}
+n <- 500
+blksize <- 8
+theta <- .3
+target <- c(0, 1, theta)
+set.seed(2345)
+sim_.3_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.3_5h,"../Data/Raw/sim_.3_5h.csv", row.names = FALSE)
+mychk(sim_.3_5h, target)
+```
 ```{r ma = .3, n = 1000}
@@
 theta <- .3
-target <- c(0, 1, theta / (1 + theta^2))
-set.seed(2345)
+target <- c(0, 1, theta)
+set.seed(3456)
 sim_.3_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.3_1k,"../Data/Raw/sim_.3_1k.csv", row.names = FALSE)
 mychk(sim_.3_1k, target)
 ```
-
-```{r ma = .3, n = 3375}
-n <- 3375
-blksize <- 15
-theta <- .3
-target <- c(0, 1, theta / (1 + theta^2))
+```{r ma = .5, n = 100}
+n <- 100
+blksize <- 5
+theta <- .5
+target <- c(0, 1, theta)
+set.seed(1234)
+sim_.5_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.5_1h,"../Data/Raw/sim_.5_1h.csv", row.names = FALSE)
+mychk(sim_.5_1h, target)
+```
+```{r ma = .5, n = 500}
+n <- 500
+blksize <- 8
+theta <- .5
+target <- c(0, 1, theta)
+set.seed(2345)
+sim_.5_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.5_5h,"../Data/Raw/sim_.5_5h.csv", row.names = FALSE)
+mychk(sim_.5_5h, target)
+```
+```{r ma = .5, n = 1000}
+n <- 1000
+blksize <- 10
+theta <- .5
+target <- c(0, 1, theta)
 set.seed(3456)
-sim_.3_3375 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-mychk(sim_.3_3375, target)
+sim_.5_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
+write.csv(sim_.5_1k,"../Data/Raw/sim_.5_1k.csv", row.names = FALSE)
+mychk(sim_.5_1k, target)
 ```
-
-```{r ma = .3, n = 8000}
-n <- 8000
-blksize <- 20
-theta <- .3
-target <- c(0, 1, theta / (1 + theta^2))
-set.seed(4567)
-sim_.3_8k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-mychk(sim_.3_8k, target)
-```

### 2023-01-18 Manuscript/manuscript.tex
Manuscript Change

@@
 A potential solution to this issue is to center the intervals around either the original sample estimate $\hat{\theta}$ or the mean of all $\hat{\theta}_{b}$.
+To do this, the distribution of $\delta = $\hat{\theta}_{b}$ - $\hat{\theta}$ or
 
@@
 \begin{figure}[tbp]
-\caption{The figure below shows results for block bootstrap estimation when theta is 0.
-When the target was the mean and the moving method was used, the coverage rate confidence interval included .95 when the sample length was 512, indicating that even for a sample with no temporal dependence, a very large sample length of around 500 is necessary to get an accurate estimation of the mean.
-Similarly, when the target was the mean and the non-moving method was used, the coverage rate confidence interval included .95 when the sample length was 512, showing that a sample size of around 500 is necessary for good block bootstrap estimation.
-When the target was the AR(1) coefficient and the moving method was used, the parameter was over-covered - all of the coverage rate confidence interval lower bounds were greater than .95 - for all sample sizes that were observed (32, 64, 128, 256, and 512).
-This indicates that the variance of the parameter is being overestimated.
-When the target was the AR(1) coefficient and the non-moving method was used, the parameter was under-covered when the sample length was 32 and slightly over-covered when the sample length was 256.
-For sample lengths 64, 128, and 512, the non-moving method recovered the parameter well.}
+\caption{}
   \centering
-  \includegraphics[width=\textwidth]{theta_0}
+  \includegraphics[width=\textwidth]{figures/plot_.1}
   \caption{}
-  \label{fig:theta_0}
+  \label{fig:plot_.1}
 \end{figure}
@@
 \begin{figure}[tbp]
-\caption{The figure below shows results for block bootstrap estimation when theta is 0.2.
-When the target was the mean and the moving method was used, the coverage rate confidence interval included .95 when the sample length was 2048 and 4096, indicating that even for a sample with relatively low temporal dependence, a very large sample of around 2000 is necessary to get an accurate estimation of the mean.
-Similarly, when the target was the mean and the non-moving method was used, the coverage rate confidence interval included .95 when the sample length was 2048 and 4096, showing that a sample size of around 2000 is necessary for good block bootstrap estimation.
-When the target was the AR(1) coefficient, for both methods, the parameter was under-covered for sample lengths as large as 4096, although the moving method appeared to perform better for all sample sizes.
-}
+\caption{}
   \centering
-  \includegraphics[width=\textwidth]{theta_0.2}
+  \includegraphics[width=\textwidth]{figures/plot_.3}
   \caption{}
-  \label{fig:theta_0.2}
+  \label{fig:plot_.3}
 \end{figure}
@@
 \begin{figure}[tbp]
-\caption{The figure below shows results for block bootstrap estimation when theta is 0.4.
-When the target was the mean, for both methods, the coverage rate was under-covered for sample sizes as large as 8192.
-When the target was the AR(1) coefficient, for both methods, the parameter was under-covered for sample lengths as large as 4096, although the moving method appeared to perform better for smaller sample sizes.
-}
+\caption{}
   \centering
-  \includegraphics[width=\textwidth]{theta_0.4}
+  \includegraphics[width=\textwidth]{figures/plot_.5}
   \caption{}
-  \label{fig:theta_0.4}
+  \label{fig:plot_.5}
 \end{figure}

### 2023-01-19 Code/NewPlots.Rmd
Data Update

@@
 graph_bts(cov, theta, target, width = 50)
-ggsave('../Manuscript/plot_.1.pdf')
+ggsave('../Manuscript/figures/plot_.1.pdf')
 ```
@@
 graph_bts(cov, theta, target, width = 25)
-ggsave('../Manuscript/plot_.3.pdf')
+ggsave('../Manuscript/figures/plot_.3.pdf')
 ```
@@
 graph_bts(cov, theta, target, width = 10)
-ggsave('../Manuscript/plot_.5.pdf')
+ggsave('../Manuscript/figures/plot_.5.pdf')
 ```

### 2023-01-26 Code/NewPlots.Rmd
Manuscript Update

--- 2023-01-18 Code/NewPlots.Rmd
@@
 ```{r}
-graph_bts <- function(cov, theta, target, width, nrep = 1000, sizes = c(100, 500, 1000), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'theta'), level = .95) {
+graph_bts <- function(cov, phi, target, width, nrep = 1000, sizes = c(100, 200, 300, 400, 500), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'phi'), level = .95) {
   n <- rep(sizes, each = length(types) * length(parameters))
@@
 ```{r}
-theta <- 0.1
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.1_1h, target), mychk(sim_.1_5h, target), mychk(sim_.1_1k, target))
-
-graph_bts(cov, theta, target, width = 50)
-ggsave('../Manuscript/plot_.1.pdf')
+phi <- 0
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_0_1h, target), mychk(sim_0_2h, target), mychk(sim_0_3h, target), mychk(sim_0_4h, target), mychk(sim_0_5h, target))
+graph_bts(cov, phi, target, width = 25)
+ggsave('../Manuscript/figures/plot_0.pdf')
 ```
 ```{r}
-theta <- 0.3
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))
-
-graph_bts(cov, theta, target, width = 25)
-ggsave('../Manuscript/plot_.3.pdf')
+phi <- .2
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_.2_1h, target), mychk(sim_.2_2h, target), mychk(sim_.2_3h, target), mychk(sim_.2_4h, target), mychk(sim_.2_5h, target))
+graph_bts(cov, phi, target, width = 25)
+ggsave('../Manuscript/figures/plot_.2.pdf')
 ```
 ```{r}
-theta <- 0.5
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))
+phi <- .4
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_.4_1h, target), mychk(sim_.4_2h, target), mychk(sim_.4_3h, target), mychk(sim_.4_4h, target), mychk(sim_.4_5h, target))
 
-graph_bts(cov, theta, target, width = 10)
-ggsave('../Manuscript/plot_.5.pdf')
+graph_bts(cov, phi, target, width = 10)
+ggsave('../Manuscript/figures/plot_.4.pdf')
 ```

### 2023-01-26 Code/simulation.Rmd
Manuscript Update

@@
 
-do1rep <- function(n, theta, statistic, blksize, R = 1000, level = .95) {
-    x <- arima.sim(list(ar = theta), n = n) * sqrt(1 - theta^2)
+do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
+    if (phi == 0) {
+      x <- rnorm(n)
+    }
+    else {
+      x <- arima.sim(list(ar = phi), n = n) * sqrt(1 - phi^2)
+    }
     bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
@@
 
-```{r ma = .1, n = 100}
+```{r ar = 0, n = 100}
 n <- 100
 blksize <- 5
-theta <- .1
-target <- c(0, 1, theta)
+phi <- 0
+target <- c(0, 1, phi)
 set.seed(1234)
-sim_.1_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.1_1h,"../Data/Raw/sim_.1_1h.csv", row.names = FALSE)
-mychk(sim_.1_1h, target)
+sim_0_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_0_1h,"../Data/Raw/sim_0_1h.csv", row.names = FALSE)
+mychk(sim_0_1h, target)
 ```
-```{r ma = .1, n = 500}
+
+```{r ar = 0, n = 200}
+n <- 200
+blksize <- 6
+phi <- 0
+target <- c(0, 1, phi)
+set.seed(2345)
+sim_0_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_0_2h,"../Data/Raw/sim_0_2h.csv", row.names = FALSE)
+mychk(sim_0_2h, target)
+```
+
+```{r ar = 0, n = 300}
+n <- 300
+blksize <- 7
+phi <- 0
+target <- c(0, 1, phi)
+set.seed(3456)
+sim_0_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_0_3h,"../Data/Raw/sim_0_3h.csv", row.names = FALSE)
+mychk(sim_0_3h, target)
+```
+
+```{r ar = 0, n = 400}
+n <- 400
+blksize <- 7
+phi <- 0
+target <- c(0, 1, phi)
+set.seed(4567)
+sim_0_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_0_4h,"../Data/Raw/sim_0_4h.csv", row.names = FALSE)
+mychk(sim_0_4h, target)
+```
+
+```{r ar = 0, n = 500}
 n <- 500
 blksize <- 8
-theta <- .1
-target <- c(0, 1, theta)
-set.seed(2345)
-sim_.1_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.1_5h,"../Data/Raw/sim_.1_5h.csv", row.names = FALSE)
-mychk(sim_.1_5h, target)
+phi <- 0
+target <- c(0, 1, phi)
+set.seed(5678)
+sim_0_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_0_5h,"../Data/Raw/sim_0_5h.csv", row.names = FALSE)
+mychk(sim_0_5h, target)
 ```
-```{r ma = .1, n = 1000}
-n <- 1000
-blksize <- 10
-theta <- .1
-target <- c(0, 1, theta)
-set.seed(3456)
-sim_.1_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.1_1k,"../Data/Raw/sim_.1_1k.csv", row.names = FALSE)
-mychk(sim_.1_1k, target)
-```
-```{r ma = .3, n = 100}
+
+```{r ar = .2, n = 100}
 n <- 100
 blksize <- 5
-theta <- .3
-target <- c(0, 1, theta)
+phi <- .2
+target <- c(0, 1, phi)
 set.seed(1234)
-sim_.3_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.3_1h,"../Data/Raw/sim_.3_1h.csv", row.names = FALSE)
-mychk(sim_.3_1h, target)
+sim_.2_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.2_1h,"../Data/Raw/sim_.2_1h.csv", row.names = FALSE)
+mychk(sim_.2_1h, target)
 ```
-```{r ma = .3, n = 500}
+
+```{r ar = .2, n = 200}
+n <- 200
+blksize <- 6
+phi <- .2
+target <- c(0, 1, phi)
+set.seed(2345)
+sim_.2_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.2_2h,"../Data/Raw/sim_.2_2h.csv", row.names = FALSE)
+mychk(sim_.2_2h, target)
+```
+
+```{r ar = .2, n = 300}
+n <- 300
+blksize <- 7
+phi <- .2
+target <- c(0, 1, phi)
+set.seed(3456)
+sim_.2_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.2_3h,"../Data/Raw/sim_.2_3h.csv", row.names = FALSE)
+mychk(sim_.2_3h, target)
+```
+
+```{r ar = .2, n = 400}
+n <- 400
+blksize <- 7
+phi <- .2
+target <- c(0, 1, phi)
+set.seed(4567)
+sim_.2_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.2_4h,"../Data/Raw/sim_.2_4h.csv", row.names = FALSE)
+mychk(sim_.2_4h, target)
+```
+
+```{r ar = .2, n = 500}
 n <- 500
 blksize <- 8
-theta <- .3
-target <- c(0, 1, theta)
-set.seed(2345)
-sim_.3_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.3_5h,"../Data/Raw/sim_.3_5h.csv", row.names = FALSE)
-mychk(sim_.3_5h, target)
+phi <- .2
+target <- c(0, 1, phi)
+set.seed(5678)
+sim_.2_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.2_5h,"../Data/Raw/sim_.2_5h.csv", row.names = FALSE)
+mychk(sim_.2_5h, target)
 ```
-```{r ma = .3, n = 1000}
-n <- 1000
-blksize <- 10
-theta <- .3
-target <- c(0, 1, theta)
-set.seed(3456)
-sim_.3_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.3_1k,"../Data/Raw/sim_.3_1k.csv", row.names = FALSE)
-mychk(sim_.3_1k, target)
-```
-```{r ma = .5, n = 100}
+
+```{r ar = .4, n = 100}
 n <- 100
 blksize <- 5
-theta <- .5
-target <- c(0, 1, theta)
+phi <- .4
+target <- c(0, 1, phi)
 set.seed(1234)
-sim_.5_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.5_1h,"../Data/Raw/sim_.5_1h.csv", row.names = FALSE)
-mychk(sim_.5_1h, target)
+sim_.4_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.4_1h,"../Data/Raw/sim_.4_1h.csv", row.names = FALSE)
+mychk(sim_.4_1h, target)
 ```
-```{r ma = .5, n = 500}
+
+```{r ar = .4, n = 200}
+n <- 200
+blksize <- 6
+phi <- .4
+target <- c(0, 1, phi)
+set.seed(2345)
+sim_.4_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.4_2h,"../Data/Raw/sim_.4_2h.csv", row.names = FALSE)
+mychk(sim_.4_2h, target)
+```
+
+```{r ar = .4, n = 300}
+n <- 300
+blksize <- 7
+phi <- .4
+target <- c(0, 1, phi)
+set.seed(3456)
+sim_.4_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.4_3h,"../Data/Raw/sim_.4_3h.csv", row.names = FALSE)
+mychk(sim_.4_3h, target)
+```
+
+```{r ar = .4, n = 400}
+n <- 400
+blksize <- 7
+phi <- .4
+target <- c(0, 1, phi)
+set.seed(4567)
+sim_.4_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.4_4h,"../Data/Raw/sim_.4_4h.csv", row.names = FALSE)
+mychk(sim_.4_4h, target)
+```
+
+```{r ar = .4, n = 500}
 n <- 500
 blksize <- 8
-theta <- .5
-target <- c(0, 1, theta)
-set.seed(2345)
-sim_.5_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.5_5h,"../Data/Raw/sim_.5_5h.csv", row.names = FALSE)
-mychk(sim_.5_5h, target)
+phi <- .4
+target <- c(0, 1, phi)
+set.seed(5678)
+sim_.4_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.4_5h,"../Data/Raw/sim_.4_5h.csv", row.names = FALSE)
+mychk(sim_.4_5h, target)
 ```
-```{r ma = .5, n = 1000}
-n <- 1000
-blksize <- 10
-theta <- .5
-target <- c(0, 1, theta)
-set.seed(3456)
-sim_.5_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
-write.csv(sim_.5_1k,"../Data/Raw/sim_.5_1k.csv", row.names = FALSE)
-mychk(sim_.5_1k, target)
-```

### 2023-01-26 Manuscript/manuscript.tex
Quick Fix
Manuscript Update

@@
 large, the method will work perfectly. However, for a finite sample size, the method will 
-not work as well as expected.
+not work as well as expected. In the context of planning an applied 
+statistical procedure, for which a large sample size is not always practical, it may be helpful to know how large the sample must be for the method to work at an acceptable level.
+
 \citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from nonparametric bootstrapping are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
-In the context of planning an applied
-statistical procedure, for which a large sample size is not always practical, it may be helpful to know how large the sample must be for the method to work at an acceptable level. 
-The goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
-is an effective method for estimating a parameter.
-The method is effective if approximately 1 - $\alpha$/2 \% (for some predetermined significance level $\alpha$) of confidence intervals created from samples of the same size recover the parameter.
-
 \citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for estimation using the bootstrap method (simple resampling with no blocks involved).
-However, in this study, the focus is block bootstrapping a temporally dependent sample.This is a different situation altogether, first, because the sample has a dependence factor that must be accounted for, and second because block bootstrapping involves splitting the sample into blocks.
-
 \citet{goncalves2005bootstrap} found that standard error estimates from block bootstrapping small 
-samples 
-may be significantly more accurate than inference from closed-form asymptotic estimates.
+samples may be significantly more accurate than inference from closed-form asymptotic estimates.
 That study focused on the estimation of a coefficient parameter within the context of linear regression.
 Still, the block bootstrap percentile confidence intervals under-covered the parameter even for n = 1024.
-This study aims to find how small the sample size can be for a time series (which has a time dependence factor comparable to a coefficient of a linear regression) in order for the coverage rate to be close to the confidence level.
 
-For this study, the block bootstrap method was applied to time series simulations in R.
+The goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
+is an effective method for estimating a parameter in the context of a time series.
+The method is effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals created from samples of the same size recover the parameter.
+This study will focus on estimating parameters of an AR(1) process with several types of confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} which will be reviewed in Section 2.
 
@@
 
-Bootstrapping is the procedure of creating new pseudo-samples of the same size by resampling observations with replacement from
-the original sample. Basic bootstrapping works well for samples
-that are do not have a dependence factor. However, for a time series such as an auto-regressive or moving-average process,
-a different procedure is required to account for the time dependence.
+%Bootstrapping is the procedure of creating new pseudo-samples of the same size by resampling observations with replacement from the original sample. Basic bootstrapping works well for samples
+% that are do not have a dependence factor.
+However, for a time series such as an auto-regressive or moving-average process, a different procedure is required to account for the time dependence.
 In such a situation, instead of resampling observations, blocks of the original sample can be resampled (these blocks must be of a certain length by which the sample length is divisible) to create a pseudo-sample.
@@
 
-The various ways which these intervals can be constructed are described in \citet{diciccio1996bootstrap} and \citet{rice2006mathematical}.
+%The various ways which these intervals can be constructed are described in \citet{diciccio1996bootstrap} and \citet{rice2006mathematical}.
 They will be discussed later in a review of the block bootstrap method.
-For the purposes of this study (in which the true parameters are known), in order to establish whether or not the method is effective, the block bootstrapping of a simulated sample can be replicated many times,
-and the proportion of confidence intervals that recover the true known parameter 
-(coverage rate) is recorded. The goal of this is simply to observe how successful the block bootstrapping procedure
-is at estimating a parameter. The key variable being observed was, the sample length (n). It is known that as n
-increases, block bootstrapping should become a more accurate and precise method for estimation
-(the coverage rates will approach the theoretical confidence level and the interval widths will decrease).
+For the purposes of this study (in which the true parameters are known), in order to establish whether or not the method is effective, the block bootstrapping of a simulated sample can be replicated many times, and the proportion of confidence intervals that recover the true known parameter (coverage rate) is recorded.
+The goal of this is simply to observe how successful the block bootstrapping procedure is at estimating a parameter.
+The key variable being observed was, the sample length (n).
+It is known that as n increases, block bootstrapping should become a more accurate and precise method for estimation(the coverage rates will approach the theoretical confidence level and the interval widths will decrease).
 The question is what is the minimum sample length necessary to reach a coverage rate of 1 - $\alpha$/2 \%.
 
-In this experiment, there are certain variables that are expected to affect the performance of block bootstrap. As the the time dependence (AR or MA coefficient) of the time series 
-increases, we expect the coverage rates of the confidence intervals to decrease.
-The coverage rates are also affected by the size of the blocks - more specifically,
-how the size of the blocks (l) relates to the size of the time series (n) - 
-and whether or not they overlap. It is known that as the size of the time series 
-increases, the optimal block length should increase, and the ratio of the block length to 
-the time series length should decrease. l = n$^{1/3}$ is typically considered the optimal 
-block length according to asymptotic theory. \citep{buhlmann1999block} Therefore, simulations in this study were conducted using this optimal function of l = n$^{1/3}$.
+% In this experiment, there are certain variables that are expected to affect the performance of block bootstrap.
+As the the time dependence (AR or MA coefficient) of the time series increases, we expect the coverage rates of the confidence intervals to decrease.The coverage rates are also affected by the size of the blocks - more specifically,how the size of the blocks (l) relates to the size of the time series (n) - and whether or not they overlap.
+It is known that as the size of the time series increases, the optimal block length should increase, and the ratio of the block length to the time series length should decrease.
+l = n$^{1/3}$ is typically considered the optimal block length according to asymptotic theory.
+\citep{buhlmann1999block} Therefore, simulations in this study were conducted using this optimal function of l = n$^{1/3}$.
 
 %In order to solve the question of what sample length is necessary for effective block bootstrapping while still accounting for all these factors, the simulations were repeated for different variations of the MA coefficient, target parameter, and non-moving vs moving method.
-
 For each of these variations, results for block bootstrap estimation of mean, MA coefficient, and standard deviation were recorded for a wide range of sample length.
@@
 
-Block bootstrapping is a method that can be applied to a non-stationary process to estimate a parameter.
-Suppose that a sample of length n of a time series is given.
-In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the with replacement.
+Block bootstrapping is a method that can be used to estimate a parameter of an AR(1) process. Suppose that one wants to estimate a parameter or parameters $\theta$ of an AR(1) process: 
+\[X_{t} = \mu + \epsilon_{t} + \phi*X_{t-1}.\] The first step is to generate a sample of length $n$ from the process.
+An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample.
+A pseudo-estimate $\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample.
+The mean $\bar\theta_n^*$ of many (typically 1000) replicate $\hat\theta_n^*$ can also be computed.
+Lastly, for each $\hat\theta_n^*$, $\delta = \hat\theta_n^* - \hat{\theta}_{n}$ and $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.
+
+In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the original sample with replacement.
 In the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size.
-The block should be of size l large enough to include time dependence, yet small enough to include some variance.
-l should also divide n.
-As n increases, an ideal l should also increase, but the ratio of l to n should decrease.
-To achieve this, l is often assigned a value as a function of n.
-A common function that is considered the best by much previous literature is l = n$^{1/3}$.
-To make things sample for this study, only perfect cubes were used for the sample length.
-A bootstrapped sample is created by taking a sample of n / l blocks with replacement to create a new pseudo-sample of size n.
+The block should be of size $l$ large enough to include time dependence, yet small enough to include some variance.
+As $n$ increases, an ideal $l$ should also increase, but the ratio of $l$ to $n$ should decrease.
+To achieve this, $l$ is often assigned a value as a function of $n$.
+A common function that is considered the best by much previous literature is $l = \lceil = n^{1/3} \rceil$.
+\citep{buhlmann1999block} A bootstrapped sample is created by taking a sample of $n / l$ blocks with replacement to create a new pseudo-sample of size $n$.
 The designer of the study can choose whether the blocks overlap or not.
 If the blocks can never overlap, it is called a non-moving block bootstrap.
-In this case, the original sample is split evenly into n / l blocks, and the same number of blocks are sampled with replacement to create a bootstrapped pseudo-sample.
+In this case, the original sample is split evenly into $n / l$ blocks, and the same number of blocks are sampled with replacement to create a bootstrapped pseudo-sample.
 If the blocks do overlap, it is called a moving block bootstrap.
-n / l samples are taken randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
-An estimate of the parameter (or parameters) $\hat{\theta}_{b}$ is computed from the bootstrapped sample.
-This procedure can be repeated many times to create a distribution of $\hat{\theta}_{b}$.
-In this study, 1000 bootstrapped pseudo-samples were created for each simulation.
-Using this distribution of $\hat{\theta}_{b}$, a 1 - $\alpha$/2 \% confidence interval for the parameter can be created.
+$n / l$ samples are taken randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
+$\hat\theta_n^*$ is computed from the pseudo-sample.
+This procedure can be repeated many times to create a distribution of $\hat\theta_n^*$.
+
+In this study, 1000 bootstrapped $\hat\theta_n^*$ were created for each simulation.
+Using this distribution of $\hat\theta_n^*$, a $1 - \alpha$/2 \% confidence interval for the parameter can be created.
 The most simplistic method for constructing this interval is the percentile confidence interval.
-For a parameter $\theta$, the percentile confidence interval takes the form: \[ [\hat{\theta}_{b, .025}, \hat{\theta}_{b, .975}].\] Another method is the bias-corrected and accelerated
-(BCA) confidence interval, which takes the form: \[ [\hat{\theta}_{b, \alpha_{L}}, \hat{\theta}_{b, \alpha_{U}}].\] $\alpha{L}$ and $\alpha{U}$ are the cumulative probability of $z{L}$ and $z{U}$, respectively, where:
-\[z_{L} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} + z_{0}\] and
-\[z_{U} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} + z_{0}.\] 
-	Both of these intervals are good at recovering the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as n increases.
-A potential solution to this issue is to center the intervals around either the original sample estimate $\hat{\theta}$ or the mean of all $\hat{\theta}_{b}$.
-To do this, the distribution of $\delta = $\hat{\theta}_{b}$ - $\hat{\theta}$ or
+For a parameter $\theta$, the percentile $1 - \alpha$/2 \% confidence interval takes the form:
+\[ [\hat\theta_{n, \alpha/2}^*, \hat\theta_{n, 1 - \alpha/2}^*].\] 
+Another method is the bias-corrected and accelerated 
+(BCA) $1 - \alpha$/2 \% confidence interval, which takes the form: 
+\[ [\hat\theta_{n, \alpha_1}^*,\hat\theta_{n, \alpha_2}^*].\] 
+$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and $z_{2}$, respectively, where:
+\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} + z_{0}\] and
+\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} + z_{0}.\] 
+Where $z_0$ is the quantile function of the proportion of $\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness of ...
 
-\section{Simulation Study Design}
-\label{sec:simdesign}
+	Both of these intervals are good at recovering the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as $n$ increases.
+A potential solution to this issue is to center the intervals around either $\hat{\theta}_{n}$ or $\bar\theta_n^*$.
+To do this, the distribution of $\delta$ or $\delta^*$ should be considered.
+A percentile interval centered around $\hat{\theta}_{n}$ takes the form:
+\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\] 
+A percentile interval centered around $\bar\theta_n^*$ takes the form: 
+\[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\]
+An alternative is an interval of the form:
+\[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] 
+which is equivalent to:
+\[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] 
+and therefore is also equivalent to:
+\[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] 
+Thus, the interval is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.
 
-The central objective of the study was to assess what sample size is necessary for the the block bootstrap method to estimate a parameter of an autoregressive process.
+This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ takes the form:
+\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
+A BCA interval centered around $\bar\theta_n^*$ takes the form: 
+\[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\]
+An alternative is an interval of the form:
+\[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}],\]
+
+\section{Simulation Study}
+\label{sec:simstudy}
+
+%The central objective of the study was to assess what sample size is necessary for the the block bootstrap method to estimate a parameter of an autoregressive process.
 The method will work better as the sample size goes to infinity, but the goal is to see what is the smallest sample size that is acceptable.
@@
 
-R has a built in ARIMA simulation function which allows you to set the mean, AR and MA coefficients, and the standard deviation of the error term $\epsilon$.
-The standard deviation $\sigma_{\epsilon}$ of a AR(1) process with mean 0 can be written as a function of $\sigma_{x}$ and the AR(1) coefficient $\theta$.
-\[X_{t} = \epsilon_{t} + \theta*X_{t-1}\]
-\[Var(X_{t}) = Var(\epsilon_{t} + \theta*X_{t-1})\]
-\[\sigma^2_{x} = \sigma^2_{\epsilon} + \theta^2*\sigma^2_{x}\]
-\[\sigma^2_{x}(1 - \theta^2) = \sigma^2_{\epsilon}\]
-\[\sigma_{\epsilon} = \sigma_{x}\sqrt{1 - \theta^2}\]
+R has a built in function that allows you to simulate an AR(1) process, for which one can set the theoretical $\phi$.
+For the purposes of this study, $\mu$ should be fixed at 0, and the standard deviation of the process $\sigma_{x}$ should be fixed at 1.
+By default, the standard deviation of the error term $\sigma_{\epsilon}$ is 1, so the observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
 
-For the purposes of this study, $\mu$ should be fixed at 0, and $\sigma_{x}$ at 1.
-By default, $\mu$ is 0 and $\sigma_{\epsilon}$ is 1, so the observations can be multiplied by $\sqrt{1 - \theta^2}$ so that the theoretical $\sigma_{x}$ is equivalent to 1.
+\[X_{t} = \epsilon_{t} + \phi*X_{t-1}.\]
+\[Var(X_{t}) = Var(\epsilon_{t} + \phi*X_{t-1})\]
+\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2*\sigma^2_{x}\]
+\[\sigma^2_{x}(1 - \phi^2) = \sigma^2_{\epsilon}\]
+\[\sigma_{\epsilon} = \sigma_{x}\sqrt{1 - \phi^2}\]
 
-For all simulation studies, , but $\mu$ and $\sigma_{x}$ can be kept constant, but increasing temporal dependence factors such as AR and MA Coefficients can make block bootstrap less effective in estimation, so its impact on the method's performance should be analyzed.
+As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process.
+In this study, $\theta$ is composed of the target parameters $\mu$, $\sigma_{x}$, and $\phi$.
+From a sample of length $n$, six block bootstrap 95\% confidence intervals can be constructed for each target parameter: ....
+
+Each of these 18 intervals either recovers $\theta$ or does not.
+Remember that 95\% of a certain type of 95\% confidence intervals constructed from samples of the same $n$ should recover $\theta$.
+To see if this is approximately the case, one can run 1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers $\theta$ can be recorded.
+
+For all simulation studies, but $\mu$ and $\sigma_{x}$ can be kept constant, but increasing temporal dependence factors such as AR and MA Coefficients can make block bootstrap less effective in estimation, so its impact on the method's performance should be analyzed.
 For a certain variation of an AR(1) process, block bootstrap 95\% confidence intervals for each of 3 parameters ($\mu$, $\sigma_{x}$, and the autocorrelation function$\rho$) can be replicated for 1000 simulated samples of a certain length.
@@
 
-\section{Methods}
-\label{sec:methods}
-
 1000 replicates of length-n random samples of an AR(1) process with theoretical $\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1 were simulated using R.
@@
 
-\section{Results}
-\label{sec:results}
-
 \begin{figure}[tbp]
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_.1}
-  \caption{}
-  \label{fig:plot_.1}
+  \includegraphics[width=\textwidth]{figures/plot_0}
+  \caption{At $\phi = 0$, all intervals covered $\mu$ correctly at $n = 500$.
+All but three intervals seem to cover $\phi$ generally well for $n = 300$.
+The alternate percentile interval slightly under-covers $\phi$ for all sample lengths observed.
+The BCA interval centered around $\hat{\theta}_{n}$ significantly under-covers $\phi$ and the percentile interval centered around $\bar\theta_n^*$ over-covers $\phi$.
+All intervals seem to cover $\sigma$ generally well for n = 500 except for the $\hat{\theta}_{n}$-centered BCA interval, which slightly under-covers $\sigma$ for all sample lengths observed, and the  $\bar\theta_n^*$-centered BCA interval, which also under-covers $\sigma$.}
+  \label{fig:plot_0}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_.3}
-  \caption{}
-  \label{fig:plot_.3}
+  \includegraphics[width=\textwidth]{figures/plot_.2}
+  \caption{At $\phi = .2$, all intervals covered $\mu$ correctly at $n = 300$ and $n = 400$.
+The alternate percentile interval and the $\hat{\theta}_{n}$-centered percentile interval cover $\phi$ well at $n = 500$.
+The $\bar\theta_n^*$-centered BCA interval slightly under-covers $\phi$ for all sample lengths observed.}
+  \label{fig:plot_.2}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_.5}
+  \includegraphics[width=\textwidth]{figures/plot_.4}
   \caption{}
-  \label{fig:plot_.5}
+  \label{fig:plot_.4}
 \end{figure}
 
-\section{Discussion}
-\label{sec:discuss}
+\section{Concluding Remarks}
+\label{sec:conremarks}
 

### 2023-01-26 Manuscript/manuscript.tex
Another update

@@
 
+The only parameter of the AR(1) process that was varied was $\phi$, as the temporal dependence affects the performance of block bootstrap.
+$\phi$ = 0 (a standard normal distribution), 0.2, and 0.4 were used in this study.
+
 As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process.
@@
 
-For all simulation studies, but $\mu$ and $\sigma_{x}$ can be kept constant, but increasing temporal dependence factors such as AR and MA Coefficients can make block bootstrap less effective in estimation, so its impact on the method's performance should be analyzed.
+If $\theta$ is not covered at that $n$, a larger sample size must be necessary. $n = 100, 200, 300, 400, and 500$ were used in this study.
+
+%For all simulation studies, but $\mu$ and $\sigma_{x}$ can be kept constant, but increasing temporal dependence factors such as AR and MA Coefficients can make block bootstrap less effective in estimation, so its impact on the method's performance should be analyzed.
 For a certain variation of an AR(1) process, block bootstrap 95\% confidence intervals for each of 3 parameters ($\mu$, $\sigma_{x}$, and the autocorrelation function$\rho$) can be replicated for 1000 simulated samples of a certain length.
@@
 
-1000 replicates of length-n random samples of an AR(1) process with theoretical $\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1 were simulated using R.
+%1000 replicates of length-n random samples of an AR(1) process with theoretical $\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1 were simulated using R.
 For each of three target parameters ($\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1, three types of block bootstrap (with block length l) confidence intervals (percentile, empirical, and BCA) were constructed for each replicate sample.
@@
 The alternate percentile interval and the $\hat{\theta}_{n}$-centered percentile interval cover $\phi$ well at $n = 500$.
-The $\bar\theta_n^*$-centered BCA interval slightly under-covers $\phi$ for all sample lengths observed.}
+The $\bar\theta_n^*$-centered BCA interval slightly under-covers $\phi$ for all sample lengths observed.
+The alternate BCA interval under-covers $\phi$, and its performance deteriorates as $n$ increases, as does the $\bar\theta_n^*$-centered percentile interval but with lower coverage rates and more noticeable deterioration.
+The $\hat{\theta}_{n}$-centered BCA interval significantly under-covers $\phi$, although there is no clear deterioration.}
   \label{fig:plot_.2}
@@
   \includegraphics[width=\textwidth]{figures/plot_.4}
-  \caption{}
+  \caption{At $\phi = .4$,}
   \label{fig:plot_.4}

### 2023-02-02 Code/NewPlots.Rmd
Manuscript Update

--- 2023-01-18 Code/NewPlots.Rmd
@@
 ```{r}
-graph_bts <- function(cov, theta, target, width, nrep = 1000, sizes = c(100, 500, 1000), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'theta'), level = .95) {
+graph_bts <- function(cov, phi, target, width, trans = 'identity', nrep = 1000, sizes = c(100, 200, 300, 400, 500, 600), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'phi'), level = .95) {
   n <- rep(sizes, each = length(types) * length(parameters))
@@
     geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
-    facet_grid(t ~ CI)
+    facet_grid(factor(t, levels = parameters) ~ factor(CI, levels = types)) +
+    scale_y_continuous(trans=trans)
 }
@@
 ```{r}
-theta <- 0.1
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.1_1h, target), mychk(sim_.1_5h, target), mychk(sim_.1_1k, target))
+phi <- -.4
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_n.4_1h, target), mychk(sim_n.4_2h, target), mychk(sim_n.4_3h, target), mychk(sim_n.4_4h, target), mychk(sim_n.4_5h, target), mychk(sim_n.4_6h, target))
 
-graph_bts(cov, theta, target, width = 50)
-ggsave('../Manuscript/plot_.1.pdf')
+graph_bts(cov, phi, target, width = 25, trans = 'probit')
+ggsave('../Manuscript/figures/plot_n.4.pdf')
 ```
 ```{r}
-theta <- 0.3
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))
+phi <- -.2
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_n.2_1h, target), mychk(sim_n.2_2h, target), mychk(sim_n.2_3h, target), mychk(sim_n.2_4h, target), mychk(sim_n.2_5h, target), mychk(sim_n.2_6h, target))
+graph_bts(cov, phi, target, width = 25, trans = 'exp')
+ggsave('../Manuscript/figures/plot_n.2.pdf')
+```
 
-graph_bts(cov, theta, target, width = 25)
-ggsave('../Manuscript/plot_.3.pdf')
+```{r}
+phi <- 0
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_0_1h, target), mychk(sim_0_2h, target), mychk(sim_0_3h, target), mychk(sim_0_4h, target), mychk(sim_0_5h, target), mychk(sim_0_6h, target))
+graph_bts(cov, phi, target, width = 25)
+ggsave('../Manuscript/figures/plot_0.pdf')
 ```
 ```{r}
-theta <- 0.5
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))
+phi <- .2
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_.2_1h, target), mychk(sim_.2_2h, target), mychk(sim_.2_3h, target), mychk(sim_.2_4h, target), mychk(sim_.2_5h, target), mychk(sim_.2_6h, target))
+graph_bts(cov, phi, target, width = 25)
+ggsave('../Manuscript/figures/plot_.2.pdf')
+```
+```{r}
+phi <- .4
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_.4_1h, target), mychk(sim_.4_2h, target), mychk(sim_.4_3h, target), mychk(sim_.4_4h, target), mychk(sim_.4_5h, target), mychk(sim_.4_6h, target))
 
-graph_bts(cov, theta, target, width = 10)
-ggsave('../Manuscript/plot_.5.pdf')
+graph_bts(cov, phi, target, width = 25, trans = 'probit')
+ggsave('../Manuscript/figures/plot_.4.pdf')
 ```

### 2023-02-02 Code/simulation.Rmd
Manuscript Update

@@
 
+```{r ar = -.4, n = 100}
+n <- 100
+blksize <- 5
+phi <- -.4
+target <- c(0, 1, phi)
+set.seed(1234)
+sim_n.4_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.4_1h,"../Data/Raw/sim_n.4_1h.csv", row.names = FALSE)
+mychk(sim_n.4_1h, target)
+```
+
+```{r ar = -.4, n = 200}
+n <- 200
+blksize <- 6
+phi <- -.4
+target <- c(0, 1, phi)
+set.seed(2345)
+sim_n.4_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.4_2h,"../Data/Raw/sim_n.4_2h.csv", row.names = FALSE)
+mychk(sim_n.4_2h, target)
+```
+
+```{r ar = -.4, n = 300}
+n <- 300
+blksize <- 7
+phi <- -.4
+target <- c(0, 1, phi)
+set.seed(3456)
+sim_n.4_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.4_3h,"../Data/Raw/sim_n.4_3h.csv", row.names = FALSE)
+mychk(sim_n.4_3h, target)
+```
+
+```{r ar = -.4, n = 400}
+n <- 400
+blksize <- 7
+phi <- -.4
+target <- c(0, 1, phi)
+set.seed(4567)
+sim_n.4_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.4_4h,"../Data/Raw/sim_n.4_4h.csv", row.names = FALSE)
+mychk(sim_n.4_4h, target)
+```
+
+```{r ar = -.4, n = 500}
+n <- 500
+blksize <- 8
+phi <- -.4
+target <- c(0, 1, phi)
+set.seed(5678)
+sim_n.4_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.4_5h,"../Data/Raw/sim_n.4_5h.csv", row.names = FALSE)
+mychk(sim_n.4_5h, target)
+```
+
+```{r ar = -.4, n = 600}
+n <- 600
+blksize <- 9
+phi <- -.4
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_n.4_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.4_6h,"../Data/Raw/sim_n.4_6h.csv", row.names = FALSE)
+mychk(sim_n.4_6h, target)
+```
+
+```{r ar = -.2, n = 100}
+n <- 100
+blksize <- 5
+phi <- -.2
+target <- c(0, 1, phi)
+set.seed(1234)
+sim_n.2_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.2_1h,"../Data/Raw/sim_n.2_1h.csv", row.names = FALSE)
+mychk(sim_n.2_1h, target)
+```
+
+```{r ar = -.2, n = 200}
+n <- 200
+blksize <- 6
+phi <- -.2
+target <- c(0, 1, phi)
+set.seed(2345)
+sim_n.2_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.2_2h,"../Data/Raw/sim_n.2_2h.csv", row.names = FALSE)
+mychk(sim_n.2_2h, target)
+```
+
+```{r ar = -.2, n = 300}
+n <- 300
+blksize <- 7
+phi <- -.2
+target <- c(0, 1, phi)
+set.seed(3456)
+sim_n.2_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.2_3h,"../Data/Raw/sim_n.2_3h.csv", row.names = FALSE)
+mychk(sim_n.2_3h, target)
+```
+
+```{r ar = -.2, n = 400}
+n <- 400
+blksize <- 7
+phi <- -.2
+target <- c(0, 1, phi)
+set.seed(4567)
+sim_n.2_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.2_4h,"../Data/Raw/sim_n.2_4h.csv", row.names = FALSE)
+mychk(sim_n.2_4h, target)
+```
+
+```{r ar = -.2, n = 500}
+n <- 500
+blksize <- 8
+phi <- -.2
+target <- c(0, 1, phi)
+set.seed(5678)
+sim_n.2_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.2_5h,"../Data/Raw/sim_n.2_5h.csv", row.names = FALSE)
+mychk(sim_n.2_5h, target)
+```
+
+```{r ar = -.2, n = 600}
+n <- 600
+blksize <- 9
+phi <- -.2
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_n.2_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.2_6h,"../Data/Raw/sim_n.2_6h.csv", row.names = FALSE)
+mychk(sim_n.2_6h, target)
+```
+
 ```{r ar = 0, n = 100}
@@
 mychk(sim_0_5h, target)
+```
+
+```{r ar = 0, n = 600}
+n <- 600
+blksize <- 9
+phi <- 0
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_0_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_0_6h,"../Data/Raw/sim_0_6h.csv", row.names = FALSE)
+mychk(sim_0_6h, target)
 ```
@@
 
+```{r ar = .2, n = 600}
+n <- 600
+blksize <- 9
+phi <- .2
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_.2_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.2_6h,"../Data/Raw/sim_.2_6h.csv", row.names = FALSE)
+mychk(sim_.2_6h, target)
+```
+
 ```{r ar = .4, n = 100}
@@
 ```
+
+```{r ar = .4, n = 600}
+n <- 600
+blksize <- 9
+phi <- .4
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_.4_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.4_6h,"../Data/Raw/sim_.4_6h.csv", row.names = FALSE)
+mychk(sim_.4_6h, target)
+```

### 2023-02-02 Manuscript/manuscript.tex
Manuscript Update

@@
 
-Block bootstrapping is a method that can be used to estimate a parameter of an AR(1) process. Suppose that one wants to estimate a parameter or parameters $\theta$ of an AR(1) process: 
-\[X_{t} = \mu + \epsilon_{t} + \phi*X_{t-1}.\] The first step is to generate a sample of length $n$ from the process.
+Block bootstrapping is a method that can be used to estimate a parameter of serially dependent data.
+Suppose that one wants to estimate a parameter or parameters $\theta$ of a population.
+The first step is to generate a sample of length $n$ from the population.
 An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample.
@@
 To do this, the distribution of $\delta$ or $\delta^*$ should be considered.
-A percentile interval centered around $\hat{\theta}_{n}$ takes the form:
+A percentile interval centered around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
 \[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\] 
-A percentile interval centered around $\bar\theta_n^*$ takes the form: 
+A percentile interval centered around $\bar\theta_n^*$ ($CI_{\bar\theta_n^*}$) takes the form: 
 \[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\]
@@
 \[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] 
-Thus, the interval is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.
+Thus, the interval ($CI_{\hat{\theta}_{n}, \bar\theta_n^*}$) is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.
 
-This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ takes the form:
+This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the form:
 \[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
-A BCA interval centered around $\bar\theta_n^*$ takes the form: 
+A BCA interval centered around $\bar\theta_n^*$ ($CI_{BCA, \bar\theta_n^*}$) takes the form: 
 \[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\]
-An alternative is an interval of the form:
-\[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}],\]
+An alternative (($CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$) is an interval of the form:
+\[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}]\]
+
+Thus there are three possible ways to center an interval: $CI_{\hat{\theta}_{n}}$, $CI_{\bar\theta_n^*}$, $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$, and three additional intervals which use bias-correction and acceleration to determine the percentiles for the critical values: $CI_{BCA, \hat{\theta}_{n}}$, $CI_{BCA, \bar\theta_n^*}$, $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$.
 
@@
 R has a built in function that allows you to simulate an AR(1) process, for which one can set the theoretical $\phi$.
-For the purposes of this study, $\mu$ should be fixed at 0, and the standard deviation of the process $\sigma_{x}$ should be fixed at 1.
-By default, the standard deviation of the error term $\sigma_{\epsilon}$ is 1, so the observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
+By default, the mean of the process $\mu$ is 0 and the standard deviation of the error term $\sigma_{\epsilon}$ is 1.
+For the purposes of this study, the standard deviation of the process $\sigma_{x}$ should be controlled at 1.
+The observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
 
-\[X_{t} = \epsilon_{t} + \phi*X_{t-1}.\]
-\[Var(X_{t}) = Var(\epsilon_{t} + \phi*X_{t-1})\]
-\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2*\sigma^2_{x}\]
-\[\sigma^2_{x}(1 - \phi^2) = \sigma^2_{\epsilon}\]
-\[\sigma_{\epsilon} = \sigma_{x}\sqrt{1 - \phi^2}\]
+\[X_{t} = \epsilon_{t} + \phi X_{t-1}.\]
+\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1})\]
+\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x}\]
+\[\sigma^2_{x}(1 - \phi^2) = 1\]
+\[\sigma_{x}\sqrt{1 - \phi^2} = 1\]
 
-The only parameter of the AR(1) process that was varied was $\phi$, as the temporal dependence affects the performance of block bootstrap.
-$\phi$ = 0 (a standard normal distribution), 0.2, and 0.4 were used in this study.
+The experimental factor of this study was $\phi$, as the temporal dependence affects the performance of block bootstrap.
+$\phi = -0.4 -0.2,$ and $0$ (a standard normal distribution)$, 0.2, and 0.4$ were used in this study.
 
 As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process.
-In this study, $\theta$ is composed of the target parameters $\mu$, $\sigma_{x}$, and $\phi$.
+In this study, $\theta$ is composed of the target parameters $\mu = 0$, $\sigma_{x}$, and $\phi$.
 From a sample of length $n$, six block bootstrap 95\% confidence intervals can be constructed for each target parameter: ....
@@
   \centering
+  \includegraphics[width=\textwidth]{figures/plot_n.4}
+  \caption{At $\phi = -.4$, all intervals covered $\mu$ correctly as low as $n = 100$.
+$CI_{\hat{\theta}_{n}}$, $CI_{\bar\theta_n^*}$, $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$, and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ seem to cover $\sigma$ well at $n = 600$.
+$CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ undercover $\sigma$, but there is no clear pattern of deterioration of coverage, so increasing $n$ will eventually result in good coverage.
+$CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ are the only two intervals that cover $\phi$ well with no deterioration, and this is true as low as $n = 200$.
+The other types of intervals greatly under-cover $\sigma$ and there is a clear pattern of deterioration of coverage.}
+  \label{fig:plot_n.4}
+\end{figure}
+
+\begin{figure}[tbp]
+\caption{}
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_n.2}
+  \caption{At $\phi = -.2$, all intervals covered $\mu$ correctly as low as $n = 100$.
+All intervals seem to cover $\sigma$ generally well at $n = 600$, although $CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ have noticeably lower coverage rates.
+$CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ are the only two intervals that cover $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.
+$CI_{\bar\theta_n^*}$ and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ cover $\phi$ well at $n = 100$, but the coverage deteriorates as $n$ increases.
+$CI_{BCA, \bar\theta_n^*}$ slightly under-covers $\phi$, and there is a slight coverage deterioration trend as $n$ increases.
+$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a coverage deterioration trend as $n$ increases.}
+  \label{fig:plot_n.2}
+\end{figure}
+
+\begin{figure}[tbp]
+\caption{}
+  \centering
   \includegraphics[width=\textwidth]{figures/plot_0}
-  \caption{At $\phi = 0$, all intervals covered $\mu$ correctly at $n = 500$.
-All but three intervals seem to cover $\phi$ generally well for $n = 300$.
-The alternate percentile interval slightly under-covers $\phi$ for all sample lengths observed.
-The BCA interval centered around $\hat{\theta}_{n}$ significantly under-covers $\phi$ and the percentile interval centered around $\bar\theta_n^*$ over-covers $\phi$.
-All intervals seem to cover $\sigma$ generally well for n = 500 except for the $\hat{\theta}_{n}$-centered BCA interval, which slightly under-covers $\sigma$ for all sample lengths observed, and the  $\bar\theta_n^*$-centered BCA interval, which also under-covers $\sigma$.}
+  \caption{At $\phi = 0$, all intervals covered $\mu$ correctly as low as $n = 500$.
+$CI_{\hat{\theta}_{n}}$, $CI_{\bar\theta_n^*}$, $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$, and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ seem to cover $\sigma$ well as low as $n = 500$.
+$CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ slightly undercover $\sigma$, but there is no clear pattern of deterioration of coverage, so increasing $n$ will eventually result in good coverage.
+$CI_{\hat{\theta}_{n}}$, $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$, $CI_{BCA, \bar\theta_n^*}$, and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ seem to cover $\phi$ generally well at $n = 600$, but $CI_{\bar\theta_n^*}$ over-covers $\phi$ with a slight coverage deterioration trend as $n$ increase, and $CI_{BCA, \bar\theta_n^*}$ under-covers $\phi$, although there is no clear coverage deterioration.}
   \label{fig:plot_0}
@@
   \includegraphics[width=\textwidth]{figures/plot_.2}
-  \caption{At $\phi = .2$, all intervals covered $\mu$ correctly at $n = 300$ and $n = 400$.
-The alternate percentile interval and the $\hat{\theta}_{n}$-centered percentile interval cover $\phi$ well at $n = 500$.
-The $\bar\theta_n^*$-centered BCA interval slightly under-covers $\phi$ for all sample lengths observed.
-The alternate BCA interval under-covers $\phi$, and its performance deteriorates as $n$ increases, as does the $\bar\theta_n^*$-centered percentile interval but with lower coverage rates and more noticeable deterioration.
-The $\hat{\theta}_{n}$-centered BCA interval significantly under-covers $\phi$, although there is no clear deterioration.}
+  \caption{At $\phi = .2$, all intervals covered $\mu$ correctly as low as $n = 300$.
+All intervals except for $CI_{BCA, \bar\theta_n^*}$ seem to cover $\sigma$ generally well at $n = 600$.
+However, $CI_{BCA, \bar\theta_n^*}$ shows no clear pattern of coverage deterioration, so increasing $n$ will eventually result in good coverage.
+$CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ are the only two intervals that cover $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.
+$CI_{BCA, \bar\theta_n^*}$ slightly under-covers $\phi$ with no clear deterioration.
+$CI_{\bar\theta_n^*}$ and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ under-cover $\phi$ with a clear coverage deterioration trend as $n$ increases.
+$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with no clear coverage deterioration.}
   \label{fig:plot_.2}
@@
   \includegraphics[width=\textwidth]{figures/plot_.4}
-  \caption{At $\phi = .4$,}
+  \caption{At $\phi = .4$, all intervals seem to cover $\mu$ generally well at $n = 600$, although $CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ have slightly higher coverage rates.
+$CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ cover $\sigma$ well as low as $n = 400$, $CI_{BCA, \bar\theta_n^*}$ and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ slightly under-cover $\sigma$, and $CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ more noticeable under-cover $\sigma$.
+For all intervals, there is not sign of coverage deterioration, indicating that increasing $n$ will eventually result in proper coverage.
+$CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ are the only two intervals that cover $\phi$ well with no deterioration of coverage, and this is true as low as $n = 300$.
+The other intervals greatly under-cover $\phi$ with a clear coverage deterioration trend as $n$ increases.}
   \label{fig:plot_.4}
 \end{figure}
+
+Only $CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ managed to solve the deterioration problem with respect to recovering $\phi$, indicating that these intervals should be used as opposed to the other types when estimating $\phi$.
 
@@
 
-This study finds that as the AR coefficient increases, the sample size necessary for effective block bootstrap estimation must be larger.
-When implementing the block bootstrap method to estimate the mean or variance of an autoregressive process, the non-moving method and moving method perform about the same.
-However, when estimating the AR(1) coefficient, the non-moving method performs noticeably worse than the moving method, which still covers the coefficient poorly when theta is greater than 0.
-Whereas the performance improves as sample length increases when the target is the mean or variance, the performance decays as sample length increases when the target is the AR(1) coefficient.
+The motivation for this study is what is a good enough sample size for block bootstrap.
 

### 2023-02-02 Code/demo.R

@@ -2,46 +2,46 @@
 ## block bootstrap with series generated from an MA process
 
 mystat <- function(x) {
-    c(mean(x),
-      sd(x),
-      cor(x[-1], x[-length(x)]))
-      # acf(x, lag.max = 1, plot = FALSE)$acf[2])
+  c(mean(x),
+    sd(x),
+    cor(x[-1], x[-length(x)]))
+  # acf(x, lag.max = 1, plot = FALSE)$acf[2])
 }
 
 do1rep <- function(n, theta, statistic, blksize, R = 1000, level = .95) {
-    x <- arima.sim(list(ma = theta), n = n) / sqrt(1 + theta^2)
-    bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
-    alpha <- 1 - level
-    ## returns a vector with length twice of that of mystat's returned values
-    ## each pair forms an interval for one target
-    ## pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
-    mbts <- apply(bts$t, 2, mean)
-    crit <- apply(abs(t(t(bts$t) - mbts)), 2, quantile, prob = level)
-    pctCI <- rbind(bts$t0 - crit, bts$t0 + crit)  
-    empCI <- matrix(2 * bts$t0, 2, length(bts$t0), byrow = TRUE) - pctCI[c(2, 1),]
-    ## BCa interval
-    z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
-    ## thetajack <- sapply(1:n, function(i) statistic(x[-i]))
-    thetajack <- sapply(1: (n / blksize),
-                        function(i) statistic(x[ - ((i - 1) * blksize + 1:blksize)]))
-    a <- apply(thetajack, 1, e1071::skewness) / 6
-    alpha1 <- pnorm(z0 + (z0 + qnorm(alpha/2)) / (1 - a * (z0 + qnorm(alpha/2))))
-    alpha2 <- pnorm(z0 + (z0 + qnorm(1 - alpha/2)) / (1 - a * (z0 + qnorm(1 - alpha/2))))
-    bcaCI <- sapply(1:length(bts$t0),
-                    function(i) quantile(bts$t[,i], prob = c(alpha1[i], alpha2[i])))
-    ## return all intervals
-    c(pctCI, empCI, bcaCI)
[…]

### 2023-02-09 Code/NewPlots.Rmd
Manuscript Update

--- 2023-01-19 Code/NewPlots.Rmd
@@
 ```{r}
-graph_bts <- function(cov, theta, target, width, nrep = 1000, sizes = c(100, 500, 1000), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'theta'), level = .95) {
+graph_bts <- function(cov, phi, target, width, trans = 'identity', nrep = 1000, sizes = c(100, 200, 300, 400, 500, 600, 700), types = c('estCI', 'bcaCIest'), parameters = c('mu', 'sigma', 'phi'), level = .95) {
   n <- rep(sizes, each = length(types) * length(parameters))
@@
 ```{r}
-theta <- 0.1
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.1_1h, target), mychk(sim_.1_5h, target), mychk(sim_.1_1k, target))
+phi <- -.4
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_n.4_1h, target), mychk(sim_n.4_2h, target), mychk(sim_n.4_3h, target), mychk(sim_n.4_4h, target), mychk(sim_n.4_5h, target), mychk(sim_n.4_6h, target), mychk(sim_n.4_7h, target))
 
-graph_bts(cov, theta, target, width = 50)
-ggsave('../Manuscript/figures/plot_.1.pdf')
+graph_bts(cov, phi, target, width = 10)
+ggsave('../Manuscript/figures/plot_n.4.pdf')
 ```
 ```{r}
-theta <- 0.3
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))
+phi <- -.2
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_n.2_1h, target), mychk(sim_n.2_2h, target), mychk(sim_n.2_3h, target), mychk(sim_n.2_4h, target), mychk(sim_n.2_5h, target), mychk(sim_n.2_6h, target), mychk(sim_n.2_7h, target))
+graph_bts(cov, phi, target, width = 25)
+ggsave('../Manuscript/figures/plot_n.2.pdf')
+```
 
-graph_bts(cov, theta, target, width = 25)
-ggsave('../Manuscript/figures/plot_.3.pdf')
+```{r}
+phi <- 0
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_0_1h, target), mychk(sim_0_2h, target), mychk(sim_0_3h, target), mychk(sim_0_4h, target), mychk(sim_0_5h, target), mychk(sim_0_6h, target), mychk(sim_0_7h, target))
+graph_bts(cov, phi, target, width = 25)
+ggsave('../Manuscript/figures/plot_0.pdf')
 ```
 ```{r}
-theta <- 0.5
-target <- c(0, 1, theta)
-cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))
+phi <- .2
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_.2_1h, target), mychk(sim_.2_2h, target), mychk(sim_.2_3h, target), mychk(sim_.2_4h, target), mychk(sim_.2_5h, target), mychk(sim_.2_6h, target), mychk(sim_.2_7h, target))
+graph_bts(cov, phi, target, width = 25)
+ggsave('../Manuscript/figures/plot_.2.pdf')
+```
+```{r}
+phi <- .4
+target <- c(0, 1, phi)
+cov <- c(mychk(sim_.4_1h, target), mychk(sim_.4_2h, target), mychk(sim_.4_3h, target), mychk(sim_.4_4h, target), mychk(sim_.4_5h, target), mychk(sim_.4_6h, target), mychk(sim_.4_7h, target))
 
-graph_bts(cov, theta, target, width = 10)
-ggsave('../Manuscript/figures/plot_.5.pdf')
+graph_bts(cov, phi, target, width = 25)
+ggsave('../Manuscript/figures/plot_.4.pdf')
 ```

### 2023-02-09 Code/simulation.Rmd
Manuscript Update

@@
     ## of pseudo-estimate - mean of pseudo-estimates
-    crit2 <- 
-      apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
+    # crit2 <- 
+    #  apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
     ## alpha/2 and 1 - alpha/2 critical values 
@@
     ## LB: bts$t0 + alpha/2 crit, UB: bts$t0 + (1 - alpha/2) crit
-    mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
+    # mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
     ## LB: mbts + alpha/2 crit2, UB: mbts + (1 - alpha/2) crit2
-    altCI <- sweep(-crit[order(2:1),], 2, bts$t0, FUN = '+') # both
+    # altCI <- sweep(-crit[order(2:1),], 2, bts$t0, FUN = '+') # both
     ## LB: bts$t0 - (1 - alpha/2) crit, UB: bts$t0 - alpha/2 crit and
@@
     ## of pseudo-estimate - mean of pseudo-estimates
-    crit4 <- sapply(1:length(bts$t0), function(i) 
-      quantile(t(t(bts$t[,i]) - bts$t0[i]), prob = c(alpha1[i], alpha2[i])))
+    # crit4 <- sapply(1:length(bts$t0), function(i) 
+    #  quantile(t(t(bts$t[,i]) - bts$t0[i]), prob = c(alpha1[i], alpha2[i])))
     ## alpha1 and alpha2 critical values 
@@
     ## LB: bts$t0 + alpha1 crit3, UB: bts$t0 + alpha2 crit3
-    bcaCImbt <- sweep(crit4, 2, mbts, FUN = '+') # mean of pseudo-estimates
+    # bcaCImbt <- sweep(crit4, 2, mbts, FUN = '+') # mean of pseudo-estimates
     ## LB: mbts + alpha1 crit4, UB: mbts + alpha2 crit4
-    bcaCIalt <- sweep(-crit3[order(2:1),], 2, bts$t0, FUN = '+') # both
+    # bcaCIalt <- sweep(-crit3[order(2:1),], 2, bts$t0, FUN = '+') # both
     ## LB: bts$t0 - alpha2 crit3, UB: bts$t0 - alpha1 crit3 and
@@
     ## return all intervals
-    c(estCI, mbtCI, altCI, bcaCIest, bcaCImbt, bcaCIalt)
+    c(estCI, bcaCIest)
 }
@@
 
+```{r ar = -.4, n = 700}
+n <- 700
+blksize <- 9
+phi <- -.4
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_n.4_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.4_7h,"../Data/Raw/sim_n.4_7h.csv", row.names = FALSE)
+mychk(sim_n.4_7h, target)
+```
+
 ```{r ar = -.2, n = 100}
@@
 mychk(sim_n.2_6h, target)
+```
+
+```{r ar = -.2, n = 700}
+n <- 700
+blksize <- 9
+phi <- -.2
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_n.2_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_n.2_7h,"../Data/Raw/sim_n.2_7h.csv", row.names = FALSE)
+mychk(sim_n.2_7h, target)
 ```
@@
 
+```{r ar = 0, n = 700}
+n <- 700
+blksize <- 9
+phi <- 0
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_0_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_0_7h,"../Data/Raw/sim_0_7h.csv", row.names = FALSE)
+mychk(sim_0_7h, target)
+```
+
 ```{r ar = .2, n = 100}
@@
 mychk(sim_.2_6h, target)
+```
+
+```{r ar = .2, n = 700}
+n <- 700
+blksize <- 9
+phi <- .2
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_.2_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.2_7h,"../Data/Raw/sim_.2_7h.csv", row.names = FALSE)
+mychk(sim_.2_7h, target)
 ```
@@
 ```
+
+```{r ar = .4, n = 700}
+n <- 700
+blksize <- 9
+phi <- .4
+target <- c(0, 1, phi)
+set.seed(6789)
+sim_.4_7h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
+write.csv(sim_.4_7h,"../Data/Raw/sim_.4_7h.csv", row.names = FALSE)
+mychk(sim_.4_7h, target)
+```

### 2023-02-09 Manuscript/manuscript.tex
Manuscript Update

--- 2023-01-26 Manuscript/manuscript.tex
@@
 \begin{abstract}
-Block bootstrapping is a method that can be used for estimating a parameter of a time
-series. It involves splitting a series into blocks (in order to account for the temporal dependence
-factor) and re-sampling the blocks to create many new bootstrapped pseudo-samples of the time series.
-This method becomes more effective as the length of the time series increases. 
-The question that this study seeks to answer is what sample length is necessary for the block
-bootstrap method to be effective in estimating a parameter of a time
-series.
+Block bootstrapping is a method that is useful for estimating a parameter of a time
+series. Theoretically, the method will work perfectly given an infinitely large sample of the time series.
+It is necessary to know how large of a finite sample is required to for block bootstrap estimation to work.
+Before this study, there have been no investigations into this problem in the literature.
+The aim of this study is to answer this question by simulating replications of block bootstrap interval estimations of a parameter of a time series, and recording the rate at which the parameter is recovered by each replicate interval.
+The sample length required for acceptable performance is unsurprisingly found to be dependent on the type of interval construction and the series' level of temporal dependence.
 
@@
 \noindent\sc{Keywords}:
-block bootstrap;
+simulation;
 \end{abstract}
@@
 as econometrics \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}. It can be used for 
-situations in which there is temporal dependence within a population, and the goal is the estimation or testing a hypothesis about a parameter. Assuming that the sample is infinitely 
-large, the method will work perfectly. However, for a finite sample size, the method will 
+situations in which there is temporal dependence within a population, and the goal is to estimate or test a hypothesis about a parameter. Assuming that the sample is infinitely 
+large, the method should work perfectly. However, for a finite sample size, the method may 
 not work as well as expected. In the context of planning an applied 
-statistical procedure, for which a large sample size is not always practical, it may be helpful to know how large the sample must be for the method to work at an acceptable level.
+statistical procedure, for which a large sample size is not always practical, it may be helpful to know how large the sample must be for the method to perform at an acceptable level.
 
-\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from nonparametric bootstrapping are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
-\citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for estimation using the bootstrap method (simple resampling with no blocks involved).
+\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from basic nonparametric bootstrapping (simple resampling with no blocks involved) are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
+\citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for interval estimation using basic nonparametric bootstrapping.
 \citet{goncalves2005bootstrap} found that standard error estimates from block bootstrapping small 
@@
 
-The goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
-is an effective method for estimating a parameter in the context of a time series.
-The method is effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals created from samples of the same size recover the parameter.
-This study will focus on estimating parameters of an AR(1) process with several types of confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} which will be reviewed in Section 2.
+While the aforementioned studies have looked into the necessary sample size for various bootstrap methods, the goal of this study is to find a threshold or range of sample sizes at which block bootstrap
+is an effective method for estimating a parameter specifically in the context of a time series.
+The method can be considered effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals created from samples of the same size recover the parameter.
+This study will focus on estimating parameters of an AR(1) process with two types of confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} which will be reviewed in Section 2.
 
@@
 
-Block bootstrapping is a method that can be used to estimate a parameter of an AR(1) process. Suppose that one wants to estimate a parameter or parameters $\theta$ of an AR(1) process: 
-\[X_{t} = \mu + \epsilon_{t} + \phi*X_{t-1}.\] The first step is to generate a sample of length $n$ from the process.
+Block bootstrapping is a method that can be used to estimate a parameter of serially dependent data.
+Suppose that one wants to estimate a parameter or parameters $\theta$ of a population.
+The first step is to generate a sample of length $n$ from the population.
 An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample.
 A pseudo-estimate $\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample.
-The mean $\bar\theta_n^*$ of many (typically 1000) replicate $\hat\theta_n^*$ can also be computed.
-Lastly, for each $\hat\theta_n^*$, $\delta = \hat\theta_n^* - \hat{\theta}_{n}$ and $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.
+The mean $\bar\theta_n^*$ of many replicate $\hat\theta_n^*$ can also be computed.
+Lastly, for each $\hat\theta_n^*$, $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.
 
 In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the original sample with replacement.
-In the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size.
-The block should be of size $l$ large enough to include time dependence, yet small enough to include some variance.
-As $n$ increases, an ideal $l$ should also increase, but the ratio of $l$ to $n$ should decrease.
+However, in the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size.
+The block should be of size $l$ large enough for each pseudo-sample to exhibit some temporal dependence, yet small enough for there to be some variability between each pseudo-sample.
+Ideally, as $n$ increases, $l$ should also increase, but $l / n$ should decrease.
 To achieve this, $l$ is often assigned a value as a function of $n$.
-A common function that is considered the best by much previous literature is $l = \lceil = n^{1/3} \rceil$.
-\citep{buhlmann1999block} A bootstrapped sample is created by taking a sample of $n / l$ blocks with replacement to create a new pseudo-sample of size $n$.
-The designer of the study can choose whether the blocks overlap or not.
-If the blocks can never overlap, it is called a non-moving block bootstrap.
-In this case, the original sample is split evenly into $n / l$ blocks, and the same number of blocks are sampled with replacement to create a bootstrapped pseudo-sample.
+A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$.
+\citep{buhlmann1999block} The designer of the study can choose whether the blocks overlap or not.
+If the blocks do not overlap, it is called a non-moving block bootstrap.
+In this case, the original sample is split evenly into blocks, which will then be resampled to create new pseudo-samples.
 If the blocks do overlap, it is called a moving block bootstrap.
-$n / l$ samples are taken randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
-$\hat\theta_n^*$ is computed from the pseudo-sample.
+Blocks are resampled randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
+For moving block bootstrap, if $l \vert n$, a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks of size $l$ with replacement to create a new pseudo-sample of size $n$.
+If $l does not divide n$, the pseudo-sample is created by taking a sample of $\lfloor n / l \rfloor$ blocks of size $l$ and one block of size $(n \;\mathrm{mod})\; l$.
+An estimate $\hat\theta_n^*$ is computed from the pseudo-sample.
 This procedure can be repeated many times to create a distribution of $\hat\theta_n^*$.
 
-In this study, 1000 bootstrapped $\hat\theta_n^*$ were created for each simulation.
-Using this distribution of $\hat\theta_n^*$, a $1 - \alpha$/2 \% confidence interval for the parameter can be created.
+In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block bootstrap estimation.
+Using this distribution of $\hat\theta_n^*$, a $1 - \alpha$/2 \% confidence interval for the parameter can be constructed.
 The most simplistic method for constructing this interval is the percentile confidence interval.
@@
 \[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} + z_{0}.\] 
-Where $z_0$ is the quantile function of the proportion of $\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness of ...
+Where $z_0$ is the quantile function of the proportion of $\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness of $\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the original sample computed without the $i^{th}$ block.
 
-	Both of these intervals are good at recovering the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as $n$ increases.
-A potential solution to this issue is to center the intervals around either $\hat{\theta}_{n}$ or $\bar\theta_n^*$.
-To do this, the distribution of $\delta$ or $\delta^*$ should be considered.
-A percentile interval centered around $\hat{\theta}_{n}$ takes the form:
+	Both of these intervals work well when attempting to recover the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as $n$ increases.
+A potential solution to this issue is to center the intervals $\hat{\theta}_{n}$.
+To do this, the distribution $\delta^*$ should be considered.
+A percentile interval centered around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
 \[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]
-A percentile interval centered around $\bar\theta_n^*$ takes the form: 
-\[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\]
-An alternative is an interval of the form:
-\[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] 
-which is equivalent to:
-\[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] 
-and therefore is also equivalent to:
-\[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] 
-Thus, the interval is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.
 
-This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ takes the form:
+%A percentile interval centered around $\bar\theta_n^*$ ($CI_{\bar\theta_n^*}$) takes the form: \[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\] An alternative is an interval of the form: \[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] which is equivalent to: \[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] and therefore is also equivalent to: \[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] Thus, the interval ($CI_{\hat{\theta}_{n}, \bar\theta_n^*}$) is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.
+
+This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the form:
 \[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
-A BCA interval centered around $\bar\theta_n^*$ takes the form: 
-\[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\]
-An alternative is an interval of the form:
-\[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}],\]
+%A BCA interval centered around $\bar\theta_n^*$ ($CI_{BCA, \bar\theta_n^*}$) takes the form: \[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\] An alternative (($CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$) is an interval of the form: \[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}]\]
+
+Thus, there are two types of intervals used for estimation in this study: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
+Note that both of these intervals are centered around $\hat{\theta}_{n}$ and asymmetric.
 
@@
 
-R has a built in function that allows you to simulate an AR(1) process, for which one can set the theoretical $\phi$.
-For the purposes of this study, $\mu$ should be fixed at 0, and the standard deviation of the process $\sigma_{x}$ should be fixed at 1.
-By default, the standard deviation of the error term $\sigma_{\epsilon}$ is 1, so the observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
+Base R has a built in function arima.sim that allows one to simulate an AR(1) process, for which one can set the theoretical $\phi$.
+By default, the mean of the process $\mu$ is 0 and the standard deviation of the error term $\sigma_{\epsilon}$ is 1.
+For the purposes of this study, the standard deviation of the process $\sigma_{x}$ should be controlled at 1.
+The observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
 
-\[X_{t} = \epsilon_{t} + \phi*X_{t-1}.\]
-\[Var(X_{t}) = Var(\epsilon_{t} + \phi*X_{t-1})\]
-\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2*\sigma^2_{x}\]
-\[\sigma^2_{x}(1 - \phi^2) = \sigma^2_{\epsilon}\]
-\[\sigma_{\epsilon} = \sigma_{x}\sqrt{1 - \phi^2}\]
+\[X_{t} = \epsilon_{t} + \phi X_{t-1}.\]
+\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1})\]
+\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x}\]
+\[\sigma^2_{x}(1 - \phi^2) = 1\]
+\[\sigma_{x}\sqrt{1 - \phi^2} = 1\]
 
-The only parameter of the AR(1) process that was varied was $\phi$, as the temporal dependence affects the performance of block bootstrap.
-$\phi$ = 0 (a standard normal distribution), 0.2, and 0.4 were used in this study.
+The experimental factor of this study was $\phi$, as the temporal dependence affects the performance of block bootstrap.
+$\phi = -0.4 -0.2,$ and $0$ (a standard normal distribution)$, 0.2, and 0.4$ were used in this study.
 
 As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process.
-In this study, $\theta$ is composed of the target parameters $\mu$, $\sigma_{x}$, and $\phi$.
-From a sample of length $n$, six block bootstrap 95\% confidence intervals can be constructed for each target parameter: ....
+This method can be simulated with the tsboot function from the boot R package.
+In this study, $\theta$ is composed of the target parameters $\mu = 0$, $\sigma_{x}$, and $\phi$.
+From a sample of length $n$, two types of block bootstrap 95\% confidence intervals can be constructed for each target parameter: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
 
-Each of these 18 intervals either recovers $\theta$ or does not.
-Remember that 95\% of a certain type of 95\% confidence intervals constructed from samples of the same $n$ should recover $\theta$.
-To see if this is approximately the case, one can run 1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers $\theta$ can be recorded.
+Each of these 6 intervals either recovers $\theta$ or does not.
+Remember that 95\% of many of a certain type of 95\% confidence intervals constructed from samples of the same $n$ should recover $\theta$.
+To see if this is generally or approximately the case, one can run 1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers $\theta$ can be recorded.
 
-If $\theta$ is not covered at that $n$, a larger sample size must be necessary. $n = 100, 200, 300, 400, and 500$ were used in this study.
+If $\theta$ is not covered at that $n$, a larger sample size must be necessary. $n = $100, 200, 300, 400, and 500, 600, 700 were used in this study.
 
@@
   \centering
+  \includegraphics[width=\textwidth]{figures/plot_n.4}
+  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as $n = 100$.
+$CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as $n = 400$.
+$CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$.
+$CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, and this is true as low as $n = 200$.
+$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear pattern of deterioration of coverage.}
+  \label{fig:plot_n.4}
+\end{figure}
+
+\begin{figure}[tbp]
+\caption{}
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_n.2}
+  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as $n = 100$.
+Both intervals seem to cover $\sigma$ generally well, although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
+$CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.
+$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear coverage deterioration trend as $n$ increases.}
+  \label{fig:plot_n.2}
+\end{figure}
+
+\begin{figure}[tbp]
+\caption{}
+  \centering
   \includegraphics[width=\textwidth]{figures/plot_0}
-  \caption{At $\phi = 0$, all intervals covered $\mu$ correctly at $n = 500$.
-All but three intervals seem to cover $\phi$ generally well for $n = 300$.
-The alternate percentile interval slightly under-covers $\phi$ for all sample lengths observed.
-The BCA interval centered around $\hat{\theta}_{n}$ significantly under-covers $\phi$ and the percentile interval centered around $\bar\theta_n^*$ over-covers $\phi$.
-All intervals seem to cover $\sigma$ generally well for n = 500 except for the $\hat{\theta}_{n}$-centered BCA interval, which slightly under-covers $\sigma$ for all sample lengths observed, and the  $\bar\theta_n^*$-centered BCA interval, which also under-covers $\sigma$.}
+  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as $n = 500$.
+$CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as $n = 400$.
+$CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$.
+$CI_{\hat{\theta}_{n}}$ seems to cover $\phi$ generally well at $n = 400$, but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the method's performance seems to improve as $n$ increases.}
   \label{fig:plot_0}
@@
   \includegraphics[width=\textwidth]{figures/plot_.2}
-  \caption{At $\phi = .2$, all intervals covered $\mu$ correctly at $n = 300$ and $n = 400$.
-The alternate percentile interval and the $\hat{\theta}_{n}$-centered percentile interval cover $\phi$ well at $n = 500$.
-The $\bar\theta_n^*$-centered BCA interval slightly under-covers $\phi$ for all sample lengths observed.
-The alternate BCA interval under-covers $\phi$, and its performance deteriorates as $n$ increases, as does the $\bar\theta_n^*$-centered percentile interval but with lower coverage rates and more noticeable deterioration.
-The $\hat{\theta}_{n}$-centered BCA interval significantly under-covers $\phi$, although there is no clear deterioration.}
+  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as $n = 300$.
+Both intervals seem to cover $\sigma$ generally well, although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
+$CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.
+$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no clear coverage deterioration trend as $n$ increases.}
   \label{fig:plot_.2}
@@
   \includegraphics[width=\textwidth]{figures/plot_.4}
-  \caption{At $\phi = .4$,}
+  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well as low as $n = 400$.
+$CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low as $n = 400$.
+$CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear sign of coverage deterioration, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$.
+$CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.
+$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear coverage deterioration trend as $n$ increases.}
   \label{fig:plot_.4}
 \end{figure}
+
+Only $CI_{\hat{\theta}_{n}}$ managed to solve the deterioration problem with respect to recovering $\phi$, indicating that this interval should be used as opposed to $CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$.
 
@@
 
-This study finds that as the AR coefficient increases, the sample size necessary for effective block bootstrap estimation must be larger.
-When implementing the block bootstrap method to estimate the mean or variance of an autoregressive process, the non-moving method and moving method perform about the same.
-However, when estimating the AR(1) coefficient, the non-moving method performs noticeably worse than the moving method, which still covers the coefficient poorly when theta is greater than 0.
-Whereas the performance improves as sample length increases when the target is the mean or variance, the performance decays as sample length increases when the target is the AR(1) coefficient.
+The motivation for the study is the idea that block bootstrap procedure will perfectly estimate a parameter of a time series given an infinitely large sample.
+The goal for this study was to find what is a good enough finite sample length for block bootstrap estimation to recover the parameter of a time series at an acceptable rate.
+Assuming that $CI_{\hat{\theta}_{n}}$ is used, The results of this study suggest that even for estimating $\mu$, an $n$ of around 500 may be necessary if $\phi$ is unknown.
+An $n$ of around 400 may be necessary to estimate $\sigma$ is $\phi$ is unknown.
+If $\phi$ is already known, a lesser $n$ may be adequate to estimate these parameters.
+Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
+This information could prove to be useful for researching using block bootstrap estimation of time series in domains such as econometrics.
+Future studies could investigate the sample size needed to estimate or test an hypothesis about other forms of serially dependent data such as an MA process.
 

### 2023-02-10 Manuscript/manuscript.tex
opening paragraph

@@
 \usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
+\usepackage{hyperref, url}
 \hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
@@
 \begin{abstract}
-Block bootstrapping is a method that is useful for estimating a parameter of a time
+Block bootstrap is a method that is useful for estimating a parameter of a time
 series. Theoretically, the method will work perfectly given an infinitely large sample of the time series.
@@
 
+\jy{Practice my writing tips on latex (e.g., keep line width under 80; use
+  double blank lines to separate paragraphs; etc.):
+\url{https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html}}
+
 \section{Introduction}
@@
 
-Block bootstrapping is a widely used method in Statistics. The concept for block 
-bootstrapping was developed independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
-\citet{kunsch1989jackknife}. \citet{radovanov2014comparison} It has been applied to a variety of 
-different domains such 
-as econometrics \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}. It can be used for 
-situations in which there is temporal dependence within a population, and the goal is to estimate or test a hypothesis about a parameter. Assuming that the sample is infinitely 
-large, the method should work perfectly. However, for a finite sample size, the method may 
-not work as well as expected. In the context of planning an applied 
-statistical procedure, for which a large sample size is not always practical, it may be helpful to know how large the sample must be for the method to perform at an acceptable level.
+Block bootstrap is an important tool for constructing confidence intervals when
+making inferences about dependent data. Early ideas were developed independently
+by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
+\citet{kunsch1989jackknife}. % \citet{radovanov2014comparison}
+It has been applied to a variety of different domains such 
+as econometrics \citep{mackinnon2006bootstrap} and meteorology
+\citep{varga2017generalised}. It is particularly useful for serially dependent
+data when the serial dependence is not specified or of not primary interest.
+As the sample size goes to infinity, block bootstrap confidence intervals are
+expected to have coverage rates matching their nominal levels. For finite sample
+sizes, however, a natural question is, how large a sample size is large enough
+for block bootstrap confidence intervals to have the desired coverage rates?
 
-\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from basic nonparametric bootstrapping (simple resampling with no blocks involved) are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
-\citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for interval estimation using basic nonparametric bootstrapping.
-\citet{goncalves2005bootstrap} found that standard error estimates from block bootstrapping small 
+\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from basic nonparametric bootstrap (simple resampling with no blocks involved) are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
+\citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for interval estimation using basic nonparametric bootstrap.
+\citet{goncalves2005bootstrap} found that standard error estimates from block bootstrap small 
 samples may be significantly more accurate than inference from closed-form asymptotic estimates.
@@
 
-%At the base level, we are block-bootstrapping an auto-regressive process with true mean 0, and some AR(1) coefficient.
+%At the base level, we are block-bootstrap an auto-regressive process with true mean 0, and some AR(1) coefficient.
 
-%Bootstrapping is the procedure of creating new pseudo-samples of the same size by resampling observations with replacement from the original sample. Basic bootstrapping works well for samples
+%Bootstrap is the procedure of creating new pseudo-samples of the same size by resampling observations with replacement from the original sample. Basic bootstrap works well for samples
 % that are do not have a dependence factor.
@@
 They will be discussed later in a review of the block bootstrap method.
-For the purposes of this study (in which the true parameters are known), in order to establish whether or not the method is effective, the block bootstrapping of a simulated sample can be replicated many times, and the proportion of confidence intervals that recover the true known parameter (coverage rate) is recorded.
-The goal of this is simply to observe how successful the block bootstrapping procedure is at estimating a parameter.
+For the purposes of this study (in which the true parameters are known), in order to establish whether or not the method is effective, the block bootstrap of a simulated sample can be replicated many times, and the proportion of confidence intervals that recover the true known parameter (coverage rate) is recorded.
+The goal of this is simply to observe how successful the block bootstrap procedure is at estimating a parameter.
 The key variable being observed was, the sample length (n).
-It is known that as n increases, block bootstrapping should become a more accurate and precise method for estimation(the coverage rates will approach the theoretical confidence level and the interval widths will decrease).
+It is known that as n increases, block bootstrap should become a more accurate and precise method for estimation(the coverage rates will approach the theoretical confidence level and the interval widths will decrease).
 The question is what is the minimum sample length necessary to reach a coverage rate of 1 - $\alpha$/2 \%.
@@
 
-%In order to solve the question of what sample length is necessary for effective block bootstrapping while still accounting for all these factors, the simulations were repeated for different variations of the MA coefficient, target parameter, and non-moving vs moving method.
+%In order to solve the question of what sample length is necessary for effective block bootstrap while still accounting for all these factors, the simulations were repeated for different variations of the MA coefficient, target parameter, and non-moving vs moving method.
 For each of these variations, results for block bootstrap estimation of mean, MA coefficient, and standard deviation were recorded for a wide range of sample length.
@@
 
-Block bootstrapping is a method that can be used to estimate a parameter of serially dependent data.
+Block bootstrap is a method that can be used to estimate a parameter of serially dependent data.
 Suppose that one wants to estimate a parameter or parameters $\theta$ of a population.

### 2023-02-14 Manuscript/manuscript.tex
Small Change

@@
 To achieve this, $l$ is often assigned a value as a function of $n$.
-A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$.
-\citep{buhlmann1999block} The designer of the study can choose whether the blocks overlap or not.
+A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}.
+The designer of the study can choose whether the blocks overlap or not.
 If the blocks do not overlap, it is called a non-moving block bootstrap.
@@
 
-\[X_{t} = \epsilon_{t} + \phi X_{t-1}.\]
-\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1})\]
-\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x}\]
-\[\sigma^2_{x}(1 - \phi^2) = 1\]
-\[\sigma_{x}\sqrt{1 - \phi^2} = 1\]
+\[X_{t} = \epsilon_{t} + \phi X_{t-1};\]
+\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1});\]
+\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\]
+\[\sigma^2_{x}(1 - \phi^2) = 1;\]
+\[\sigma_{x}\sqrt{1 - \phi^2} = 1.\]
 

### 2023-02-16 Manuscript/manuscript.tex
Line Width

@@
 It is necessary to know how large of a finite sample is required to for block bootstrap estimation to work. 
-Before this study, there have been no investigations into this problem in the literature.
-The aim of this study is to answer this question by simulating replications of block bootstrap interval estimations of a parameter of a time series, and recording the rate at which the parameter is recovered by each replicate interval.
-The sample length required for acceptable performance is unsurprisingly found to be dependent on the type of interval construction and the series' level of temporal dependence.
+Before this study, there have been no investigations into this problem in the literature. The aim of this study 
+is to answer this question by simulating replications of block bootstrap interval estimations of a parameter of a time series, 
+and recording the rate at which the parameter is recovered by each replicate interval. 
+The sample length required for acceptable performance is unsurprisingly found to be dependent 
+on the type of interval construction and the series' level of temporal dependence.
 
@@
 
-\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from basic nonparametric bootstrap (simple resampling with no blocks involved) are more accurate than t-intervals for larger sample sizes, they are less accurate for smaller sample sizes.
-\citet{nevitt2001performance} find that a sample size of 200-1000 is usually sufficient for interval estimation using basic nonparametric bootstrap.
+\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from basic nonparametric bootstrap 
+(simple resampling with no blocks involved) are more accurate than t-intervals for larger sample sizes, 
+they are less accurate for smaller sample sizes. \citet{nevitt2001performance} find that a sample size of 
+200-1000 is usually sufficient for interval estimation using basic nonparametric bootstrap.
 \citet{goncalves2005bootstrap} found that standard error estimates from block bootstrap small 
@@
 
-While the aforementioned studies have looked into the necessary sample size for various bootstrap methods, the goal of this study is to find a threshold or range of sample sizes at which block bootstrap
+While the aforementioned studies have looked into the necessary sample size for various bootstrap methods, 
+the goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
 is an effective method for estimating a parameter specifically in the context of a time series. 
-The method can be considered effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals created from samples of the same size recover the parameter.
-This study will focus on estimating parameters of an AR(1) process with two types of confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} which will be reviewed in Section 2.
-
-%At the base level, we are block-bootstrap an auto-regressive process with true mean 0, and some AR(1) coefficient.
-
-%Bootstrap is the procedure of creating new pseudo-samples of the same size by resampling observations with replacement from the original sample. Basic bootstrap works well for samples
-% that are do not have a dependence factor.
-However, for a time series such as an auto-regressive or moving-average process, a different procedure is required to account for the time dependence.
-In such a situation, instead of resampling observations, blocks of the original sample can be resampled (these blocks must be of a certain length by which the sample length is divisible) to create a pseudo-sample.
-Point estimates of a parameter calculated from many block bootstrapped pseudo-samples are then used to create a distribution to create an interval estimation of the parameter.
-
-%In this experiment, the mean, auto-correlation function (with a maximum lag of 1), and variance of a 1000 block-bootstrapped time series samples are computed, and 95\% confidence intervals of these parameters is created.
-
-%The various ways which these intervals can be constructed are described in \citet{diciccio1996bootstrap} and \citet{rice2006mathematical}.
-They will be discussed later in a review of the block bootstrap method.
-For the purposes of this study (in which the true parameters are known), in order to establish whether or not the method is effective, the block bootstrap of a simulated sample can be replicated many times, and the proportion of confidence intervals that recover the true known parameter (coverage rate) is recorded.
-The goal of this is simply to observe how successful the block bootstrap procedure is at estimating a parameter.
-The key variable being observed was, the sample length (n).
-It is known that as n increases, block bootstrap should become a more accurate and precise method for estimation(the coverage rates will approach the theoretical confidence level and the interval widths will decrease).
-The question is what is the minimum sample length necessary to reach a coverage rate of 1 - $\alpha$/2 \%.
-
-% In this experiment, there are certain variables that are expected to affect the performance of block bootstrap.
-As the the time dependence (AR or MA coefficient) of the time series increases, we expect the coverage rates of the confidence intervals to decrease.The coverage rates are also affected by the size of the blocks - more specifically,how the size of the blocks (l) relates to the size of the time series (n) - and whether or not they overlap.
-It is known that as the size of the time series increases, the optimal block length should increase, and the ratio of the block length to the time series length should decrease.
-l = n$^{1/3}$ is typically considered the optimal block length according to asymptotic theory.
-\citep{buhlmann1999block} Therefore, simulations in this study were conducted using this optimal function of l = n$^{1/3}$.
-
-%In order to solve the question of what sample length is necessary for effective block bootstrap while still accounting for all these factors, the simulations were repeated for different variations of the MA coefficient, target parameter, and non-moving vs moving method.
-For each of these variations, results for block bootstrap estimation of mean, MA coefficient, and standard deviation were recorded for a wide range of sample length.
+The method can be considered effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals 
+created from samples of the same size recover the parameter. This study will focus on estimating parameters of an 
+AR(1) process with two types of block bootstrap confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} 
+which is reviewed in Section 2. Section 3 offers an explanation of the simulation design and results. 
+Section 4 discusses the results and how these findings could be useful.
 
@@
 
-Block bootstrap is a method that can be used to estimate a parameter of serially dependent data.
-Suppose that one wants to estimate a parameter or parameters $\theta$ of a population.
-The first step is to generate a sample of length $n$ from the population.
-An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample.
-A pseudo-estimate $\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample.
-The mean $\bar\theta_n^*$ of many replicate $\hat\theta_n^*$ can also be computed.
-Lastly, for each $\hat\theta_n^*$, $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.
+Block bootstrap is a method that can be used to estimate a parameter of serially dependent data. Suppose that one wants to 
+estimate a parameter or parameters $\theta$ of a population. The first step is to generate a sample of length $n$ from the population. 
+An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate $\hat\theta_n^*$ 
+can be computed from a bootstrapped pseudo-sample. The mean $\bar\theta_n^*$ of many replicate $\hat\theta_n^*$ 
+can also be computed. Lastly, for each $\hat\theta_n^*$, $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.
 
-In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the original sample with replacement.
-However, in the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size.
-The block should be of size $l$ large enough for each pseudo-sample to exhibit some temporal dependence, yet small enough for there to be some variability between each pseudo-sample.
-Ideally, as $n$ increases, $l$ should also increase, but $l / n$ should decrease.
-To achieve this, $l$ is often assigned a value as a function of $n$.
-A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}.
-The designer of the study can choose whether the blocks overlap or not.
-If the blocks do not overlap, it is called a non-moving block bootstrap.
+In basic bootstrap procedure, the new pseudo-sample of size $n$ would be created by simply resampling observations from 
+the original sample with replacement. However, in the case of a time series, in order to account for the temporal dependence, 
+the time series can be split into blocks, typically of the same size. The block should be of size $l$ large enough for each pseudo-sample
+ to exhibit some temporal dependence, yet small enough for there to be some variability between each pseudo-sample. 
+ Ideally, as $n$ increases, $l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is often assigned 
+ a value as a function of $n$. A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}. 
+ The designer of the study can choose whether the blocks overlap or not. If the blocks do not overlap, it is called a non-moving block bootstrap. 
  In this case, the original sample is split evenly into blocks, which will then be resampled to create new pseudo-samples. 
-If the blocks do overlap, it is called a moving block bootstrap.
-Blocks are resampled randomly from the original sample, but they do not have to be from a set of evenly spaced blocks.
-For moving block bootstrap, if $l \vert n$, a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks of size $l$ with replacement to create a new pseudo-sample of size $n$.
-If $l does not divide n$, the pseudo-sample is created by taking a sample of $\lfloor n / l \rfloor$ blocks of size $l$ and one block of size $(n \;\mathrm{mod})\; l$.
-An estimate $\hat\theta_n^*$ is computed from the pseudo-sample.
+ If the blocks do overlap, it is called a moving block bootstrap. Blocks are resampled randomly from the original sample, 
+ but they do not have to be from a set of evenly spaced blocks. For moving block bootstrap, if $l \vert n$, a bootstrapped 
+ pseudo-sample is created by taking a sample of $n / l$ blocks of size $l$ with replacement to create a new pseudo-sample of size $n$. 
+ If $l does not divide n$, the pseudo-sample is created by taking a sample of $\lfloor n / l \rfloor$ blocks of size $l$ 
+ and one block of size $(n \;\mathrm{mod})\; l$. An estimate $\hat\theta_n^*$ is computed from the pseudo-sample. 
  This procedure can be repeated many times to create a distribution of $\hat\theta_n^*$.
 
-In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block bootstrap estimation.
-Using this distribution of $\hat\theta_n^*$, a $1 - \alpha$/2 \% confidence interval for the parameter can be constructed.
+In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block bootstrap estimation. Using this distribution of 
+$\hat\theta_n^*$, a $1 - \alpha$/2 \% confidence interval for the parameter can be constructed. 
 The most simplistic method for constructing this interval is the percentile confidence interval. 
@@
 \[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} + z_{0}.\] 
-Where $z_0$ is the quantile function of the proportion of $\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness of $\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the original sample computed without the $i^{th}$ block.
+Where $z_0$ is the quantile function of the proportion of $\hat\theta_n^* < \bar\theta_n^*$, 
+and $a$ is the skewness of $\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the original sample computed without the $i^{th}$ block.
 
-	Both of these intervals work well when attempting to recover the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as $n$ increases.
-A potential solution to this issue is to center the intervals $\hat{\theta}_{n}$.
-To do this, the distribution $\delta^*$ should be considered.
-A percentile interval centered around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
+Both of these intervals work well when attempting to recover the mean and standard deviation of a temporally dependent process, 
+but their coverage of the temporal dependence deteriorates as $n$ increases. A potential solution to this issue is to center the intervals 
+$\hat{\theta}_{n}$. To do this, the distribution $\delta^*$ should be considered. A percentile interval 
+centered around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
 \[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]
@@
 
-Thus, there are two types of intervals used for estimation in this study: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
-Note that both of these intervals are centered around $\hat{\theta}_{n}$ and asymmetric.
+Thus, there are two types of intervals that can be constructed for block bootstrap estimation in this study: 
+$CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$. Note that both of these intervals are centered around $\hat{\theta}_{n}$ and asymmetric.
 
@@
 As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process. 
-This method can be simulated with the tsboot function from the boot R package.
-In this study, $\theta$ is composed of the target parameters $\mu = 0$, $\sigma_{x}$, and $\phi$.
-From a sample of length $n$, two types of block bootstrap 95\% confidence intervals can be constructed for each target parameter: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
+This method can be simulated with the tsboot function from the boot R package. In this study, $\theta$ is composed of the target 
+parameters $\mu = 0$, $\sigma_{x}$, and $\phi$. From a sample of length $n$, two types of block bootstrap 95\% confidence intervals 
+can be constructed for each target parameter: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
 
-Each of these 6 intervals either recovers $\theta$ or does not.
-Remember that 95\% of many of a certain type of 95\% confidence intervals constructed from samples of the same $n$ should recover $\theta$.
-To see if this is generally or approximately the case, one can run 1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers $\theta$ can be recorded.
+Each of these 6 intervals either recovers $\theta$ or does not. Remember that 95\% of many of a certain type of 95\% confidence intervals 
+constructed from samples of the same $n$ should recover $\theta$. To see if this is generally or approximately the case, one can run 
+1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers 
+$\theta$ can be recorded. The coverage rate is, of course, a point estimate of a proportion, so a 95\% confidence interval of this coverage proportion 
+(with $n_{CI} = 1000$) can be constructed, and if the proportion .95 is included in the interval, the block bootstrap method is likely working well.
 
 If $\theta$ is not covered at that $n$, a larger sample size must be necessary. $n = $100, 200, 300, 400, and 500, 600, 700 were used in this study. 
+Remember that the goal is to find the smallest $n$ which is sufficient for proper coverage.
 
@@
   \includegraphics[width=\textwidth]{figures/plot_n.4}
-  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as $n = 100$.
-$CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as $n = 400$.
-$CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$.
-$CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, and this is true as low as $n = 200$.
-$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear pattern of deterioration of coverage.}
+  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as $n = 100$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as 
+  low as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can 
+  expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, 
+  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear pattern of deterioration of coverage.}
   \label{fig:plot_n.4}
@@
   \includegraphics[width=\textwidth]{figures/plot_n.2}
-  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as $n = 100$.
-Both intervals seem to cover $\sigma$ generally well, although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
-$CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.
-$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear coverage deterioration trend as $n$ increases.}
+  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as $n = 100$. Both intervals seem to cover $\sigma$ generally well, 
+  although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
+  and this is true as low as $n = 200$.  $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear coverage deterioration trend as $n$ increases.}
   \label{fig:plot_n.2}
@@
   \includegraphics[width=\textwidth]{figures/plot_0}
-  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as $n = 500$.
-$CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as $n = 400$.
-$CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$.
-$CI_{\hat{\theta}_{n}}$ seems to cover $\phi$ generally well at $n = 400$, but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the method's performance seems to improve as $n$ increases.}
+  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as $n = 500$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as 
+  $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, 
+  so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ seems to cover 
+  $\phi$ generally well at $n = 400$, but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the method's performance seems to improve as $n$ increases.}
   \label{fig:plot_0}
@@
   \includegraphics[width=\textwidth]{figures/plot_.2}
-  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as $n = 300$.
-Both intervals seem to cover $\sigma$ generally well, although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
-$CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.
-$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no clear coverage deterioration trend as $n$ increases.}
+  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as $n = 300$. Both intervals seem to cover $\sigma$ generally well, 
+  although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
+  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no clear coverage deterioration trend as $n$ increases.}
   \label{fig:plot_.2}
@@
   \includegraphics[width=\textwidth]{figures/plot_.4}
-  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well as low as $n = 400$.
-$CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low as $n = 400$.
-$CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear sign of coverage deterioration, so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$.
-$CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.
-$CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear coverage deterioration trend as $n$ increases.}
+  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well as low as $n = 400$. $CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low as $n = 400$. 
+  $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear sign of coverage deterioration, so one can expect that increasing $n$ 
+  will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
+  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear coverage deterioration trend as $n$ increases.}
   \label{fig:plot_.4}
@@
 
-Only $CI_{\hat{\theta}_{n}}$ managed to solve the deterioration problem with respect to recovering $\phi$, indicating that this interval should be used as opposed to $CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$.
+Only $CI_{\hat{\theta}_{n}}$ managed to solve the deterioration problem with respect to recovering $\phi$, indicating that this interval 
+should be used as opposed to $CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$. As expected, a higher $\phi$ demands a 
+larger $n$ to estimate all parameters, but a negative $\phi$ may only require a lesser $n$. For example, for both $\phi = 0.2$ and $0.4$, 
+$n = 100$ was sufficient to recover $\mu$ at a rate of approximately 95\%.
 
@@
 The motivation for the study is the idea that block bootstrap procedure will perfectly estimate a parameter of a time series given an infinitely large sample. 
-The goal for this study was to find what is a good enough finite sample length for block bootstrap estimation to recover the parameter of a time series at an acceptable rate.
-Assuming that $CI_{\hat{\theta}_{n}}$ is used, The results of this study suggest that even for estimating $\mu$, an $n$ of around 500 may be necessary if $\phi$ is unknown.
-An $n$ of around 400 may be necessary to estimate $\sigma$ is $\phi$ is unknown.
-If $\phi$ is already known, a lesser $n$ may be adequate to estimate these parameters.
-Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
+The goal for this study was to find what is a good enough finite sample length for block bootstrap estimation to recover the parameter of a 
+time series at an acceptable rate. Assuming that $CI_{\hat{\theta}_{n}}$ is used (as it was found to work better overall, especially when estimation $\phi$), 
+the results of this study suggest that even for estimating $\mu$, an $n$ of around 500 may be necessary if $\phi$ is unknown. 
+An $n$ of around 400 may be necessary to estimate $\sigma$ is $\phi$ is unknown. If $\phi$ is already known, 
+a lesser $n$ may be adequate to estimate these parameters. When $\phi$ was negative, 
+a $n$ of around 100 was sufficient to estimate $\mu$. However, in real world applications, $\phi$ is more commonly found to be positive, 
+so a larger $n$ is more likely to be necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary. 
 This information could prove to be useful for researching using block bootstrap estimation of time series in domains such as econometrics. 
-Future studies could investigate the sample size needed to estimate or test an hypothesis about other forms of serially dependent data such as an MA process.
+Future studies could investigate if there are types of block bootstrap intervals that can be constructed that 
+would more appropriate recover the parameters of a time series. One could also investigate the $n$ needed to 
+make inferences about other forms of serially dependent data such as an MA process.
 

### 2023-02-23 Manuscript/manuscript.tex
2/16 Notes
commented on line width
Manuscript Update

@@
 \usepackage{hyperref, url}
-\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
+\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor =
+  blue}
 \usepackage{natbib}
@@
 
-\title{Sample Length at Which Block Bootstrapping is Effective for Estimation of Parameter of Time Series}
+\title{Sample Length at Which Block Bootstrapping is Effective for Estimation
+  of Parameter of Time Series}
 
@@
 Block bootstrap is a method that is useful for estimating a parameter of a time
-series. Theoretically, the method will work perfectly given an infinitely large sample of the time series.
-It is necessary to know how large of a finite sample is required to for block bootstrap estimation to work. 
-Before this study, there have been no investigations into this problem in the literature. The aim of this study 
-is to answer this question by simulating replications of block bootstrap interval estimations of a parameter of a time series, 
-and recording the rate at which the parameter is recovered by each replicate interval. 
-The sample length required for acceptable performance is unsurprisingly found to be dependent 
-on the type of interval construction and the series' level of temporal dependence.
+series. Theoretically, the method will work perfectly given an infinitely
+large sample of the time series. It is necessary to know how large of a finite
+sample is required for block bootstrap estimation to work. Before this study,
+there have been no investigations into this problem within the literature. The
+aim of this study is to answer this question by simulating replications of
+block bootstrap interval estimations of a parameter of a time series, and
+recording the rate at which the parameter is recovered by each replicate
+interval. The sample length required for acceptable performance is
+unsurprisingly found to be dependent on the type of interval construction and
+the series' level of temporal dependence.
 
@@
   double blank lines to separate paragraphs; etc.):
-\url{https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html}}
+  \url{
+https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html}}
+
+\jy{turn on the column number mode of your editor. Keep the width to under 80.}
 
@@
 Block bootstrap is an important tool for constructing confidence intervals when
-making inferences about dependent data. Early ideas were developed independently
-by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
+making inferences about dependent data. Early ideas were developed
+independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
 \citet{kunsch1989jackknife}. % \citet{radovanov2014comparison}
@@
 As the sample size goes to infinity, block bootstrap confidence intervals are
-expected to have coverage rates matching their nominal levels. For finite sample
-sizes, however, a natural question is, how large a sample size is large enough
-for block bootstrap confidence intervals to have the desired coverage rates?
+expected to have coverage rates matching their nominal levels. For finite
+sample sizes, however, a natural question is, how large a sample size is large
+enough for block bootstrap confidence intervals to have the desired coverage
+rates?
 
-\citet{hesterberg2015teachers} notes that while percentile-based confidence intervals from basic nonparametric bootstrap 
-(simple resampling with no blocks involved) are more accurate than t-intervals for larger sample sizes, 
-they are less accurate for smaller sample sizes. \citet{nevitt2001performance} find that a sample size of 
-200-1000 is usually sufficient for interval estimation using basic nonparametric bootstrap.
-\citet{goncalves2005bootstrap} found that standard error estimates from block bootstrap small 
-samples may be significantly more accurate than inference from closed-form asymptotic estimates. 
-That study focused on the estimation of a coefficient parameter within the context of linear regression. 
-Still, the block bootstrap percentile confidence intervals under-covered the parameter even for n = 1024.
+\citet{hesterberg2015teachers} notes that while percentile-based confidence
+intervals from basic nonparametric bootstrap (simple resampling with no blocks
+involved) are more accurate than t-intervals for larger sample sizes, they are
+less accurate for smaller sample sizes. \citet{nevitt2001performance} find
+that a sample size of 200-1000 is usually sufficient for interval estimation
+using basic nonparametric bootstrap. \citet{goncalves2005bootstrap} found that
+standard error estimates from block bootstrap small samples may be
+significantly more accurate than inference from closed-form asymptotic
+estimates. That study focused on the estimation of a coefficient parameter
+within the context of linear regression. Still, the block bootstrap percentile
+confidence intervals under-covered the parameter even for n = 1024.
 
-While the aforementioned studies have looked into the necessary sample size for various bootstrap methods, 
-the goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
-is an effective method for estimating a parameter specifically in the context of a time series. 
-The method can be considered effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals 
-created from samples of the same size recover the parameter. This study will focus on estimating parameters of an 
-AR(1) process with two types of block bootstrap confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} 
-which is reviewed in Section 2. Section 3 offers an explanation of the simulation design and results. 
-Section 4 discusses the results and how these findings could be useful.
+While the aforementioned studies have looked into the necessary sample size
+for various bootstrap methods to make inferences about various types of data,
+the goal of this study is to find a threshold or range of sample sizes at
+which block bootstrap is an effective method for estimating a parameter
+specifically in the context of a time series. The method can be considered
+effective if the rate at which confidence intervals created from samples of
+the same size recover the parameter is approximately equal to the nominal
+confidence level. This study will focus on estimating parameters of an AR(1)
+process with two types of block bootstrap confidence intervals from the
+literature \citep{diciccio1996bootstrap} \citep{rice2006mathematical}. How
+these intervals are constructed as well as the general procedure for block
+bootstrap parameter estimation is reviewed in Section 2. Section 3 offers an
+explanation of the simulation design and results. Section 4 discusses the main
+takeaways from the results, how these findings could be useful, and possible
+future explorations.
 
@@
 
-Block bootstrap is a method that can be used to estimate a parameter of serially dependent data. Suppose that one wants to 
-estimate a parameter or parameters $\theta$ of a population. The first step is to generate a sample of length $n$ from the population. 
-An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate $\hat\theta_n^*$ 
-can be computed from a bootstrapped pseudo-sample. The mean $\bar\theta_n^*$ of many replicate $\hat\theta_n^*$ 
-can also be computed. Lastly, for each $\hat\theta_n^*$, $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.
+Block bootstrap is a method that can be used to estimate a parameter of
+serially dependent data. Suppose that one wants to estimate a parameter or
+parameters $\theta$ of a population. The first step is to generate a sample of
+length $n$ from the population. An estimate of the parameter
+$\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate
+$\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample. The mean
+$\bar\theta_n^*$ of many replicate $\hat\theta_n^*$ can also be computed.
+Lastly, for each $\hat\theta_n^*$, $\delta^* = \hat\theta_n^* -
+\bar\theta_n^*$ can be computed.
 
-In basic bootstrap procedure, the new pseudo-sample of size $n$ would be created by simply resampling observations from 
-the original sample with replacement. However, in the case of a time series, in order to account for the temporal dependence, 
-the time series can be split into blocks, typically of the same size. The block should be of size $l$ large enough for each pseudo-sample
- to exhibit some temporal dependence, yet small enough for there to be some variability between each pseudo-sample. 
- Ideally, as $n$ increases, $l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is often assigned 
- a value as a function of $n$. A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}. 
- The designer of the study can choose whether the blocks overlap or not. If the blocks do not overlap, it is called a non-moving block bootstrap. 
- In this case, the original sample is split evenly into blocks, which will then be resampled to create new pseudo-samples. 
- If the blocks do overlap, it is called a moving block bootstrap. Blocks are resampled randomly from the original sample, 
- but they do not have to be from a set of evenly spaced blocks. For moving block bootstrap, if $l \vert n$, a bootstrapped 
- pseudo-sample is created by taking a sample of $n / l$ blocks of size $l$ with replacement to create a new pseudo-sample of size $n$. 
- If $l does not divide n$, the pseudo-sample is created by taking a sample of $\lfloor n / l \rfloor$ blocks of size $l$ 
- and one block of size $(n \;\mathrm{mod})\; l$. An estimate $\hat\theta_n^*$ is computed from the pseudo-sample. 
- This procedure can be repeated many times to create a distribution of $\hat\theta_n^*$.
+In basic bootstrap procedure, the new pseudo-sample of size $n$ would be
+created by simply resampling observations from the original sample with
+replacement. However, in the case of a time series, in order to account for
+the temporal dependence, the time series can be split into blocks, typically
+of the same size. The block should be of size $l$ large enough for each
+pseudo-sample to exhibit some temporal dependence, yet small enough for there
+to be some variability between each pseudo-sample. Ideally, as $n$ increases,
+$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
+often assigned a value as a function of $n$. A common function that is
+considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
+\citep{buhlmann1999block}. The designer of the study can choose whether the
+blocks overlap or not. If the blocks do not overlap, it is called a non-moving
+block bootstrap. In this case, the original sample is split evenly into
+blocks, which will then be resampled to create new pseudo-samples. If the
+blocks do overlap, it is called a moving block bootstrap. Blocks are resampled
+randomly from the original sample, but they do not have to be from a set of
+evenly spaced blocks. For moving block bootstrap, if $l \vert n$, a
+bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks of
+size $l$ with replacement to create a new pseudo-sample of size $n$. If
+$l does not divide n$, the pseudo-sample is created by taking a sample of
+$\lfloor n / l \rfloor$ blocks of size $l$ and one block of size
+$(n \;\mathrm{mod})\; l$. An estimate $\hat\theta_n^*$ is computed from the
+pseudo-sample. This procedure can be repeated many times to create a
+distribution of $\hat\theta_n^*$.
 
-In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block bootstrap estimation. Using this distribution of 
-$\hat\theta_n^*$, a $1 - \alpha$/2 \% confidence interval for the parameter can be constructed. 
-The most simplistic method for constructing this interval is the percentile confidence interval. 
-For a parameter $\theta$, the percentile $1 - \alpha$/2 \% confidence interval takes the form: 
+In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block
+bootstrap estimation. Using this distribution of $\hat\theta_n^*$, a
+$1 - \alpha$/2 \% confidence interval for the parameter can be constructed. 
+The most simplistic method for constructing this interval is the percentile
+confidence interval. For a parameter $\theta$, the percentile $1 - \alpha$/2
+\% confidence interval takes the form: 
 \[ [\hat\theta_{n, \alpha/2}^*, \hat\theta_{n, 1 - \alpha/2}^*].\] 
@@
 \[ [\hat\theta_{n, \alpha_1}^*,\hat\theta_{n, \alpha_2}^*].\] 
-$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and $z_{2}$, respectively, where:
-\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} + z_{0}\] and
-\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} + z_{0}.\] 
-Where $z_0$ is the quantile function of the proportion of $\hat\theta_n^* < \bar\theta_n^*$, 
-and $a$ is the skewness of $\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the original sample computed without the $i^{th}$ block.
+$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
+$z_{2}$, respectively, where:
+\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
+z_{0}\] and
+\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
+z_{0}.\] 
+Where $z_0$ is the quantile function of the proportion of
+$\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness of
+$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
+original sample computed without the $i^{th}$ block.
 
-Both of these intervals work well when attempting to recover the mean and standard deviation of a temporally dependent process, 
-but their coverage of the temporal dependence deteriorates as $n$ increases. A potential solution to this issue is to center the intervals 
-$\hat{\theta}_{n}$. To do this, the distribution $\delta^*$ should be considered. A percentile interval 
-centered around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
-\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]
+Both of these intervals work well when attempting to recover the mean and
+standard deviation of a temporally dependent process, but their coverage of
+the temporal dependence deteriorates as $n$ increases. A potential solution to
+this issue is to center the intervals $\hat{\theta}_{n}$. To do this, the
+distribution $\delta^*$ should be considered. A percentile interval centered
+around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
+\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2},
+  \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\] 
+This centering procedure can also be applied to a BCA interval. A BCA interval
+centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the
+form:
+\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1},
+  \hat{\theta}_{n} + \delta^*_{\alpha_2}].\]
 
-%A percentile interval centered around $\bar\theta_n^*$ ($CI_{\bar\theta_n^*}$) takes the form: \[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\] An alternative is an interval of the form: \[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] which is equivalent to: \[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] and therefore is also equivalent to: \[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] Thus, the interval ($CI_{\hat{\theta}_{n}, \bar\theta_n^*}$) is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.
-
-This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the form:
-\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
-%A BCA interval centered around $\bar\theta_n^*$ ($CI_{BCA, \bar\theta_n^*}$) takes the form: \[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\] An alternative (($CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$) is an interval of the form: \[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}]\]
-
-Thus, there are two types of intervals that can be constructed for block bootstrap estimation in this study: 
-$CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$. Note that both of these intervals are centered around $\hat{\theta}_{n}$ and asymmetric.
+Thus, there are two types of intervals that can be constructed for block
+bootstrap estimation in this study: $CI_{\hat{\theta}_{n}}$ and
+$CI_{BCA, \hat{\theta}_{n}}$. Note that both of these intervals are centered
+around $\hat{\theta}_{n}$ and asymmetric.
 
@@
 
-%The central objective of the study was to assess what sample size is necessary for the the block bootstrap method to estimate a parameter of an autoregressive process.
-The method will work better as the sample size goes to infinity, but the goal is to see what is the smallest sample size that is acceptable.
-The sample size is acceptable if many 1 - $\alpha$/2 confidence intervals for that sample size recover the parameter at a rate of 1 - $\alpha$/2 \%.
-In the previous section, the procedures for creating three types of confidence interval of a parameter using the block bootstrap method are described.
+Base R has a built in function arima.sim that allows one to simulate an AR(1)
+process, for which one can set the theoretical $\phi$. By default, the mean of
+the process $\mu$ is 0 and the standard deviation of the error term
+$\sigma_{\epsilon}$ is 1. For the purposes of this study, the standard
+deviation of the process $\sigma_{x}$ should be controlled at 1. The
+observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new
+theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
+\begin{align}
+X_{t} &= \epsilon_{t} + \phi X_{t-1};\\
+Var(X_{t}) &= Var(\epsilon_{t} + \phi X_{t-1});\\
+\sigma^2_{x} &= \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\\
+\sigma^2_{x}(1 - \phi^2) &= 1;\\
+\sigma_{x}\sqrt{1 - \phi^2} &= 1.
+\end{align}
+The experimental factor of this study was $\phi$, as the temporal dependence
+affects the performance of block bootstrap. $\phi = -0.4 -0.2,$ and $0$ (a
+standard normal distribution)$, 0.2, and 0.4$ were used in this study.
 
-%These procedures are applied to a simulation of an autoregressive integrated moving average (ARIMA) process to create three confidence interval of certain parameters (the mean, the AR(1) coefficient, the MA(1) coefficient, the standard deviation, etc.).
+As described in the last section, the block bootstrap method can be used to
+estimate a parameter $\theta$ of an AR(1) process. This method can be
+simulated with the tsboot function from the boot R package. In this study,
+$\theta$ is composed of the target parameters $\mu = 0$, $\sigma_{x}$, and
+$\phi$. The sample mean $\bar{x}$ can be used as the statistic to estimate
+$\mu$, the sample standard deviation $S_x$ can be used as the statistic to
+estimate $\sigma$, and the autocorrelation function of the sample at lag 1
+$\rho_1$ can be used as the statistic to estimate $\phi$. In the R
+implementation, these three statistics are incorporated into a function that
+will apply each statistic to the original sample and to each bootstrapped
+pseudo-sample. From a sample of length $n$, two types of block bootstrap 95\%
+confidence intervals can be constructed for each target parameter:
+$CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
 
-Base R has a built in function arima.sim that allows one to simulate an AR(1) process, for which one can set the theoretical $\phi$. 
-By default, the mean of the process $\mu$ is 0 and the standard deviation of the error term $\sigma_{\epsilon}$ is 1. 
-For the purposes of this study, the standard deviation of the process $\sigma_{x}$ should be controlled at 1. 
-The observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
+Each of these 6 intervals either recovers $\theta$ or does not. Remember that
+95\% of many of a certain type of 95\% confidence intervals constructed from
+samples of the same $n$ should recover $\theta$. To see if this is
+approximately the case, one can run 1000 replications of the block bootstrap
+procedure, and for each interval-$\theta$ pair, the rate at which that type of
+interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
+point estimate of a proportion, so a 95\% confidence interval of this coverage
+proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
+.95 is included in the interval, the block bootstrap method is likely working
+well. If all values in the interval are below .95, the results suggest that the
+method either is providing an inaccurate estimation, is underestimating the
+process' variability, or a combination of both. If all values in the interval
+are above .95, the results suggest that the method is overestimating the
+process' variability.
 
-\[X_{t} = \epsilon_{t} + \phi X_{t-1};\]
-\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1});\]
-\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\]
-\[\sigma^2_{x}(1 - \phi^2) = 1;\]
-\[\sigma_{x}\sqrt{1 - \phi^2} = 1.\]
-
-The experimental factor of this study was $\phi$, as the temporal dependence affects the performance of block bootstrap. 
-$\phi = -0.4 -0.2,$ and $0$ (a standard normal distribution)$, 0.2, and 0.4$ were used in this study.
-
-As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process. 
-This method can be simulated with the tsboot function from the boot R package. In this study, $\theta$ is composed of the target 
-parameters $\mu = 0$, $\sigma_{x}$, and $\phi$. From a sample of length $n$, two types of block bootstrap 95\% confidence intervals 
-can be constructed for each target parameter: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
-
-Each of these 6 intervals either recovers $\theta$ or does not. Remember that 95\% of many of a certain type of 95\% confidence intervals 
-constructed from samples of the same $n$ should recover $\theta$. To see if this is generally or approximately the case, one can run 
-1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers 
-$\theta$ can be recorded. The coverage rate is, of course, a point estimate of a proportion, so a 95\% confidence interval of this coverage proportion 
-(with $n_{CI} = 1000$) can be constructed, and if the proportion .95 is included in the interval, the block bootstrap method is likely working well.
-
-If $\theta$ is not covered at that $n$, a larger sample size must be necessary. $n = $100, 200, 300, 400, and 500, 600, 700 were used in this study. 
-Remember that the goal is to find the smallest $n$ which is sufficient for proper coverage.
-
-%For all simulation studies, but $\mu$ and $\sigma_{x}$ can be kept constant, but increasing temporal dependence factors such as AR and MA Coefficients can make block bootstrap less effective in estimation, so its impact on the method's performance should be analyzed.
-For a certain variation of an AR(1) process, block bootstrap 95\% confidence intervals for each of 3 parameters ($\mu$, $\sigma_{x}$, and the autocorrelation function$\rho$) can be replicated for 1000 simulated samples of a certain length.
-For each individual confidence interval, it can be recorded whether or not the interval includes the true parameter.
-The coverage rate, or the proportion of intervals that include the true parameter, can then be recorded.
-If the parameter is being properly estimated by the block bootstrap, the coverage rate should reflect this by being close to the confidence level of 95\%.
-If this is not the case, the method is not working as well as it should.
-The width of the confidence interval for each replication is dependent on the variability of the parameter of the time series.
-If the interval is on average not wide enough to capture the parameter at the expected rate of 95\%, it indicates that the variability of the parameter is underestimated.
-If the interval is too wide and captures the parameter at a rate above 95\%, it indicates that the variability of the parameter is overestimated.
-Since the coverage rate is a proportion based on 1000 independent binary outcomes (the interval recovers the parameter or it doesn't), a 95\% confidence interval of the coverage rate for each parameter can also be created.
-The inclusion of .95 in the interval indicates that the block bootstrap method is working well for its respective parameter.
-If this is not the case for this sample length, the procedure can be conducted again with a larger sample length.
-This can be repeated until the method is determined to be working acceptably, meaning that .95 is included in the 95\% confidence interval of the coverage rate of the parameter.
-
-%1000 replicates of length-n random samples of an AR(1) process with theoretical $\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1 were simulated using R.
-For each of three target parameters ($\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1, three types of block bootstrap (with block length l) confidence intervals (percentile, empirical, and BCA) were constructed for each replicate sample.
-The statistic used to estimate $\mu$ is the sample mean $\bar{x}$, the statistic used to estimate $\sigma$ is the sample standard deviation $S^2$, and the statistic used to estimate $\theta$ is the auto-correlation function of the sample.
-For each of these nine categories of confidence intervals, the coverage rate of its respective parameter was computed, along with a 95\% confidence interval of the proportion given 4000 trials.
-For a certain variation of the process, the study was repeated for n = 125, 1000, 3375, and 8000.
-The only parameter of the process that was varied was $\theta$, and 0.1, 0.3, and 0.5 were the values used.
+If $\theta$ is not covered at that $n$, a larger $n$ may be
+necessary, assuming that performance will improve as $n$ is increased. $n =$
+100, 200, 300, 400, and 500, 600, 700 were used in this study. Remember that
+the goal of this study is to find the smallest $n$ which is sufficient for
+proper coverage.
 
 \begin{figure}[tbp]
-\caption{}
   \centering
   \includegraphics[width=\textwidth]{figures/plot_n.4}
-  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as $n = 100$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as 
-  low as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can 
-  expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, 
-  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear pattern of deterioration of coverage.}
+  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as
+    $n = 100$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as
+    $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there
+    is no clear pattern of deterioration of coverage, so one can expect that
+    increasing $n$ will eventually result in proper coverage of $\sigma$.
+    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, and this
+    is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly
+    under-covers $\phi$, and there is a clear pattern of deterioration of
+    coverage.}
   \label{fig:plot_n.4}
@@
 \begin{figure}[tbp]
-\caption{}
   \centering
   \includegraphics[width=\textwidth]{figures/plot_n.2}
-  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as $n = 100$. Both intervals seem to cover $\sigma$ generally well, 
-  although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
-  and this is true as low as $n = 200$.  $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear coverage deterioration trend as $n$ increases.}
+  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as
+    $n = 100$. Both intervals seem to cover $\sigma$ generally well, although
+    $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
+    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
+    coverage, and this is true as low as $n = 200$.
+    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a
+    clear coverage deterioration trend as $n$ increases.}
   \label{fig:plot_n.2}
@@
 \begin{figure}[tbp]
-\caption{}
   \centering
   \includegraphics[width=\textwidth]{figures/plot_0}
-  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as $n = 500$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as 
-  $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, 
-  so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ seems to cover 
-  $\phi$ generally well at $n = 400$, but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the method's performance seems to improve as $n$ increases.}
+  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as
+    $n = 500$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as 
+    $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but
+    there is no clear pattern of deterioration of coverage, so one can expect
+    that increasing $n$ will eventually result in proper coverage of $\sigma$.
+    $CI_{\hat{\theta}_{n}}$ seems to cover $\phi$ generally well at $n = 400$,
+    but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the
+    method's performance seems to improve as $n$ increases.}
   \label{fig:plot_0}
@@
 \begin{figure}[tbp]
-\caption{}
   \centering
   \includegraphics[width=\textwidth]{figures/plot_.2}
-  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as $n = 300$. Both intervals seem to cover $\sigma$ generally well, 
-  although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
-  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no clear coverage deterioration trend as $n$ increases.}
+  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as
+    $n = 300$. Both intervals seem to cover $\sigma$ generally well, although
+    $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
+    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
+    coverage, and this is true as low as $n = 200$.
+    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no
+    clear coverage deterioration trend as $n$ increases.}
   \label{fig:plot_.2}
@@
 \begin{figure}[tbp]
-\caption{}
   \centering
   \includegraphics[width=\textwidth]{figures/plot_.4}
-  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well as low as $n = 400$. $CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low as $n = 400$. 
-  $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear sign of coverage deterioration, so one can expect that increasing $n$ 
-  will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
-  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear coverage deterioration trend as $n$ increases.}
+  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well
+    as low as $n = 400$. $CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low
+    as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but
+    there is no clear sign of coverage deterioration, so one can expect that
+    increasing $n$ will eventually result in proper coverage of $\sigma$.
+    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
+    coverage, and this is true as low as $n = 200$.
+    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear
+    coverage deterioration trend as $n$ increases.}
   \label{fig:plot_.4}
@@
 
-Only $CI_{\hat{\theta}_{n}}$ managed to solve the deterioration problem with respect to recovering $\phi$, indicating that this interval 
-should be used as opposed to $CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$. As expected, a higher $\phi$ demands a 
-larger $n$ to estimate all parameters, but a negative $\phi$ may only require a lesser $n$. For example, for both $\phi = 0.2$ and $0.4$, 
-$n = 100$ was sufficient to recover $\mu$ at a rate of approximately 95\%.
+As shown in the above figures, only $CI_{\hat{\theta}_{n}}$ managed to solve
+the deterioration problem with respect to recovering $\phi$, indicating that
+this interval should be used as opposed to the more complex
+$CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$. Increasing $n$ will not
+fix the performance of $CI_{BCA, \hat{\theta}_{n}}$ because the assumption that
+the coverage rate will approach an upper limit of .95 as $n$ increases is
+invalid. As expected for $CI_{\hat{\theta}_{n}}$, a higher $\phi$ demands a
+larger $n$ to estimate all parameters, but a negative $\phi$ may require a
+lesser $n$. For example, for both $\phi = 0.2$ and $0.4$, $n = 100$ was
+sufficient to recover $\mu$ at a rate of approximately 95\%.
 
@@
 
-The motivation for the study is the idea that block bootstrap procedure will perfectly estimate a parameter of a time series given an infinitely large sample. 
-The goal for this study was to find what is a good enough finite sample length for block bootstrap estimation to recover the parameter of a 
-time series at an acceptable rate. Assuming that $CI_{\hat{\theta}_{n}}$ is used (as it was found to work better overall, especially when estimation $\phi$), 
-the results of this study suggest that even for estimating $\mu$, an $n$ of around 500 may be necessary if $\phi$ is unknown. 
-An $n$ of around 400 may be necessary to estimate $\sigma$ is $\phi$ is unknown. If $\phi$ is already known, 
-a lesser $n$ may be adequate to estimate these parameters. When $\phi$ was negative, 
-a $n$ of around 100 was sufficient to estimate $\mu$. However, in real world applications, $\phi$ is more commonly found to be positive, 
-so a larger $n$ is more likely to be necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary. 
-This information could prove to be useful for researching using block bootstrap estimation of time series in domains such as econometrics. 
-Future studies could investigate if there are types of block bootstrap intervals that can be constructed that 
-would more appropriate recover the parameters of a time series. One could also investigate the $n$ needed to 
-make inferences about other forms of serially dependent data such as an MA process.
+The motivation for the study is the idea that block bootstrap procedure will
+perfectly estimate a parameter of a time series given an infinitely large
+sample. The goal for this study was to find what is a good enough finite
+sample length for block bootstrap estimation to recover the parameter of a
+time series at an acceptable rate. Again, this relies on the assumption that
+there is a size $n$ large enough for the method to work: that is, the method's
+performance improves as $n$ increases. Out of the two types of intervals used
+in this study, this assumption was found to hold true with respect to
+estimating $\phi$ only for $CI_{\hat{\theta}_{n}}$, whereas
+$CI_{BCA, \hat{\theta}_{n}}$ exhibited coverage deterioration as $n$
+increased. When using $CI_{\hat{\theta}_{n}}$ and $\phi$ is unknown, the
+results of this study suggest that an $n$ of around 500 may be necessary to
+estimate $\mu$, and an $n$ of around 400 may be necessary to estimate
+$\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to estimate
+these parameters. When $\phi$ was negative, a $n$ of around 100 was sufficient
+to estimate $\mu$. However, in real world applications, $\phi$ is more
+commonly found to be positive, so a larger $n$ is more likely to be necessary.
+Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary. This
+information could prove to be useful for researching using block bootstrap
+estimation of time series in domains such as econometrics. Future studies
+could investigate if there are types of block bootstrap intervals
+constructions that would more appropriately recover the parameters of a time
+series. One could also investigate the $n$ needed to make inferences about
+other forms of serially dependent data such as an MA process.
 

### 2023-03-01 Manuscript/manuscript.tex
smoothed intro

@@
 
-\title{Sample Length at Which Block Bootstrapping is Effective for Estimation
-  of Parameter of Time Series}
+\title{How Large a Sample Size is Needed for Block Bootstrap Confidence Intrvals
+  to Have Desired Coverage Rates?}
 
-\author{Mathew Chandy\\
+\author{Mathew Chandy
 %   \href{mailto:mathew.chandy@uconn.edu}
 % {\nolinkurl{mathew.chandy@uconn.edu}}\\
-  Jun Yan\\[1ex]
+  \and Jun Yan\\[1ex]
   Department of Statistics, University of Connecticut\\
@@
 \maketitle
-
-\doublespace
 
@@
 \bigskip
-\noindent\sc{Keywords}:
-simulation;
+\noindent{\sc Keywords}:
+dependent data; gsimulation
 \end{abstract}
+
+\doublespace
 
@@
   \url{
-https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html}}
+https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html},
+  chapter 2}
 
@@
 
-Block bootstrap is an important tool for constructing confidence intervals when
+Block bootstrap is a powerful tool for constructing confidence intervals when
 making inferences about dependent data. Early ideas were developed
 independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
-\citet{kunsch1989jackknife}. % \citet{radovanov2014comparison}
-It has been applied to a variety of different domains such 
-as econometrics \citep{mackinnon2006bootstrap} and meteorology
-\citep{varga2017generalised}. It is particularly useful for serially dependent
-data when the serial dependence is not specified or of not primary interest.
-As the sample size goes to infinity, block bootstrap confidence intervals are
-expected to have coverage rates matching their nominal levels. For finite
-sample sizes, however, a natural question is, how large a sample size is large
-enough for block bootstrap confidence intervals to have the desired coverage
-rates?
+\citet{kunsch1989jackknife}.
+It has since been applied in various fields such as econometrics
+\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
+Block bootstrap is particularly useful for serially dependent
+data when the serial dependence is not specified or not of primary interest.
+The method is expected to produce confidence intervals with coverage rates
+matching their nominal levels as the sample size grows to infinity. However,
+when dealing with finite sample sizes, an important question is how large the
+sample size needs to be for block bootstrap confidence intervals to have the
+desired coverage rates.
 
-\citet{hesterberg2015teachers} notes that while percentile-based confidence
-intervals from basic nonparametric bootstrap (simple resampling with no blocks
-involved) are more accurate than t-intervals for larger sample sizes, they are
-less accurate for smaller sample sizes. \citet{nevitt2001performance} find
-that a sample size of 200-1000 is usually sufficient for interval estimation
-using basic nonparametric bootstrap. \citet{goncalves2005bootstrap} found that
-standard error estimates from block bootstrap small samples may be
-significantly more accurate than inference from closed-form asymptotic
-estimates. That study focused on the estimation of a coefficient parameter
-within the context of linear regression. Still, the block bootstrap percentile
-confidence intervals under-covered the parameter even for n = 1024.
+The necessary sample size for bootstrap standard errors to provide valid
+uncertainty measures in practice has not been extensively studied. For
+independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
+that while percentile-based confidence intervals from nonparametric bootstrap
+are more accurate than $t$-intervals for larger sample sizes, they are
+less accurate for smaller sample sizes. In the contect of structural equation
+modeling, \citet{nevitt2001performance} find
+that a sample size of 200--1000 is usually sufficient for interval estimation
+using standard nonparametric bootstrap. For dependent data, the necessary sample
+size for block bootstrap is even less clear. In a linear regression setting with
+dependent data, \citet{goncalves2005bootstrap} find that, standard error
+estimates from block bootstrap in small samples may be more accurate than
+inference from closed-form asymptotic estimates, but block bootstrap percentile
+confidence intervals still do not have sufficient coverage even for sample size
+$n = 1024$.
 
-While the aforementioned studies have looked into the necessary sample size
-for various bootstrap methods to make inferences about various types of data,
-the goal of this study is to find a threshold or range of sample sizes at
-which block bootstrap is an effective method for estimating a parameter
-specifically in the context of a time series. The method can be considered
-effective if the rate at which confidence intervals created from samples of
-the same size recover the parameter is approximately equal to the nominal
-confidence level. This study will focus on estimating parameters of an AR(1)
-process with two types of block bootstrap confidence intervals from the
-literature \citep{diciccio1996bootstrap} \citep{rice2006mathematical}. How
+The goal of this paper is to provide some practical recommendations on necessary
+sample size for block bootstrap with dependent data. We consider a simple
+situation of a stationary time series, where the parameters of interests are the
+mean, standard deviation, and the first-order autocorrelation coefficient.
+We compare four variants of confidence intervals from block bootstrap:
+\jy{list them} literature \citep{diciccio1996bootstrap}
+\citep{rice2006mathematical}.
+Their empirical coverage rates at different sample sizes and dependence levels
+are compared in a simulation study.
+\jy{may reveal the most interesting result here to engage interests.}
+
+The remainder of the papers is organized as follows.
+\jy{refer to sections by label instead of hard number}
 these intervals are constructed as well as the general procedure for block
@@
 
-\section{Review of Block Bootstrap}
+\section{Block Bootstrap Confidence Intervals}
 \label{sec:blkbootreview}

### 2023-03-01 Manuscript/manuscript.tex
comments on review section

@@
 
+\jy{set up notations for sample; give the algorithm to perform bootstrap
+  procedure}
+
+\jy{two subsections: 1) block bootstrap basics; 2) bootstrap CIs. The different
+  CIs should each take a paragraph.}
+
+\jy{Needs to distinguish the basic percentile bootstrap and corrected percentile
+  bootstrap. Recall that we had trouble covering phi using the basic percentile
+  method.}
+
 Block bootstrap is a method that can be used to estimate a parameter of
@@
 The experimental factor of this study was $\phi$, as the temporal dependence
-affects the performance of block bootstrap. $\phi = -0.4 -0.2,$ and $0$ (a
-standard normal distribution)$, 0.2, and 0.4$ were used in this study.
+affects the performance of block bootstrap.
+$\phi \in \{-0.4 -0.2, 0, 0.2, 0.4\}$.
 

### 2023-03-08 Code/NewPlots.Rmd
Manuscript Update

--- 2023-01-26 Code/NewPlots.Rmd
@@
 ```{r}
-graph_bts <- function(cov, phi, target, width, nrep = 1000, sizes = c(100, 200, 300, 400, 500), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'phi'), level = .95) {
-  n <- rep(sizes, each = length(types) * length(parameters))
-  CI <- rep(types, times = length(sizes), each = length(parameters))
-  t <- rep(parameters, times = length(sizes) * length(types))
+df_bts <- function(cov, nrep = 1000, phis = c(-0.4, -0.2, 0, 0.2, 0.4), sizes = c(100, 200, 300, 400, 500, 600, 700), types = c('pctCI', 'estCI', 'bcaCIest'), parameters = c('mu', 'sigma', 'phi')) {
+  phi <- rep(phis, each = length(sizes) * length(types) * length(parameters))
+  n <- rep(sizes, times = length(phis), each = length(types) * length(parameters))
+  CI <- rep(types, times = length(phis) * length(sizes), each = length(parameters))
+  t <- rep(parameters, times = length(phis) * length(types) * length(sizes))
   LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
-  UB <-sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
+  UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
 
-  df <- data.frame(n, CI, t, cov, LB, UB)
+  c(data.frame(phi, n, CI, t, cov, LB, UB))
+}
+
+```
+
+```{r}
+target <- c(0, 1, -.4)
+cov <- c(mychk(sim_n.4_1h, target), mychk(sim_n.4_2h, target), mychk(sim_n.4_3h, target), mychk(sim_n.4_4h, target), mychk(sim_n.4_5h, target), mychk(sim_n.4_6h, target), mychk(sim_n.4_7h, target))
+target <- c(0, 1, -.2)
+cov <- c(cov, mychk(sim_n.2_1h, target), mychk(sim_n.2_2h, target), mychk(sim_n.2_3h, target), mychk(sim_n.2_4h, target), mychk(sim_n.2_5h, target), mychk(sim_n.2_6h, target), mychk(sim_n.2_7h, target))
+target <- c(0, 1, 0)
+cov <- c(cov, mychk(sim_0_1h, target), mychk(sim_0_2h, target), mychk(sim_0_3h, target), mychk(sim_0_4h, target), mychk(sim_0_5h, target), mychk(sim_0_6h, target), mychk(sim_0_7h, target))
+target <- c(0, 1, .2)
+cov <- c(cov, mychk(sim_.2_1h, target), mychk(sim_.2_2h, target), mychk(sim_.2_3h, target), mychk(sim_.2_4h, target), mychk(sim_.2_5h, target), mychk(sim_.2_6h, target), mychk(sim_.2_7h, target)) 
+target <- c(0, 1, .4)
+cov <- c(cov, mychk(sim_.4_1h, target), mychk(sim_.4_2h, target), mychk(sim_.4_3h, target), mychk(sim_.4_4h, target), mychk(sim_.4_5h, target), mychk(sim_.4_6h, target), mychk(sim_.4_7h, target))
+
+df <- data.frame(df_bts(cov))
+graph_bts <- function(t, width, data, trans = 'identity', level = .95)
+{
+  library(latex2exp)
   library(ggplot2)
-  ggplot(df, aes(x = n, y = cov)) +
+
+  ggplot(data, aes(x = n, y = cov)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
@@
     geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
-    facet_grid(t ~ CI)
+    facet_grid(factor(phi) ~ factor(CI), labeller = label_parsed) +
+    scale_y_continuous(trans=trans)
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''))
 }
@@
 ```{r}
-phi <- 0
-target <- c(0, 1, phi)
-cov <- c(mychk(sim_0_1h, target), mychk(sim_0_2h, target), mychk(sim_0_3h, target), mychk(sim_0_4h, target), mychk(sim_0_5h, target))
-graph_bts(cov, phi, target, width = 25)
-ggsave('../Manuscript/figures/plot_0.pdf')
+t <- 'mu'
+width <- 10
+df1 <- df[(df$t == t),]
+graph_bts(t, width, df1)
 ```
+
 ```{r}
-phi <- .2
-target <- c(0, 1, phi)
-cov <- c(mychk(sim_.2_1h, target), mychk(sim_.2_2h, target), mychk(sim_.2_3h, target), mychk(sim_.2_4h, target), mychk(sim_.2_5h, target))
-graph_bts(cov, phi, target, width = 25)
-ggsave('../Manuscript/figures/plot_.2.pdf')
+t <- 'sigma'
+width <- 10
+df2 <- df[(df$t == t),]
+graph_bts(t, width, df2)
 ```
+
 ```{r}
-phi <- .4
-target <- c(0, 1, phi)
-cov <- c(mychk(sim_.4_1h, target), mychk(sim_.4_2h, target), mychk(sim_.4_3h, target), mychk(sim_.4_4h, target), mychk(sim_.4_5h, target))
-
-graph_bts(cov, phi, target, width = 10)
-ggsave('../Manuscript/figures/plot_.4.pdf')
+t <- 'phi'
+width <- 10
+df3 <- df[(df$t == t),]
+graph_bts(t, width, df3)
 ```

### 2023-03-08 Manuscript/manuscript.tex
Manuscript Update

@@
 
-\title{How Large a Sample Size is Needed for Block Bootstrap Confidence Intrvals
+\title{How Large a Sample Size is Needed for Block Bootstrap Confidence
+  Intervals
   to Have Desired Coverage Rates?}
@@
 
-The goal of this paper is to provide some practical recommendations on necessary
-sample size for block bootstrap with dependent data. We consider a simple
-situation of a stationary time series, where the parameters of interests are the
-mean, standard deviation, and the first-order autocorrelation coefficient.
-We compare four variants of confidence intervals from block bootstrap:
-\jy{list them} literature \citep{diciccio1996bootstrap}
-\citep{rice2006mathematical}.
-Their empirical coverage rates at different sample sizes and dependence levels
-are compared in a simulation study.
-\jy{may reveal the most interesting result here to engage interests.}
+The goal of this paper is to provide some practical recommendations on
+necessary sample size for block bootstrap with dependent data. We consider a
+simple situation of a stationary time series, where the parameters of
+interests are the mean, standard deviation, and the first-order
+autocorrelation coefficient. We compare three variants of block bootstrap
+confidence intervals from the literature \citep{diciccio1996bootstrap}
+\citep{rice2006mathematical}: a basic percentile interval, a percentile
+interval centered around the original estimate, and a bias-corrected and
+accelerated ($BC_a$) interval also centered around the original estimate. Their
+empirical coverage rates at different sample sizes and dependence levels are
+compared in a simulation study. The results of this study suggest that
+appropriate recovery of temporal dependence parameters is heavily dependent on
+the type of interval used.
 
-The remainder of the papers is organized as follows.
-\jy{refer to sections by label instead of hard number}
-these intervals are constructed as well as the general procedure for block
-bootstrap parameter estimation is reviewed in Section 2. Section 3 offers an
-explanation of the simulation design and results. Section 4 discusses the main
-takeaways from the results, how these findings could be useful, and possible
-future explorations.
+The remainder of the papers is organized as follows:
+The Block Bootstrap Confidence Intervals section reviews how these intervals
+are constructed as well as the general procedure for block bootstrap parameter
+estimation. The Simulation Study section offers an explanation of the
+simulation design and results. Finally, the Concluding Remarks section
+discusses the main takeaways from the results, how these findings could be
+useful, and possible future explorations.
 
@@
 considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
-\citep{buhlmann1999block}. The designer of the study can choose whether the
-blocks overlap or not. If the blocks do not overlap, it is called a non-moving
-block bootstrap. In this case, the original sample is split evenly into
-blocks, which will then be resampled to create new pseudo-samples. If the
-blocks do overlap, it is called a moving block bootstrap. Blocks are resampled
-randomly from the original sample, but they do not have to be from a set of
-evenly spaced blocks. For moving block bootstrap, if $l \vert n$, a
-bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks of
-size $l$ with replacement to create a new pseudo-sample of size $n$. If
-$l does not divide n$, the pseudo-sample is created by taking a sample of
-$\lfloor n / l \rfloor$ blocks of size $l$ and one block of size
-$(n \;\mathrm{mod})\; l$. An estimate $\hat\theta_n^*$ is computed from the
-pseudo-sample. This procedure can be repeated many times to create a
-distribution of $\hat\theta_n^*$.
+\citep{buhlmann1999block}.
+
+The designer of the study can choose whether the blocks overlap or not. If the
+blocks do not overlap, it is called non-overlapping or non-moving block
+bootstrap. In this case, blocks are resample randomly from the set of all
+non-overlapping blocks of size $l$. For non-moving block bootstrap, $l \vert n$
+must always be true. In this case, a set of $n / l$ non-overlapping blocks of
+size $l$ is constructed from the original sample. Each bootstrapped
+pseudo-sample is created by sampling $n / l$ blocks with replacement from the
+same set.
+
+If the blocks do overlap, it is called overlapping or moving block bootstrap.
+In this case, blocks are resampled randomly from the set of all possible
+blocks of size $l$. For moving block bootstrap, $l \vert n$ is not a necessary
+condition. The set of available blocks is created by iterating through each
+observation $i$ in the original sample and adding to the set the block of size
+$l$ that begins with $i$. This set can limited to blocks that end with an
+$i <= n$, meaning that $n - l + 1$ blocks are availabe to resample from, or it
+can be expanded to include blocks that ``wrap around'': in
+other words, blocks that end with a lesser index than the index they began
+with, meaning that $n$ blocks are available to resample from. If $l \vert n$,
+a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks
+from the set with replacement to create a new pseudo-sample of size $n$. If
+$l does not divide n$, the last block selected will be reduced in size so that
+the final size of the pseudo-sample is $n$. Moving block bootstrap was used in
+this study as it has been found to yield the lowest error in general
+\citep{radovanov2014comparison}. The set of available was not limited as
+described above.
+
+An estimate $\hat\theta_n^*$ is computed from the pseudo-sample. This
+procedure can be repeated many times to create a distribution of
+$\hat\theta_n^*$.
 
 In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block
-bootstrap estimation. Using this distribution of $\hat\theta_n^*$, a
-$1 - \alpha$/2 \% confidence interval for the parameter can be constructed. 
-The most simplistic method for constructing this interval is the percentile
-confidence interval. For a parameter $\theta$, the percentile $1 - \alpha$/2
-\% confidence interval takes the form: 
+bootstrap estimation. Using this distribution of $\hat\theta_n^*$, several
+variants of a $1 - \alpha$/2 \% confidence interval for the parameter can be
+constructed. The most simplistic method for constructing this interval is the
+basic percentile confidence interval. For a parameter $\theta$, the percentile
+$1 - \alpha$/2 \% confidence interval takes the form: 
 \[ [\hat\theta_{n, \alpha/2}^*, \hat\theta_{n, 1 - \alpha/2}^*].\]
-Another method is the bias-corrected and accelerated 
-(BCA) $1 - \alpha$/2 \% confidence interval, which takes the form: 
-\[ [\hat\theta_{n, \alpha_1}^*,\hat\theta_{n, \alpha_2}^*].\] 
+
+This interval works well when attempting to recover the mean and
+standard deviation of a temporally dependent process, but its coverage of
+the temporal dependence deteriorates as $n$ increases. A potential solution to
+this issue is to center the intervals around $\hat{\theta}_{n}$. To do this,
+the distribution of $\delta^*$ should be considered. For a parameter $\theta$,
+the $\hat{\theta}_{n}$-centered $1 - \alpha$/2 \% confidence interval takes
+the form:
+\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2},
+  \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]
+
+An alternative method is a $BC_a$ interval centered around $\hat{\theta}_{n}$.
+For a parameter $\theta$, the $BC_a$ $1 - \alpha$/2 \% confidence interval
+takes the form:
+\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1},
+  \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
 $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
@@
 Where $z_0$ is the quantile function of the proportion of
-$\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness of
+$\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness (computed using
+the skewness function from the R e1071 package \citep{e1071}) of
 $\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
@@
 
-Both of these intervals work well when attempting to recover the mean and
-standard deviation of a temporally dependent process, but their coverage of
-the temporal dependence deteriorates as $n$ increases. A potential solution to
-this issue is to center the intervals $\hat{\theta}_{n}$. To do this, the
-distribution $\delta^*$ should be considered. A percentile interval centered
-around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
-\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2},
-  \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\] 
-This centering procedure can also be applied to a BCA interval. A BCA interval
-centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the
-form:
-\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1},
-  \hat{\theta}_{n} + \delta^*_{\alpha_2}].\]
-
-Thus, there are two types of intervals that can be constructed for block
-bootstrap estimation in this study: $CI_{\hat{\theta}_{n}}$ and
-$CI_{BCA, \hat{\theta}_{n}}$. Note that both of these intervals are centered
-around $\hat{\theta}_{n}$ and asymmetric.
+Thus, there are three types of intervals that can be constructed for block
+bootstrap estimation in this study: Percentile, $\hat{\theta}_{n}$-Centered,
+and $BC_a$.
 
@@
 
-Base R has a built in function arima.sim that allows one to simulate an AR(1)
-process, for which one can set the theoretical $\phi$. By default, the mean of
-the process $\mu$ is 0 and the standard deviation of the error term
-$\sigma_{\epsilon}$ is 1. For the purposes of this study, the standard
-deviation of the process $\sigma_{x}$ should be controlled at 1. The
-observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new
+The Base R stats package has a built in function arima.sim that allows one to
+simulate an AR(1) process, for which one can set the theoretical $\phi$
+\citep{R}. By default, the mean of the process $\mu$ is 0 and the standard
+deviation of the error term $\sigma_{\epsilon}$ is 1. For the purposes of this
+study, the standard deviation of the process $\sigma_{x}$ should be controlled
+at 1. The observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new
 theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
@@
 estimate a parameter $\theta$ of an AR(1) process. This method can be
-simulated with the tsboot function from the boot R package. In this study,
-$\theta$ is composed of the target parameters $\mu = 0$, $\sigma_{x}$, and
-$\phi$. The sample mean $\bar{x}$ can be used as the statistic to estimate
-$\mu$, the sample standard deviation $S_x$ can be used as the statistic to
-estimate $\sigma$, and the autocorrelation function of the sample at lag 1
-$\rho_1$ can be used as the statistic to estimate $\phi$. In the R
-implementation, these three statistics are incorporated into a function that
-will apply each statistic to the original sample and to each bootstrapped
-pseudo-sample. From a sample of length $n$, two types of block bootstrap 95\%
-confidence intervals can be constructed for each target parameter:
+simulated with the tsboot function from the R boot package \citep{boot}
+\citep{davison}. In this study, $\theta$ is composed of the target parameters
+$\mu = 0$, $\sigma_{x}$, and $\phi$. The sample mean $\bar{x}$ can be used as
+the statistic to estimate $\mu$, the sample standard deviation $S_x$ can be
+used as the statistic to estimate $\sigma$, and the autocorrelation function
+of the sample at lag 1 $\rho_1$ can be used as the statistic to estimate
+$\phi$. In the R implementation, these three statistics are incorporated into
+a function that will apply each statistic to the original sample and to each
+bootstrapped pseudo-sample. From a sample of length $n$, two types of block
+bootstrap 95\% confidence intervals can be constructed for each target
+parameter:
 $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
@@
 
+The figures below were created using the R ggplot2 package \citep{ggplot2}.
 \begin{figure}[tbp]

### 2023-03-08 Code/functions.R

@@ -1,0 +1,112 @@
+## This note checks the empirical coverage rate of CIs constructed from
+## block bootstrap with series generated from an AR process
+
+mystat <- function(x) {
+  c(mean(x),
+    sd(x),
+    cor(x[-1], x[-length(x)]))
+  # acf(x, lag.max = 1, plot = FALSE)$acf[2])
+}
+
+do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
+  if (phi == 0) {
+    x <- rnorm(n)
+  }
+  else {
+    x <- arima.sim(list(ar = phi), n = n) * sqrt(1 - phi^2)
+  }
+  bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
+  alpha <- 1 - level
+  
+  
+  ## Percentile interval
+  pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
+  
+  ## Centered interval
+  mbts <- apply(bts$t, 2, mean)
+  crit <- 
+    apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
+  ## alpha/2 and 1 - alpha/2 critical values 
+  ## of pseudo-estimate - mean of pseudo-estimates
+  # crit2 <- 
+  #  apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
+  ## alpha/2 and 1 - alpha/2 critical values 
+  ## of pseudo-estimate - original estimate
+  
+  ## interval centered around...
+  estCI <- sweep(crit, 2, bts$t0, FUN = '+') # original estimate
+  ## LB: bts$t0 + alpha/2 crit, UB: bts$t0 + (1 - alpha/2) crit
+  # mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
+  ## LB: mbts + alpha/2 crit2, UB: mbts + (1 - alpha/2) crit2
+  # altCI <- sweep(-crit[order(2:1),], 2, bts$t0, FUN = '+') # both
+  ## LB: bts$t0 - (1 - alpha/2) crit, UB: bts$t0 - alpha/2 crit and
+  ## LB: mbts - (1 - alpha/2) crit2, UB: mbts - alpha/2 crit2
+  
+  
+  ## BCa interval
+  z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
[…]

### 2023-03-08 Code/plots.R

@@ -1,0 +1,8 @@
+width <- 10
+graph_bts(t, width, df_mu)
+
+width <- 10
+graph_bts(t, width, df_sigma)
+
+width <- 10
+graph_bts(t, width, df_phi)

### 2023-03-08 Code/simulation.R

@@ -1,110 +1,13 @@
-```{r functions}
-## This note checks the empirical coverage rate of CIs constructed from
-## block bootstrap with series generated from an AR process
-
-mystat <- function(x) {
-    c(mean(x),
-      sd(x),
-      cor(x[-1], x[-length(x)]))
-      # acf(x, lag.max = 1, plot = FALSE)$acf[2])
-}
-
-do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
-    if (phi == 0) {
-      x <- rnorm(n)
-    }
-    else {
-      x <- arima.sim(list(ar = phi), n = n) * sqrt(1 - phi^2)
-    }
-    bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
-    alpha <- 1 - level
-    
-    
-    ## Percentile interval
-    pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
-    
-    ## Centered interval
-    mbts <- apply(bts$t, 2, mean)
-    crit <- 
-      apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
-    ## alpha/2 and 1 - alpha/2 critical values 
-    ## of pseudo-estimate - mean of pseudo-estimates
-    # crit2 <- 
-    #  apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
-    ## alpha/2 and 1 - alpha/2 critical values 
-    ## of pseudo-estimate - original estimate
-  
-    ## interval centered around...
-    estCI <- sweep(crit, 2, bts$t0, FUN = '+') # original estimate
-    ## LB: bts$t0 + alpha/2 crit, UB: bts$t0 + (1 - alpha/2) crit
-    # mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
-    ## LB: mbts + alpha/2 crit2, UB: mbts + (1 - alpha/2) crit2
[…]

### 2023-03-09 Manuscript/manuscript.tex
Few Manuscript Chagnes

@@
 simulated with the tsboot function from the R boot package \citep{boot}
-\citep{davison}. In this study, $\theta$ is composed of the target parameters
+\citep{davison1997bootstrap}. In this study, $\theta$ is composed of the target parameters
 $\mu = 0$, $\sigma_{x}$, and $\phi$. The sample mean $\bar{x}$ can be used as
@@
 a function that will apply each statistic to the original sample and to each
-bootstrapped pseudo-sample. From a sample of length $n$, two types of block
+bootstrapped pseudo-sample. From a sample of length $n$, three types of block
 bootstrap 95\% confidence intervals can be constructed for each target
 parameter:
-$CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.
+Percentile, $\hat{\theta}_{n}$-Centered,
+and $BC_a$.
 
-Each of these 6 intervals either recovers $\theta$ or does not. Remember that
+Each of these 9 intervals either recovers $\theta$ or does not. Remember that
 95\% of many of a certain type of 95\% confidence intervals constructed from
@@
 
-The figures below were created using the R ggplot2 package \citep{ggplot2}.
+The figures below which are grouped by the target $\theta$  were created using
+the R ggplot2 package \citep{ggplot2}.
+
 \begin{figure}[tbp]
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_n.4}
-  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as
-    $n = 100$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as
-    $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there
-    is no clear pattern of deterioration of coverage, so one can expect that
-    increasing $n$ will eventually result in proper coverage of $\sigma$.
-    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, and this
-    is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly
-    under-covers $\phi$, and there is a clear pattern of deterioration of
-    coverage.}
-  \label{fig:plot_n.4}
+  \includegraphics[width=\textwidth]{figures/plot_mu}
+  \caption{At $\phi = -.4, -.2$, all intervals seem to cover $\mu$ correctly
+    as low as $n = 100$. At $\phi = 0$, an $n$ of 500 seems large enough to
+    cover $\mu$ acceptably regardless of interval type. At $\phi = .2$,
+    $n = 300$ seems to be sufficient to appropriately recover $\mu$ for all
+    intervals. A much larger $n$ seems to be necessary to recover $\mu$ at a
+    $\phi$ as high as $.4$.}
+  \label{fig:plot_mu}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_n.2}
-  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as
-    $n = 100$. Both intervals seem to cover $\sigma$ generally well, although
-    $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
-    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
-    coverage, and this is true as low as $n = 200$.
-    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a
-    clear coverage deterioration trend as $n$ increases.}
-  \label{fig:plot_n.2}
+  \includegraphics[width=\textwidth]{figures/plot_sigma}
+  \caption{At $\phi = -.4$, the percentile and the
+    $\hat{\theta}_{n}$-centered intervals recovered $\mu$ well as low as
+    $n = 400$, whereas the $BC_a$ interval undercovered $\mu$ for all $n$
+    observed. At $\phi = -.2$, the percentile and the
+    $\hat{\theta}_{n}$-centered intervals recovered $\mu$ well as low as
+    $n = 500$, but the $BC_a$ coverage rates were lower.}
+  \label{fig:plot_sigma}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_0}
-  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as
-    $n = 500$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as 
-    $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but
-    there is no clear pattern of deterioration of coverage, so one can expect
-    that increasing $n$ will eventually result in proper coverage of $\sigma$.
-    $CI_{\hat{\theta}_{n}}$ seems to cover $\phi$ generally well at $n = 400$,
-    but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the
-    method's performance seems to improve as $n$ increases.}
-  \label{fig:plot_0}
+  \includegraphics[width=\textwidth]{figures/plot_phi}
+  \caption{}
+  \label{fig:plot_phi}
 \end{figure}
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_.2}
-  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as
-    $n = 300$. Both intervals seem to cover $\sigma$ generally well, although
-    $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
-    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
-    coverage, and this is true as low as $n = 200$.
-    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no
-    clear coverage deterioration trend as $n$ increases.}
-  \label{fig:plot_.2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_.4}
-  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well
-    as low as $n = 400$. $CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low
-    as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but
-    there is no clear sign of coverage deterioration, so one can expect that
-    increasing $n$ will eventually result in proper coverage of $\sigma$.
-    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
-    coverage, and this is true as low as $n = 200$.
-    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear
-    coverage deterioration trend as $n$ increases.}
-  \label{fig:plot_.4}
-\end{figure}
-
-As shown in the above figures, only $CI_{\hat{\theta}_{n}}$ managed to solve
-the deterioration problem with respect to recovering $\phi$, indicating that
-this interval should be used as opposed to the more complex
-$CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$. Increasing $n$ will not
-fix the performance of $CI_{BCA, \hat{\theta}_{n}}$ because the assumption that
-the coverage rate will approach an upper limit of .95 as $n$ increases is
-invalid. As expected for $CI_{\hat{\theta}_{n}}$, a higher $\phi$ demands a
+As shown in the above figures, only $\hat{\theta}_{n}$-centered intervals
+managed to solve the deterioration problem with respect to recovering $\phi$,
+indicating that this interval should be used as opposed to the uncentered
+percentile interval or the more complex $BC_a$ interval when estimating
+$\phi$. Increasing $n$ will not fix the performance of either of these
+intervals because the assumption that the coverage rate will approach an upper
+limit of .95 as $n$ increases is invalid. As expected for
+$\hat{\theta}_{n}$-centered intervals, a higher positive $\phi$ demands a
 larger $n$ to estimate all parameters, but a negative $\phi$ may require a
@@
 in this study, this assumption was found to hold true with respect to
-estimating $\phi$ only for $CI_{\hat{\theta}_{n}}$, whereas
-$CI_{BCA, \hat{\theta}_{n}}$ exhibited coverage deterioration as $n$
-increased. When using $CI_{\hat{\theta}_{n}}$ and $\phi$ is unknown, the
-results of this study suggest that an $n$ of around 500 may be necessary to
-estimate $\mu$, and an $n$ of around 400 may be necessary to estimate
-$\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to estimate
-these parameters. When $\phi$ was negative, a $n$ of around 100 was sufficient
-to estimate $\mu$. However, in real world applications, $\phi$ is more
-commonly found to be positive, so a larger $n$ is more likely to be necessary.
-Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary. This
-information could prove to be useful for researching using block bootstrap
+estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
+percentile $BC_a$ intervals exhibited coverage deterioration as $n$
+increased. When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
+unknown, the results of this study suggest that an $n$ of around 500 may be
+necessary to estimate $\mu$, and an $n$ of around 400 may be necessary to
+estimate $\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to
+estimate these parameters. When $\phi$ was negative, a $n$ of around 100 was
+sufficient to estimate $\mu$. However, in real world applications, $\phi$ is
+more commonly found to be positive, so a larger $n$ is more likely to be
+necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
+This information could prove to be useful for researching using block bootstrap
 estimation of time series in domains such as econometrics. Future studies

### 2023-03-09 Code/plots.R

@@ -1,8 +1,11 @@
+t <- 'mu'
 width <- 10
 graph_bts(t, width, df_mu)
 
+t <- 'sigma'
 width <- 10
 graph_bts(t, width, df_sigma)
 
+t <- 'phi'
 width <- 10
 graph_bts(t, width, df_phi)

### 2023-03-10 Manuscript/manuscript.tex
structure for section 2

@@
 
-\title{How Large a Sample Size is Needed for Block Bootstrap Confidence
-  Intervals
-  to Have Desired Coverage Rates?}
+\title{On Sample Size for Block Bootstrap Confidence Intervals 
+  to Have Desired Coverage Rates}
 
@@
 % {\nolinkurl{mathew.chandy@uconn.edu}}\\
-  \and Jun Yan\\[1ex]
+  and Jun Yan\\[1ex]
   Department of Statistics, University of Connecticut\\
@@
 autocorrelation coefficient. We compare three variants of block bootstrap
-confidence intervals from the literature \citep{diciccio1996bootstrap}
-\citep{rice2006mathematical}: a basic percentile interval, a percentile
-interval centered around the original estimate, and a bias-corrected and
+confidence intervals from the literature \citep{diciccio1996bootstrap,
+  rice2006mathematical}: a basic percentile interval, a percentile
+interval centered around the estimate, and a bias-corrected and
 accelerated ($BC_a$) interval also centered around the original estimate. Their
@@
 
-\jy{set up notations for sample; give the algorithm to perform bootstrap
-  procedure}
+Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
+Our goal is to construct a confidence intervals for a parameter $\theta$ in the
+data generating model of the series. Suppose that $\hat\theta_n$ is a point
+estimator of~$\theta$ based on the observed series. Bootstrap is a powerful
+approach to construct confidence intervals. If the observations in the series
+were independent, a standard nonparametric bootstrap procedure would draw a
+large number~$B$ bootstrap copies of the observed data, and calculate an
+estimate $\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. The uncertainty
+of $\hat\theta_n$ is then estimated by the empirical uncertainty of the
+$\hat\theta_n^{(b)}$'s. When serial dependence is present, the bootstrap
+procedure needs to preserve the serial dependence. Block bootstrap was motivated
+for this situation.
 
-\jy{two subsections: 1) block bootstrap basics; 2) bootstrap CIs. The different
-  CIs should each take a paragraph.}
+\subsection{Draw a Block Bootstrap Sample}
 
-\jy{Needs to distinguish the basic percentile bootstrap and corrected percentile
-  bootstrap. Recall that we had trouble covering phi using the basic percentile
-  method.}
+\jy{Paragraph: describe how to construct one non-overlapping block bootstrap
+  sample.}
+
+\jy{Paragraph: describe how to construct one overlapping block bootstrap.}
+
+\jy{Paragraph: comment on selection block size;
+  mention that the two procedures are both valid with similar performance (cite
+  references to support the claim).}
+
+\subsection{Construct Confidence Intervals}
+
+Suppose that we have repeated the steps in the last subsection $B$ times, and
+that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
+$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
+that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
+Now the question is, how to construct confidence intervals for $\theta$
+using the $B$ bootstrap point estimates
+$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.
+
+\jy{Paragraph: bascic percentiles; use the terminologies in the literature.}
+
+\jy{Paragraph: centered.}
+
+\jy{Paragraph: BCa}
 

### 2023-03-10 Manuscript/manuscript.tex
comments/edits on simulation and conclusion

@@
 
-The Base R stats package has a built in function arima.sim that allows one to
-simulate an AR(1) process, for which one can set the theoretical $\phi$
-\citep{R}. By default, the mean of the process $\mu$ is 0 and the standard
-deviation of the error term $\sigma_{\epsilon}$ is 1. For the purposes of this
-study, the standard deviation of the process $\sigma_{x}$ should be controlled
-at 1. The observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new
-theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
-\begin{align}
-X_{t} &= \epsilon_{t} + \phi X_{t-1};\\
-Var(X_{t}) &= Var(\epsilon_{t} + \phi X_{t-1});\\
-\sigma^2_{x} &= \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\\
-\sigma^2_{x}(1 - \phi^2) &= 1;\\
-\sigma_{x}\sqrt{1 - \phi^2} &= 1.
-\end{align}
-The experimental factor of this study was $\phi$, as the temporal dependence
-affects the performance of block bootstrap.
-$\phi \in \{-0.4 -0.2, 0, 0.2, 0.4\}$.
+We designed a simulation study to compare the performance of the different block
+bootstrap confidence intervals. In particular, we generated time series $X_t$
+from a 1st order auto-regressive (AR1) process:
+\[
+X_t = \phi X_{t-1} + \epsilon_t,
+\]
+where $\phi$ is an auto-regressive coefficient, and $\epsilon_t$ is a series of
+independent errors from a normal distribution with mean zero and variance
+$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
+$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$.
+The series $X_t$ has mean zero and variance
+$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we
+set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
 
-As described in the last section, the block bootstrap method can be used to
-estimate a parameter $\theta$ of an AR(1) process. This method can be
-simulated with the tsboot function from the R boot package \citep{boot}
-\citep{davison1997bootstrap}. In this study, $\theta$ is composed of the target parameters
-$\mu = 0$, $\sigma_{x}$, and $\phi$. The sample mean $\bar{x}$ can be used as
-the statistic to estimate $\mu$, the sample standard deviation $S_x$ can be
-used as the statistic to estimate $\sigma$, and the autocorrelation function
-of the sample at lag 1 $\rho_1$ can be used as the statistic to estimate
-$\phi$. In the R implementation, these three statistics are incorporated into
-a function that will apply each statistic to the original sample and to each
-bootstrapped pseudo-sample. From a sample of length $n$, three types of block
-bootstrap 95\% confidence intervals can be constructed for each target
-parameter:
-Percentile, $\hat{\theta}_{n}$-Centered,
-and $BC_a$.
+Three target parameters of $X_t$ were considered:
+1) $\mu = 0$, the mean of $X_t$;
+2) $\sigma_x^2 = 1$, the variance of $X_t$; and
+2) $\phi$, the lag-1 auto-correlation coefficient.
+To investigate the effect of sample size~$n$, we considered an array of values
+$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we genrated 1000
+replicates. For each replicate, we constructed three 95\% block bootstrap
+confidence intervals for each parameter as described in the last section, and
+estimated their actual coverage rates along with their 95\% confidence
+intervals from the 1000 replicates. The block bootstrap sampling step was done
+with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
+block size \jy{size? also it was overlapping blocks. Describe the details here.}
+The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi}.
+
+\jy{One paragraph for each parameter; write down your observations in bullet
+  points and then organize them into a logically flowing paragraph.}
+
+\jy{One summary paragraph at the end.}
 
@@
 
+\jy{Discussion points:
+  1) common practice on block bootstrap even for simple parameter such as the
+  mean;
+  2) further investigation needed for phi;
+  3) impact on applied statsitics courses; student reactions (Dr. Schifano).
+}
+
 The motivation for the study is the idea that block bootstrap procedure will
@@
 \bibliographystyle{chicago}
-\bibliography{citations}[tp]
+\bibliography{citations}
 

### 2023-03-22 Code/Visualizations.Rmd
Manuscript Update 3/22

@@
 ```
+
+```{r}
+plot(c(0, 1200), c(600, 1400), type= "n", xlab = "", ylab = "")
+xleft = rep(c(200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100), times = 4)
+ybottom = rep(c(1200, 900, 600, 0), each = 10)
+xright = rep(c(300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200), times = 4)
+ytop = rep(c(1400, 1100, 800, 200), each = 10)
+rect(xleft = xleft, ybottom = ybottom, xright = xright, ytop = ytop)
+rect(xleft = c(200, 500, 900), ybottom = c(1200, 900, 600), xright = c(500, 800, 1200), 
+     ytop = c(1400, 1100, 800), col= rgb(1,0,0,alpha=0.25))
+x = rep(c(250, 350, 450, 550, 650, 750, 850, 950, 1050, 1150), times = 4)
+y = rep(c(1300, 1000, 700, 100), each = 10)
+labels = rep(c('X1', 'X2', 'X3', 'X4', 'X5', 'X6', '...', 'Xn-2', 'Xn-1', 'Xn'), times = 4)
+text(x=x, y=y, labels=labels)
+text(x=100, y=1300, labels='Block 1')
+text(x=100, y=1000, labels='Block 2')
+text(x=100, y=700, labels='Block n/l')
+```
+
+```{r}
+plot(c(0, 1200), c(0, 1400), type= "n", xlab = "", ylab = "")
+rect(xleft = xleft, ybottom = ybottom, xright = xright, ytop = ytop)
+rect(xleft = c(200, 300, 400, 200, 1100), ybottom = c(1200, 900, 600, 0, 0), xright = c(500, 600, 700, 400, 1200), ytop = c(1400, 1100, 800, 200, 200), col= rgb(1,0,0,alpha=0.25))
+labels = rep(c('X1', 'X2', 'X3', 'X4', 'X5', 'X6', '...', 'Xn-2', 'Xn-1', 'Xn'), times = 4)
+text(x=x, y=y, labels=labels)
+text(x=100, y=1300, labels='Block 1')
+text(x=100, y=1000, labels='Block 2')
+text(x=100, y=700, labels='Block 3')
+text(x=100, y=100, labels='Block n')
+```

### 2023-03-22 Manuscript/manuscript.tex
Manuscript Update 3/22

@@
 $\hat\theta_n^{(b)}$'s. When serial dependence is present, the bootstrap
-procedure needs to preserve the serial dependence. Block bootstrap was motivated
-for this situation.
+procedure needs to preserve the serial dependence. Block bootstrap was
+motivated for this situation.
 
@@
 
+The designer of the study can choose whether the blocks overlap or not. If the
+blocks do not overlap, it is called non-overlapping or non-moving block
+bootstrap. In this case, blocks are resample randomly from the set of all
+non-overlapping blocks of size $l$. For non-moving block bootstrap, $l \vert n$
+must always be true. In this case, a set of $n / l$ non-overlapping blocks of
+size $l$ is constructed from the original sample. The set would take the form:
+$\{[X_1, ..., X_l], [X_{l+1}, ..., X_{2l}], ..., [X_{n-l+1}, X_n]\}$. Each
+bootstrapped pseudo-sample is created by sampling $n / l$ blocks with
+replacement from the same set.
+
 \jy{Paragraph: describe how to construct one overlapping block bootstrap.}
+
+If the blocks do overlap, it is called overlapping or moving block bootstrap.
+In this case, blocks are resampled randomly from the set of all possible
+blocks of size $l$. For moving block bootstrap, $l \vert n$ is not a necessary
+condition. The set of available blocks is created by iterating through each
+observation $i$ in the original sample and adding to the set the block of size
+$l$ that begins with $i$. This set can limited to blocks that end with an
+$i <= n$, meaning that $n - l + 1$ blocks are available to resample from. This
+set takes the form:
+$\{[X_1, ..., X_l], [X_2, ..., X_{l+1}], ..., [X_{n-l+1}, X_n]\}$. 
+The set can also include blocks that ``wrap around'': in
+other words, blocks that end with a lesser index than the index they began
+with, meaning that $n$ blocks are available to resample from. This set takes
+the form:
+$\{[X_1, ..., X_l], [X_2, ..., X_{l+1}], ..., [X_n, X_{l-1}]\}$.
+If $l \vert n$,
+a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks
+from the set with replacement to create a new pseudo-sample of size $n$. If
+$l does not divide n$, the last block selected will be reduced in size so that
+the final size of the pseudo-sample is $n$. Moving block bootstrap was used in
+this study as it has been found to yield the lowest error in general
+\citep{radovanov2014comparison}. The larger set of available blocks was used.
 
@@
   references to support the claim).}
+
+The block should be of size $l$ large enough for each
+pseudo-sample to exhibit some temporal dependence, yet small enough for there
+to be some variability between each pseudo-sample. Ideally, as $n$ increases,
+$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
+often assigned a value as a function of $n$. A common function that is
+considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
+\citep{buhlmann1999block}.
 
@@
 
-\jy{Paragraph: bascic percentiles; use the terminologies in the literature.}
+\jy{Paragraph: basic percentiles; use the terminologies in the literature.}
+
+In this study, 1000 $\hat\theta_n^{(b)}$ were created for one simulation of
+block bootstrap estimation. Using this distribution of $\hat\theta_n^{(b)}$,
+several variants of a $1 - \alpha$/2 \% confidence interval for the parameter
+can be constructed. The most simplistic method for constructing this interval
+is the basic percentile confidence interval. For a parameter $\theta$, the
+percentile $1 - \alpha$/2 \% confidence interval takes the form:
+\[ [\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}].\]
+
+This interval works well when attempting to recover the mean and
+standard deviation of a temporally dependent process, but its coverage of
+the temporal dependence deteriorates as $n$ increases.
 
@@
 
-\jy{Paragraph: BCa}
-
-Block bootstrap is a method that can be used to estimate a parameter of
-serially dependent data. Suppose that one wants to estimate a parameter or
-parameters $\theta$ of a population. The first step is to generate a sample of
-length $n$ from the population. An estimate of the parameter
-$\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate
-$\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample. The mean
-$\bar\theta_n^*$ of many replicate $\hat\theta_n^*$ can also be computed.
-Lastly, for each $\hat\theta_n^*$, $\delta^* = \hat\theta_n^* -
-\bar\theta_n^*$ can be computed.
-
-In basic bootstrap procedure, the new pseudo-sample of size $n$ would be
-created by simply resampling observations from the original sample with
-replacement. However, in the case of a time series, in order to account for
-the temporal dependence, the time series can be split into blocks, typically
-of the same size. The block should be of size $l$ large enough for each
-pseudo-sample to exhibit some temporal dependence, yet small enough for there
-to be some variability between each pseudo-sample. Ideally, as $n$ increases,
-$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
-often assigned a value as a function of $n$. A common function that is
-considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
-\citep{buhlmann1999block}.
-
-The designer of the study can choose whether the blocks overlap or not. If the
-blocks do not overlap, it is called non-overlapping or non-moving block
-bootstrap. In this case, blocks are resample randomly from the set of all
-non-overlapping blocks of size $l$. For non-moving block bootstrap, $l \vert n$
-must always be true. In this case, a set of $n / l$ non-overlapping blocks of
-size $l$ is constructed from the original sample. Each bootstrapped
-pseudo-sample is created by sampling $n / l$ blocks with replacement from the
-same set.
-
-If the blocks do overlap, it is called overlapping or moving block bootstrap.
-In this case, blocks are resampled randomly from the set of all possible
-blocks of size $l$. For moving block bootstrap, $l \vert n$ is not a necessary
-condition. The set of available blocks is created by iterating through each
-observation $i$ in the original sample and adding to the set the block of size
-$l$ that begins with $i$. This set can limited to blocks that end with an
-$i <= n$, meaning that $n - l + 1$ blocks are availabe to resample from, or it
-can be expanded to include blocks that ``wrap around'': in
-other words, blocks that end with a lesser index than the index they began
-with, meaning that $n$ blocks are available to resample from. If $l \vert n$,
-a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks
-from the set with replacement to create a new pseudo-sample of size $n$. If
-$l does not divide n$, the last block selected will be reduced in size so that
-the final size of the pseudo-sample is $n$. Moving block bootstrap was used in
-this study as it has been found to yield the lowest error in general
-\citep{radovanov2014comparison}. The set of available was not limited as
-described above.
-
-An estimate $\hat\theta_n^*$ is computed from the pseudo-sample. This
-procedure can be repeated many times to create a distribution of
-$\hat\theta_n^*$.
-
-In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block
-bootstrap estimation. Using this distribution of $\hat\theta_n^*$, several
-variants of a $1 - \alpha$/2 \% confidence interval for the parameter can be
-constructed. The most simplistic method for constructing this interval is the
-basic percentile confidence interval. For a parameter $\theta$, the percentile
-$1 - \alpha$/2 \% confidence interval takes the form: 
-\[ [\hat\theta_{n, \alpha/2}^*, \hat\theta_{n, 1 - \alpha/2}^*].\]
-
-This interval works well when attempting to recover the mean and
-standard deviation of a temporally dependent process, but its coverage of
-the temporal dependence deteriorates as $n$ increases. A potential solution to
+A potential solution to
 this issue is to center the intervals around $\hat{\theta}_{n}$. To do this,
@@
   \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]
+
+\jy{Paragraph: BCa}
 
@@
 Where $z_0$ is the quantile function of the proportion of
-$\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness (computed using
+$\hat\theta_n^{(b)} < \bar\theta_n^{(b)}$, and $a$ is the skewness (computed
+using
 the skewness function from the R e1071 package \citep{e1071}) of
@@
 
-We designed a simulation study to compare the performance of the different block
+We designed a simulation study to compare the performance of the different
+block
 bootstrap confidence intervals. In particular, we generated time series $X_t$
@@
 The series $X_t$ has mean zero and variance
-$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we
+$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$,
+we
 set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
@@
 To investigate the effect of sample size~$n$, we considered an array of values
-$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we genrated 1000
+$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 1000
 replicates. For each replicate, we constructed three 95\% block bootstrap
@@
 with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
-block size \jy{size? also it was overlapping blocks. Describe the details here.}
-The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi}.
+block size $\lceil n / l \rceil$. This function by default is an implementation
+of moving block bootstrap as described in the previous section.
+\jy{size? also it was overlapping blocks. Describe the details here.}
+The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
+these figures were generated using the using
+the R ggplot2 package \citep{ggplot2}.
 
-\jy{One paragraph for each parameter; write down your observations in bullet
-  points and then organize them into a logically flowing paragraph.}
-
-\jy{One summary paragraph at the end.}
-
-Each of these 9 intervals either recovers $\theta$ or does not. Remember that
+Each interval either recovers $\theta$ or does not. Remember that
 95\% of many of a certain type of 95\% confidence intervals constructed from
@@
 
-The figures below which are grouped by the target $\theta$  were created using
-the R ggplot2 package \citep{ggplot2}.
+\jy{One paragraph for each parameter; write down your observations in bullet
+  points and then organize them into a logically flowing paragraph.}
+
+- For mu, performance looks about the same regardless of interval type.
+- When phi is negative, n = 100 seems large enough.
+- When phi is zero, n = 500 is large enough.
+- When phi is 0.2, n = 300
+- When phi is 0.4, a much larger n seems to be necessary
+
+Based on \ref{fig:mu}, performance is
+about the same for the three interval types studied. When $\phi < 0$,
+$n = 100$ seems to  be large enough to cover $\mu$ at the nominal rate. When
+$\phi = 0$, or in other other words, the sample is from a normal distribution,
+$n = 500$ seems to be large enough to cover $\mu$ at the nominal rate. Samples
+from processes with $\phi > 0$ appear to require a larger $n$ than samples from
+processes with $\phi < 0$. When $\phi = 0.2$, $n = 300$ seemed to be necessary
+for adequate performance, and when $\phi = 0.4$, an even larger $n$ appeared
+to be necessary to properly cover $\mu$. It is rare for $\phi$ to be so high,
+so in most cases, if $\phi$ is unknown, a sample of $n \geq 500$ should be
+used when the target parameter is $\mu$.
+
+- For sigma, coverage looks lower for BCa, whereas percentile and centered
+look about the same.
+- For percentile and centered intervals, n = 400 looks enough when phi = -0.4.
+- When phi = -0.2, n = 500 seems to be necessary for percentile and centered
+intervals.
+- When phi = 0, n = 400 seems to be necessary for percentile and centered
+intervals.
+- When phi = 0.2, n = 300 seems to be necessary...
+- When phi = 0.4, n = 400 seems to be necessary...
+
+Based on \ref{fig:sigma}, coverage is
+notably lower for $BC_a$ intervals, but $\hat{\theta}_{n}$-centered intervals
+and basic intervals have similar performance. For these two interval types,
+$n = 500$ seems to be necessary to cover $\sigma$ at the nominal rate when
+$\phi < 0$. If $\phi = 0$, $n = 400$ seems to large enough to cover $\sigma$ at
+the nominal rate. If $\phi = 0.2$, $n = 300$ seems large enough, but if the
+process has a greater $\phi$ of $0.4$, $n = 400$ may be necessary. It is more
+common for $\phi$ to be $> 0$ in applied analysis, so in most cases, if $\phi$
+is unknown, using a sample of $n \geq 400$ should be sufficient for estimation
+of $\sigma$.
+
+- BCa and percentile deteriorate in coverage as n increases, except for when
+phi = 0.
+- BCa coverage is very bad when absolute value of phi is high.
+- Percentile coverage is not as bad
+- n = 200 seems to be enough for centered interval, regardless of phi.
+
+When block bootstrap is used to estimate $\phi$ using $BC_a$ and percentile
+intervals, the assumption that coverage rates asymptotically approach the
+nominal rate as $n$ increases appears to be invalid based on \ref{fig:sigma}.
+The $BC_a$ interval performs very poorly and deteriorates more noticeable
+when the absolute value $\phi$ gets
+higher, but even when $\phi = 0$, $\phi$ is still undercovered for $n$ as high
+as $700$. Like the $BC_a$ interval, the percentile interval deteriorates in
+coverage when $\phi$ is high, although the coverage is not as low.
+Interestingly, when $\phi = 0$, the percentile interval appears to actually
+over-cover $\phi$. These results suggest that $BC_a$ and basic percentile
+block bootstrap intervals should not be used estimate temporal dependence
+factors of time series. On the other hand, $\hat{\theta}_{n}$-centered
+intervals seem to recover $\phi$ correctly as long as $n >= 200$, and this
+appears to be true regardless of $\phi$, although a greater $\phi$ may result
+in a decline in performance.
+
+\jy{One summary paragraph at the end.}
+
+To summarize, the interval type chosen should be based on the target parameter.
+For estimating $\mu$, any of the three interval types can be used, but for
+$\sigma$, only $\hat{\theta}_{n}$-centered and basic percentile intervals
+should be used, and only $\hat{\theta}_{n}$-centered intervals should be used
+for $\phi$. When estimating
+$\mu$, $n = 500$ should be large enough in situations where $\phi$ is unknown.
+When estimating $\sigma$, $n = 400$ is sufficient is situations where $\phi$ is
+unknown. If $\phi$ is known, a lesser $n$ may be adequate. When estimating
+$\phi$, $n = 200$ is large enough when using the correct type of interval.
 
@@
   \includegraphics[width=\textwidth]{figures/plot_mu}
-  \caption{At $\phi = -.4, -.2$, all intervals seem to cover $\mu$ correctly
-    as low as $n = 100$. At $\phi = 0$, an $n$ of 500 seems large enough to
-    cover $\mu$ acceptably regardless of interval type. At $\phi = .2$,
-    $n = 300$ seems to be sufficient to appropriately recover $\mu$ for all
-    intervals. A much larger $n$ seems to be necessary to recover $\mu$ at a
-    $\phi$ as high as $.4$.}
-  \label{fig:plot_mu}
+  \caption{Plots of $\mu$ coverage rates for each interval type and $\phi$
+    combination. The orange dotted line represents the 95\% nominal coverage
+    rate. The error bars represent a 95\% confidence interval for the coverage
+    proportion out of 1000 replications for each $n$. Results from $n$
+    ranging from 100-700 were recorded.}
+  \label{fig:mu}
 \end{figure}
@@
   \includegraphics[width=\textwidth]{figures/plot_sigma}
-  \caption{At $\phi = -.4$, the percentile and the
-    $\hat{\theta}_{n}$-centered intervals recovered $\mu$ well as low as
-    $n = 400$, whereas the $BC_a$ interval undercovered $\mu$ for all $n$
-    observed. At $\phi = -.2$, the percentile and the
-    $\hat{\theta}_{n}$-centered intervals recovered $\mu$ well as low as
-    $n = 500$, but the $BC_a$ coverage rates were lower.}
-  \label{fig:plot_sigma}
+  \caption{Plots of $\sigma$ coverage rates for each interval type and $\phi$
+    combination. The orange dotted line represents the 95\% nominal coverage
+    rate. The error bars represent a 95\% confidence interval for the coverage
+    proportion out of 1000 replications for each $n$. Results from $n$
+    ranging from 100-700 were recorded.}
+  \label{fig:sigma}
 \end{figure}
@@
   \includegraphics[width=\textwidth]{figures/plot_phi}
-  \caption{}
-  \label{fig:plot_phi}
+  \caption{Plots of $\phi$ coverage rates for each interval type and $\phi$
+    combination. The orange dotted line represents the 95\% nominal coverage
+    rate. The error bars represent a 95\% confidence interval for the coverage
+    proportion out of 1000 replications for each $n$. Results from $n$
+    ranging from 100-700 were recorded.}
+  \label{fig:phi}
 \end{figure}
@@
 
+Block bootstrap method is a useful method for estimating parameters of a time
+series: from simple parameters like the mean to temporal dependence factors.
 The motivation for the study is the idea that block bootstrap procedure will
@@
 unknown, the results of this study suggest that an $n$ of around 500 may be
-necessary to estimate $\mu$, and an $n$ of around 400 may be necessary to
+necessary for common practice to estimate a simple parameter like $\mu$, and
+an $n$ of around 400 may be necessary to
 estimate $\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to
@@
 necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
+Further investigation may be necessary to see if there are other interval
+corrections that fix the coverage deterioration problem for $\phi$.
+This study could be used as a guide for applied statistics courses for students
+to generally understand how large of a sample size is sufficient for block
+bootstrap to be used versus other inference methods.
 This information could prove to be useful for researching using block bootstrap
@@
 \end{document}
+
+BBOB

### 2023-03-24 Manuscript/manuscript.tex
edits/comments on methods

@@
 
-\jy{turn on the column number mode of your editor. Keep the width to under 80.}
-
 \section{Introduction}
@@
 
-Block bootstrap is a powerful tool for constructing confidence intervals when
-making inferences about dependent data. Early ideas were developed
+Block bootstrap is a powerful tool for constructing confidence intervals (CI)
+when making inferences about dependent data. Early ideas were developed
 independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
@@
 data when the serial dependence is not specified or not of primary interest.
-The method is expected to produce confidence intervals with coverage rates
+The method is expected to produce CIs with coverage rates
 matching their nominal levels as the sample size grows to infinity. However,
 when dealing with finite sample sizes, an important question is how large the
-sample size needs to be for block bootstrap confidence intervals to have the
+sample size needs to be for block bootstrap CIs to have the
 desired coverage rates.
@@
 independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
-that while percentile-based confidence intervals from nonparametric bootstrap
+that while percentile-based CIs from nonparametric bootstrap
 are more accurate than $t$-intervals for larger sample sizes, they are
@@
 inference from closed-form asymptotic estimates, but block bootstrap percentile
-confidence intervals still do not have sufficient coverage even for sample size
+CIs still do not have sufficient coverage even for sample size
 $n = 1024$.
@@
 autocorrelation coefficient. We compare three variants of block bootstrap
-confidence intervals from the literature \citep{diciccio1996bootstrap,
+CIs from the literature \citep{diciccio1996bootstrap,
   rice2006mathematical}: a basic percentile interval, a percentile
@@
 The remainder of the papers is organized as follows:
-The Block Bootstrap Confidence Intervals section reviews how these intervals
+The Block Bootstrap CIs section reviews how these intervals
 are constructed as well as the general procedure for block bootstrap parameter
@@
 
-\section{Block Bootstrap Confidence Intervals}
+\section{Block Bootstrap CIs}
 \label{sec:blkbootreview}
@@
 Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
-Our goal is to construct a confidence intervals for a parameter $\theta$ in the
+Our goal is to construct a CIs for a parameter $\theta$ in the
 data generating model of the series. Suppose that $\hat\theta_n$ is a point
 estimator of~$\theta$ based on the observed series. Bootstrap is a powerful
-approach to construct confidence intervals. If the observations in the series
+approach to construct CIs. If the observations in the series
 were independent, a standard nonparametric bootstrap procedure would draw a
@@
 
-\subsection{Draw a Block Bootstrap Sample}
+\subsection{Block Bootstrap Sample}
 
-\jy{Paragraph: describe how to construct one non-overlapping block bootstrap
-  sample.}
+Block bootstrap preserves the serial dependence in the observed data by
+partitioning the data into blocks and perform bootstrap on the blocks.
+In particular, consider block size~$l$ and, for convenience, suppose that
+$n$ is a multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$
+is $Y_j = \{X_{(j - 1) * l + 1}, \ldots, X_{(j - 1) * l + l}\}$,
+$j = 1, \ldots,   k$.  Then, we sample $k$ blocks of $Y_j$'s from the set 
+$\{Y_1, \ldots, Y_k\}$ with replacement and concatenate the $k$ sampled blocks
+in the order they are picked to form a bootstrap sample of the data. The
+formation of the bootstrap sample ensures that the between-block dependence is
+week and that the within-block serial dependence is preserved. Because the
+blocks here are non-overlapping, this bootstrap approach is known as
+non-overlapping block bootstrap, or simple block bootstrap.
 
-The designer of the study can choose whether the blocks overlap or not. If the
-blocks do not overlap, it is called non-overlapping or non-moving block
-bootstrap. In this case, blocks are resample randomly from the set of all
-non-overlapping blocks of size $l$. For non-moving block bootstrap, $l \vert n$
-must always be true. In this case, a set of $n / l$ non-overlapping blocks of
-size $l$ is constructed from the original sample. The set would take the form:
-$\{[X_1, ..., X_l], [X_{l+1}, ..., X_{2l}], ..., [X_{n-l+1}, X_n]\}$. Each
-bootstrapped pseudo-sample is created by sampling $n / l$ blocks with
-replacement from the same set.
-
-\jy{Paragraph: describe how to construct one overlapping block bootstrap.}
-
-If the blocks do overlap, it is called overlapping or moving block bootstrap.
-In this case, blocks are resampled randomly from the set of all possible
-blocks of size $l$. For moving block bootstrap, $l \vert n$ is not a necessary
-condition. The set of available blocks is created by iterating through each
-observation $i$ in the original sample and adding to the set the block of size
-$l$ that begins with $i$. This set can limited to blocks that end with an
-$i <= n$, meaning that $n - l + 1$ blocks are available to resample from. This
-set takes the form:
-$\{[X_1, ..., X_l], [X_2, ..., X_{l+1}], ..., [X_{n-l+1}, X_n]\}$. 
-The set can also include blocks that ``wrap around'': in
-other words, blocks that end with a lesser index than the index they began
-with, meaning that $n$ blocks are available to resample from. This set takes
-the form:
-$\{[X_1, ..., X_l], [X_2, ..., X_{l+1}], ..., [X_n, X_{l-1}]\}$.
-If $l \vert n$,
-a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks
-from the set with replacement to create a new pseudo-sample of size $n$. If
-$l does not divide n$, the last block selected will be reduced in size so that
-the final size of the pseudo-sample is $n$. Moving block bootstrap was used in
+Alternatively, block-bootstrap can be done with overlapping or moving blocks.
+Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
+$j = 1, \ldots, n - b + 1$. Now we draw $k$ blocks from the $(n - b + 1)$ blocks
+of $Z_j$'s with replacement and then aligning them in the order they were picked
+to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
+block selected will be reduced in size so that the final size of the
+block bootstrap sample is $n$. Moving block bootstrap was used in
 this study as it has been found to yield the lowest error in general
 \citep{radovanov2014comparison}. The larger set of available blocks was used.
+\jy{what does the last sentence mean?}
 
-\jy{Paragraph: comment on selection block size;
-  mention that the two procedures are both valid with similar performance (cite
-  references to support the claim).}
-
-The block should be of size $l$ large enough for each
-pseudo-sample to exhibit some temporal dependence, yet small enough for there
-to be some variability between each pseudo-sample. Ideally, as $n$ increases,
+The block size~$l$ needs to chosen with care. It needs to be large enough for
+each bootstrap sample to preserve the serial dependence, yet small enough for
+there to be some variability between each bootstrap sample. As $n$ increases,
 $l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
@@
 
-\subsection{Construct Confidence Intervals}
+\subsection{Construct CIs}
 
@@
 that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
-Now the question is, how to construct confidence intervals for $\theta$
+Now the question is, how to construct CIs for $\theta$
 using the $B$ bootstrap point estimates
 $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.
+We consider three kinds of CIs.
 
-\jy{Paragraph: basic percentiles; use the terminologies in the literature.}
+\paragraph{Percentile CI}
+Let $\hat\theta_{n, B, \alpha}$ be the empirical $100\alpha$th percentile of
+$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
+empirical percentile CI is
+\[
+(\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}).
+\]
+This CI is not necessarily centered by the point estimator $\hat\theta_n$.
+%% Not the right place
+%% This interval works well when attempting to recover the mean and
+%% standard deviation of a temporally dependent process, but its coverage of
+%% the temporal dependence deteriorates as $n$ increases.
 
-In this study, 1000 $\hat\theta_n^{(b)}$ were created for one simulation of
-block bootstrap estimation. Using this distribution of $\hat\theta_n^{(b)}$,
-several variants of a $1 - \alpha$/2 \% confidence interval for the parameter
-can be constructed. The most simplistic method for constructing this interval
-is the basic percentile confidence interval. For a parameter $\theta$, the
-percentile $1 - \alpha$/2 \% confidence interval takes the form:
-\[ [\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}].\]
+\paragraph{Centered Percentile CI}
+Centered percentile CI is centered at the point estimator and uses the variation
+in the bootstrap estimates to construct the error bound. A $(1 - \alpha)$ CI is
+\[
+(\hat{\theta}_{n} + \delta^*_{\alpha/2},
+\hat{\theta}_{n} + \delta^*_{1 - \alpha/2}).
+\]
+\jy{Define $\delta^*$?}
+\jy{Say a few words about its properties}
 
-This interval works well when attempting to recover the mean and
-standard deviation of a temporally dependent process, but its coverage of
-the temporal dependence deteriorates as $n$ increases.
-
-\jy{Paragraph: centered.}
-
-A potential solution to
-this issue is to center the intervals around $\hat{\theta}_{n}$. To do this,
-the distribution of $\delta^*$ should be considered. For a parameter $\theta$,
-the $\hat{\theta}_{n}$-centered $1 - \alpha$/2 \% confidence interval takes
-the form:
-\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2},
-  \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]
-
-\jy{Paragraph: BCa}
-
-An alternative method is a $BC_a$ interval centered around $\hat{\theta}_{n}$.
-For a parameter $\theta$, the $BC_a$ $1 - \alpha$/2 \% confidence interval
-takes the form:
-\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1},
-  \hat{\theta}_{n} + \delta^*_{\alpha_2}].\]
-$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
+\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
+The $1 - \alpha$ \% BCA CI takes the form:
+\[
+(\hat{\theta}_{n} + \delta^*_{\alpha_1},
+\hat{\theta}_{n} + \delta^*_{\alpha_2}),
+\]
+\jy{Not clear and not flowing well. Restructure the writing. Practice my writing tips.}
+where $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
 $z_{2}$, respectively, where:
@@
 original sample computed without the $i^{th}$ block.
-
-Thus, there are three types of intervals that can be constructed for block
-bootstrap estimation in this study: Percentile, $\hat{\theta}_{n}$-Centered,
-and $BC_a$.
+\jy{Say a few words about its properties.}
 
@@
 block
-bootstrap confidence intervals. In particular, we generated time series $X_t$
+bootstrap CIs. In particular, we generated time series $X_t$
 from a 1st order auto-regressive (AR1) process:
@@
 replicates. For each replicate, we constructed three 95\% block bootstrap
-confidence intervals for each parameter as described in the last section, and
+CIs for each parameter as described in the last section, and
 estimated their actual coverage rates along with their 95\% confidence
@@
 \jy{size? also it was overlapping blocks. Describe the details here.}
-The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
-these figures were generated using the using
-the R ggplot2 package \citep{ggplot2}.
 
+\jy{Explain what metric was used to compare their performances. That is, the
+  coverage rates and how it was calculated. If a CI is valid, then the coverages
+  rate is expected to match its nominal level.}
+
+\jy{Make it flow better and conciser}
 Each interval either recovers $\theta$ or does not. Remember that
-95\% of many of a certain type of 95\% confidence intervals constructed from
+95\% of many of a certain type of 95\% CIs constructed from
 samples of the same $n$ should recover $\theta$. To see if this is
@@
 interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
-point estimate of a proportion, so a 95\% confidence interval of this coverage
+point estimate of a proportion, so a 95\% CI of this coverage
 proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
@@
 proper coverage.
+
+The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
+these figures were generated using the using
+the R ggplot2 package \citep{ggplot2}.
 
@@
     combination. The orange dotted line represents the 95\% nominal coverage
-    rate. The error bars represent a 95\% confidence interval for the coverage
+    rate. The error bars represent a 95\% CI for the coverage
     proportion out of 1000 replications for each $n$. Results from $n$

### 2023-03-29 Manuscript/manuscript.tex
Manuscript Update 3/29

@@
 Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
-$j = 1, \ldots, n - b + 1$. Now we draw $k$ blocks from the $(n - b + 1)$ blocks
-of $Z_j$'s with replacement and then aligning them in the order they were picked
+$j = 1, \ldots, n - b + 1$. Now we draw $k$ blocks from the $(n - b + 1)$
+blocks
+of $Z_j$'s with replacement and then aligning them in the order they were
+picked
 to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
@@
 this study as it has been found to yield the lowest error in general
-\citep{radovanov2014comparison}. The larger set of available blocks was used.
+\citep{radovanov2014comparison}.  
 \jy{what does the last sentence mean?}
@@
 \paragraph{Centered Percentile CI}
-Centered percentile CI is centered at the point estimator and uses the variation
-in the bootstrap estimates to construct the error bound. A $(1 - \alpha)$ CI is
+Centered percentile CI is centered at the point estimator and uses the
+variation
+in the bootstrap estimates to construct the error bound. This interval is
+dependent on $\delta^{(b)}$, or the difference between a bootstrap point
+estimate $\hat\theta_n^{(b)}$ and
+the mean of all bootstrap point estimates.
+ A $(1 - \alpha)$ CI is
 \[
-(\hat{\theta}_{n} + \delta^*_{\alpha/2},
-\hat{\theta}_{n} + \delta^*_{1 - \alpha/2}).
+(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2},
+\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
 \]
+This CI is asymmetric, as different critical values are used to compute
+the lower and upper bounds.
 \jy{Define $\delta^*$?}
@@
 \paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
-The $1 - \alpha$ \% BCA CI takes the form:
-\[
-(\hat{\theta}_{n} + \delta^*_{\alpha_1},
-\hat{\theta}_{n} + \delta^*_{\alpha_2}),
-\]
-\jy{Not clear and not flowing well. Restructure the writing. Practice my writing tips.}
-where $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
-$z_{2}$, respectively, where:
+In this study, the BCA CI is an interval centered at the point estimator.
+However, unlike the Centered Percentile CI, which uses the simpler $\alpha/2$
+and $1 - \alpha/2$ critical values, a more complex procedure is used to get
+the critical values for the BCA CI. The first step is to compute $z_0$, the
+quantile function of the proportion of 
+$\hat\theta_n^{(b)} < \hat\theta_n$, and $a$, the skewness (computed
+using
+the skewness function from the R e1071 package \citep{e1071}) of
+$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
+original sample computed without the $i^{th}$ block. From these two values,
 \[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
@@
 \[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
-z_{0}.\]
-Where $z_0$ is the quantile function of the proportion of
-$\hat\theta_n^{(b)} < \bar\theta_n^{(b)}$, and $a$ is the skewness (computed
-using
-the skewness function from the R e1071 package \citep{e1071}) of
-$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
-original sample computed without the $i^{th}$ block.
+z_{0}\] can be computed.
+
+The $1 - \alpha$ \% BCA CI takes the form:
+\[
+(\hat{\theta}_{n} + \delta^{(b)}_{\alpha_1},
+\hat{\theta}_{n} + \delta^{(b)}_{\alpha_2}),
+\]
+\jy{Not clear and not flowing well. Restructure the writing. Practice my
+  writing tips.}
+where $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$
+and
+$z_{2}$, respectively.
+Like the Centered CI, the BCA CI is asymmetric.
+
 \jy{Say a few words about its properties.}
@@
 \jy{Make it flow better and conciser}
-Each interval either recovers $\theta$ or does not. Remember that
-95\% of many of a certain type of 95\% CIs constructed from
-samples of the same $n$ should recover $\theta$. To see if this is
+The coverage rates of the CIs were used to compare the performance of CIs. To
+compute a CI's coverage rate of a target parameter for a certain interval,
+the coverage for each replicate CI must be recorded. If the true value of the
+parameter is greater than the lower bound of the CI and lesser than the upper
+bound, then the CI's coverage for that parameter is assigned a value of 1. If
+this is false, then the CI's coverage for that parameter is assigned a value
+of 0.
+
+Remember that 95\% of many of a certain type of 95\% CIs constructed from
+samples of the same $n$ should recover a target $\theta$. To see if this is
 approximately the case, one can run 1000 replications of the block bootstrap
-procedure, and for each interval-$\theta$ pair, the rate at which that type of
-interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
+procedure, and the proportion of replicate CIs that recover $\theta$ - or the
+mean of the coverages for each replicate CI - can be
+recorded as the coverage rate. The coverage rate is, of course, a
 point estimate of a proportion, so a 95\% CI of this coverage
-proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
-.95 is included in the interval, the block bootstrap method is likely working
+proportion (with $n_{CI} = 1000$) can be constructed. If the proportion
+.95 is included in the interval, the block bootstrap method is likely
+performing
 well. If all values in the interval are below .95, the results suggest that the
@@
 
-To summarize, the interval type chosen should be based on the target parameter.
+To summarize, the CI type chosen should be based on the target parameter.
 For estimating $\mu$, any of the three interval types can be used, but for

### 2023-03-29 Code/functions.R

@@ -87,10 +87,16 @@ mychk <- function(sim, target) {
   ret
 }
 
-df_bts <- function(cov, nrep = 1000, phis = c(-0.4, -0.2, 0, 0.2, 0.4), sizes = c(100, 200, 300, 400, 500, 600, 700), types = c('pctCI', 'estCI', 'bcaCIest'), parameters = c('mu', 'sigma', 'phi')) {
-  phi <- rep(phis, each = length(sizes) * length(types) * length(parameters))
-  n <- rep(sizes, times = length(phis), each = length(types) * length(parameters))
-  CI <- rep(types, times = length(phis) * length(sizes), each = length(parameters))
+df_bts <- function(cov, nrep = 1000, phis = c(-0.4, -0.2, 0, 0.2, 0.4), 
+                   sizes = c(100, 200, 300, 400, 500, 600, 700), 
+                   types = c('pctCI', 'estCI', 'bcaCIest'), 
+                   parameters = c('mu', 'sigma', 'phi')) {
+  phi <- 
+    rep(phis, each = length(sizes) * length(types) * length(parameters))
+  n <- 
+    rep(sizes, times = length(phis), each = length(types) * length(parameters))
+  CI <- 
+    rep(types, times = length(phis) * length(sizes), each = length(parameters))
   t <- rep(parameters, times = length(phis) * length(types) * length(sizes))
   LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
   UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
@@ -103,10 +109,14 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
   library(latex2exp)
   library(ggplot2)
   
+  data$CI <- factor(data$CI, levels = c("pctCI", "estCI", "bcaCIest"), 
+                    labels = c("Percentile", "Centered", "BCA"))
+  
   ggplot(data, aes(x = n, y = cov)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
     geom_line() +
     geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
-    facet_grid(factor(phi) ~ factor(CI), labeller = label_parsed) +
+    facet_grid(factor(phi) ~ CI) +
     scale_y_continuous(trans=trans)
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''))
 }

### 2023-03-29 Code/plots.R

@@ -1,3 +1,7 @@
+df_mu <- read.csv("../Data/df_mu.csv")
+df_sigma <- read.csv("../Data/df_sigma.csv")
+df_phi <- read.csv("../Data/df_phi.csv")
+
 t <- 'mu'
 width <- 10
 graph_bts(t, width, df_mu)

### 2023-04-17 Manuscript/manuscript.tex
Manuscript Update 4/17

--- 2023-03-24 Manuscript/manuscript.tex
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{booktabs}
@@
 Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
-$j = 1, \ldots, n - b + 1$. Now we draw $k$ blocks from the $(n - b + 1)$ blocks
-of $Z_j$'s with replacement and then aligning them in the order they were picked
+$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
+blocks
+of $Z_j$'s with replacement and then aligning them in the order they were
+picked
 to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
 block selected will be reduced in size so that the final size of the
-block bootstrap sample is $n$. Moving block bootstrap was used in
-this study as it has been found to yield the lowest error in general
-\citep{radovanov2014comparison}. The larger set of available blocks was used.
-\jy{what does the last sentence mean?}
+block bootstrap sample is $n$. It is also possible to implement moving block
+bootstrap while allowing blocks to wrap around the end of the series. In other
+words, define moving blocks (assuming $l > 1$):
+
+\begin{equation}
+Z_j =
+    \begin{cases}
+        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
+        \{X_j, \ldots, X_n, X_1, \ldots, X_{l - 1}\} & \text{if } j = n - l + 2 ,\dots, n
+    \end{cases}
+\end{equation}
+
+The second implementation of moving block bootstrap was used in
+this study, and moving block bootstrap in general had been found to yield the 
+lowest error.
+\citep{radovanov2014comparison}.  
+\jy{what does the last sentence mean?} Addressed
 
@@
 \paragraph{Percentile CI}
-Let $\hat\theta_{n, B, \alpha}$ be the empirical $100\alpha$th percentile of
+Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
 $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
@@
 \paragraph{Centered Percentile CI}
-Centered percentile CI is centered at the point estimator and uses the variation
-in the bootstrap estimates to construct the error bound. A $(1 - \alpha)$ CI is
+Centered percentile CI is centered at the point estimator and uses the
+variation
+in the bootstrap estimates to construct the error bound. This interval requires
+the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
+estimates, and $\delta$, the difference between a point estimate and
+$\bar\theta_n^{(b)}$. For $b \in \{1, \ldots, B\}$, we can obtain a
+$\delta^{(b)}$ based on the $b$th bootstrap point estimate. Let
+$\delta_{\alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
+$\{\delta^{(1)}, \ldots,  \delta^{(B)}\}$.  
+A $(1 - \alpha)$ centered percentile CI is
 \[
-(\hat{\theta}_{n} + \delta^*_{\alpha/2},
-\hat{\theta}_{n} + \delta^*_{1 - \alpha/2}).
+(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2},
+\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
 \]
-\jy{Define $\delta^*$?}
-\jy{Say a few words about its properties}
+This CI is necessarily centered by the point estimator $\hat\theta_n$ and is
+asymmetric, as different critical values are used to compute
+the lower and upper bounds.
+\jy{Define $\delta^*$?} Addressed
+\jy{Say a few words about its properties} Addressed
 
 \paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
-The $1 - \alpha$ \% BCA CI takes the form:
+In this study, the BCA CI is an interval centered at the point estimator.
+Let $\hat{G}(c) = \#\{\hat\theta_n^{(b)} < c\}/B$ for $b \in \{1, \ldots, B\}$, let
+$z_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$, let
+$\hat{\theta}_{n, -i}$ be the statistic of the sample without the $i^{th}$
+block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
+ $\hat\theta_{BCA}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
+A $(1 - \alpha)$ centered percentile CI is
 \[
-(\hat{\theta}_{n} + \delta^*_{\alpha_1},
-\hat{\theta}_{n} + \delta^*_{\alpha_2}),
+(\hat\theta_{BCA}[\alpha/2],
+\hat\theta_{BCA}[1 - \alpha/2]).
 \]
-\jy{Not clear and not flowing well. Restructure the writing. Practice my writing tips.}
-where $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
-$z_{2}$, respectively, where:
-\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
-z_{0}\] and
-\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
-z_{0}.\]
-Where $z_0$ is the quantile function of the proportion of
-$\hat\theta_n^{(b)} < \bar\theta_n^{(b)}$, and $a$ is the skewness (computed
-using
-the skewness function from the R e1071 package \citep{e1071}) of
-$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
-original sample computed without the $i^{th}$ block.
-\jy{Say a few words about its properties.}
+This CI is not necessarily centered by the point estimator $\hat\theta_n$.
 
@@
 To investigate the effect of sample size~$n$, we considered an array of values
-$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 1000
+$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 10000
 replicates. For each replicate, we constructed three 95\% block bootstrap
@@
 estimated their actual coverage rates along with their 95\% confidence
-intervals from the 1000 replicates. The block bootstrap sampling step was done
+intervals from the 10000 replicates. The block bootstrap sampling step was done
 with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
@@
 \jy{Make it flow better and conciser}
-Each interval either recovers $\theta$ or does not. Remember that
-95\% of many of a certain type of 95\% CIs constructed from
-samples of the same $n$ should recover $\theta$. To see if this is
-approximately the case, one can run 1000 replications of the block bootstrap
-procedure, and for each interval-$\theta$ pair, the rate at which that type of
-interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
+The coverage rates of the CIs were used to compare the performance of CIs. Let
+$\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower bound and upper bound,
+respectively, $ for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI} is the number of 
+CIs.
+Then $cov = \#\{$\hat\theta_{L, CI}$ < \theta < $\hat\theta_{U, CI}$ \}/n_{CI}$, $ 
+for $CI \in \{1, \ldots, n_{CI}\}$.
+The coverage rate is, of course, a
 point estimate of a proportion, so a 95\% CI of this coverage
-proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
-.95 is included in the interval, the block bootstrap method is likely working
+proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
+.95 is included in the interval, the block bootstrap method is likely
+performing
 well. If all values in the interval are below .95, the results suggest that the
@@
 
-- For mu, performance looks about the same regardless of interval type.
-- When phi is negative, n = 100 seems large enough.
-- When phi is zero, n = 500 is large enough.
-- When phi is 0.2, n = 300
-- When phi is 0.4, a much larger n seems to be necessary
-
 Based on \ref{fig:mu}, performance is
-about the same for the three interval types studied. When $\phi < 0$,
+about the same for the three interval types studied for $\mu$. As dependence gets stronger,
+a larger sample size is necessary. For $\mu$, all three types are working asymptotically 
+but for finite sizes, they more or less need about the same sample size to have the 
+correct coverage. When $\phi < 0$,
 $n = 100$ seems to  be large enough to cover $\mu$ at the nominal rate. When
@@
 
-- For sigma, coverage looks lower for BCa, whereas percentile and centered
-look about the same.
-- For percentile and centered intervals, n = 400 looks enough when phi = -0.4.
-- When phi = -0.2, n = 500 seems to be necessary for percentile and centered
-intervals.
-- When phi = 0, n = 400 seems to be necessary for percentile and centered
-intervals.
-- When phi = 0.2, n = 300 seems to be necessary...
-- When phi = 0.4, n = 400 seems to be necessary...
-
 Based on \ref{fig:sigma}, coverage is
@@
 is unknown, using a sample of $n \geq 400$ should be sufficient for estimation
-of $\sigma$.
-
-- BCa and percentile deteriorate in coverage as n increases, except for when
-phi = 0.
-- BCa coverage is very bad when absolute value of phi is high.
-- Percentile coverage is not as bad
-- n = 200 seems to be enough for centered interval, regardless of phi.
+of $\sigma$. Based on our results, $BC_a$ intervals should not be used to 
+estimate $\sigma$.
 
@@
 Interestingly, when $\phi = 0$, the percentile interval appears to actually
-over-cover $\phi$. These results suggest that $BC_a$ and basic percentile
+over-cover $\phi$. Regardless of whether $\phi$ is positive or negative, these two 
+intervals do not perform wellThese results suggest that $BC_a$ and basic percentile
 block bootstrap intervals should not be used estimate temporal dependence
@@
     rate. The error bars represent a 95\% CI for the coverage
-    proportion out of 1000 replications for each $n$. Results from $n$
+    proportion out of 10000 replications for each $n$. Results from $n$
     ranging from 100-700 were recorded.}
@@
 sample length for block bootstrap estimation to recover the parameter of a
-time series at an acceptable rate. Again, this relies on the assumption that
+time series at an acceptable rate.
+
+Again, this relies on the assumption that
 there is a size $n$ large enough for the method to work: that is, the method's
@@
 percentile $BC_a$ intervals exhibited coverage deterioration as $n$
-increased. When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
+increased.
+
+When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
 unknown, the results of this study suggest that an $n$ of around 500 may be
@@
 corrections that fix the coverage deterioration problem for $\phi$.
+
 This study could be used as a guide for applied statistics courses for students
@@
 BBOB
+B

### 2023-04-18 Manuscript/manuscript.tex
Error Fix

@@
 $\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower bound and upper bound,
-respectively, $ for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI} is the number of 
+respectively,  for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI}$ is the number of 
 CIs.
-Then $cov = \#\{$\hat\theta_{L, CI}$ < \theta < $\hat\theta_{U, CI}$ \}/n_{CI}$, $ 
+Then $cov = \#\{\hat\theta_{L, CI} < \theta < \hat\theta_{U, CI} \}/n_{CI}$,  
 for $CI \in \{1, \ldots, n_{CI}\}$.

### 2023-04-20 Manuscript/manuscript.tex

@@
 
-The remainder of the papers is organized as follows:
-The Block Bootstrap CIs section reviews how these intervals
-are constructed as well as the general procedure for block bootstrap parameter
-estimation. The Simulation Study section offers an explanation of the
-simulation design and results. Finally, the Concluding Remarks section
-discusses the main takeaways from the results, how these findings could be
-useful, and possible future explorations.
+The remainder of the papers is organized as follows.
+Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
+bootstrap estimates construct CIs. Section~\ref{sec:simu} reports a simulation
+study comparing the coverage rates of the block bootstrap CIs. A discussion
+concludes in Section~\ref{sec:disc}.
 
 \section{Block Bootstrap CIs}
-\label{sec:blkbootreview}
+\label{sec:bbci}
 
@@
 words, define moving blocks (assuming $l > 1$):
+\jy{Any equation must be a part of a sentence and should be punctuated.}
+\jy{Recall a blank line means a new paragraph.}
+\jy{Define your response command with color and respond}
 
@@
 \end{equation}
-
+\jy{The ending index does not seem right}
 The second implementation of moving block bootstrap was used in
 this study, and moving block bootstrap in general had been found to yield the 
-lowest error.
+lowest error \jy{state we use it because it is implemented in package boot and
+  cite boot}
 \citep{radovanov2014comparison}.  
-\jy{what does the last sentence mean?} Addressed
-
+\jy{This reference is from a low-tier journal. Find something from a stronger journal?}
 The block size~$l$ needs to chosen with care. It needs to be large enough for
@@
 
-\subsection{Construct CIs}
+\subsection{Bootstrap CIs}
 
@@
 
+\jy{can we give references to each of the method? How about the review paper in
+  Statistical Science?}
+
 \paragraph{Percentile CI}
@@
 This CI is not necessarily centered by the point estimator $\hat\theta_n$.
-%% Not the right place
-%% This interval works well when attempting to recover the mean and
-%% standard deviation of a temporally dependent process, but its coverage of
-%% the temporal dependence deteriorates as $n$ increases.
+As will be shown in our simulation study, this approach works well for the
+marginal mean and standard deviation of a serially dependent process, but its
+coverage of the temporal dependence deteriorates as $n$ increases, which is in
+contrary to what one would expect.
 
@@
 \[
-(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2},
+(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2}, \quad
 \hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
@@
 the lower and upper bounds.
-\jy{Define $\delta^*$?} Addressed
-\jy{Say a few words about its properties} Addressed
 
@@
 In this study, the BCA CI is an interval centered at the point estimator.
+\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
+  What is your reference for this description?}
 Let $\hat{G}(c) = \#\{\hat\theta_n^{(b)} < c\}/B$ for $b \in \{1, \ldots, B\}$, let
@@
 \[
-(\hat\theta_{BCA}[\alpha/2],
+(\hat\theta_{BCA}[\alpha/2], \quad
 \hat\theta_{BCA}[1 - \alpha/2]).
@@
 This CI is not necessarily centered by the point estimator $\hat\theta_n$.
+\jy{why is it called BCA?}
 
 \section{Simulation Study}
-\label{sec:simstudy}
+\label{sec:simu}
 
@@
 necessary, assuming that performance will improve as $n$ is increased. $n =$
+\jy{learn from how I presented this}
 100, 200, 300, 400, and 500, 600, 700 were used in this study. Remember that
@@
 
-\section{Concluding Remarks}
-\label{sec:conremarks}
+\section{Discussion}
+\label{sec:disc}
 
@@
 \end{document}
-
-BBOB
-B

### 2023-04-26 Manuscript/manuscript.tex
comments through discussion of Figure 1

@@
 \noindent{\sc Keywords}:
-dependent data; gsimulation
+dependent data; resampling; simulation; time series
 \end{abstract}
@@
 are more accurate than $t$-intervals for larger sample sizes, they are
-less accurate for smaller sample sizes. In the contect of structural equation
+less accurate for smaller sample sizes. In the context of structural equation
 modeling, \citet{nevitt2001performance} find
@@
 size for block bootstrap is even less clear. In a linear regression setting with
-dependent data, \citet{goncalves2005bootstrap} find that, standard error
+dependent data, \citet{goncalves2005bootstrap} find that standard error
 estimates from block bootstrap in small samples may be more accurate than
@@
 
-The remainder of the papers is organized as follows.
+The remainder of the paper is organized as follows.
 Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
-bootstrap estimates construct CIs. Section~\ref{sec:simu} reports a simulation
+bootstrap estimates to construct CIs. Section~\ref{sec:simu} reports a simulation
 study comparing the coverage rates of the block bootstrap CIs. A discussion
@@
 Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
-Our goal is to construct a CIs for a parameter $\theta$ in the
+Our goal is to construct a CI for a parameter $\theta$ in the
 data generating model of the series. Suppose that $\hat\theta_n$ is a point
@@
 Block bootstrap preserves the serial dependence in the observed data by
-partitioning the data into blocks and perform bootstrap on the blocks.
+partitioning the data into blocks and performing bootstrap on the blocks.
 In particular, consider block size~$l$ and, for convenience, suppose that
@@
 formation of the bootstrap sample ensures that the between-block dependence is
-week and that the within-block serial dependence is preserved. Because the
+weak and that the within-block serial dependence is preserved. Because the
 blocks here are non-overlapping, this bootstrap approach is known as
@@
 blocks
-of $Z_j$'s with replacement and then aligning them in the order they were
+of $Z_j$'s with replacement and then align them in the order they were
 picked
@@
 that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
-Now the question is, how to construct CIs for $\theta$
+Now the question is, how to construct a CI for $\theta$
 using the $B$ bootstrap point estimates
@@
 marginal mean and standard deviation of a serially dependent process, but its
-coverage of the temporal dependence deteriorates as $n$ increases, which is in
+coverage of the temporal dependence deteriorates as $n$ increases, which is
 contrary to what one would expect.
@@
 \]
-This CI is necessarily centered by the point estimator $\hat\theta_n$ and is
+This CI is necessarily centered around the point estimator $\hat\theta_n$ and is
 asymmetric, as different critical values are used to compute
@@
 In this study, the BCA CI is an interval centered at the point estimator.
+\eds{a different abbrevation/notation was used for this in the introduction}
 \jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
@@
 block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
- $\hat\theta_{BCA}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
-A $(1 - \alpha)$ centered percentile CI is
+ $\hat\theta_{BCA}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$ \eds{notation will need to be cleaned and clarified}
+A $(1 - \alpha)$ centered percentile \eds{BCA?} CI is
 \[
@@
 block
-bootstrap CIs. In particular, we generated time series $X_t$
+bootstrap CI methods. In particular, we generated time series $X_t$
 from a 1st order auto-regressive (AR1) process:
@@
 performing
-well. If all values in the interval are below .95, the results suggest that the
-method either is providing an inaccurate estimation, is underestimating the
+well. If all values in the interval are below .95, the results would suggest 
+that the
+method either is providing inaccurate estimation, is underestimating the
 process' variability, or a combination of both. If all values in the interval
@@
 The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
-these figures were generated using the using
-the R ggplot2 package \citep{ggplot2}.
+these figures were generated using the R \textsl{ggplot2} package \citep{ggplot2}.
 
@@
 
-Based on \ref{fig:mu}, performance is
-about the same for the three interval types studied for $\mu$. As dependence gets stronger,
+Based on Figure~\ref{fig:mu}, the performance is
+about the same for the three interval types studied for $\mu$. As dependence 
+gets stronger,
 a larger sample size is necessary. For $\mu$, all three types are working asymptotically 
-but for finite sizes, they more or less need about the same sample size to have the 
-correct coverage. When $\phi < 0$,
+but for finite sizes, they more or less need about the same sample size to have 
+the correct coverage. When $\phi < 0$,
 $n = 100$ seems to  be large enough to cover $\mu$ at the nominal rate. When
-$\phi = 0$, or in other other words, the sample is from a normal distribution,
-$n = 500$ seems to be large enough to cover $\mu$ at the nominal rate. Samples
+$\phi = 0$, or in other other words, the sample is independently normally
+distributed, %from a normal distribution,
+$n = 500$ \eds{$n=400$?} seems to be large enough to cover $\mu$ at the nominal 
+rate. Samples
 from processes with $\phi > 0$ appear to require a larger $n$ than samples from
@@
 so in most cases, if $\phi$ is unknown, a sample of $n \geq 500$ should be
-used when the target parameter is $\mu$.
+used when the target parameter is $\mu$. \eds{I would argue that none of the 
+sample sizes considered work well for $\phi=0.2$ or $\phi=0.2$ based on 
+Figure~\ref{fig:mu}}
 

### 2023-04-27 Manuscript/manuscript.tex
finished first pass

@@
 \jy{size? also it was overlapping blocks. Describe the details here.}
+\eds{Is $l = \lceil n^{1/3} \rceil$? Is it also worth investigating different 
+choices of $l$ for fixed (large) $n$?}
+\eds{how did you estimate $\mu$, $\sigma_x$ and $\phi$?}
 
@@
 The coverage rates of the CIs were used to compare the performance of CIs. Let
-$\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower bound and upper bound,
-respectively,  for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI}$ is the number of 
-CIs.
+$\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower and upper bound,
+respectively,  for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI}$ is the number 
+of CIs.
 Then $cov = \#\{\hat\theta_{L, CI} < \theta < \hat\theta_{U, CI} \}/n_{CI}$,  
 for $CI \in \{1, \ldots, n_{CI}\}$.
+\eds{this notation is a bit sloppy, as it implies $n_{CI}$ changes for each 
+value of $CI$; consider using a summation of indicators with a different index}
 The coverage rate is, of course, a
@@
 proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
-.95 is included in the interval, the block bootstrap method is likely
+0.95 is included in the interval, the block bootstrap method is likely
 performing
-well. If all values in the interval are below .95, the results would suggest 
+well. If all values in the interval are below 0.95, the results would suggest 
 that the
@@
 used when the target parameter is $\mu$. \eds{I would argue that none of the 
-sample sizes considered work well for $\phi=0.2$ or $\phi=0.2$ based on 
-Figure~\ref{fig:mu}}
+sample sizes considered work well for $\phi=0.2$ or $\phi=0.4$ based on 
+Figure~\ref{fig:mu} and your criteria above (``If all values in the interval are
+ below 0.95, the results would suggest that the
+method either is providing inaccurate estimation, is underestimating the
+process' variability, or a combination of both.")}
 
-Based on \ref{fig:sigma}, coverage is
-notably lower for $BC_a$ intervals, but $\hat{\theta}_{n}$-centered intervals
+Based on Figure~\ref{fig:sigma}, coverage is
+notably lower for $BC_a$ intervals \eds{use consistent notation for this}, 
+but $\hat{\theta}_{n}$-centered intervals
 and basic intervals have similar performance. For these two interval types,
-$n = 500$ seems to be necessary to cover $\sigma$ at the nominal rate when
+$n = 500$ seems to be necessary to cover $\sigma$ 
+\eds{use $\sigma_x$ instead of $\sigma$} at the nominal rate when
 $\phi < 0$. If $\phi = 0$, $n = 400$ seems to large enough to cover $\sigma$ at
 the nominal rate. If $\phi = 0.2$, $n = 300$ seems large enough, but if the
-process has a greater $\phi$ of $0.4$, $n = 400$ may be necessary. It is more
+process has a greater $\phi$ of $0.4$, $n = 400$ may be necessary. 
+\eds{$n=400$ does not appear to be enough to me. I would also argue larger $n$
+is needed for the other values of $\phi$ unless the curves asymptote at a value
+lower than 0.95. Do the point estimates eventually get closer to the nominal 
+level with larger $n$?}  
+It is more
 common for $\phi$ to be $> 0$ in applied analysis, so in most cases, if $\phi$
@@
 intervals, the assumption that coverage rates asymptotically approach the
-nominal rate as $n$ increases appears to be invalid based on \ref{fig:sigma}.
-The $BC_a$ interval performs very poorly and deteriorates more noticeable
+nominal rate as $n$ increases appears to be invalid based on 
+Figure~\ref{fig:sigma}.
+\eds{Figure~\ref{fig:phi}?}
+The $BC_a$ interval performs very poorly and deteriorates more noticeably
 when the absolute value $\phi$ gets
-higher, but even when $\phi = 0$, $\phi$ is still undercovered for $n$ as high
+higher. Even when $\phi = 0$, $\phi$ is still undercovered for $n$ as high
 as $700$. Like the $BC_a$ interval, the percentile interval deteriorates in
@@
 Interestingly, when $\phi = 0$, the percentile interval appears to actually
-over-cover $\phi$. Regardless of whether $\phi$ is positive or negative, these two 
-intervals do not perform wellThese results suggest that $BC_a$ and basic percentile
+over-cover $\phi$. Regardless of whether $\phi$ is positive or negative, these 
+two intervals do not perform well. These results suggest that $BC_a$ and basic 
+percentile
 block bootstrap intervals should not be used estimate temporal dependence
 factors of time series. On the other hand, $\hat{\theta}_{n}$-centered
-intervals seem to recover $\phi$ correctly as long as $n >= 200$, and this
+intervals seem to recover $\phi$ correctly as long as $n \geq 200$, and this
 appears to be true regardless of $\phi$, although a greater $\phi$ may result
@@
 sufficient to recover $\mu$ at a rate of approximately 95\%.
+\eds{not sure if above paragraph is needed - seems to repeat information in the 
+previous two paragraphs}
 
@@
 
-Block bootstrap method is a useful method for estimating parameters of a time
-series: from simple parameters like the mean to temporal dependence factors.
-The motivation for the study is the idea that block bootstrap procedure will
-perfectly estimate a parameter of a time series given an infinitely large
-sample. The goal for this study was to find what is a good enough finite
-sample length for block bootstrap estimation to recover the parameter of a
-time series at an acceptable rate.
+Block bootstrap is a useful method for estimating parameters of a time
+series, from simple parameters like the mean to more complicated temporal
+ dependence factors.
+%The motivation for the study is the idea that block bootstrap procedure will
+%perfectly estimate a parameter of a time series given an infinitely large
+%sample. The goal for this study was to find what is a good enough finite
+%sample length for block bootstrap estimation to recover the parameter of a
+%time series at an acceptable rate.
+We know theoretically that the block bootstrap procedure will
+perfectly estimate \eds{? interval will correctly cover?  What does the theory 
+actually say?} a parameter of a time series given an infinitely large
+sample, so the goal for this study was to find the smallest finite
+sample length $n$ of a time series in order for the block bootstrap procedure to 
+recover its associated parameters at an acceptable rate.
 
-Again, this relies on the assumption that
+Again, this \eds{what?} relies on the assumption that
 there is a size $n$ large enough for the method to work: that is, the method's
@@
 estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
-percentile $BC_a$ intervals exhibited coverage deterioration as $n$
+percentile and $BC_a$ intervals exhibited coverage deterioration as $n$
 increased.
@@
 bootstrap to be used versus other inference methods.
-This information could prove to be useful for researching using block bootstrap
+This information could also prove to be useful for research using block bootstrap
 estimation of time series in domains such as econometrics. Future studies
-could investigate if there are types of block bootstrap intervals
-constructions that would more appropriately recover the parameters of a time
-series. One could also investigate the $n$ needed to make inferences about
-other forms of serially dependent data such as an MA process.
+could investigate if there are types of block bootstrap interval
+construction that would more appropriately recover the parameters of a time
+series. \eds{are there other methods that you know of?} 
+One could also investigate the $n$ needed to make inferences about
+other forms of serially dependent data such as a moving average process.
 

### 2023-05-04 Manuscript/manuscript.tex
Manuscript Update (some comments I still have to address)

@@
 \newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
+\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}
 
@@
 bootstrap while allowing blocks to wrap around the end of the series. In other
-words, define moving blocks (assuming $l > 1$):
+words, define moving blocks (assuming $l > 1$) as:
 \jy{Any equation must be a part of a sentence and should be punctuated.}
@@
 \jy{Define your response command with color and respond}
-
+\mc{addressed above comments}
 \begin{equation}
@@
         \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
-        \{X_j, \ldots, X_n, X_1, \ldots, X_{l - 1}\} & \text{if } j = n - l + 2 ,\dots, n
+        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\} & \text{if } j = n - l
+        + 2 ,\dots, n.
     \end{cases}
@@
 \jy{The ending index does not seem right}
-The second implementation of moving block bootstrap was used in
-this study, and moving block bootstrap in general had been found to yield the 
-lowest error \jy{state we use it because it is implemented in package boot and
-  cite boot}
-\citep{radovanov2014comparison}.  
-\jy{This reference is from a low-tier journal. Find something from a stronger journal?}
+\mc{addressed above}
+The second version of moving block bootstrap was used in
+this study because it is the implementation provided in the function
+\texttt{tsboot} from R package \textsl{boot} \citep{boot}, and it is easier
+overall because $l$ need not divide $n$.
+\jy{state we use it because it is implemented in package boot and cite boot}  
+\jy{This reference is from a low-tier journal. Find something from a stronger
+  journal?}
+\mc{addressed above comments}
 The block size~$l$ needs to chosen with care. It needs to be large enough for
@@
 
-\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
-In this study, the BCA CI is an interval centered at the point estimator.
+\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
+In this study, the $BC_a$ CI is an interval centered at the point estimator.
 \eds{a different abbrevation/notation was used for this in the introduction}
+\mc{used $BC_a$}
 \jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
@@
 block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
- $\hat\theta_{BCA}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$ \eds{notation will need to be cleaned and clarified}
-A $(1 - \alpha)$ centered percentile \eds{BCA?} CI is
+ $\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$ \eds{notation will need to be cleaned and clarified}
+A $(1 - \alpha)$ centered $BC_a$ CI is
 \[
-(\hat\theta_{BCA}[\alpha/2], \quad
-\hat\theta_{BCA}[1 - \alpha/2]).
+(\hat\theta_{BC_a}[\alpha/2], \quad
+\hat\theta_{BC_a}[1 - \alpha/2]).
 \]
-This CI is not necessarily centered by the point estimator $\hat\theta_n$.
+This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
+$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
+estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
+bias-correction and acceleration factors. 
 \jy{why is it called BCA?}
+\mc{addressed}
 
@@
 The coverage rates of the CIs were used to compare the performance of CIs. Let
-$\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower and upper bound,
-respectively,  for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI}$ is the number 
-of CIs.
-Then $cov = \#\{\hat\theta_{L, CI} < \theta < \hat\theta_{U, CI} \}/n_{CI}$,  
-for $CI \in \{1, \ldots, n_{CI}\}$.
+$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
+respectively, for the confidence interval constructed for each replicate
+$r \in \{1, \ldots, R\}$, where $R$ is the
+number of replicates.
+Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
+for $r \in \{1, \ldots, R\}$.
 \eds{this notation is a bit sloppy, as it implies $n_{CI}$ changes for each 
 value of $CI$; consider using a summation of indicators with a different index}
+\mc{replaced $CI$ with $r$, and $n_{CI}$ with $R$}
 The coverage rate is, of course, a
@@
 %time series at an acceptable rate.
-We know theoretically that the block bootstrap procedure will
-perfectly estimate \eds{? interval will correctly cover?  What does the theory 
-actually say?} a parameter of a time series given an infinitely large
+ We know theoretically that the block bootstrap procedure will cover
+ \eds{? interval will correctly cover?  What does the theory  actually say?}
+ \mc{addressed} a
+ parameter of a time series at the nominal level given an
+ infinitely large
 sample, so the goal for this study was to find the smallest finite
-sample length $n$ of a time series in order for the block bootstrap procedure to 
+sample length $n$ of a time series in order for the block bootstrap procedure
+to 
 recover its associated parameters at an acceptable rate.
 
-Again, this \eds{what?} relies on the assumption that
+Again, this analysis \eds{what?} \mc{addressed} relies on the assumption that
 there is a size $n$ large enough for the method to work: that is, the method's

### 2023-05-07 Manuscript/manuscript.tex
New Figures

@@
 \paragraph{Percentile CI}
+The percentile interval was first suggested in \citet{efron1979bootstrap}.
 Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
@@
 \paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
-In this study, the $BC_a$ CI is an interval centered at the point estimator.
+The $BC_a$ CI was first suggested in \citet{efron1987better}.
 \eds{a different abbrevation/notation was used for this in the introduction}
@@
 \mc{addressed}
+
+\paragraph{Standard Normal CI}
+
+\paragraph{Student's t CI}
 

### 2023-05-09 Manuscript/manuscript.tex
5/9 Manuscript Udate

@@
   What is your reference for this description?}
-Let $\hat{G}(c) = \#\{\hat\theta_n^{(b)} < c\}/B$ for $b \in \{1, \ldots, B\}$, let
-$z_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$, let
-$\hat{\theta}_{n, -i}$ be the statistic of the sample without the $i^{th}$
-block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
+Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$. 
+Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, and let
+$\hat{\theta}_{n, -i}$ be the jackknife values of $Z_{(i)}$ for $i \in \{1, \ldots, n\}$, 
+and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
  $\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$ \eds{notation will need to be cleaned and clarified}
@@
 \paragraph{Standard Normal CI}
+A $(1 - \alpha$ standard normal CI is
+\[
+(\hat{\theta}_{n} - z_{(1-\alpha/2)}*\hat{se}, \hat{\theta}_{n} - z_{(\alpha/2)}*\hat{se}.
+\]
+This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
 
 \paragraph{Student's t CI}
+A $(1 - \alpha$ student's t CI is
+\[
+(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}*\hat{se}, \hat{\theta}_{n} - t_{(\alpha/2), k -1}*\hat{se}.
+\]
+This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
 
@@
 \jy{learn from how I presented this}
-100, 200, 300, 400, and 500, 600, 700 were used in this study. Remember that
+100, 200, 400, 800, and 1600 were used in this study. Remember that
 the goal of this study is to find the smallest $n$ which is sufficient for
@@
 
-Based on Figure~\ref{fig:mu}, the performance is
-about the same for the three interval types studied for $\mu$. As dependence 
-gets stronger,
-a larger sample size is necessary. For $\mu$, all three types are working asymptotically 
-but for finite sizes, they more or less need about the same sample size to have 
-the correct coverage. When $\phi < 0$,
-$n = 100$ seems to  be large enough to cover $\mu$ at the nominal rate. When
-$\phi = 0$, or in other other words, the sample is independently normally
-distributed, %from a normal distribution,
-$n = 500$ \eds{$n=400$?} seems to be large enough to cover $\mu$ at the nominal 
-rate. Samples
-from processes with $\phi > 0$ appear to require a larger $n$ than samples from
-processes with $\phi < 0$. When $\phi = 0.2$, $n = 300$ seemed to be necessary
-for adequate performance, and when $\phi = 0.4$, an even larger $n$ appeared
-to be necessary to properly cover $\mu$. It is rare for $\phi$ to be so high,
-so in most cases, if $\phi$ is unknown, a sample of $n \geq 500$ should be
-used when the target parameter is $\mu$. \eds{I would argue that none of the 
-sample sizes considered work well for $\phi=0.2$ or $\phi=0.4$ based on 
-Figure~\ref{fig:mu} and your criteria above (``If all values in the interval are
- below 0.95, the results would suggest that the
-method either is providing inaccurate estimation, is underestimating the
-process' variability, or a combination of both.")}
+% mu
+%As dependence gets stronger, a larger sample size is necessary. 
+%For $\mu$, Percentile, Centered, and BCA, and Standard more or less 
+% need about the same 
+% For phi = -0.4, they slightly over-cover mu for all sample sizes, but 
+% the error bars generally hover around the 95% line
+% For phi = -0.2, all four cover mu at the nominal rate when n = 400, and when 
+% n = 1600, although there is a dip in coverage for n = 800.
+% Besides that, the coverage rates remain about .9375 for all sample sizes
+% For phi = 0, n = 1600 seems to be enough
+% For phi = 0.2, the coverage rates are above .9375 when n = 800 and 1600.
+% Although there is a slight downward trend from 800 to 1600
+% For phi = 0.4, the coverage rates are above .925 when n = 800 and 1600.
+% Although there is a more noticeable downward trend from 800 to 1600.
+% Student's t performs noticeably better
+% For phi = -0.4, it over-covers mu for all sample sizes, and the lower bounds
+% are all above the line
+%For phi = -0.2, it slightly over-covers mu, and the error bars generally hover
+% around the line
+% For phi = 0, the interval for mu's coverage rate contains .95 for all sample sizes
+% For phi = 0.2 and 0.4, the trend in coverage is similar to the other intervals, but 
+% the overall coverage rates are higher.
+% The deviations in trend
+% for all intervals can be most likely be attributed to noise.
 
-Based on Figure~\ref{fig:sigma}, coverage is
-notably lower for $BC_a$ intervals \eds{use consistent notation for this}, 
-but $\hat{\theta}_{n}$-centered intervals
-and basic intervals have similar performance. For these two interval types,
-$n = 500$ seems to be necessary to cover $\sigma$ 
-\eds{use $\sigma_x$ instead of $\sigma$} at the nominal rate when
-$\phi < 0$. If $\phi = 0$, $n = 400$ seems to large enough to cover $\sigma$ at
-the nominal rate. If $\phi = 0.2$, $n = 300$ seems large enough, but if the
-process has a greater $\phi$ of $0.4$, $n = 400$ may be necessary. 
-\eds{$n=400$ does not appear to be enough to me. I would also argue larger $n$
-is needed for the other values of $\phi$ unless the curves asymptote at a value
-lower than 0.95. Do the point estimates eventually get closer to the nominal 
-level with larger $n$?}  
-It is more
-common for $\phi$ to be $> 0$ in applied analysis, so in most cases, if $\phi$
-is unknown, using a sample of $n \geq 400$ should be sufficient for estimation
-of $\sigma$. Based on our results, $BC_a$ intervals should not be used to 
-estimate $\sigma$.
+% sigma
+%As dependence gets stronger, a larger sample size is necessary. 
+% BCA greatly undercovers for all sample sizes, but no trend of coverage deterioration
+% Should not be used
+%For $\sigma$, Percentile, Centered, and Standard Ci perform similarly
+% For phi = -0.4, -0.2, and 0, n = 1600 seems nearly enough to cover sigma at the 
+% nomal rate
+% For phi = 0.2 and 0.4, a larger sample size seems to be necessary to cover at nominal rate, 
+% 0.2: n = 800 and 1600, coverage is above .93 for all three intervals
+% 0.4: But at n = 1600, coverage is above .93 for all three intervals
+% Student's t performs well
+% For phi = -0.4, sigma is covered at the nominal rate for n >= 1600
+% For phi = -0.2, sigma is covered at the nominal rate for n >= 400
+% For phi = 0, sigma is covered at the nominal rate for n >= 400
+% For phi = 0.2, coverage seems to level out at n = 400, but seems to be around .945
+% For phi = 0.4, coverage does not seem to increase much from n = 400 onwards, but is above .93
+% The deviations in trend
+% for all intervlas can be most likely be attributed to noise.
 
-When block bootstrap is used to estimate $\phi$ using $BC_a$ and percentile
-intervals, the assumption that coverage rates asymptotically approach the
-nominal rate as $n$ increases appears to be invalid based on 
-Figure~\ref{fig:sigma}.
-\eds{Figure~\ref{fig:phi}?}
-The $BC_a$ interval performs very poorly and deteriorates more noticeably
-when the absolute value $\phi$ gets
-higher. Even when $\phi = 0$, $\phi$ is still undercovered for $n$ as high
-as $700$. Like the $BC_a$ interval, the percentile interval deteriorates in
-coverage when $\phi$ is high, although the coverage is not as low.
-Interestingly, when $\phi = 0$, the percentile interval appears to actually
-over-cover $\phi$. Regardless of whether $\phi$ is positive or negative, these 
-two intervals do not perform well. These results suggest that $BC_a$ and basic 
-percentile
-block bootstrap intervals should not be used estimate temporal dependence
-factors of time series. On the other hand, $\hat{\theta}_{n}$-centered
-intervals seem to recover $\phi$ correctly as long as $n \geq 200$, and this
-appears to be true regardless of $\phi$, although a greater $\phi$ may result
-in a decline in performance.
-
+%phi
+%As dependence gets stronger, a larger sample size is necessary. 
+%Percentile and BCA deteriorate clearly for any level of temporal correlation 
+%Regardless of negative or positive
+%Should not be used
+%Centered and Standard perform similarly
+%For these a sample size of n = 800 appears to be necessary to recover phi at the nominal level
+% Student's t appears to recover phi at the nominal level for n >= 100
 \jy{One summary paragraph at the end.}
@@
 To summarize, the CI type chosen should be based on the target parameter.
-For estimating $\mu$, any of the three interval types can be used, but for
-$\sigma$, only $\hat{\theta}_{n}$-centered and basic percentile intervals
-should be used, and only $\hat{\theta}_{n}$-centered intervals should be used
-for $\phi$. When estimating
-$\mu$, $n = 500$ should be large enough in situations where $\phi$ is unknown.
-When estimating $\sigma$, $n = 400$ is sufficient is situations where $\phi$ is
-unknown. If $\phi$ is known, a lesser $n$ may be adequate. When estimating
-$\phi$, $n = 200$ is large enough when using the correct type of interval.
+...
 
@@
     rate. The error bars represent a 95\% CI for the coverage
-    proportion out of 10000 replications for each $n$. Results from $n$
-    ranging from 100-700 were recorded.}
+    proportion out of 10000 replications for each $n$. Results for 
+    $n = 100, 200, 400, 800, 1600$ were recorded.}
   \label{fig:mu}
@@
   \includegraphics[width=\textwidth]{figures/plot_sigma}
-  \caption{Plots of $\sigma$ coverage rates for each interval type and $\phi$
+  \caption{Plots of $\sigma_x$ coverage rates for each interval type and $\phi$
     combination. The orange dotted line represents the 95\% nominal coverage
     rate. The error bars represent a 95\% CI for the coverage
-    proportion out of 10000 replications for each $n$. Results from $n$
-    ranging from 100-700 were recorded.}
+    proportion out of 10000 replications for each $n$. Results for 
+    $n = 100, 200, 400, 800, 1600$ were recorded.}
   \label{fig:sigma}
@@
     rate. The error bars represent a 95\% CI for the coverage
-    proportion out of 10000 replications for each $n$. Results from $n$
-    ranging from 100-700 were recorded.}
+    proportion out of 10000 replications for each $n$. Results for 
+    $n = 100, 200, 400, 800, 1600$ were recorded.}
   \label{fig:phi}
 \end{figure}
-
-As shown in the above figures, only $\hat{\theta}_{n}$-centered intervals
-managed to solve the deterioration problem with respect to recovering $\phi$,
-indicating that this interval should be used as opposed to the uncentered
-percentile interval or the more complex $BC_a$ interval when estimating
-$\phi$. Increasing $n$ will not fix the performance of either of these
-intervals because the assumption that the coverage rate will approach an upper
-limit of .95 as $n$ increases is invalid. As expected for
-$\hat{\theta}_{n}$-centered intervals, a higher positive $\phi$ demands a
-larger $n$ to estimate all parameters, but a negative $\phi$ may require a
-lesser $n$. For example, for both $\phi = 0.2$ and $0.4$, $n = 100$ was
-sufficient to recover $\mu$ at a rate of approximately 95\%.
-\eds{not sure if above paragraph is needed - seems to repeat information in the 
-previous two paragraphs}
 
@@
 an $n$ of around 400 may be necessary to
-estimate $\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to
+estimate $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate to
 estimate these parameters. When $\phi$ was negative, a $n$ of around 100 was
@@
 could investigate if there are types of block bootstrap interval
-construction that would more appropriately recover the parameters of a time
+construction such as $ABC$ or bootstrap-t intervals
+that would more appropriately recover the parameters of a time
 series. \eds{are there other methods that you know of?} 

### 2023-05-10 Manuscript/manuscript.tex
5/10 Manuscript Update

@@
 that a sample size of 200--1000 is usually sufficient for interval estimation
-using standard nonparametric bootstrap. For dependent data, the necessary sample
-size for block bootstrap is even less clear. In a linear regression setting with
+using standard nonparametric bootstrap. For dependent data, the necessary
+sample
+size for block bootstrap is even less clear. In a linear regression setting
+with
 dependent data, \citet{goncalves2005bootstrap} find that standard error
@@
 interests are the mean, standard deviation, and the first-order
-autocorrelation coefficient. We compare three variants of block bootstrap
+autocorrelation coefficient. We compare five variants of block bootstrap
 CIs from the literature \citep{diciccio1996bootstrap,
   rice2006mathematical}: a basic percentile interval, a percentile
-interval centered around the estimate, and a bias-corrected and
-accelerated ($BC_a$) interval also centered around the original estimate. Their
+interval centered around the estimate, a bias-corrected and
+accelerated ($BC_a$) interval, a standard normal interval, and a student's $t$
+interval. Their
 empirical coverage rates at different sample sizes and dependence levels are
@@
 Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
-bootstrap estimates to construct CIs. Section~\ref{sec:simu} reports a simulation
+bootstrap estimates to construct CIs. Section~\ref{sec:simu} reports a
+simulation
 study comparing the coverage rates of the block bootstrap CIs. A discussion
@@
 considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
-\citep{buhlmann1999block}.
+\citep{buhlmann1999block}, which is how the value of $l$ was determined for
+this
+study. It may be worth investigating in a future study if another block size
+scheme is 
+optimal for the context of a time series by comparing different block sizes
+whilst keeping the sample size fixed.
 
@@
 $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.
-We consider three kinds of CIs.
+We consider five kinds of CIs.
 
@@
   Statistical Science?}
+\mc{references for percentile and BCA, couldn't find for centered, standard,
+  or student's t}
 
@@
 \]
-This CI is necessarily centered around the point estimator $\hat\theta_n$ and is
-asymmetric, as different critical values are used to compute
+This CI is necessarily centered around the point estimator $\hat\theta_n$ and
+is asymmetric, as different critical values are used to compute
 the lower and upper bounds.
@@
   What is your reference for this description?}
-Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$. 
+Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
+for $b \in \{1, \ldots, B\}$. 
 Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, and let
-$\hat{\theta}_{n, -i}$ be the jackknife values of $Z_{(i)}$ for $i \in \{1, \ldots, n\}$, 
+$\hat{\theta}_{n, -i}$ be the jackknife values of $Z_{(i)}$
+for $i \in \{1, \ldots, n\}$, 
 and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
- $\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$ \eds{notation will need to be cleaned and clarified}
+$\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} +
+  z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
+\eds{notation will need to be cleaned and clarified}
 A $(1 - \alpha)$ centered $BC_a$ CI is
@@
 estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
-bias-correction and acceleration factors. 
+bias-correction and acceleration factors. The acceleration factor refers to
+the 
+rate of change of of the standard error of $\hat\theta_n$ with respect to
+$\theta$.
 \jy{why is it called BCA?}
@@
 \paragraph{Standard Normal CI}
-A $(1 - \alpha$ standard normal CI is
+
+A $(1 - \alpha$ standard normal CI depends on the standard error $\hat{se}$
+for each of the
+$B$ bootstrap point estimates
+$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. 
 \[
-(\hat{\theta}_{n} - z_{(1-\alpha/2)}*\hat{se}, \hat{\theta}_{n} - z_{(\alpha/2)}*\hat{se}.
+(\hat{\theta}_{n} - z_{(1-\alpha/2)}*\hat{se}, \hat{\theta}_{n} -
+z_{(\alpha/2)}*\hat{se}).
 \]
 This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
+The standard
+normal CI is a table-based bootstrap interval approach, which is to say that
+it relies on the 
+assumption that $\hat\theta_n$ is normally distributed and the expected value
+of $\hat\theta_n$
+is $\theta$.
 
-\paragraph{Student's t CI}
-A $(1 - \alpha$ student's t CI is
+\paragraph{Student's $t$ CI}
+A $(1 - \alpha$ student's $t$ CI is
 \[
-(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}*\hat{se}, \hat{\theta}_{n} - t_{(\alpha/2), k -1}*\hat{se}.
+(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}*\hat{se}, \hat{\theta}_{n} -
+t_{(\alpha/2), k -1}*\hat{se}),
 \]
+where k is the number of blocks.
 This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
+Like the standard 
+normal interval, the student's t CI is a table-based bootstrap interval
+approach. In this case,
+we assume that $\hat\theta_n$ follows the $t_{k-1}$ distribution with an
+expected value of $\theta$.
 
@@
 1) $\mu = 0$, the mean of $X_t$;
-2) $\sigma_x^2 = 1$, the variance of $X_t$; and
+2) $\sigma_x = 1$, the standard deviation of $X_t$; and
 2) $\phi$, the lag-1 auto-correlation coefficient.
 To investigate the effect of sample size~$n$, we considered an array of values
-$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 10000
+$n \in \{100, 200, 400, 800, 1600\}$. In each configuration, we generated 10000
 replicates. For each replicate, we constructed three 95\% block bootstrap
-CIs for each parameter as described in the last section, and
-estimated their actual coverage rates along with their 95\% confidence
+CIs for each parameter as described in the last section. We can estimate 
+$\mu$, $\sigma_x$, and $\phi$ by computing the sample mean, sample 
+standard deviation,
+and lag-1 auto-correlation, respectively, of each bootstrap sample, and then 
+constructing intervals for each parameter using the appropriate procedures
+described in Section~\ref{sec:bbci} .
+Then we estimated their actual coverage rates along with their 95\% confidence
 intervals from the 10000 replicates. The block bootstrap sampling step was done
@@
 block size $\lceil n / l \rceil$. This function by default is an implementation
-of moving block bootstrap as described in the previous section.
+of moving block bootstrap as described in the previous section, meaning that
+that blocks are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.
 \jy{size? also it was overlapping blocks. Describe the details here.}
+\mc{addressed}
 \eds{Is $l = \lceil n^{1/3} \rceil$? Is it also worth investigating different 
 choices of $l$ for fixed (large) $n$?}
+\mc{Addressed in the Block Bootstrap Sample subsection}
 \eds{how did you estimate $\mu$, $\sigma_x$ and $\phi$?}
+\mc{addressed}
 
@@
 \mc{replaced $CI$ with $r$, and $n_{CI}$ with $R$}
-The coverage rate is, of course, a
-point estimate of a proportion, so a 95\% CI of this coverage
-proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
+If a CI method is valid, then the coverage rate is expected to match the
+nominal 
+level. Because it is unlikely for the coverage to exactly match the nominal
+level,
+we can construct a 95\% CI of the coverage
+rate (which is an estimate of a proportion with $n = 10000$). If the proportion
 0.95 is included in the interval, the block bootstrap method is likely
@@
 If $\theta$ is not covered at that $n$, a larger $n$ may be
-necessary, assuming that performance will improve as $n$ is increased. $n =$
-\jy{learn from how I presented this}
-100, 200, 400, 800, and 1600 were used in this study. Remember that
+necessary, assuming that performance will improve as $n$ is increased.
+Remember that
 the goal of this study is to find the smallest $n$ which is sufficient for
@@
 The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
-these figures were generated using the R \textsl{ggplot2} package \citep{ggplot2}.
+these figures were generated using the R \textsl{ggplot2} package
+\citep{ggplot2}.
 
@@
   points and then organize them into a logically flowing paragraph.}
+\mc{paragraphs below}
 
-% mu
-%As dependence gets stronger, a larger sample size is necessary. 
-%For $\mu$, Percentile, Centered, and BCA, and Standard more or less 
-% need about the same 
-% For phi = -0.4, they slightly over-cover mu for all sample sizes, but 
-% the error bars generally hover around the 95% line
-% For phi = -0.2, all four cover mu at the nominal rate when n = 400, and when 
-% n = 1600, although there is a dip in coverage for n = 800.
-% Besides that, the coverage rates remain about .9375 for all sample sizes
-% For phi = 0, n = 1600 seems to be enough
-% For phi = 0.2, the coverage rates are above .9375 when n = 800 and 1600.
-% Although there is a slight downward trend from 800 to 1600
-% For phi = 0.4, the coverage rates are above .925 when n = 800 and 1600.
-% Although there is a more noticeable downward trend from 800 to 1600.
-% Student's t performs noticeably better
-% For phi = -0.4, it over-covers mu for all sample sizes, and the lower bounds
-% are all above the line
-%For phi = -0.2, it slightly over-covers mu, and the error bars generally hover
-% around the line
-% For phi = 0, the interval for mu's coverage rate contains .95 for all sample sizes
-% For phi = 0.2 and 0.4, the trend in coverage is similar to the other intervals, but 
-% the overall coverage rates are higher.
-% The deviations in trend
-% for all intervals can be most likely be attributed to noise.
+Based on Figure~\ref{fig:mu}, 
+the performance is about the same for Percentile, Centered, BCA, and 
+Standard CIs with respect to estimating $\mu$. They more or less need
+about the same sample size to have the correct coverage. For $\phi = -0.4$, 
+they slightly over-cover $\mu$ for all sample sizes, but the error bars generally 
+hover around the $95\%$ line. For $\phi = -0.2$, all four cover $\mu$ at the nominal 
+rate when $n = 400$, and when $n = 1600$, although there seems to be a dip in 
+coverage for $n = 800$. However, this deviation in trend can most likely be 
+attributed to noise. Besides that, the coverage rates remain above $.9375$ 
+for all sample sizes for this level of $\phi$. For $\phi = 0$, or when the 
+sample is independently normally distributed, $n = 1600$ seems to 
+be enough to recover $\mu$. For $\phi = 0.2$, the coverage rates are above 
+$.9375$ when $n = 800$ and $n = 1600$, but the coverage intervals do not contain
+$95\%$. Interestingly, there seems to be a drop in coverage rate from 
+$n = 800$ to $n = 1600$. For $\phi = 0.4$, the coverage rates are above $.925$
+when $n = 800$ and $n = 1600$, and there is a more noticeable downward 
+trend from $n = 800$ to $n = 1600$. Student's $t$ CI has noticeably higher coverage
+than the other CIs. For $\phi = -0.4$, the Student's $t$ CI actually 
+over-covers $\mu$ for all sample sizes, and the lower error bars
+are above the $95\%$ line for all sample sizes. For $\phi = -0.2$, it still slightly 
+over-covers $\mu$ for all sample sizers, but the error bars generally hover
+lower and around the $95\%$ line. For $\phi = 0$, the interval for the 
+coverage rate contains $.95$ for all sample sizes. For $\phi = 0.2$ and 
+$\phi = 0.4$, the trend in coverage is similar to the other CIs, but 
+the overall coverage rates are higher, although they still do not reach the $95\%$
+line.
 
-% sigma
-%As dependence gets stronger, a larger sample size is necessary. 
-% BCA greatly undercovers for all sample sizes, but no trend of coverage deterioration
-% Should not be used
-%For $\sigma$, Percentile, Centered, and Standard Ci perform similarly
-% For phi = -0.4, -0.2, and 0, n = 1600 seems nearly enough to cover sigma at the 
-% nomal rate
-% For phi = 0.2 and 0.4, a larger sample size seems to be necessary to cover at nominal rate, 
-% 0.2: n = 800 and 1600, coverage is above .93 for all three intervals
-% 0.4: But at n = 1600, coverage is above .93 for all three intervals
-% Student's t performs well
-% For phi = -0.4, sigma is covered at the nominal rate for n >= 1600
-% For phi = -0.2, sigma is covered at the nominal rate for n >= 400
-% For phi = 0, sigma is covered at the nominal rate for n >= 400
-% For phi = 0.2, coverage seems to level out at n = 400, but seems to be around .945
-% For phi = 0.4, coverage does not seem to increase much from n = 400 onwards, but is above .93
-% The deviations in trend
-% for all intervlas can be most likely be attributed to noise.
+Based on Figure~\ref{fig:sigma}, 
+$BC_a$ CIs greatly undercover $\sigma_x$ for all sample sizes, although
+there is no trend of coverage deterioration, indicating that there may eventually
+a sample size large enough for $\sigma_x$ to be covered at the nominal level.
+However, because it's performance is so much poorer than the other CIs,
+$BC_a$ should not be used. Percentile, Centered, and Standard CIs perform similarly,
+with respect to estimating $\sigma_x$. For $\phi = -0.4$, $\phi = -0.2$, and $\phi = 0$, 
+$n = 1600$ seems to be large enough to cover $\sigma_x$ at the nominal level
+when using the Standard Normal CI interval, while the others are very close, hovering
+around $.945$ for $n = 1600$. For $\phi > 0$, a larger sample size does seem
+to be necessary to cover $\sigma_x$ at the nominal rate. However, for $\phi = 0.2$, 
+when $n \geq 400$, coverage is above $.93$ for all three of these CIs. For $\phi = 0.4$,
+when $n = 1600$, coverage is above $.93$ for all three of these CIs.
+Like for $\mu$, Student's $t$ CIs have the highest overall coverage of $\sigma_x$.
+Additionally, the Student's $t$ method does not over-cover $\sigma_x$ for any $n$.
+For $\phi = -0.4$, $\sigma_x$ is covered at the nominal rate for $n \geq 1600$.
+For $\phi = -0.2$ and $\phi = 0$, $\sigma_x$ is covered at the nominal rate for $n \geq 400$.
+For $\phi = 0.2$, although the coverage does not reach the $95\%$ line by $n = 1600$, 
+it seems to be around $.945$ for $n \geq 400$
+For $\phi = 0.4$, although the coverage does not reach the $95\%$ line by $n = 1600$, 
+it seems to be above $.93$ for $n \geq 400$
 
-%phi
-%As dependence gets stronger, a larger sample size is necessary. 
-%Percentile and BCA deteriorate clearly for any level of temporal correlation 
-%Regardless of negative or positive
-%Should not be used
-%Centered and Standard perform similarly
-%For these a sample size of n = 800 appears to be necessary to recover phi at the nominal level
-% Student's t appears to recover phi at the nominal level for n >= 100
+Based on Figure~\ref{fig:phi}, 
+Percentile and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
+so they should not be used. The deterioration becomes more evident
+as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
+negative or positive. Centered and Standard CIs perform similarly;
+a sample size of $n = 800$ appears to be sufficient to recover $\phi$ at the 
+nominal level when using either of these two CIs. 
+Student's $t$ CIs appear to recover $\phi$ at the nominal level for $n \geq 100$ for all 
+$\phi$.
 \jy{One summary paragraph at the end.}
+\mc{paragraph below}
 
 To summarize, the CI type chosen should be based on the target parameter. 
-...
+When estimating $\mu$, the Student's t CI seems to have the highest coverage
+overall, although that leads to over-coverage when $\phi$ is -0.4. For a
+sample with no temporal dependence, the Student's t CI cover $\mu$ perfectly
+at the nominal rate even for small sample sizes. For positive $\phi$, a larger
+sample size appears to be necessary regardless of the CI used. In the case
+that $\phi$ is unknown and expected to be greater than $0$, $n > 1600$ may be
+necessary for block bootstrap interval estimation of $\mu$. If that is not the
+case, a lesser sample size is likely sufficient. When estimating $\sigma$,
+$BC_a$ should not be used, and Student's t again has the greatest coverage
+rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
+$n > 1600$ may be necessary for block bootstrap interval estimation of
+$\sigma$. If that is not the case, a lesser sample size is likely sufficent.
+When estimating $\phi$, Percentile and $BC_a$ CIs 
+deteriorate in coverage, indicating they should not be used in this context. 
+Increasing n will not fix the performance of either of these intervals 
+because the assumption that the coverage rate will approach the nominal level
+as n increases is invalid. Centered and Standard CIs managed to fix the
+deterioration problem, and they perform similarly, but Student's t covers
+$\phi$ at the nominal rate for small sample sizes regardless of the absolute
+value or sign of $\phi$. Interestingly, $n = 100$ seems to be large enough to
+recover $\phi$ when using the Student's t method.
 
@@
 When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
-unknown, the results of this study suggest that an $n$ of around 500 may be
-necessary for common practice to estimate a simple parameter like $\mu$, and
-an $n$ of around 400 may be necessary to
-estimate $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate to
-estimate these parameters. When $\phi$ was negative, a $n$ of around 100 was
-sufficient to estimate $\mu$. However, in real world applications, $\phi$ is
+unknown, the results of this study suggest that an $n$ of around $1600$ may be
+necessary for common practice to estimate a simple parameters like $\mu$ 
+or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
+to
+estimate these parameters. ... However, in real world applications, $\phi$ is
 more commonly found to be positive, so a larger $n$ is more likely to be
-necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
+necessary. Lastly, to estimate $\phi$, an $n$ of around $100$ using the Student's $t$ method
+ may be sufficient
 Further investigation may be necessary to see if there are other interval
@@
 bootstrap to be used versus other inference methods.
-This information could also prove to be useful for research using block bootstrap
+This information could also prove to be useful for research using block
+bootstrap
 estimation of time series in domains such as econometrics. Future studies

### 2023-05-13 Code/functions.R
New Data and Figures

@@ -100,36 +100,19 @@ mychk <- function(sim, target) {
   ret
 }
 
-df_bts <- function(cov, nrep = 10000, phis = c(-0.4, -0.2, 0, 0.2, 0.4), 
-                   sizes = c(100, 200, 400, 800, 1600), 
-                   types = c('pctCI', 'ctrCI', 'bcaCI', 'stdCI', 'stuCI'), 
-                   parameters = c('mu', 'sigma', 'phi')) {
-  phi <- 
-    rep(phis, each = length(sizes) * length(types) * length(parameters))
-  n <- 
-    rep(sizes, times = length(phis), each = length(types) * length(parameters))
-  CI <- 
-    rep(types, times = length(phis) * length(sizes), each = length(parameters))
-  t <- rep(parameters, times = length(phis) * length(types) * length(sizes))
-  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
-  UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
-  
-  c(data.frame(phi, n, CI, t, cov, LB, UB))
-}
-
 graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 {
   library(ggplot2)
   
-  data$CI <- factor(data$CI, levels = c("pctCI", "ctrCI", 'bcaCI', 'stdCI', 'stuCI'), 
-                    labels = c("Percentile", "Centered", "BCA", "Standard", 'Student\'s t'))
+  data$CI <- factor(data$CI, levels = c("stdCI", "stuCI", 'pctCI', 'ctrCI', 'bcaCI'), 
+                    labels = c("Standard", "Student\'s t", "Percentile", "Centered", 'BCA'))
   
   ggplot(data, aes(x = n, y = cov)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
     geom_line() +
     geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
     facet_grid(factor(phi) ~ CI) +
-    scale_x_continuous(breaks = c(100, 200, 400, 800, 1600), trans='log2') +
+    scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
     scale_y_continuous(trans=trans)
   ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''))

### 2023-05-13 Code/jobs.R

@@ -1,0 +1,15 @@
+source("functions.R")
+i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+results <- list()
+names(results) <- c()
+for (phi in c(-.4, -.2, 0, .2, .4)) {
+  for (n in c(100, 200, 400, 800, 1600, 3200)) {
+    blksize <- ceiling(n^(1/3))
+    target <- c(0, 1, phi)
+    set.seed(as.integer(i))
+    sim <- replicate(100, do1rep(n, phi, mystat, blksize))
+    results[[paste(phi, n, sep = '_')]] <- sim
+  }
+}
+saveRDS(results, paste('../Data/results', '_', i, '.rds', sep = ''))
+

### 2023-05-13 Code/processing.R

@@ -1,0 +1,40 @@
+source("functions.R")
+setwd("../Data")
+file_names <- list.files(pattern = "\\.rds$")
+all_lists <- lapply(file_names, function(x) {
+  loaded_list <- readRDS(x)
+  return(loaded_list)
+})
+list_of_matrices <- do.call(c, all_lists)
+grouped_matrices <- split(list_of_matrices, names(list_of_matrices))
+combined_matrices <- lapply(grouped_matrices, function(x) {
+  Reduce(cbind, x)
+})
+df <- data.frame(phi = numeric(), n = numeric(), CI = character(), 
+                 target = character(), cov = numeric(),
+                 LB = numeric(), UB = numeric())
+for(i in names(combined_matrices)) {
+  phi <- as.numeric(strsplit(i, '_')[[1]][1])
+  n <- as.integer(strsplit(i, '_')[[1]][2])
+  cov <- mychk(combined_matrices[[i]], c(0, 1, phi))
+  types <- c('pctCI', 'ctrCI', 'bcaCI', 'stdCI', 'stuCI')
+  CI <- rep(types, each = length(cov) / length(types))
+  parameters <- c('mu', 'sigma', 'phi')
+  target <- rep(parameters, length(cov) / length(parameters))
+  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
+  UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
+  new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), CI, target, cov, LB, UB)
+  df <- rbind(df, new_rows)
+}
+
+t <- 'mu'
+df_mu <- df[(df$target == t),]
+write.csv(df_mu,"df_mu.csv", row.names = FALSE)
+
+t <- 'sigma'
+df_sigma <- df[(df$target == t),]
+write.csv(df_sigma,"df_sigma.csv", row.names = FALSE)
+
+t <- 'phi'
+df_phi <- df[(df$target == t),]
+write.csv(df_phi,"df_phi.csv", row.names = FALSE)

### 2023-05-13 Code/simulation.R

@@ -1,27 +1,0 @@
-source("functions.R")
-nrep <- 10000
-cov <- c()
-for (phi in c(-.4, -.2, 0, .2, .4)) {
-  for (n in c(100, 200, 400, 800, 1600)) {
-    blksize <- ceiling(n^(1/3))
-    target <- c(0, 1, phi)
-    set.seed(10*(phi+n))
-    sim <- replicate(nrep, do1rep(n, phi, mystat, blksize))
-    write.csv(sim, paste('../Data/Raw/sim', '_', as.character(phi), '_', as.character(n), '.csv', sep = ''))
-    cov <- c(cov, mychk(sim, target))
-  }
-}
-
-df <- data.frame(df_bts(cov))
-
-t <- 'mu'
-df_mu <- df[(df$t == t),]
-write.csv(df_mu,"../Data/df_mu.csv", row.names = FALSE)
-
-t <- 'sigma'
-df_sigma <- df[(df$t == t),]
-write.csv(df_sigma,"../Data/df_sigma.csv", row.names = FALSE)
-
-t <- 'phi'
-df_phi <- df[(df$t == t),]
-write.csv(df_phi,"../Data/df_phi.csv", row.names = FALSE)

### 2023-05-13 Manuscript/manuscript.tex

@@
 $n$ is a multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$
-is $Y_j = \{X_{(j - 1) * l + 1}, \ldots, X_{(j - 1) * l + l}\}$,
+is $Y_j = \{X_{(j - 1) l + 1}, \ldots, X_{(j - 1) l + l}\}$,
 $j = 1, \ldots,   k$.  Then, we sample $k$ blocks of $Y_j$'s from the set 
@@
 words, define moving blocks (assuming $l > 1$) as:
-\jy{Any equation must be a part of a sentence and should be punctuated.}
-\jy{Recall a blank line means a new paragraph.}
-\jy{Define your response command with color and respond}
-\mc{addressed above comments}
 \begin{equation}
@@
     \begin{cases}
-        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
-        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\} & \text{if } j = n - l
+        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
+        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
         + 2 ,\dots, n.
@@
 \end{equation}
-\jy{The ending index does not seem right}
-\mc{addressed above}
-The second version of moving block bootstrap was used in
-this study because it is the implementation provided in the function
-\texttt{tsboot} from R package \textsl{boot} \citep{boot}, and it is easier
-overall because $l$ need not divide $n$.
-\jy{state we use it because it is implemented in package boot and cite boot}  
-\jy{This reference is from a low-tier journal. Find something from a stronger
-  journal?}
-\mc{addressed above comments}
-The block size~$l$ needs to chosen with care. It needs to be large enough for
+The wrap-around version does not require that $n/l$ be an integer.
+We used this version in this study as implemented in the function
+\texttt{tsboot} from R package \textsl{boot} \citep{boot}.
+
+The block size~$l$ needs to be chosen with care. It should be large enough for
 each bootstrap sample to preserve the serial dependence, yet small enough for
-there to be some variability between each bootstrap sample. As $n$ increases,
-$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
+there to be a large number of blocks to give sufficient variability between
+each bootstrap sample. As $n$ increases, both~$l$
+and $n / l$ should also increase. To achieve this, $l$ is
 often assigned a value as a function of $n$. A common function that is
-considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
-\citep{buhlmann1999block}, which is how the value of $l$ was determined for
-this
+considered optimal is $l = \lceil n^{1/3} \rceil$
+\citep{buhlmann1999block}, which was adopted in this
 study. It may be worth investigating in a future study if another block size
-scheme is 
+scheme is \jy{Seems out of place. Maybe in the discussion section.}
 optimal for the context of a time series by comparing different block sizes
@@
 
-\jy{can we give references to each of the method? How about the review paper in
-  Statistical Science?}
-\mc{references for percentile and BCA, couldn't find for centered, standard,
-  or student's t}
+\jy{order them as we discussed.}
 

### 2023-05-16 Manuscript/manuscript.tex
5/15 Manuscript Update

@@
 interval centered around the estimate, a bias-corrected and
-accelerated ($BC_a$) interval, a standard normal interval, and a student's $t$
+accelerated ($BC_a$) interval, a standard normal interval, and a Student's $t$
 interval. Their
@@
 \citep{buhlmann1999block}, which was adopted in this
-study. It may be worth investigating in a future study if another block size
-scheme is \jy{Seems out of place. Maybe in the discussion section.}
-optimal for the context of a time series by comparing different block sizes
-whilst keeping the sample size fixed.
+study.
 
@@
 \jy{order them as we discussed.}
+\mc{addressed}
+\paragraph{Standard Normal CI}
+The procedure for constructing a Standard Normal CI is described in 
+\citet{efron1993introduction}.
+A $(1 - \alpha$ standard normal CI depends on the standard error $\hat{SE}$
+for each of the
+$B$ bootstrap point estimates
+$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. 
+\[
+(\hat{\theta}_{n} - z_{(1-\alpha/2)}\hat{SE}, \hat{\theta}_{n} -
+z_{(\alpha/2)}\hat{SE}).
+\]
+This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
+The standard
+normal CI is a table-based bootstrap interval approach, which is to say that
+it relies on the 
+assumption that $\hat\theta_n$ is normally distributed and the expected value
+of $\hat\theta_n$
+is $\theta$.
+
+\paragraph{Student's $t$ CI}
+The procedure for constructing a Student's $t$ CI is described in 
+\citet{efron1993introduction}.
+A $(1 - \alpha$ Student's $t$ CI is
+\[
+(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{SE}, \hat{\theta}_{n} -
+t_{(\alpha/2), k -1}\hat{SE}),
+\]
+where $k$ is the number of blocks.
+This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
+Like the standard 
+normal interval, the Student's $t$ CI is a table-based bootstrap interval
+approach. In this case,
+we assume that $\hat\theta_n$ follows the $t_{k-1}$ distribution with an
+expected value of $\theta$.
 
@@
 
-\paragraph{Standard Normal CI}
-
-A $(1 - \alpha$ standard normal CI depends on the standard error $\hat{se}$
-for each of the
-$B$ bootstrap point estimates
-$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. 
-\[
-(\hat{\theta}_{n} - z_{(1-\alpha/2)}*\hat{se}, \hat{\theta}_{n} -
-z_{(\alpha/2)}*\hat{se}).
-\]
-This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
-The standard
-normal CI is a table-based bootstrap interval approach, which is to say that
-it relies on the 
-assumption that $\hat\theta_n$ is normally distributed and the expected value
-of $\hat\theta_n$
-is $\theta$.
-
-\paragraph{Student's $t$ CI}
-A $(1 - \alpha$ student's $t$ CI is
-\[
-(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}*\hat{se}, \hat{\theta}_{n} -
-t_{(\alpha/2), k -1}*\hat{se}),
-\]
-where k is the number of blocks.
-This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
-Like the standard 
-normal interval, the student's t CI is a table-based bootstrap interval
-approach. In this case,
-we assume that $\hat\theta_n$ follows the $t_{k-1}$ distribution with an
-expected value of $\theta$.
-
 \section{Simulation Study}
@@
 To investigate the effect of sample size~$n$, we considered an array of values
-$n \in \{100, 200, 400, 800, 1600\}$. In each configuration, we generated 10000
+$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 10000
 replicates. For each replicate, we constructed three 95\% block bootstrap
@@
 Based on Figure~\ref{fig:mu}, 
-the performance is about the same for Percentile, Centered, BCA, and 
-Standard CIs with respect to estimating $\mu$. They more or less need
-about the same sample size to have the correct coverage. For $\phi = -0.4$, 
-they slightly over-cover $\mu$ for all sample sizes, but the error bars generally 
-hover around the $95\%$ line. For $\phi = -0.2$, all four cover $\mu$ at the nominal 
-rate when $n = 400$, and when $n = 1600$, although there seems to be a dip in 
-coverage for $n = 800$. However, this deviation in trend can most likely be 
-attributed to noise. Besides that, the coverage rates remain above $.9375$ 
-for all sample sizes for this level of $\phi$. For $\phi = 0$, or when the 
-sample is independently normally distributed, $n = 1600$ seems to 
-be enough to recover $\mu$. For $\phi = 0.2$, the coverage rates are above 
-$.9375$ when $n = 800$ and $n = 1600$, but the coverage intervals do not contain
-$95\%$. Interestingly, there seems to be a drop in coverage rate from 
-$n = 800$ to $n = 1600$. For $\phi = 0.4$, the coverage rates are above $.925$
-when $n = 800$ and $n = 1600$, and there is a more noticeable downward 
-trend from $n = 800$ to $n = 1600$. Student's $t$ CI has noticeably higher coverage
-than the other CIs. For $\phi = -0.4$, the Student's $t$ CI actually 
-over-covers $\mu$ for all sample sizes, and the lower error bars
-are above the $95\%$ line for all sample sizes. For $\phi = -0.2$, it still slightly 
-over-covers $\mu$ for all sample sizers, but the error bars generally hover
-lower and around the $95\%$ line. For $\phi = 0$, the interval for the 
-coverage rate contains $.95$ for all sample sizes. For $\phi = 0.2$ and 
-$\phi = 0.4$, the trend in coverage is similar to the other CIs, but 
-the overall coverage rates are higher, although they still do not reach the $95\%$
-line.
+Student's $t$ CIs appear to have the greatest coverage rates with respect 
+to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover $\mu$
+for all sample sizes, whereas other CIs have coverage rates that
+hover around the $95\%$ line at this level of $\phi$. For $\phi = -0.2$, 
+Standard, Percentile, Centered, and $BC_a$ CIs cover $\mu$ at the nominal 
+rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
+for $n \geq 100$. For $\phi = 0$, or when the 
+sample is independently normally distributed, $n = 800$ seems to 
+be enough to recover $\mu$ when using Standard, Percentile, Centered, or $BC_a$ 
+CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$
+For $\phi = 0.2$, $n = 3200$ seems to be large enough when using
+Standard, Student's $t$, or Centered CIs, but Percentile and $BC_a$ CIs undercover
+$\mu$ for all sample sizes at this level of $\phi$.
+For $\phi = 0.4$, the Student's $t$ is the only type of CI that is able to recover $\mu$
+for a sample as large as $n = 3200$. The other CIs undercover $\mu$ for all sample 
+sizes at this level of $\phi$. Unsurprisingly, a greater level of $\phi$ demands a 
+larger $n$ to recover $\mu$ at the nominal rate.
 
@@
 there is no trend of coverage deterioration, indicating that there may eventually
-a sample size large enough for $\sigma_x$ to be covered at the nominal level.
-However, because it's performance is so much poorer than the other CIs,
-$BC_a$ should not be used. Percentile, Centered, and Standard CIs perform similarly,
-with respect to estimating $\sigma_x$. For $\phi = -0.4$, $\phi = -0.2$, and $\phi = 0$, 
-$n = 1600$ seems to be large enough to cover $\sigma_x$ at the nominal level
-when using the Standard Normal CI interval, while the others are very close, hovering
-around $.945$ for $n = 1600$. For $\phi > 0$, a larger sample size does seem
-to be necessary to cover $\sigma_x$ at the nominal rate. However, for $\phi = 0.2$, 
-when $n \geq 400$, coverage is above $.93$ for all three of these CIs. For $\phi = 0.4$,
-when $n = 1600$, coverage is above $.93$ for all three of these CIs.
-Like for $\mu$, Student's $t$ CIs have the highest overall coverage of $\sigma_x$.
-Additionally, the Student's $t$ method does not over-cover $\sigma_x$ for any $n$.
-For $\phi = -0.4$, $\sigma_x$ is covered at the nominal rate for $n \geq 1600$.
-For $\phi = -0.2$ and $\phi = 0$, $\sigma_x$ is covered at the nominal rate for $n \geq 400$.
-For $\phi = 0.2$, although the coverage does not reach the $95\%$ line by $n = 1600$, 
-it seems to be around $.945$ for $n \geq 400$
-For $\phi = 0.4$, although the coverage does not reach the $95\%$ line by $n = 1600$, 
-it seems to be above $.93$ for $n \geq 400$
+be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
+For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma$ when 
+$n = 3200$, whereas as the other CIs undercover $\sigma$ for all sample sizes.
+For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma$ at the 
+nominal rate for $n \geq 1600$, and Student's $t$ CIs cover $\sigma$ at the 
+nominal rate when $n \geq 800$. When $\phi = 0$, $n \geq 1600$ seems to 
+be large enough if Standard and Student's $t$ CIs are used. For $\phi = 0.2$, 
+consistent coverage of $\sigma$ at the nominal level appears to only be true
+for Student's $t$ CIs for $n \geq 1600$. For $\phi = 0.4$, the Student's $t$ CI is 
+able to reach nominal coverage of $\sigma$ when $n = 1600$, although in 
+our results, coverage appears to drop below the nominal rate for $n = 3200$, 
+indicating that perhaps an even larger $n$ is needed to recover $\sigma$ at
+this level of $\phi$.
 
@@
 $\phi$.
+
 \jy{One summary paragraph at the end.}
@@
 To summarize, the CI type chosen should be based on the target parameter. 
-When estimating $\mu$, the Student's t CI seems to have the highest coverage
+When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
 overall, although that leads to over-coverage when $\phi$ is -0.4. For a
-sample with no temporal dependence, the Student's t CI cover $\mu$ perfectly
+sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
 at the nominal rate even for small sample sizes. For positive $\phi$, a larger
 sample size appears to be necessary regardless of the CI used. In the case
-that $\phi$ is unknown and expected to be greater than $0$, $n > 1600$ may be
-necessary for block bootstrap interval estimation of $\mu$. If that is not the
-case, a lesser sample size is likely sufficient. When estimating $\sigma$,
-$BC_a$ should not be used, and Student's t again has the greatest coverage
+that $\phi$ is unknown and expected to be greater than $0$, $n = 3200$ may be
+necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
+a lesser sample size may be sufficient. When estimating $\sigma$,
+$BC_a$ should not be used, and Student's $t$ again has the greatest coverage
 rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
-$n > 1600$ may be necessary for block bootstrap interval estimation of
-$\sigma$. If that is not the case, a lesser sample size is likely sufficent.
+$n > 3200$ may be necessary for block bootstrap interval estimation of
+$\sigma$. Again, if $\phi$ is known, a lesser sample size may be enough.
 When estimating $\phi$, Percentile and $BC_a$ CIs 
 deteriorate in coverage, indicating they should not be used in this context. 
-Increasing n will not fix the performance of either of these intervals 
+Increasing $n$ will not fix the performance of either of these intervals 
 because the assumption that the coverage rate will approach the nominal level
-as n increases is invalid. Centered and Standard CIs managed to fix the
-deterioration problem, and they perform similarly, but Student's t covers
+as $n$ increases is invalid. Centered and Standard CIs managed to fix the
+deterioration problem, and they perform similarly, but Student's $t$ covers
 $\phi$ at the nominal rate for small sample sizes regardless of the absolute
 value or sign of $\phi$. Interestingly, $n = 100$ seems to be large enough to
-recover $\phi$ when using the Student's t method.
+recover $\phi$ when using the Student's $t$ method.
 
@@
     proportion out of 10000 replications for each $n$. Results for 
-    $n = 100, 200, 400, 800, 1600$ were recorded.}
+    $n = 100, 200, 400, 800, 1600, 3200$ were recorded.}
   \label{fig:mu}
@@
     proportion out of 10000 replications for each $n$. Results for 
-    $n = 100, 200, 400, 800, 1600$ were recorded.}
+    $n = 100, 200, 400, 800, 1600, 3200$ were recorded.}
   \label{fig:sigma}
@@
     proportion out of 10000 replications for each $n$. Results for 
-    $n = 100, 200, 400, 800, 1600$ were recorded.}
+    $n = 100, 200, 400, 800, 1600, 3200$ were recorded.}
   \label{fig:phi}
@@
 When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
-unknown, the results of this study suggest that an $n$ of around $1600$ may be
+unknown, the results of this study suggest that an $n$ of around $3200$ may be
 necessary for common practice to estimate a simple parameters like $\mu$ 
@@
 more commonly found to be positive, so a larger $n$ is more likely to be
-necessary. Lastly, to estimate $\phi$, an $n$ of around $100$ using the Student's $t$ method
+necessary. Lastly, to estimate $\phi$, an $n$ of around $100$ using the 
+Student's $t$ method
  may be sufficient

### 2023-05-16 Code/functions.R

@@ -112,6 +112,7 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
     geom_line() +
     geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
     facet_grid(factor(phi) ~ CI) +
+    labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
     scale_y_continuous(trans=trans)

### 2023-05-16 Manuscript/manuscript.tex
abstract rewritten

@@
 
-\author{Mathew Chandy
+\author{Mathew Chandy, Elizabeth Schifano,
 %   \href{mailto:mathew.chandy@uconn.edu}
@@
 \begin{abstract}
-Block bootstrap is a method that is useful for estimating a parameter of a time
-series. Theoretically, the method will work perfectly given an infinitely
-large sample of the time series. It is necessary to know how large of a finite
-sample is required for block bootstrap estimation to work. Before this study,
-there have been no investigations into this problem within the literature. The
-aim of this study is to answer this question by simulating replications of
-block bootstrap interval estimations of a parameter of a time series, and
-recording the rate at which the parameter is recovered by each replicate
-interval. The sample length required for acceptable performance is
-unsurprisingly found to be dependent on the type of interval construction and
-the series' level of temporal dependence.
+Block bootstrap is widely used in constructing confidence intervals for
+parameters estimated from stationary time series. Theoretically, the method
+should provide valid confidence intervals as the length of the time series goes
+to infinity. In practice, however, it is necessary to know how large of a finite
+sample is required for block bootstrap confidence intervals to work well. This
+study aims to answer this question in a simple simulation setting where the data
+are generated from an autoregressive process of order~1. The empirical coverage
+rates of several commonly used bootstrap confidence intervals for the mean,
+standard deviation, and the lag-1 autocorrelation are compared. \jy{put most
+  notable findings here. Possibly 1) large sample is needed; percentile
+  bootstrap is not working well for rho (can we offer some explanation?).}
 
@@
 \doublespace
-
-\jy{Practice my writing tips on latex (e.g., keep line width under 80; use
-  double blank lines to separate paragraphs; etc.):
-  \url{
-https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html},
-  chapter 2}
 
@@
 inference from closed-form asymptotic estimates, but block bootstrap percentile
+\jy{did they do block or standard bootstrap?}
 CIs still do not have sufficient coverage even for sample size

### 2023-05-17 Manuscript/manuscript.tex
cleaning/comments

@@
 study aims to answer this question in a simple simulation setting where the data
-are generated from an autoregressive process of order~1. The empirical coverage
+are generated from a first-order autoregressive process. The empirical coverage
 rates of several commonly used bootstrap confidence intervals for the mean,
@@
 
+\jy{I added more references to the reference folder that studied coverage of
+  bootstrap CIs but not block bootstrap CIs.}
+
 The goal of this paper is to provide some practical recommendations on
@@
 
-\subsection{Block Bootstrap Sample}
+\subsection{Block Bootstrap}
 
@@
 \end{equation}
-The wrap-around version does not require that $n/l$ be an integer.
+This version does not require that $n/l$ be an integer.
 We used this version in this study as implemented in the function
@@
 considered optimal is $l = \lceil n^{1/3} \rceil$
-\citep{buhlmann1999block}, which was adopted in this
-study.
+\citep{buhlmann1999block}, which was adopted in this study.
 
@@
 
-\jy{order them as we discussed.}
-\mc{addressed}
+\jy{Read carpenter2000bootstrap and cite it; quite useful in sorting the literature}
+
 \paragraph{Standard Normal CI}
-The procedure for constructing a Standard Normal CI is described in 
-\citet{efron1993introduction}.
-A $(1 - \alpha$ standard normal CI depends on the standard error $\hat{SE}$
-for each of the
-$B$ bootstrap point estimates
-$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. 
+Assuming that $\hat\theta_n$ is asymptotically normally distributed with
+$\theta$ as the mean, we just need an estimate of the standard error to
+construct an approximate CI \citep[p.168]{efron1993introduction}.
+Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
+copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$.
+A $(1 - \alpha)$ standard normal CI is
 \[
-(\hat{\theta}_{n} - z_{(1-\alpha/2)}\hat{SE}, \hat{\theta}_{n} -
-z_{(\alpha/2)}\hat{SE}).
+(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
+\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
 \]
 This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
-The standard
-normal CI is a table-based bootstrap interval approach, which is to say that
-it relies on the 
-assumption that $\hat\theta_n$ is normally distributed and the expected value
-of $\hat\theta_n$
-is $\theta$.
+Its validity relies on whether the distribution of $\hat\theta_n$ is reasonaly
+well approximated by its asymptotic normal distribution and whether the
+bootstrap $\widehat{\text{SE}}$ approximates the true standard error.
 
@@
 $\theta$.
-\jy{why is it called BCA?}
-\mc{addressed}
 
@@
 that blocks are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.
-\jy{size? also it was overlapping blocks. Describe the details here.}
-\mc{addressed}
+
 \eds{Is $l = \lceil n^{1/3} \rceil$? Is it also worth investigating different 
@@
 
-\jy{One paragraph for each parameter; write down your observations in bullet
-  points and then organize them into a logically flowing paragraph.}
-\mc{paragraphs below}
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_mu}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of an AR(1) process with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates.
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_sigma}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma$ of an AR(1) process with AR
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates.
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:sigma}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_phi}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates.
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:phi}
+\end{figure}
+
+\jy{I'm curiouss why the coverge is so poor for the percentile method. Could
+  plot 50 intervals for phi using different sample sizes?}
 
@@
 
-\jy{One summary paragraph at the end.}
-\mc{paragraph below}
-
 To summarize, the CI type chosen should be based on the target parameter. 
@@
 recover $\phi$ when using the Student's $t$ method.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_mu}
-  \caption{Plots of $\mu$ coverage rates for each interval type and $\phi$
-    combination. The orange dotted line represents the 95\% nominal coverage
-    rate. The error bars represent a 95\% CI for the coverage
-    proportion out of 10000 replications for each $n$. Results for 
-    $n = 100, 200, 400, 800, 1600, 3200$ were recorded.}
-  \label{fig:mu}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_sigma}
-  \caption{Plots of $\sigma_x$ coverage rates for each interval type and $\phi$
-    combination. The orange dotted line represents the 95\% nominal coverage
-    rate. The error bars represent a 95\% CI for the coverage
-    proportion out of 10000 replications for each $n$. Results for 
-    $n = 100, 200, 400, 800, 1600, 3200$ were recorded.}
-  \label{fig:sigma}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_phi}
-  \caption{Plots of $\phi$ coverage rates for each interval type and $\phi$
-    combination. The orange dotted line represents the 95\% nominal coverage
-    rate. The error bars represent a 95\% CI for the coverage
-    proportion out of 10000 replications for each $n$. Results for 
-    $n = 100, 200, 400, 800, 1600, 3200$ were recorded.}
-  \label{fig:phi}
-\end{figure}
 

### 2023-05-17 Manuscript/manuscript.tex
Included New References in Introduction

@@
 rates of several commonly used bootstrap confidence intervals for the mean,
-standard deviation, and the lag-1 autocorrelation are compared. \jy{put most
+standard deviation, and the lag-1 autocorrelation are compared. In this 
+study, we find that a large sample is needed to recover even a simple
+parameter like the mean, and that the selection of interval type is very
+important, especially in the case of $\phi$, for which the coverage deteriorates
+as the sample size increases.
+\jy{put most
   notable findings here. Possibly 1) large sample is needed; percentile
@@
 when making inferences about dependent data. Early ideas were developed
-independently by \citet{hall1985resampling}, \citet{carlstein1986use}, and 
-\citet{kunsch1989jackknife}.
+independently by \citet{hall1985resampling, carlstein1986use, kunsch1989jackknife}.
 It has since been applied in various fields such as econometrics
@@
 with
-dependent data, \citet{goncalves2005bootstrap} find that standard error
-estimates from block bootstrap in small samples may be more accurate than
-inference from closed-form asymptotic estimates, but block bootstrap percentile
+dependent data where the
+regression errors are generated from a homoscedastic AR(1) process, 
+\citet{goncalves2005bootstrap} find that standard error
+estimates from bootstrap in small samples may be more accurate than
+inference from closed-form asymptotic estimates, but moving block bootstrap 
 \jy{did they do block or standard bootstrap?}
-CIs still do not have sufficient coverage even for sample size
+\mc{moving block bootstrap}
+CIs still do not have sufficient coverage of the target parameter even for sample size
 $n = 1024$.
-
+Also in the setting of linear regression, but focused on estimating the proportion of 
+variation attributable to a certain variable, \citet{burch2012nonparametric} finds
+that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected and
+Accelerated) approach the coverage of a pivotal quantity as $n$ gets larger for an
+underlying normal distribution. However, they find that for other distributions, 
+coverage may deteriorate as $n$ increases.
+\citet{chernick2009revisiting} finds that the the best choice of method for estimating
+the parameter of a distribution is dependent on the sample size, the number of
+bootstrap resamples, and the confidence level.
+When attempting to create interval estimations for the Pearson correlation 
+coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
+methods to be less accurate than the Fisher's transformation method even 
+for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
 \jy{I added more references to the reference folder that studied coverage of
@@
 The goal of this paper is to provide some practical recommendations on
-necessary sample size for block bootstrap with dependent data. We consider a
+necessary sample size for block bootstrap with dependent data, similar to what 
+was done for basic bootstrap in \citet{hesterberg2015teachers}. We consider a
 simple situation of a stationary time series, where the parameters of
@@
 This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
-Its validity relies on whether the distribution of $\hat\theta_n$ is reasonaly
+Its validity relies on whether the distribution of $\hat\theta_n$ is reasonably
 well approximated by its asymptotic normal distribution and whether the
@@
 approach. In this case,
-we assume that $\hat\theta_n$ follows the $t_{k-1}$ distribution with an
-expected value of $\theta$.
+its validity relies on whether the distribution of $\hat\theta_n$ is
+reasonably well approximation by the $t_{k-1}$ distribution with an
+expected value of $\theta$, and whether the bootstrap 
+$\widehat{\text{SE}}$ approximates the true standard error.
 

### 2023-05-17 Code/phi_intervals.R
Phi Interval Figures

@@ -1,0 +1,48 @@
+results_1 <- readRDS('../Data/results_1.rds')
+mtrx <- c()
+for(i in names(results_1)) {
+  toadd <- results_1[[i]][c(5,6,17,18),]
+  toadd <- cbind(rep(i, nrow(toadd)), rep(c('PCT', 'BCA'), each = 2, length.out = nrow(toadd)), toadd)
+  mtrx <- rbind(mtrx, toadd)
+}
+# Assuming your matrix is named 'data_matrix'
+# 'data_matrix' is a 120x100 matrix with title in the first column
+
+# Set the number of plots and intervals
+num_plots <- nrow(mtrx) / 2
+num_intervals <- ncol(mtrx) - 2
+
+# Iterate over each plot
+for (i in 1:num_plots) {
+  # Calculate the row indices for the current plot
+  pdf(paste('../Manuscript/figures/', plot_title, '.pdf'))
+  start_row <- (i - 1) * 2 + 1
+  end_row <- start_row + 1
+  
+  # Extract the data for the current plot
+  interval_data <- mtrx[start_row:end_row, 3:ncol(mtrx)]
+  interval_data <- apply(interval_data, c(1, 2), as.numeric)
+  plot_title <- paste(mtrx[start_row, 1], mtrx[start_row, 2])
+  
+  # Create a new plot
+  plot(x = 1:num_intervals,
+       y = NULL,
+       xlim = c(1, num_intervals),
+       ylim = range(-.75, .75),
+       type = 'n',
+       xlab = 'Interval',
+       ylab = 'Confidence Interval',
+       main = plot_title,
+       yaxt = 'n')
+  
+  # Add lower and upper bounds as line segments
+  for (j in 1:num_intervals) {
+    lower_bound <- interval_data[1, j]
+    upper_bound <- interval_data[2, j]
+    
+    lines(c(j, j), c(lower_bound, upper_bound), type = 'l', col = 'blue')
+  }
+  
+  axis(2, at = c(-0.4, -0.2, 0, 0.2, 0.4))
+  dev.off()
+}

### 2023-05-18 Manuscript/manuscript.tex
Fixed carpenter2000bootstrap

@@
 \paragraph{Centered Percentile CI}
+The procedure for constructing a Centered Percentile CI - referred to as
+a Non-Studentized pivotal method - is described in \citet{carpenter2000bootstrap}.
 Centered percentile CI is centered at the point estimator and uses the

### 2023-05-18 Code/functions.R
Code Changes and New Method

@@ -18,23 +18,30 @@ do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
   bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
   alpha <- 1 - level
   
+  ## Standard interval
+  se <- apply(bts$t, 2, sd)
+  stdCI <- sapply(1:length(bts$t0),
+                  function(i) c(bts$t0[i] - qnorm(1-alpha/2)*se[i], bts$t0[i] - 
+                                  qnorm(alpha/2)*se[i]))
   
+  ## Student's t interval
+  stuCI <- sapply(1:length(bts$t0),
+                  function(i) c(bts$t0[i] - qt(1-alpha/2, n/blksize)*se[i], 
+                                bts$t0[i] - qt(alpha/2, n/blksize)*se[i]))
   ## Percentile interval
   pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
   
-  ## Centered interval
-  mbts <- apply(bts$t, 2, mean)
+  ## Centered Bootstrap Percentile interval (from singh2008bootstrap)
   crit <- 
-    apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
-  ## alpha/2 and 1 - alpha/2 critical values 
-  ## of pseudo-estimate - mean of pseudo-estimates
-  # crit2 <- 
-  #  apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
-  ## alpha/2 and 1 - alpha/2 critical values 
-  ## of pseudo-estimate - original estimate
+    apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(1 - alpha/2, alpha/2)) 
+  mbts <- apply(bts$t, 2, mean)
+  ctrCI <- -sweep(crit, 2, bts$t0, FUN = '-')
   
-  ## interval centered around...
-  ctrCI <- sweep(crit, 2, bts$t0, FUN = '+') # original estimate
+  ## Our Centered interval
+  crit2 <- 
+    apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
+  ourctrCI <- sweep(crit2, 2, bts$t0, FUN = '+') # original estimate
+  
[…]

### 2023-05-18 Code/processing.R

@@ -17,7 +17,7 @@ for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
   cov <- mychk(combined_matrices[[i]], c(0, 1, phi))
-  types <- c('pctCI', 'ctrCI', 'bcaCI', 'stdCI', 'stuCI')
+  types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'ourctrCI', 'bcaCI')
   CI <- rep(types, each = length(cov) / length(types))
   parameters <- c('mu', 'sigma', 'phi')
   target <- rep(parameters, length(cov) / length(parameters))

### 2023-05-21 Manuscript/manuscript.tex
5/21 Manuscript Update

--- 2023-05-17 Manuscript/manuscript.tex
@@
 are more accurate than $t$-intervals for larger sample sizes, they are
-less accurate for smaller sample sizes. In the context of structural equation
+less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds that the the best choice of method for estimating
+the parameter of a distribution is dependent on the sample size, the number of
+bootstrap resamples, and the confidence level. In the context of structural equation
 modeling, \citet{nevitt2001performance} find
@@
 sample
-size for block bootstrap is even less clear. In a linear regression setting
+size for bootstrap is even less clear. In the setting of linear regression and focused on estimating the proportion of 
+variation attributable to a certain variable, \citet{burch2012nonparametric} finds
+that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected and
+Accelerated) approach the coverage of a pivotal quantity as $n$ gets larger for an
+underlying normal distribution. However, they find that for other distributions, 
+coverage may deteriorate as $n$ increases. 
+When attempting to create interval estimations for the Pearson correlation 
+coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
+methods to be less accurate than the Fisher's transformation method even 
+for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
+Few studies have provided a practical guide on what size is needed
+for block bootstrap inference for dependent data.
+In a linear regression setting
 with
@@
 \citet{goncalves2005bootstrap} find that standard error
-estimates from bootstrap in small samples may be more accurate than
+estimates from moving 
+block bootstrap in small samples may be more accurate than
 inference from closed-form asymptotic estimates, but moving block bootstrap 
@@
 $n = 1024$.
-Also in the setting of linear regression, but focused on estimating the proportion of 
-variation attributable to a certain variable, \citet{burch2012nonparametric} finds
-that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected and
-Accelerated) approach the coverage of a pivotal quantity as $n$ gets larger for an
-underlying normal distribution. However, they find that for other distributions, 
-coverage may deteriorate as $n$ increases.
-\citet{chernick2009revisiting} finds that the the best choice of method for estimating
-the parameter of a distribution is dependent on the sample size, the number of
-bootstrap resamples, and the confidence level.
-When attempting to create interval estimations for the Pearson correlation 
-coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
-methods to be less accurate than the Fisher's transformation method even 
-for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
 \jy{I added more references to the reference folder that studied coverage of
@@
 as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
-negative or positive. Centered and Standard CIs perform similarly;
-a sample size of $n = 800$ appears to be sufficient to recover $\phi$ at the 
-nominal level when using either of these two CIs. 
-Student's $t$ CIs appear to recover $\phi$ at the nominal level for $n \geq 100$ for all 
-$\phi$.
+negative or positive. When $\phi = -0.4$, Standard and Centered CIs 
+recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
+Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
+$\phi = -0.2$, Standard and Centered CIs recover $\phi$ at $n = 800$, whereas 
+Student's $t$ CIs recover $\phi$ for $n \geq 100$. When
+$\phi = 0$, Standard and Centered CIs recover $\phi$ at $n = 3200$, and 
+$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
+and Centered CIs cover $\phi$ at the nominal rate for $n \geq 800$, whereas 
+Student's $t$ CIs can accomplish this at $n \geq 400$. For $\phi = 0.4$, $n \geq 
+800$ is large enough for Standard and Centered CIs. Student's $t$ CIs either
+recover or over-cover $\phi$ for all $n \geq 100$.
 
@@
 deterioration problem, and they perform similarly, but Student's $t$ covers
-$\phi$ at the nominal rate for small sample sizes regardless of the absolute
-value or sign of $\phi$. Interestingly, $n = 100$ seems to be large enough to
+$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
+$n = 800$ is large enough to
 recover $\phi$ when using the Student's $t$ method.
@@
 there is a size $n$ large enough for the method to work: that is, the method's
-performance improves as $n$ increases. Out of the two types of intervals used
+performance improves as $n$ increases. Out of the five types of intervals used
 in this study, this assumption was found to hold true with respect to
-estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
-percentile and $BC_a$ intervals exhibited coverage deterioration as $n$
-increased.
+estimating $\phi$ only for Standard, Student's $t$, and Centered CIs, whereas both
+Percentile and $BC_a$ intervals exhibited coverage deterioration as $n$
+increased. The Percentile CI's coverage deterioration can be attributed to
+bias that is not corrected as $n$ increases. Specifically, as $n$ increases, 
+the width of the CI decreases, but because the Percentile CI
+underestimates $\phi$, the coverage decreases. The $BC_a$ CI does seem to correct the bias, but the acceleration factor seems to fail, as the width of the CI
+seems to be inconsistent.
 
-When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
+When using Student's $t$ centered intervals and $\phi$ is
 unknown, the results of this study suggest that an $n$ of around $3200$ may be
-necessary for common practice to estimate a simple parameters like $\mu$ 
+necessary for common practice to estimate simpler parameters like $\mu$ 
 or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
 to
-estimate these parameters. ... However, in real world applications, $\phi$ is
-more commonly found to be positive, so a larger $n$ is more likely to be
-necessary. Lastly, to estimate $\phi$, an $n$ of around $100$ using the 
+estimate these parameters. For lower absolute values of $\phi$, a smaller
+$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
+values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
+Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$, 
+meaning that if $\phi$ is known to have a very negative value, another CI
+should be used.
+$However, in real world applications, $\phi$ is
+more commonly found to be positive, so Student's $t$ should still be used
+if $\phi$ is unknown.
+Lastly, to estimate $\phi$, an $n$ of around $800$ using the 
 Student's $t$ method
- may be sufficient
+ may be sufficient.
 Further investigation may be necessary to see if there are other interval

### 2023-05-21 Code/functions.R

@@ -109,7 +109,7 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
     geom_line() +
     geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
-    facet_grid(factor(phi) ~ CI) +
+    facet_grid(factor(CI) ~ factor(phi), scales = 'free') +
     labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) +

### 2023-05-21 Code/plots.R

@@ -3,13 +3,13 @@ df_sigma <- read.csv("../Data/df_sigma.csv")
 df_phi <- read.csv("../Data/df_phi.csv")
 
 t <- 'mu'
-width <- .1
+width <- .2
 graph_bts(t, width, df_mu)
 
 t <- 'sigma'
-width <- .1
+width <- .2
 graph_bts(t, width, df_sigma)
 
 t <- 'phi'
-width <- .1
+width <- .2
 graph_bts(t, width, df_phi)

### 2023-05-21 Manuscript/manuscript.tex
BC and question about BCA

@@
 \paragraph{Student's $t$ CI}
-The procedure for constructing a Student's $t$ CI is described in 
-\citet{efron1993introduction}.
-A $(1 - \alpha$ Student's $t$ CI is
+The procedure for constructing a Student's $t$ CI based on standard bootstrap is
+described in \citet{efron1993introduction}. \jy{give page or section number when
+  citing a book}
+With block bootstrapping, a $(1 - \alpha)$ Student's $t$ CI is
 \[
-(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{SE}, \hat{\theta}_{n} -
-t_{(\alpha/2), k -1}\hat{SE}),
+(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
+\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
 \]
@@
 \paragraph{Percentile CI}
-The percentile interval was first suggested in \citet{efron1979bootstrap}.
+The percentile CI was first suggested in \citet{efron1979bootstrap}.
 Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
@@
 \[
-(\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}).
+(\hat\theta_{n, \alpha/2}^{(b)}, \quad \hat\theta_{n, 1 - \alpha/2}^{(b)}).
 \]
@@
 should be used.
-$However, in real world applications, $\phi$ is
+However, in real world applications, $\phi$ is
 more commonly found to be positive, so Student's $t$ should still be used

### 2023-05-21 Code/functions.R

@@ -17,6 +17,7 @@ do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
   }
   bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
   alpha <- 1 - level
+
   
   ## Standard interval
   se <- apply(bts$t, 2, sd)
@@ -41,7 +42,14 @@ do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
   crit2 <- 
     apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
   ourctrCI <- sweep(crit2, 2, bts$t0, FUN = '+') # original estimate
-  
+
+  ## Carpenter et al 2000, p. 1153
+  b <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
+  qup <- pnorm(2 * b - qnorm(alpha / 2))
+  qlo <- pnorm(2 * b - qnorm(1 - alpha / 2))
+  bcCI <- sapply(1:length(bts$t0),
+                 function(i) quantile(bts$t[,i], prob=c(qlo[i], qup[i])))
+
   ## LB: bts$t0 + alpha/2 crit, UB: bts$t0 + (1 - alpha/2) crit
   # mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
   ## LB: mbts + alpha/2 crit2, UB: mbts + (1 - alpha/2) crit2
@@ -49,12 +57,12 @@ do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
   ## LB: bts$t0 - (1 - alpha/2) crit, UB: bts$t0 - alpha/2 crit and
   ## LB: mbts - (1 - alpha/2) crit2, UB: mbts - alpha/2 crit2
   
-  ## BCa interval
-  z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
+  ## BCa interval: Diciccio and Efron (1996): p.195
+  z0 <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0)) # same as b in Carpenter 2000
   thetajack <- sapply(1: (n / blksize),
                       function(i)
                         statistic(x[ - ((i - 1) * blksize + 1:blksize)]))
-  a <- apply(thetajack, 1, e1071::skewness, type = 1) / 6 * (n / blksize)^-0.5
[…]

### 2023-05-22 Manuscript/manuscript.tex
Updated BCA Procedure

@@
 for $b \in \{1, \ldots, B\}$. 
-Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, and let
-$\hat{\theta}_{n, -i}$ be the jackknife values of $Z_{(i)}$
+Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
+$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
 for $i \in \{1, \ldots, n\}$, 
-and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
-$\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} +
-  z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
+and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
+Let 
+\[
+\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} - \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} - \hat{\theta}_{(i)})^2\}^{3/2}}
+.\] For a $1 - \alpha$ CI, let
+\[
+\alpha_1 = \Phi(z_0 + \frac{z_{0} +
+  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}).
+\]
+\[
+\alpha_2 = \Phi(z_0 + \frac{z_{0} +
+  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}).
+\]
 \eds{notation will need to be cleaned and clarified}
-A $(1 - \alpha)$ centered $BC_a$ CI is
+A $(1 - \alpha) BC_a$ CI is
 \[
-(\hat\theta_{BC_a}[\alpha/2], \quad
-\hat\theta_{BC_a}[1 - \alpha/2]).
+(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
 \]

### 2023-05-24 Manuscript/manuscript.tex
New CIs

@@
 
+\paragraph{Centered Bootstrap Percentile CI}
+The procedure for constructing a Centered Bootstrap Percentile CI based on standard bootstrap is
+described in \citet{singh2008bootstrap}.
+The $(1 - \alpha)$ Centered Bootstrap Percentile CI is
+\[
+(2\hat{\theta}_{n} - \hat\theta_{n, 1 - \alpha/2}^{(b)}, \quad
+2\hat{\theta}_{n} - \hat\theta_{n, \alpha/2}^{(b)})).
+\]
+This CI is necessarily centered around the point estimator $\hat\theta_n$ and
+is asymmetric, as different critical values are used to compute
+the lower and upper bounds.
+
 \paragraph{Centered Percentile CI}
@@
 the lower and upper bounds.
+
+\paragraph{Bias Corrected Bootstrap CI}
+The procedure for constructing a Bias Corrected Bootstrap CI based on standard bootstrap is
+described in \citet{carpenter2000bootstrap}.
+Let $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
+for $b \in \{1, \ldots, B\}$. 
+For a $1 - \alpha$ CI, let
+\[
+\alpha_1 = \Phi(2b - z_{\alpha/2}).
+\]
+\[
+\alpha_2 = \Phi(2b - z_{1 - \alpha/2}).
+\]
+A $(1 - \alpha) BC_a$ CI is
+\[
+(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
+\]
 

### 2023-05-25 Manuscript/manuscript.tex
5/25 Manuscript Update

@@
 for all sample sizes, whereas other CIs have coverage rates that
-hover around the $95\%$ line at this level of $\phi$. For $\phi = -0.2$, 
-Standard, Percentile, Centered, and $BC_a$ CIs cover $\mu$ at the nominal 
+hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
+$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
+Standard, Percentile, CBP, Centered, and $BC$ CIs seem to 
+generally cover $\mu$ at the nominal 
 rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
 for $n \geq 100$. For $\phi = 0$, or when the 
-sample is independently normally distributed, $n = 800$ seems to 
-be enough to recover $\mu$ when using Standard, Percentile, Centered, or $BC_a$ 
-CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$
-For $\phi = 0.2$, $n = 3200$ seems to be large enough when using
-Standard, Student's $t$, or Centered CIs, but Percentile and $BC_a$ CIs undercover
-$\mu$ for all sample sizes at this level of $\phi$.
-For $\phi = 0.4$, the Student's $t$ is the only type of CI that is able to recover $\mu$
-for a sample as large as $n = 3200$. The other CIs undercover $\mu$ for all sample 
-sizes at this level of $\phi$. Unsurprisingly, a greater level of $\phi$ demands a 
-larger $n$ to recover $\mu$ at the nominal rate.
+sample is independently normally distributed, $n = 1600$ seems to 
+be enough to recover $\mu$ when using Standard, Percentile, CBP, Centered, or $BC$ 
+CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
+$\phi = 0$.
+For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
+at the nominal level when using
+any of the CIs, although some CIs, such as Student's $t$, are much closer to the
+$95\%$ line than others, most notably $BC_a$.
+For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
+Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.
 
 Based on Figure~\ref{fig:sigma}, 
-$BC_a$ CIs greatly undercover $\sigma_x$ for all sample sizes, although
+$BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
+$\phi$, observed, although
 there is no trend of coverage deterioration, indicating that there may eventually
@@
 For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma$ when 
-$n = 3200$, whereas as the other CIs undercover $\sigma$ for all sample sizes.
+$n = 1600$, but undercover $\sigma$ for $n = 3200$, indicating
+that a larger $n$ is most likely necessary to consistently cover $\sigma$ at the 
+nominal rate.
+The other CI types undercover $\sigma$ for all sample sizes at $\phi = 0.4$.
 For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma$ at the 
-nominal rate for $n \geq 1600$, and Student's $t$ CIs cover $\sigma$ at the 
-nominal rate when $n \geq 800$. When $\phi = 0$, $n \geq 1600$ seems to 
-be large enough if Standard and Student's $t$ CIs are used. For $\phi = 0.2$, 
-consistent coverage of $\sigma$ at the nominal level appears to only be true
-for Student's $t$ CIs for $n \geq 1600$. For $\phi = 0.4$, the Student's $t$ CI is 
-able to reach nominal coverage of $\sigma$ when $n = 1600$, although in 
-our results, coverage appears to drop below the nominal rate for $n = 3200$, 
-indicating that perhaps an even larger $n$ is needed to recover $\sigma$ at
-this level of $\phi$.
+nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
+nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
+be large enough if Standard CIs are used, and $n \geq 400$ is fine is
+Student's $t$ CIs are used. $n \geq 3200$ appears necessary 
+for other CIs. For $\phi = 0.2$, 
+comfortable coverage of $\sigma$ at the nominal level appears to only be true
+for Student's $t$ CIs for $n \geq 3200$, although Standard and CBP CIs.
+For $\phi = 0.4$, a much larger sample size appears to be necessary.
+Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.
 
 Based on Figure~\ref{fig:phi}, 
-Percentile and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
+Percentile, CBP, $BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
 so they should not be used. The deterioration becomes more evident
@@
 Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
-$\phi = -0.2$, Standard and Centered CIs recover $\phi$ at $n = 800$, whereas 
-Student's $t$ CIs recover $\phi$ for $n \geq 100$. When
-$\phi = 0$, Standard and Centered CIs recover $\phi$ at $n = 3200$, and 
+$\phi = -0.2$, Standard and Centered CIs recover $\phi$ at $n = 800$ and 
+$n = 1600$, 
+although they undercover $\phi$ at $n = 3600$, indicating that 
+perhaps a larger $n$ is needed if these CIs are uses. However,
+Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
+$\phi = 0$, Standard and Centered CIs recover $\phi$ relatively comfortably 
+at $n = 3200$, and 
 $n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
-and Centered CIs cover $\phi$ at the nominal rate for $n \geq 800$, whereas 
-Student's $t$ CIs can accomplish this at $n \geq 400$. For $\phi = 0.4$, $n \geq 
+and Centered CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
+Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
 800$ is large enough for Standard and Centered CIs. Student's $t$ CIs either
@@
 sample size appears to be necessary regardless of the CI used. In the case
-that $\phi$ is unknown and expected to be greater than $0$, $n = 3200$ may be
+that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
 necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
@@
 in this study, this assumption was found to hold true with respect to
-estimating $\phi$ only for Standard, Student's $t$, and Centered CIs, whereas both
-Percentile and $BC_a$ intervals exhibited coverage deterioration as $n$
+estimating $\phi$ only for Standard, Student's $t$, and Centered CIs, whereas 
+Percentile, CBP, $BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
 increased. The Percentile CI's coverage deterioration can be attributed to
@@
 When using Student's $t$ centered intervals and $\phi$ is
-unknown, the results of this study suggest that an $n$ of around $3200$ may be
+unknown, the results of this study suggest that an $n > 3200$ may be
 necessary for common practice to estimate simpler parameters like $\mu$ 

### 2023-05-28 Manuscript/manuscript.tex
Small Manuscript Update

@@
 
-\paragraph{Centered Percentile CI}
-Centered percentile CI is centered at the point estimator and uses the
+\paragraph{Proposed Method CI}
+Our Proposed Method CI is centered at the point estimator and uses the
 variation
@@
 the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
-estimates, and $\delta$, the difference between a point estimate and
-$\bar\theta_n^{(b)}$. For $b \in \{1, \ldots, B\}$, we can obtain a
-$\delta^{(b)}$ based on the $b$th bootstrap point estimate. Let
-$\delta_{\alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
-$\{\delta^{(1)}, \ldots,  \delta^{(B)}\}$.  
-A $(1 - \alpha)$ centered percentile CI is
+estimates, and $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$.
+A $(1 - \alpha)$ CI using our Proposed Method is
 \[
-(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2}, \quad
-\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
+(\hat\theta_{n, \alpha/2}^{(b)} - \hat{bias}, \quad
+\hat\theta_{n, 1 - \alpha/2}^{(b)} - \hat{bias}).
 \]
-This CI is necessarily centered around the point estimator $\hat\theta_n$ and
+This CI is necessarily centered around .... and
 is asymmetric, as different critical values are used to compute
@@
 $BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
-Standard, Percentile, CBP, Centered, and $BC$ CIs seem to 
+Standard, Percentile, CBP, Proposed Method, and $BC$ CIs seem to 
 generally cover $\mu$ at the nominal 
@@
 sample is independently normally distributed, $n = 1600$ seems to 
-be enough to recover $\mu$ when using Standard, Percentile, CBP, Centered, or $BC$ 
+be enough to recover $\mu$ when using Standard, Percentile, CBP, Proposed Method, or $BC$ 
 CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
@@
 as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
-negative or positive. When $\phi = -0.4$, Standard and Centered CIs 
+negative or positive. When $\phi = -0.4$, Standard and Proposed Method CIs 
 recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
 Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
-$\phi = -0.2$, Standard and Centered CIs recover $\phi$ at $n = 800$ and 
+$\phi = -0.2$, Standard and Proposed Method CIs recover $\phi$ at $n = 800$ and 
 $n = 1600$, 
@@
 Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
-$\phi = 0$, Standard and Centered CIs recover $\phi$ relatively comfortably 
+$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively comfortably 
 at $n = 3200$, and 
 $n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
-and Centered CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
+and Proposed Method CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
 Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
-800$ is large enough for Standard and Centered CIs. Student's $t$ CIs either
+800$ is large enough for Standard and Proposed Method CIs. Student's $t$ CIs either
 recover or over-cover $\phi$ for all $n \geq 100$.
@@
 because the assumption that the coverage rate will approach the nominal level
-as $n$ increases is invalid. Centered and Standard CIs managed to fix the
+as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix the
 deterioration problem, and they perform similarly, but Student's $t$ covers
@@
 recover $\phi$ when using the Student's $t$ method.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/pct}
+  \caption{}
+  \label{fig:pct}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/prop}
+  \caption{}
+  \label{fig:prop}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/bc}
+  \caption{}
+  \label{fig:bc}
+\end{figure}
 
@@
 in this study, this assumption was found to hold true with respect to
-estimating $\phi$ only for Standard, Student's $t$, and Centered CIs, whereas 
+estimating $\phi$ only for Standard, Student's $t$, and Proposed Method CIs, whereas 
 Percentile, CBP, $BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$

### 2023-05-28 Code/phi_intervals.R

@@ -1,4 +1,5 @@
 source("functions.R")
+set.seed(1234)
 sim <- replicate(100, do1rep(800, 0.4, mystat, 10))
 new_sim <- sim[c(3, 6, 23, 24, 35, 36, 41, 42), ]
 
@@ -18,8 +19,10 @@ for (i in 1:3) {
   
   lines(x_values, bts_mean, col = 'red')
   # Add confidence intervals
-  for (j in 1:100) {
-    segments(x_values[j], lower_bound[j], x_values[j], upper_bound[j])
-  }
+  lines(x_values, lower_bound, col = "gray")
+  lines(x_values, upper_bound, col = "gray")
+  abline(h = 0.4, lty = "dotted")
+  legend("topright", legend = c("Point Estimate", "Bootstrap Mean", "Interval Bounds"),
+         col = c('blue', 'red', 'gray'), lty = c(1, 1, 1), bty = "n")
   dev.off()
 }

### 2023-05-30 Manuscript/manuscript.tex
5/30 Manuscript Update

@@
 methods to be less accurate than the Fisher's transformation method even 
-for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
+for a sample of size $n = 100$ and correlation coefficient equivalent to $0$.
 Few studies have provided a practical guide on what size is needed
@@
 
-\paragraph{Proposed Method CI}
-Our Proposed Method CI is centered at the point estimator and uses the
-variation
-in the bootstrap estimates to construct the error bound. This interval requires
-the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
-estimates, and $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$.
-A $(1 - \alpha)$ CI using our Proposed Method is
-\[
-(\hat\theta_{n, \alpha/2}^{(b)} - \hat{bias}, \quad
-\hat\theta_{n, 1 - \alpha/2}^{(b)} - \hat{bias}).
-\]
-This CI is necessarily centered around .... and
-is asymmetric, as different critical values are used to compute
-the lower and upper bounds.
-
 \paragraph{Bias Corrected Bootstrap CI}
@@
 
+\paragraph{Proposed Method CI}
+Our Proposed Method CI is centered at the point estimator and uses the
+variation
+in the bootstrap estimates to construct the error bound. This interval requires
+the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
+estimates, and $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$.
+A $(1 - \alpha)$ CI using our Proposed Method is
+\[
+(\hat\theta_{n, \alpha/2}^{(b)} - \hat{bias}, \quad
+\hat\theta_{n, 1 - \alpha/2}^{(b)} - \hat{bias}).
+\]
+This CI is necessarily centered around .... and
+is asymmetric, as different critical values are used to compute
+the lower and upper bounds.
+
 \section{Simulation Study}
@@
 bootstrap CI methods. In particular, we generated time series $X_t$
-from a 1st order auto-regressive (AR1) process:
+from a 1st order auto-regressive (AR(1)) process:
 \[
@@
 
+These results beg the question of why certain methods perform poorly. To address this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed methods were constructed.
+
 \begin{figure}[tbp]
@@
   \includegraphics[width=\textwidth]{figures/pct}
-  \caption{}
+  \caption{100 replicate Percentile Bootstrap CIs for samples of $n = 800$ for
+  an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$. }
   \label{fig:pct}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/prop}
-  \caption{}
-  \label{fig:prop}
+  \includegraphics[width=\textwidth]{figures/bc}
+  \caption{100 replicate Bias-Corrected Bootstrap CIs for samples of $n = 800$ for
+  an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
+  \label{fig:bc}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/bc}
-  \caption{}
-  \label{fig:bc}
+  \includegraphics[width=\textwidth]{figures/prop}
+  \caption{100 replicate Proposed Method CIs for samples of $n = 800$ for
+  an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
+  \label{fig:prop}
 \end{figure}
+
+As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias; specifically, they seem to heavily underestimate $\phi$.
+As shown in Figure~\ref{fig:bc, $BC$ CIs do seem to correct this bias on average, but the width of the
+CIs is very inconsistent. From Figure~\ref{fig:prop, we can see that 
+$prop$ CIs correct the bias using $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$, which seems to usually be negative, indicating a positive correction from
+interval construction in \ref{sec:bbci}.
 
@@
 the width of the CI decreases, but because the Percentile CI
-underestimates $\phi$, the coverage decreases. The $BC_a$ CI does seem to correct the bias, but the acceleration factor seems to fail, as the width of the CI
+underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct the bias, but the width of the CI seems to be inconsistent. The acceleration 
+factor of the $BC_a$ CI seems to fail, as the width of the CI
 seems to be inconsistent.

### 2023-05-31 Manuscript/manuscript.tex
fixed missing curly braces for figure references

@@
 As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias; specifically, they seem to heavily underestimate $\phi$.
-As shown in Figure~\ref{fig:bc, $BC$ CIs do seem to correct this bias on average, but the width of the
-CIs is very inconsistent. From Figure~\ref{fig:prop, we can see that 
+As shown in Figure~\ref{fig:bc}, $BC$ CIs do seem to correct this bias on average, but the width of the
+CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that 
 $prop$ CIs correct the bias using $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$, which seems to usually be negative, indicating a positive correction from
-interval construction in \ref{sec:bbci}.
+interval construction in Section~\ref{sec:bbci}.
 

### 2023-05-31 Manuscript/manuscript.tex
Update

@@
 parameter like the mean, and that the selection of interval type is very
-important, especially in the case of $\phi$, for which the coverage deteriorates
-as the sample size increases.
+important, especially in the case of the lag-1 autocorrelation, for which the coverage
+deteriorates as the sample size increases when using Percentile, 
+%Centered Bootstrap Percentile,
+Bias-Corrected, or Bias-Corrected and Accelerated Bootstrap intervals.
+
 \jy{put most
@@
 are more accurate than $t$-intervals for larger sample sizes, they are
-less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds that the the best choice of method for estimating
+less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds that the
+the best choice of method for estimating
 the parameter of a distribution is dependent on the sample size, the number of
@@
 sample
-size for bootstrap is even less clear. In the setting of linear regression and focused on estimating the proportion of 
+size for bootstrap is even less clear. In the setting of linear regression with a
+focus on estimating the proportion of 
 variation attributable to a certain variable, \citet{burch2012nonparametric} finds
-that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected and
+that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected
+and
 Accelerated) approach the coverage of a pivotal quantity as $n$ gets larger for an
@@
 methods to be less accurate than the Fisher's transformation method even 
-for a sample of size $n = 100$ and correlation coefficient equivalent to $0$.
+for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
 Few studies have provided a practical guide on what size is needed
@@
 interests are the mean, standard deviation, and the first-order
-autocorrelation coefficient. We compare five variants of block bootstrap
+autocorrelation coefficient. We compare six variants of block bootstrap
 CIs from the literature \citep{diciccio1996bootstrap,
-  rice2006mathematical}: a basic percentile interval, a percentile
-interval centered around the estimate, a bias-corrected and
-accelerated ($BC_a$) interval, a standard normal interval, and a Student's $t$
-interval. Their
+  rice2006mathematical}: a Standard Normal CI, and a Student's $t$ CI, a Percentile
+Interval CI, 
+%a Centered Bootstrap Percentile Interval, 
+a Bias-Corrected CI, a Bias-Correct and Accelerated($BC_a$) CI, and a CI using a new
+Proposed Method. Their
 empirical coverage rates at different sample sizes and dependence levels are
@@
 
-\paragraph{Centered Bootstrap Percentile CI}
-The procedure for constructing a Centered Bootstrap Percentile CI based on standard bootstrap is
-described in \citet{singh2008bootstrap}.
-The $(1 - \alpha)$ Centered Bootstrap Percentile CI is
-\[
-(2\hat{\theta}_{n} - \hat\theta_{n, 1 - \alpha/2}^{(b)}, \quad
-2\hat{\theta}_{n} - \hat\theta_{n, \alpha/2}^{(b)})).
-\]
-This CI is necessarily centered around the point estimator $\hat\theta_n$ and
-is asymmetric, as different critical values are used to compute
-the lower and upper bounds.
+%\paragraph{Centered Bootstrap Percentile CI}
+%The procedure for constructing a Centered Bootstrap Percentile CI based on
+%standard
+%bootstrap is
+%described in \citet{singh2008bootstrap}.
+%The $(1 - \alpha)$ Centered Bootstrap Percentile CI is
+%\[
+%(2\hat{\theta}_{n} - \hat\theta_{n, 1 - \alpha/2}^{(b)}, \quad
+%2\hat{\theta}_{n} - \hat\theta_{n, \alpha/2}^{(b)})).
+%\]
+%This CI is necessarily centered around the point estimator $\hat\theta_n$ and
+%is asymmetric, as different critical values are used to compute
+%the lower and upper bounds.
 
 \paragraph{Bias Corrected Bootstrap CI}
-The procedure for constructing a Bias Corrected Bootstrap CI based on standard bootstrap is
+The procedure for constructing a Bias Corrected Bootstrap CI based on standard
+bootstrap is
 described in \citet{carpenter2000bootstrap}.
@@
 \[
-\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} - \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} - \hat{\theta}_{(i)})^2\}^{3/2}}
+\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
+  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
+  \hat{\theta}_{(i)})^2\}^{3/2}}
 .\] For a $1 - \alpha$ CI, let
@@
 the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
-estimates, and $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$.
+estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
 A $(1 - \alpha)$ CI using our Proposed Method is
 \[
-(\hat\theta_{n, \alpha/2}^{(b)} - \hat{bias}, \quad
-\hat\theta_{n, 1 - \alpha/2}^{(b)} - \hat{bias}).
+(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
+\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
 \]
@@
 $BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
-Standard, Percentile, CBP, Proposed Method, and $BC$ CIs seem to 
+Standard, Percentile, %CBP, 
+Proposed Method, and $BC$ CIs seem to 
 generally cover $\mu$ at the nominal 
@@
 sample is independently normally distributed, $n = 1600$ seems to 
-be enough to recover $\mu$ when using Standard, Percentile, CBP, Proposed Method, or $BC$ 
+be enough to recover $\mu$ when using Standard, Percentile, 
+%CBP, 
+Proposed Method, or $BC$ 
 CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
@@
 comfortable coverage of $\sigma$ at the nominal level appears to only be true
-for Student's $t$ CIs for $n \geq 3200$, although Standard and CBP CIs.
-For $\phi = 0.4$, a much larger sample size appears to be necessary.
-Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.
+for Student's $t$ CIs for $n \geq 3200$, although Standard %and CBP% 
+CIs do reach the nominal level in our simulation results. For $\phi = 0.4$, a much
+larger sample size appears to be necessary. Student's $t$ CIs are the closest to
+$95\%$ coverage, and $BC_a$ CIs are the furthest.
 
 Based on Figure~\ref{fig:phi}, 
-Percentile, CBP, $BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
+Percentile, %CBP, %
+$BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
 so they should not be used. The deterioration becomes more evident
@@
 $n = 1600$, 
-although they undercover $\phi$ at $n = 3600$, indicating that 
+although they undercover $\phi$ at $n = 3200$, indicating that 
 perhaps a larger $n$ is needed if these CIs are uses. However,
@@
 
-These results beg the question of why certain methods perform poorly. To address this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed methods were constructed.
+These results beg the question of why certain methods perform poorly. To address this
+question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed methods
+were constructed.
 
@@
   \caption{100 replicate Percentile Bootstrap CIs for samples of $n = 800$ for
-  an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$. }
+    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
+    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$. }
   \label{fig:pct}
@@
   \caption{100 replicate Bias-Corrected Bootstrap CIs for samples of $n = 800$ for
-  an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
+    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
+    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
   \label{fig:bc}
@@
   \caption{100 replicate Proposed Method CIs for samples of $n = 800$ for
-  an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
+    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
+    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
   \label{fig:prop}
@@
 
-As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias; specifically, they seem to heavily underestimate $\phi$.
-As shown in Figure~\ref{fig:bc}, $BC$ CIs do seem to correct this bias on average, but the width of the
+As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias;
+specifically, they seem to heavily underestimate $\phi$. As shown in
+Figure~\ref{fig:bc}, $BC$ CIs do seem to correct this bias on average, but the width of
+  the 
 CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that 
-$prop$ CIs correct the bias using $\hat{bias} = \bar\theta_n^{(b)} - \hat\theta_n$, which seems to usually be negative, indicating a positive correction from
-interval construction in Section~\ref{sec:bbci}.
+  $prop$ CIs correct the bias using $\widehat{\text{bias}} = \bar\theta_n^{(b)} -
+  \hat\theta_n$, which seems to usually be negative, indicating a positive correction
+  from
+interval construction in \ref{sec:bbci}.
 
@@
 estimating $\phi$ only for Standard, Student's $t$, and Proposed Method CIs, whereas 
-Percentile, CBP, $BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
+Percentile, 
+%CBP, 
+$BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
 increased. The Percentile CI's coverage deterioration can be attributed to
@@
 the width of the CI decreases, but because the Percentile CI
-underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct the bias, but the width of the CI seems to be inconsistent. The acceleration 
+underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct the bias,
+but the width of the CI seems to be inconsistent. The acceleration 
 factor of the $BC_a$ CI seems to fail, as the width of the CI
@@
 
-When using Student's $t$ centered intervals and $\phi$ is
+When using Student's $t$ intervals and $\phi$ is
 unknown, the results of this study suggest that an $n > 3200$ may be

### 2023-05-31 Code/functions.R

@@ -1,4 +1,5 @@
 .libPaths("~/rlibs")
+library(ggplot2) # put package loading outside of the function
 ## This note checks the empirical coverage rate of CIs constructed from
 ## block bootstrap with series generated from an AR process
 
@@ -26,7 +27,6 @@ do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
   bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
   alpha <- 1 - level
   
-  
   ## Standard interval
   se <- apply(bts$t, 2, sd)
   stdCI <- sapply(1:length(bts$t0),
@@ -37,6 +37,7 @@ do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
   stuCI <- sapply(1:length(bts$t0),
                   function(i) c(bts$t0[i] - qt(1-alpha/2, n/blksize)*se[i], 
                                 bts$t0[i] - qt(alpha/2, n/blksize)*se[i]))
+  
   ## Percentile interval
   pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))
   
@@ -46,12 +47,7 @@ do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
   mbts <- apply(bts$t, 2, mean)
   ctrCI <- -sweep(crit, 2, bts$t0, FUN = '-')
   
-  ## Our Centered interval
-  crit2 <- 
-    apply(t(t(bts$t) - mbts), 2, quantile, prob = c(alpha/2, 1 - alpha/2)) 
-  ourctrCI <- sweep(crit2, 2, bts$t0, FUN = '+') # original estimate
-  
-  ## Carpenter et al 2000, p. 1153
+  ## Bias-Corrected interval (Carpenter et al 2000, p. 1153)
   b <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
   qup <- pnorm(2 * b - qnorm(alpha / 2))
   qlo <- pnorm(2 * b - qnorm(1 - alpha / 2))
@@ -97,11 +93,13 @@ do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
   ## LB: bts$t0 - alpha2 crit3, UB: bts$t0 - alpha1 crit3 and
   ## LB: mbts - alpha2 crit4, UB: mbts - alpha1 crit4
   
-  
[…]

### 2023-05-31 Code/local_processing.R

@@ -9,7 +9,7 @@ for(i in names(local_results)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
   cov <- mychk(local_results[[i]], c(0, 1, phi))
-  types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'ourctrCI', 'bcCI', 'bcaCI')
+  types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'bcCI', 'bcaCI', 'propCI')
   CI <- rep(types, each = length(cov) / length(types))
   parameters <- c('mu', 'sigma', 'phi')
   target <- rep(parameters, length(cov) / length(parameters))

### 2023-05-31 Code/processing.R

@@ -17,7 +17,7 @@ for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
   cov <- mychk(combined_matrices[[i]], c(0, 1, phi))
-  types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'ourctrCI', 'bcCI', 'bcaCI')
+  types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'bcCI', 'bcaCI', 'propCI')
   CI <- rep(types, each = length(cov) / length(types))
   parameters <- c('mu', 'sigma', 'phi')
   target <- rep(parameters, length(cov) / length(parameters))

### 2023-06-01 Manuscript/manuscript.tex
minor; removed resolved

@@
 independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
-that while percentile-based CIs from nonparametric bootstrap
+that while percentile-based CIs \eds{for the mean? differences in means?} from 
+nonparametric bootstrap
 are more accurate than $t$-intervals for larger sample sizes, they are
-less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds that the
-the best choice of method for estimating
+less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
+that the best choice of method for estimating
 the parameter of a distribution is dependent on the sample size, the number of
@@
 copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$.
-A $(1 - \alpha)$ standard normal CI is
+A $(1 - \alpha)100\%$ standard normal CI is
 \[
@@
 \]
+\eds{define $z_{(.)}$ and check the signs}
 This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
@@
   citing a book}
-With block bootstrapping, a $(1 - \alpha)$ Student's $t$ CI is
+With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
 \[
@@
 \]
+\eds{define $t_{(.)}$ and check the signs}
 where $k$ is the number of blocks.
@@
 Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
-$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
+$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)100\%$
 empirical percentile CI is
@@
 
-\paragraph{Bias Corrected Bootstrap CI}
+\paragraph{Bias Corrected ($BC$) Bootstrap CI}
 The procedure for constructing a Bias Corrected Bootstrap CI based on standard
@@
 for $b \in \{1, \ldots, B\}$. 
-For a $1 - \alpha$ CI, let
+For a $(1 - \alpha)100\%$ CI, let
 \[
@@
 \]
-A $(1 - \alpha) BC_a$ CI is
+A $(1 - \alpha)100\%~BC$ CI is
 \[
@@
 The $BC_a$ CI was first suggested in \citet{efron1987better}.
-\eds{a different abbrevation/notation was used for this in the introduction}
-\mc{used $BC_a$}
 \jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
@@
   \hat{\theta}_{(i)})^2\}^{3/2}}
-.\] For a $1 - \alpha$ CI, let
+.\] For a $(1 - \alpha)100\%$ CI, let
 \[
-\alpha_1 = \Phi(z_0 + \frac{z_{0} +
-  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}).
+\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
+  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right).
 \]
 \[
-\alpha_2 = \Phi(z_0 + \frac{z_{0} +
-  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}).
+\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
+  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
 \]
-\eds{notation will need to be cleaned and clarified}
-A $(1 - \alpha) BC_a$ CI is
+A $(1 - \alpha)100\%~BC_a$ CI is
 \[
@@
 estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
-A $(1 - \alpha)$ CI using our Proposed Method is
+A $(1 - \alpha)100\%$ CI using our Proposed Method is
 \[
@@
 To investigate the effect of sample size~$n$, we considered an array of values
-$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 10000
-replicates. For each replicate, we constructed three 95\% block bootstrap
+$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
+10000 replicates. For each replicate, we constructed seven 95\% block bootstrap
 CIs for each parameter as described in the last section. We can estimate 
@@
 and lag-1 auto-correlation, respectively, of each bootstrap sample, and then 
-constructing intervals for each parameter using the appropriate procedures
-described in Section~\ref{sec:bbci} .
+construct intervals for each parameter using the appropriate procedures
+described in Section~\ref{sec:bbci}.
 Then we estimated their actual coverage rates along with their 95\% confidence
@@
 that blocks are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.
-
-\eds{Is $l = \lceil n^{1/3} \rceil$? Is it also worth investigating different 
-choices of $l$ for fixed (large) $n$?}
-\mc{Addressed in the Block Bootstrap Sample subsection}
-\eds{how did you estimate $\mu$, $\sigma_x$ and $\phi$?}
-\mc{addressed}
 
@@
 for $r \in \{1, \ldots, R\}$.
-\eds{this notation is a bit sloppy, as it implies $n_{CI}$ changes for each 
-value of $CI$; consider using a summation of indicators with a different index}
-\mc{replaced $CI$ with $r$, and $n_{CI}$ with $R$}
 If a CI method is valid, then the coverage rate is expected to match the
@@
 we can construct a 95\% CI of the coverage
-rate (which is an estimate of a proportion with $n = 10000$). If the proportion
+rate (which is an estimate of a proportion with $n = 10000$ \eds{R?}). If the
+proportion
 0.95 is included in the interval, the block bootstrap method is likely
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma$ of an AR(1) process with AR
+    the marginal standard deviation $\sigma_x$ of an AR(1) 
+		process with AR
     coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
@@
 Based on Figure~\ref{fig:mu}, 
-Student's $t$ CIs appear to have the greatest coverage rates with respect 
-to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover $\mu$
-for all sample sizes, whereas other CIs have coverage rates that
+Student's $t$ CIs appear to have the greatest \eds{largest?} coverage rates with 
+respect 
+to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
+$\mu$ for all sample sizes, whereas other CIs have coverage rates that
 hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
@@
 For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
-Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.
+Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the 
+furthest.
 
@@
 $BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
-$\phi$, observed, although
-there is no trend of coverage deterioration, indicating that there may eventually
+$\phi$ observed, although there is no trend of coverage deterioration, 
+indicating that there may eventually
 be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
-For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma$ when 
-$n = 1600$, but undercover $\sigma$ for $n = 3200$, indicating
-that a larger $n$ is most likely necessary to consistently cover $\sigma$ at the 
-nominal rate.
-The other CI types undercover $\sigma$ for all sample sizes at $\phi = 0.4$.
-For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma$ at the 
-nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
+For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma_x$ when 
+$n = 1600$, but undercover $\sigma_x$ for $n = 3200$, indicating
+that a larger $n$ is most likely necessary to consistently cover $\sigma_x$ at 
+the nominal rate.
+The other CI types undercover $\sigma_x$ for all sample sizes at $\phi = 0.4$.
+For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma_x$ at 
+the nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
 nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
@@
 for other CIs. For $\phi = 0.2$, 
-comfortable coverage of $\sigma$ at the nominal level appears to only be true
+comfortable coverage of $\sigma_x$ at the nominal level appears to only be true
 for Student's $t$ CIs for $n \geq 3200$, although Standard %and CBP% 
@@
 although they undercover $\phi$ at $n = 3200$, indicating that 
-perhaps a larger $n$ is needed if these CIs are uses. However,
+perhaps a larger $n$ is needed if these CIs are used. However,
 Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
-$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively comfortably 
-at $n = 3200$, and 
+$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively 
+comfortably at $n = 3200$, and 
 $n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
@@
 necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
-a lesser sample size may be sufficient. When estimating $\sigma$,
-$BC_a$ should not be used, and Student's $t$ again has the greatest coverage
+a lesser sample size may be sufficient. When estimating $\sigma_x$,
+$BC_a$ should not be used, and Student's $t$ again has the greatest 
+\eds{highest?} coverage
 rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
 $n > 3200$ may be necessary for block bootstrap interval estimation of
-$\sigma$. Again, if $\phi$ is known, a lesser sample size may be enough.
+$\sigma_x$. Again, if $\phi$ is known, a lesser sample size may be enough.
 When estimating $\phi$, Percentile and $BC_a$ CIs 
@@
 
-These results beg the question of why certain methods perform poorly. To address this
-question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed methods
-were constructed.
+These results beg the question of why certain methods perform poorly. To address 
+this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed 
+methods were constructed.
 
@@
   the 
-CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that 
-  $prop$ CIs correct the bias using $\widehat{\text{bias}} = \bar\theta_n^{(b)} -
-  \hat\theta_n$, which seems to usually be negative, indicating a positive correction
-  from
-interval construction in \ref{sec:bbci}.
+CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that the 
+Proposed Method CIs correct the bias using 
+$\widehat{\text{bias}} = \bar\theta_n^{(b)} -
+  \hat\theta_n$, which seems to usually be negative, indicating a positive 
+	correction from interval construction in Section~\ref{sec:bbci}.
 
@@
  We know theoretically that the block bootstrap procedure will cover
- \eds{? interval will correctly cover?  What does the theory  actually say?}
- \mc{addressed} a
   parameter of a time series at the nominal level given an
@@
 
-Again, this analysis \eds{what?} \mc{addressed} relies on the assumption that
+Again, this analysis relies on the assumption that
 there is a size $n$ large enough for the method to work: that is, the method's
@@
 in this study, this assumption was found to hold true with respect to
-estimating $\phi$ only for Standard, Student's $t$, and Proposed Method CIs, whereas 
-Percentile, 
+estimating $\phi$ only for Standard, Student's $t$, and Proposed Method CIs, 
+whereas Percentile, 
 %CBP, 
@@
 the width of the CI decreases, but because the Percentile CI
-underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct the bias,
-but the width of the CI seems to be inconsistent. The acceleration 
+underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct the 
+bias, but the width of the CI seems to be inconsistent. The acceleration 
 factor of the $BC_a$ CI seems to fail, as the width of the CI

### 2023-06-07 Manuscript/manuscript.tex
Faceted Interval Plots

@@
   \centering
-  \includegraphics[width=\textwidth]{figures/pct}
-  \caption{100 replicate Percentile Bootstrap CIs for samples of $n = 800$ for
+  \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
+  \caption{100 replicate Percentile, Bias-Corrected, and Proposed Method Bootstrap CIs for samples of $n = 800$ for
     an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
     of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$. }
-  \label{fig:pct}
+  \label{fig:npi}
 \end{figure}
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/bc}
-  \caption{100 replicate Bias-Corrected Bootstrap CIs for samples of $n = 800$ for
-    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
-    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
-  \label{fig:bc}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/prop}
-  \caption{100 replicate Proposed Method CIs for samples of $n = 800$ for
-    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
-    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
-  \label{fig:prop}
-\end{figure}
-
-As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias;
-specifically, they seem to heavily underestimate $\phi$. As shown in
-Figure~\ref{fig:bc}, $BC$ CIs do seem to correct this bias on average, but the width of
+As shown in Figure~\ref{fig:npi}, Percentile CIs appear to suffer from bias;
+specifically, they seem to heavily underestimate $\phi$. $BC$ CIs do seem to correct this bias on average, but the width of
   the 
-CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that the 
+CIs is very inconsistent. We can see that the 
 Proposed Method CIs correct the bias using 

### 2023-06-07 Code/phi_intervals.R

@@ -1,28 +1,32 @@
 source("functions.R")
+library(ggplot2)
+
 set.seed(1234)
-sim <- replicate(100, do1rep(800, 0.4, mystat, 10))
-new_sim <- sim[c(3, 6, 23, 24, 35, 36, 41, 42), ]
+sim <- replicate(50, do1rep(800, 0.4, mystat, 10))
+new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
 
-file_titles <- c("pct", "prop", "bc")
+file_titles <- c("pct", "bc", "prop")
+custom_titles <- c("Percentile", "Bias-Corrected", "Proposed")
 
-for (i in 1:3) {
-  pdf(paste('../Manuscript/figures/', file_titles[i], '.pdf', sep = ''))
-  lower_bound <- new_sim[(2 * i + 1), ]
-  upper_bound <- new_sim[(2 * i + 2), ]
-  point_estimate <- new_sim[1, ]
-  bts_mean <- new_sim[2, ]
-  
-  x_values <- 1:100
-  
-  plot(x_values, point_estimate, type = 'l', ylim = range(lower_bound, upper_bound),
-       xlab = 'Replication', ylab = 'Value', main = '', col = 'blue')
-  
-  lines(x_values, bts_mean, col = 'red')
-  # Add confidence intervals
-  lines(x_values, lower_bound, col = "gray")
-  lines(x_values, upper_bound, col = "gray")
-  abline(h = 0.4, lty = "dotted")
-  legend("topright", legend = c("Point Estimate", "Bootstrap Mean", "Interval Bounds"),
-         col = c('blue', 'red', 'gray'), lty = c(1, 1, 1), bty = "n")
-  dev.off()
-}
+# Create a data frame for plotting
+plot_data <- data.frame(replication = 1:50,
+                        point_estimate = new_sim[1, ],
+                        bts_mean = new_sim[2, ],
+                        lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
+                        upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
+                        file_title = rep(file_titles, each = 50),
+                        custom_title = rep(custom_titles, each = 50))
+
+# Create facet plot using ggplot2
+ggplot(plot_data, aes(x = replication, y = point_estimate)) +
[…]

### 2023-06-07 Manuscript/manuscript.tex
Small Manuscript Update

@@
 The procedure for constructing a Student's $t$ CI based on standard bootstrap is
-described in \citet{efron1993introduction}. \jy{give page or section number when
-  citing a book}
+described in \citet[p.158]{efron1993introduction}. \jy{give page or section number when
+  citing a book} \mc{addressed}
 With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
@@
 \]
-This CI is necessarily centered around .... and
-is asymmetric, as different critical values are used to compute
+This CI is necessarily centered around $\hat\theta_n$ and can also be rewritten
+as 
+\[
+(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
+\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
+\]
+and is asymmetric, as different critical values are used to compute
 the lower and upper bounds.
@@
 to generally understand how large of a sample size is sufficient for block
-bootstrap to be used versus other inference methods.
+bootstrap to be used versus other inference methods. For undergraduate or
+graduate students, block bootstrap is not typically a part of curriculum, but the 
+results of this study can easily be used to demonstrate when it is practical to use 
+this method.
 This information could also prove to be useful for research using block

### 2023-08-11 Manuscript/manuscript.tex
Addressed Some Comments Still Need to Look over Everything

@@
 independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
-that while percentile-based CIs \eds{for the mean? differences in means?} from 
+that while percentile-based CIs for the mean \eds{for the mean? differences in means?} \mc{addressed} from 
 nonparametric bootstrap
@@
 Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
-copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$.
+copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the critical value for the $100\alpha$th percentile of the standard normal distribution.
 A $(1 - \alpha)100\%$ standard normal CI is
@@
 \]
-\eds{define $z_{(.)}$ and check the signs}
+\eds{define $z_{(.)}$ and check the signs} \mc{addressed}
 This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
@@
 described in \citet[p.158]{efron1993introduction}. \jy{give page or section number when
-  citing a book} \mc{addressed}
+  citing a book} \mc{addressed} Let $t_{(\alpha, k)}$ be the critical value for the $100\alpha$th percentile of the student's $t$ distribution with $k$ degrees of freedom.
 With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
@@
 \]
-\eds{define $t_{(.)}$ and check the signs}
+\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
 where $k$ is the number of blocks.
@@
 we can construct a 95\% CI of the coverage
-rate (which is an estimate of a proportion with $n = 10000$ \eds{R?}). If the
+rate (which is an estimate of a proportion with $R = 10000$ \eds{R?} \mc{addressed}). If the
 proportion
@@
 Based on Figure~\ref{fig:mu}, 
-Student's $t$ CIs appear to have the greatest \eds{largest?} coverage rates with 
+Student's $t$ CIs appear to have the highest \eds{largest?} \mc{addressed} coverage rates with 
 respect 
@@
 a lesser sample size may be sufficient. When estimating $\sigma_x$,
-$BC_a$ should not be used, and Student's $t$ again has the greatest 
-\eds{highest?} coverage
+$BC_a$ should not be used, and Student's $t$ again has the highest
+\eds{highest?} \mc{addressed} coverage
 rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
@@
     an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
-    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$. }
+    of the CIs are displayed, as well as $\hat\theta_n$ (blue) and $\bar\theta_n^{(b)}$ (red). }
   \label{fig:npi}

### 2023-08-11 Code/phi_intervals.R

@@ -20,8 +20,8 @@ plot_data <- data.frame(replication = 1:50,
 # Create facet plot using ggplot2
 ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound), width = 0.5, color = 'gray') +
-  geom_line(color = 'blue') +
-  geom_line(aes(y = bts_mean), color = 'red') +
+  geom_point(color = 'blue') +
+  geom_point(aes(y = bts_mean), color = 'red') +
   geom_hline(yintercept = 0.4, linetype = "dotted") +
   facet_wrap(~ custom_title, ncol = 1) +
   labs(x = 'Replication', y = 'Value') +

### 2023-08-14 Manuscript/manuscript.tex
Small Change

@@
 Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
-copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the critical value for the $100\alpha$th percentile of the standard normal distribution.
+copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the $100\alpha$th percentile of the standard normal distribution.
 A $(1 - \alpha)100\%$ standard normal CI is
@@
 described in \citet[p.158]{efron1993introduction}. \jy{give page or section number when
-  citing a book} \mc{addressed} Let $t_{(\alpha, k)}$ be the critical value for the $100\alpha$th percentile of the student's $t$ distribution with $k$ degrees of freedom.
+  citing a book} \mc{addressed} Let $t_{(\alpha, k)}$ be the $100\alpha$th percentile of the student's $t$ distribution with $k$ degrees of freedom.
 With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_mu}
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_sigma}
+  \includegraphics[width=\textwidth]{figures/plot_norm_sigma}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_phi}
+  \includegraphics[width=\textwidth]{figures/plot_norm_phi}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for

### 2023-08-17 Manuscript/manuscript.tex
Small Change
cleaning and edits

@@
 rates of several commonly used bootstrap confidence intervals for the mean,
-standard deviation, and the lag-1 autocorrelation are compared. In this 
-study, we find that a large sample is needed to recover even a simple
-parameter like the mean, and that the selection of interval type is very
-important, especially in the case of the lag-1 autocorrelation, for which the coverage
-deteriorates as the sample size increases when using Percentile, 
-%Centered Bootstrap Percentile,
-Bias-Corrected, or Bias-Corrected and Accelerated Bootstrap intervals.
-
-\jy{put most
-  notable findings here. Possibly 1) large sample is needed; percentile
-  bootstrap is not working well for rho (can we offer some explanation?).}
+standard deviation, and the lag-1 autocorrelation coefficient are compared.
+A quite large sample is found necessary for the intervals to have the right
+coverage rates even when estimaiting a simple parameter like the mean. Some
+block bootstrap methods could fail when estimating the lag-1 autocorrelation.
+It is surprising that the coverage property even deteriorates as the sample size
+increases with some commonly used block bootstrap confidence intervals including
+the percentile intervals and Bias-Corrected intervals.
 
@@
 
-The necessary sample size for bootstrap standard errors to provide valid
-uncertainty measures in practice has not been extensively studied. For
-independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
-that while percentile-based CIs for the mean \eds{for the mean? differences in means?} \mc{addressed} from 
-nonparametric bootstrap
+\jy{too wordy; do some condensing}
+The performance of bootstrap standard errors with independent data
+in providing valid uncertainty measures has been extensively studied.
+For example, for non-block bootstrap, \citet{hesterberg2015teachers} notes
+that while percentile-based CIs for the mean from nonparametric bootstrap
 are more accurate than $t$-intervals for larger sample sizes, they are
@@
 the parameter of a distribution is dependent on the sample size, the number of
-bootstrap resamples, and the confidence level. In the context of structural equation
-modeling, \citet{nevitt2001performance} find
+bootstrap resamples, and the confidence level. In the context of structural
+equation modeling, \citet{nevitt2001performance} find
 that a sample size of 200--1000 is usually sufficient for interval estimation
-using standard nonparametric bootstrap. For dependent data, the necessary
-sample
-size for bootstrap is even less clear. In the setting of linear regression with a
-focus on estimating the proportion of 
-variation attributable to a certain variable, \citet{burch2012nonparametric} finds
-that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected
-and
-Accelerated) approach the coverage of a pivotal quantity as $n$ gets larger for an
-underlying normal distribution. However, they find that for other distributions, 
-coverage may deteriorate as $n$ increases. 
+using standard nonparametric bootstrap. In estimating the proportion of 
+variation attributable to certain variable, \citet{burch2012nonparametric} finds
+that three nonparametric bootstrap methods (standard, percentile, and bias-corrected
+and accelerated) approach the coverage of a pivotal quantity as the sample size
+gets larger for an underlying normal distribution, but for other distributions, 
+coverage may deteriorate even as the sample size increases.
 When attempting to create interval estimations for the Pearson correlation 
@@
 methods to be less accurate than the Fisher's transformation method even 
-for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
+for a sample of size of 100 and the correlation coefficientis equivalent to 0.
+The general consensus is that a big sample size is necessary.
+
 Few studies have provided a practical guide on what size is needed
 for block bootstrap inference for dependent data.
-In a linear regression setting
-with
-dependent data where the
+In a linear regression setting with dependent data where the
 regression errors are generated from a homoscedastic AR(1) process, 
-\citet{goncalves2005bootstrap} find that standard error
-estimates from moving 
-block bootstrap in small samples may be more accurate than
-inference from closed-form asymptotic estimates, but moving block bootstrap 
-\jy{did they do block or standard bootstrap?}
-\mc{moving block bootstrap}
-CIs still do not have sufficient coverage of the target parameter even for sample size
-$n = 1024$.
-\jy{I added more references to the reference folder that studied coverage of
-  bootstrap CIs but not block bootstrap CIs.}
+\citet{goncalves2005bootstrap} find that the standard error estimates from
+moving block bootstrap in small samples may be more accurate than those
+from closed-form asymptotic estimates, but moving block bootstrap 
+CIs still do not have sufficient coverage of the target parameter even for
+sample size~$1024$.
 
@@
 CIs from the literature \citep{diciccio1996bootstrap,
-  rice2006mathematical}: a Standard Normal CI, and a Student's $t$ CI, a Percentile
-Interval CI, 
-%a Centered Bootstrap Percentile Interval, 
-a Bias-Corrected CI, a Bias-Correct and Accelerated($BC_a$) CI, and a CI using a new
-Proposed Method. Their
+  rice2006mathematical}: a standard normal CI, and a Student's $t$ CI,
+a percentile CI, a bias-corrected CI, a bias-correct and accelerated ($BC_a$)
+CI, and a CI proposed in this article. Their
 empirical coverage rates at different sample sizes and dependence levels are
@@
 Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
-bootstrap estimates to construct CIs. Section~\ref{sec:simu} reports a
+bootstrap estimates to construct CIs; a simple CI obtained by recentering at the
+point estimate is proposed for comparison. Section~\ref{sec:simu} reports a
 simulation
-study comparing the coverage rates of the block bootstrap CIs. A discussion
+study comparing the coverage rates of six???block bootstrap CIs. A discussion
 concludes in Section~\ref{sec:disc}.
@@
 \label{sec:bbci}
+
+\jy{Practice my writing style guidelines. Use two blank lines to separate
+  paragraphs.}
 
@@
 This version does not require that $n/l$ be an integer.
-We used this version in this study as implemented in the function
-\texttt{tsboot} from R package \textsl{boot} \citep{boot}.
 
@@
 
-\jy{Read carpenter2000bootstrap and cite it; quite useful in sorting the literature}
-
 \paragraph{Standard Normal CI}
@@
 Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
-copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the $100\alpha$th percentile of the standard normal distribution.
+copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the
+upper $\alpha$ quantile of the standard normal distribution.
 A $(1 - \alpha)100\%$ standard normal CI is
@@
 \]
-\eds{define $z_{(.)}$ and check the signs} \mc{addressed}
 This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
@@
 The procedure for constructing a Student's $t$ CI based on standard bootstrap is
-described in \citet[p.158]{efron1993introduction}. \jy{give page or section number when
-  citing a book} \mc{addressed} Let $t_{(\alpha, k)}$ be the $100\alpha$th percentile of the student's $t$ distribution with $k$ degrees of freedom.
+described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the
+upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom.
 With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
@@
 
-%\paragraph{Centered Bootstrap Percentile CI}
-%The procedure for constructing a Centered Bootstrap Percentile CI based on
-%standard
-%bootstrap is
-%described in \citet{singh2008bootstrap}.
-%The $(1 - \alpha)$ Centered Bootstrap Percentile CI is
-%\[
-%(2\hat{\theta}_{n} - \hat\theta_{n, 1 - \alpha/2}^{(b)}, \quad
-%2\hat{\theta}_{n} - \hat\theta_{n, \alpha/2}^{(b)})).
-%\]
-%This CI is necessarily centered around the point estimator $\hat\theta_n$ and
-%is asymmetric, as different critical values are used to compute
-%the lower and upper bounds.
-
 \paragraph{Bias Corrected ($BC$) Bootstrap CI}
 The procedure for constructing a Bias Corrected Bootstrap CI based on standard
-bootstrap is
-described in \citet{carpenter2000bootstrap}.
+bootstrap is described in \citet{carpenter2000bootstrap}.
 Let $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
-for $b \in \{1, \ldots, B\}$. 
-For a $(1 - \alpha)100\%$ CI, let
-\[
-\alpha_1 = \Phi(2b - z_{\alpha/2}).
-\]
-\[
-\alpha_2 = \Phi(2b - z_{1 - \alpha/2}).
-\]
+for $b \in \{1, \ldots, B\}$. Define
+$\alpha_1 = \Phi(2b - z_{\alpha/2})$ and 
+$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$.
 A $(1 - \alpha)100\%~BC$ CI is
@@
 The $BC_a$ CI was first suggested in \citet{efron1987better}.
-\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
-  What is your reference for this description?}
 Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
@@
   \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
-  \hat{\theta}_{(i)})^2\}^{3/2}}
-.\] For a $(1 - \alpha)100\%$ CI, let
+  \hat{\theta}_{(i)})^2\}^{3/2}}.
+\]
+Define
 \[
 \alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
-  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right).
-\]
-\[
+  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right)
+\text{ and }
 \alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
@@
 bias-correction and acceleration factors. The acceleration factor refers to
-the 
-rate of change of of the standard error of $\hat\theta_n$ with respect to
-$\theta$.
+the rate of change of of the standard error of $\hat\theta_n$ with respect
+to~$\theta$.
 
-\paragraph{Proposed Method CI}
-Our Proposed Method CI is centered at the point estimator and uses the
-variation
+\paragraph{A Proposed CI}
+We propose a CI that is centered at the point estimator and uses the variation
 in the bootstrap estimates to construct the error bound. This interval requires
@@
 estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
-A $(1 - \alpha)100\%$ CI using our Proposed Method is
+A $(1 - \alpha)100\%$ CI is
 \[
@@
 \]
-This CI is necessarily centered around $\hat\theta_n$ and can also be rewritten
+This CI is centered around $\hat\theta_n$ and can also be rewritten
 as 
@@
 \]
-and is asymmetric, as different critical values are used to compute
+It is asymmetric, as different critical values are used to compute
 the lower and upper bounds.
+\jy{Double check}
 
@@
 
-\jy{Explain what metric was used to compare their performances. That is, the
-  coverage rates and how it was calculated. If a CI is valid, then the coverages
-  rate is expected to match its nominal level.}
-
-\jy{Make it flow better and conciser}
 The coverage rates of the CIs were used to compare the performance of CIs. Let
@@
 we can construct a 95\% CI of the coverage
-rate (which is an estimate of a proportion with $R = 10000$ \eds{R?} \mc{addressed}). If the
+rate (which is an estimate of a proportion with $R = 10000$. If the
 proportion
@@
 process' variability.
-
-If $\theta$ is not covered at that $n$, a larger $n$ may be
-necessary, assuming that performance will improve as $n$ is increased.
-Remember that
-the goal of this study is to find the smallest $n$ which is sufficient for
-proper coverage.
-
-The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
-these figures were generated using the R \textsl{ggplot2} package
-\citep{ggplot2}.
+Figures~\ref{fig:mu}--\ref{fig:phi} summarizes the empirical coverage rates and
+the 95\% confidence intervals of the real coverage, generated using the R
+\textsl{ggplot2} package \citep{ggplot2}.
 
@@
 
-\jy{I'm curiouss why the coverge is so poor for the percentile method. Could
-  plot 50 intervals for phi using different sample sizes?}
-
-Based on Figure~\ref{fig:mu}, 
-Student's $t$ CIs appear to have the highest \eds{largest?} \mc{addressed} coverage rates with 
-respect 
-to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
+For estimating~$\mu$,
+Student's $t$ CIs appear to have the highest coverage rates with respect 
+to estimating~$\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
 $\mu$ for all sample sizes, whereas other CIs have coverage rates that
@@
 
-These results beg the question of why certain methods perform poorly. To address 
-this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed 
-methods were constructed.
-
 \begin{figure}[tbp]
@@
 
-As shown in Figure~\ref{fig:npi}, Percentile CIs appear to suffer from bias;
-specifically, they seem to heavily underestimate $\phi$. $BC$ CIs do seem to correct this bias on average, but the width of
-  the 
-CIs is very inconsistent. We can see that the 
-Proposed Method CIs correct the bias using 
-$\widehat{\text{bias}} = \bar\theta_n^{(b)} -
-  \hat\theta_n$, which seems to usually be negative, indicating a positive 
+These results beg the question of why certain methods perform poorly. To address 
+this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed 
+methods were constructed. As shown in Figure~\ref{fig:npi}, Percentile CIs
+appear to suffer from bias; specifically, they seem to heavily underestimate
+$\phi$. $BC$ CIs do seem to correct this bias on average, but the width of the
+CIs is very inconsistent. Our proposed CIs correct the bias using 
+$\widehat{\text{bias}} = \bar\theta_n^{(b)} -  \hat\theta_n$,
+which seems to usually be negative, indicating a positive 
 correction from interval construction in Section~\ref{sec:bbci}.
@@
 
-\jy{Discussion points:
-  1) common practice on block bootstrap even for simple parameter such as the
-  mean;
-  2) further investigation needed for phi;
-  3) impact on applied statsitics courses; student reactions (Dr. Schifano).
-}
+\jy{Keep the tex source tidy. Clean it up.}
 

### 2023-08-19 Manuscript/manuscript.tex
Update

--- 2023-08-14 Manuscript/manuscript.tex
@@
 the 
-rate of change of of the standard error of $\hat\theta_n$ with respect to
+rate of change of the standard error of $\hat\theta_n$ with respect to
 $\theta$.
@@
 
-Based on Figure~\ref{fig:mu}, 
-Student's $t$ CIs appear to have the highest \eds{largest?} \mc{addressed} coverage rates with 
-respect 
-to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
-$\mu$ for all sample sizes, whereas other CIs have coverage rates that
-hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
-$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
-Standard, Percentile, %CBP, 
-Proposed Method, and $BC$ CIs seem to 
-generally cover $\mu$ at the nominal 
-rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
-for $n \geq 100$. For $\phi = 0$, or when the 
-sample is independently normally distributed, $n = 1600$ seems to 
-be enough to recover $\mu$ when using Standard, Percentile, 
-%CBP, 
-Proposed Method, or $BC$ 
-CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
-$\phi = 0$.
-For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
+Based on Figure~\ref{fig:mu}, Student's $t$ seems to generally
+be the best method for estimating $\mu$.
+For $\phi = -0.4$, Student's $t$ CIs over-cover 
+$\mu$ for smaller $n$, whereas other CIs recover $\mu$ at the
+nominal rate for all $n$ observed. For 
+$\phi = -0.2$, 
+all CIs recover $\mu$ at the nominal rate for all $n$. For $\phi = 0$, or when the 
+sample is independently normally distributed, $n \geq 200$ seems to 
+be large enough to recover $\mu$ at the nominal rate when using any CIs
+ besides Student's $t$ CIs, which seem to recover $\mu$ at the nominal rate for
+  all $n$.
+For $\phi = 0.2$, $n \geq 800$ seems to be sufficient to recover $\mu$
 at the nominal level when using
-any of the CIs, although some CIs, such as Student's $t$, are much closer to the
-$95\%$ line than others, most notably $BC_a$.
-For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
-Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the 
-furthest.
+any CIs besides Student's $t$ CIS, which recover $\mu$ at the nominal
+ rate for all $n \geq 200$.
+For $\phi = 0.4$, $n \geq 3200$ seems to be large enough to recover $\mu$
+at the nominal level when using
+any CIs besides Student's $t$ CIS, which seem to recover $\mu$ at the nominal
+ rate for all $n \geq 800$.
 
-Based on Figure~\ref{fig:sigma}, 
-$BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
-$\phi$ observed, although there is no trend of coverage deterioration, 
-indicating that there may eventually
-be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
-For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma_x$ when 
-$n = 1600$, but undercover $\sigma_x$ for $n = 3200$, indicating
-that a larger $n$ is most likely necessary to consistently cover $\sigma_x$ at 
-the nominal rate.
-The other CI types undercover $\sigma_x$ for all sample sizes at $\phi = 0.4$.
-For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma_x$ at 
-the nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
-nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
-be large enough if Standard CIs are used, and $n \geq 400$ is fine is
-Student's $t$ CIs are used. $n \geq 3200$ appears necessary 
-for other CIs. For $\phi = 0.2$, 
-comfortable coverage of $\sigma_x$ at the nominal level appears to only be true
-for Student's $t$ CIs for $n \geq 3200$, although Standard %and CBP% 
-CIs do reach the nominal level in our simulation results. For $\phi = 0.4$, a much
-larger sample size appears to be necessary. Student's $t$ CIs are the closest to
-$95\%$ coverage, and $BC_a$ CIs are the furthest.
+Based on Figure~\ref{fig:sigma}, Student's $t$ also seems to generally
+be the best method for estimating $\sigma$.
+for $\phi = -0.4$, $n \geq 1600$ is sufficient to recover $\sigma$
+at the nominal level when using
+any CIs besides Standard CIs, which seem to recover $\sigma$ at the nominal 
+rate for all $n \geq 800$, and Student's $t$ CIs, which seem to recover $\sigma$
+at the nominal rate for all $n \geq 400$. For $\phi = -0.2$, $n \geq 200$ is 
+adequate to recover $\sigma$ at the nominal rate with Student $t$ CIs, 
+but other CIs seem to require $n \geq 800$. For $\phi = 0$, or when the sample
+is independently normally distributed, $n \geq 400$ seems to be about enough
+to recover $\sigma$ for all CIs, but Student's $t$ CIs can recover $\sigma$ for
+$n \geq 100$. For $\phi = 0.2$, $n \geq 800$ is adequate for CIs besides the
+Student's $t$ CI, which recovers $\sigma$ well for $n \geq 200$. For 
+$\phi  = 0.4$, $n \geq 1600$ seems necessary for CIs other that Student's $t$ 
+CIs, which recover $\sigma$ at the nominal level for $n \geq 400$.
 
-Based on Figure~\ref{fig:phi}, 
-Percentile, %CBP, %
-$BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
-so they should not be used. The deterioration becomes more evident
-as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
-negative or positive. When $\phi = -0.4$, Standard and Proposed Method CIs 
-recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
-Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
-$\phi = -0.2$, Standard and Proposed Method CIs recover $\phi$ at $n = 800$ and 
-$n = 1600$, 
-although they undercover $\phi$ at $n = 3200$, indicating that 
-perhaps a larger $n$ is needed if these CIs are used. However,
-Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
-$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively 
-comfortably at $n = 3200$, and 
-$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
-and Proposed Method CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
-Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
-800$ is large enough for Standard and Proposed Method CIs. Student's $t$ CIs either
-recover or over-cover $\phi$ for all $n \geq 100$.
+Based on Figure~\ref{fig:phi}, Student's $t$ again seems to generally
+be the best method for estimating $\phi$. For high absolute values of $\phi$, 
+Percentile, $BC$, and $BC_a$ CIs
+deteriorate in coverage as $n$ increases. For $\phi = -0.4$, Standard, Student's
+$t$, and Proposed CIs recover $\phi$ for $n \geq 100$. For $\phi = -0.2$, 
+Standard and Proposed CIs recover $\phi$ at the nominal rate for $n \geq 200$, 
+whereas this can be done for $n \geq 100$ with Student's $t$ CIs. For $\phi = 
+0$, or when the sample
+is independently normally distributed, Standard and Proposed CIs recover 
+$\phi$ at the nominal level  for $n \geq 400$, and this is achievable for 
+$n \geq 100$ with Student's $t$ CIs. For $\phi = 0.2$ and $\phi = 0.4$, Standard 
+and Proposed CIs recover $\phi$ for $n \geq 200$, and Student's $t$ CIs 
+recover $\phi$ for all $n \geq 100$.
 
 To summarize, the CI type chosen should be based on the target parameter. 
-When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
-overall, although that leads to over-coverage when $\phi$ is -0.4. For a
-sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
-at the nominal rate even for small sample sizes. For positive $\phi$, a larger
-sample size appears to be necessary regardless of the CI used. In the case
-that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
-necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
+When estimating $\mu$, the Student's $t$ CI seems to have the highest
+ coverage
+overall, although that leads to over-coverage for small sample sizes when $\phi$
+ is -0.4. For a
+sample with no temporal dependence, the Student's $t$ CI recover $\mu$ 
+very close to the nominal rate even for small sample sizes. For positive $\phi$, a
+larger sample size appears to be necessary regardless of the CI used. In the
+case that $\phi$ is unknown and expected to be greater than $0$, $n > 800$
+may be
+necessary for block bootstrap interval estimation of $\mu$ when using the Student's $t$ CI. If $\phi$ is known,
 a lesser sample size may be sufficient. When estimating $\sigma_x$,
-$BC_a$ should not be used, and Student's $t$ again has the highest
-\eds{highest?} \mc{addressed} coverage
+Student's $t$ again has the highest coverage
 rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
-$n > 3200$ may be necessary for block bootstrap interval estimation of
-$\sigma_x$. Again, if $\phi$ is known, a lesser sample size may be enough.
-When estimating $\phi$, Percentile and $BC_a$ CIs 
+$n > 400$ may be necessary for block bootstrap interval estimation of
+$\sigma_x$ when using the Student's $t$ CI. Again, if $\phi$ is known, a lesser sample size may be enough.
+When estimating $\phi$, Percentile, $BC$, and $BC_a$ CIs 
 deteriorate in coverage, indicating they should not be used in this context. 
@@
 $\phi$ at the nominal rate for much smaller sample sizes. It seems that 
-$n = 800$ is large enough to
+$n = 100$ is certainly large enough to
 recover $\phi$ when using the Student's $t$ method.
@@
 When using Student's $t$ intervals and $\phi$ is
-unknown, the results of this study suggest that an $n > 3200$ may be
+unknown, the results of this study suggest that an $n \geq 800$ may be
 necessary for common practice to estimate simpler parameters like $\mu$ 
@@
 values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
-Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$, 
+Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$ when using smaller
+sample sizes, 
 meaning that if $\phi$ is known to have a very negative value, another CI
-should be used.
+may be required.
 However, in real world applications, $\phi$ is
@@
 if $\phi$ is unknown.
-Lastly, to estimate $\phi$, an $n$ of around $800$ using the 
+Lastly, to estimate $\phi$, $n \geq 100$ using the 
 Student's $t$ method

### 2023-08-19 Code/functions.R

@@ -124,8 +124,8 @@ mychk <- function(sim, target) {
 
 graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 {
-  data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'bcCI', 'bcaCI', 'propCI'), 
-                    labels = c('Standard', 'Student\'s t', 'Percentile', 'Centered', 'BC', 'BCA', 'Proposed'))
+  data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
+                    labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Proposed'))
   
   ggplot(data, aes(x = n, y = cov)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
@@ -136,5 +136,5 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
     scale_y_continuous(trans=trans)
-  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''))
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), height = 5)
 }

### 2023-08-19 Code/plots.R

@@ -1,7 +1,11 @@
+library(tidyverse)
 source("functions.R")
-norm_mu <- read.csv("../Data/norm_mu.csv")
-norm_sigma <- read.csv("../Data/norm_sigma.csv")
-norm_phi <- read.csv("../Data/norm_phi.csv")
+norm_mu <- read.csv("../Data/norm_mu.csv") %>% 
+  filter(CI != 'ctrCI')
+norm_sigma <- read.csv("../Data/norm_sigma.csv") %>% 
+  filter(CI != 'ctrCI')
+norm_phi <- read.csv("../Data/norm_phi.csv") %>% 
+  filter(CI != 'ctrCI')
 
 t <- 'norm_mu'
 width <- .2
@@ -16,9 +20,12 @@ width <- .2
 graph_bts(t, width, norm_phi)
 
 source("functions.R")
-exp_mu <- read.csv("../Data/exp_mu.csv")
-exp_sigma <- read.csv("../Data/exp_sigma.csv")
-exp_rho <- read.csv("../Data/exp_rho.csv")
+exp_mu <- read.csv("../Data/exp_mu.csv") %>% 
+  filter(CI != 'ctrCI')
+exp_sigma <- read.csv("../Data/exp_sigma.csv") %>% 
+  filter(CI != 'ctrCI')
+exp_rho <- read.csv("../Data/exp_rho.csv") %>% 
+  filter(CI != 'ctrCI')
 
 t <- 'exp_mu'
 width <- .2

### 2023-08-19 Manuscript/manuscript.tex
Small Format Changes

--- 2023-08-17 Manuscript/manuscript.tex
@@
 A quite large sample is found necessary for the intervals to have the right
-coverage rates even when estimaiting a simple parameter like the mean. Some
+coverage rates even when estimating a simple parameter like the mean. Some
 block bootstrap methods could fail when estimating the lag-1 autocorrelation.
 It is surprising that the coverage property even deteriorates as the sample size
-increases with some commonly used block bootstrap confidence intervals including
-the percentile intervals and Bias-Corrected intervals.
+increases with some commonly used block bootstrap confidence intervals
+including the percentile intervals and Bias-Corrected intervals.
 
@@
 when making inferences about dependent data. Early ideas were developed
-independently by \citet{hall1985resampling, carlstein1986use, kunsch1989jackknife}.
+independently by 
+\citet{hall1985resampling, carlstein1986use,ckunsch1989jackknife}.
 It has since been applied in various fields such as econometrics
@@
 variation attributable to certain variable, \citet{burch2012nonparametric} finds
-that three nonparametric bootstrap methods (standard, percentile, and bias-corrected
+that three nonparametric bootstrap methods (standard, percentile, and 
+bias-corrected
 and accelerated) approach the coverage of a pivotal quantity as the sample size
@@
 methods to be less accurate than the Fisher's transformation method even 
-for a sample of size of 100 and the correlation coefficientis equivalent to 0.
+for a sample of size of 100 and the correlation coefficient is equivalent to 0.
 The general consensus is that a big sample size is necessary.
@@
 compared in a simulation study. The results of this study suggest that
-appropriate recovery of temporal dependence parameters is heavily dependent on
-the type of interval used.
+appropriate recovery of temporal dependence parameters is heavily dependent
+on the type of interval used.
 
@@
 simulation
-study comparing the coverage rates of six???block bootstrap CIs. A discussion
+study comparing the coverage rates of six block bootstrap CIs. A discussion
 concludes in Section~\ref{sec:disc}.
@@
 \jy{Practice my writing style guidelines. Use two blank lines to separate
-  paragraphs.}
+  paragraphs.} \mc{addressed}
 
@@
 in the order they are picked to form a bootstrap sample of the data. The
-formation of the bootstrap sample ensures that the between-block dependence is
-weak and that the within-block serial dependence is preserved. Because the
+formation of the bootstrap sample ensures that the between-block dependence
+is weak and that the within-block serial dependence is preserved. Because the
 blocks here are non-overlapping, this bootstrap approach is known as
@@
 that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
-$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
+$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same
+method
 that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
@@
 \paragraph{Student's $t$ CI}
-The procedure for constructing a Student's $t$ CI based on standard bootstrap is
-described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the
+The procedure for constructing a Student's $t$ CI based on standard bootstrap
+is described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the
 upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom.
@@
 bias-correction and acceleration factors. The acceleration factor refers to
-the rate of change of of the standard error of $\hat\theta_n$ with respect
-to~$\theta$.
+the 
+rate of change of the standard error of $\hat\theta_n$ with respect to
+$\theta$.
 
@@
 $n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
-10000 replicates. For each replicate, we constructed seven 95\% block bootstrap
-CIs for each parameter as described in the last section. We can estimate 
-$\mu$, $\sigma_x$, and $\phi$ by computing the sample mean, sample 
+10000 replicates. For each replicate, we constructed seven 95\% block
+bootstrap CIs for each parameter as described in the last section. We can
+estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean,
+sample 
 standard deviation,
@@
 
-The coverage rates of the CIs were used to compare the performance of CIs. Let
-$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
+The coverage rates of the CIs were used to compare the performance of CIs.
+Let $\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
 respectively, for the confidence interval constructed for each replicate
@@
 
-For estimating~$\mu$,
-Student's $t$ CIs appear to have the highest coverage rates with respect 
-to estimating~$\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
-$\mu$ for all sample sizes, whereas other CIs have coverage rates that
-hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
-$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
-Standard, Percentile, %CBP, 
-Proposed Method, and $BC$ CIs seem to 
-generally cover $\mu$ at the nominal 
-rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
-for $n \geq 100$. For $\phi = 0$, or when the 
-sample is independently normally distributed, $n = 1600$ seems to 
-be enough to recover $\mu$ when using Standard, Percentile, 
-%CBP, 
-Proposed Method, or $BC$ 
-CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
-$\phi = 0$.
-For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
+Based on Figure~\ref{fig:mu}, Student's $t$ seems to generally
+be the best method for estimating $\mu$.
+For $\phi = -0.4$, Student's $t$ CIs over-cover 
+$\mu$ for smaller $n$, whereas other CIs recover $\mu$ at the
+nominal rate for all $n$ observed. For 
+$\phi = -0.2$, 
+all CIs recover $\mu$ at the nominal rate for all $n$. For $\phi = 0$, or when the 
+sample is independently normally distributed, $n \geq 200$ seems to 
+be large enough to recover $\mu$ at the nominal rate when using any CIs
+ besides Student's $t$ CIs, which seem to recover $\mu$ at the nominal rate for
+  all $n$.
+For $\phi = 0.2$, $n \geq 800$ seems to be sufficient to recover $\mu$
 at the nominal level when using
-any of the CIs, although some CIs, such as Student's $t$, are much closer to the
-$95\%$ line than others, most notably $BC_a$.
-For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
-Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the 
-furthest.
+any CIs besides Student's $t$ CIS, which recover $\mu$ at the nominal
+ rate for all $n \geq 200$.
+For $\phi = 0.4$, $n \geq 3200$ seems to be large enough to recover $\mu$
+at the nominal level when using
+any CIs besides Student's $t$ CIS, which seem to recover $\mu$ at the nominal
+ rate for all $n \geq 800$.
 
-Based on Figure~\ref{fig:sigma}, 
-$BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
-$\phi$ observed, although there is no trend of coverage deterioration, 
-indicating that there may eventually
-be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
-For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma_x$ when 
-$n = 1600$, but undercover $\sigma_x$ for $n = 3200$, indicating
-that a larger $n$ is most likely necessary to consistently cover $\sigma_x$ at 
-the nominal rate.
-The other CI types undercover $\sigma_x$ for all sample sizes at $\phi = 0.4$.
-For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma_x$ at 
-the nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
-nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
-be large enough if Standard CIs are used, and $n \geq 400$ is fine is
-Student's $t$ CIs are used. $n \geq 3200$ appears necessary 
-for other CIs. For $\phi = 0.2$, 
-comfortable coverage of $\sigma_x$ at the nominal level appears to only be true
-for Student's $t$ CIs for $n \geq 3200$, although Standard %and CBP% 
-CIs do reach the nominal level in our simulation results. For $\phi = 0.4$, a much
-larger sample size appears to be necessary. Student's $t$ CIs are the closest to
-$95\%$ coverage, and $BC_a$ CIs are the furthest.
+Based on Figure~\ref{fig:sigma}, Student's $t$ also seems to generally
+be the best method for estimating $\sigma$.
+for $\phi = -0.4$, $n \geq 1600$ is sufficient to recover $\sigma$
+at the nominal level when using
+any CIs besides Standard CIs, which seem to recover $\sigma$ at the nominal 
+rate for all $n \geq 800$, and Student's $t$ CIs, which seem to recover $\sigma$
+at the nominal rate for all $n \geq 400$. For $\phi = -0.2$, $n \geq 200$ is 
+adequate to recover $\sigma$ at the nominal rate with Student $t$ CIs, 
+but other CIs seem to require $n \geq 800$. For $\phi = 0$, or when the sample
+is independently normally distributed, $n \geq 400$ seems to be about enough
+to recover $\sigma$ for all CIs, but Student's $t$ CIs can recover $\sigma$ for
+$n \geq 100$. For $\phi = 0.2$, $n \geq 800$ is adequate for CIs besides the
+Student's $t$ CI, which recovers $\sigma$ well for $n \geq 200$. For 
+$\phi  = 0.4$, $n \geq 1600$ seems necessary for CIs other that Student's $t$ 
+CIs, which recover $\sigma$ at the nominal level for $n \geq 400$.
 
-Based on Figure~\ref{fig:phi}, 
-Percentile, %CBP, %
-$BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
-so they should not be used. The deterioration becomes more evident
-as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
-negative or positive. When $\phi = -0.4$, Standard and Proposed Method CIs 
-recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
-Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
-$\phi = -0.2$, Standard and Proposed Method CIs recover $\phi$ at $n = 800$ and 
-$n = 1600$, 
-although they undercover $\phi$ at $n = 3200$, indicating that 
-perhaps a larger $n$ is needed if these CIs are used. However,
-Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
-$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively 
-comfortably at $n = 3200$, and 
-$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
-and Proposed Method CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
-Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
-800$ is large enough for Standard and Proposed Method CIs. Student's $t$ CIs either
-recover or over-cover $\phi$ for all $n \geq 100$.
+Based on Figure~\ref{fig:phi}, Student's $t$ again seems to generally
+be the best method for estimating $\phi$. For high absolute values of $\phi$, 
+Percentile, $BC$, and $BC_a$ CIs
+deteriorate in coverage as $n$ increases. For $\phi = -0.4$, Standard, Student's
+$t$, and Proposed CIs recover $\phi$ for $n \geq 100$. For $\phi = -0.2$, 
+Standard and Proposed CIs recover $\phi$ at the nominal rate for $n \geq 200$, 
+whereas this can be done for $n \geq 100$ with Student's $t$ CIs. For $\phi = 
+0$, or when the sample
+is independently normally distributed, Standard and Proposed CIs recover 
+$\phi$ at the nominal level  for $n \geq 400$, and this is achievable for 
+$n \geq 100$ with Student's $t$ CIs. For $\phi = 0.2$ and $\phi = 0.4$, Standard 
+and Proposed CIs recover $\phi$ for $n \geq 200$, and Student's $t$ CIs 
+recover $\phi$ for all $n \geq 100$.
 
 To summarize, the CI type chosen should be based on the target parameter. 
-When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
-overall, although that leads to over-coverage when $\phi$ is -0.4. For a
-sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
-at the nominal rate even for small sample sizes. For positive $\phi$, a larger
-sample size appears to be necessary regardless of the CI used. In the case
-that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
-necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
+When estimating $\mu$, the Student's $t$ CI seems to have the highest
+ coverage
+overall, although that leads to over-coverage for small sample sizes when $\phi$
+ is -0.4. For a
+sample with no temporal dependence, the Student's $t$ CI recover $\mu$ 
+very close to the nominal rate even for small sample sizes. For positive $\phi$, a
+larger sample size appears to be necessary regardless of the CI used. In the
+case that $\phi$ is unknown and expected to be greater than $0$, $n > 800$
+may be
+necessary for block bootstrap interval estimation of $\mu$ when using the
+Student's $t$ CI. If $\phi$ is known,
 a lesser sample size may be sufficient. When estimating $\sigma_x$,
-$BC_a$ should not be used, and Student's $t$ again has the highest
-\eds{highest?} \mc{addressed} coverage
+Student's $t$ again has the highest coverage
 rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
-$n > 3200$ may be necessary for block bootstrap interval estimation of
-$\sigma_x$. Again, if $\phi$ is known, a lesser sample size may be enough.
-When estimating $\phi$, Percentile and $BC_a$ CIs 
+$n > 400$ may be necessary for block bootstrap interval estimation of
+$\sigma_x$ when using the Student's $t$ CI. Again, if $\phi$ is known, a lesser
+sample size may be enough.
+When estimating $\phi$, Percentile, $BC$, and $BC_a$ CIs 
 deteriorate in coverage, indicating they should not be used in this context. 
@@
 because the assumption that the coverage rate will approach the nominal level
-as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix the
+as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix
+the
 deterioration problem, and they perform similarly, but Student's $t$ covers
 $\phi$ at the nominal rate for much smaller sample sizes. It seems that 
-$n = 800$ is large enough to
+$n = 100$ is certainly large enough to
 recover $\phi$ when using the Student's $t$ method.
@@
   \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
-  \caption{100 replicate Percentile, Bias-Corrected, and Proposed Method Bootstrap CIs for samples of $n = 800$ for
-    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
-    of the CIs are displayed, as well as $\hat\theta_n$ (blue) and $\bar\theta_n^{(b)}$ (red). }
+  \caption{100 replicate Percentile, Bias-Corrected, and Proposed Method
+  Bootstrap CIs for samples of $n = 800$ for
+    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper
+    bounds
+    of the CIs are displayed, as well as $\hat\theta_n$ (blue) and $
+    \bar\theta_n^{(b)}$ (red). }
   \label{fig:npi}
@@
 
-These results beg the question of why certain methods perform poorly. To address 
+These results beg the question of why certain methods perform poorly. To
+address 
 this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed 
@@
  dependence factors.
-%The motivation for the study is the idea that block bootstrap procedure will
-%perfectly estimate a parameter of a time series given an infinitely large
-%sample. The goal for this study was to find what is a good enough finite
-%sample length for block bootstrap estimation to recover the parameter of a
-%time series at an acceptable rate.
  We know theoretically that the block bootstrap procedure will cover
@@
 whereas Percentile, 
-%CBP, 
 $BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
@@
 the width of the CI decreases, but because the Percentile CI
-underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct the 
+underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct
+the 
 bias, but the width of the CI seems to be inconsistent. The acceleration 

### 2023-08-19 Manuscript/manuscript.tex
Condensed a Little Bit

@@
 
-Block bootstrap is a powerful tool for constructing confidence intervals (CI)
-when making inferences about dependent data. Early ideas were developed
+Block bootstrap is a tool to construct confidence intervals (CI)
+to make inferences about dependent data. Early ideas were developed
 independently by 
@@
 \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
-Block bootstrap is particularly useful for serially dependent
+Block bootstrap is useful for serially dependent
 data when the serial dependence is not specified or not of primary interest.
 The method is expected to produce CIs with coverage rates
-matching their nominal levels as the sample size grows to infinity. However,
+matching their nominal levels as the sample size grows. However,
 when dealing with finite sample sizes, an important question is how large the
-sample size needs to be for block bootstrap CIs to have the
+sample size must be for block bootstrap CIs to have the
 desired coverage rates.
 
-\jy{too wordy; do some condensing}
+\jy{too wordy; do some condensing} \mc{condensed a little bit}
 The performance of bootstrap standard errors with independent data
@@
 less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
-that the best choice of method for estimating
-the parameter of a distribution is dependent on the sample size, the number of
+that the best method to estimate
+the parameter of a distribution depends on the sample size, the number of
 bootstrap resamples, and the confidence level. In the context of structural
 equation modeling, \citet{nevitt2001performance} find
-that a sample size of 200--1000 is usually sufficient for interval estimation
+that a sample size of 200--1000 is sufficient for interval estimation
 using standard nonparametric bootstrap. In estimating the proportion of 
-variation attributable to certain variable, \citet{burch2012nonparametric} finds
+variation attributable to a certain variable, \citet{burch2012nonparametric} finds
 that three nonparametric bootstrap methods (standard, percentile, and 
@@
 gets larger for an underlying normal distribution, but for other distributions, 
-coverage may deteriorate even as the sample size increases.
+coverage may deteriorate as the sample size increases.
 When attempting to create interval estimations for the Pearson correlation 
@@
 methods to be less accurate than the Fisher's transformation method even 
-for a sample of size of 100 and the correlation coefficient is equivalent to 0.
+for a sample with size~$100$ and correlation coefficient equal to 0.
 The general consensus is that a big sample size is necessary.
@@
 
-The goal of this paper is to provide some practical recommendations on
+The goal of this paper is to provide recommendations on
 necessary sample size for block bootstrap with dependent data, similar to what 
@@
 empirical coverage rates at different sample sizes and dependence levels are
-compared in a simulation study. The results of this study suggest that
-appropriate recovery of temporal dependence parameters is heavily dependent
+compared in a simulation study. The results of this study suggest that recovery of temporal dependence parameters is reliant
 on the type of interval used.

### 2023-08-19 Manuscript/manuscript.tex
Manuscript Update

@@
 independently by 
-\citet{hall1985resampling, carlstein1986use,ckunsch1989jackknife}.
+\citet{hall1985resampling, carlstein1986use,kunsch1989jackknife}.
 It has since been applied in various fields such as econometrics
@@
 that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
-Now the question is, how to construct a CI for $\theta$
+Now the question is how to construct a CI for $\theta$
 using the $B$ bootstrap point estimates
 $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.
-We consider five kinds of CIs.
+We consider six kinds of CIs.
 
@@
 \]
-This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
-Its validity relies on whether the distribution of $\hat\theta_n$ is reasonably
+This CI is centered by the point estimator $\hat\theta_n$ and is symmetric. The
+Standard CI is a table-based bootstrap interval
+approach. Its validity relies on whether the distribution of $\hat\theta_n$ is
+ reasonably
 well approximated by its asymptotic normal distribution and whether the
@@
 for $b \in \{1, \ldots, B\}$. 
-Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
-$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
-for $i \in \{1, \ldots, n\}$, 
+Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$ for 
+$i \in \{1, \ldots, k\}$, let
+$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$,
 and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
@@
 \alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
-  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right)
+  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
 \text{ and }
 \alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
-  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
+  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
 \]
@@
 the lower and upper bounds.
-\jy{Double check}
+\jy{Double check} \mc{changed BCA, had to rerun simulations because I did k
+degrees of freedom instead of k - 1}
 

### 2023-08-19 Code/functions.R

@@ -42,8 +42,8 @@ do1rep <- function(n, phi, statistic, blksize, dstr = qnorm, R = 1000, level = .
   
   ## Student's t interval
   stuCI <- sapply(1:length(bts$t0),
-                  function(i) c(bts$t0[i] - qt(1-alpha/2, n/blksize)*se[i], 
-                                bts$t0[i] - qt(alpha/2, n/blksize)*se[i]))
+                  function(i) c(bts$t0[i] - qt(1-alpha/2, n/blksize - 1)*se[i], 
+                                bts$t0[i] - qt(alpha/2, n/blksize - 1)*se[i]))
   
   ## Percentile interval
   pctCI <- apply(bts$t, 2, quantile, prob = c(alpha/2, 1 - alpha/2))

### 2023-08-20 Code/exp_processing.R
Plot Updates

@@ -1,4 +1,5 @@
 source("functions.R")
+library(copula)
 setwd("../Data")
 file_names <- list.files(pattern = "^exp_results")
 all_lists <- lapply(file_names, function(x) {

### 2023-08-21 Manuscript/manuscript.tex
smoothed intro

@@
 Block bootstrap is a tool to construct confidence intervals (CI)
-to make inferences about dependent data. Early ideas were developed
-independently by 
-\citet{hall1985resampling, carlstein1986use,kunsch1989jackknife}.
-It has since been applied in various fields such as econometrics
+to make inferences about dependent data. Essentially, it depends on correct
+estimation of the uncertainty in the estimation. Early ideas were developed
+by \citet{hall1985resampling, carlstein1986use,kunsch1989jackknife}.
+It has since been applied in various fields, for instance, econometrics
 \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
-Block bootstrap is useful for serially dependent
+Block bootstrap is especially useful for serially dependent
 data when the serial dependence is not specified or not of primary interest.
@@
 
-\jy{too wordy; do some condensing} \mc{condensed a little bit}
-The performance of bootstrap standard errors with independent data
-in providing valid uncertainty measures has been extensively studied.
-For example, for non-block bootstrap, \citet{hesterberg2015teachers} notes
-that while percentile-based CIs for the mean from nonparametric bootstrap
-are more accurate than $t$-intervals for larger sample sizes, they are
-less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
-that the best method to estimate
-the parameter of a distribution depends on the sample size, the number of
-bootstrap resamples, and the confidence level. In the context of structural
+For independent data, extensive research has explored the effectiveness of
+bootstrap standard errors in providing accurate uncertainty measures.
+For example, \citet{hesterberg2015teachers} observes
+that while percentile-based CIs for the mean parameter
+are more accurate than $t$-intervals for larger sample sizes, they accuracy
+diminishes for smaller sample sizes. The optimal parameter estimation of a
+distribution, according to \citet{chernick2009revisiting},
+depends on the sample size, the number of
+bootstrap replicates, and the confidence level. In structural
 equation modeling, \citet{nevitt2001performance} find
 that a sample size of 200--1000 is sufficient for interval estimation
-using standard nonparametric bootstrap. In estimating the proportion of 
-variation attributable to a certain variable, \citet{burch2012nonparametric} finds
-that three nonparametric bootstrap methods (standard, percentile, and 
-bias-corrected
-and accelerated) approach the coverage of a pivotal quantity as the sample size
-gets larger for an underlying normal distribution, but for other distributions, 
-coverage may deteriorate as the sample size increases.
-When attempting to create interval estimations for the Pearson correlation 
-coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
-methods to be less accurate than the Fisher's transformation method even 
-for a sample with size~$100$ and correlation coefficient equal to 0.
-The general consensus is that a big sample size is necessary.
+using standard nonparametric bootstrap. Estimating variance component,
+\citet{burch2012nonparametric} report that as the sample size increases under a
+normal distribution, nonparametric bootstrap methods approach the coverage of a
+pivotal quantity as the sample size, but for other distributions, the coverage
+can deteriorate. In estimating the correlation coefficient of bivariate normal
+data, \citet{puth2015variety} note that even for a sample size of~$100$ with
+true correlation coefficient~0, bootstrap methods are less accurate than the
+Fisher's transformation. The prevailing consensus highlights the necessity of a
+substantial sample size for bootstrap CIs to attain the desired coverage.
 
-Few studies have provided a practical guide on what size is needed
-for block bootstrap inference for dependent data.
-In a linear regression setting with dependent data where the
-regression errors are generated from a homoscedastic AR(1) process, 
-\citet{goncalves2005bootstrap} find that the standard error estimates from
-moving block bootstrap in small samples may be more accurate than those
-from closed-form asymptotic estimates, but moving block bootstrap 
-CIs still do not have sufficient coverage of the target parameter even for
-sample size~$1024$.
+Limited research has offered practical guidance concerning the requisite sample
+size for employing block bootstrap inference with dependent data. In the context
+of linear regression involving dependent data, where regression errors stem from
+a homoscedastic autoregressive process of order-1, the investigation conducted
+by \citet{goncalves2005bootstrap} reveals that, in cases of small sample sizes,
+standard error estimates derived from the moving block bootstrap approach may
+demonstrate greater accuracy than those based on closed-form asymptotic
+estimates. Nonetheless, even when considering a substantial sample size of
+~$1024$, confidence intervals generated through the moving block bootstrap
+method still fail to adequately encompass the target parameter. The scarcity of
+existing literature addressing the necessary sample sizes conducive to the
+efficacy of block bootstrap techniques has spurred the initiation of the present
+study.
 
@@
 empirical coverage rates at different sample sizes and dependence levels are
-compared in a simulation study. The results of this study suggest that recovery of temporal dependence parameters is reliant
+compared in a simulation study. The results of this study suggest that recovery
+of temporal dependence parameters is reliant
 on the type of interval used.
@@
 \label{sec:bbci}
-
-\jy{Practice my writing style guidelines. Use two blank lines to separate
-  paragraphs.} \mc{addressed}
 
@@
 the lower and upper bounds.
-\jy{Double check} \mc{changed BCA, had to rerun simulations because I did k
-degrees of freedom instead of k - 1}
 

### 2023-08-21 Manuscript/manuscript.tex
suggestions on simulation result summari

@@
 
+\jy{Can we come up with a good name for the proposed method? Other people may cite this.}
 \paragraph{A Proposed CI}
@@
 
-Based on Figure~\ref{fig:mu}, Student's $t$ seems to generally
-be the best method for estimating $\mu$.
+\jy{The results discussion need to be streamlined. The three paragraphs are too
+  similar, and only student's ci is discussed. Questions to consider:
+  1) which methods give the right coverage as sample size increases?
+  2) which methods needs smaller sample sizes to get the right coverage?
+  3) what's the difference between the results in positive and negative
+  dependence?
+  4) how does the result change as dependence gets stronger?
+  }
+
+For estimating the mean parameter~$\mu$,
+Figure~\ref{fig:mu} suggests that the Student's $t$ interval is the best method.
 For $\phi = -0.4$, Student's $t$ CIs over-cover 

### 2023-08-21 Manuscript/manuscript.tex
Respond to Comments

@@
 should provide valid confidence intervals as the length of the time series goes
-to infinity. In practice, however, it is necessary to know how large of a finite
-sample is required for block bootstrap confidence intervals to work well. This
-study aims to answer this question in a simple simulation setting where the data
-are generated from a first-order autoregressive process. The empirical coverage
-rates of several commonly used bootstrap confidence intervals for the mean,
-standard deviation, and the lag-1 autocorrelation coefficient are compared.
-A quite large sample is found necessary for the intervals to have the right
-coverage rates even when estimating a simple parameter like the mean. Some
-block bootstrap methods could fail when estimating the lag-1 autocorrelation.
-It is surprising that the coverage property even deteriorates as the sample size
-increases with some commonly used block bootstrap confidence intervals
-including the percentile intervals and Bias-Corrected intervals.
+to infinity. In practice, however, it is necessary to know how large of a
+finite sample is required for block bootstrap confidence intervals to work
+well. This study aims to answer this question in a simple simulation setting
+where the data are generated from a first-order autoregressive process. The
+empirical coverage rates of several commonly used bootstrap confidence
+intervals for the mean, standard deviation, and the lag-1 autocorrelation
+coefficient are compared. A quite large sample is found necessary for the
+intervals to have the right coverage rates even when estimating a simple
+parameter like the mean. Some block bootstrap methods could fail when
+estimating the lag-1 autocorrelation. It is surprising that the coverage
+property even deteriorates as the sample size increases with some commonly
+used block bootstrap confidence intervals including the percentile intervals
+and Bias-Corrected intervals.
 
@@
 
-Block bootstrap is a tool to construct confidence intervals (CI)
-to make inferences about dependent data. Essentially, it depends on correct
-estimation of the uncertainty in the estimation. Early ideas were developed
-by \citet{hall1985resampling, carlstein1986use,kunsch1989jackknife}.
-It has since been applied in various fields, for instance, econometrics
+Block bootstrap is a tool to construct confidence intervals (CI) to make
+inferences about dependent data. Essentially, it depends on correct estimation
+of the uncertainty in the estimation. Early ideas were developed by
+\citet{hall1985resampling, carlstein1986use,kunsch1989jackknife}. It has since
+been applied in various fields, for instance, econometrics
 \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
-Block bootstrap is especially useful for serially dependent
-data when the serial dependence is not specified or not of primary interest.
-The method is expected to produce CIs with coverage rates
-matching their nominal levels as the sample size grows. However,
-when dealing with finite sample sizes, an important question is how large the
-sample size must be for block bootstrap CIs to have the
-desired coverage rates.
+Block bootstrap is especially useful for serially dependent data when the
+serial dependence is not specified or not of primary interest. The method is
+expected to produce CIs with coverage rates matching their nominal levels as
+the sample size grows. However, when dealing with finite sample sizes, an
+important question is how large the sample size must be for block bootstrap
+CIs to have the desired coverage rates.
 
 For independent data, extensive research has explored the effectiveness of
-bootstrap standard errors in providing accurate uncertainty measures.
-For example, \citet{hesterberg2015teachers} observes
-that while percentile-based CIs for the mean parameter
-are more accurate than $t$-intervals for larger sample sizes, they accuracy
-diminishes for smaller sample sizes. The optimal parameter estimation of a
-distribution, according to \citet{chernick2009revisiting},
-depends on the sample size, the number of
-bootstrap replicates, and the confidence level. In structural
-equation modeling, \citet{nevitt2001performance} find
-that a sample size of 200--1000 is sufficient for interval estimation
-using standard nonparametric bootstrap. Estimating variance component,
-\citet{burch2012nonparametric} report that as the sample size increases under a
-normal distribution, nonparametric bootstrap methods approach the coverage of a
-pivotal quantity as the sample size, but for other distributions, the coverage
-can deteriorate. In estimating the correlation coefficient of bivariate normal
-data, \citet{puth2015variety} note that even for a sample size of~$100$ with
-true correlation coefficient~0, bootstrap methods are less accurate than the
-Fisher's transformation. The prevailing consensus highlights the necessity of a
-substantial sample size for bootstrap CIs to attain the desired coverage.
+bootstrap standard errors in providing accurate uncertainty measures. For
+example, \citet{hesterberg2015teachers} observes that while percentile-based
+CIs for the mean parameter are more accurate than $t$-intervals for larger
+sample sizes, they accuracy diminishes for smaller sample sizes. The optimal
+parameter estimation of a distribution, according to
+\citet{chernick2009revisiting}, depends on the sample size, the number of
+bootstrap replicates, and the confidence level. In structural equation
+modeling, \citet{nevitt2001performance} find that a sample size of 200--1000
+is sufficient for interval estimation using standard nonparametric bootstrap.
+Estimating variance component, \citet{burch2012nonparametric} report that as
+the sample size increases under a normal distribution, nonparametric bootstrap
+methods approach the coverage of a pivotal quantity as the sample size, but
+for other distributions, the coverage can deteriorate. In estimating the
+correlation coefficient of bivariate normal data, \citet{puth2015variety} note
+that even for a sample size of~$100$ with true correlation coefficient~0,
+bootstrap methods are less accurate than the Fisher's transformation. The
+prevailing consensus highlights the necessity of a substantial sample size for
+bootstrap CIs to attain the desired coverage.
 
 Limited research has offered practical guidance concerning the requisite sample
-size for employing block bootstrap inference with dependent data. In the context
-of linear regression involving dependent data, where regression errors stem from
-a homoscedastic autoregressive process of order-1, the investigation conducted
-by \citet{goncalves2005bootstrap} reveals that, in cases of small sample sizes,
-standard error estimates derived from the moving block bootstrap approach may
-demonstrate greater accuracy than those based on closed-form asymptotic
-estimates. Nonetheless, even when considering a substantial sample size of
-~$1024$, confidence intervals generated through the moving block bootstrap
-method still fail to adequately encompass the target parameter. The scarcity of
-existing literature addressing the necessary sample sizes conducive to the
-efficacy of block bootstrap techniques has spurred the initiation of the present
-study.
+size for employing block bootstrap inference with dependent data. In the
+context of linear regression involving dependent data, where regression errors
+stem from a homoscedastic autoregressive process of order-1, the investigation
+conducted by \citet{goncalves2005bootstrap} reveals that, in cases of small
+sample sizes, standard error estimates derived from the moving block bootstrap
+approach may demonstrate greater accuracy than those based on closed-form
+asymptotic estimates. Nonetheless, even when considering a substantial sample
+size of ~$1024$, confidence intervals generated through the moving block
+bootstrap method still fail to adequately encompass the target parameter. The
+scarcity of existing literature addressing the necessary sample sizes
+conducive to the efficacy of block bootstrap techniques has spurred the
+initiation of the present study.
 
-The goal of this paper is to provide recommendations on
-necessary sample size for block bootstrap with dependent data, similar to what 
-was done for basic bootstrap in \citet{hesterberg2015teachers}. We consider a
-simple situation of a stationary time series, where the parameters of
-interests are the mean, standard deviation, and the first-order
-autocorrelation coefficient. We compare six variants of block bootstrap
-CIs from the literature \citep{diciccio1996bootstrap,
-  rice2006mathematical}: a standard normal CI, and a Student's $t$ CI,
-a percentile CI, a bias-corrected CI, a bias-correct and accelerated ($BC_a$)
-CI, and a CI proposed in this article. Their
-empirical coverage rates at different sample sizes and dependence levels are
-compared in a simulation study. The results of this study suggest that recovery
-of temporal dependence parameters is reliant
-on the type of interval used.
+The goal of this paper is to provide recommendations on necessary sample size
+for block bootstrap with dependent data, similar to what was done for basic
+bootstrap in \citet{hesterberg2015teachers}. We consider a simple situation of
+a stationary time series, where the parameters of interests are the mean,
+standard deviation, and the first-order autocorrelation coefficient. We
+compare six variants of block bootstrap CIs from the literature
+\citep{diciccio1996bootstrap, rice2006mathematical}: a standard normal CI, and
+a Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-correct and
+accelerated ($BC_a$) CI, and a CI proposed in this article. Their empirical
+coverage rates at different sample sizes and dependence levels are compared in
+a simulation study. The results of this study suggest that recovery of
+temporal dependence parameters is reliant on the type of interval used.
 
-The remainder of the paper is organized as follows.
-Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
-bootstrap estimates to construct CIs; a simple CI obtained by recentering at the
-point estimate is proposed for comparison. Section~\ref{sec:simu} reports a
-simulation
-study comparing the coverage rates of six block bootstrap CIs. A discussion
+The remainder of the paper is organized as follows. Section~\ref{sec:bbci}
+reviews block bootstrap procedures and how to use block bootstrap estimates to
+construct CIs; a simple CI obtained by recentering at the point estimate is
+proposed for comparison. Section~\ref{sec:simu} reports a simulation study
+comparing the coverage rates of six block bootstrap CIs. A discussion
 concludes in Section~\ref{sec:disc}.
@@
 Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
-Our goal is to construct a CI for a parameter $\theta$ in the
-data generating model of the series. Suppose that $\hat\theta_n$ is a point
-estimator of~$\theta$ based on the observed series. Bootstrap is a powerful
-approach to construct CIs. If the observations in the series
-were independent, a standard nonparametric bootstrap procedure would draw a
-large number~$B$ bootstrap copies of the observed data, and calculate an
-estimate $\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. The uncertainty
-of $\hat\theta_n$ is then estimated by the empirical uncertainty of the
-$\hat\theta_n^{(b)}$'s. When serial dependence is present, the bootstrap
-procedure needs to preserve the serial dependence. Block bootstrap was
-motivated for this situation.
+Our goal is to construct a CI for a parameter $\theta$ in the data generating
+model of the series. Suppose that $\hat\theta_n$ is a point estimator
+of~$\theta$ based on the observed series. Bootstrap is a powerful approach to
+construct CIs. If the observations in the series were independent, a standard
+nonparametric bootstrap procedure would draw a large number~$B$ bootstrap
+copies of the observed data, and calculate an estimate $\hat\theta_n^{(b)}$
+for each copy $b = 1, \ldots, B$. The uncertainty of $\hat\theta_n$ is then
+estimated by the empirical uncertainty of the $\hat\theta_n^{(b)}$'s. When
+serial dependence is present, the bootstrap procedure needs to preserve the
+serial dependence. Block bootstrap was motivated for this situation.
 
@@
 Block bootstrap preserves the serial dependence in the observed data by
-partitioning the data into blocks and performing bootstrap on the blocks.
-In particular, consider block size~$l$ and, for convenience, suppose that
-$n$ is a multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$
-is $Y_j = \{X_{(j - 1) l + 1}, \ldots, X_{(j - 1) l + l}\}$,
-$j = 1, \ldots,   k$.  Then, we sample $k$ blocks of $Y_j$'s from the set 
-$\{Y_1, \ldots, Y_k\}$ with replacement and concatenate the $k$ sampled blocks
-in the order they are picked to form a bootstrap sample of the data. The
-formation of the bootstrap sample ensures that the between-block dependence
-is weak and that the within-block serial dependence is preserved. Because the
-blocks here are non-overlapping, this bootstrap approach is known as
-non-overlapping block bootstrap, or simple block bootstrap.
+partitioning the data into blocks and performing bootstrap on the blocks. In
+particular, consider block size~$l$ and, for convenience, suppose that $n$ is
+a multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$ is
+$Y_j = \{X_{(j - 1) l + 1}, \ldots, X_{(j - 1) l + l}\}$, $j = 1, \ldots, k$.
+Then, we sample $k$ blocks of $Y_j$'s from the set $\{Y_1, \ldots, Y_k\}$ with
+replacement and concatenate the $k$ sampled blocks in the order they are
+picked to form a bootstrap sample of the data. The formation of the bootstrap
+sample ensures that the between-block dependence is weak and that the
+within-block serial dependence is preserved. Because the blocks here are
+non-overlapping, this bootstrap approach is known as non-overlapping block
+bootstrap, or simple block bootstrap.
 
@@
 $j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
-blocks
-of $Z_j$'s with replacement and then align them in the order they were
-picked
-to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
-block selected will be reduced in size so that the final size of the
+blocks of $Z_j$'s with replacement and then align them in the order they were
+picked to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the
+last block selected will be reduced in size so that the final size of the
 block bootstrap sample is $n$. It is also possible to implement moving block
@@
 there to be a large number of blocks to give sufficient variability between
-each bootstrap sample. As $n$ increases, both~$l$
-and $n / l$ should also increase. To achieve this, $l$ is
-often assigned a value as a function of $n$. A common function that is
-considered optimal is $l = \lceil n^{1/3} \rceil$
+each bootstrap sample. As $n$ increases, both~$l$ and $n / l$ should also
+increase. To achieve this, $l$ is often assigned a value as a function of $n$.
+A common function that is considered optimal is $l = \lceil n^{1/3} \rceil$
 \citep{buhlmann1999block}, which was adopted in this study.
@@
 that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
-$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same
-method
-that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
-Now the question is how to construct a CI for $\theta$
-using the $B$ bootstrap point estimates
-$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.
-We consider six kinds of CIs.
+$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
+that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$. Now
+the question is how to construct a CI for $\theta$ using the $B$ bootstrap
+point estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. We
+consider six kinds of CIs.
 
@@
 $\theta$ as the mean, we just need an estimate of the standard error to
-construct an approximate CI \citep[p.168]{efron1993introduction}.
-Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
+construct an approximate CI \citep[p.168]{efron1993introduction}. Let
+$\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
 copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the
-upper $\alpha$ quantile of the standard normal distribution.
-A $(1 - \alpha)100\%$ standard normal CI is
+upper $\alpha$ quantile of the standard normal distribution. A
+$(1 - \alpha)100\%$ standard normal CI is
 \[
@@
 This CI is centered by the point estimator $\hat\theta_n$ and is symmetric. The
-Standard CI is a table-based bootstrap interval
-approach. Its validity relies on whether the distribution of $\hat\theta_n$ is
- reasonably
-well approximated by its asymptotic normal distribution and whether the
-bootstrap $\widehat{\text{SE}}$ approximates the true standard error.
+Standard CI is a table-based bootstrap interval approach. Its validity relies
+on whether the distribution of $\hat\theta_n$ is reasonably well approximated
+by its asymptotic normal distribution and whether the bootstrap
+$\widehat{\text{SE}}$ approximates the true standard error.
 
@@
 The procedure for constructing a Student's $t$ CI based on standard bootstrap
-is described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the
-upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom.
+is described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be
+the upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom.
 With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
@@
 \eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
-where $k$ is the number of blocks.
-This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
-Like the standard 
-normal interval, the Student's $t$ CI is a table-based bootstrap interval
-approach. In this case,
+where $k$ is the number of blocks. This CI is centered by the point estimator
+$\hat\theta_n$ and is symmetric. Like the standard normal interval, the
+Student's $t$ CI is a table-based bootstrap interval approach. In this case,
 its validity relies on whether the distribution of $\hat\theta_n$ is
-reasonably well approximation by the $t_{k-1}$ distribution with an
-expected value of $\theta$, and whether the bootstrap 
-$\widehat{\text{SE}}$ approximates the true standard error.
+reasonably well approximation by the $t_{k-1}$ distribution with an expected
+value of $\theta$, and whether the bootstrap $\widehat{\text{SE}}$
+approximates the true standard error.
 
@@
 \]
-This CI is not necessarily centered by the point estimator $\hat\theta_n$.
-As will be shown in our simulation study, this approach works well for the
+This CI is not necessarily centered by the point estimator $\hat\theta_n$. As
+will be shown in our simulation study, this approach works well for the
 marginal mean and standard deviation of a serially dependent process, but its
@@
 The procedure for constructing a Bias Corrected Bootstrap CI based on standard
-bootstrap is described in \citet{carpenter2000bootstrap}.
-Let $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
-for $b \in \{1, \ldots, B\}$. Define
-$\alpha_1 = \Phi(2b - z_{\alpha/2})$ and 
-$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$.
-A $(1 - \alpha)100\%~BC$ CI is
+bootstrap is described in \citet{carpenter2000bootstrap}. Let
+$b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
+$b \in \{1, \ldots, B\}$. Define $\alpha_1 = \Phi(2b - z_{\alpha/2})$ and 
+$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$. A $(1 - \alpha)100\%~BC$ CI is
 \[
@@
 \paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
-The $BC_a$ CI was first suggested in \citet{efron1987better}.
-Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
-for $b \in \{1, \ldots, B\}$. 
-Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$ for 
-$i \in \{1, \ldots, k\}$, let
-$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$,
-and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
+The $BC_a$ CI was first suggested in \citet{efron1987better}.Let
+$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
+$b \in \{1, \ldots, B\}$. Let $Z_{(i)}$ be the original sample without the
+$i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let $\hat{\theta}_{(i)}$ be
+the statistic of $Z_{(i)}$, and let
+$\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
 Let 
@@
 bias-correction and acceleration factors. The acceleration factor refers to
-the 
-rate of change of the standard error of $\hat\theta_n$ with respect to
+the rate of change of the standard error of $\hat\theta_n$ with respect to
 $\theta$.
 
-\jy{Can we come up with a good name for the proposed method? Other people may cite this.}
+\jy{Can we come up with a good name for the proposed method? Other people may cite this.}\mc{bias-centered? i'm not sure}
 \paragraph{A Proposed CI}
@@
 the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
-estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
-A $(1 - \alpha)100\%$ CI is
+estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$. A
+$(1 - \alpha)100\%$ CI is
 \[
@@
 We designed a simulation study to compare the performance of the different
-block
-bootstrap CI methods. In particular, we generated time series $X_t$
-from a 1st order auto-regressive (AR(1)) process:
+block bootstrap CI methods. In particular, we generated time series $X_t$ from
+a 1st order auto-regressive (AR(1)) process:
 \[
@@
 $\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
-$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$.
-The series $X_t$ has mean zero and variance
+$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. The
+series $X_t$ has mean zero and variance
 $\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$,
-we
-set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
+we set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
 
@@
 To investigate the effect of sample size~$n$, we considered an array of values
-$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
-10000 replicates. For each replicate, we constructed seven 95\% block
+$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we
+generated 10000 replicates. For each replicate, we constructed seven 95\% block
 bootstrap CIs for each parameter as described in the last section. We can
-estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean,
-sample 
-standard deviation,
-and lag-1 auto-correlation, respectively, of each bootstrap sample, and then 
-construct intervals for each parameter using the appropriate procedures
-described in Section~\ref{sec:bbci}.
-Then we estimated their actual coverage rates along with their 95\% confidence
-intervals from the 10000 replicates. The block bootstrap sampling step was done
-with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
-block size $\lceil n / l \rceil$. This function by default is an implementation
-of moving block bootstrap as described in the previous section, meaning that
-that blocks are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.
+estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean, sample 
+standard deviation, and lag-1 auto-correlation, respectively, of each
+bootstrap sample, and then construct intervals for each parameter using the
+appropriate procedures described in Section~\ref{sec:bbci}. Then we estimated
+their actual coverage rates along with their 95\% confidence intervals from
+the 10000 replicates. The block bootstrap sampling step was done with function
+\texttt{tsboot} from R package \textsl{boot} \citep{boot}, with block size
+$\lceil n / l \rceil$. This function by default is an implementation of moving
+block bootstrap as described in the previous section, meaning that that blocks
+are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.
 
-The coverage rates of the CIs were used to compare the performance of CIs.
-Let $\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
+The coverage rates of the CIs were used to compare the performance of CIs. Let
+$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
 respectively, for the confidence interval constructed for each replicate
-$r \in \{1, \ldots, R\}$, where $R$ is the
-number of replicates.
-Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
-for $r \in \{1, \ldots, R\}$.
-If a CI method is valid, then the coverage rate is expected to match the
-nominal 
-level. Because it is unlikely for the coverage to exactly match the nominal
-level,
-we can construct a 95\% CI of the coverage
-rate (which is an estimate of a proportion with $R = 10000$. If the
-proportion
+$r \in \{1, \ldots, R\}$, where $R$ is the number of replicates. Then
+$cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$, for
+$r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
+expected to match the nominal level. Because it is unlikely for the coverage
+to exactly match the nominal level, we can construct a 95\% CI of the coverage
+rate (which is an estimate of a proportion with $R = 10000$. If the proportion
 0.95 is included in the interval, the block bootstrap method is likely
-performing
-well. If all values in the interval are below 0.95, the results would suggest 
-that the
-method either is providing inaccurate estimation, is underestimating the
-process' variability, or a combination of both. If all values in the interval
-are above .95, the results suggest that the method is overestimating the
-process' variability.
-Figures~\ref{fig:mu}--\ref{fig:phi} summarizes the empirical coverage rates and
-the 95\% confidence intervals of the real coverage, generated using the R
-\textsl{ggplot2} package \citep{ggplot2}.
+performing well. If all values in the interval are below 0.95, the results
+would suggest that the method either is providing inaccurate estimation, is
+underestimating the process' variability, or a combination of both. If all
+values in the interval are above .95, the results suggest that the method is
+overestimating the process' variability. Figures~\ref{fig:mu}--\ref{fig:phi}
+summarizes the empirical coverage rates and the 95\% confidence intervals of
+the real coverage, generated using the R \textsl{ggplot2} package
+\citep{ggplot2}.
 
@@
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates.
-    The error bars represent 95\% CIs of the real coverage rates.}
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
+    error bars represent 95\% CIs of the real coverage rates.}
   \label{fig:mu}
@@
     the marginal standard deviation $\sigma_x$ of an AR(1) 
-		process with AR
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates.
-    The error bars represent 95\% CIs of the real coverage rates.}
+    process with AR coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and
+    series length $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000
+    replicates. The error bars represent 95\% CIs of the real coverage rates.}
   \label{fig:sigma}
@@
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates.
-    The error bars represent 95\% CIs of the real coverage rates.}
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
+    error bars represent 95\% CIs of the real coverage rates.}
   \label{fig:phi}
@@
   4) how does the result change as dependence gets stronger?
-  }
+  } \mc{addressed}
 
-For estimating the mean parameter~$\mu$,
-Figure~\ref{fig:mu} suggests that the Student's $t$ interval is the best method.
-For $\phi = -0.4$, Student's $t$ CIs over-cover 
-$\mu$ for smaller $n$, whereas other CIs recover $\mu$ at the
-nominal rate for all $n$ observed. For 
-$\phi = -0.2$, 
-all CIs recover $\mu$ at the nominal rate for all $n$. For $\phi = 0$, or when the 
-sample is independently normally distributed, $n \geq 200$ seems to 
-be large enough to recover $\mu$ at the nominal rate when using any CIs
- besides Student's $t$ CIs, which seem to recover $\mu$ at the nominal rate for
-  all $n$.
-For $\phi = 0.2$, $n \geq 800$ seems to be sufficient to recover $\mu$
-at the nominal level when using
-any CIs besides Student's $t$ CIS, which recover $\mu$ at the nominal
- rate for all $n \geq 200$.
-For $\phi = 0.4$, $n \geq 3200$ seems to be large enough to recover $\mu$
-at the nominal level when using
-any CIs besides Student's $t$ CIS, which seem to recover $\mu$ at the nominal
- rate for all $n \geq 800$.
+For estimating the mean parameter~$\mu$, Figure~\ref{fig:mu} suggests that all
+methods eventually approach correct coverage of $\mu$ as sample size
+increases. Student's $t$ CIs generally does not need relatively large sample
+sizes to achieve correct coverage, except for samples with strong negative
+dependence, in which case, they actually over-cover $\mu$ for smaller sample
+sizes. For instance, for a sample with $n = 100$ and $\phi = -0.4$, the lower
+bound for a Students $t$ CIs coverage of $\mu$ is greater than 95\%, whereas
+the coverage intervals for other methods contain 95\%. In fact, Standard,
+Percentile, $BC$, and $BC_a$, and Proposed Method CIs require similar sample
+sizes to to recover $\mu$ at the nominal level for all combinations of $n$ and
+$\phi$. All methods seem to require a smaller sample to recover $\mu$ at the
+nominal rate when dealing with negative dependence versus positive dependence.
+For example, $BC$ CIs recovers $\mu$ for $n \geq 100$ when $\phi = -0.2$, but
+they only recover $\mu$ for $n \geq 800$ when $\phi = 0.2$. In addition, as a
+negative dependence gets stronger, holding everything else equal, coverage
+increases, which lead to the Student $t$ CI's aforementioned over-coverage. As
+a positive dependence gets stronger, holding everything else equal, coverage
+decreases, and a larger sample is necessary to recover $\mu$.
 
-Based on Figure~\ref{fig:sigma}, Student's $t$ also seems to generally
-be the best method for estimating $\sigma$.
-for $\phi = -0.4$, $n \geq 1600$ is sufficient to recover $\sigma$
-at the nominal level when using
-any CIs besides Standard CIs, which seem to recover $\sigma$ at the nominal 
-rate for all $n \geq 800$, and Student's $t$ CIs, which seem to recover $\sigma$
-at the nominal rate for all $n \geq 400$. For $\phi = -0.2$, $n \geq 200$ is 
-adequate to recover $\sigma$ at the nominal rate with Student $t$ CIs, 
-but other CIs seem to require $n \geq 800$. For $\phi = 0$, or when the sample
-is independently normally distributed, $n \geq 400$ seems to be about enough
-to recover $\sigma$ for all CIs, but Student's $t$ CIs can recover $\sigma$ for
-$n \geq 100$. For $\phi = 0.2$, $n \geq 800$ is adequate for CIs besides the
-Student's $t$ CI, which recovers $\sigma$ well for $n \geq 200$. For 
-$\phi  = 0.4$, $n \geq 1600$ seems necessary for CIs other that Student's $t$ 
-CIs, which recover $\sigma$ at the nominal level for $n \geq 400$.
+For estimating the standard deviation parameter~$\sigma_x$,
+Figure~\ref{fig:sigma} suggests that each method can reach nominal coverage of
+$\sigma_x$ if the sample is large enough, but for a given $n$ and $\phi$,
+coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general. Like
+$\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample sizes
+when compared to other methods, and there is no over-coverage issue for
+$\phi = -0.4$. Standard, Percentile, $BC$, $BC_a$, and Proposed Method CIs
+again have similar performance. All methods seem to have slightly higher
+coverage of $\sigma_x$ when $\phi$ is negative versus when $\phi$ is positive.
+Regardless of the sign, coverage of $\sigma_x$ gets worse as the strength of
+the temporal dependence increases.
 
-Based on Figure~\ref{fig:phi}, Student's $t$ again seems to generally
-be the best method for estimating $\phi$. For high absolute values of $\phi$, 
-Percentile, $BC$, and $BC_a$ CIs
-deteriorate in coverage as $n$ increases. For $\phi = -0.4$, Standard, Student's
-$t$, and Proposed CIs recover $\phi$ for $n \geq 100$. For $\phi = -0.2$, 
-Standard and Proposed CIs recover $\phi$ at the nominal rate for $n \geq 200$, 
-whereas this can be done for $n \geq 100$ with Student's $t$ CIs. For $\phi = 
-0$, or when the sample
-is independently normally distributed, Standard and Proposed CIs recover 
-$\phi$ at the nominal level  for $n \geq 400$, and this is achievable for 
-$n \geq 100$ with Student's $t$ CIs. For $\phi = 0.2$ and $\phi = 0.4$, Standard 
-and Proposed CIs recover $\phi$ for $n \geq 200$, and Student's $t$ CIs 
-recover $\phi$ for all $n \geq 100$.
+For estimating the auto-correlation parameter~$\phi$, Figure~\ref{fig:phi}
+suggests that while Standard, Student's $t$, and Proposed Method CIs do
+approach correct coverage as sample size increases, Percentile, $BC$, and
+$BC_a$ CIs deteriorate as sample size increases, especially as the strength of
+the temporal dependence increases. Because of this, only Standard, Student's
+$t$, and Proposed Method CIs should be considered as effective block bootstrap
+methods to estimate $\phi$. Student's $t$ CIs once again can achieve correct
+coverage with smaller sample sizes when compared to Standard and Proposed CIs
+which perform similarly. Student's $t$ CIs can can recover $\phi$ at the
+nominal level for $n \geq 100$ when the sample's temporal dependence is as
+strong as 0.4. Coverage appears to be higher for all methods when the
+dependence is negative rather than positive. Whether or not the dependence is
+negative or positive, coverage of $\phi$ seems to increase slightly as the
+absolute value increases.
 
-To summarize, the CI type chosen should be based on the target parameter. 
-When estimating $\mu$, the Student's $t$ CI seems to have the highest
- coverage
-overall, although that leads to over-coverage for small sample sizes when $\phi$
- is -0.4. For a
-sample with no temporal dependence, the Student's $t$ CI recover $\mu$ 
-very close to the nominal rate even for small sample sizes. For positive $\phi$, a
-larger sample size appears to be necessary regardless of the CI used. In the
-case that $\phi$ is unknown and expected to be greater than $0$, $n > 800$
-may be
-necessary for block bootstrap interval estimation of $\mu$ when using the
-Student's $t$ CI. If $\phi$ is known,
-a lesser sample size may be sufficient. When estimating $\sigma_x$,
-Student's $t$ again has the highest coverage
-rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
-$n > 400$ may be necessary for block bootstrap interval estimation of
-$\sigma_x$ when using the Student's $t$ CI. Again, if $\phi$ is known, a lesser
-sample size may be enough.
-When estimating $\phi$, Percentile, $BC$, and $BC_a$ CIs 
-deteriorate in coverage, indicating they should not be used in this context. 
-Increasing $n$ will not fix the performance of either of these intervals 
-because the assumption that the coverage rate will approach the nominal level
-as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix
-the
-deterioration problem, and they perform similarly, but Student's $t$ covers
-$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
-$n = 100$ is certainly large enough to
-recover $\phi$ when using the Student's $t$ method.
+To summarize, the CI type chosen should be based on the target parameter. When
+estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
+perform noticeably better than the others. However, when estimating $\phi$,
+the choice of method is of utmost importance as to avoid coverage
+deterioration. A smaller sample size is generally required to estimate a
+parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the
+same magnitude. In order to know if coverage will increase as the strength of
+the temporal dependence increases, one must know what the parameter of
+interest is, and in the case of $\mu$: $\phi$'s sign.
 
@@
   \caption{100 replicate Percentile, Bias-Corrected, and Proposed Method
-  Bootstrap CIs for samples of $n = 800$ for
-    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper
-    bounds
-    of the CIs are displayed, as well as $\hat\theta_n$ (blue) and $
-    \bar\theta_n^{(b)}$ (red). }
+    Bootstrap CIs for samples of $n = 800$ for an AR(1) process with
+    $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs
+    are displayed, as well as $\hat\theta_n$ (blue) and $\bar\theta_n^{(b)}$
+    (red). }
   \label{fig:npi}
@@
 These results beg the question of why certain methods perform poorly. To
-address 
-this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed 
-methods were constructed. As shown in Figure~\ref{fig:npi}, Percentile CIs
-appear to suffer from bias; specifically, they seem to heavily underestimate
-$\phi$. $BC$ CIs do seem to correct this bias on average, but the width of the
-CIs is very inconsistent. Our proposed CIs correct the bias using 
-$\widehat{\text{bias}} = \bar\theta_n^{(b)} -  \hat\theta_n$,
-which seems to usually be negative, indicating a positive 
-correction from interval construction in Section~\ref{sec:bbci}.
+address this question, plots of 100 CIs using each of the Percentile, $BC$,
+and Proposed methods were constructed. As shown in Figure~\ref{fig:npi},
+Percentile CIs appear to suffer from bias; specifically, they seem to heavily
+underestimate $\phi$. $BC$ CIs do seem to correct this bias on average, but
+the width of the CIs is very inconsistent. Our proposed CIs correct the bias
+using $\widehat{\text{bias}} = \bar\theta_n^{(b)} -  \hat\theta_n$, which
+seems to usually be negative, indicating a positive correction from interval
+construction in Section~\ref{sec:bbci}.
 
@@
 
-\jy{Keep the tex source tidy. Clean it up.}
+\jy{Keep the tex source tidy. Clean it up.}\mc{addressed}
 
-Block bootstrap is a useful method for estimating parameters of a time
-series, from simple parameters like the mean to more complicated temporal
- dependence factors.
- We know theoretically that the block bootstrap procedure will cover
-  parameter of a time series at the nominal level given an
- infinitely large
-sample, so the goal for this study was to find the smallest finite
-sample length $n$ of a time series in order for the block bootstrap procedure
-to 
+Block bootstrap is a useful method for estimating parameters of a time series,
+from simple parameters like the mean to more complicated temporal dependence
+factors. We know theoretically that the block bootstrap procedure will cover
+parameter of a time series at the nominal level given an infinitely large
+sample, so the goal for this study was to find the smallest finite sample
+length $n$ of a time series in order for the block bootstrap procedure to 
 recover its associated parameters at an acceptable rate.
 
-Again, this analysis relies on the assumption that
-there is a size $n$ large enough for the method to work: that is, the method's
-performance improves as $n$ increases. Out of the five types of intervals used
-in this study, this assumption was found to hold true with respect to
-estimating $\phi$ only for Standard, Student's $t$, and Proposed Method CIs, 
-whereas Percentile, 
-$BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
-increased. The Percentile CI's coverage deterioration can be attributed to
-bias that is not corrected as $n$ increases. Specifically, as $n$ increases, 
-the width of the CI decreases, but because the Percentile CI
-underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct
-the 
-bias, but the width of the CI seems to be inconsistent. The acceleration 
-factor of the $BC_a$ CI seems to fail, as the width of the CI
-seems to be inconsistent.
+Again, this analysis relies on the assumption that there is a size $n$ large
+enough for the method to work: that is, the method's performance improves as
+$n$ increases. Out of the five types of intervals used in this study, this
+assumption was found to hold true with respect to estimating $\phi$ only for
+Standard, Student's $t$, and Proposed Method CIs, whereas Percentile, $BC$,
+and $BC_a$ intervals exhibited coverage deterioration as $n$ increased. The
+Percentile CI's coverage deterioration can be attributed to bias that is not
+corrected as $n$ increases. Specifically, as $n$ increases, the width of the
+CI decreases, but because the Percentile CI underestimates $\phi$, the
+coverage decreases. The $BC$ CI seems to correct the bias, but the width of
+the CI seems to be inconsistent. The acceleration factor of the $BC_a$ CI
+seems to fail, as the width of the CI seems to be inconsistent.
 
-When using Student's $t$ intervals and $\phi$ is
-unknown, the results of this study suggest that an $n \geq 800$ may be
-necessary for common practice to estimate simpler parameters like $\mu$ 
-or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
-to
-estimate these parameters. For lower absolute values of $\phi$, a smaller
-$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
-values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
-Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$ when using smaller
-sample sizes, 
-meaning that if $\phi$ is known to have a very negative value, another CI
-may be required.
-However, in real world applications, $\phi$ is
-more commonly found to be positive, so Student's $t$ should still be used
-if $\phi$ is unknown.
-Lastly, to estimate $\phi$, $n \geq 100$ using the 
-Student's $t$ method
- may be sufficient.
-Further investigation may be necessary to see if there are other interval
-corrections that fix the coverage deterioration problem for $\phi$.
+When using Student's $t$ intervals and $\phi$ is unknown, the results of this
+study suggest that an $n \geq 800$ may be necessary for common practice to
+estimate simpler parameters like $\mu$ or $\sigma_x$. If $\phi$ is already
+known, a lesser $n$ may be adequate to estimate these parameters. For lower
+absolute values of $\phi$, a smaller $n$ is sufficient when estimating $\mu$
+or $\sigma$. For negative values of $\phi$, coverage of $\mu$ is higher in
+general. In fact, Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$
+when using smaller sample sizes, meaning that if $\phi$ is known to have a
+very negative value, another CI may be required. However, in real world
+applications, $\phi$ is more commonly found to be positive, so Student's $t$
+should still be used if $\phi$ is unknown. Lastly, to estimate $\phi$,
+$n \geq 100$ using the Student's $t$ method may be sufficient. Further
+investigation may be necessary to see if there are other interval corrections
+that fix the coverage deterioration problem for $\phi$.
 
@@
 bootstrap to be used versus other inference methods. For undergraduate or
-graduate students, block bootstrap is not typically a part of curriculum, but the 
-results of this study can easily be used to demonstrate when it is practical to use 
-this method.
-This information could also prove to be useful for research using block
-bootstrap
-estimation of time series in domains such as econometrics. Future studies
-could investigate if there are types of block bootstrap interval
-construction such as $ABC$ or bootstrap-t intervals
-that would more appropriately recover the parameters of a time
-series. \eds{are there other methods that you know of?} 
-One could also investigate the $n$ needed to make inferences about
-other forms of serially dependent data such as a moving average process.
+graduate students, block bootstrap is not typically a part of curriculum, but
+the results of this study can easily be used to demonstrate when it is
+practical to use this method. This information could also prove to be useful
+for research using block bootstrap estimation of time series in domains such
+as econometrics. Future studies could investigate if there are types of block
+bootstrap interval construction such as $ABC$ or bootstrap-t intervals, or
+alternatives to block bootstrap such as AR-Sieve bootstrap that would more
+appropriately recover the parameters of a time series.
+\eds{are there other methods that you know of?} \mc{mentioned an alternative
+  to block bootstrap}
+One could also investigate the $n$ needed to make inferences about other forms
+of serially dependent data such as a moving average process.
 

### 2023-08-21 Manuscript/manuscript.tex
smoothed simulation and conclusion

@@
 
+\paragraph{A Proposed CI}
 \jy{Can we come up with a good name for the proposed method? Other people may cite this.}\mc{bias-centered? i'm not sure}
-\paragraph{A Proposed CI}
+\jy{How about ``recentered percentile''? It has the same length as the
+  percentile approach but is centered at the point estimate.}
+
 We propose a CI that is centered at the point estimator and uses the variation
@@
 
+\subsection{Design}
 We designed a simulation study to compare the performance of the different
@@
 
-\jy{The results discussion need to be streamlined. The three paragraphs are too
-  similar, and only student's ci is discussed. Questions to consider:
-  1) which methods give the right coverage as sample size increases?
-  2) which methods needs smaller sample sizes to get the right coverage?
-  3) what's the difference between the results in positive and negative
-  dependence?
-  4) how does the result change as dependence gets stronger?
-  } \mc{addressed}
+\subsection{Results}
 
@@
 methods eventually approach correct coverage of $\mu$ as sample size
-increases. Student's $t$ CIs generally does not need relatively large sample
-sizes to achieve correct coverage, except for samples with strong negative
+increases. Student's $t$ CIs appear to need the smallest sample size
+to achieve correct coverage, except for samples with strong negative
 dependence, in which case, they actually over-cover $\mu$ for smaller sample
@@
 bound for a Students $t$ CIs coverage of $\mu$ is greater than 95\%, whereas
-the coverage intervals for other methods contain 95\%. In fact, Standard,
+the coverage intervals for other methods contain 95\%. The standard,
 Percentile, $BC$, and $BC_a$, and Proposed Method CIs require similar sample
@@
 a positive dependence gets stronger, holding everything else equal, coverage
-decreases, and a larger sample is necessary to recover $\mu$.
+decreases, and a larger sample is necessary to recover~$\mu$.
 
 For estimating the standard deviation parameter~$\sigma_x$,
-Figure~\ref{fig:sigma} suggests that each method can reach nominal coverage of
+Figure~\ref{fig:sigma} suggests that every method can reach nominal coverage of
 $\sigma_x$ if the sample is large enough, but for a given $n$ and $\phi$,
@@
 when compared to other methods, and there is no over-coverage issue for
-$\phi = -0.4$. Standard, Percentile, $BC$, $BC_a$, and Proposed Method CIs
+$\phi = -0.4$. Standard, percentile, $BC$, $BC_a$, and Proposed Method CIs
 again have similar performance. All methods seem to have slightly higher
@@
 the temporal dependence increases.
+\jy{Compared to Figure 1, there is no over-coverage in this case. Say someting
+  about this observation.}
 
@@
 
-To summarize, the CI type chosen should be based on the target parameter. When
-estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
-perform noticeably better than the others. However, when estimating $\phi$,
-the choice of method is of utmost importance as to avoid coverage
-deterioration. A smaller sample size is generally required to estimate a
-parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the
-same magnitude. In order to know if coverage will increase as the strength of
-the temporal dependence increases, one must know what the parameter of
-interest is, and in the case of $\mu$: $\phi$'s sign.
+\jy{Use cross for red. Otherwise, they are not distinguishable when printed in b/w.}
 
@@
     $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs
-    are displayed, as well as $\hat\theta_n$ (blue) and $\bar\theta_n^{(b)}$
-    (red). }
+    are displayed, as well as $\hat\theta_n$ (blue circle) and
+    $\bar\theta_n^{(b)}$ (red cross). }
   \label{fig:npi}
@@
 
-These results beg the question of why certain methods perform poorly. To
-address this question, plots of 100 CIs using each of the Percentile, $BC$,
-and Proposed methods were constructed. As shown in Figure~\ref{fig:npi},
-Percentile CIs appear to suffer from bias; specifically, they seem to heavily
-underestimate $\phi$. $BC$ CIs do seem to correct this bias on average, but
-the width of the CIs is very inconsistent. Our proposed CIs correct the bias
-using $\widehat{\text{bias}} = \bar\theta_n^{(b)} -  \hat\theta_n$, which
-seems to usually be negative, indicating a positive correction from interval
-construction in Section~\ref{sec:bbci}.
+\jy{can you also do the same plot for sample size 1600? And then put the two
+  plots in one figure?}
+
+The outcomes of the $\phi$ estimation raise a natural question about the
+lackluster performance of certain methodologies. To delve into this inquiry, a
+set of 100 CIs was generated for each of the percentile,
+$BC$, and Proposed techniques. Illustrated in Figure~\ref{fig:npi}, it becomes
+evident that the percentile-based CIs exhibit a notable bias, predominantly
+manifesting as a substantial underestimation of $\phi$. On the other hand, $BC$
+CIs do display a tendency to rectify this bias on average, albeit accompanied by
+a rather inconsistent width across the intervals. Our proposed CIs manage to
+effectively mitigate the bias, employing $\widehat{\text{bias}} =
+\bar\theta_n^{(b)} - \hat\theta_n$ as a corrective measure. Notably, this
+correction often takes a negative form, indicative of a positive adjustment
+arising from the interval construction detailed in Section~\ref{sec:bbci}.
+
+To summarize, the performance of the CIs depends on the target parameter. When
+estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
+perform noticeably better than the others. However, when estimating $\phi$,
+the choice of method is of utmost importance as to avoid coverage
+deterioration. A smaller sample size is generally required to estimate a
+parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the
+same magnitude. In order to know if coverage will increase as the strength of
+the temporal dependence increases, one need to know what the parameter of
+interest is, and in the case of $\mu$, the direction of the serial dependence.
+\jy{The BC approach appears not correcting the bias correctly. The proposed
+  approach simply does not correct point estimate and only uses the spreadness
+  from the bootstrap to construct CIs.}
 
@@
 \label{sec:disc}
-
-\jy{Keep the tex source tidy. Clean it up.}\mc{addressed}
 
@@
 recover its associated parameters at an acceptable rate.
-
-Again, this analysis relies on the assumption that there is a size $n$ large
+Our analysis relies on the assumption that there is a size $n$ large
 enough for the method to work: that is, the method's performance improves as
@@
 corrected as $n$ increases. Specifically, as $n$ increases, the width of the
-CI decreases, but because the Percentile CI underestimates $\phi$, the
+CI decreases, but because the percentile CI underestimates $\phi$, the
 coverage decreases. The $BC$ CI seems to correct the bias, but the width of
@@
 
+\jy{use a better topic sentence.}
 When using Student's $t$ intervals and $\phi$ is unknown, the results of this
@@
 alternatives to block bootstrap such as AR-Sieve bootstrap that would more
+\jy{Cite references for AR-sieve}
 appropriately recover the parameters of a time series.

### 2023-08-22 Manuscript/manuscript.tex
minor grammar fixes and new paper reference

@@
 \citep{diciccio1996bootstrap, rice2006mathematical}: a standard normal CI, and
-a Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-correct and
+a Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and
 accelerated ($BC_a$) CI, and a CI proposed in this article. Their empirical
@@
 \]
-\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
+%\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
 where $k$ is the number of blocks. This CI is centered by the point estimator
@@
 \paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
-The $BC_a$ CI was first suggested in \citet{efron1987better}.Let
+The $BC_a$ CI was first suggested in \citet{efron1987better}. Let
 $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
@@
 2) $\sigma_x = 1$, the standard deviation of $X_t$; and
-2) $\phi$, the lag-1 auto-correlation coefficient.
+3) $\phi$, the lag-1 auto-correlation coefficient.
 To investigate the effect of sample size~$n$, we considered an array of values
@@
 to exactly match the nominal level, we can construct a 95\% CI of the coverage
-rate (which is an estimate of a proportion with $R = 10000$. If the proportion
+rate (which is an estimate of a proportion with $R = 10000$). If the proportion
 0.95 is included in the interval, the block bootstrap method is likely
@@
 Percentile, $BC$, and $BC_a$, and Proposed Method CIs require similar sample
-sizes to to recover $\mu$ at the nominal level for all combinations of $n$ and
+sizes to recover $\mu$ at the nominal level for all combinations of $n$ and
 $\phi$. All methods seem to require a smaller sample to recover $\mu$ at the
 nominal rate when dealing with negative dependence versus positive dependence.
-For example, $BC$ CIs recovers $\mu$ for $n \geq 100$ when $\phi = -0.2$, but
+For example, $BC$ CIs recover $\mu$ for $n \geq 100$ when $\phi = -0.2$, but
 they only recover $\mu$ for $n \geq 800$ when $\phi = 0.2$. In addition, as a
@@
 appropriately recover the parameters of a time series.
-\eds{are there other methods that you know of?} \mc{mentioned an alternative
-  to block bootstrap}
+
+\eds{Check out this paper:
+Peter Buhlmann. "Bootstraps for Time Series." Statist. Sci. 17(1) 52 - 72, 
+May 2002 - the conclusions of this paper are interesting in their own right:
+``Disadvantages of the [block bootstrap] method include the following.
+The block bootstrap sample should not be viewed as
+a reasonable sample mimicking the data-generating
+process: it is not stationary and exhibits artifacts where
+resampled blocks are linked together. This implies that
+the plug-in rule for bootstrapping an estimator $\hat{\theta}$ is not
+appropriate. A prevectorization of the data is highly
+recommended, but the bootstrapped estimator and its
+computing routine may then need to be redesigned. As
+a general nonparametric scheme, the block bootstrap
+may be outperformed in various niches of stationary
+time series, for example, for linear time series (see Section 3) 
+and for categorical processes (see Section 5).
+Second-order accuracy for a confidence interval has
+been justified with the approach of Studentizing and
+BCa correction (in the case of noncategorical time series); 
+the latter was found to yield marginal improvement in a 
+simulated example (we did not consider the former). }
+
 One could also investigate the $n$ needed to make inferences about other forms

### 2023-08-22 Manuscript/manuscript.tex
inserted missing negative sign in conclusion

@@
 or $\sigma$. For negative values of $\phi$, coverage of $\mu$ is higher in
-general. In fact, Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$
+general. In fact, Student's $t$ seems to over-cover $\mu$ for $\phi = - 0.4$
 when using smaller sample sizes, meaning that if $\phi$ is known to have a

### 2023-08-22 Manuscript/manuscript.tex
Still Need to Address Some Comments

@@
 a Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and
-accelerated ($BC_a$) CI, and a CI proposed in this article. Their empirical
+accelerated ($BC_a$) CI, and a recentered percentile CI proposed in this article.
+Their empirical
 coverage rates at different sample sizes and dependence levels are compared in
@@
 
-\paragraph{A Proposed CI}
-\jy{Can we come up with a good name for the proposed method? Other people may cite this.}\mc{bias-centered? i'm not sure}
+\paragraph{Recentered Percentile CI}
+\jy{Can we come up with a good name for the proposed method? Other people may cite this.} \mc{bias-centered? i'm not sure}
 \jy{How about ``recentered percentile''? It has the same length as the
-  percentile approach but is centered at the point estimate.}
+  percentile approach but is centered at the point estimate.} \mc{replaced "proposed
+  method" with "recentered"}
 
@@
 \]
-It is asymmetric, as different critical values are used to compute
-the lower and upper bounds.
+It is not necessarily symmetric, as different critical values are used to compute
+the lower and upper bounds. It has the same width as the Percentile CI.
 
@@
 bound for a Students $t$ CIs coverage of $\mu$ is greater than 95\%, whereas
-the coverage intervals for other methods contain 95\%. The standard,
-Percentile, $BC$, and $BC_a$, and Proposed Method CIs require similar sample
+the coverage intervals for other methods contain 95\%. The Standard,
+Percentile, $BC$, and $BC_a$, and Recentered CIs require similar sample
 sizes to recover $\mu$ at the nominal level for all combinations of $n$ and
@@
 $\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample sizes
-when compared to other methods, and there is no over-coverage issue for
-$\phi = -0.4$. Standard, percentile, $BC$, $BC_a$, and Proposed Method CIs
-again have similar performance. All methods seem to have slightly higher
+when compared to other methods. Unlike $\mu$, there is no over-coverage issue for
+$\sigma$ when $\phi = -0.4$. Standard, Percentile, $BC$, $BC_a$, and Recentered
+CIs again have similar performance. All methods seem to have slightly higher
 coverage of $\sigma_x$ when $\phi$ is negative versus when $\phi$ is positive.
@@
 \jy{Compared to Figure 1, there is no over-coverage in this case. Say someting
-  about this observation.}
+  about this observation.} \mc{addressed}
 
 For estimating the auto-correlation parameter~$\phi$, Figure~\ref{fig:phi}
-suggests that while Standard, Student's $t$, and Proposed Method CIs do
+suggests that while Standard, Student's $t$, and Recentered CIs do
 approach correct coverage as sample size increases, Percentile, $BC$, and
@@
 the temporal dependence increases. Because of this, only Standard, Student's
-$t$, and Proposed Method CIs should be considered as effective block bootstrap
+$t$, and Recentered CIs should be considered as effective block bootstrap
 methods to estimate $\phi$. Student's $t$ CIs once again can achieve correct
-coverage with smaller sample sizes when compared to Standard and Proposed CIs
+coverage with smaller sample sizes when compared to Standard and Recentered CIs
 which perform similarly. Student's $t$ CIs can can recover $\phi$ at the
@@
 negative or positive, coverage of $\phi$ seems to increase slightly as the
-absolute value increases.
+absolute value increases for Standard, Student's $t$, and Recentereed CIs. For the
+values of $\phi$ observed, there are no examples
+of over-coverage for Standard, Student's $t$, $BC$, $BC_a$, or Recentered CIs.
+However, Percentile CIs appear to over-cover $\phi$ for smaller sample sizes when 
+$\phi = -0.2$ and when $\phi = 0$, indicating again that they should not be used.
 
 \jy{Use cross for red. Otherwise, they are not distinguishable when printed in b/w.}
+\mc{addressed}
 
@@
   \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
-  \caption{100 replicate Percentile, Bias-Corrected, and Proposed Method
+  \caption{100 replicate Percentile, Bias-Corrected, and Recentered
     Bootstrap CIs for samples of $n = 800$ for an AR(1) process with
@@
 \jy{can you also do the same plot for sample size 1600? And then put the two
-  plots in one figure?}
+  plots in one figure?} \mc{addressed}
 
@@
 set of 100 CIs was generated for each of the percentile,
-$BC$, and Proposed techniques. Illustrated in Figure~\ref{fig:npi}, it becomes
+$BC$, and Recentered techniques. Illustrated in Figure~\ref{fig:npi}, it becomes
 evident that the percentile-based CIs exhibit a notable bias, predominantly
@@
 CIs do display a tendency to rectify this bias on average, albeit accompanied by
-a rather inconsistent width across the intervals. Our proposed CIs manage to
+a rather inconsistent width across the intervals. Our Recentered CIs manage to
 effectively mitigate the bias, employing $\widehat{\text{bias}} =
@@
 the temporal dependence increases, one need to know what the parameter of
-interest is, and in the case of $\mu$, the direction of the serial dependence.
-\jy{The BC approach appears not correcting the bias correctly. The proposed
+interest is, and in the case of $\mu$, the direction of the serial dependence. The
+$BC$ approach does not seem to be correcting bias appropriately when estimating
+$\phi$. Like the Percentile method, the Recentered method uses the spread from the 
+bootstrap to construct the width of the CI. However, the Recentered approach, does
+not correct from the original point estimate $\hat\theta_n$.
+\jy{The BC approach appears not correcting the bias correctly. The Recentered
   approach simply does not correct point estimate and only uses the spreadness
-  from the bootstrap to construct CIs.}
+  from the bootstrap to construct CIs.} \mc{addressed}
 
@@
 assumption was found to hold true with respect to estimating $\phi$ only for
-Standard, Student's $t$, and Proposed Method CIs, whereas Percentile, $BC$,
+Standard, Student's $t$, and Recentered Method CIs, whereas Percentile, $BC$,
 and $BC_a$ intervals exhibited coverage deterioration as $n$ increased. The
@@
 \jy{use a better topic sentence.}
-When using Student's $t$ intervals and $\phi$ is unknown, the results of this
-study suggest that an $n \geq 800$ may be necessary for common practice to
+One of the goals of this study was to provide practical recommendations for 
+necessary sample sizes when using block bootstrap to estimate parameters of 
+serially dependent data. When using Student's $t$ intervals and $\phi$ is unknown,
+the results of this study suggest that an $n \geq 800$ may be necessary for common practice to
 estimate simpler parameters like $\mu$ or $\sigma_x$. If $\phi$ is already

### 2023-08-22 Code/functions.R

@@ -125,7 +125,7 @@ mychk <- function(sim, target) {
 graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 {
   data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
-                    labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Proposed'))
+                    labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Recentered'))
   
   ggplot(data, aes(x = n, y = cov)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
@@ -136,5 +136,5 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
     scale_y_continuous(trans=trans)
-  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), height = 5)
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), height = 6)
 }

### 2023-08-22 Code/phi_intervals.R

@@ -6,27 +6,51 @@ sim <- replicate(50, do1rep(800, 0.4, mystat, 10))
 new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
 
 file_titles <- c("pct", "bc", "prop")
-custom_titles <- c("Percentile", "Bias-Corrected", "Proposed")
+custom_titles <- c("Percentile", "Bias-Corrected", "Recentered")
 
 # Create a data frame for plotting
-plot_data <- data.frame(replication = 1:50,
+plot_data_800 <- data.frame(replication = 1:50,
                         point_estimate = new_sim[1, ],
                         bts_mean = new_sim[2, ],
                         lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
                         upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
                         file_title = rep(file_titles, each = 50),
-                        custom_title = rep(custom_titles, each = 50))
+                        custom_title = rep(custom_titles, each = 50),
+                        sample.size = rep("n = 800", 150))
+
+set.seed(1234)
+sim <- replicate(50, do1rep(1600, 0.4, mystat, 10))
+new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
+
+# Create a data frame for plotting
+plot_data_1600 <- data.frame(replication = 1:50,
+                          point_estimate = new_sim[1, ],
+                          bts_mean = new_sim[2, ],
+                          lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
+                          upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
+                          file_title = rep(file_titles, each = 50),
+                          custom_title = rep(custom_titles, each = 50),
+                          sample.size = rep("n = 1600", 150))
+
+plot_data <- rbind(plot_data_800, plot_data_1600)
 
 # Create facet plot using ggplot2
+plot_data$custom_title <- factor(plot_data$custom_title, 
+                  levels = c("Percentile", "Bias-Corrected", "Recentered"))
+
+plot_data$sample.size <- factor(plot_data$sample.size,
+                  levels = c("n = 800", "n = 1600"))
+
 ggplot(plot_data, aes(x = replication, y = point_estimate)) +
[…]

### 2023-08-22 Manuscript/manuscript.tex
Two New References

@@
 \paragraph{Recentered Percentile CI}
-\jy{Can we come up with a good name for the proposed method? Other people may cite this.} \mc{bias-centered? i'm not sure}
+\jy{Can we come up with a good name for the proposed method? Other people may
+ cite this.} \mc{bias-centered? i'm not sure}
 \jy{How about ``recentered percentile''? It has the same length as the
-  percentile approach but is centered at the point estimate.} \mc{replaced "proposed
+  percentile approach but is centered at the point estimate.} \mc{replaced
+  all instances of "proposed
   method" with "recentered"}
@@
 
-\jy{use a better topic sentence.}
-One of the goals of this study was to provide practical recommendations for 
+\jy{use a better topic sentence.} \mc{addressed}
+One of the goals of this study was to provide some practical recommendations for 
 necessary sample sizes when using block bootstrap to estimate parameters of 
@@
 for research using block bootstrap estimation of time series in domains such
-as econometrics. Future studies could investigate if there are types of block
+as econometrics. Future studies could investigate the $n$ needed to make
+inferences about other forms
+of serially dependent data such as a moving average process. One could also
+investigate if there are types of block
 bootstrap interval construction such as $ABC$ or bootstrap-t intervals, or
-alternatives to block bootstrap such as AR-Sieve bootstrap that would more
-\jy{Cite references for AR-sieve}
-appropriately recover the parameters of a time series.
+alternatives to block bootstrap, such as AR-Sieve bootstrap
+ \citep{kreiss1992bootstrap}, that would more
+\jy{Cite references for AR-sieve} \mc{addressed}
+appropriately recover the parameters of a time series. In addition, as noted by
+\citet{buhlmann2002bootstraps}, there are some 
+general drawbacks of block bootstrap - with respect to how reasonably it imitates 
+the data-generating process - which may be addressed in a future study.
 
@@
 the latter was found to yield marginal improvement in a 
-simulated example (we did not consider the former). }
-
-One could also investigate the $n$ needed to make inferences about other forms
-of serially dependent data such as a moving average process.
+simulated example (we did not consider the former). } \mc{addressed}
 

### 2023-08-25 Manuscript/manuscript.tex
Fixed Reference
interpretation of the lackluster and comments on notations

@@
 used block bootstrap confidence intervals including the percentile intervals
-and Bias-Corrected intervals.
+and bias-corrected intervals.
 
@@
 inferences about dependent data. Essentially, it depends on correct estimation
-of the uncertainty in the estimation. Early ideas were developed by
-\citet{hall1985resampling, carlstein1986use,kunsch1989jackknife}. It has since
+of the uncertainty in the estimation, similar to the standard bootstrap
+\citep{efron1979bootstrap} but for serially dependent data. Early ideas of block
+bootstrap were developed not long after the startard bootstrap 
+\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife}. It has since
 been applied in various fields, for instance, econometrics
@@
 a Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and
-accelerated ($BC_a$) CI, and a recentered percentile CI proposed in this article.
+accelerated CI, and a recentered percentile CI proposed in this article.
 Their empirical
@@
 
-\subsection{Bootstrap CIs}
+\subsection{Block Bootstrap CIs}
 
@@
 point estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. We
-consider six kinds of CIs.
+consider six kinds of block bootstrap CIs adapted from standard bootstrap CIs.
 
@@
 The percentile CI was first suggested in \citet{efron1979bootstrap}.
-Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
+\jy{The previous superscript does not make sense because
+  $b \in \{1, \ldots,  B\}$. Make similar changes to other places as needed.}
+Let $\hat\theta_{n, \alpha}^B$ be the empirical $100\alpha$th percentile of
 $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)100\%$
@@
 
-\paragraph{Bias Corrected ($BC$) Bootstrap CI}
+\paragraph{Bias Corrected (BC) CI}
 The procedure for constructing a Bias Corrected Bootstrap CI based on standard
@@
 
-\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
-The $BC_a$ CI was first suggested in \citet{efron1987better}. Let
+\paragraph{Bias Corrected and Accelerated (BCA) CI}
+The BCA CI was first suggested in \citet{efron1987better}. Let
 $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
@@
 This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
-$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
+BCA method corrects for bias and skewness of the $B$ bootstrap point
 estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
@@
 \paragraph{Recentered Percentile CI}
-\jy{Can we come up with a good name for the proposed method? Other people may
- cite this.} \mc{bias-centered? i'm not sure}
-\jy{How about ``recentered percentile''? It has the same length as the
-  percentile approach but is centered at the point estimate.} \mc{replaced
-  all instances of "proposed
-  method" with "recentered"}
 
@@
 in the bootstrap estimates to construct the error bound. This interval requires
-the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
+\jy{Note the notation change and do a thorough check}
+the computation of
+$\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the mean of all bootstrap point
 estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$. A
@@
 bound for a Students $t$ CIs coverage of $\mu$ is greater than 95\%, whereas
-the coverage intervals for other methods contain 95\%. The Standard,
-Percentile, $BC$, and $BC_a$, and Recentered CIs require similar sample
+the coverage intervals for other methods contain 95\%. The standard,
+percentile, BC, and BCA, and recentered percentile CIs require similar sample
 sizes to recover $\mu$ at the nominal level for all combinations of $n$ and
@@
 nominal rate when dealing with negative dependence versus positive dependence.
-For example, $BC$ CIs recover $\mu$ for $n \geq 100$ when $\phi = -0.2$, but
+For example, BC CIs recover $\mu$ for $n \geq 100$ when $\phi = -0.2$, but
 they only recover $\mu$ for $n \geq 800$ when $\phi = 0.2$. In addition, as a
@@
 when compared to other methods. Unlike $\mu$, there is no over-coverage issue for
-$\sigma$ when $\phi = -0.4$. Standard, Percentile, $BC$, $BC_a$, and Recentered
+$\sigma$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and recentered percentile
 CIs again have similar performance. All methods seem to have slightly higher
@@
 For estimating the auto-correlation parameter~$\phi$, Figure~\ref{fig:phi}
-suggests that while Standard, Student's $t$, and Recentered CIs do
-approach correct coverage as sample size increases, Percentile, $BC$, and
-$BC_a$ CIs deteriorate as sample size increases, especially as the strength of
+suggests that while standard, Student's $t$, and recentered percentile CIs do
+approach correct coverage as sample size increases, Percentile, BC, and
+BCA CIs deteriorate as sample size increases, especially as the strength of
 the temporal dependence increases. Because of this, only Standard, Student's
-$t$, and Recentered CIs should be considered as effective block bootstrap
+$t$, and recentered percentile CIs should be considered as effective block bootstrap
 methods to estimate $\phi$. Student's $t$ CIs once again can achieve correct
-coverage with smaller sample sizes when compared to Standard and Recentered CIs
+coverage with smaller sample sizes when compared to standard and recentered percentile CIs
 which perform similarly. Student's $t$ CIs can can recover $\phi$ at the
@@
 negative or positive, coverage of $\phi$ seems to increase slightly as the
-absolute value increases for Standard, Student's $t$, and Recentereed CIs. For the
-values of $\phi$ observed, there are no examples
-of over-coverage for Standard, Student's $t$, $BC$, $BC_a$, or Recentered CIs.
+absolute value increases for standard, Student's $t$, and recentereed percentile
+CIs. For the values of $\phi$ observed, there are no examples
+of over-coverage for standard, Student's $t$, BC, BCA, or recentered percentile CIs.
 However, Percentile CIs appear to over-cover $\phi$ for smaller sample sizes when 
@@
 
-\jy{Use cross for red. Otherwise, they are not distinguishable when printed in b/w.}
-\mc{addressed}
+\jy{check for no uppercases for recentered percentile, etc. throughout}
 
@@
   \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
-  \caption{100 replicate Percentile, Bias-Corrected, and Recentered
-    Bootstrap CIs for samples of $n = 800$ for an AR(1) process with
+  \caption{50 replicate percentile, BC, and recentered percentile
+    CIs for samples of $n \in \{800, 1600\}$ for an AR(1) process with
     $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs
@@
 
-\jy{can you also do the same plot for sample size 1600? And then put the two
-  plots in one figure?} \mc{addressed}
+\jy{The red cross is not $\theta_n^{(b)}$, but their average over
+  $b = 1,  \ldots, B$. Define this as bootstrap point estimate in section 2.2
+  for ease of referencing in the discussion.}
+
+\jy{Keep the interval labels consistent in figure and in the text}
 
@@
 lackluster performance of certain methodologies. To delve into this inquiry, a
-set of 100 CIs was generated for each of the percentile,
-$BC$, and Recentered techniques. Illustrated in Figure~\ref{fig:npi}, it becomes
+set of 50 CIs was generated for each of the percentile, BC, and recentered
+percentile  approaches. Illustrated in Figure~\ref{fig:npi}, it becomes
 evident that the percentile-based CIs exhibit a notable bias, predominantly
-manifesting as a substantial underestimation of $\phi$. On the other hand, $BC$
-CIs do display a tendency to rectify this bias on average, albeit accompanied by
-a rather inconsistent width across the intervals. Our Recentered CIs manage to
-effectively mitigate the bias, employing $\widehat{\text{bias}} =
-\bar\theta_n^{(b)} - \hat\theta_n$ as a corrective measure. Notably, this
-correction often takes a negative form, indicative of a positive adjustment
-arising from the interval construction detailed in Section~\ref{sec:bbci}.
+manifesting as a substantial underestimation of $\phi$ with point estimator
+$\bar\theta_n^B$, that is, the average of $B$ bootstrap point estimate. As the
+sample size increases from 800 to 1600, this bias does not vanish while the
+uncertainty reduces, which explains why the coverage rates deteriorate. The bias
+in $\bar\theta_n^N$ also appears to invalidate the bias correction in the BC
+bootstrap, leading to the poor performance of the BC intervals. The BCA
+intervals have the same problem as the BC intervals in the bias-correction step.
+The root of the issue appears to be that the autocorrelation in the block
+bootstrap samples is somehow smaller compared to that in the original sample.
+On the other hand, the original point estimate $\hat\phi_n$ is asymptotically
+unbiased. Since the uncertainty in the bootstrap point estimates
+$\hat\theta_n^{(b)}$, $b = 1, \ldots, B$, the percentile CIs recentered at the
+point estimate provide desired coverage.
 
@@
 interest is, and in the case of $\mu$, the direction of the serial dependence. The
-$BC$ approach does not seem to be correcting bias appropriately when estimating
-$\phi$. Like the Percentile method, the Recentered method uses the spread from the 
-bootstrap to construct the width of the CI. However, the Recentered approach, does
+BC approach does not seem to be correcting bias appropriately when estimating
+$\phi$. Like the percentile method, the recentered percentile method uses the spread from the 
+bootstrap to construct the width of the CI. However, the recentered approach, does
 not correct from the original point estimate $\hat\theta_n$.
-\jy{The BC approach appears not correcting the bias correctly. The Recentered
-  approach simply does not correct point estimate and only uses the spreadness
-  from the bootstrap to construct CIs.} \mc{addressed}
 
@@
 assumption was found to hold true with respect to estimating $\phi$ only for
-Standard, Student's $t$, and Recentered Method CIs, whereas Percentile, $BC$,
-and $BC_a$ intervals exhibited coverage deterioration as $n$ increased. The
+Standard, Student's $t$, and Recentered Method CIs, whereas Percentile, BC,
+and BCA intervals exhibited coverage deterioration as $n$ increased. The
 Percentile CI's coverage deterioration can be attributed to bias that is not
@@
 CI decreases, but because the percentile CI underestimates $\phi$, the
-coverage decreases. The $BC$ CI seems to correct the bias, but the width of
-the CI seems to be inconsistent. The acceleration factor of the $BC_a$ CI
+coverage decreases. The BC CI seems to correct the bias, but the width of
+6the CI seems to be inconsistent. The acceleration factor of the BCA CI
 seems to fail, as the width of the CI seems to be inconsistent.
@@
 alternatives to block bootstrap, such as AR-Sieve bootstrap
- \citep{kreiss1992bootstrap}, that would more
+ \citep{kreiss1992bootstrap}, that could more
 \jy{Cite references for AR-sieve} \mc{addressed}
@@
 been justified with the approach of Studentizing and
-BCa correction (in the case of noncategorical time series); 
+BCA correction (in the case of noncategorical time series); 
 the latter was found to yield marginal improvement in a 

### 2023-08-25 Manuscript/manuscript.tex
Update

@@
 should provide valid confidence intervals as the length of the time series goes
-to infinity. In practice, however, it is necessary to know how large of a
-finite sample is required for block bootstrap confidence intervals to work
-well. This study aims to answer this question in a simple simulation setting
-where the data are generated from a first-order autoregressive process. The
-empirical coverage rates of several commonly used bootstrap confidence
-intervals for the mean, standard deviation, and the lag-1 autocorrelation
-coefficient are compared. A quite large sample is found necessary for the
-intervals to have the right coverage rates even when estimating a simple
-parameter like the mean. Some block bootstrap methods could fail when
-estimating the lag-1 autocorrelation. It is surprising that the coverage
-property even deteriorates as the sample size increases with some commonly
-used block bootstrap confidence intervals including the percentile intervals
-and bias-corrected intervals.
+to infinity. In practice, however, it is necessary to know how large of a finite 
+sample is required for block bootstrap confidence intervals to work well. This 
+study aims to answer this question in a simple simulation setting where the data 
+are generated from a first-order autoregressive process. The empirical coverage 
+rates of several commonly used bootstrap confidence intervals for the mean, 
+standard deviation, and the lag-1 autocorrelation coefficient are compared. A 
+quite large sample is found necessary for the intervals to have the right 
+coverage rates even when estimating a simple parameter like the mean. Some block 
+bootstrap methods could fail when estimating the lag-1 autocorrelation. It is 
+surprising that the coverage property even deteriorates as the sample size 
+increases with some commonly used block bootstrap confidence intervals including 
+the percentile intervals and bias-corrected intervals.
 
@@
 \citep{efron1979bootstrap} but for serially dependent data. Early ideas of block
-bootstrap were developed not long after the startard bootstrap 
+bootstrap were developed not long after the standard bootstrap 
 \citep{hall1985resampling, carlstein1986use,kunsch1989jackknife}. It has since
@@
 \citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
-Block bootstrap is especially useful for serially dependent data when the
-serial dependence is not specified or not of primary interest. The method is
-expected to produce CIs with coverage rates matching their nominal levels as
-the sample size grows. However, when dealing with finite sample sizes, an
-important question is how large the sample size must be for block bootstrap
-CIs to have the desired coverage rates.
+Block bootstrap is especially useful for serially dependent data when the serial 
+dependence is not specified or not of primary interest. The method is expected 
+to produce CIs with coverage rates matching their nominal levels as the sample 
+size grows. However, when dealing with finite sample sizes, an important 
+question is how large the sample size must be for block bootstrap CIs to have 
+the desired coverage rates.
 
@@
 bootstrap standard errors in providing accurate uncertainty measures. For 
-example, \citet{hesterberg2015teachers} observes that while percentile-based
-CIs for the mean parameter are more accurate than $t$-intervals for larger
-sample sizes, they accuracy diminishes for smaller sample sizes. The optimal
-parameter estimation of a distribution, according to
-\citet{chernick2009revisiting}, depends on the sample size, the number of
-bootstrap replicates, and the confidence level. In structural equation
-modeling, \citet{nevitt2001performance} find that a sample size of 200--1000
-is sufficient for interval estimation using standard nonparametric bootstrap.
-Estimating variance component, \citet{burch2012nonparametric} report that as
-the sample size increases under a normal distribution, nonparametric bootstrap
-methods approach the coverage of a pivotal quantity as the sample size, but
-for other distributions, the coverage can deteriorate. In estimating the
-correlation coefficient of bivariate normal data, \citet{puth2015variety} note
-that even for a sample size of~$100$ with true correlation coefficient~0,
-bootstrap methods are less accurate than the Fisher's transformation. The
-prevailing consensus highlights the necessity of a substantial sample size for
-bootstrap CIs to attain the desired coverage.
+example, \citet{hesterberg2015teachers} observes that while percentile-based CIs 
+for the mean parameter are more accurate than $t$-intervals for larger sample 
+sizes, their accuracy diminishes for smaller sample sizes. The optimal parameter 
+estimation of a distribution, according to \citet{chernick2009revisiting}, 
+depends on the sample size, the number of bootstrap replicates, and the 
+confidence level. In structural equation modeling, \citet{nevitt2001performance} 
+find that a sample size of 200--1000 is sufficient for interval estimation using 
+standard nonparametric bootstrap. In estimating variance components, 
+\citet{burch2012nonparametric} reports that as the sample size increases under a 
+normal distribution, nonparametric bootstrap methods approach the coverage of a 
+pivotal quantity, but for other distributions, the coverage can deteriorate. In 
+estimating the correlation coefficient of bivariate normal data, 
+\citet{puth2015variety} note that even for a sample size of~$100$ with true 
+correlation coefficient~0, bootstrap methods are less accurate than the Fisher's 
+transformation. The prevailing consensus highlights the necessity of a 
+substantial sample size for bootstrap CIs to attain the desired coverage.
 
 Limited research has offered practical guidance concerning the requisite sample
-size for employing block bootstrap inference with dependent data. In the
-context of linear regression involving dependent data, where regression errors
-stem from a homoscedastic autoregressive process of order-1, the investigation
-conducted by \citet{goncalves2005bootstrap} reveals that, in cases of small
-sample sizes, standard error estimates derived from the moving block bootstrap
-approach may demonstrate greater accuracy than those based on closed-form
-asymptotic estimates. Nonetheless, even when considering a substantial sample
-size of ~$1024$, confidence intervals generated through the moving block
-bootstrap method still fail to adequately encompass the target parameter. The
-scarcity of existing literature addressing the necessary sample sizes
-conducive to the efficacy of block bootstrap techniques has spurred the
-initiation of the present study.
+size for employing block bootstrap inference with dependent data. In the context 
+of linear regression involving dependent data, where regression errors stem from 
+a homoscedastic autoregressive process of order-1, the investigation conducted 
+by \citet{goncalves2005bootstrap} reveals that, in cases of small sample sizes, 
+standard error estimates derived from the moving block bootstrap approach may 
+demonstrate greater accuracy than those based on closed-form asymptotic 
+estimates. Nonetheless, even when considering a substantial sample size of 
+~$1024$, confidence intervals generated through the moving block bootstrap 
+method still fail to adequately encompass the target parameter. The scarcity of 
+existing literature addressing the necessary sample sizes conducive to the 
+efficacy of block bootstrap techniques has spurred the initiation of the present 
+study.
 
@@
 a stationary time series, where the parameters of interests are the mean, 
-standard deviation, and the first-order autocorrelation coefficient. We
-compare six variants of block bootstrap CIs from the literature
-\citep{diciccio1996bootstrap, rice2006mathematical}: a standard normal CI, and
-a Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and
-accelerated CI, and a recentered percentile CI proposed in this article.
-Their empirical
-coverage rates at different sample sizes and dependence levels are compared in
-a simulation study. The results of this study suggest that recovery of
-temporal dependence parameters is reliant on the type of interval used.
+standard deviation, and the first-order autocorrelation coefficient. We compare 
+six variants of block bootstrap CIs from the literature
+\citep{diciccio1996bootstrap, rice2006mathematical}: a standard normal CI, a 
+Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and 
+accelerated CI, and a recentered percentile CI proposed in this article. Their 
+empirical coverage rates at different sample sizes and dependence levels are 
+compared in a simulation study. The results of this study suggest that recovery 
+of temporal dependence parameters is reliant on the type of interval used.
 
@@
 reviews block bootstrap procedures and how to use block bootstrap estimates to
-construct CIs; a simple CI obtained by recentering at the point estimate is
-proposed for comparison. Section~\ref{sec:simu} reports a simulation study
-comparing the coverage rates of six block bootstrap CIs. A discussion
+construct CIs; a simple CI obtained by recentering at the original point 
+estimate is proposed for comparison. Section~\ref{sec:simu} reports a simulation 
+study comparing the coverage rates of six block bootstrap CIs. A discussion
 concludes in Section~\ref{sec:disc}.
@@
 construct CIs. If the observations in the series were independent, a standard
-nonparametric bootstrap procedure would draw a large number~$B$ bootstrap
-copies of the observed data, and calculate an estimate $\hat\theta_n^{(b)}$
-for each copy $b = 1, \ldots, B$. The uncertainty of $\hat\theta_n$ is then
-estimated by the empirical uncertainty of the $\hat\theta_n^{(b)}$'s. When
-serial dependence is present, the bootstrap procedure needs to preserve the
-serial dependence. Block bootstrap was motivated for this situation.
+nonparametric bootstrap procedure would draw a large number~$B$ bootstrap copies 
+of the observed data, and calculate a bootstrap point estimate 
+$\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. The uncertainty of 
+$\hat\theta_n$ is then estimated by the empirical uncertainty of the bootstrap 
+point estimates. When serial dependence is present, the bootstrap procedure 
+needs to preserve the serial dependence. Block bootstrap was motivated for this 
+situation.
 
@@
 partitioning the data into blocks and performing bootstrap on the blocks. In
-particular, consider block size~$l$ and, for convenience, suppose that $n$ is
-a multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$ is
+particular, consider block size~$l$ and, for convenience, suppose that $n$ is a 
+multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$ is
 $Y_j = \{X_{(j - 1) l + 1}, \ldots, X_{(j - 1) l + l}\}$, $j = 1, \ldots, k$.
 Then, we sample $k$ blocks of $Y_j$'s from the set $\{Y_1, \ldots, Y_k\}$ with
-replacement and concatenate the $k$ sampled blocks in the order they are
-picked to form a bootstrap sample of the data. The formation of the bootstrap
-sample ensures that the between-block dependence is weak and that the
-within-block serial dependence is preserved. Because the blocks here are
-non-overlapping, this bootstrap approach is known as non-overlapping block
-bootstrap, or simple block bootstrap.
+replacement and concatenate the $k$ sampled blocks in the order they are picked 
+to form a bootstrap sample of the data. The formation of the bootstrap sample 
+ensures that the between-block dependence is weak and that the within-block 
+serial dependence is preserved. Because the blocks here are non-overlapping, 
+this bootstrap approach is known as non-overlapping block bootstrap, or simple 
+block bootstrap.
 
@@
 Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$, 
-$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
-blocks of $Z_j$'s with replacement and then align them in the order they were
-picked to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the
-last block selected will be reduced in size so that the final size of the
-block bootstrap sample is $n$. It is also possible to implement moving block
-bootstrap while allowing blocks to wrap around the end of the series. In other
-words, define moving blocks (assuming $l > 1$) as:
+$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$ blocks 
+of $Z_j$'s with replacement and then align them in the order they were picked to 
+form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last block 
+selected will be reduced in size so that the final size of the block bootstrap 
+sample is $n$. It is also possible to implement moving block bootstrap while 
+allowing blocks to wrap around the end of the series. In other words, define 
+moving blocks (assuming $l > 1$) as:
 \begin{equation}
@@
 each bootstrap sample to preserve the serial dependence, yet small enough for
-there to be a large number of blocks to give sufficient variability between
-each bootstrap sample. As $n$ increases, both~$l$ and $n / l$ should also
-increase. To achieve this, $l$ is often assigned a value as a function of $n$.
-A common function that is considered optimal is $l = \lceil n^{1/3} \rceil$
+there to be a large number of blocks to give sufficient variability between each 
+bootstrap sample. As $n$ increases, both~$l$ and $n / l$ should also increase. 
+To achieve this, $l$ is often assigned a value as a function of $n$. A common 
+function that is considered optimal is $l = \lceil n^{1/3} \rceil$ 
 \citep{buhlmann1999block}, which was adopted in this study.
@@
 Suppose that we have repeated the steps in the last subsection $B$ times, and
-that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
+that for $b \in \{1, \ldots, B\}$, we have obtained a bootstrap point estimate
 $\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
 that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$. Now
-the question is how to construct a CI for $\theta$ using the $B$ bootstrap
-point estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. We
-consider six kinds of block bootstrap CIs adapted from standard bootstrap CIs.
+the question is how to construct a CI for $\theta$ using the $B$ bootstrap point 
+estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. We consider six 
+kinds of block bootstrap CIs adapted from standard bootstrap CIs.
 
@@
 construct an approximate CI \citep[p.168]{efron1993introduction}. Let
-$\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
-copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the
-upper $\alpha$ quantile of the standard normal distribution. A
-$(1 - \alpha)100\%$ standard normal CI is
+$\widehat{\text{SE}}$ be the empirical standard error of the bootstrap point 
+estimates $\hat\theta_n^{(b)}$ for $b \in \{1, \ldots, B\}$. Let $z_{(\alpha)}$ 
+be the upper $\alpha$ quantile of the standard normal distribution. 
+A $(1 - \alpha)100\%$ standard normal CI is
 \[
@@
 \]
-This CI is centered by the point estimator $\hat\theta_n$ and is symmetric. The
-Standard CI is a table-based bootstrap interval approach. Its validity relies
-on whether the distribution of $\hat\theta_n$ is reasonably well approximated
-by its asymptotic normal distribution and whether the bootstrap
+This CI is centered by the original point estimate $\hat\theta_n$ and is 
+symmetric. The standard CI is a table-based bootstrap interval approach. Its 
+validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
+approximated by its asymptotic normal distribution and whether the bootstrap
 $\widehat{\text{SE}}$ approximates the true standard error.
@@
 \paragraph{Student's $t$ CI}
-The procedure for constructing a Student's $t$ CI based on standard bootstrap
-is described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be
-the upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom.
-With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
+The procedure for constructing a Student's $t$ CI based on standard bootstrap is 
+described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
+upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom. With 
+block bootstrapping, 
+a $(1 - \alpha)100\%$ Student's $t$ CI is
 \[
-(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
-\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
+(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\widehat{\text{SE}}, \quad
+\hat{\theta}_{n} - t_{(\alpha/2), k -1}\widehat{\text{SE}}),
 \]
 %\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
-where $k$ is the number of blocks. This CI is centered by the point estimator
-$\hat\theta_n$ and is symmetric. Like the standard normal interval, the
-Student's $t$ CI is a table-based bootstrap interval approach. In this case,
-its validity relies on whether the distribution of $\hat\theta_n$ is
-reasonably well approximation by the $t_{k-1}$ distribution with an expected
-value of $\theta$, and whether the bootstrap $\widehat{\text{SE}}$
-approximates the true standard error.
+where $k$ is the number of blocks. This CI is centered by the original point 
+estimate $\hat\theta_n$ and is symmetric. Like the standard normal interval, the
+Student's $t$ CI is a table-based bootstrap interval approach. In this case, its 
+validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
+approximated by the $t_{k-1}$ distribution with an expected value of $\theta$ 
+and whether the bootstrap $\widehat{\text{SE}}$ approximates the true standard 
+error.
 
@@
   $b \in \{1, \ldots,  B\}$. Make similar changes to other places as needed.} 
+\mc{addressed}
 Let $\hat\theta_{n, \alpha}^B$ be the empirical $100\alpha$th percentile of
-$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)100\%$
-empirical percentile CI is
+$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. 
+A $(1 - \alpha)100\%$ empirical percentile CI is
 \[
-(\hat\theta_{n, \alpha/2}^{(b)}, \quad \hat\theta_{n, 1 - \alpha/2}^{(b)}).
+(\hat\theta_{n, \alpha/2}^{B}, \quad \hat\theta_{n, 1 - \alpha/2}^{B}).
 \]
-This CI is not necessarily centered by the point estimator $\hat\theta_n$. As
-will be shown in our simulation study, this approach works well for the
-marginal mean and standard deviation of a serially dependent process, but its
-coverage of the temporal dependence deteriorates as $n$ increases, which is
-contrary to what one would expect.
+This CI is not necessarily centered by the original point estimate 
+$\hat\theta_n$. As will be shown in our simulation study, this approach works 
+well for the marginal mean and standard deviation of a serially dependent 
+process, but its coverage of the temporal dependence deteriorates as $n$ 
+increases, which is contrary to what one would expect.
 
-\paragraph{Bias Corrected (BC) CI}
-The procedure for constructing a Bias Corrected Bootstrap CI based on standard
+\paragraph{Bias-Corrected (BC) CI}
+The procedure for constructing a bias-corrected Bootstrap CI based on standard
 bootstrap is described in \citet{carpenter2000bootstrap}. Let
@@
 $b \in \{1, \ldots, B\}$. Define $\alpha_1 = \Phi(2b - z_{\alpha/2})$ and 
-$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$. A $(1 - \alpha)100\%~BC$ CI is
+$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$. 
+A $(1 - \alpha)100\%$ ~BC CI is
 \[
-(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
+(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
 \]
 
-\paragraph{Bias Corrected and Accelerated (BCA) CI}
+\paragraph{Bias-Corrected and Accelerated (BCA) CI}
 The BCA CI was first suggested in \citet{efron1987better}. Let
@@
 $b \in \{1, \ldots, B\}$. Let $Z_{(i)}$ be the original sample without the
-$i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let $\hat{\theta}_{(i)}$ be
-the statistic of $Z_{(i)}$, and let
-$\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
+$i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let $\hat{\theta}_{(i)}$ be the 
+statistic of $Z_{(i)}$, and let
+$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
 Let 
@@
 \]
-A $(1 - \alpha)100\%~BC_a$ CI is
+A $(1 - \alpha)100\%$ ~BCA CI is
 \[
-(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
+(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
 \]
-This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
-BCA method corrects for bias and skewness of the $B$ bootstrap point
-estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
-bias-correction and acceleration factors. The acceleration factor refers to
-the rate of change of the standard error of $\hat\theta_n$ with respect to
-$\theta$.
+This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
+for bias and skewness of the $B$ bootstrap point estimates 
+$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
+bias-correction and acceleration factors. The acceleration factor refers to the 
+rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.
 
@@
 
-We propose a CI that is centered at the point estimator and uses the variation
-in the bootstrap estimates to construct the error bound. This interval requires
-\jy{Note the notation change and do a thorough check}
-the computation of
-$\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the mean of all bootstrap point
-estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$. A
-$(1 - \alpha)100\%$ CI is
+We propose a CI that is centered at the original point estimate and uses the 
+variation in the bootstrap estimates to construct the error bound. This interval 
+requires
+\jy{Note the notation change and do a thorough check} \mc{addressed}
+the computation of $\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the 
+mean of all bootstrap point estimates, and 
+$\widehat{\text{bias}} = \bar\theta_n^{B} - \hat\theta_n$. 
+A $(1 - \alpha)100\%$ CI is
 \[
-(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
-\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
+(\hat\theta_{n, \alpha/2}^{B} - \widehat{\text{bias}}, \quad
+\hat\theta_{n, 1 - \alpha/2}^{B} - \widehat{\text{bias}}).
 \]
-This CI is centered around $\hat\theta_n$ and can also be rewritten
-as 
+This CI is centered around $\hat\theta_n$ and can also be rewritten as 
 \[
-(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
-\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
+(\hat\theta_n + \hat\theta_{n, \alpha/2}^{B} - \bar\theta_n^{B}, \quad
+\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{B} - \bar\theta_n^{B}).
 \]
-It is not necessarily symmetric, as different critical values are used to compute
-the lower and upper bounds. It has the same width as the Percentile CI.
+It is not necessarily symmetric, as different critical values are used to 
+compute the lower and upper bounds. It has the same width as the percentile CI.
 
@@
 \subsection{Design}
-We designed a simulation study to compare the performance of the different
-block bootstrap CI methods. In particular, we generated time series $X_t$ from
-a 1st order auto-regressive (AR(1)) process:
+We designed a simulation study to compare the performance of the different block 
+bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
+order auto-regressive (AR(1)) process:
 \[
@@
 series $X_t$ has mean zero and variance 
-$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$,
-we set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
+$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
+set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
 
@@
 To investigate the effect of sample size~$n$, we considered an array of values
-$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we
-generated 10000 replicates. For each replicate, we constructed seven 95\% block
-bootstrap CIs for each parameter as described in the last section. We can
-estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean, sample 
-standard deviation, and lag-1 auto-correlation, respectively, of each
-bootstrap sample, and then construct intervals for each parameter using the
-appropriate procedures described in Section~\ref{sec:bbci}. Then we estimated
-their actual coverage rates along with their 95\% confidence intervals from
-the 10000 replicates. The block bootstrap sampling step was done with function
-\texttt{tsboot} from R package \textsl{boot} \citep{boot}, with block size
-$\lceil n / l \rceil$. This function by default is an implementation of moving
-block bootstrap as described in the previous section, meaning that that blocks
-are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.
+$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
+10000 replicates. For each replicate, we constructed six 95\% block bootstrap 
+CIs for each parameter as described in the last section. We can estimate $\mu$, 
+$\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
+and lag-1 auto-correlation, respectively, of each bootstrap sample. Then we can 
+construct intervals for each parameter using the appropriate procedures 
+described in Section~\ref{sec:bbci}. Then we estimated their actual coverage 
+rates along with their 95\% confidence intervals from the 10000 replicates. The 
+block bootstrap sampling step was done with function \texttt{tsboot} from R 
+package \textsl{boot} \citep{boot}, with block size $\lceil n / l \rceil$. This 
+function by default is an implementation of moving block bootstrap as described 
+in the previous section, meaning that that blocks are allowed to wrap around, 
+and $l = \lceil n^{1/3} \rceil$.
 
@@
 $r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
-expected to match the nominal level. Because it is unlikely for the coverage
-to exactly match the nominal level, we can construct a 95\% CI of the coverage
-rate (which is an estimate of a proportion with $R = 10000$). If the proportion
-0.95 is included in the interval, the block bootstrap method is likely
-performing well. If all values in the interval are below 0.95, the results
-would suggest that the method either is providing inaccurate estimation, is
-underestimating the process' variability, or a combination of both. If all
-values in the interval are above .95, the results suggest that the method is
-overestimating the process' variability. Figures~\ref{fig:mu}--\ref{fig:phi}
-summarizes the empirical coverage rates and the 95\% confidence intervals of
-the real coverage, generated using the R \textsl{ggplot2} package
-\citep{ggplot2}.
+expected to match the nominal level. Because it is unlikely for the coverage to 
+exactly match the nominal level, we can construct a 95\% CI of the coverage rate 
+(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
+is included in the interval, the block bootstrap method is likely performing 
+well. If all values in the interval are below 0.95, the results would suggest 
+that the method either is providing inaccurate estimation, is underestimating 
+the process' variability, or a combination of both. If all values in the 
+interval are above .95, the results suggest that the method is overestimating 
+the process' variability. Figures~\ref{fig:mu}--\ref{fig:phi} summarizes the 
+empirical coverage rates and the 95\% confidence intervals of the real coverage, 
+generated using the R \textsl{ggplot2} package \citep{ggplot2}.
 
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) 
-    process with AR coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and
-    series length $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000
-    replicates. The error bars represent 95\% CIs of the real coverage rates.}
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with AR 
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The 
+    error bars represent 95\% CIs of the real coverage rates.}
   \label{fig:sigma}
@@
 For estimating the mean parameter~$\mu$, Figure~\ref{fig:mu} suggests that all
-methods eventually approach correct coverage of $\mu$ as sample size
-increases. Student's $t$ CIs appear to need the smallest sample size
-to achieve correct coverage, except for samples with strong negative
-dependence, in which case, they actually over-cover $\mu$ for smaller sample
-sizes. For instance, for a sample with $n = 100$ and $\phi = -0.4$, the lower
-bound for a Students $t$ CIs coverage of $\mu$ is greater than 95\%, whereas
-the coverage intervals for other methods contain 95\%. The standard,
-percentile, BC, and BCA, and recentered percentile CIs require similar sample
-sizes to recover $\mu$ at the nominal level for all combinations of $n$ and
-$\phi$. All methods seem to require a smaller sample to recover $\mu$ at the
-nominal rate when dealing with negative dependence versus positive dependence.
-For example, BC CIs recover $\mu$ for $n \geq 100$ when $\phi = -0.2$, but
-they only recover $\mu$ for $n \geq 800$ when $\phi = 0.2$. In addition, as a
-negative dependence gets stronger, holding everything else equal, coverage
-increases, which lead to the Student $t$ CI's aforementioned over-coverage. As
-a positive dependence gets stronger, holding everything else equal, coverage
-decreases, and a larger sample is necessary to recover~$\mu$.
+methods eventually approach correct coverage of $\mu$ as sample size increases. 
+Student's $t$ CIs appear to need the smallest sample size to achieve correct 
+coverage, except for samples with strong negative dependence, in which case, 
+they actually over-cover $\mu$ for smaller sample sizes. For instance, for a 
+sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ CI's 
+coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for other 
+methods contain 95\%. The standard, percentile, BC, and BCA, and recentered 
+percentile CIs require similar sample sizes to recover $\mu$ at the nominal 
+level for all combinations of $n$ and $\phi$. All methods seem to require a 
+smaller sample to recover $\mu$ at the nominal rate when dealing with negative 
+dependence versus positive dependence. For example, BC CIs recover $\mu$ for 
+$n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for $n \geq 800$ 
+when $\phi = 0.2$. In addition, as a negative dependence gets stronger, holding 
+everything else equal, coverage increases, which lead to the Student $t$ CI's 
+aforementioned over-coverage. As a positive dependence gets stronger, holding 
+everything else equal, coverage decreases, and a larger sample is necessary to 
+recover~$\mu$.
 
@@
 $\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample sizes
-when compared to other methods. Unlike $\mu$, there is no over-coverage issue for
-$\sigma$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and recentered percentile
-CIs again have similar performance. All methods seem to have slightly higher
-coverage of $\sigma_x$ when $\phi$ is negative versus when $\phi$ is positive.
-Regardless of the sign, coverage of $\sigma_x$ gets worse as the strength of
-the temporal dependence increases.
-\jy{Compared to Figure 1, there is no over-coverage in this case. Say someting
+when compared to other methods. Unlike $\mu$, there is no over-coverage issue 
+for $\sigma_x$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and recentered 
+percentile CIs again have similar performance. All methods seem to have slightly 
+higher coverage of $\sigma_x$ when $\phi$ is negative versus when $\phi$ is 
+positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as the 
+strength of the temporal dependence increases.
+\jy{Compared to Figure 1, there is no over-coverage in this case. Say something
   about this observation.} \mc{addressed}
@@
 suggests that while standard, Student's $t$, and recentered percentile CIs do
-approach correct coverage as sample size increases, Percentile, BC, and
-BCA CIs deteriorate as sample size increases, especially as the strength of
-the temporal dependence increases. Because of this, only Standard, Student's
-$t$, and recentered percentile CIs should be considered as effective block bootstrap
+approach correct coverage as sample size increases, percentile, BC, and BCA CIs 
+deteriorate as sample size increases, especially as the strength of the temporal 
+dependence increases. Because of this, only standard, Student's $t$, and 
+recentered percentile CIs should be considered as effective block bootstrap 
 methods to estimate $\phi$. Student's $t$ CIs once again can achieve correct
-coverage with smaller sample sizes when compared to standard and recentered percentile CIs
-which perform similarly. Student's $t$ CIs can can recover $\phi$ at the
-nominal level for $n \geq 100$ when the sample's temporal dependence is as
-strong as 0.4. Coverage appears to be higher for all methods when the
+coverage with smaller sample sizes when compared to standard and recentered 
+percentile CIs which perform similarly. Student's $t$ CIs can can recover $\phi$ 
+at the nominal level for $n \geq 100$ when the sample's temporal dependence is 
+as strong as 0.4. Coverage appears to be higher for all methods when the
 dependence is negative rather than positive. Whether or not the dependence is
 negative or positive, coverage of $\phi$ seems to increase slightly as the
-absolute value increases for standard, Student's $t$, and recentereed percentile
-CIs. For the values of $\phi$ observed, there are no examples
-of over-coverage for standard, Student's $t$, BC, BCA, or recentered percentile CIs.
-However, Percentile CIs appear to over-cover $\phi$ for smaller sample sizes when 
+absolute value increases for standard, Student's $t$, and recentered percentile
+CIs. For the values of $\phi$ observed, there are no examples of over-coverage 
+for standard, Student's $t$, BC, BCA, or recentered percentile CIs. However, 
+percentile CIs appear to over-cover $\phi$ for smaller sample sizes when 
 $\phi = -0.2$ and when $\phi = 0$, indicating again that they should not be used.
@@
 \jy{check for no uppercases for recentered percentile, etc. throughout}
+\mc{addressed}
 
@@
   \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
-  \caption{50 replicate percentile, BC, and recentered percentile
-    CIs for samples of $n \in \{800, 1600\}$ for an AR(1) process with
-    $\phi = 0.4$. For each replicate, the lower and upper bounds of the CIs
-    are displayed, as well as $\hat\theta_n$ (blue circle) and
-    $\bar\theta_n^{(b)}$ (red cross). }
+  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
+    samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$. For 
+    each replicate, the lower and upper bounds of the CIs are displayed, as well 
+    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
   \label{fig:npi}
@@
   for ease of referencing in the discussion.}
+\mc{I'm not sure if I addressed this like you intended, I defined 
+$\hat\theta_n^{(b)}$ as bootstrap point estimate, and referred to 
+$\hat\theta_n$ as the original point estimate. Did you want me to define
+$\bar\theta_n^{B}$ as the bootstrap point estimate?}
 
 \jy{Keep the interval labels consistent in figure and in the text}
+\mc{is it fine to have them capitalized in the figures?}
 
@@
 set of 50 CIs was generated for each of the percentile, BC, and recentered
-percentile  approaches. Illustrated in Figure~\ref{fig:npi}, it becomes
-evident that the percentile-based CIs exhibit a notable bias, predominantly
-manifesting as a substantial underestimation of $\phi$ with point estimator
-$\bar\theta_n^B$, that is, the average of $B$ bootstrap point estimate. As the
-sample size increases from 800 to 1600, this bias does not vanish while the
-uncertainty reduces, which explains why the coverage rates deteriorate. The bias
-in $\bar\theta_n^N$ also appears to invalidate the bias correction in the BC
-bootstrap, leading to the poor performance of the BC intervals. The BCA
-intervals have the same problem as the BC intervals in the bias-correction step.
-The root of the issue appears to be that the autocorrelation in the block
-bootstrap samples is somehow smaller compared to that in the original sample.
-On the other hand, the original point estimate $\hat\phi_n$ is asymptotically
-unbiased. Since the uncertainty in the bootstrap point estimates
-$\hat\theta_n^{(b)}$, $b = 1, \ldots, B$, the percentile CIs recentered at the
-point estimate provide desired coverage.
+percentile  approaches for samples of $n \in \{800, 1600\}$. Illustrated in 
+Figure~\ref{fig:npi}, it becomes evident that the percentile-based CIs exhibit a 
+notable bias, predominantly manifesting as a substantial underestimation of 
+$\phi$ with point estimator $\bar\theta_n^B$, that is, the average of $B$ 
+bootstrap point estimates. As the sample size increases from 800 to 1600, this 
+bias does not vanish while the uncertainty reduces, which explains why the 
+coverage rates deteriorate. The bias in $\bar\theta_n^B$ also appears to 
+invalidate the bias-correction in the BC bootstrap, leading to the poor 
+performance of the BC intervals. The BCA intervals have the same problem as the 
+BC intervals in the bias-correction step. The root of the issue appears to be 
+that the autocorrelation in the block bootstrap samples is somehow smaller 
+compared to that in the original sample. On the other hand, the original point 
+estimate $\hat\theta_n$ is asymptotically unbiased. Since the width is based on 
+the uncertainty in the bootstrap point estimates $\hat\theta_n^{(b)}$, 
+$b = 1, \ldots, B$, the percentile CIs recentered at the original point estimate 
+provide desired coverage.
 
@@
 estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
-perform noticeably better than the others. However, when estimating $\phi$,
-the choice of method is of utmost importance as to avoid coverage
-deterioration. A smaller sample size is generally required to estimate a
-parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the
-same magnitude. In order to know if coverage will increase as the strength of
-the temporal dependence increases, one need to know what the parameter of
-interest is, and in the case of $\mu$, the direction of the serial dependence. The
-BC approach does not seem to be correcting bias appropriately when estimating
-$\phi$. Like the percentile method, the recentered percentile method uses the spread from the 
-bootstrap to construct the width of the CI. However, the recentered approach, does
-not correct from the original point estimate $\hat\theta_n$.
+perform noticeably better than the others. However, when estimating $\phi$, the 
+choice of method is of utmost importance as to avoid coverage deterioration. A 
+smaller sample size is generally required to estimate a parameter for a sample 
+with a negative $\phi$ versus a positive $\phi$ of the same magnitude. In order 
+to know if coverage will increase as the strength of the temporal dependence 
+increases, one need to know what the parameter of interest is, and in the case 
+of $\mu$, the direction of the serial dependence. The BC approach does not seem 
+to be correcting bias appropriately when estimating $\phi$. Like the percentile 
+method, the recentered percentile method uses the spread from the bootstrap to 
+construct the width of the CI. However, the recentered approach, does not 
+correct from the original point estimate $\hat\theta_n$.
 
@@
 from simple parameters like the mean to more complicated temporal dependence
-factors. We know theoretically that the block bootstrap procedure will cover
+factors. We know theoretically that the block bootstrap procedure will cover a 
 parameter of a time series at the nominal level given an infinitely large 
-sample, so the goal for this study was to find the smallest finite sample
-length $n$ of a time series in order for the block bootstrap procedure to 
-recover its associated parameters at an acceptable rate.
-Our analysis relies on the assumption that there is a size $n$ large
-enough for the method to work: that is, the method's performance improves as
-$n$ increases. Out of the five types of intervals used in this study, this
-assumption was found to hold true with respect to estimating $\phi$ only for
-Standard, Student's $t$, and Recentered Method CIs, whereas Percentile, BC,
-and BCA intervals exhibited coverage deterioration as $n$ increased. The
-Percentile CI's coverage deterioration can be attributed to bias that is not
-corrected as $n$ increases. Specifically, as $n$ increases, the width of the
-CI decreases, but because the percentile CI underestimates $\phi$, the
-coverage decreases. The BC CI seems to correct the bias, but the width of
-6the CI seems to be inconsistent. The acceleration factor of the BCA CI
-seems to fail, as the width of the CI seems to be inconsistent.
+sample, so the goal for this study was to find the smallest finite sample length 
+$n$ of a time series in order for the block bootstrap procedure to recover its 
+associated parameters at an acceptable rate. Our analysis relies on the 
+assumption that there is a size $n$ large enough for the method to work: that 
+is, the method's performance improves as $n$ increases. Out of the six types of 
+intervals used in this study, this assumption was found to hold true with 
+respect to estimating $\phi$ only for standard, Student's $t$, and recentered 
+percentile CIs, whereas percentile, BC, and BCA intervals exhibited coverage 
+deterioration as $n$ increased. The percentile CI's coverage deterioration can 
+be attributed to bias that is not corrected as $n$ increases. Specifically, as 
+$n$ increases, the width of the CI decreases, but because the percentile CI 
+underestimates $\phi$, the coverage decreases. The BC CI seems to correct the 
+bias, but the width of the CI seems to be inconsistent. The acceleration factor 
+of the BCA CI seems to fail, as the width of the CI seems to be inconsistent.
 
@@
 necessary sample sizes when using block bootstrap to estimate parameters of 
-serially dependent data. When using Student's $t$ intervals and $\phi$ is unknown,
-the results of this study suggest that an $n \geq 800$ may be necessary for common practice to
-estimate simpler parameters like $\mu$ or $\sigma_x$. If $\phi$ is already
-known, a lesser $n$ may be adequate to estimate these parameters. For lower
-absolute values of $\phi$, a smaller $n$ is sufficient when estimating $\mu$
-or $\sigma$. For negative values of $\phi$, coverage of $\mu$ is higher in
-general. In fact, Student's $t$ seems to over-cover $\mu$ for $\phi = - 0.4$
-when using smaller sample sizes, meaning that if $\phi$ is known to have a
-very negative value, another CI may be required. However, in real world
-applications, $\phi$ is more commonly found to be positive, so Student's $t$
-should still be used if $\phi$ is unknown. Lastly, to estimate $\phi$,
-$n \geq 100$ using the Student's $t$ method may be sufficient. Further
+serially dependent data. When using Student's $t$ intervals and $\phi$ is 
+unknown, the results of this study suggest that an $n \geq 800$ may be necessary 
+for common practice to estimate simpler parameters like $\mu$ or $\sigma_x$. If 
+$\phi$ is already known, a lesser $n$ may be adequate to estimate these 
+parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
+when estimating $\sigma_x$. For negative values of $\phi$, coverage of all 
+parameters is higher in general. In fact, Student's $t$ seems to over-cover 
+$\mu$ for $\phi = - 0.4$ when using smaller sample sizes, meaning that if $\phi$ 
+is known to have a very negative value, another CI may be required. However, in 
+real world applications, $\phi$ is more commonly found to be positive, so 
+Student's $t$ should still be used if $\phi$ is unknown. Lastly, to estimate 
+$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Further
 investigation may be necessary to see if there are other interval corrections
@@
 graduate students, block bootstrap is not typically a part of curriculum, but
-the results of this study can easily be used to demonstrate when it is
-practical to use this method. This information could also prove to be useful
-for research using block bootstrap estimation of time series in domains such
-as econometrics. Future studies could investigate the $n$ needed to make
-inferences about other forms
-of serially dependent data such as a moving average process. One could also
-investigate if there are types of block
-bootstrap interval construction such as $ABC$ or bootstrap-t intervals, or
-alternatives to block bootstrap, such as AR-Sieve bootstrap
- \citep{kreiss1992bootstrap}, that could more
+the results of this study can easily be used to demonstrate when it is practical 
+to use this method. This information could also prove to be useful for research 
+using block bootstrap estimation of time series in domains such as econometrics. 
+Future studies could investigate the $n$ needed to make inferences about other 
+forms of serially dependent data such as a moving average process. One could 
+also investigate if there are types of block bootstrap interval construction 
+such as $ABC$ or bootstrap-t intervals, or alternatives to block bootstrap, such 
+as AR-Sieve bootstrap \citep{kreiss1992bootstrap}, that could more
 \jy{Cite references for AR-sieve} \mc{addressed}
 appropriately recover the parameters of a time series. In addition, as noted by
-\citet{buhlmann2002bootstraps}, there are some 
-general drawbacks of block bootstrap - with respect to how reasonably it imitates 
-the data-generating process - which may be addressed in a future study.
+\citet{buhlmann2002bootstraps}, there are some general drawbacks of block 
+bootstrap - with respect to how reasonably it imitates the data-generating 
+process - which may be addressed in a future study.
 

### 2023-08-25 Code/functions.R

@@ -1,19 +1,17 @@
 .libPaths("~/rlibs")
-library(ggplot2) # put package loading outside of the function
-## This note checks the empirical coverage rate of CIs constructed from
-## block bootstrap with series generated from an AR process
+library(ggplot2) 
 
 mystat <- function(x) {
   c(mean(x),
     sd(x),
     cor(x[-1], x[-length(x)]))
-  # acf(x, lag.max = 1, plot = FALSE)$acf[2])
+    # acf(x, lag.max = 1, plot = FALSE)$acf[2])
 }
 
 expstat <- function(x) {
   c(1 / mean(x),
     cor(x[-1], x[-length(x)]))
-  # acf(x, lag.max = 1, plot = FALSE)$acf[2])
+    # acf(x, lag.max = 1, plot = FALSE)$acf[2])
 }
 
 calculate_a_hat <- function(row) {
@@ -51,30 +49,22 @@ do1rep <- function(n, phi, statistic, blksize, dstr = qnorm, R = 1000, level = .
   ## Centered Bootstrap Percentile interval (from singh2008bootstrap)
   crit <- 
     apply(t(t(bts$t) - bts$t0), 2, quantile, prob = c(1 - alpha/2, alpha/2)) 
-  mbts <- apply(bts$t, 2, mean)
+  mbts <- apply(bts$t, 2, mean) # mean of bootstrap point estimates
   ctrCI <- -sweep(crit, 2, bts$t0, FUN = '-')
   
-  ## Bias-Corrected interval (Carpenter et al 2000, p. 1153)
+  ## BC interval (Carpenter et al 2000, p. 1153)
   b <- qnorm(colMeans(sweep(bts$t, 2, bts$t0) < 0))
   qup <- pnorm(2 * b - qnorm(alpha / 2))
   qlo <- pnorm(2 * b - qnorm(1 - alpha / 2))
   bcCI <- sapply(1:length(bts$t0),
                  function(i) quantile(bts$t[,i], prob=c(qlo[i], qup[i])))
   
-  ## LB: bts$t0 + alpha/2 crit, UB: bts$t0 + (1 - alpha/2) crit
-  # mbtCI <- sweep(crit2, 2, mbts, FUN = '+') # mean of pseudo-estimates
-  ## LB: mbts + alpha/2 crit2, UB: mbts + (1 - alpha/2) crit2
[…]

### 2023-08-25 Code/phi_intervals.R

@@ -6,9 +6,8 @@ sim <- replicate(50, do1rep(800, 0.4, mystat, 10))
 new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
 
 file_titles <- c("pct", "bc", "prop")
-custom_titles <- c("Percentile", "Bias-Corrected", "Recentered")
+custom_titles <- c("Percentile", "BC", "Recentered")
 
-# Create a data frame for plotting
 plot_data_800 <- data.frame(replication = 1:50,
                         point_estimate = new_sim[1, ],
                         bts_mean = new_sim[2, ],
@@ -22,7 +21,6 @@ set.seed(1234)
 sim <- replicate(50, do1rep(1600, 0.4, mystat, 10))
 new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
 
-# Create a data frame for plotting
 plot_data_1600 <- data.frame(replication = 1:50,
                           point_estimate = new_sim[1, ],
                           bts_mean = new_sim[2, ],
@@ -34,9 +32,8 @@ plot_data_1600 <- data.frame(replication = 1:50,
 
 plot_data <- rbind(plot_data_800, plot_data_1600)
 
-# Create facet plot using ggplot2
 plot_data$custom_title <- factor(plot_data$custom_title, 
-                  levels = c("Percentile", "Bias-Corrected", "Recentered"))
+                  levels = c("Percentile", "BC", "Recentered"))
 
 plot_data$sample.size <- factor(plot_data$sample.size,
                   levels = c("n = 800", "n = 1600"))

### 2023-08-25 Manuscript/manuscript.tex
removed addressed comments and one new comment

@@
 The percentile CI was first suggested in \citet{efron1979bootstrap}.
-\jy{The previous superscript does not make sense because
-  $b \in \{1, \ldots,  B\}$. Make similar changes to other places as needed.} 
-\mc{addressed}
 Let $\hat\theta_{n, \alpha}^B$ be the empirical $100\alpha$th percentile of
@@
 bootstrap is described in \citet{carpenter2000bootstrap}. Let
+\jy{Use a different symbol because $b$ has been used. Isn't is the same as $\hat
+  z_0$ in the next paragraph?}
 $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
@@
 requires
-\jy{Note the notation change and do a thorough check} \mc{addressed}
 the computation of $\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the 
@@
 A $(1 - \alpha)100\%$ CI is
-\[
-(\hat\theta_{n, \alpha/2}^{B} - \widehat{\text{bias}}, \quad
-\hat\theta_{n, 1 - \alpha/2}^{B} - \widehat{\text{bias}}).
-\]
-This CI is centered around $\hat\theta_n$ and can also be rewritten as 
+centered around $\hat\theta_n$ and can be rewritten as 
 \[
@@
 strength of the temporal dependence increases.
-\jy{Compared to Figure 1, there is no over-coverage in this case. Say something
-  about this observation.} \mc{addressed}
 
@@
 
-\jy{check for no uppercases for recentered percentile, etc. throughout}
-\mc{addressed}
-
 \begin{figure}[tbp]
@@
 \end{figure}
-
-\jy{The red cross is not $\theta_n^{(b)}$, but their average over
-  $b = 1,  \ldots, B$. Define this as bootstrap point estimate in section 2.2
-  for ease of referencing in the discussion.}
-\mc{I'm not sure if I addressed this like you intended, I defined 
-$\hat\theta_n^{(b)}$ as bootstrap point estimate, and referred to 
-$\hat\theta_n$ as the original point estimate. Did you want me to define
-$\bar\theta_n^{B}$ as the bootstrap point estimate?}
-
-\jy{Keep the interval labels consistent in figure and in the text}
-\mc{is it fine to have them capitalized in the figures?}
 
@@
 $b = 1, \ldots, B$, the percentile CIs recentered at the original point estimate
-provide desired coverage.
+$\hat\theta_n$ provide desired coverage.
 
@@
 
-\jy{use a better topic sentence.} \mc{addressed}
 One of the goals of this study was to provide some practical recommendations for 
@@
 as AR-Sieve bootstrap \citep{kreiss1992bootstrap}, that could more
-\jy{Cite references for AR-sieve} \mc{addressed}
 appropriately recover the parameters of a time series. In addition, as noted by
 \citet{buhlmann2002bootstraps}, there are some general drawbacks of block 
-bootstrap - with respect to how reasonably it imitates the data-generating 
-process - which may be addressed in a future study.
+bootstrap --- with respect to how reasonably it imitates the data-generating 
+process --- which may be investigated in a future study.
+
+\bibliographystyle{chicago}
+\bibliography{citations}
+
+\end{document}
 
@@
 simulated example (we did not consider the former). } \mc{addressed}
-
-\bibliographystyle{chicago}
-\bibliography{citations}
-
-\end{document}

### 2023-08-25 Manuscript/manuscript.tex
Fixed Notation

@@
 \jy{Use a different symbol because $b$ has been used. Isn't is the same as $\hat
-  z_0$ in the next paragraph?}
-$b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
-$b \in \{1, \ldots, B\}$. Define $\alpha_1 = \Phi(2b - z_{\alpha/2})$ and 
-$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$. 
+  z_0$ in the next paragraph?} \mc{addressed}
+$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
+$b \in \{1, \ldots, B\}$. Define $\alpha_1 = \Phi(2\hat{z}_0 - z_{\alpha/2})$ 
+and $\alpha_2 = \Phi(2\hat{z}_0 - z_{1 - \alpha/2})$. 
 A $(1 - \alpha)100\%$ ~BC CI is
@@
 \paragraph{Bias-Corrected and Accelerated (BCA) CI}
-The BCA CI was first suggested in \citet{efron1987better}. Let
-$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
-$b \in \{1, \ldots, B\}$. Let $Z_{(i)}$ be the original sample without the
-$i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let $\hat{\theta}_{(i)}$ be the 
-statistic of $Z_{(i)}$, and let
+The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
+original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
+$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
 $\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
@@
 \[
-\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
+\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
   z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
 \text{ and }
-\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
+\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
   z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).

### 2023-08-25 Manuscript/manuscript.tex
minor

@@
 bootstrap is described in \citet{carpenter2000bootstrap}. Let
-\jy{Use a different symbol because $b$ has been used. Isn't is the same as $\hat
-  z_0$ in the next paragraph?} \mc{addressed}
 $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
@@
 \paragraph{Recentered Percentile CI}
-
 We propose a CI that is centered at the original point estimate and uses the 
@@
 the computation of $\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the 
-mean of all bootstrap point estimates, and 
-$\widehat{\text{bias}} = \bar\theta_n^{B} - \hat\theta_n$. 
-A $(1 - \alpha)100\%$ CI is
+mean of all bootstrap point estimates. A $(1 - \alpha)100\%$ CI is
 centered around $\hat\theta_n$ and can be rewritten as 

### 2023-08-26 Manuscript/manuscript.tex
Applied AJUR Format, Still have to make some changes

@@
-\documentclass[12pt, letterpaper, titlepage]{article}
+% Created by Bonita Graham
+% Last update: December 2019 By Kestutis Bendinskas
 
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{booktabs}
-\usepackage{amsthm}
+% Authors: 
+% Please do not make changes to the preamble until after the solid line of %s.
+
+\documentclass[10pt]{article}
+\usepackage[explicit]{titlesec}
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{1em}
+\usepackage{hyphenat}
+\usepackage{ragged2e}
+\RaggedRight
+
+% These commands change the font. If you do not have Garamond on your computer, you will need to install it.
+\usepackage{garamondx}
+\usepackage[T1]{fontenc}
+\usepackage{amsmath, amsthm}
 \usepackage{graphicx}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref, url}
-\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor =
-  blue}
-\usepackage{natbib}
-\usepackage{enumitem}
-\usepackage{setspace}
 
-\usepackage[pagewise]{lineno}
-%\linenumbers*[1]
-% %% patches to make lineno work better with amsmath
-\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
- \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
- \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
- \renewenvironment{#1}%
- {\linenomath\csname old#1\endcsname}%
- {\csname oldend#1\endcsname\endlinenomath}}%
-\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
- \patchAmsMathEnvironmentForLineno{#1}%
- \patchAmsMathEnvironmentForLineno{#1*}}%
+% This adjusts the underline to be in keeping with word processors.
+\usepackage{soul}
+\setul{.6pt}{.4pt}
 
-\AtBeginDocument{%
- \patchBothAmsMathEnvironmentsForLineno{equation}%
- \patchBothAmsMathEnvironmentsForLineno{align}%
- \patchBothAmsMathEnvironmentsForLineno{flalign}%
- \patchBothAmsMathEnvironmentsForLineno{alignat}%
- \patchBothAmsMathEnvironmentsForLineno{gather}%
- \patchBothAmsMathEnvironmentsForLineno{multline}%
-}
+% The following sets margins to 1 in. on top and bottom and .75 in on left and right, and remove page numbers.
+\usepackage{geometry}
+\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\pagenumbering{gobble}
+\renewcommand{\headrulewidth}{0.0pt}
+\renewcommand{\footrulewidth}{0.0pt}
 
-% control floats
-\renewcommand\floatpagefraction{.9}
-\renewcommand\topfraction{.9}
-\renewcommand\bottomfraction{.9}
-\renewcommand\textfraction{.1}
-\setcounter{totalnumber}{50}
-\setcounter{topnumber}{50}
-\setcounter{bottomnumber}{50}
+% These Commands create the label style for tables, figures and equations.
+\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
+\captionsetup{labelformat=simple, labelsep=period}
+\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
+\renewcommand{\theequation}{\arabic{equation}}
+\makeatletter
+\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
+\makeatother
+\setlength{\intextsep}{10pt}
+\setlength{\abovecaptionskip}{2pt}
+\setlength{\belowcaptionskip}{-10pt}
 
-\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
-\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
-\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}
+\renewcommand{\textfraction}{0.10}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\floatpagefraction}{0.90}
 
+% These commands set the paragraph and line spacing
+\titleformat{\section}
+  {\normalfont}{\thesection}{1em}{\MakeUppercase{\textbf{#1}}}
+\titlespacing\section{0pt}{0pt}{-10pt}
+\titleformat{\subsection}
+  {\normalfont}{\thesubsection}{1em}{\textit{#1}}
+\titlespacing\subsection{0pt}{0pt}{-8pt}
+\renewcommand{\baselinestretch}{1.15}
+
+% This designs the title display style for the maketitle command
+\makeatletter
+\newcommand\sixteen{\@setfontsize\sixteen{17pt}{6}}
+\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
+\begin{flushleft}
+\sixteen\bfseries \@title
+\medskip
+\end{flushleft}
+\textit{\@author}
+\egroup}
+\makeatother
+
+% This styles the bibliography and citations.
+%\usepackage[biblabel]{cite}
+\usepackage[sort&compress]{natbib}
+\setlength\bibindent{2em}
+\makeatletter
+\renewcommand\@biblabel[1]{\textbf{#1.}\hfill}
+\makeatother
+\renewcommand{\citenumfont}[1]{\textbf{#1}}
+\bibpunct{}{}{,~}{s}{,}{,}
+\setlength{\bibsep}{0pt plus 0.3ex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Authors: Add additional packages and new commands here.  
+% Limit your use of new commands and special formatting.
+
+% Place your title below. Use Title Capitalization.
 \title{On Sample Size for Block Bootstrap Confidence Intervals 
@@
 
-\author{Mathew Chandy, Elizabeth Schifano,
-%   \href{mailto:mathew.chandy@uconn.edu}
-% {\nolinkurl{mathew.chandy@uconn.edu}}\\
-  and Jun Yan\\[1ex]
-  Department of Statistics, University of Connecticut\\
+% Add author information below. Communicating author is indicated by an 
+% asterisk, the affiliation is shown by superscripted lower case letter if 
+% several affiliations need to be noted.
+\author{
+Mathew Chandy*$^{a}$, Elizabeth Schifano$^{a}$, Jun Yan$^{a}$ \\ \medskip 
+$^{a}$Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
+Student: mathew.chandy@uconn.edu* \\
+Mentors: elizabeth.schifano@uconn.edu, jun.yan@uconn.edu
 }
-\date{}
+\pagestyle{empty}
+\begin{document}
 
-\begin{document} 
+% Makes the title and author information appear.
+\vspace*{.01 in}
 \maketitle
+\vspace{.12 in}
 
-\begin{abstract}
+% Abstracts are required.
+\section*{abstract}
 Block bootstrap is widely used in constructing confidence intervals for 
@@
 
-\bigskip
-\noindent{\sc Keywords}:
-dependent data; resampling; simulation; time series
-\end{abstract}
+% Keywords are required.
+\section*{keywords} 
+List Eight to Ten Capitalized Keywords Separated by \ul{Semicolons}; Do Not Use Period at The End
+Dependent Data; Resampling; Simulation; Time Series
 
-\doublespace
+\vspace{.12 in}
 
-\section{Introduction}
-\label{sec:intro}
+% Start the main part of the manuscript here.
+% Comment out section headings if inappropriate to your discipline.
+% If you add additional section or subsection headings, use an asterisk * to avoid numbering.
+
+\section*{introduction}
 
@@
 
-The remainder of the paper is organized as follows. Section~\ref{sec:bbci} 
+The remainder of the paper is organized as follows. The first section 
 reviews block bootstrap procedures and how to use block bootstrap estimates to
 construct CIs; a simple CI obtained by recentering at the original point 
-estimate is proposed for comparison. Section~\ref{sec:simu} reports a simulation 
+estimate is proposed for comparison. The second section reports a simulation 
 study comparing the coverage rates of six block bootstrap CIs. A discussion
-concludes in Section~\ref{sec:disc}.
+concludes in the final section.
 
-\section{Block Bootstrap CIs}
+\section*{block bootstrap cis}
 \label{sec:bbci}
@@
 
-\subsection{Block Bootstrap}
+\subsection*{Block Bootstrap}
 
@@
 
-\subsection{Block Bootstrap CIs}
+\subsection*{Block Bootstrap CIs}
 
@@
 Let 
-\[
+\begin{equation}
 \hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
@@
   \hat{\theta}_{(i)})^2\}^{3/2}}.
-\]
+\end{equation}
 Define
-\[
+\begin{equation}
 \alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
   z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
-\text{ and }
+\end{equation}
+and
+\begin{equation}
 \alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
   z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
-\]
+\end{equation}
 A $(1 - \alpha)100\%$ ~BCA CI is
@@
 \paragraph{Recentered Percentile CI}
+
 We propose a CI that is centered at the original point estimate and uses the 
@@
 mean of all bootstrap point estimates. A $(1 - \alpha)100\%$ CI is
-centered around $\hat\theta_n$ and can be rewritten as 
+centered around $\hat\theta_n$ and can be written as 
 \[
@@
 
-\section{Simulation Study}
+\section*{simulation study}
 \label{sec:simu}
 
-\subsection{Design}
+\subsection*{Design}
 We designed a simulation study to compare the performance of the different block 
@@
 order auto-regressive (AR(1)) process:
-\[
+\begin{equation}
 X_t = \phi X_{t-1} + \epsilon_t,
-\]
+\end{equation}
 where $\phi$ is an auto-regressive coefficient, and $\epsilon_t$ is a series of
@@
 construct intervals for each parameter using the appropriate procedures 
-described in Section~\ref{sec:bbci}. Then we estimated their actual coverage 
+described in \textit{Block Bootstrap CIs}. Then we estimated their actual coverage 
 rates along with their 95\% confidence intervals from the 10000 replicates. The 
@@
 interval are above .95, the results suggest that the method is overestimating 
-the process' variability. Figures~\ref{fig:mu}--\ref{fig:phi} summarizes the 
-empirical coverage rates and the 95\% confidence intervals of the real coverage, 
-generated using the R \textsl{ggplot2} package \citep{ggplot2}.
+the process' variability. \textbf{Figures~\ref{fig:mu}--\ref{fig:phi}} 
+summarizes the empirical coverage rates and the 95\% confidence intervals of the 
+real coverage, generated using the R \textsl{ggplot2} package \citep{ggplot2}.
 
@@
 
-\subsection{Results}
+\subsection*{Results}
 
-For estimating the mean parameter~$\mu$, Figure~\ref{fig:mu} suggests that all
-methods eventually approach correct coverage of $\mu$ as sample size increases. 
-Student's $t$ CIs appear to need the smallest sample size to achieve correct 
-coverage, except for samples with strong negative dependence, in which case, 
-they actually over-cover $\mu$ for smaller sample sizes. For instance, for a 
-sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ CI's 
-coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for other 
-methods contain 95\%. The standard, percentile, BC, and BCA, and recentered 
-percentile CIs require similar sample sizes to recover $\mu$ at the nominal 
-level for all combinations of $n$ and $\phi$. All methods seem to require a 
-smaller sample to recover $\mu$ at the nominal rate when dealing with negative 
-dependence versus positive dependence. For example, BC CIs recover $\mu$ for 
-$n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for $n \geq 800$ 
-when $\phi = 0.2$. In addition, as a negative dependence gets stronger, holding 
-everything else equal, coverage increases, which lead to the Student $t$ CI's 
-aforementioned over-coverage. As a positive dependence gets stronger, holding 
-everything else equal, coverage decreases, and a larger sample is necessary to 
-recover~$\mu$.
+For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
+that all methods eventually approach correct coverage of $\mu$ as sample size 
+increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
+correct coverage, except for samples with strong negative dependence, in which 
+case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
+a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
+CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
+other methods contain 95\%. The standard, percentile, BC, and BCA, and 
+recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
+nominal level for all combinations of $n$ and $\phi$. All methods seem to 
+require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
+negative dependence versus positive dependence. For example, BC CIs recover 
+$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
+$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
+stronger, holding everything else equal, coverage increases, which lead to the 
+Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
+stronger, holding everything else equal, coverage decreases, and a larger sample 
+is necessary to recover~$\mu$.
 
 For estimating the standard deviation parameter~$\sigma_x$,
-Figure~\ref{fig:sigma} suggests that every method can reach nominal coverage of
-$\sigma_x$ if the sample is large enough, but for a given $n$ and $\phi$,
-coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general. Like 
-$\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample sizes
-when compared to other methods. Unlike $\mu$, there is no over-coverage issue 
-for $\sigma_x$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and recentered 
-percentile CIs again have similar performance. All methods seem to have slightly 
-higher coverage of $\sigma_x$ when $\phi$ is negative versus when $\phi$ is 
-positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as the 
-strength of the temporal dependence increases.
+\textbf{Figure~\ref{fig:sigma}} suggests that every method can reach nominal 
+coverage of $\sigma_x$ if the sample is large enough, but for a given $n$ and 
+$\phi$, coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general.
+Like $\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample 
+sizes when compared to other methods. Unlike $\mu$, there is no over-coverage 
+issue for $\sigma_x$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and 
+recentered percentile CIs again have similar performance. All methods seem to 
+have slightly higher coverage of $\sigma_x$ when $\phi$ is negative versus when 
+$\phi$ is positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as 
+the strength of the temporal dependence increases.
 
-For estimating the auto-correlation parameter~$\phi$, Figure~\ref{fig:phi}
-suggests that while standard, Student's $t$, and recentered percentile CIs do
-approach correct coverage as sample size increases, percentile, BC, and BCA CIs 
-deteriorate as sample size increases, especially as the strength of the temporal 
-dependence increases. Because of this, only standard, Student's $t$, and 
-recentered percentile CIs should be considered as effective block bootstrap 
-methods to estimate $\phi$. Student's $t$ CIs once again can achieve correct
-coverage with smaller sample sizes when compared to standard and recentered 
-percentile CIs which perform similarly. Student's $t$ CIs can can recover $\phi$ 
-at the nominal level for $n \geq 100$ when the sample's temporal dependence is 
-as strong as 0.4. Coverage appears to be higher for all methods when the
-dependence is negative rather than positive. Whether or not the dependence is
-negative or positive, coverage of $\phi$ seems to increase slightly as the
-absolute value increases for standard, Student's $t$, and recentered percentile
-CIs. For the values of $\phi$ observed, there are no examples of over-coverage 
-for standard, Student's $t$, BC, BCA, or recentered percentile CIs. However, 
-percentile CIs appear to over-cover $\phi$ for smaller sample sizes when 
-$\phi = -0.2$ and when $\phi = 0$, indicating again that they should not be used.
+For estimating the auto-correlation parameter~$\phi$, 
+\textbf{Figure~\ref{fig:phi}} suggests that while standard, Student's $t$, and 
+recentered percentile CIs do approach correct coverage as sample size increases, 
+percentile, BC, and BCA CIs deteriorate as sample size increases, especially as 
+the strength of the temporal dependence increases. Because of this, only 
+standard, Student's $t$, and recentered percentile CIs should be considered as 
+effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
+again can achieve correct coverage with smaller sample sizes when compared to 
+standard and recentered percentile CIs which perform similarly. Student's $t$ 
+CIs can can recover $\phi$ at the nominal level for $n \geq 100$ when the 
+sample's temporal dependence is as strong as 0.4. Coverage appears to be higher 
+for all methods when the dependence is negative rather than positive. Whether or 
+not the dependence is negative or positive, coverage of $\phi$ seems to increase 
+slightly as the absolute value increases for standard, Student's $t$, and 
+recentered percentile CIs. For the values of $\phi$ observed, there are no 
+examples of over-coverage for standard, Student's $t$, BC, BCA, or recentered 
+percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
+sample sizes when $\phi = -0.2$ and when $\phi = 0$, indicating again that they 
+should not be used.
 
@@
 percentile  approaches for samples of $n \in \{800, 1600\}$. Illustrated in 
-Figure~\ref{fig:npi}, it becomes evident that the percentile-based CIs exhibit a 
-notable bias, predominantly manifesting as a substantial underestimation of 
-$\phi$ with point estimator $\bar\theta_n^B$, that is, the average of $B$ 
-bootstrap point estimates. As the sample size increases from 800 to 1600, this 
-bias does not vanish while the uncertainty reduces, which explains why the 
-coverage rates deteriorate. The bias in $\bar\theta_n^B$ also appears to 
+\textbf{Figure~\ref{fig:npi}}, it becomes evident that the percentile-based CIs 
+exhibit a notable bias, predominantly manifesting as a substantial 
+underestimation of $\phi$ with point estimator $\bar\theta_n^B$, that is, the 
+average of $B$ bootstrap point estimates. As the sample size increases from 800 
+to 1600, this bias does not vanish while the uncertainty reduces, which explains 
+why the coverage rates deteriorate. The bias in $\bar\theta_n^B$ also appears to 
 invalidate the bias-correction in the BC bootstrap, leading to the poor 
@@
 
-\section{Discussion}
+\section*{discussion}
 \label{sec:disc}
@@
 \end{document}
-
-\eds{Check out this paper:
-Peter Buhlmann. "Bootstraps for Time Series." Statist. Sci. 17(1) 52 - 72, 
-May 2002 - the conclusions of this paper are interesting in their own right:
-``Disadvantages of the [block bootstrap] method include the following.
-The block bootstrap sample should not be viewed as
-a reasonable sample mimicking the data-generating
-process: it is not stationary and exhibits artifacts where
-resampled blocks are linked together. This implies that
-the plug-in rule for bootstrapping an estimator $\hat{\theta}$ is not
-appropriate. A prevectorization of the data is highly
-recommended, but the bootstrapped estimator and its
-computing routine may then need to be redesigned. As
-a general nonparametric scheme, the block bootstrap
-may be outperformed in various niches of stationary
-time series, for example, for linear time series (see Section 3) 
-and for categorical processes (see Section 5).
-Second-order accuracy for a confidence interval has
-been justified with the approach of Studentizing and
-BCA correction (in the case of noncategorical time series); 
-the latter was found to yield marginal improvement in a 
-simulated example (we did not consider the former). } \mc{addressed}

### 2023-08-26 Code/functions.R

@@ -1,5 +1,6 @@
 .libPaths("~/rlibs")
 library(ggplot2) 
+library(showtext)
 
 mystat <- function(x) {
   c(mean(x),
@@ -96,6 +97,11 @@ mychk <- function(sim, target) {
 
 graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 {
+  font_add_google("EB Garamond")
+#  windows()
+  
+  showtext_auto()
+  
   data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
                     labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Recentered'))
   
@@ -106,7 +112,8 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
     facet_grid(factor(CI) ~ factor(phi), scales = 'free') +
     labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
+            element_text(family = "EB Garamond")) +
     scale_y_continuous(trans=trans)
   ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), height = 6)
 }

### 2023-08-26 Code/phi_intervals.R

@@ -1,5 +1,6 @@
 source("functions.R")
 library(ggplot2)
+library(showtext)
 
 set.seed(1234)
 sim <- replicate(50, do1rep(800, 0.4, mystat, 10))
@@ -38,6 +39,11 @@ plot_data$custom_title <- factor(plot_data$custom_title,
 plot_data$sample.size <- factor(plot_data$sample.size,
                   levels = c("n = 800", "n = 1600"))
 
+font_add_google("EB Garamond")
+#  windows()
+
+showtext_auto()
+
 ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound), width = 0.5, color = 'gray') +
   geom_point(color = 'blue') +
@@ -48,6 +54,7 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   scale_color_manual(values = c('blue', 'red', 'gray')) +
   scale_linetype_manual(values = c(1, 1, 1)) +
   theme_minimal() + 
-  theme(strip.text=element_text(size=10))
+  theme(strip.text=element_text(size=10), text =
+          element_text(family = "EB Garamond"))
 
 ggsave('../Manuscript/figures/norm_phi_intervals.pdf', width = 10)

### 2023-08-26 Manuscript/manuscript.tex
comments on styles and appendix

@@
 
+\usepackage{xcolor}
+\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
+\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
+\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Place your title below. Use Title Capitalization.
-\title{On Sample Size for Block Bootstrap Confidence Intervals 
+\title{On Sample Size Needed for Block Bootstrap Confidence Intervals
   to Have Desired Coverage Rates}
@@
 \section*{keywords} 
-List Eight to Ten Capitalized Keywords Separated by \ul{Semicolons}; Do Not Use Period at The End
+% List Eight to Ten Capitalized Keywords Separated by \ul{Semicolons}; Do Not Use Period at The End
 Dependent Data; Resampling; Simulation; Time Series
@@
 % If you add additional section or subsection headings, use an asterisk * to avoid numbering.
+
+\jy{Are the results from exponential margins the same? If so, we can put them in
+  an appendix; make sure we have the data generation process accurately
+  described. Then briefly summarize and refer to it at the end of the simulation
+  section.}
+
+\jy{The 80-width is for maximum. No need to re-wrap shorter lines because it
+  would show a lot of diff while there is no diff.}
 
@@
 
+\jy{The fonts of labels/annotatios in these figures are too big compared to the
+  captions. Try pointsize = 9. The plots also seem oversized. Generate them in R
+  with the right size in mind.}
+
 \begin{figure}[tbp]
@@
 
+\jy{Could do one for the exponential margin study too. Maybe for the negative dependence.}
+
 The outcomes of the $\phi$ estimation raise a natural question about the 
@@
 
+\appendix
+
+\section{Simulation Study with Exponential Marginal Distribution}
+
+\jy{Motivation; data generation (calibration of copula parameters to give the
+  desired rho); simulation design; plots; brief discussion of results.}
+
 \bibliographystyle{chicago}

### 2023-08-26 Code/copula.R
copula.R can run now

@@ -1,6 +1,7 @@
 ## Need packages copula and pracma
 
-myd <- dMv
+library(copula)
+
 mymvd <- copula::mvdc(normalCopula(0.4), margins = "exp", paramMargins = list(rate=1), marginsIdentical = TRUE)
 
 ## numerical integration to get 

### 2023-08-26 Manuscript/manuscript.tex
Update, not finished

@@
 bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
-order auto-regressive (AR(1)) process:
+order autoregressive (AR(1)) process:
 \begin{equation}
@@
 \end{equation}
-where $\phi$ is an auto-regressive coefficient, and $\epsilon_t$ is a series of
+where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
 independent errors from a normal distribution with mean zero and variance
@@
 2) $\sigma_x = 1$, the standard deviation of $X_t$; and
-3) $\phi$, the lag-1 auto-correlation coefficient.
+3) $\phi$, the lag-1 autocorrelation coefficient.
 To investigate the effect of sample size~$n$, we considered an array of values
@@
 $\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
-and lag-1 auto-correlation, respectively, of each bootstrap sample. Then we can 
+and lag-1 autocorrelation, respectively, of each bootstrap sample. Then we can 
 construct intervals for each parameter using the appropriate procedures 
@@
   captions. Try pointsize = 9. The plots also seem oversized. Generate them in R
-  with the right size in mind.}
+  with the right size in mind.} \mc{addressed}
 
@@
 
-For estimating the auto-correlation parameter~$\phi$, 
+For estimating the autocorrelation parameter~$\phi$, 
 \textbf{Figure~\ref{fig:phi}} suggests that while standard, Student's $t$, and 
@@
 
+An additional simulation study in which block bootstrap is used to estimate 
+parameters of an AR(1) process with an underlying exponential marginal 
+distribution is discussed in the appendix.
+
 \section*{discussion}
@@
 
-\section{Simulation Study with Exponential Marginal Distribution}
+\section*{Simulation Study with Exponential Marginal Distribution}
 
@@
   desired rho); simulation design; plots; brief discussion of results.}
+
+This appendix concerns the performance of block bootstrap when used to estimate
+the mean, standard deviation, and the lag-1 autocorrelation coefficient of a 
+AR(1) process with an underlying exponential marginal distribution. The 
+motivation for this additional simulation study was to observe if the results of 
+the main simulation study will change if the underlying marginal distribution is
+not normal. The data
 

### 2023-08-26 Code/functions.R

@@ -107,13 +107,14 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
   
   ggplot(data, aes(x = n, y = cov)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
-    geom_line() +
-    geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
+    geom_line(size = .2) +
+    geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width, size = .2) +
     facet_grid(factor(CI) ~ factor(phi), scales = 'free') +
     labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
-            element_text(family = "EB Garamond")) +
+            element_text(family = "EB Garamond", size = 9),
+          strip.text.y = element_text(angle = 0, hjust = 1)) +
     scale_y_continuous(trans=trans)
-  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), height = 6)
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), height = 3)
 }

### 2023-08-26 Code/neg_phi_intervals.R

@@ -1,0 +1,60 @@
+source("functions.R")
+library(ggplot2)
+library(showtext)
+
+set.seed(1234)
+sim <- replicate(50, do1rep(800, -0.4, mystat, 10))
+new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
+
+file_titles <- c("pct", "bc", "prop")
+custom_titles <- c("Percentile", "BC", "Recentered")
+
+plot_data_800 <- data.frame(replication = 1:50,
+                            point_estimate = new_sim[1, ],
+                            bts_mean = new_sim[2, ],
+                            lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
+                            upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
+                            file_title = rep(file_titles, each = 50),
+                            custom_title = rep(custom_titles, each = 50),
+                            sample.size = rep("n = 800", 150))
+
+set.seed(1234)
+sim <- replicate(50, do1rep(1600, -0.4, mystat, 10))
+new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
+
+plot_data_1600 <- data.frame(replication = 1:50,
+                             point_estimate = new_sim[1, ],
+                             bts_mean = new_sim[2, ],
+                             lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
+                             upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
+                             file_title = rep(file_titles, each = 50),
+                             custom_title = rep(custom_titles, each = 50),
+                             sample.size = rep("n = 1600", 150))
+
+plot_data <- rbind(plot_data_800, plot_data_1600)
+
+plot_data$custom_title <- factor(plot_data$custom_title, 
+                                 levels = c("Percentile", "BC", "Recentered"))
+
+plot_data$sample.size <- factor(plot_data$sample.size,
+                                levels = c("n = 800", "n = 1600"))
+
+font_add_google("EB Garamond")
+#  windows()
+
+showtext_auto()
+
+ggplot(plot_data, aes(x = replication, y = point_estimate)) +
+  geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound), width = 0.5, color = 'gray') +
+  geom_point(color = 'blue') +
[…]

### 2023-08-26 Manuscript/manuscript.tex
Update, still need to make format changes

@@
   described. Then briefly summarize and refer to it at the end of the simulation
-  section.}
+  section.} \mc{addressed}
 
@@
   would show a lot of diff while there is no diff.}
+\mc{addressed}
 
@@
 construct intervals for each parameter using the appropriate procedures 
-described in \textit{Block Bootstrap CIs}. Then we estimated their actual coverage 
+described in \textit{Block Bootstrap CIs}. 
+Then we estimated their actual coverage 
 rates along with their 95\% confidence intervals from the 10000 replicates. The 
@@
 
-\jy{Could do one for the exponential margin study too. Maybe for the negative dependence.}
+\jy{Could do one for the exponential margin study too. 
+Maybe for the negative dependence.}
+\mc{created negative dependence plots not included in manuscript yet}
 
@@
   desired rho); simulation design; plots; brief discussion of results.}
+\mc{addressed}
 
@@
 the main simulation study will change if the underlying marginal distribution is
-not normal. The data
+not normal.
+
+We generated time series $X_t$ from a 1st order autoregressive 
+(AR(1)) process as we did previously, but transformed the data from a standard
+normal distribution to an exponential distribution with rate $\lambda = 1$, so 
+that for $t \in \{1, \ldots, n\}$, we can define:
+\begin{equation}
+W_t = F^{-1}(\Phi(X_t), 1)
+\end{equation}
+where $F^{-1}(p, \lambda)$ is the quantile function for the exponential 
+distribution with rate parameter $\lambda$.
+
+The simulation design was the same, except the target parameters of $W_t$ were:
+1) $\mu = 1$, the mean of $W_t$;
+2) $\sigma_w = 1$, the standard deviation of $W_t$; and
+3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$
+Although we may have set $\phi$ to these five levels for $X_t$: 
+$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
+the new five autocorrelation coefficients for $W_t$ will be different.
+\mc{I may need some help explaining the calibration of copula parameters}
+After calibrating the copula parameters, we can again plot empirical coverage 
+rates and the 95\% confidence intervals of the real coverage.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_mu}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of an AR(1) process with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
+    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_mu}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with AR 
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
+    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_sigma}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_rho}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient $\rho$ of an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
+    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_phi}
+\end{figure}
+
+Additionally, another set of 50 CIs was generated for each of the percentile, 
+BC, and recentered percentile approaches for exponentially distributed
+samples of $n \in \{800, 1600\}$.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/exp_rho_intervals}
+  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
+    samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$ 
+    transformed to an exponential distribution iwth $\lambda = 1$. For 
+    each replicate, the lower and upper bounds of the CIs are displayed, as well 
+    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
+  \label{fig:eri}
+\end{figure}
+
+Although there are differences in the ranges of sample sizes needed to cover 
+parameters of a normally distributed AR(1) process versus an exponentially 
+distributed AR(1) process, the trends and patterns are generally the same.
+Student's $t$ CIs still appear to yield higher coverage rates than other 
+methods. Performance is still generally better when temporal dependence is 
+negative rather than positive. Most importantly, percentile, BC, and BCA CIs
+still deteriorate in coverage of $\rho$ as sample size increases. As exhibited 
+in \textbf{Figure~\ref{fig:eri}}, percentile and BC CIs still have the same bias
+issue.
 

### 2023-08-26 Manuscript/manuscript.tex
Changed citations and bibliography order according to AJUR Guide

@@
 inferences about dependent data. Essentially, it depends on correct estimation
-of the uncertainty in the estimation, similar to the standard bootstrap
-\citep{efron1979bootstrap} but for serially dependent data. Early ideas of block
-bootstrap were developed not long after the standard bootstrap 
-\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife}. It has since
-been applied in various fields, for instance, econometrics
-\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
+of the uncertainty in the estimation, similar to the standard bootstrap - 
+originated by \citet{efron1979bootstrap} - but for serially dependent data.
+\mc{style guide says to have citations after punctuation, not sure what to do 
+with textual citations}
+Early ideas of block
+bootstrap were developed not long after the standard 
+bootstrap.\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife} It 
+has since
+been applied in various fields, for instance, econometrics and 
+meteorology.\citep{mackinnon2006bootstrap, varga2017generalised}
 Block bootstrap is especially useful for serially dependent data when the serial 
@@
 standard deviation, and the first-order autocorrelation coefficient. We compare 
-six variants of block bootstrap CIs from the literature
-\citep{diciccio1996bootstrap, rice2006mathematical}: a standard normal CI, a 
+six variants of block bootstrap CIs from the 
+literature:\citep{diciccio1996bootstrap, rice2006mathematical} a standard normal 
+CI, a 
 Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and 
@@
 To achieve this, $l$ is often assigned a value as a function of $n$. A common 
-function that is considered optimal is $l = \lceil n^{1/3} \rceil$ 
-\citep{buhlmann1999block}, which was adopted in this study.
+function that is considered optimal is $l = \lceil n^{1/3} \rceil$,\citep{buhlmann1999block} 
+which was adopted in this study.
 
@@
 $\theta$ as the mean, we just need an estimate of the standard error to 
-construct an approximate CI \citep[p.168]{efron1993introduction}. Let
+construct an approximate CI.\citep[p.168]{efron1993introduction} Let
 $\widehat{\text{SE}}$ be the empirical standard error of the bootstrap point 
@@
 block bootstrap sampling step was done with function \texttt{tsboot} from R 
-package \textsl{boot} \citep{boot}, with block size $\lceil n / l \rceil$. This 
+package \textsl{boot},\citep{boot} with block size $\lceil n / l \rceil$. This 
 function by default is an implementation of moving block bootstrap as described 
@@
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage, generated using the R \textsl{ggplot2} package \citep{ggplot2}.
+real coverage, generated using the R \textsl{ggplot2} package.\citep{ggplot2}
 
@@
 such as $ABC$ or bootstrap-t intervals, or alternatives to block bootstrap, such 
-as AR-Sieve bootstrap \citep{kreiss1992bootstrap}, that could more
+as AR-Sieve bootstrap,\citep{kreiss1992bootstrap} that could more
 appropriately recover the parameters of a time series. In addition, as noted by
@@
 \mc{I may need some help explaining the calibration of copula parameters}
-After calibrating the copula parameters, we can again plot empirical coverage 
+After calibrating the copula parameters using the \textsl{copula} and 
+\textsl{pracma} packages, \citep{copula, pracma} we can again plot empirical coverage 
 rates and the 95\% confidence intervals of the real coverage.
@@
 
-\bibliographystyle{chicago}
+\bibliographystyle{unsrtnat}
 \bibliography{citations}

### 2023-08-27 Manuscript/manuscript.tex
Attempt at Explaining Copula

@@
 $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
-the new five autocorrelation coefficients for $W_t$ will be different.
+the new five true autocorrelation coefficients for $W_t$ were different.
 \mc{I may need some help explaining the calibration of copula parameters}
-After calibrating the copula parameters using the \textsl{copula} and 
-\textsl{pracma} packages, \citep{copula, pracma} we can again plot empirical coverage 
-rates and the 95\% confidence intervals of the real coverage.
+To calibrate the copula parameters, we first constructed a multivariate
+exponential distribution from a normal copula using the \textsl{copula} package.
+\citep{copula} Then we computed $E[XY]$, which 
+requires double integration using the \textsl{pracma} package. \citep{pracma} 
+Finally, we obtained true $\rho = E[XY] - 1$, which was used as the target
+parameter when evaluating CI performance when estimating $\rho$.
+After this step, we again plotted empirical coverage 
+rates for $\mu$, $\sigma$, and $\rho$, as well as 95\% confidence intervals of 
+the real coverage. These are displayed in 
+\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_rho}}.
 
@@
     The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi}
+  \label{fig:exp_rho}
 \end{figure}

### 2023-08-27 Manuscript/manuscript.tex
comments on graphs and calibration

@@
 
-\jy{Are the results from exponential margins the same? If so, we can put them in
-  an appendix; make sure we have the data generation process accurately
-  described. Then briefly summarize and refer to it at the end of the simulation
-  section.} \mc{addressed}
-
-\jy{The 80-width is for maximum. No need to re-wrap shorter lines because it
-  would show a lot of diff while there is no diff.}
-\mc{addressed}
-
 \section*{introduction}
@@
 inferences about dependent data. Essentially, it depends on correct estimation
-of the uncertainty in the estimation, similar to the standard bootstrap - 
-originated by \citet{efron1979bootstrap} - but for serially dependent data.
-\mc{style guide says to have citations after punctuation, not sure what to do 
-with textual citations}
-Early ideas of block
-bootstrap were developed not long after the standard 
+of the uncertainty in the estimation, similar to the standard bootstrap 
+\citep{efron1979bootstrap}, but for serially dependent data.
+Early ideas of block bootstrap were developed not long after the standard 
 bootstrap.\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife} It 
@@
 Alternatively, block-bootstrap can be done with overlapping or moving blocks.
-Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$, 
-$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$ blocks 
+Define moving blocks
+\[
+Z_j = \{X_j, \ldots, X_{j + l - 1}\}, \quad, 
+j = 1, \ldots, n - l + 1.
+\]
+Now we draw $k$ blocks from the $(n - l + 1)$ blocks 
 of $Z_j$'s with replacement and then align them in the order they were picked to 
@@
 moving blocks (assuming $l > 1$) as:
-\begin{equation}
+\begin{equation*}
 Z_j =
@@
     \end{cases}
-\end{equation}
+\end{equation*}
 This version does not require that $n/l$ be an integer.
@@
 $\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
-Let 
-\begin{equation}
+Let \jy{No need to number an equation if it is not referred to}
+\begin{equation*}
 \hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
@@
   \hat{\theta}_{(i)})^2\}^{3/2}}.
-\end{equation}
+\end{equation*}
 Define
-\begin{equation}
+\begin{equation*}
 \alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
   z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
-\end{equation}
+\end{equation*}
 and
-\begin{equation}
+\begin{equation*}
 \alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
   z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
-\end{equation}
+\end{equation*}
 A $(1 - \alpha)100\%$ ~BCA CI is
@@
 order autoregressive (AR(1)) process:
-\begin{equation}
+\begin{equation*}
 X_t = \phi X_{t-1} + \epsilon_t,
-\end{equation}
+\end{equation*}
 where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
@@
 
-\jy{The fonts of labels/annotatios in these figures are too big compared to the
-  captions. Try pointsize = 9. The plots also seem oversized. Generate them in R
-  with the right size in mind.} \mc{addressed}
-
 \begin{figure}[tbp]
@@
 \end{figure}
+
+\jy{I like the font size of the labels and axis of Figure 4. They are still
+  overly large in Figures 1--3. The panel head is also too wide. The axis ticks
+  look crowded. The panel
+  labels on the right also does not look pretty. I'd prefer the old version if
+  the font sizes were smaller.}
 
@@
 
+\jy{Is textbf of Figure requried? Never manual formatting.}
 For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
@@
 CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
-other methods contain 95\%. The standard, percentile, BC, and BCA, and 
+other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
 recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
@@
 sizes when compared to other methods. Unlike $\mu$, there is no over-coverage 
-issue for $\sigma_x$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and 
+issue for $\sigma_x$ when $\phi = -0.4$. Standard normal, percentile, BC, BCA, and 
 recentered percentile CIs again have similar performance. All methods seem to 
@@
 For estimating the autocorrelation parameter~$\phi$, 
-\textbf{Figure~\ref{fig:phi}} suggests that while standard, Student's $t$, and 
+\textbf{Figure~\ref{fig:phi}} suggests that while standard normal, Student's $t$, and 
 recentered percentile CIs do approach correct coverage as sample size increases, 
@@
 the strength of the temporal dependence increases. Because of this, only 
-standard, Student's $t$, and recentered percentile CIs should be considered as 
+standard normal, Student's $t$, and recentered percentile CIs should be considered as 
 effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
@@
 not the dependence is negative or positive, coverage of $\phi$ seems to increase 
-slightly as the absolute value increases for standard, Student's $t$, and 
+slightly as the absolute value increases for standard normal, Student's $t$, and 
 recentered percentile CIs. For the values of $\phi$ observed, there are no 
-examples of over-coverage for standard, Student's $t$, BC, BCA, or recentered 
+examples of over-coverage for standard normal, Student's $t$, BC, BCA, or recentered 
 percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
@@
 \end{figure}
-
-\jy{Could do one for the exponential margin study too. 
-Maybe for the negative dependence.}
-\mc{created negative dependence plots not included in manuscript yet}
 
@@
 intervals used in this study, this assumption was found to hold true with 
-respect to estimating $\phi$ only for standard, Student's $t$, and recentered 
+respect to estimating $\phi$ only for standard normal, Student's $t$, and recentered 
 percentile CIs, whereas percentile, BC, and BCA intervals exhibited coverage 
@@
 
-\appendix
-
-\section*{Simulation Study with Exponential Marginal Distribution}
-
-\jy{Motivation; data generation (calibration of copula parameters to give the
-  desired rho); simulation design; plots; brief discussion of results.}
-\mc{addressed}
+\section*{Appendix: Simulation Study with Exponential Marginal Distribution}
 
@@
 the mean, standard deviation, and the lag-1 autocorrelation coefficient of a 
-AR(1) process with an underlying exponential marginal distribution. The 
+AR(1) process with an underlying unit exponential marginal distribution. The
 motivation for this additional simulation study was to observe if the results of 
@@
 that for $t \in \{1, \ldots, n\}$, we can define:
-\begin{equation}
+\begin{equation*}
 W_t = F^{-1}(\Phi(X_t), 1)
-\end{equation}
+\end{equation*}
 where $F^{-1}(p, \lambda)$ is the quantile function for the exponential 
@@
 \mc{I may need some help explaining the calibration of copula parameters}
+
 To calibrate the copula parameters, we first constructed a multivariate
@@
 \textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_rho}}.
+
+\jy{Let $\rho$ and $\phi$ be the autocorrelation coefficient of $X_t$ and $W_t$,
+  respectively. There is a 1-1 map between $\rho$ to $\phi$. You already figured
+  out how to transform from $\rho$ to $\phi$. Now we want $\phi$ to be, say,
+  0.4, you can calibrate $\rho$ to give you the desired value. This only need to
+  be done once before your run your simulation. }
+
+\jy{cite the copula book instead of the package}
+
+\jy{comment on the similarity of the results with those reported in the main text.}
 
@@
 still deteriorate in coverage of $\rho$ as sample size increases. As exhibited 
-in \textbf{Figure~\ref{fig:eri}}, percentile and BC CIs still have the same bias
+in Figure~\ref{fig:eri}, percentile and BC CIs still have the same bias
 issue.

### 2023-08-27 Manuscript/manuscript.tex
Responded to Some Comments

@@
 Let \jy{No need to number an equation if it is not referred to}
+\mc{addressed}
 \begin{equation*}
@@
   the font sizes were smaller.}
+\mc{addressed}
 
@@
 \jy{Is textbf of Figure requried? Never manual formatting.}
+\mc{The guide says "When you need to refer to Figure 1, Reference 1, Table 1, 
+Scheme 1, Step 1, and Equation 1 please bold those words in the text (size 10) 
+and in the title (size eight)." If I don't use textbf, the references don't get
+bolded by default.}
 For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
@@
 exponential distribution from a normal copula using the \textsl{copula} package.
-\citep{copula} Then we computed $E[XY]$, which 
+\citep{nelsen2006introduction} Then we computed $E[XY]$, which 
 requires double integration using the \textsl{pracma} package. \citep{pracma} 
@@
 
-\jy{cite the copula book instead of the package}
+\jy{cite the copula book instead of the package} \mc{i cited the nelsen book 
+referenced in the manual}
 
-\jy{comment on the similarity of the results with those reported in the main text.}
+\jy{comment on the similarity of the results with those reported in the main 
+text.} \mc{addressed}
 
@@
 
-Although there are differences in the ranges of sample sizes needed to cover 
-parameters of a normally distributed AR(1) process versus an exponentially 
-distributed AR(1) process, the trends and patterns are generally the same.
-Student's $t$ CIs still appear to yield higher coverage rates than other 
+Iit seems that range of sample sizes needed 
+to cover parameters of an exponentially distributed AR(1) process is generally 
+higher than that needed to cover parameters of a normally.
+distributed AR(1) process. Despite this, the trends and patterns discussed 
+previously with respect
+to the performance of different methods and with different parameters are the 
+same.
+For instance, Student's $t$ CIs still appear to yield higher coverage rates than 
+other 
 methods. Performance is still generally better when temporal dependence is 
@@
 in Figure~\ref{fig:eri}, percentile and BC CIs still have the same bias
-issue.
+issue. Overall, the results with an underlying marginal exponential distribution 
+are very similar to the results with an underlying normal distribution from the
+main study.
 

### 2023-08-27 Code/functions.R

@@ -113,8 +113,8 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
     labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
-            element_text(family = "EB Garamond", size = 9),
-          strip.text.y = element_text(angle = 0, hjust = 1)) +
+            element_text(family = "EB Garamond", size = 10),
+          strip.text.y = element_text(angle = 270, hjust = 1)) +
     scale_y_continuous(trans=trans)
-  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), height = 3)
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10)
 }

### 2023-08-28 Manuscript/manuscript.tex
demo for rho2phi and comments on details

@@
 $\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
-Let \jy{No need to number an equation if it is not referred to}
-\mc{addressed}
+Let
 \begin{equation*}
@@
 
+\subsection*{Results}
+
+\jy{I'd slightly increase the heights of the figures such that two of them
+  would occupied a whole page. This reduces the complexity of floating in
+  finding best locations.}
+
+\jy{Clarify normal margins in captions.}
+
 \begin{figure}[tbp]
@@
 \end{figure}
-
-\jy{I like the font size of the labels and axis of Figure 4. They are still
-  overly large in Figures 1--3. The panel head is also too wide. The axis ticks
-  look crowded. The panel
-  labels on the right also does not look pretty. I'd prefer the old version if
-  the font sizes were smaller.}
-\mc{addressed}
 
@@
 
-\subsection*{Results}
-
-\jy{Is textbf of Figure requried? Never manual formatting.}
-\mc{The guide says "When you need to refer to Figure 1, Reference 1, Table 1, 
-Scheme 1, Step 1, and Equation 1 please bold those words in the text (size 10) 
-and in the title (size eight)." If I don't use textbf, the references don't get
-bolded by default.}
 For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
@@
 \mc{I may need some help explaining the calibration of copula parameters}
+\jy{see demo code in \texttt{copula.R}}
 
@@
 
-\jy{Let $\rho$ and $\phi$ be the autocorrelation coefficient of $X_t$ and $W_t$,
-  respectively. There is a 1-1 map between $\rho$ to $\phi$. You already figured
-  out how to transform from $\rho$ to $\phi$. Now we want $\phi$ to be, say,
-  0.4, you can calibrate $\rho$ to give you the desired value. This only need to
-  be done once before your run your simulation. }
-
 \jy{cite the copula book instead of the package} \mc{i cited the nelsen book 
 referenced in the manual}
+\jy{Cite my book on the copula package}
 
-\jy{comment on the similarity of the results with those reported in the main 
-text.} \mc{addressed}
+\jy{Let's call this process marginally transformed AR(1) proess. Itself is not
+  an AR(1) process. Correct the captions.}
 
@@
 
+\jy{comment on that the recentered percentile CI for autocorrelation still works
+  as the point estimator is unbiased.}
+
 \bibliographystyle{unsrtnat}

### 2023-08-28 Code/copula.R

@@ -1,6 +1,7 @@
 ## Need packages copula and pracma
 
 library(copula)
+library(pracma)
 
 mymvd <- copula::mvdc(normalCopula(0.4), margins = "exp", paramMargins = list(rate=1), marginsIdentical = TRUE)
 
@@ -13,3 +14,19 @@ rho <- (EXY - 1) / 1
 ## empirical check
 z <- rMvdc(100000, mymvd)
 cor(z[,1], z[,2])
+
+
+
+rho2phi <- function(rho) {
+    mymvd <- copula::mvdc(copula::normalCopula(rho), margins = "exp",
+                          paramMargins = list(rate=1), marginsIdentical = TRUE)
+    EXY <- pracma::dblquad(function(x, y) x * y * copula::dMvdc(cbind(x, y), mymvd),
+                           0, 20, 0, 20)
+    phi <- (EXY - 1) / 1
+    phi
+}
+
+uniroot(function(x) rho2phi(x) - 0.4, interval = c(0, 0.9))
+
+uniroot(function(x) rho2phi(x) + 0.4, interval = c(-.56, 0))
+    

### 2023-08-28 Manuscript/manuscript.tex
two comments

@@
 \author{
-Mathew Chandy*$^{a}$, Elizabeth Schifano$^{a}$, Jun Yan$^{a}$ \\ \medskip 
+Mathew Chandy*$^{a}$, Elizabeth D. Schifano$^{a}$, Jun Yan$^{a}$ \\ \medskip 
 $^{a}$Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
@@
 the desired coverage rates.
+\eds{I think the superscript citations need to go before the punctuation.  
+Please check in other AJUR papers and adjust throughout the paper if needed.}
 
@@
 \[
-Z_j = \{X_j, \ldots, X_{j + l - 1}\}, \quad, 
+Z_j = \{X_j, \ldots, X_{j + l - 1}\}, \quad 
 j = 1, \ldots, n - l + 1.
@@
 \]
+\eds{If $z_{(\alpha)}$ is the upper quantile, then $z_{(\alpha/2)}$ will be 
+positive and $z_{(1-\alpha/2)}$ will be negative for small $\alpha$ values; with
+the subtraction of the quantiles, the smaller CI endpoint would appear to
+be listed first.  Please check this notation, and the notation for Student's $t$ 
+CI, and other intervals which use the $z_{(\alpha)}$ upper standard normal 
+quantile.} 
 This CI is centered by the original point estimate $\hat\theta_n$ and is 
@@
 parameters of an AR(1) process with an underlying exponential marginal 
-distribution is discussed in the appendix.
+distribution is discussed in the Appendix. Overall, the results with an 
+underlying marginal exponential distribution are very similar to the results 
+with an underlying normal distribution discussed above.
 
@@
 \begin{equation*}
-W_t = F^{-1}(\Phi(X_t), 1)
+W_t = F^{-1}(\Phi(X_t), 1),
 \end{equation*}
@@
 2) $\sigma_w = 1$, the standard deviation of $W_t$; and
-3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$
+3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$.
 Although we may have set $\phi$ to these five levels for $X_t$: 
@@
 After this step, we again plotted empirical coverage 
-rates for $\mu$, $\sigma$, and $\rho$, as well as 95\% confidence intervals of 
+rates for $\mu$, $\sigma_w$, and $\rho$, as well as 95\% confidence intervals of 
 the real coverage. These are displayed in 
@@
 
-Iit seems that range of sample sizes needed 
+It seems that range of sample sizes needed 
 to cover parameters of an exponentially distributed AR(1) process is generally 
-higher than that needed to cover parameters of a normally.
+higher than that needed to cover parameters of a normally
 distributed AR(1) process. Despite this, the trends and patterns discussed 

### 2023-08-29 Manuscript/manuscript.tex
BCA Error

@@
 Please check in other AJUR papers and adjust throughout the paper if needed.}
+\mc{from the style guide: "Please bold and superscript the numbers for 
+references in the text.1 Separate superscripted numbers by comma and space,1, 2 
+they should be separated by an en-dash if the consecutive list of more than two 
+numbers is used.1–3 List them AFTER punctuation (be it comma or period) with no 
+space.2}
 
@@
 estimates $\hat\theta_n^{(b)}$ for $b \in \{1, \ldots, B\}$. Let $z_{(\alpha)}$ 
-be the upper $\alpha$ quantile of the standard normal distribution. 
+be the quantile function $F^{-1}(\alpha)$ of the standard normal distribution. 
 A $(1 - \alpha)100\%$ standard normal CI is
@@
 quantile.} 
+\mc{Replaced upper quantile with quantile function}
 This CI is centered by the original point estimate $\hat\theta_n$ and is 
@@
 described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
-upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom. With 
+quantile function $F^{-1}(\alpha, k)$ of a $t$ distribution with $k$ degrees of 
+freedom. With 
 block bootstrapping, 
@@
   finding best locations.}
+\mc{addressed}
 
 \jy{Clarify normal margins in captions.}
+\mc{addressed}
 
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with AR coefficient
+    the marginal mean $\mu$ of an AR(1) process with an underlying standard 
+    normal distribution with AR coefficient
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with AR 
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with an 
+    underlying standard normal distribution with AR 
     coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
@@
     the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    an underlying standard normal distribution with 
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
@@
 2) $\sigma_w = 1$, the standard deviation of $W_t$; and
-3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$.
-Although we may have set $\phi$ to these five levels for $X_t$: 
+3) $\phi$, the lag-1 autocorrelation coefficient of $W_t$.
+Let $\rho$ be the lag-1 autocorrelation coefficient of $X_t$.
+Although we may have set $\rho$ to these five levels for $X_t$: 
 $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
@@
 To calibrate the copula parameters, we first constructed a multivariate
-exponential distribution from a normal copula using the \textsl{copula} package.
-\citep{nelsen2006introduction} Then we computed $E[XY]$, which 
+exponential distribution from a normal copula with 
+$\rho \in \{-0.4, -0.2, 0.0, 0.2, 0.4\} $using the \textsl{copula} package.
+\citep{hofert2018elements} Then we computed $E[XY]$, which 
 requires double integration using the \textsl{pracma} package. \citep{pracma} 
-Finally, we obtained true $\rho = E[XY] - 1$, which was used as the target
-parameter when evaluating CI performance when estimating $\rho$.
+Finally, we obtained true $\phi = E[XY] - 1$, which was used as the target
+parameter when evaluating CI performance when estimating $\phi$.
 After this step, we again plotted empirical coverage 
-rates for $\mu$, $\sigma_w$, and $\rho$, as well as 95\% confidence intervals of 
+rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\% confidence intervals of 
 the real coverage. These are displayed in 
-\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_rho}}.
+\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}.
 
@@
 \jy{Cite my book on the copula package}
+\mc{addressed}
 
@@
   an AR(1) process. Correct the captions.}
+\mc{addressed}
 
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with AR coefficient
+    the marginal mean $\mu$ of a marginally transformed AR(1) process with an 
+    underlying exponential distribution ($\lambda = 1$) with AR 
+    coefficient
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ with
     an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with AR 
+    the marginal standard deviation $\sigma_x$ of a marginally transformed AR(1) 
+    process with an 
+    underlying exponential distribution ($\lambda = 1$) with AR 
     coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_rho}
+  \includegraphics[width=\textwidth]{figures/plot_exp_phi}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\rho$ of an AR(1) process with
+    the first-order autocorrelation coefficient $\phi$ of a marginally 
+    transformed AR(1) process with 
+    an 
+    underlying exponential distribution ($\lambda = 1$) with
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
@@
     The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_rho}
+  \label{fig:exp_phi}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/exp_rho_intervals}
+  \includegraphics[width=\textwidth]{figures/exp_pho_intervals}
   \caption{50 replicate percentile, BC, and recentered percentile CIs for 
@@
 negative rather than positive. Most importantly, percentile, BC, and BCA CIs
-still deteriorate in coverage of $\rho$ as sample size increases. As exhibited 
+still deteriorate in coverage of $\phi$ as sample size increases. As exhibited 
 in Figure~\ref{fig:eri}, percentile and BC CIs still have the same bias

### 2023-08-29 Code/copula.R

@@ -26,7 +26,19 @@ rho2phi <- function(rho) {
     phi
 }
 
-uniroot(function(x) rho2phi(x) - 0.4, interval = c(0, 0.9))
+rho <- c()
+names(rho) <- c()
 
-uniroot(function(x) rho2phi(x) + 0.4, interval = c(-.56, 0))
+rho['-0.4'] <- uniroot(function(x) rho2phi(x) + 0.4, interval = c(-.56, 0))$root
+
+rho['-0.2'] <- uniroot(function(x) rho2phi(x) + 0.2, interval = c(-.56, 0))$root
+
+rho['0'] <- uniroot(function(x) rho2phi(x) - 0, interval = c(0, 0.9))$root
+
+rho['0.2'] <- uniroot(function(x) rho2phi(x) - 0.2, interval = c(0, 0.9))$root
+
+rho['0.4'] <- uniroot(function(x) rho2phi(x) - 0.4, interval = c(0, 0.9))$root
+
+saveRDS(rho, file = '../Data/rho')
+
     

### 2023-08-29 Code/exp_phi_intervals.R

@@ -45,20 +45,11 @@ font_add_google("EB Garamond")
 
 showtext_auto()
 
-mymvd <- copula::mvdc(normalCopula(0.4), margins = "exp", 
-                      paramMargins = list(rate=1), marginsIdentical = TRUE)
-
-## numerical integration to get 
-EXY <- pracma::dblquad(function(x, y) x * y * 
-                         copula::dMvdc(cbind(x, y), mymvd), 0, 20, 0, 20)
-## approximate true rho
-rho <- (EXY - 1) / 1
-
 ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound), width = 0.5, color = 'gray') +
   geom_point(color = 'blue') +
   geom_point(aes(y = bts_mean), color = 'red', shape = 'cross') +
-  geom_hline(yintercept = rho, linetype = "dotted") +
+  geom_hline(yintercept = 0.4, linetype = "dotted") +
   facet_grid(custom_title ~ sample.size) +
   labs(x = 'Replication', y = 'Value') +
   scale_color_manual(values = c('blue', 'red', 'gray')) +
@@ -67,4 +58,5 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   theme(strip.text=element_text(size=10), text =
           element_text(family = "EB Garamond"))
 
-ggsave('../Manuscript/figures/exp_rho_intervals.pdf', width = 10)
+ggsave('../Manuscript/figures/exp_phi_intervals.pdf', width = 10,
+       height = 5)

### 2023-08-29 Code/exp_processing.R

@@ -1,5 +1,4 @@
 source("functions.R")
-library(copula)
 setwd("../Data")
 file_names <- list.files(pattern = "^exp_results")
 all_lists <- lapply(file_names, function(x) {
@@ -14,24 +13,17 @@ combined_matrices <- lapply(grouped_matrices, function(x) {
 df <- data.frame(phi = numeric(), n = numeric(), CI = character(), 
                  target = character(), cov = numeric(),
                  LB = numeric(), UB = numeric())
+nrep = 10000
 for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
-  mymvd <- copula::mvdc(normalCopula(phi), margins = "exp", 
-                        paramMargins = list(rate=1), marginsIdentical = TRUE)
-  
-  ## numerical integration to get 
-  EXY <- pracma::dblquad(function(x, y) x * y * 
-                           copula::dMvdc(cbind(x, y), mymvd), 0, 20, 0, 20)
-  ## approximate true rho
-  rho <- (EXY - 1) / 1
-  cov <- mychk(combined_matrices[[i]], c(1, 1, rho))
+  cov <- mychk(combined_matrices[[i]], c(1, 1, phi))
   types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'bcCI', 'bcaCI', 'propCI')
   CI <- rep(types, each = length(cov) / length(types))
-  parameters <- c('mu', 'sigma', 'rho')
+  parameters <- c('mu', 'sigma', 'phi')
   target <- rep(parameters, length(cov) / length(parameters))
-  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
-  UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
+  LB <- sapply(cov, function(j) prop.test(j*nrep, nrep)$conf.int[1])
+  UB <- sapply(cov, function(j) prop.test(j*nrep, nrep)$conf.int[2])
   new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), CI, target, cov, LB, UB)
   df <- rbind(df, new_rows)
 }
@@ -44,6 +36,8 @@ t <- 'sigma'
 exp_sigma <- df[(df$target == t),]
[…]

### 2023-08-29 Code/functions.R

@@ -1,6 +1,17 @@
 .libPaths("~/rlibs")
 library(ggplot2) 
 library(showtext)
+# library(copula)
+# library(pracma)
+
+# rho2phi <- function(rho) {
+#  mymvd <- copula::mvdc(copula::normalCopula(rho), margins = "exp",
+#                        paramMargins = list(rate=1), marginsIdentical = TRUE)
+#  EXY <- pracma::dblquad(function(x, y) x * y * copula::dMvdc(cbind(x, y), mymvd),
+#                         0, 20, 0, 20)
+#  phi <- (EXY - 1) / 1
+#  phi
+# }
 
 mystat <- function(x) {
   c(mean(x),
@@ -86,11 +97,11 @@ mychk <- function(sim, target) {
   start <- length(target) * 2 + 1
   new_sim <- sim[start:nrow(sim), ]
   p <- nrow(new_sim) / length(target) / 2
-  target <- rep(target, p)
-  ret <- rep(NA, length(target))
+  t <- rep(target, p)
+  ret <- rep(NA, length(t))
   for (i in seq_along(ret)) {
     ii <- (i - 1) * 2
-    ret[i] <- mean(new_sim[ii + 1,] < target[i] & target[i] < new_sim[ii + 2,])
+    ret[i] <- mean(new_sim[ii + 1,] < t[i] & t[i] < new_sim[ii + 2,])
   }
   ret
 }
@@ -116,5 +127,6 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
             element_text(family = "EB Garamond", size = 10),
           strip.text.y = element_text(angle = 270, hjust = 1)) +
     scale_y_continuous(trans=trans)
-  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10)
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10,
+         height = 5)
 }

### 2023-08-29 Code/jobs.R

@@ -1,4 +1,5 @@
 source("functions.R")
+rho <- readRDS('../Data/rho')
 i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 norm_results <- list()
 names(norm_results) <- c()
@@ -11,9 +12,10 @@ for (phi in c(-.4, -.2, 0, .2, .4)) {
     sim <- replicate(100, do1rep(n, phi, mystat, blksize))
     norm_results[[paste(phi, n, sep = '_')]] <- sim
     set.seed(as.integer(i))
-    sim <- replicate(100, do1rep(n, phi, mystat, blksize, qexp))
+    sim <- replicate(100, do1rep(n, rho[paste(phi)], mystat, blksize, qexp))
     exp_results[[paste(phi, n, sep = '_')]] <- sim
   }
 }
+
 saveRDS(norm_results, paste('../Data/norm_results', '_', i, '.rds', sep = ''))
 saveRDS(exp_results, paste('../Data/exp_results', '_', i, '.rds', sep = ''))

### 2023-08-29 Code/jobs.sh

@@ -5,7 +5,7 @@
 #SBATCH --ntasks=1 ## OBS 1
 #SBATCH --cpus-per-task=1 ## OBS 2
 #SBATCH --mem-per-cpu=500M ## OBS 3
-#SBATCH --mail-type=FAIL                       # Event(s) that triggers email notification (BEGIN,END,FAIL,ALL)
+#SBATCH --mail-type=ALL                       # Event(s) that triggers email notification (BEGIN,END,FAIL,ALL)
 #SBATCH --mail-user=mathew.chandy@uconn.edu    
 
 module load r/4.2.2

### 2023-08-29 Code/neg_exp_phi_intervals.R

@@ -45,20 +45,11 @@ font_add_google("EB Garamond")
 
 showtext_auto()
 
-mymvd <- copula::mvdc(normalCopula(-0.4), margins = "exp", 
-                      paramMargins = list(rate=1), marginsIdentical = TRUE)
-
-## numerical integration to get 
-EXY <- pracma::dblquad(function(x, y) x * y * 
-                         copula::dMvdc(cbind(x, y), mymvd), 0, 20, 0, 20)
-## approximate true rho
-rho <- (EXY - 1) / 1
-
 ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound), width = 0.5, color = 'gray') +
   geom_point(color = 'blue') +
   geom_point(aes(y = bts_mean), color = 'red', shape = 'cross') +
-  geom_hline(yintercept = rho, linetype = "dotted") +
+  geom_hline(yintercept = -0.4, linetype = "dotted") +
   facet_grid(custom_title ~ sample.size) +
   labs(x = 'Replication', y = 'Value') +
   scale_color_manual(values = c('blue', 'red', 'gray')) +
@@ -67,4 +58,4 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   theme(strip.text=element_text(size=10), text =
           element_text(family = "EB Garamond"))
 
-ggsave('../Manuscript/figures/neg_rho_intervals.pdf', width = 10)
+ggsave('../Manuscript/figures/neg_exp_phi_intervals.pdf', width = 10)

### 2023-08-29 Code/norm_processing.R

@@ -13,6 +13,7 @@ combined_matrices <- lapply(grouped_matrices, function(x) {
 df <- data.frame(phi = numeric(), n = numeric(), CI = character(), 
                  target = character(), cov = numeric(),
                  LB = numeric(), UB = numeric())
+nrep = 10000
 for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
@@ -21,8 +22,8 @@ for(i in names(combined_matrices)) {
   CI <- rep(types, each = length(cov) / length(types))
   parameters <- c('mu', 'sigma', 'phi')
   target <- rep(parameters, length(cov) / length(parameters))
-  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
-  UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
+  LB <- sapply(cov, function(j) prop.test(j*nrep, nrep)$conf.int[1])
+  UB <- sapply(cov, function(j) prop.test(j*nrep, nrep)$conf.int[2])
   new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), CI, target, cov, LB, UB)
   df <- rbind(df, new_rows)
 }
@@ -38,3 +39,5 @@ write.csv(norm_sigma,"norm_sigma.csv", row.names = FALSE)
 t <- 'phi'
 norm_phi <- df[(df$target == t),]
 write.csv(norm_phi,"norm_phi.csv", row.names = FALSE)
+
+setwd("../Code")

### 2023-08-29 Code/plots.R

@@ -35,6 +35,6 @@ t <- 'exp_sigma'
 width <- .2
 graph_bts(t, width, exp_sigma)
 
-t <- 'exp_rho'
+t <- 'exp_phi'
 width <- .2
-graph_bts(t, width, exp_rho)
+graph_bts(t, width, exp_phi)

### 2023-08-29 Code/singlejob.R

@@ -4,13 +4,19 @@ names(norm_results) <- c()
 exp_results <- list()
 names(exp_results) <- c()
 phi <- -.4
-n = 100
+n = 3200
 blksize <- ceiling(n^(1/3))
-set.seed(as.integer(1))
+set.seed(13)
 sim <- replicate(100, do1rep(n, phi, mystat, blksize))
 norm_results[[paste(phi, n, sep = '_')]] <- sim
-set.seed(as.integer(1))
-sim <- replicate(100, do1rep(n, phi, mystat, blksize, qexp))
+set.seed(13)
+rho <- 0
+if (phi >= 0) {
+  rho <- uniroot(function(x) rho2phi(x) - phi, interval = c(0, 0.9))$root
+} else {
+  rho <- uniroot(function(x) rho2phi(x) - phi, interval = c(-.56, 0))$root
+}
+sim <- replicate(100, do1rep(n, rho, mystat, blksize, qexp))
 exp_results[[paste(phi, n, sep = '_')]] <- sim
 
 saveRDS(norm_results, '../Data/norm_result.rds')

### 2023-08-29 Manuscript/manuscript.tex
removed addressed comments

@@
 \newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
-\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}
+\newcommand{\mc}[1]{\textcolor{orange}{MC: (#1)}}
 
@@
 
-\jy{I'd slightly increase the heights of the figures such that two of them
-  would occupied a whole page. This reduces the complexity of floating in
-  finding best locations.}
-\mc{addressed}
-
-\jy{Clarify normal margins in captions.}
-\mc{addressed}
-
 \begin{figure}[tbp]
@@
 the new five true autocorrelation coefficients for $W_t$ were different.
-\mc{I may need some help explaining the calibration of copula parameters}
-\jy{see demo code in \texttt{copula.R}}
 
@@
 exponential distribution from a normal copula with 
-$\rho \in \{-0.4, -0.2, 0.0, 0.2, 0.4\} $using the \textsl{copula} package.
-\citep{hofert2018elements} Then we computed $E[XY]$, which 
-requires double integration using the \textsl{pracma} package. \citep{pracma} 
+$\rho \in \{-0.4, -0.2, 0.0, 0.2, 0.4\} $using the \texttt{copula} package.
+\citep{hofert2018ealements} Then we computed $E[XY]$, which 
+requires double integration using the \texttt{pracma} package. \citep{pracma} 
 Finally, we obtained true $\phi = E[XY] - 1$, which was used as the target
@@
 \textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}.
-
-\jy{cite the copula book instead of the package} \mc{i cited the nelsen book 
-referenced in the manual}
-\jy{Cite my book on the copula package}
-\mc{addressed}
-
-\jy{Let's call this process marginally transformed AR(1) proess. Itself is not
-  an AR(1) process. Correct the captions.}
-\mc{addressed}
 
@@
     samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$
+    \jy{not accurate}
     transformed to an exponential distribution iwth $\lambda = 1$. For 

### 2023-08-30 Manuscript/manuscript.tex

@@
 
+\jy{What was $B$?}
+
 Three target parameters of $X_t$ were considered:
@@
 An additional simulation study in which block bootstrap is used to estimate
+\jy{not an AR(1) process...}
 parameters of an AR(1) process with an underlying exponential marginal 

### 2023-08-30 Manuscript/manuscript.tex
Responded to Comments

@@
 
-\jy{What was $B$?}
+\jy{What was $B$?} \mc{addressed}
 
@@
 10000 replicates. For each replicate, we constructed six 95\% block bootstrap 
-CIs for each parameter as described in the last section. We can estimate $\mu$, 
+CIs for each parameter as described in the last section with $B = 1000$. We can 
+estimate $\mu$, 
 $\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
@@
 compared to that in the original sample. On the other hand, the original point 
-estimate $\hat\theta_n$ is asymptotically unbiased. Since the width is based on 
+estimator $\hat\theta_n$ is asymptotically unbiased. Since the width is based on 
 the uncertainty in the bootstrap point estimates $\hat\theta_n^{(b)}$, 
@@
 An additional simulation study in which block bootstrap is used to estimate
-\jy{not an AR(1) process...}
-parameters of an AR(1) process with an underlying exponential marginal 
-distribution is discussed in the Appendix. Overall, the results with an 
-underlying marginal exponential distribution are very similar to the results 
-with an underlying normal distribution discussed above.
+\jy{not an AR(1) process...} \mc{addressed}
+parameters of a marginally transformed AR(1) process with an underlying 
+exponential distribution is discussed in the Appendix.
 
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a marginally transformed AR(1) process with an 
-    underlying exponential distribution ($\lambda = 1$) with AR 
+    the marginal mean $\mu$ of a marginally transformed AR(1) process with AR 
     coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with an 
+    underlying exponential distribution ($\lambda = 1$) and series length
     $n \in \{100, 200, 400, 800, 1600, 3200\}$ with
@@
     the marginal standard deviation $\sigma_x$ of a marginally transformed AR(1) 
-    process with an 
-    underlying exponential distribution ($\lambda = 1$) with AR 
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
-    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
+    process with AR 
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with an 
+    underlying exponential distribution ($\lambda = 1$) and series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
     The error bars represent 95\% CIs of the real coverage rates.}
@@
     transformed AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with 
     an 
-    underlying exponential distribution ($\lambda = 1$) with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
-    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
+    underlying exponential distribution ($\lambda = 1$) and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
     The error bars represent 95\% CIs of the real coverage rates.}
@@
   \caption{50 replicate percentile, BC, and recentered percentile CIs for 
-    samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$
-    \jy{not accurate}
-    transformed to an exponential distribution iwth $\lambda = 1$. For 
+    samples of $n \in \{800, 1600\}$ for a marginally transformed AR(1) process 
+    with $\phi = 0.4$
+    \jy{not accurate} \mc{is this better}
+    with an underlying exponential distribution ($\lambda = 1$). For 
     each replicate, the lower and upper bounds of the CIs are displayed, as well 
@@
 still deteriorate in coverage of $\phi$ as sample size increases. As exhibited 
-in Figure~\ref{fig:eri}, percentile and BC CIs still have the same bias
-issue. Overall, the results with an underlying marginal exponential distribution 
+in Figure~\ref{fig:eri}, percentile and BC CIs still suffer from the same bias
+issue, whereas recentered percentile CI still work when estimating $\phi$ 
+because the 
+original point estimator is unbiased. Overall, the results with an underlying 
+marginal 
+exponential distribution 
 are very similar to the results with an underlying normal distribution from the
@@
 \jy{comment on that the recentered percentile CI for autocorrelation still works
-  as the point estimator is unbiased.}
+  as the point estimator is unbiased.} \mc{addressed}
 

### 2023-08-30 Code/copula.R
Revert changes

@@ -26,19 +26,7 @@ rho2phi <- function(rho) {
     phi
 }
 
-rho <- c()
-names(rho) <- c()
+uniroot(function(x) rho2phi(x) - 0.4, interval = c(0, 0.9))
 
-rho['-0.4'] <- uniroot(function(x) rho2phi(x) + 0.4, interval = c(-.56, 0))$root
-
-rho['-0.2'] <- uniroot(function(x) rho2phi(x) + 0.2, interval = c(-.56, 0))$root
-
-rho['0'] <- uniroot(function(x) rho2phi(x) - 0, interval = c(0, 0.9))$root
-
-rho['0.2'] <- uniroot(function(x) rho2phi(x) - 0.2, interval = c(0, 0.9))$root
-
-rho['0.4'] <- uniroot(function(x) rho2phi(x) - 0.4, interval = c(0, 0.9))$root
-
-saveRDS(rho, file = '../Data/rho')
-
+uniroot(function(x) rho2phi(x) + 0.4, interval = c(-.56, 0))
     

### 2023-08-30 Code/exp_processing.R

@@ -1,4 +1,5 @@
 source("functions.R")
+library(copula)
 setwd("../Data")
 file_names <- list.files(pattern = "^exp_results")
 all_lists <- lapply(file_names, function(x) {
@@ -13,17 +14,24 @@ combined_matrices <- lapply(grouped_matrices, function(x) {
 df <- data.frame(phi = numeric(), n = numeric(), CI = character(), 
                  target = character(), cov = numeric(),
                  LB = numeric(), UB = numeric())
-nrep = 10000
 for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
-  cov <- mychk(combined_matrices[[i]], c(1, 1, phi))
+  mymvd <- copula::mvdc(normalCopula(phi), margins = "exp", 
+                        paramMargins = list(rate=1), marginsIdentical = TRUE)
+  
+  ## numerical integration to get 
+  EXY <- pracma::dblquad(function(x, y) x * y * 
+                           copula::dMvdc(cbind(x, y), mymvd), 0, 20, 0, 20)
+  ## approximate true rho
+  rho <- (EXY - 1) / 1
+  cov <- mychk(combined_matrices[[i]], c(1, 1, rho))
   types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'bcCI', 'bcaCI', 'propCI')
   CI <- rep(types, each = length(cov) / length(types))
-  parameters <- c('mu', 'sigma', 'phi')
+  parameters <- c('mu', 'sigma', 'rho')
   target <- rep(parameters, length(cov) / length(parameters))
-  LB <- sapply(cov, function(j) prop.test(j*nrep, nrep)$conf.int[1])
-  UB <- sapply(cov, function(j) prop.test(j*nrep, nrep)$conf.int[2])
+  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
+  UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
   new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), CI, target, cov, LB, UB)
   df <- rbind(df, new_rows)
 }
@@ -36,8 +44,6 @@ t <- 'sigma'
 exp_sigma <- df[(df$target == t),]
[…]

### 2023-08-30 Code/functions.R

@@ -1,17 +1,6 @@
 .libPaths("~/rlibs")
 library(ggplot2) 
 library(showtext)
-# library(copula)
-# library(pracma)
-
-# rho2phi <- function(rho) {
-#  mymvd <- copula::mvdc(copula::normalCopula(rho), margins = "exp",
-#                        paramMargins = list(rate=1), marginsIdentical = TRUE)
-#  EXY <- pracma::dblquad(function(x, y) x * y * copula::dMvdc(cbind(x, y), mymvd),
-#                         0, 20, 0, 20)
-#  phi <- (EXY - 1) / 1
-#  phi
-# }
 
 mystat <- function(x) {
   c(mean(x),
@@ -97,11 +86,11 @@ mychk <- function(sim, target) {
   start <- length(target) * 2 + 1
   new_sim <- sim[start:nrow(sim), ]
   p <- nrow(new_sim) / length(target) / 2
-  t <- rep(target, p)
-  ret <- rep(NA, length(t))
+  target <- rep(target, p)
+  ret <- rep(NA, length(target))
   for (i in seq_along(ret)) {
     ii <- (i - 1) * 2
-    ret[i] <- mean(new_sim[ii + 1,] < t[i] & t[i] < new_sim[ii + 2,])
+    ret[i] <- mean(new_sim[ii + 1,] < target[i] & target[i] < new_sim[ii + 2,])
   }
   ret
 }
@@ -127,6 +116,5 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
             element_text(family = "EB Garamond", size = 10),
           strip.text.y = element_text(angle = 270, hjust = 1)) +
     scale_y_continuous(trans=trans)
-  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10,
-         height = 5)
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10)
 }

### 2023-08-30 Code/jobs.R

@@ -1,5 +1,4 @@
 source("functions.R")
-rho <- readRDS('../Data/rho')
 i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 norm_results <- list()
 names(norm_results) <- c()
@@ -12,10 +11,9 @@ for (phi in c(-.4, -.2, 0, .2, .4)) {
     sim <- replicate(100, do1rep(n, phi, mystat, blksize))
     norm_results[[paste(phi, n, sep = '_')]] <- sim
     set.seed(as.integer(i))
-    sim <- replicate(100, do1rep(n, rho[paste(phi)], mystat, blksize, qexp))
+    sim <- replicate(100, do1rep(n, phi, mystat, blksize, qexp))
     exp_results[[paste(phi, n, sep = '_')]] <- sim
   }
 }
-
 saveRDS(norm_results, paste('../Data/norm_results', '_', i, '.rds', sep = ''))
 saveRDS(exp_results, paste('../Data/exp_results', '_', i, '.rds', sep = ''))

### 2023-08-30 Code/jobs.sh

@@ -5,7 +5,7 @@
 #SBATCH --ntasks=1 ## OBS 1
 #SBATCH --cpus-per-task=1 ## OBS 2
 #SBATCH --mem-per-cpu=500M ## OBS 3
-#SBATCH --mail-type=ALL                       # Event(s) that triggers email notification (BEGIN,END,FAIL,ALL)
+#SBATCH --mail-type=FAIL                       # Event(s) that triggers email notification (BEGIN,END,FAIL,ALL)
 #SBATCH --mail-user=mathew.chandy@uconn.edu    
 
 module load r/4.2.2

### 2023-08-30 Code/neg_rho_intervals.R

@@ -1,0 +1,70 @@
+source("functions.R")
+library(ggplot2)
+library(showtext)
+library(copula)
+
+set.seed(1234)
+sim <- replicate(50, do1rep(800, -0.4, mystat, 10, qexp))
+new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
+
+file_titles <- c("pct", "bc", "prop")
+custom_titles <- c("Percentile", "BC", "Recentered")
+
+plot_data_800 <- data.frame(replication = 1:50,
+                            point_estimate = new_sim[1, ],
+                            bts_mean = new_sim[2, ],
+                            lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
+                            upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
+                            file_title = rep(file_titles, each = 50),
+                            custom_title = rep(custom_titles, each = 50),
+                            sample.size = rep("n = 800", 150))
+
+set.seed(1234)
+sim <- replicate(50, do1rep(1600, -0.4, mystat, 10, qexp))
+new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
+
+plot_data_1600 <- data.frame(replication = 1:50,
+                             point_estimate = new_sim[1, ],
+                             bts_mean = new_sim[2, ],
+                             lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
+                             upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
+                             file_title = rep(file_titles, each = 50),
+                             custom_title = rep(custom_titles, each = 50),
+                             sample.size = rep("n = 1600", 150))
+
+plot_data <- rbind(plot_data_800, plot_data_1600)
+
+plot_data$custom_title <- factor(plot_data$custom_title, 
+                                 levels = c("Percentile", "BC", "Recentered"))
+
+plot_data$sample.size <- factor(plot_data$sample.size,
+                                levels = c("n = 800", "n = 1600"))
+
+font_add_google("EB Garamond")
+#  windows()
+
+showtext_auto()
+
+mymvd <- copula::mvdc(normalCopula(-0.4), margins = "exp", 
+                      paramMargins = list(rate=1), marginsIdentical = TRUE)
+
[…]

### 2023-08-30 Code/norm_processing.R

@@ -13,7 +13,6 @@ combined_matrices <- lapply(grouped_matrices, function(x) {
 df <- data.frame(phi = numeric(), n = numeric(), CI = character(), 
                  target = character(), cov = numeric(),
                  LB = numeric(), UB = numeric())
-nrep = 10000
 for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
@@ -22,8 +21,8 @@ for(i in names(combined_matrices)) {
   CI <- rep(types, each = length(cov) / length(types))
   parameters <- c('mu', 'sigma', 'phi')
   target <- rep(parameters, length(cov) / length(parameters))
-  LB <- sapply(cov, function(j) prop.test(j*nrep, nrep)$conf.int[1])
-  UB <- sapply(cov, function(j) prop.test(j*nrep, nrep)$conf.int[2])
+  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
+  UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
   new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), CI, target, cov, LB, UB)
   df <- rbind(df, new_rows)
 }
@@ -39,5 +38,3 @@ write.csv(norm_sigma,"norm_sigma.csv", row.names = FALSE)
 t <- 'phi'
 norm_phi <- df[(df$target == t),]
 write.csv(norm_phi,"norm_phi.csv", row.names = FALSE)
-
-setwd("../Code")

### 2023-08-30 Code/phi_intervals.R

@@ -57,5 +57,4 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   theme(strip.text=element_text(size=10), text =
           element_text(family = "EB Garamond"))
 
-ggsave('../Manuscript/figures/norm_phi_intervals.pdf', width = 10,
-       height = 5)
+ggsave('../Manuscript/figures/norm_phi_intervals.pdf', width = 10)

### 2023-08-30 Code/plots.R

@@ -35,6 +35,6 @@ t <- 'exp_sigma'
 width <- .2
 graph_bts(t, width, exp_sigma)
 
-t <- 'exp_phi'
+t <- 'exp_rho'
 width <- .2
-graph_bts(t, width, exp_phi)
+graph_bts(t, width, exp_rho)

### 2023-08-30 Code/rho_intervals.R

@@ -1,0 +1,70 @@
+source("functions.R")
+library(ggplot2)
+library(showtext)
+library(copula)
+
+set.seed(1234)
+sim <- replicate(50, do1rep(800, 0.4, mystat, 10, qexp))
+new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
+
+file_titles <- c("pct", "bc", "prop")
+custom_titles <- c("Percentile", "BC", "Recentered")
+
+plot_data_800 <- data.frame(replication = 1:50,
+                            point_estimate = new_sim[1, ],
+                            bts_mean = new_sim[2, ],
+                            lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
+                            upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
+                            file_title = rep(file_titles, each = 50),
+                            custom_title = rep(custom_titles, each = 50),
+                            sample.size = rep("n = 800", 150))
+
+set.seed(1234)
+sim <- replicate(50, do1rep(1600, 0.4, mystat, 10, qexp))
+new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
+
+plot_data_1600 <- data.frame(replication = 1:50,
+                             point_estimate = new_sim[1, ],
+                             bts_mean = new_sim[2, ],
+                             lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
+                             upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
+                             file_title = rep(file_titles, each = 50),
+                             custom_title = rep(custom_titles, each = 50),
+                             sample.size = rep("n = 1600", 150))
+
+plot_data <- rbind(plot_data_800, plot_data_1600)
+
+plot_data$custom_title <- factor(plot_data$custom_title, 
+                                 levels = c("Percentile", "BC", "Recentered"))
+
+plot_data$sample.size <- factor(plot_data$sample.size,
+                                levels = c("n = 800", "n = 1600"))
+
+font_add_google("EB Garamond")
+#  windows()
+
+showtext_auto()
+
+mymvd <- copula::mvdc(normalCopula(0.4), margins = "exp", 
+                      paramMargins = list(rate=1), marginsIdentical = TRUE)
+
[…]

### 2023-08-30 Code/singlejob.R

@@ -4,19 +4,13 @@ names(norm_results) <- c()
 exp_results <- list()
 names(exp_results) <- c()
 phi <- -.4
-n = 3200
+n = 100
 blksize <- ceiling(n^(1/3))
-set.seed(13)
+set.seed(as.integer(1))
 sim <- replicate(100, do1rep(n, phi, mystat, blksize))
 norm_results[[paste(phi, n, sep = '_')]] <- sim
-set.seed(13)
-rho <- 0
-if (phi >= 0) {
-  rho <- uniroot(function(x) rho2phi(x) - phi, interval = c(0, 0.9))$root
-} else {
-  rho <- uniroot(function(x) rho2phi(x) - phi, interval = c(-.56, 0))$root
-}
-sim <- replicate(100, do1rep(n, rho, mystat, blksize, qexp))
+set.seed(as.integer(1))
+sim <- replicate(100, do1rep(n, phi, mystat, blksize, qexp))
 exp_results[[paste(phi, n, sep = '_')]] <- sim
 
 saveRDS(norm_results, '../Data/norm_result.rds')

### 2023-08-30 Code/exp_phi_intervals.R
Small Update

@@ -45,11 +45,20 @@ font_add_google("EB Garamond")
 
 showtext_auto()
 
+mymvd <- copula::mvdc(normalCopula(0.4), margins = "exp", 
+                      paramMargins = list(rate=1), marginsIdentical = TRUE)
+
+## numerical integration to get 
+EXY <- pracma::dblquad(function(x, y) x * y * 
+                         copula::dMvdc(cbind(x, y), mymvd), 0, 20, 0, 20)
+## approximate true phi
+phi <- (EXY - 1) / 1
+
 ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound), width = 0.5, color = 'gray') +
   geom_point(color = 'blue') +
   geom_point(aes(y = bts_mean), color = 'red', shape = 'cross') +
-  geom_hline(yintercept = 0.4, linetype = "dotted") +
+  geom_hline(yintercept = phi, linetype = "dotted") +
   facet_grid(custom_title ~ sample.size) +
   labs(x = 'Replication', y = 'Value') +
   scale_color_manual(values = c('blue', 'red', 'gray')) +

### 2023-08-30 Code/exp_processing.R

@@ -11,28 +11,28 @@ grouped_matrices <- split(list_of_matrices, names(list_of_matrices))
 combined_matrices <- lapply(grouped_matrices, function(x) {
   Reduce(cbind, x)
 })
-df <- data.frame(phi = numeric(), n = numeric(), CI = character(), 
+df <- data.frame(rho = numeric(), n = numeric(), CI = character(), 
                  target = character(), cov = numeric(),
                  LB = numeric(), UB = numeric())
 for(i in names(combined_matrices)) {
-  phi <- as.numeric(strsplit(i, '_')[[1]][1])
+  rho <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
-  mymvd <- copula::mvdc(normalCopula(phi), margins = "exp", 
+  mymvd <- copula::mvdc(normalCopula(rho), margins = "exp", 
                         paramMargins = list(rate=1), marginsIdentical = TRUE)
   
   ## numerical integration to get 
   EXY <- pracma::dblquad(function(x, y) x * y * 
                            copula::dMvdc(cbind(x, y), mymvd), 0, 20, 0, 20)
-  ## approximate true rho
-  rho <- (EXY - 1) / 1
-  cov <- mychk(combined_matrices[[i]], c(1, 1, rho))
+  ## approximate true phi
+  phi <- (EXY - 1) / 1
+  cov <- mychk(combined_matrices[[i]], c(1, 1, phi))
   types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'bcCI', 'bcaCI', 'propCI')
   CI <- rep(types, each = length(cov) / length(types))
-  parameters <- c('mu', 'sigma', 'rho')
+  parameters <- c('mu', 'sigma', 'phi')
   target <- rep(parameters, length(cov) / length(parameters))
   LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
   UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
-  new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), CI, target, cov, LB, UB)
+  new_rows <- data.frame(rho = rep(rho, length(cov)), n = rep(n, length(cov)), CI, target, cov, LB, UB)
[…]

### 2023-08-30 Code/functions.R

@@ -116,5 +116,6 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
             element_text(family = "EB Garamond", size = 10),
           strip.text.y = element_text(angle = 270, hjust = 1)) +
     scale_y_continuous(trans=trans)
-  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10)
+  ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10,
+         height = 5)
 }

### 2023-08-30 Code/neg_exp_phi_intervals.R

@@ -45,11 +45,20 @@ font_add_google("EB Garamond")
 
 showtext_auto()
 
+mymvd <- copula::mvdc(normalCopula(-0.4), margins = "exp", 
+                      paramMargins = list(rate=1), marginsIdentical = TRUE)
+
+## numerical integration to get 
+EXY <- pracma::dblquad(function(x, y) x * y * 
+                         copula::dMvdc(cbind(x, y), mymvd), 0, 20, 0, 20)
+## approximate true phi
+phi <- (EXY - 1) / 1
+
 ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound), width = 0.5, color = 'gray') +
   geom_point(color = 'blue') +
   geom_point(aes(y = bts_mean), color = 'red', shape = 'cross') +
-  geom_hline(yintercept = -0.4, linetype = "dotted") +
+  geom_hline(yintercept = phi, linetype = "dotted") +
   facet_grid(custom_title ~ sample.size) +
   labs(x = 'Replication', y = 'Value') +
   scale_color_manual(values = c('blue', 'red', 'gray')) +
@@ -58,4 +67,5 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   theme(strip.text=element_text(size=10), text =
           element_text(family = "EB Garamond"))
 
-ggsave('../Manuscript/figures/neg_exp_phi_intervals.pdf', width = 10)
+ggsave('../Manuscript/figures/neg_exp_phi_intervals.pdf', width = 10,
+       height = 5)

### 2023-08-30 Code/neg_rho_intervals.R

@@ -1,70 +1,0 @@
-source("functions.R")
-library(ggplot2)
-library(showtext)
-library(copula)
-
-set.seed(1234)
-sim <- replicate(50, do1rep(800, -0.4, mystat, 10, qexp))
-new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
-
-file_titles <- c("pct", "bc", "prop")
-custom_titles <- c("Percentile", "BC", "Recentered")
-
-plot_data_800 <- data.frame(replication = 1:50,
-                            point_estimate = new_sim[1, ],
-                            bts_mean = new_sim[2, ],
-                            lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
-                            upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
-                            file_title = rep(file_titles, each = 50),
-                            custom_title = rep(custom_titles, each = 50),
-                            sample.size = rep("n = 800", 150))
-
-set.seed(1234)
-sim <- replicate(50, do1rep(1600, -0.4, mystat, 10, qexp))
-new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
-
-plot_data_1600 <- data.frame(replication = 1:50,
-                             point_estimate = new_sim[1, ],
-                             bts_mean = new_sim[2, ],
-                             lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
-                             upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
-                             file_title = rep(file_titles, each = 50),
-                             custom_title = rep(custom_titles, each = 50),
-                             sample.size = rep("n = 1600", 150))
-
-plot_data <- rbind(plot_data_800, plot_data_1600)
-
-plot_data$custom_title <- factor(plot_data$custom_title, 
-                                 levels = c("Percentile", "BC", "Recentered"))
-
-plot_data$sample.size <- factor(plot_data$sample.size,
-                                levels = c("n = 800", "n = 1600"))
-
-font_add_google("EB Garamond")
-#  windows()
-
-showtext_auto()
-
-mymvd <- copula::mvdc(normalCopula(-0.4), margins = "exp", 
-                      paramMargins = list(rate=1), marginsIdentical = TRUE)
-
[…]

### 2023-08-30 Code/phi_intervals.R

@@ -57,4 +57,5 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   theme(strip.text=element_text(size=10), text =
           element_text(family = "EB Garamond"))
 
-ggsave('../Manuscript/figures/norm_phi_intervals.pdf', width = 10)
+ggsave('../Manuscript/figures/norm_phi_intervals.pdf', width = 10,
+       height = 5)

### 2023-08-30 Code/plots.R

@@ -24,7 +24,7 @@ exp_mu <- read.csv("../Data/exp_mu.csv") %>%
   filter(CI != 'ctrCI')
 exp_sigma <- read.csv("../Data/exp_sigma.csv") %>% 
   filter(CI != 'ctrCI')
-exp_rho <- read.csv("../Data/exp_rho.csv") %>% 
+exp_phi <- read.csv("../Data/exp_phi.csv") %>% 
   filter(CI != 'ctrCI')
 
 t <- 'exp_mu'
@@ -35,6 +35,6 @@ t <- 'exp_sigma'
 width <- .2
 graph_bts(t, width, exp_sigma)
 
-t <- 'exp_rho'
+t <- 'exp_phi'
 width <- .2
-graph_bts(t, width, exp_rho)
+graph_bts(t, width, exp_phi)

### 2023-08-30 Code/rho_intervals.R

@@ -1,70 +1,0 @@
-source("functions.R")
-library(ggplot2)
-library(showtext)
-library(copula)
-
-set.seed(1234)
-sim <- replicate(50, do1rep(800, 0.4, mystat, 10, qexp))
-new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
-
-file_titles <- c("pct", "bc", "prop")
-custom_titles <- c("Percentile", "BC", "Recentered")
-
-plot_data_800 <- data.frame(replication = 1:50,
-                            point_estimate = new_sim[1, ],
-                            bts_mean = new_sim[2, ],
-                            lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
-                            upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
-                            file_title = rep(file_titles, each = 50),
-                            custom_title = rep(custom_titles, each = 50),
-                            sample.size = rep("n = 800", 150))
-
-set.seed(1234)
-sim <- replicate(50, do1rep(1600, 0.4, mystat, 10, qexp))
-new_sim <- sim[c(3, 6, 23, 24, 35, 36, 47, 48), ]
-
-plot_data_1600 <- data.frame(replication = 1:50,
-                             point_estimate = new_sim[1, ],
-                             bts_mean = new_sim[2, ],
-                             lower_bound = c(new_sim[3, ], new_sim[5, ], new_sim[7, ]),
-                             upper_bound = c(new_sim[4, ], new_sim[6, ], new_sim[8, ]),
-                             file_title = rep(file_titles, each = 50),
-                             custom_title = rep(custom_titles, each = 50),
-                             sample.size = rep("n = 1600", 150))
-
-plot_data <- rbind(plot_data_800, plot_data_1600)
-
-plot_data$custom_title <- factor(plot_data$custom_title, 
-                                 levels = c("Percentile", "BC", "Recentered"))
-
-plot_data$sample.size <- factor(plot_data$sample.size,
-                                levels = c("n = 800", "n = 1600"))
-
-font_add_google("EB Garamond")
-#  windows()
-
-showtext_auto()
-
-mymvd <- copula::mvdc(normalCopula(0.4), margins = "exp", 
-                      paramMargins = list(rate=1), marginsIdentical = TRUE)
-
[…]

### 2023-09-01 Manuscript/manuscript.tex
Small Update
went over exp simulation; tuned floats

@@
 
-\renewcommand{\textfraction}{0.10}
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\bottomfraction}{0.85}
-\renewcommand{\floatpagefraction}{0.90}
+% control floats
+%% \renewcommand\floatpagefraction{.9}
+%% \renewcommand\topfraction{.9}
+%% \renewcommand\bottomfraction{.9}
+%% \renewcommand\textfraction{.2}
+%% \setcounter{totalnumber}{50}
+%% \setcounter{topnumber}{50}
+%% \setcounter{bottomnumber}{50}
 
@@
 \setlength{\bibsep}{0pt plus 0.3ex}
+
+\usepackage{physics} % for \dd
 
@@
 
-\jy{What was $B$?} \mc{addressed}
-
 Three target parameters of $X_t$ were considered:
@@
 
-\begin{figure}[tbp]
+\begin{figure}[bp]
   \centering
@@
 
-An additional simulation study in which block bootstrap is used to estimate
-\jy{not an AR(1) process...} \mc{addressed}
-parameters of a marginally transformed AR(1) process with an underlying 
-exponential distribution is discussed in the Appendix.
+An additional simulation study in which block bootstrap is used to estimate the
+parameters of a stationary series with exponential distribution distribution is
+reported in the Appendix. The results are similar.
 
@@
 the mean, standard deviation, and the lag-1 autocorrelation coefficient of a
-AR(1) process with an underlying unit exponential marginal distribution. The
-motivation for this additional simulation study was to observe if the results of 
-the main simulation study will change if the underlying marginal distribution is
-not normal.
+stationary series with an exponential marginal distribution. The motivation of
+for this study was to investigate if the results are robust to nonnormal
+marginal distributions.
 
-We generated time series $X_t$ from a 1st order autoregressive 
-(AR(1)) process as we did previously, but transformed the data from a standard
-normal distribution to an exponential distribution with rate $\lambda = 1$, so 
-that for $t \in \{1, \ldots, n\}$, we can define:
+The series were generated by marginally transforming the
+AR(1) series  $X_t$in the simulation study by
 \begin{equation*}
-W_t = F^{-1}(\Phi(X_t), 1),
+W_t = F^{-1}[\Phi(X_t)],
 \end{equation*}
-where $F^{-1}(p, \lambda)$ is the quantile function for the exponential 
-distribution with rate parameter $\lambda$.
-
-The simulation design was the same, except the target parameters of $W_t$ were:
-1) $\mu = 1$, the mean of $W_t$;
-2) $\sigma_w = 1$, the standard deviation of $W_t$; and
-3) $\phi$, the lag-1 autocorrelation coefficient of $W_t$.
-Let $\rho$ be the lag-1 autocorrelation coefficient of $X_t$.
-Although we may have set $\rho$ to these five levels for $X_t$: 
-$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
-the new five true autocorrelation coefficients for $W_t$ were different.
-
-To calibrate the copula parameters, we first constructed a multivariate
-exponential distribution from a normal copula with 
-$\rho \in \{-0.4, -0.2, 0.0, 0.2, 0.4\} $using the \texttt{copula} package.
-\citep{hofert2018ealements} Then we computed $E[XY]$, which 
-requires double integration using the \texttt{pracma} package. \citep{pracma} 
-Finally, we obtained true $\phi = E[XY] - 1$, which was used as the target
-parameter when evaluating CI performance when estimating $\phi$.
-After this step, we again plotted empirical coverage 
-rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\% confidence intervals of 
-the real coverage. These are displayed in 
-\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}.
+where $F^{-1}(p)$ is the quantile function for the unit exponential 
+distribution. The true mean and standard deviation parameters are~1. The lag-1
+autocorrelation coefficient is not invariant to the
+transformation\citep{hofert2018ealements}, but its value can be obtained by
+\begin{equation*}
+\int_\infty^\infty \int_\infty^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
+\end{equation*}
+where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
+distribution with correlation~$\phi$. We kept the configuration of
+$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$.
 
@@
 
-Additionally, another set of 50 CIs was generated for each of the percentile, 
-BC, and recentered percentile approaches for exponentially distributed
-samples of $n \in \{800, 1600\}$.
-
 \begin{figure}[tbp]
   \centering
-  \includegraphics[width=\textwidth]{figures/exp_pho_intervals}
-  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
-    samples of $n \in \{800, 1600\}$ for a marginally transformed AR(1) process 
-    with $\phi = 0.4$
-    \jy{not accurate} \mc{is this better}
-    with an underlying exponential distribution ($\lambda = 1$). For 
+  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
+  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
+    mean, standard deviation, and lag-1 autocorrelation coefficient
+    of a stationary series with marginal exponential distribution
+    obtained by transforming an AR(1) process with $\phi = 0.4$ with
+    sample size $n \in \{800, 1600\}$. For 
     each replicate, the lower and upper bounds of the CIs are displayed, as well 
@@
 
-It seems that range of sample sizes needed 
-to cover parameters of an exponentially distributed AR(1) process is generally 
-higher than that needed to cover parameters of a normally
-distributed AR(1) process. Despite this, the trends and patterns discussed 
-previously with respect
-to the performance of different methods and with different parameters are the 
-same.
-For instance, Student's $t$ CIs still appear to yield higher coverage rates than 
-other 
-methods. Performance is still generally better when temporal dependence is 
-negative rather than positive. Most importantly, percentile, BC, and BCA CIs
-still deteriorate in coverage of $\phi$ as sample size increases. As exhibited 
-in Figure~\ref{fig:eri}, percentile and BC CIs still suffer from the same bias
-issue, whereas recentered percentile CI still work when estimating $\phi$ 
-because the 
-original point estimator is unbiased. Overall, the results with an underlying 
-marginal 
-exponential distribution 
-are very similar to the results with an underlying normal distribution from the
-main study.
+\jy{change the captions of the other three figures accordingly}
 
-\jy{comment on that the recentered percentile CI for autocorrelation still works
-  as the point estimator is unbiased.} \mc{addressed}
+The empirical coverage rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\%
+confidence intervals of the real coverage are displayed in 
+\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
+Additionally, another set of 50 CIs was generated for each of the percentile, 
+BC, and recentered percentile approaches for exponentially distributed
+samples of $n \in \{800, 1600\}$ in Figure~\ref{fig:eri}.
+
+It appears that a greater sample size is generally required for the bootstrap
+CIs to cover the mean and standard deviation parameters in the exponential
+margin case than in the normal margin case. However, the trends and patterns
+discussed in the main text regarding the performance of various methods and
+diverse parameters remain consistent. For example, Student's $t$ confidence
+intervals still exhibit higher coverage rates in comparison to alternative
+methods. Performance continues to be more favorable when temporal dependence is
+negative rather than positive. Of particular significance, the percentile, BC,
+and BCA confidence intervals still display a decline in coverage accuracy for
+the lag-1 autocorrelation coefficient as sample size increases as demonstrated
+in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
+manifesting the same bias issue. On the other hand, the recentered percentile
+confidence interval continues to be effective in estimating $\phi$ due to the
+inherent unbiasedness of the original point estimator. In sum, the findings for
+series that are marginally exponentially distributed closely mirror those
+attained for series that are marginally normally distributed.
 

### 2023-09-01 Manuscript/manuscript.tex
added true values of lag-1 autocorr
Responded to Commit

@@
 The series were generated by marginally transforming the
-AR(1) series  $X_t$in the simulation study by
+AR(1) series  $X_t$ in the simulation study by
 \begin{equation*}
@@
 autocorrelation coefficient is not invariant to the
-transformation\citep{hofert2018ealements}, but its value can be obtained by
+transformation, \citep{hofert2018elements} but its value can be obtained by
 \begin{equation*}
-\int_\infty^\infty \int_\infty^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
+\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
 \end{equation*}
@@
 distribution with correlation~$\phi$. We kept the configuration of
-$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$.
+$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
+autocorrelation coefficients are $\{-0.298, -0.156, 0, 0.170, 0.355\}$.
 
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a marginally transformed AR(1) process with AR 
-    coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with an 
-    underlying exponential distribution ($\lambda = 1$) and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ with
-    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
+    the marginal mean $\mu$ of a stationary series with marginal exponential
+    distribution obtained by transforming an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
     The error bars represent 95\% CIs of the real coverage rates.}
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of a marginally transformed AR(1) 
-    process with AR 
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with an 
-    underlying exponential distribution ($\lambda = 1$) and series length 
+    the marginal standard deviation $\sigma_x$ of a stationary series with 
+    marginal exponential distribution obtained by transforming an AR(1) process
+    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
     $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\phi$ of a marginally 
-    transformed AR(1) process with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with 
-    an 
-    underlying exponential distribution ($\lambda = 1$) and series length
+    the first-order autocorrelation coefficient $\phi$ of a stationary series
+    with marginal exponential distribution obtained by transforming an AR(1) 
+    process with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
     $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
@@
 \jy{change the captions of the other three figures accordingly}
+\mc{addressed}
 

### 2023-09-02 Manuscript/manuscript.tex
minor edits; use hyperref

@@
 \usepackage{physics} % for \dd
+\usepackage{hyperref}
 
@@
 where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
-distribution with correlation~$\phi$. We kept the configuration of
+distribution with correlation parameter~$\phi$. We kept the configuration of
 $\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
@@
   \caption{50 replicate percentile, BC, and recentered percentile CIs for the
-    mean, standard deviation, and lag-1 autocorrelation coefficient
+    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
     of a stationary series with marginal exponential distribution
@@
 
-\jy{change the captions of the other three figures accordingly}
-\mc{addressed}
-
 The empirical coverage rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\%
@@
 \textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
-Additionally, another set of 50 CIs was generated for each of the percentile, 
+Additionally, a set of 50 CIs are displayed for each of the percentile, 
 BC, and recentered percentile approaches for exponentially distributed
-samples of $n \in \{800, 1600\}$ in Figure~\ref{fig:eri}.
+samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
+($\phi = 0.4$) in Figure~\ref{fig:eri}.
 

### 2023-09-04 Manuscript/manuscript.tex
Keywords

@@
 % List Eight to Ten Capitalized Keywords Separated by \ul{Semicolons}; Do Not Use Period at The End
-Dependent Data; Resampling; Simulation; Time Series
+Dependent Data; Resampling; Simulation; Time Series; Block Bootstrap;
+Confidence Intervals; Bias-Correction; Auto-Correlation
+
+\mc{we need eight to ten keywords, are the ones I added okay?}
 
@@
 $\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
-autocorrelation coefficients are $\{-0.298, -0.156, 0, 0.170, 0.355\}$.
+autocorrelation coefficients are $\{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.
 

### 2023-09-06 Code/exp_phi_intervals.R
Fixed Keywords and Figure Heights

@@ -68,4 +68,4 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
           element_text(family = "EB Garamond"))
 
 ggsave('../Manuscript/figures/exp_phi_intervals.pdf', width = 10,
-       height = 5)
+       height = 5.8)

### 2023-09-06 Code/functions.R

@@ -117,5 +117,5 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
           strip.text.y = element_text(angle = 270, hjust = 1)) +
     scale_y_continuous(trans=trans)
   ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10,
-         height = 5)
+         height = 5.8)
 }

### 2023-09-06 Code/neg_exp_phi_intervals.R

@@ -68,4 +68,4 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
           element_text(family = "EB Garamond"))
 
 ggsave('../Manuscript/figures/neg_exp_phi_intervals.pdf', width = 10,
-       height = 5)
+       height = 5.8)

### 2023-09-06 Code/neg_phi_intervals.R

@@ -57,4 +57,5 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
   theme(strip.text=element_text(size=10), text =
           element_text(family = "EB Garamond"))
 
-ggsave('../Manuscript/figures/neg_phi_intervals.pdf', width = 10)
+ggsave('../Manuscript/figures/neg_phi_intervals.pdf', width = 10,
+       height = 5.8)

### 2023-09-06 Code/phi_intervals.R

@@ -58,4 +58,4 @@ ggplot(plot_data, aes(x = replication, y = point_estimate)) +
           element_text(family = "EB Garamond"))
 
 ggsave('../Manuscript/figures/norm_phi_intervals.pdf', width = 10,
-       height = 5)
+       height = 5.8)

### 2023-09-07 Manuscript/manuscript.tex
Fixed Keywords and Figure Heights
few minor comments

@@
 % List Eight to Ten Capitalized Keywords Separated by \ul{Semicolons}; Do Not Use Period at The End
-Dependent Data; Resampling; Simulation; Time Series; Block Bootstrap;
-Confidence Intervals; Bias-Correction; Auto-Correlation
+Autocorrelation; Bias-Correction; Centering; Dependent Data; Percentile; 
+Resampling; Simulation; Time Series
 
 \mc{we need eight to ten keywords, are the ones I added okay?}
+\eds{These look fine to me.}
 
@@
 the desired coverage rates.
-\eds{I think the superscript citations need to go before the punctuation.  
-Please check in other AJUR papers and adjust throughout the paper if needed.}
-\mc{from the style guide: "Please bold and superscript the numbers for 
-references in the text.1 Separate superscripted numbers by comma and space,1, 2 
-they should be separated by an en-dash if the consecutive list of more than two 
-numbers is used.1–3 List them AFTER punctuation (be it comma or period) with no 
-space.2}
+%\eds{I think the superscript citations need to go before the punctuation.  
+%Please check in other AJUR papers and adjust throughout the paper if needed.}
+%\mc{from the style guide: "Please bold and superscript the numbers for 
+%references in the text.1 Separate superscripted numbers by comma and space,1, 2 
+%they should be separated by an en-dash if the consecutive list of more than two 
+%numbers is used.1–3 List them AFTER punctuation (be it comma or period) with no 
+%space.2} 
+%\eds{thank you for checking!}
 
@@
 \]
-\eds{If $z_{(\alpha)}$ is the upper quantile, then $z_{(\alpha/2)}$ will be 
-positive and $z_{(1-\alpha/2)}$ will be negative for small $\alpha$ values; with
-the subtraction of the quantiles, the smaller CI endpoint would appear to
-be listed first.  Please check this notation, and the notation for Student's $t$ 
-CI, and other intervals which use the $z_{(\alpha)}$ upper standard normal 
-quantile.} 
-\mc{Replaced upper quantile with quantile function}
+%\eds{If $z_{(\alpha)}$ is the upper quantile, then $z_{(\alpha/2)}$ will be 
+%positive and $z_{(1-\alpha/2)}$ will be negative for small $\alpha$ values; with
+%the subtraction of the quantiles, the smaller CI endpoint would appear to
+%be listed first.  Please check this notation, and the notation for Student's $t$ 
+%CI, and other intervals which use the $z_{(\alpha)}$ upper standard normal 
+%quantile.} 
+%\mc{Replaced upper quantile with quantile function}
+\eds{this is not usually how I see it written, but it looks correct now}
 This CI is centered by the original point estimate $\hat\theta_n$ and is 
@@
 \]
+\eds{the $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ may need to be switched now in 
+$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$ -- 
+please check.}
 
@@
 \end{equation*}
+\eds{please check $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ in 
+$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$} 
 A $(1 - \alpha)100\%$ ~BCA CI is
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of a stationary series with 
+    the marginal standard deviation $\sigma_x$ \eds{$\sigma_w$?} of a stationary series with 
     marginal exponential distribution obtained by transforming an AR(1) process
@@
 
-The empirical coverage rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\%
+The empirical coverage rates for $\mu$, $\sigma_w$, \eds{define $\sigma_w$} and $\phi$, as well as 95\%
 confidence intervals of the real coverage are displayed in 

### 2023-09-08 Manuscript/manuscript.tex
Responded to Comments

@@
 Resampling; Simulation; Time Series
-
-\mc{we need eight to ten keywords, are the ones I added okay?}
-\eds{These look fine to me.}
 
@@
 %\mc{Replaced upper quantile with quantile function}
-\eds{this is not usually how I see it written, but it looks correct now}
+
 This CI is centered by the original point estimate $\hat\theta_n$ and is 
@@
 $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
-$b \in \{1, \ldots, B\}$. Define $\alpha_1 = \Phi(2\hat{z}_0 - z_{\alpha/2})$ 
-and $\alpha_2 = \Phi(2\hat{z}_0 - z_{1 - \alpha/2})$. 
+$b \in \{1, \ldots, B\}$. Define 
+$\alpha_1 = \Phi(2\hat{z}_0 - z_{1 - \alpha/2})$ 
+and $\alpha_2 = \Phi(2\hat{z}_0 - z_{\alpha/2})$. 
 A $(1 - \alpha)100\%$ ~BC CI is
@@
 please check.} 
+\mc{yes they had to be switched}
 
@@
 $\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$} 
+\mc{this one is okay}
 A $(1 - \alpha)100\%$ ~BCA CI is
@@
 where $F^{-1}(p)$ is the quantile function for the unit exponential 
-distribution. The true mean and standard deviation parameters are~1. The lag-1
+distribution. The true mean ($\mu$) and standard deviation ($\sigma_w$) 
+parameters 
+of $W_t$ are~1. The 
+lag-1
 autocorrelation coefficient is not invariant to the
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ \eds{$\sigma_w$?} of a stationary series with 
+    the marginal standard deviation $\sigma_w$ \eds{$\sigma_w$?} \mc{addressed}
+    of a stationary series with 
     marginal exponential distribution obtained by transforming an AR(1) process
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\phi$ of a stationary series
+    the first-order autocorrelation coefficient of a stationary series
     with marginal exponential distribution obtained by transforming an AR(1) 
@@
 
-The empirical coverage rates for $\mu$, $\sigma_w$, \eds{define $\sigma_w$} and $\phi$, as well as 95\%
+The empirical coverage rates for $\mu$, $\sigma_w$, \eds{define $\sigma_w$} 
+\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} and 
+the lag-1 autocorrelation coefficient \mc{replaced $\phi$ here, as I understand
+it, we are not using $\phi$ in reference to the temporal dependence of the 
+exponentially distributed series?}, as well as 95\%
 confidence intervals of the real coverage are displayed in 
@@
 manifesting the same bias issue. On the other hand, the recentered percentile
-confidence interval continues to be effective in estimating $\phi$ due to the
+confidence interval continues to be effective in estimating the temporal 
+dependence \mc{replaced $\phi$ again here} due to the
 inherent unbiasedness of the original point estimator. In sum, the findings for

### 2023-09-08 Manuscript/manuscript.tex
marginal instead of underlying

@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with an underlying standard 
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
     normal distribution with AR coefficient
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with an 
-    underlying standard normal distribution with AR 
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
+    marginal standard normal distribution with AR 
     coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
@@
     the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    an underlying standard normal distribution with 
+    a marginal standard normal distribution with 
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a stationary series with marginal exponential
+    the marginal mean $\mu$ of a stationary series with marginal unit exponential
     distribution obtained by transforming an AR(1) process with
@@
     of a stationary series with 
-    marginal exponential distribution obtained by transforming an AR(1) process
+    marginal unit exponential distribution obtained by transforming an AR(1) process
     with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
@@
     the first-order autocorrelation coefficient of a stationary series
-    with marginal exponential distribution obtained by transforming an AR(1) 
+    with marginal unit exponential distribution obtained by transforming an AR(1) 
     process with 

### 2023-09-10 Manuscript/manuscript.tex
removed resolved

@@
 \]
-\eds{the $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ may need to be switched now in 
-$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$ -- 
-please check.} 
-\mc{yes they had to be switched}
+%\eds{the $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ may need to be switched now in 
+%$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$ -- 
+%please check.} 
+%\mc{yes they had to be switched}
 
@@
 \end{equation*}
-\eds{please check $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ in 
-$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$} 
-\mc{this one is okay}
+%\eds{please check $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ in 
+%$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$} 
+%\mc{this one is okay}
 A $(1 - \alpha)100\%$ ~BCA CI is
@@
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_w$ \eds{$\sigma_w$?} \mc{addressed}
+    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
     of a stationary series with 
@@
 
-The empirical coverage rates for $\mu$, $\sigma_w$, \eds{define $\sigma_w$} 
-\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} and 
-the lag-1 autocorrelation coefficient \mc{replaced $\phi$ here, as I understand
-it, we are not using $\phi$ in reference to the temporal dependence of the 
-exponentially distributed series?}, as well as 95\%
+The empirical coverage rates for $\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
+%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
+and 
+the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
+%it, we are not using $\phi$ in reference to the temporal dependence of the 
+%exponentially distributed series?}, 
+as well as 95\%
 confidence intervals of the real coverage are displayed in 
@@
 confidence interval continues to be effective in estimating the temporal 
-dependence \mc{replaced $\phi$ again here} due to the
+dependence %\mc{replaced $\phi$ again here} 
+due to the
 inherent unbiasedness of the original point estimator. In sum, the findings for

### 2023-12-01 Manuscript/reply.tex
reply template

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{natbib}
\usepackage{hyperref}

\usepackage{listings}
\usepackage{rotating, graphicx}
\graphicspath{{./}, {./image/}}
\usepackage{booktabs, natbib}
% \usepackage{breakurl}
% \usepackage [english]{babel}
\usepackage{amsmath, amsbsy, amsthm, epsfig, epsf, psfrag, graphicx, 
amssymb, enumerate}
\usepackage{bm}
\usepackage{multirow, multicol}

\usepackage{color}
\definecolor{darkblue}{rgb}{0.1, 0.2, 0.6}

% \usepackage{xcolor}
\newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
\newcommand{\tw}[1]{\textcolor{blue}{(TW: #1)}}
\newcommand{\sx}[1]{\textcolor{teal}{(SX: #1)}}

\sloppy

% \usepackage{csquotes}
% \usepackage [autostyle, english = american]{csquotes}
% \MakeOuterQuote{"}

% \usepackage{bibentry}
\newenvironment{comment}%
{\begin{quotation}\noindent\small\it\color{darkblue}\ignorespaces%
}{\end{quotation}}

\begin{document}

\begin{center}
  {\Large\bf Response to the Comments}
\end{center}

% \jy{Spell check!}

\subsection*{Summary}

We thank the editor and the AE for the opportunity to revise the manuscript and
the two referees for their constructive comments. The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item Newly added analyses:
  \begin{enumerate}
    \item chord plots visualizing the sectors' in- and out-connectivities in
      Section~3;
    \item key sector analysis with PageRank (PR) using export value as auxiliary
      information in Appendix~B;
    \item key sector analysis with hub and authority centrality in Appendix~C;
    \item dynamics of the similarity in the sector communities within each
      country and cross the two countries in Section~6.
    \end{enumerate}
\item Strengthened presentations:
  \begin{enumerate}
  \item elaborated motivation of using network tools for the comparison of
    sectoral structures in Section~1;
  \item expanded interpretation of directed assortativity coefficients in the
    context of input-output tables (IOTs) in Section~4;
  \item clarified discussion on the PR centrality using value added as
    auxiliary information in Section~5.
  \item completely rewritten discussions in Section~7.
  \end{enumerate}
\end{enumerate}
Additionally, we undertook meticulous reviews of the entire manuscript to ensure
clarity, coherence, and grammatical precision, aiming to present methods,
results, and discussions in a lucid manner.

Point-by-point responses to the comments are as follows, with the
comments quoted in \emph{\color{darkblue} italic}.

\subsection*{To AE}

\begin{comment}
1. Strengthen the motivation, i.e., explain how the China-Japan economy
comparison be better conducted using the methods consequently adopted in the
paper.
\end{comment}

As suggested, we have fortified our rationale for employing network analysis
in examining the sectoral structures of China and Japan. Specifically:
\begin{enumerate}
\item 
  Network analysis introduces advanced tools for innovative visualization.
\item
  Network analysis provides a deeper understanding of sectoral interdependencies,
  transcending the rudimentary summaries from the intermediate flow matrix that
  traditional input-output analysis offers. Notably, it encompasses metrics like
  directed strength distributions and weighted, directed assortativities, as well
  as sector-specific centrality measures.
\item
  Network analysis presents novel techniques for pinpointing key
  sectors and discerning sectoral clusters, which surpass the capabilities of
  conventional input-output analysis.
\end{enumerate}
To provide clearer exposition, we have thoroughly revised paragraph~3 of
Section 1, thus offering a compelling prelude to our analytical approach.

% \jy{Confirm that all the locations mentioned really contain the stated changes.}
% \tw{check and revise}

\begin{comment}
2. Perform sensitivity analysis of the PageRank-based results to the 
selection of the value of the tuning parameter; I also like the idea of using
the Kleinberg's hubs-and-authorities algorithm, which is a natural extension
of the PageRank idea; the idea of studying similarities over time is an
excellent one as well. 
\end{comment}

Concurring with the suggestion for sensitivity analyses, we have expanded our
examination to gauge the robustness of our key sector results obtained from the
extended PR approach.

\begin{table}[tbp]
\centering
\caption{The sectors with top~5 PR scores,
based on the sensitivity analysis of the tuning parameter at the levels
$\gamma = \{0.5, 0.85\}$ for China and Japan from 1995 to 2018
every three years. Total value added is used as auxiliary information.}
\label{tab:prsens}
\resizebox{\textwidth}{!}{
\begin{tabular}{cccccccccccccccccccc}
\toprule
\multirow{2}{*}{Country} & \multirow{2}{*}{Rank}
& \multicolumn{9}{c}{$\gamma = 0.5$} & \multicolumn{9}{c}{$\gamma = 0.85$} \\
\cmidrule(lr){3-11} \cmidrule(lr){12-20} 
& & 1995 & 1998 & 2001 & 2004 & 2007 & 2010 & 2013 & 2016 & 2018 & 
1995 & 1998 & 2001 & 2004 & 2007 & 2010 & 2013 & 2016 & 2018 \\ 
\midrule
China & 1 & 01 & 01 & 01 & 01 & 25 & 25 & 25 & 25 & 25 & 25 & 07 & 25 & 07 & 25 
& 25 & 25 & 25 & 25 \\ 
& 2 & 06 & 06 & 25 & 25 & 01 & 01 & 26 & 26 & 26 & 06 & 06 & 07 & 25 & 07 & 17 
& 20 & 06 & 17 \\ 
& 3 & 26 & 25 & 06 & 06 & 26 & 26 & 01 & 01 & 01 & 07 & 25 & 06 & 17 & 17 & 07 
& 06 & 17 & 40 \\ 
& 4 & 25 & 26 & 26 & 26 & 06 & 06 & 06 & 06 & 40 & 26 & 01 & 01 & 06 & 15 & 19 
& 26 & 20 & 26 \\ 
& 5 & 07 & 07 & 07 & 07 & 07 & 17 & 36 & 36 & 36 & 15 & 26 & 26 & 19 & 19 & 20 
& 17 & 07 & 07 \\ [1ex]
Japan & 1 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 
& 26 & 26 & 26 & 26 \\ 
& 2 & 25 & 25 & 37 & 37 & 37 & 37 & 37 & 37 & 37 & 25 & 25 & 25 & 20 & 20 & 42 
& 42 & 42 & 42 \\ 
& 3 & 37 & 37 & 25 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 20 
& 20 & 20 & 20 \\ 
& 4 & 42 & 42 & 42 & 25 & 25 & 25 & 25 & 25 & 25 & 20 & 20 & 20 & 25 & 37 & 37 
& 37 & 37 & 37 \\ 
& 5 & 36 & 36 & 36 & 36 & 20 & 20 & 20 & 20 & 20 & 37 & 37 & 37 & 37 & 25 & 25 
& 25 & 25 & 25 \\  
\bottomrule
\end{tabular}}
\end{table}

We first obtained PR results, also using value added as auxiliary information,
with $\gamma = 0.5$ and put them sides by side with those obtained with
$\gamma = 0.85$ in Table~\ref{tab:prsens}. Within this framework, $\gamma$
signifies the emphasis placed on the ranking from the IONs, while $1 - \gamma$
represents the emphasis put on the ranking of the auxiliary variable. The
widely-accepted value of $\gamma = 0.85$, as advocated by
\citet{page1998pagerank}, affirms a reasonable inclination towards the
importance of the IONs. The side-by-side comparison in Table~\ref{tab:prsens}
reinforces our stance that $\gamma = 0.85$ better aligns with our objectives. A
setting of $\gamma = 0.5$ seems to unduly accentuate the total value added,
potentially skewing the centrality dynamics. For comprehensive scrutiny, we have
incorporated this table and its pertinent discussion in our Supplementary
Material. To guide readers to this additional resource, we have integrated a
reference in the newly added paragraph~3 of Section~5.

Kleinberg's hubs-and-authorities algorithm~\citep{kleinberg1999authoritative}
presents an alternative approach to identifying key sectors in China and
Japan. The sectors identified via this approach deviate from those highlighted
by the PR method, underscoring the unique evaluative lenses inherent to each
technique. While both methods aim to identify central nodes, the criteria and
perspectives they adopt to discern centrality differ fundamentally. To afford
our readers an exhaustive understanding, we juxtaposed the outcomes of both
methods in the newly added Appendix~C.

Studying the similarities in the cluster structures over time is indeed an
excellent idea! To assess the resemblance between clusters, we adopted the
adjusted mutual information (AMI) metric~\citep{vinh2009information,
  vinh2010information}. Specifically, we have obtained the similarity of 
community structures between the two countries for the same year, as well as 
the dynamic similarity of community structures within a single country over 
time. Comprehensive explanations for these analyses have been included at the 
last paragraph of Section~6.

\begin{comment}
3. Improve the discussion section: better explain the assortativity analyses;
discuss the limitations of the work - this is quite important especially 
given that, as one of the reviewers notes, ``international input-output 
tables involving both countries are available but not used in this study''.
\end{comment}

As suggested, we have completely rewritten the Discussion section with following
discussion points:
\begin{enumerate}
\item
  Methodological innovations in network analysis for assessing 
  disparities in the economic structures of China and Japan.
\item
  Abundance of centrality measures that can be used for key sector
  identification.
\item
  Availability of IOTs in national and international forms.
\item
  Potential followup investigation of China-Japan economic relations using
  multi-region IOTs.
\item
  Impacts of global shocks such as the 2018 global financial crisis and the
  Covid-19 pandemic.
\end{enumerate}

We acknowledge the need for a clearer interpretation of assortativity. In
response, we have added a new paragraph dedicated to the interpretation of
assortativity coefficients in terms of supplying sectors and receiving sectors.
As examples, we gave explicit interpretation of positive in-in assortativity and
negative out-out assortativity. See paragraph~2, Section~4.

We are grateful to the reviewers for highlighting the existence of international
IOTs encompassing both China and Japan. In the revised manuscript, we have
reviewed the World Input-Output Database (WIOD)~\citep{timmer2015illustrated}
and Asian Development Bank's Multiregional Input-Output Table database
(ADB-MRIO)~\citep{ADB2023iot}, explaining why they did not serve our purpose
well; see paragraph~3, Section~2. Further, the core emphasis of our paper is on
internal sectoral structures within each nation rather than the inter-country
connections. Analyzing the interconnectedness between sectors in China and Japan
remains a compelling avenue for future research, a prospect we delve into in
paragraph~4 of Section~7.

\begin{comment}
4. Expand on the insights produced; how do the reported findings compare to
those presented in the earlier-published literature? (this is important
since the authors state that the China-Japan economy comparison draws 
a lot of research attention. 
\end{comment}

We realized that our prior statement was not accurate.
While there is a significant volume of literature concentrating on the economies
of China and Japan independently, there is indeed a palpable gap in studies
directly juxtaposing the sectoral structures of these two major Asian
economies. To better reflect this reality, we have revisited and amended our
literature review in paragraph~2 of Section1. In the analysis, we undertook a
comparative exploration, accentuating both congruences and variances in relation
to the lone preceding study that touched on this theme, namely,
\citet{li2017examining}. This comparison is thoroughly elucidated in the
penultimate paragraph of Section~5.

\subsection*{To Referee 1}

\begin{comment}
1. One of my main concerns is contribution. The contribution of the paper is
 not methodological. Instead the contribution pretends to be in terms of a
better understanding of the differences between China and Japan's economies.
But the analysis done does not provide a deeper understanding different from
what one may expect. Both centrality ranking and clustering confirm what
was suspected or known. Therefore, the paper needs to make a deeper
network analysis and interpretation of results in order to show the
contribution and relevance of using network tools to analyze the
structure of economies.
\end{comment}

We appreciate the reviewer's concern on our contributions and would like to
clarify that our primary aim is to apply recent advancements in network analysis
tools, including some developed by our group, to analyze the IONs of China and
Japan's sectoral structures.

Regarding the observation that our contribution ``pretends'' to be in terms of a
better understanding of the differences between the two economies, we want to
assure that our intentions have been genuine and firmly rooted in academic
exploration. We acknowledge that sometimes, our analysis may seem to confirm
previously suspected ideas, but we see this as an essential validation in
research, further solidifying existing notions from a novel perspective.

In our literature review, we found a paucity of studies on this particular
topic, with a notable mention of \citet{li2017examining}. We would be grateful
for any additional references the reviewers could suggest to enhance our work.

To ensure clarity regarding our research contributions, the penultimate
paragraph in the introduction has been revised at large. See also our summary at
the beginning of this reply.

\begin{comment}
2. To study the structure of both economies authors use page rank as one of the
centrality measures. Why page rank? This measure requieres a tuning parameter
and therefore authors need to come up with an external measure for this. Many
times this is a subjective measure and ends up skewing the analysis.
\end{comment}

The PR method employed in our paper, which allows the inclusion of
auxiliary data, is an advancement of the standard PR traditionally used in
ION analyses \citep{cerina2015world}. This refined approach was selected
not only
because our group developed it and we were keen to assess its practical
application but also due to its alignment with our emphasis on economic
growth. Specifically, we aimed to embed the macroeconomic metric of value added
into the sectoral importance ranking. While we recognize in the revised
manuscript that this method could potentially bias the analysis, we also view
this as advantageous when the emphasis is on economic growth. This discussion
can be found in paragraph~4, Section~5.

We have also expanded our discussion to highlight the potential of alternative
centrality measures for key sector identification. See paragraph~2, Section~7.

\begin{comment}
3. Related to my previous point, why using value added as the tuning parameter
for page rank? As authors point out both economies are very different. Japan,
being a services economy is expected to have lower value added and a more
homogeneous distribution of value added across its most important sectors.
Comparably, China is a manufacturing economy with known industrial policy that
requieres certain amount of domestic value added, therefore is expected to have
higher value added and a more skewed distribution of it across sectors.
Importantly, we also have size of the economies; China is much bigger.
Consequently, using value added may skew things.
\end{comment}

% histogram vs bar chart

For our analysis, we used value added due to two primary
reasons. Firstly, given our focus on economic growth, value added serves as a
robust indicator of each sector's contribution to the overall economy. Secondly,
the IOTs readily provide this metric, ensuring its accessibility, and it has not
been utilized in the creation of the IONs.

The homogeneity of value added across sectors in China and in Japan piques
interest. To elucidate, we plotted bar charts of the value added data
for both countries in 1995 and 2018 in a newly added Figure~4. The plots suggest
marginal disparity in sectoral heterogeneity between the two countries; the
variance is 0.0261 and 0.0214 for China, and 0.0275 and 0.0278 for Japan.
Notably, as expected, sectors
contributing significantly to value added differ between these countries. This
variation underpins our motivation to integrate value added as the auxiliary
element in the PR metric. We have embedded this perspective in
paragraph~4, Section~5.

On the impact of the size of an economy on PR, we would like to clarify
that it is the composition of the auxiliary variable instead of its sizes that
matters. Specifically, $\lambda_i / \sum_{i \in V} \lambda_i$ is scale-free and
is only affected by the share of sector~$i$ in the whole economy. We have added
a clarification to end of paragraph~2, Section~5.

% There was no clarification before I added on Oct. 8

\begin{comment}
4. Therefore, I suggest two things. One, provide a sensitivity analysis and
observe how the ranking and conclusions change when using other macroeconomic
variables (or other type of variables) for the page rank tuning parameter.
Second, compute and use authority and hub scores which are a generalization of
eigenvector centrality for directed networks. They do not requiere a tuning
parameter therefore authors do not need to come up with a subjective external
measure to tune it in. These measures rank nodes according to the link
structure of the network and this is exactly what authors write that want to do.
\end{comment}

Excellent suggestions!

The choice of the auxiliary measure hinges upon the specific objectives 
of the researchers. In our case, we chose value added data as the auxiliary 
information because our focus centers on analyzing the sectoral structure, and 
value added data provides an effective reflection of the economic significance 
of each sector. Further, value added is conveniently available in the IOTs but
does not contribute to the construction of the IONs. Following the suggestion,
we performed a sensitivity analysis by using an alternative macroeconomic
variable, and reported the top sector results in Appendix~B. The results
referenced in the last paragraph, Section~5.

We agree that authority and hub scores have advantages of no need for subjective
auxiliary measures. In response, we have computed these scores and summarized
the results in Appendix~C. As expected, these results are different from ours
given the different focuses in the centrality measures. In fact, each of the
hundreds of existing centrality measures has its own rationale and
interpretation. In the paper, we kept the our results because our focus is on
economic growth and the recently proposed PR centrality with value added
as auxiliary variable meets our need. The results from authority and hub scores
are referenced in the last paragraph, Section~5.

% obvious punctuation errors
\begin{comment}
5. Provide a better and more complete interpretation of assortativity. In
particular, about what is means assortativity in-in, out-out, in-out, positive
or negative in the context of input-output networks. Remember that links are
supply and demand of inputs. For example interprete and discuss what does it 
mean that there is positive assortativity for in-in but negative for out-out?
Discussion section is poor and not precise. Actually, it is not really a
discussion. Authors limit themselves to recapitulare main findings. Therefore I
highly recommend to provide a complete and more profound discussion section.
\end{comment}

We agree that the interpretation of assortativitity needed to be improved. In
response, we have added a new paragraph dedicated to the interpretation of
assortativity coefficients in terms of supplying sectors and receiving sectors.
As examples, we gave explicit interpretation
of positive in-in assortativity and negative out-out assortativity. See
paragraph~2, Section~4.

We also agree that the discussion section in the last version did not suit the
journal style well. In response, we have completely rewritten the discussion
section covering the following:
\begin{enumerate}
\item
  Methodological innovations in network analysis for assessing 
  disparities in the economic structures of China and Japan.
\item
  Abundance of centrality measures that can be used for key sector
  identification.
\item
  Availability of IOTs in national and international forms.
\item
  Potential followup investigation of China-Japan economic relations using
  multi-region IOTs.
\item
  Impacts of global shocks such as the 2018 global financial crisis and the
  Covid-19 pandemic.
\end{enumerate}

\subsection*{To Referee 2}

\begin{comment}
1. The authors state that the economic structure comparison between China and
Japan ``has long been of interest''. But further justification and detailed
reasoning could be provided. The related development economics literature
should be surveyed.
\end{comment}

% quotes
% contractions
% proofread
% responsive

We have recognized that the phrase ``has long been of interest'' may not have
been entirely precise. While a plethora of studies exists on the economies of
both China and Japan, research that specifically zeroes in on comparing their
sectoral structures is relatively scant. Consequently, we have revised our
literature review on this topic, which can now be found in paragraph~2 of
Section~1.

We have also refined our justification for contrasting the sectoral structures
of Japan and China. This enhanced motivation can be found in the latter part of
paragraph~1 in Section~1, complete with pertinent references for further
clarity.

\begin{comment}
2. The economic interpretations of the network measures could be strengthened.
What are the economic implications of the findings? For example, the
substitutes (competition) and complements (cooperation) effects between China
and Japan from an international trade perspective can be seen in Zhu et al.
(2014) and from a global value chain perspective can be seen in Zhu et al.
(2018).
\end{comment}

We genuinely value the insightful feedback. Our core emphasis in this study
revolves around the internal sectoral structures of both China and Japan. To
reinforce the narrative and conclusions drawn from our findings, we have
enriched discussions across Sections 3 to 6. Notably:
\begin{enumerate}
\item
  We introduced chord plots in Section~3 to offer a more lucid visual
  representation of the intricate intersectoral connections.
\item
  Interpretations of the weighted, directed assortativity coefficients were
  added in paragraph~2, Section~4.
\item  
  Section~5 now includes an enhanced discussion on selection of auxiliary
  information in extended PR scoring; in discussions about the top 5 sectors,
  comparisons were made with established work by \citet{li2017examining}.
\item
  We have elucidated on the similarities in the community structures of sectors
  in the last paragraph of Section~6.
\end{enumerate}

While exploring the interconnected dynamics between China and Japan's sectors is
undoubtedly compelling, it remains beyond the immediate purview of this
research. Nevertheless, inspired by prior studies~\citep{zhu2014rise,
  zhu2018similarity}, we have alluded to the promising avenues of research in
this direction, leveraging multi-region IOTs, in paragraph~4 of Section~7.

\begin{comment}
3. The dynamics of the network measures are interesting. The authors could
apply a similarity measure (e.g., cosine similarity) for each year of the
clusters to give an overall picture for the comparison (e.g., are China and
Japan becoming more similar/dissimilar over time?). Then again, what might
be the economic development drivers behind the dynamics observed? 
\end{comment}

Thank you for the constructive feedback. Following your suggestion, we have
now incorporated the AMI as a metric to evaluate the similarity between
clusters. Our investigation compared two facets: the likeness of community
structures between China and Japan in a specific year and the temporal
similarity of community structures within each country. See detailed analysis in
the last paragraph, Section~6.

The evolving nature of community structures within both nations
presents a captivating narrative. It is striking to observe the subtle,
incremental modifications in Japan's sectoral makeup juxtaposed against China's
pronounced transformations over the years. The underlying reasons for these
pronounced shifts in China's sectoral layout are especially noteworthy. While
the scope of this paper does not extend to examining these catalysts in depth,
we concur that an exploration into the forces steering these dynamics would be a
compelling topic for subsequent research endeavors. A comment has been added to
the end of the last paragraph, Section~6.

\begin{comment}
4. The limitations of the current approach should be discussed further. For
example, the current study uses national input-output tables. But
international input-output tables involving both countries are also
available. What would be the pros and cons using alternative IO tables
(national versus international)? The most recent economic issues (e.g.,
Covid) cannot be discussed as the IO tables are only available until 2018.
Any remedy or thoughts on this? 
\end{comment}

% \jy{are these references cited in the paper? Fix the
% inconsistencies}\tw{delete the ucited.}.

We have extensively revised the discussion section, Section~7, to provide a
holistic overview of our study's limitations and potential avenues for future
exploration. To specifically address the concerns raised:
\begin{enumerate}
\item
  We discuss alternative IOT databases in paragraph~3.
\item
  The potential advantages of employing multi-region IOTs are highlighted in
  paragraph~4.
\item
  The implications of global shocks, including the recent ramifications of the
  Covid-19 pandemic, are pointed out as a promising direction in paragraph~5.
\end{enumerate}
We are indebted to the reviewers for pointing out these vital discussion areas,
which have not only enriched the current paper but also charted a clear course
for our subsequent research endeavors.

\bibliographystyle{chicago}
\bibliography{cjiot}

\end{document}

### 2023-12-01 Manuscript/reply.tex
Laid Out Comments

@@
 \newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
-\newcommand{\tw}[1]{\textcolor{blue}{(TW: #1)}}
-\newcommand{\sx}[1]{\textcolor{teal}{(SX: #1)}}
+\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
+\newcommand{\mc}[1]{\textcolor{teal}{(MC: #1)}}
 
@@
 \begin{enumerate}
-\item Newly added analyses:
+\item 
   \begin{enumerate}
-    \item chord plots visualizing the sectors' in- and out-connectivities in
-      Section~3;
-    \item key sector analysis with PageRank (PR) using export value as auxiliary
-      information in Appendix~B;
-    \item key sector analysis with hub and authority centrality in Appendix~C;
-    \item dynamics of the similarity in the sector communities within each
-      country and cross the two countries in Section~6.
+    \item 
+    \item 
+    \item 
+    \item 
     \end{enumerate}
-\item Strengthened presentations:
+\item 
   \begin{enumerate}
-  \item elaborated motivation of using network tools for the comparison of
-    sectoral structures in Section~1;
-  \item expanded interpretation of directed assortativity coefficients in the
-    context of input-output tables (IOTs) in Section~4;
-  \item clarified discussion on the PR centrality using value added as
-    auxiliary information in Section~5.
-  \item completely rewritten discussions in Section~7.
+  \item 
+  \item 
+  \item 
+  \item 
   \end{enumerate}
 \end{enumerate}
-Additionally, we undertook meticulous reviews of the entire manuscript to ensure
-clarity, coherence, and grammatical precision, aiming to present methods,
-results, and discussions in a lucid manner.
 
@@
 
-\subsection*{To AE}
+\subsection*{To Referee 1}
 
 \begin{comment}
-1. Strengthen the motivation, i.e., explain how the China-Japan economy
-comparison be better conducted using the methods consequently adopted in the
-paper.
+1. It would be helpful to comment on the rationale for the proposed centered CI, 
+especially in contrast to why a few others do not work for the log-1 
+autocorrelation coefficient.
 \end{comment}
-
-As suggested, we have fortified our rationale for employing network analysis
-in examining the sectoral structures of China and Japan. Specifically:
-\begin{enumerate}
-\item 
-  Network analysis introduces advanced tools for innovative visualization.
-\item
-  Network analysis provides a deeper understanding of sectoral interdependencies,
-  transcending the rudimentary summaries from the intermediate flow matrix that
-  traditional input-output analysis offers. Notably, it encompasses metrics like
-  directed strength distributions and weighted, directed assortativities, as well
-  as sector-specific centrality measures.
-\item
-  Network analysis presents novel techniques for pinpointing key
-  sectors and discerning sectoral clusters, which surpass the capabilities of
-  conventional input-output analysis.
-\end{enumerate}
-To provide clearer exposition, we have thoroughly revised paragraph~3 of
-Section 1, thus offering a compelling prelude to our analytical approach.
 
@@
 \begin{comment}
-2. Perform sensitivity analysis of the PageRank-based results to the 
-selection of the value of the tuning parameter; I also like the idea of using
-the Kleinberg's hubs-and-authorities algorithm, which is a natural extension
-of the PageRank idea; the idea of studying similarities over time is an
-excellent one as well. 
+2. For all the figures, would it be possible to put the 6 figures in a column in 
+a single plot? It would also be helpful to make the figures a bit larger. Right 
+now it is hard to compare across different methods regarding their comparative 
+performance.
 \end{comment}
 
-Concurring with the suggestion for sensitivity analyses, we have expanded our
-examination to gauge the robustness of our key sector results obtained from the
-extended PR approach.
-
-\begin{table}[tbp]
-\centering
-\caption{The sectors with top~5 PR scores,
-based on the sensitivity analysis of the tuning parameter at the levels
-$\gamma = \{0.5, 0.85\}$ for China and Japan from 1995 to 2018
-every three years. Total value added is used as auxiliary information.}
-\label{tab:prsens}
-\resizebox{\textwidth}{!}{
-\begin{tabular}{cccccccccccccccccccc}
-\toprule
-\multirow{2}{*}{Country} & \multirow{2}{*}{Rank}
-& \multicolumn{9}{c}{$\gamma = 0.5$} & \multicolumn{9}{c}{$\gamma = 0.85$} \\
-\cmidrule(lr){3-11} \cmidrule(lr){12-20} 
-& & 1995 & 1998 & 2001 & 2004 & 2007 & 2010 & 2013 & 2016 & 2018 & 
-1995 & 1998 & 2001 & 2004 & 2007 & 2010 & 2013 & 2016 & 2018 \\ 
-\midrule
-China & 1 & 01 & 01 & 01 & 01 & 25 & 25 & 25 & 25 & 25 & 25 & 07 & 25 & 07 & 25 
-& 25 & 25 & 25 & 25 \\ 
-& 2 & 06 & 06 & 25 & 25 & 01 & 01 & 26 & 26 & 26 & 06 & 06 & 07 & 25 & 07 & 17 
-& 20 & 06 & 17 \\ 
-& 3 & 26 & 25 & 06 & 06 & 26 & 26 & 01 & 01 & 01 & 07 & 25 & 06 & 17 & 17 & 07 
-& 06 & 17 & 40 \\ 
-& 4 & 25 & 26 & 26 & 26 & 06 & 06 & 06 & 06 & 40 & 26 & 01 & 01 & 06 & 15 & 19 
-& 26 & 20 & 26 \\ 
-& 5 & 07 & 07 & 07 & 07 & 07 & 17 & 36 & 36 & 36 & 15 & 26 & 26 & 19 & 19 & 20 
-& 17 & 07 & 07 \\ [1ex]
-Japan & 1 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 & 26 
-& 26 & 26 & 26 & 26 \\ 
-& 2 & 25 & 25 & 37 & 37 & 37 & 37 & 37 & 37 & 37 & 25 & 25 & 25 & 20 & 20 & 42 
-& 42 & 42 & 42 \\ 
-& 3 & 37 & 37 & 25 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 42 & 20 
-& 20 & 20 & 20 \\ 
-& 4 & 42 & 42 & 42 & 25 & 25 & 25 & 25 & 25 & 25 & 20 & 20 & 20 & 25 & 37 & 37 
-& 37 & 37 & 37 \\ 
-& 5 & 36 & 36 & 36 & 36 & 20 & 20 & 20 & 20 & 20 & 37 & 37 & 37 & 37 & 25 & 25 
-& 25 & 25 & 25 \\  
-\bottomrule
-\end{tabular}}
-\end{table}
-
-We first obtained PR results, also using value added as auxiliary information,
-with $\gamma = 0.5$ and put them sides by side with those obtained with
-$\gamma = 0.85$ in Table~\ref{tab:prsens}. Within this framework, $\gamma$
-signifies the emphasis placed on the ranking from the IONs, while $1 - \gamma$
-represents the emphasis put on the ranking of the auxiliary variable. The
-widely-accepted value of $\gamma = 0.85$, as advocated by
-\citet{page1998pagerank}, affirms a reasonable inclination towards the
-importance of the IONs. The side-by-side comparison in Table~\ref{tab:prsens}
-reinforces our stance that $\gamma = 0.85$ better aligns with our objectives. A
-setting of $\gamma = 0.5$ seems to unduly accentuate the total value added,
-potentially skewing the centrality dynamics. For comprehensive scrutiny, we have
-incorporated this table and its pertinent discussion in our Supplementary
-Material. To guide readers to this additional resource, we have integrated a
-reference in the newly added paragraph~3 of Section~5.
-
-Kleinberg's hubs-and-authorities algorithm~\citep{kleinberg1999authoritative}
-presents an alternative approach to identifying key sectors in China and
-Japan. The sectors identified via this approach deviate from those highlighted
-by the PR method, underscoring the unique evaluative lenses inherent to each
-technique. While both methods aim to identify central nodes, the criteria and
-perspectives they adopt to discern centrality differ fundamentally. To afford
-our readers an exhaustive understanding, we juxtaposed the outcomes of both
-methods in the newly added Appendix~C.
-
-Studying the similarities in the cluster structures over time is indeed an
-excellent idea! To assess the resemblance between clusters, we adopted the
-adjusted mutual information (AMI) metric~\citep{vinh2009information,
-  vinh2010information}. Specifically, we have obtained the similarity of 
-community structures between the two countries for the same year, as well as 
-the dynamic similarity of community structures within a single country over 
-time. Comprehensive explanations for these analyses have been included at the 
-last paragraph of Section~6.
+\begin{comment}
+3. The Appendix should be moved to the main text? Assessing the performance of 
+various CI formulations for non-normal error is of central interest.
+\end{comment}
 
 \begin{comment}
-3. Improve the discussion section: better explain the assortativity analyses;
-discuss the limitations of the work - this is quite important especially 
-given that, as one of the reviewers notes, ``international input-output 
-tables involving both countries are available but not used in this study''.
+4. The authors might want to discuss in what circumstances “non-parametric” CI 
+formulas would work better. It is a bit surprising that student’s t based 
+formula works well under both normal and non-normal error structures.
 \end{comment}
 
-As suggested, we have completely rewritten the Discussion section with following
-discussion points:
-\begin{enumerate}
-\item
-  Methodological innovations in network analysis for assessing 
-  disparities in the economic structures of China and Japan.
-\item
-  Abundance of centrality measures that can be used for key sector
-  identification.
-\item
-  Availability of IOTs in national and international forms.
-\item
-  Potential followup investigation of China-Japan economic relations using
-  multi-region IOTs.
-\item
-  Impacts of global shocks such as the 2018 global financial crisis and the
-  Covid-19 pandemic.
-\end{enumerate}
-
-We acknowledge the need for a clearer interpretation of assortativity. In
-response, we have added a new paragraph dedicated to the interpretation of
-assortativity coefficients in terms of supplying sectors and receiving sectors.
-As examples, we gave explicit interpretation of positive in-in assortativity and
-negative out-out assortativity. See paragraph~2, Section~4.
-
-We are grateful to the reviewers for highlighting the existence of international
-IOTs encompassing both China and Japan. In the revised manuscript, we have
-reviewed the World Input-Output Database (WIOD)~\citep{timmer2015illustrated}
-and Asian Development Bank's Multiregional Input-Output Table database
-(ADB-MRIO)~\citep{ADB2023iot}, explaining why they did not serve our purpose
-well; see paragraph~3, Section~2. Further, the core emphasis of our paper is on
-internal sectoral structures within each nation rather than the inter-country
-connections. Analyzing the interconnectedness between sectors in China and Japan
-remains a compelling avenue for future research, a prospect we delve into in
-paragraph~4 of Section~7.
-
 \begin{comment}
-4. Expand on the insights produced; how do the reported findings compare to
-those presented in the earlier-published literature? (this is important
-since the authors state that the China-Japan economy comparison draws 
-a lot of research attention. 
+5. Page 3, 2nd line after “Standard Normal CI”: “p.168” does not seem to fit?
 \end{comment}
-
-We realized that our prior statement was not accurate.
-While there is a significant volume of literature concentrating on the economies
-of China and Japan independently, there is indeed a palpable gap in studies
-directly juxtaposing the sectoral structures of these two major Asian
-economies. To better reflect this reality, we have revisited and amended our
-literature review in paragraph~2 of Section1. In the analysis, we undertook a
-comparative exploration, accentuating both congruences and variances in relation
-to the lone preceding study that touched on this theme, namely,
-\citet{li2017examining}. This comparison is thoroughly elucidated in the
-penultimate paragraph of Section~5.
-
-\subsection*{To Referee 1}
-
-\begin{comment}
-1. One of my main concerns is contribution. The contribution of the paper is
- not methodological. Instead the contribution pretends to be in terms of a
-better understanding of the differences between China and Japan's economies.
-But the analysis done does not provide a deeper understanding different from
-what one may expect. Both centrality ranking and clustering confirm what
-was suspected or known. Therefore, the paper needs to make a deeper
-network analysis and interpretation of results in order to show the
-contribution and relevance of using network tools to analyze the
-structure of economies.
-\end{comment}
-
-We appreciate the reviewer's concern on our contributions and would like to
-clarify that our primary aim is to apply recent advancements in network analysis
-tools, including some developed by our group, to analyze the IONs of China and
-Japan's sectoral structures.
-
-Regarding the observation that our contribution ``pretends'' to be in terms of a
-better understanding of the differences between the two economies, we want to
-assure that our intentions have been genuine and firmly rooted in academic
-exploration. We acknowledge that sometimes, our analysis may seem to confirm
-previously suspected ideas, but we see this as an essential validation in
-research, further solidifying existing notions from a novel perspective.
-
-In our literature review, we found a paucity of studies on this particular
-topic, with a notable mention of \citet{li2017examining}. We would be grateful
-for any additional references the reviewers could suggest to enhance our work.
-
-To ensure clarity regarding our research contributions, the penultimate
-paragraph in the introduction has been revised at large. See also our summary at
-the beginning of this reply.
-
-\begin{comment}
-2. To study the structure of both economies authors use page rank as one of the
-centrality measures. Why page rank? This measure requieres a tuning parameter
-and therefore authors need to come up with an external measure for this. Many
-times this is a subjective measure and ends up skewing the analysis.
-\end{comment}
-
-The PR method employed in our paper, which allows the inclusion of
-auxiliary data, is an advancement of the standard PR traditionally used in
-ION analyses \citep{cerina2015world}. This refined approach was selected
-not only
-because our group developed it and we were keen to assess its practical
-application but also due to its alignment with our emphasis on economic
-growth. Specifically, we aimed to embed the macroeconomic metric of value added
-into the sectoral importance ranking. While we recognize in the revised
-manuscript that this method could potentially bias the analysis, we also view
-this as advantageous when the emphasis is on economic growth. This discussion
-can be found in paragraph~4, Section~5.
-
-We have also expanded our discussion to highlight the potential of alternative
-centrality measures for key sector identification. See paragraph~2, Section~7.
-
-\begin{comment}
-3. Related to my previous point, why using value added as the tuning parameter
-for page rank? As authors point out both economies are very different. Japan,
-being a services economy is expected to have lower value added and a more
-homogeneous distribution of value added across its most important sectors.
-Comparably, China is a manufacturing economy with known industrial policy that
-requieres certain amount of domestic value added, therefore is expected to have
-higher value added and a more skewed distribution of it across sectors.
-Importantly, we also have size of the economies; China is much bigger.
-Consequently, using value added may skew things.
-\end{comment}
-
-% histogram vs bar chart
-
-For our analysis, we used value added due to two primary
-reasons. Firstly, given our focus on economic growth, value added serves as a
-robust indicator of each sector's contribution to the overall economy. Secondly,
-the IOTs readily provide this metric, ensuring its accessibility, and it has not
-been utilized in the creation of the IONs.
-
-The homogeneity of value added across sectors in China and in Japan piques
-interest. To elucidate, we plotted bar charts of the value added data
-for both countries in 1995 and 2018 in a newly added Figure~4. The plots suggest
-marginal disparity in sectoral heterogeneity between the two countries; the
-variance is 0.0261 and 0.0214 for China, and 0.0275 and 0.0278 for Japan.
-Notably, as expected, sectors
-contributing significantly to value added differ between these countries. This
-variation underpins our motivation to integrate value added as the auxiliary
-element in the PR metric. We have embedded this perspective in
-paragraph~4, Section~5.
-
-On the impact of the size of an economy on PR, we would like to clarify
-that it is the composition of the auxiliary variable instead of its sizes that
-matters. Specifically, $\lambda_i / \sum_{i \in V} \lambda_i$ is scale-free and
-is only affected by the share of sector~$i$ in the whole economy. We have added
-a clarification to end of paragraph~2, Section~5.
-
-% There was no clarification before I added on Oct. 8
-
-\begin{comment}
-4. Therefore, I suggest two things. One, provide a sensitivity analysis and
-observe how the ranking and conclusions change when using other macroeconomic
-variables (or other type of variables) for the page rank tuning parameter.
-Second, compute and use authority and hub scores which are a generalization of
-eigenvector centrality for directed networks. They do not requiere a tuning
-parameter therefore authors do not need to come up with a subjective external
-measure to tune it in. These measures rank nodes according to the link
-structure of the network and this is exactly what authors write that want to do.
-\end{comment}
-
-Excellent suggestions!
-
-The choice of the auxiliary measure hinges upon the specific objectives 
-of the researchers. In our case, we chose value added data as the auxiliary 
-information because our focus centers on analyzing the sectoral structure, and 
-value added data provides an effective reflection of the economic significance 
-of each sector. Further, value added is conveniently available in the IOTs but
-does not contribute to the construction of the IONs. Following the suggestion,
-we performed a sensitivity analysis by using an alternative macroeconomic
-variable, and reported the top sector results in Appendix~B. The results
-referenced in the last paragraph, Section~5.
-
-We agree that authority and hub scores have advantages of no need for subjective
-auxiliary measures. In response, we have computed these scores and summarized
-the results in Appendix~C. As expected, these results are different from ours
-given the different focuses in the centrality measures. In fact, each of the
-hundreds of existing centrality measures has its own rationale and
-interpretation. In the paper, we kept the our results because our focus is on
-economic growth and the recently proposed PR centrality with value added
-as auxiliary variable meets our need. The results from authority and hub scores
-are referenced in the last paragraph, Section~5.
-
-% obvious punctuation errors
-\begin{comment}
-5. Provide a better and more complete interpretation of assortativity. In
-particular, about what is means assortativity in-in, out-out, in-out, positive
-or negative in the context of input-output networks. Remember that links are
-supply and demand of inputs. For example interprete and discuss what does it 
-mean that there is positive assortativity for in-in but negative for out-out?
-Discussion section is poor and not precise. Actually, it is not really a
-discussion. Authors limit themselves to recapitulare main findings. Therefore I
-highly recommend to provide a complete and more profound discussion section.
-\end{comment}
-
-We agree that the interpretation of assortativitity needed to be improved. In
-response, we have added a new paragraph dedicated to the interpretation of
-assortativity coefficients in terms of supplying sectors and receiving sectors.
-As examples, we gave explicit interpretation
-of positive in-in assortativity and negative out-out assortativity. See
-paragraph~2, Section~4.
-
-We also agree that the discussion section in the last version did not suit the
-journal style well. In response, we have completely rewritten the discussion
-section covering the following:
-\begin{enumerate}
-\item
-  Methodological innovations in network analysis for assessing 
-  disparities in the economic structures of China and Japan.
-\item
-  Abundance of centrality measures that can be used for key sector
-  identification.
-\item
-  Availability of IOTs in national and international forms.
-\item
-  Potential followup investigation of China-Japan economic relations using
-  multi-region IOTs.
-\item
-  Impacts of global shocks such as the 2018 global financial crisis and the
-  Covid-19 pandemic.
-\end{enumerate}
 
@@
 \begin{comment}
-1. The authors state that the economic structure comparison between China and
-Japan ``has long been of interest''. But further justification and detailed
-reasoning could be provided. The related development economics literature
-should be surveyed.
+1. The authors say “....the standard CI is a table-based bootstrap…..”.  
+What is meant by “table-based” here?  Is this just a reference to how critical 
+values used to be listed in tables?  If that’s the case, I wouldn’t refer to 
+this as a “table-based” interval. 
 \end{comment}
 
-% quotes
-% contractions
-% proofread
-% responsive
-
-We have recognized that the phrase ``has long been of interest'' may not have
-been entirely precise. While a plethora of studies exists on the economies of
-both China and Japan, research that specifically zeroes in on comparing their
-sectoral structures is relatively scant. Consequently, we have revised our
-literature review on this topic, which can now be found in paragraph~2 of
-Section~1.
-
-We have also refined our justification for contrasting the sectoral structures
-of Japan and China. This enhanced motivation can be found in the latter part of
-paragraph~1 in Section~1, complete with pertinent references for further
-clarity.
+\begin{comment}
+2. Just a comment: The recentered percentile CI proposed here is an interesting 
+interval to study. 
+\end{comment}
 
 \begin{comment}
-2. The economic interpretations of the network measures could be strengthened.
-What are the economic implications of the findings? For example, the
-substitutes (competition) and complements (cooperation) effects between China
-and Japan from an international trade perspective can be seen in Zhu et al.
-(2014) and from a global value chain perspective can be seen in Zhu et al.
-(2018).
+3. The sections are numbered, which makes it awkward when the authors refer back 
+to a section.  For instance, they refer to “...procedures described in Block 
+Bootstrap CIS.”  This would be easier to refer to if the sections were numbered.  
+(Is this a journal style choice?  If so, then you can ignore this comment.)
 \end{comment}
 
-We genuinely value the insightful feedback. Our core emphasis in this study
-revolves around the internal sectoral structures of both China and Japan. To
-reinforce the narrative and conclusions drawn from our findings, we have
-enriched discussions across Sections 3 to 6. Notably:
-\begin{enumerate}
-\item
-  We introduced chord plots in Section~3 to offer a more lucid visual
-  representation of the intricate intersectoral connections.
-\item
-  Interpretations of the weighted, directed assortativity coefficients were
-  added in paragraph~2, Section~4.
-\item  
-  Section~5 now includes an enhanced discussion on selection of auxiliary
-  information in extended PR scoring; in discussions about the top 5 sectors,
-  comparisons were made with established work by \citet{li2017examining}.
-\item
-  We have elucidated on the similarities in the community structures of sectors
-  in the last paragraph of Section~6.
-\end{enumerate}
-
-While exploring the interconnected dynamics between China and Japan's sectors is
-undoubtedly compelling, it remains beyond the immediate purview of this
-research. Nevertheless, inspired by prior studies~\citep{zhu2014rise,
-  zhu2018similarity}, we have alluded to the promising avenues of research in
-this direction, leveraging multi-region IOTs, in paragraph~4 of Section~7.
+\begin{comment}
+4.  In Figure 1 (and all the other figures), the authors present confidence 
+intervals for the real coverage rates.  The authors should specify what type of 
+CI they are using here.  I assume the authors are using a Wald-type interval for 
+this CI as this is for a proportion.  If that’s the case, it’s well known that 
+the Wald-type interval has undercoverage when the true proportion is near 0 or 
+1, which is the case in several of these scenarios, especially when phi is -0.4. 
+\end{comment}
 
 \begin{comment}
-3. The dynamics of the network measures are interesting. The authors could
-apply a similarity measure (e.g., cosine similarity) for each year of the
-clusters to give an overall picture for the comparison (e.g., are China and
-Japan becoming more similar/dissimilar over time?). Then again, what might
-be the economic development drivers behind the dynamics observed? 
+5.  In all the figures, the y-axis is allowed to vary freely making it hard to 
+compare one row directly to another.  I would suggest fixing the limits on the 
+y-axis to make comparisons easier.  
 \end{comment}
 
-Thank you for the constructive feedback. Following your suggestion, we have
-now incorporated the AMI as a metric to evaluate the similarity between
-clusters. Our investigation compared two facets: the likeness of community
-structures between China and Japan in a specific year and the temporal
-similarity of community structures within each country. See detailed analysis in
-the last paragraph, Section~6.
-
-The evolving nature of community structures within both nations
-presents a captivating narrative. It is striking to observe the subtle,
-incremental modifications in Japan's sectoral makeup juxtaposed against China's
-pronounced transformations over the years. The underlying reasons for these
-pronounced shifts in China's sectoral layout are especially noteworthy. While
-the scope of this paper does not extend to examining these catalysts in depth,
-we concur that an exploration into the forces steering these dynamics would be a
-compelling topic for subsequent research endeavors. A comment has been added to
-the end of the last paragraph, Section~6.
+\begin{comment}
+6.  Is there a reason why the coverage for mu (in Figure 1) is better for 
+negative autoregressive terms when compared with the positive autoregressive 
+term? Can the authors give some intuition behind why that makes sense? 
+\end{comment}
 
 \begin{comment}
-4. The limitations of the current approach should be discussed further. For
-example, the current study uses national input-output tables. But
-international input-output tables involving both countries are also
-available. What would be the pros and cons using alternative IO tables
-(national versus international)? The most recent economic issues (e.g.,
-Covid) cannot be discussed as the IO tables are only available until 2018.
-Any remedy or thoughts on this? 
+7.  The authors say “A smaller sample size is generally required to estimate a 
+parameter for a sample with a negative phi versus a positive phi of the same 
+magnitude.”  On a quick reading of this it sounds like the authors are 
+recommending using a smaller sample size when phi is negative.  I believe what 
+you are trying to say is that coverage rates are acceptable at smaller sample 
+sizes when phi is negative versus when phi is positive (i.e. it takes larger 
+sample sizes to get acceptable coverage when phi is positive).  Change this 
+sentence to make it more clear. 
 \end{comment}
 
-% \jy{are these references cited in the paper? Fix the
-% inconsistencies}\tw{delete the ucited.}.
+\begin{comment}
+8.   In the Discussion section, the authors say “We know theoretically that the 
+block bootstrap procedure will cover the parameter of a time series given an 
+infinitely large sample.”  Essentially, you are stating that the estimator is 
+consistent.  Is there a citation that you can point to that shows that this is 
+true? 
+\end{comment}
 
-We have extensively revised the discussion section, Section~7, to provide a
-holistic overview of our study's limitations and potential avenues for future
-exploration. To specifically address the concerns raised:
-\begin{enumerate}
-\item
-  We discuss alternative IOT databases in paragraph~3.
-\item
-  The potential advantages of employing multi-region IOTs are highlighted in
-  paragraph~4.
-\item
-  The implications of global shocks, including the recent ramifications of the
-  Covid-19 pandemic, are pointed out as a promising direction in paragraph~5.
-\end{enumerate}
+\begin{comment}
+9.   The authors studied coverage rates of the different intervals as a function 
+of sample size, but they only looked at one choice for the number of blocks.  
+Why did the authors choose to not also look at how the number of blocks affects 
+the coverage rates?
+\end{comment}
+
+\begin{comment}
+10.   Why did the authors choose to only go as high as 0.4 (and as low as -0.4) 
+for the autocorrelation parameter?  I would think that these correlations near 1 
+(or -1) would be some of the more interesting cases to study, but they are 
+completely ignored here.  Can the authors justify their choice to leave it out 
+of this study?
+\end{comment}
+
+\begin{comment}
+11.    Last paragraph: The authors mention the “ABC and bootstrap-t intervals”.  
+They do not give a citation for these intervals.   Add a citation. 
+\end{comment}
+
+\begin{comment}
+12.    The last line of the manuscript offers one line about the drawbacks of 
+the block bootstrap almost as an afterthought.  I think a discussion of the 
+drawbacks should be expanded and added to the introduction as this is an 
+important point that isn’t mentioned at all until the literal last line. 
+\end{comment}
+
 We are indebted to the reviewers for pointing out these vital discussion areas,

### 2023-12-01 Manuscript/manuscript.tex
Laid Out Comments
Responded with Some Ideas

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Authors: Add additional packages and new commands here.  
+% Limit your use of new commands and special formatting.
+
 \usepackage{physics} % for \dd
@@
 \newcommand{\mc}[1]{\textcolor{orange}{MC: (#1)}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Authors: Add additional packages and new commands here.  
-% Limit your use of new commands and special formatting.
 
@@
 perform noticeably better than the others. However, when estimating $\phi$, the 
-choice of method is of utmost importance as to avoid coverage deterioration. A 
-smaller sample size is generally required to estimate a parameter for a sample 
-with a negative $\phi$ versus a positive $\phi$ of the same magnitude. In order 
+choice of method is of utmost importance as to avoid coverage deterioration. 
+Coverage rates are acceptable at smaller sample 
+sizes when phi is positive versus when phi is negative. In
+other words, a larger sample size is generally required to estimate a 
+parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the 
+same magnitude. In order 
 to know if coverage will increase as the strength of the temporal dependence 

### 2023-12-01 Manuscript/reply.tex
Responded with Some Ideas

@@
 
-% \jy{Confirm that all the locations mentioned really contain the stated changes.}
-% \tw{check and revise}
-
 \begin{comment}
@@
 
+\mc{Not sure what they mean by "non-parametric" CIs, maybe the Percentile, BC,
+and BCA, and Recentered CIs? In Figure 4, we showed that the autocorrelation in
+the bootstrap samples is generally smaller than in the original sample. 
+Percentile, BC, and BCA CIs perform better when the temporal dependence is low.
+In these circumstances, "non-parametric" CIs would work better}
+
 \begin{comment}
@@
 \end{comment}
+
+\mc{Can we include the page number in the superscript somehow? Otherwise it does
+not fit the journal's style.}
 
@@
 
+\mc{The Efron book refers to such tables as "confidence intervals based on 
+bootstrap 'tables'"}
+
 \begin{comment}
@@
 \end{comment}
+
+\mc{Maybe we can add this to future studies}
 
@@
 \end{comment}
+
+\mc{It is a journal style choice}
 
@@
 
+\mc{It is the Wald-type interval, should we just mention the undercoverage in
+the design section of simulation and cite a source?}
+
 \begin{comment}
@@
 \end{comment}
+
+\mc{Because of the deterioration, we found it hard to fix the limits on the 
+y-axis without making the other rows look bad}
 
@@
 
+\mc{addressed}
+
 \begin{comment}
@@
 
+\citep{ratick2009175}
+
 \begin{comment}
@@
 
+\mc{For the higher positive autocorrelations, a very large sample size is
+required. We could try it for more extreme negative autocorrelations.}
+
 \begin{comment}
@@
 \end{comment}
+
+\citep[p.160]{efron1993introduction}
+\citep[p.188]{efron1993introduction}
 
@@
 \bibliographystyle{chicago}
-\bibliography{cjiot}
+\bibliography{citations}
 

### 2023-12-23 Manuscript/manuscript.tex
Plots With 2 Times Cube Root Blocksize

@@
 $\theta$ as the mean, we just need an estimate of the standard error to 
-construct an approximate CI.\citep[p.168]{efron1993introduction} Let
+construct an approximate CI.\citep{efron1993introduction} Let
 $\widehat{\text{SE}}$ be the empirical standard error of the bootstrap point 
@@
 The procedure for constructing a Student's $t$ CI based on standard bootstrap is 
-described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
+described in \citet{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
 quantile function $F^{-1}(\alpha, k)$ of a $t$ distribution with $k$ degrees of 

### 2023-12-23 Manuscript/reply.tex
12/6 Notes
Plots With 2 Times Cube Root Blocksize

@@
 \definecolor{darkblue}{rgb}{0.1, 0.2, 0.6}
-
-% \usepackage{xcolor}
+\usepackage{xcolor}
 \newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
 \newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
-\newcommand{\mc}[1]{\textcolor{teal}{(MC: #1)}}
+\newcommand{\mc}[1]{\textcolor{green}{(MC: #1)}}
 
@@
 
-\mc{Can we include the page number in the superscript somehow? Otherwise it does
-not fit the journal's style.}
+Because of the style constraints for AJUR, we have removed page numbers in 
+citations.
 
@@
 \end{comment}
+
+- When there is a positive correlation, effective sample size is lesser
+- When there is a negative correlation, effective sample size is larger, 
+meaning the coverage is better
 

### 2023-12-23 Code/exp_processing.R

@@ -1,6 +1,7 @@
 source("functions.R")
 library(copula)
 setwd("../Data")
+nrep <- 10000
 file_names <- list.files(pattern = "^exp_results")
 all_lists <- lapply(file_names, function(x) {
   loaded_list <- readRDS(x)
@@ -11,28 +12,32 @@ grouped_matrices <- split(list_of_matrices, names(list_of_matrices))
 combined_matrices <- lapply(grouped_matrices, function(x) {
   Reduce(cbind, x)
 })
-df <- data.frame(rho = numeric(), n = numeric(), CI = character(), 
+df <- data.frame(rho = numeric(), n = numeric(), blksize = numeric(),
+                 CI = character(), 
                  target = character(), cov = numeric(),
                  LB = numeric(), UB = numeric())
 for(i in names(combined_matrices)) {
-  rho <- as.numeric(strsplit(i, '_')[[1]][1])
+  phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
-  mymvd <- copula::mvdc(normalCopula(rho), margins = "exp", 
+  blksize <- as.integer(strsplit(i, '_')[[1]][3])
+  mymvd <- copula::mvdc(normalCopula(phi), margins = "exp", 
                         paramMargins = list(rate=1), marginsIdentical = TRUE)
   
   ## numerical integration to get 
   EXY <- pracma::dblquad(function(x, y) x * y * 
                            copula::dMvdc(cbind(x, y), mymvd), 0, 20, 0, 20)
-  ## approximate true phi
-  phi <- (EXY - 1) / 1
-  cov <- mychk(combined_matrices[[i]], c(1, 1, phi))
+  ## approximate true rho
+  rho <- (EXY - 1) / 1
+  cov <- mychk(combined_matrices[[i]], c(1, 1, rho))
   types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'bcCI', 'bcaCI', 'propCI')
   CI <- rep(types, each = length(cov) / length(types))
-  parameters <- c('mu', 'sigma', 'phi')
+  parameters <- c('mu', 'sigma', 'rho')
   target <- rep(parameters, length(cov) / length(parameters))
   LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
[…]

### 2023-12-23 Code/jobs.R

@@ -6,13 +6,14 @@ exp_results <- list()
 names(exp_results) <- c()
 for (phi in c(-.4, -.2, 0, .2, .4)) {
   for (n in c(100, 200, 400, 800, 1600, 3200)) {
-    blksize <- ceiling(n^(1/3))
-    set.seed(as.integer(i))
-    sim <- replicate(100, do1rep(n, phi, mystat, blksize))
-    norm_results[[paste(phi, n, sep = '_')]] <- sim
-    set.seed(as.integer(i))
-    sim <- replicate(100, do1rep(n, phi, mystat, blksize, qexp))
-    exp_results[[paste(phi, n, sep = '_')]] <- sim
+    for (blksize in c(ceiling(n^(1/3)), ceiling(2*n^(1/3)))) {
+      set.seed(as.integer(i))
+      sim <- replicate(100, do1rep(n, phi, mystat, blksize))
+      norm_results[[paste(phi, n, blksize, sep = '_')]] <- sim
+      set.seed(as.integer(i))
+      sim <- replicate(100, do1rep(n, phi, mystat, blksize, qexp))
+      exp_results[[paste(phi, n, blksize, sep = '_')]] <- sim
+    }
   }
 }
 saveRDS(norm_results, paste('../Data/norm_results', '_', i, '.rds', sep = ''))

### 2023-12-23 Code/norm_processing.R

@@ -1,5 +1,6 @@
 source("functions.R")
 setwd("../Data")
+nrep <- 10000
 file_names <- list.files(pattern = "^norm_results")
 all_lists <- lapply(file_names, function(x) {
   loaded_list <- readRDS(x)
@@ -10,12 +11,14 @@ grouped_matrices <- split(list_of_matrices, names(list_of_matrices))
 combined_matrices <- lapply(grouped_matrices, function(x) {
   Reduce(cbind, x)
 })
-df <- data.frame(phi = numeric(), n = numeric(), CI = character(), 
+df <- data.frame(phi = numeric(), n = numeric(), blksize = numeric(), 
+                 CI = character(), 
                  target = character(), cov = numeric(),
                  LB = numeric(), UB = numeric())
 for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
+  blksize <- as.integer(strsplit(i, '_')[[1]][3])
   cov <- mychk(combined_matrices[[i]], c(0, 1, phi))
   types <- c('stdCI', 'stuCI', 'pctCI', 'ctrCI', 'bcCI', 'bcaCI', 'propCI')
   CI <- rep(types, each = length(cov) / length(types))
@@ -23,7 +26,9 @@ for(i in names(combined_matrices)) {
   target <- rep(parameters, length(cov) / length(parameters))
   LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
   UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
-  new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), CI, target, cov, LB, UB)
+  new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), 
+                         blksize = rep(blksize, length(cov)), CI, target, cov, 
+                         LB, UB)
   df <- rbind(df, new_rows)
 }
 
@@ -38,3 +43,5 @@ write.csv(norm_sigma,"norm_sigma.csv", row.names = FALSE)
 t <- 'phi'
 norm_phi <- df[(df$target == t),]
 write.csv(norm_phi,"norm_phi.csv", row.names = FALSE)
+
+setwd("../Code")

### 2023-12-23 Code/plots.R

@@ -7,19 +7,30 @@ norm_sigma <- read.csv("../Data/norm_sigma.csv") %>%
 norm_phi <- read.csv("../Data/norm_phi.csv") %>% 
   filter(CI != 'ctrCI')
 
-t <- 'norm_mu'
+t <- 'norm_mu_1'
 width <- .2
-graph_bts(t, width, norm_mu)
+graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(n^(1/3))))
 
-t <- 'norm_sigma'
+t <- 'norm_sigma_1'
 width <- .2
-graph_bts(t, width, norm_sigma)
+graph_bts(t, width, norm_sigma %>% filter(blksize == ceiling(n^(1/3))))
 
-t <- 'norm_phi'
+t <- 'norm_phi_1'
 width <- .2
-graph_bts(t, width, norm_phi)
+graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
 
-source("functions.R")
+t <- 'norm_mu_2'
+width <- .2
+graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(2*n^(1/3))))
+
+t <- 'norm_sigma_2'
+width <- .2
+graph_bts(t, width, norm_sigma %>% filter(blksize == ceiling(2*n^(1/3))))
+
+t <- 'norm_phi_2'
+width <- .2
+graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(2*n^(1/3))))
+
 exp_mu <- read.csv("../Data/exp_mu.csv") %>% 
   filter(CI != 'ctrCI')
 exp_sigma <- read.csv("../Data/exp_sigma.csv") %>% 
@@ -27,14 +38,26 @@ exp_sigma <- read.csv("../Data/exp_sigma.csv") %>%
 exp_phi <- read.csv("../Data/exp_phi.csv") %>% 
   filter(CI != 'ctrCI')
 
-t <- 'exp_mu'
+t <- 'exp_mu_1'
 width <- .2
-graph_bts(t, width, exp_mu)
+graph_bts(t, width, exp_mu %>% filter(blksize == ceiling(n^(1/3))))
 
-t <- 'exp_sigma'
+t <- 'exp_sigma_1'
 width <- .2
-graph_bts(t, width, exp_sigma)
+graph_bts(t, width, exp_sigma %>% filter(blksize == ceiling(n^(1/3))))
 
[…]

### 2023-12-23 Manuscript/manuscript.tex
First Draft of Responses to Referee 1

@@
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage, generated using the R \textsl{ggplot2} package.\citep{ggplot2}
+real coverage for a standard normal marginal distribution, generated using the 
+R \textsl{ggplot2} package.\citep{ggplot2}
+
+Additionally, we evaluated the performance of block bootstrap when used to 
+estimate
+the mean, standard deviation, and the lag-1 autocorrelation coefficient of a
+stationary series with an exponential marginal distribution. The motivation of
+for this study was to investigate if the results are robust to nonnormal
+marginal distributions.
+
+The series were generated by marginally transforming the
+AR(1) series $X_t$ in the simulation study by
+\begin{equation*}
+W_t = F^{-1}[\Phi(X_t)],
+\end{equation*}
+where $F^{-1}(p)$ is the quantile function for the unit exponential 
+distribution. The true mean ($\mu$) and standard deviation ($\sigma_w$) 
+parameters 
+of $W_t$ are~1. The 
+lag-1
+autocorrelation coefficient is not invariant to the
+transformation, \citep{hofert2018elements} but its value can be obtained by
+\begin{equation*}
+\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
+\end{equation*}
+where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
+distribution with correlation parameter~$\phi$. We kept the configuration of
+$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
+autocorrelation coefficients are $\{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.
 
@@
 
-An additional simulation study in which block bootstrap is used to estimate the
-parameters of a stationary series with exponential distribution distribution is
-reported in the Appendix. The results are similar.
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_mu}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of a stationary series with marginal unit exponential
+    distribution obtained by transforming an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_mu}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
+    of a stationary series with 
+    marginal unit exponential distribution obtained by transforming an AR(1) process
+    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_sigma}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_phi}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient of a stationary series
+    with marginal unit exponential distribution obtained by transforming an AR(1) 
+    process with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_phi}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
+  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
+    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
+    of a stationary series with marginal exponential distribution
+    obtained by transforming an AR(1) process with $\phi = 0.4$ with
+    sample size $n \in \{800, 1600\}$. For 
+    each replicate, the lower and upper bounds of the CIs are displayed, as well 
+    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
+  \label{fig:eri}
+\end{figure}
+
+For an exponential marginal distribution, the empirical coverage rates for 
+$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
+%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
+and 
+the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
+%it, we are not using $\phi$ in reference to the temporal dependence of the 
+%exponentially distributed series?}, 
+as well as 95\%
+confidence intervals of the real coverage are displayed in 
+\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
+Additionally, a set of 50 CIs are displayed for each of the percentile, 
+BC, and recentered percentile approaches for exponentially distributed
+samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
+($\phi = 0.4$) in Figure~\ref{fig:eri}.
+
+It appears that a greater sample size is generally required for the bootstrap
+CIs to cover the mean and standard deviation parameters in the exponential
+margin case than in the normal margin case. However, the trends and patterns
+discussed in the main text regarding the performance of various methods and
+diverse parameters remain consistent. For example, Student's $t$ confidence
+intervals still exhibit higher coverage rates in comparison to alternative
+methods. Performance continues to be more favorable when temporal dependence is
+negative rather than positive. Of particular significance, the percentile, BC,
+and BCA confidence intervals still display a decline in coverage accuracy for
+the lag-1 autocorrelation coefficient as sample size increases as demonstrated
+in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
+manifesting the same bias issue. On the other hand, the recentered percentile
+confidence interval continues to be effective in estimating the temporal 
+dependence %\mc{replaced $\phi$ again here} 
+due to the
+inherent unbiasedness of the original point estimator. In sum, the findings for
+series that are marginally exponentially distributed closely mirror those
+attained for series that are marginally normally distributed.
 
@@
 
-\section*{Appendix: Simulation Study with Exponential Marginal Distribution}
-
-This appendix concerns the performance of block bootstrap when used to estimate
-the mean, standard deviation, and the lag-1 autocorrelation coefficient of a
-stationary series with an exponential marginal distribution. The motivation of
-for this study was to investigate if the results are robust to nonnormal
-marginal distributions.
-
-The series were generated by marginally transforming the
-AR(1) series $X_t$ in the simulation study by
-\begin{equation*}
-W_t = F^{-1}[\Phi(X_t)],
-\end{equation*}
-where $F^{-1}(p)$ is the quantile function for the unit exponential 
-distribution. The true mean ($\mu$) and standard deviation ($\sigma_w$) 
-parameters 
-of $W_t$ are~1. The 
-lag-1
-autocorrelation coefficient is not invariant to the
-transformation, \citep{hofert2018elements} but its value can be obtained by
-\begin{equation*}
-\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
-\end{equation*}
-where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
-distribution with correlation parameter~$\phi$. We kept the configuration of
-$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
-autocorrelation coefficients are $\{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_mu}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a stationary series with marginal unit exponential
-    distribution obtained by transforming an AR(1) process with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_mu}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
-    of a stationary series with 
-    marginal unit exponential distribution obtained by transforming an AR(1) process
-    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_sigma}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_phi}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient of a stationary series
-    with marginal unit exponential distribution obtained by transforming an AR(1) 
-    process with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
-  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
-    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
-    of a stationary series with marginal exponential distribution
-    obtained by transforming an AR(1) process with $\phi = 0.4$ with
-    sample size $n \in \{800, 1600\}$. For 
-    each replicate, the lower and upper bounds of the CIs are displayed, as well 
-    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
-  \label{fig:eri}
-\end{figure}
-
-The empirical coverage rates for $\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
-%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
-and 
-the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
-%it, we are not using $\phi$ in reference to the temporal dependence of the 
-%exponentially distributed series?}, 
-as well as 95\%
-confidence intervals of the real coverage are displayed in 
-\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
-Additionally, a set of 50 CIs are displayed for each of the percentile, 
-BC, and recentered percentile approaches for exponentially distributed
-samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
-($\phi = 0.4$) in Figure~\ref{fig:eri}.
-
-It appears that a greater sample size is generally required for the bootstrap
-CIs to cover the mean and standard deviation parameters in the exponential
-margin case than in the normal margin case. However, the trends and patterns
-discussed in the main text regarding the performance of various methods and
-diverse parameters remain consistent. For example, Student's $t$ confidence
-intervals still exhibit higher coverage rates in comparison to alternative
-methods. Performance continues to be more favorable when temporal dependence is
-negative rather than positive. Of particular significance, the percentile, BC,
-and BCA confidence intervals still display a decline in coverage accuracy for
-the lag-1 autocorrelation coefficient as sample size increases as demonstrated
-in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
-manifesting the same bias issue. On the other hand, the recentered percentile
-confidence interval continues to be effective in estimating the temporal 
-dependence %\mc{replaced $\phi$ again here} 
-due to the
-inherent unbiasedness of the original point estimator. In sum, the findings for
-series that are marginally exponentially distributed closely mirror those
-attained for series that are marginally normally distributed.
-
 \bibliographystyle{unsrtnat}

### 2023-12-23 Manuscript/reply.tex
First Draft of Responses to Referee 1

@@
 
+After discussion of the flaws of percentile, BC, and BCA CIs at the end of the
+first paragraph of Discussion, we have included these additional comments on
+why the proposed CI performs well:
+
+The uncertainty measure from bootstrap, which is used to determine the width of
+the percentile CI, is quite consistent in comparison to that used for BC and 
+BCA CIs. However, for a percentile CI, the center seems
+to be at the wrong location but is corrected when $\hat\theta_n$ is used as the
+center. This is most likely the reason why the proposed recentered percentile CI
+perfoms so much better than percentile, BC, and BCA CIs.
+
 \begin{comment}
@@
 
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/alt_plot_norm_mu_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu}
+\end{figure}
+
+Here is an example of what this would look like. We find that it is a little
+cluttered to make comparisons, so we will use the original format.
+
 \begin{comment}
@@
 \end{comment}
+
+The text from the Appendix has been moved to the Simulation Study section.
 
@@
 
-\mc{Not sure what they mean by "non-parametric" CIs, maybe the Percentile, BC,
-and BCA, and Recentered CIs? In Figure 4, we showed that the autocorrelation in
-the bootstrap samples is generally smaller than in the original sample. 
-Percentile, BC, and BCA CIs perform better when the temporal dependence is low.
-In these circumstances, "non-parametric" CIs would work better}
+The formula for the "parametric" CIs concerns the distribution of the 
+bootstrapped statistic, but we actually expect such CIs to work for different
+error structures.
 

### 2023-12-23 Code/functions.R

@@ -119,3 +119,28 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
   ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10,
          height = 5.8)
 }
+
+alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
+{
+  font_add_google("EB Garamond")
+  #  windows()
+  
+  showtext_auto()
+  
+  data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
+                    labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Recentered'))
+  
+  ggplot(data, aes(x = n, y = cov, color = CI)) +
+    geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
+    geom_line(size = .2) +
+    geom_errorbar(aes(ymin=LB, ymax = UB, color = CI), width = width, size = .2) +
+    facet_grid(. ~ factor(phi), scales = 'free') +
+    labs(x = 'Sample Size', y = 'Coverage Rate') +
+    scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
+            element_text(family = "EB Garamond", size = 10),
+          strip.text.y = element_text(angle = 270, hjust = 1)) +
+    scale_y_continuous(trans=trans)
+  ggsave(paste('../Manuscript/figures/alt_plot_', t, '.pdf', sep = ''), width = 10,
+         height = 5.8)
+}

### 2023-12-23 Code/plots.R

@@ -10,6 +10,7 @@ norm_phi <- read.csv("../Data/norm_phi.csv") %>%
 t <- 'norm_mu_1'
 width <- .2
 graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(n^(1/3))))
+alt_graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(n^(1/3))))
 
 t <- 'norm_sigma_1'
 width <- .2

### 2023-12-24 Manuscript/manuscript.tex
12/24 Notes

@@
 should provide valid confidence intervals as the length of the time series goes
-to infinity. In practice, however, it is necessary to know how large of a finite 
+to infinity. \citep{calhoun2018} In practice, however, it is necessary to know 
+how large of a finite 
 sample is required for block bootstrap confidence intervals to work well. This 
@@
 %\eds{thank you for checking!}
+
+\citet{lahiri1999theoretical} finds that moving block bootstrap has better 
+performance than non-overlapping block bootstrap. Additionally, moving block 
+bootstrap with nonrandom
+block sizes results in lower mean-squared errors than moving block bootstrap
+with random block sizes. \citet{buhlmann1999block} notes that a drawback of 
+block bootstrap is that it heavily depends on block size, which has to be chosen
+by the user of the method.
+Even when using the appropriate settings, as noted by
+\citet{buhlmann2002bootstraps} notes some general drawbacks of block 
+bootstrap --- with respect to how reasonably it imitates the data-generating 
+process. In addition, although block bootstrap is primarily used for stationary 
+time series, it can be outperformed by other bootstrap schemes for linear time
+series and categorical processes.
 
@@
 bootstrap sample. As $n$ increases, both~$l$ and $n / l$ should also increase. 
-To achieve this, $l$ is often assigned a value as a function of $n$. A common 
-function that is considered optimal is $l = \lceil n^{1/3} \rceil$,\citep{buhlmann1999block} 
+To achieve this, the order of $l$ is often assigned a value as a function of 
+$n$. A common 
+expression that is considered optimal for the order of $l$ is 
+$\lceil n^{1/3} \rceil$,
+\citep{buhlmann1999block} 
 which was adopted in this study.
@@
 This CI is centered by the original point estimate $\hat\theta_n$ and is 
-symmetric. The standard CI is a table-based bootstrap interval approach. Its 
+symmetric. The standard CI is classified by \citet{efron1993introduction} 
+as a confidence interval based on bootstrap "tables". Its 
 validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
@@
 estimate $\hat\theta_n$ and is symmetric. Like the standard normal interval, the
-Student's $t$ CI is a table-based bootstrap interval approach. In this case, its 
+Student's $t$ CI is classified by \citet{efron1993introduction} 
+as a confidence interval based on bootstrap "tables". In this case, its 
 validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
@@
 $n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
-10000 replicates. For each replicate, we constructed six 95\% block bootstrap 
+10000 replicates. The 
+block bootstrap sampling step was done with function \texttt{tsboot} from R 
+package \textsl{boot},\citep{boot} with block size $\lceil n / l \rceil$. This 
+function by default is an implementation of moving block bootstrap as described 
+in the previous section, meaning that that blocks are allowed to wrap around, 
+and we tried both $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$,
+keeping the order of the block size constant but varying the coefficient. 
+For each replicate, we constructed 
+six 95\% block bootstrap 
 CIs for each parameter as described in the last section with $B = 1000$. We can 
@@
 Then we estimated their actual coverage 
-rates along with their 95\% confidence intervals from the 10000 replicates. The 
-block bootstrap sampling step was done with function \texttt{tsboot} from R 
-package \textsl{boot},\citep{boot} with block size $\lceil n / l \rceil$. This 
-function by default is an implementation of moving block bootstrap as described 
-in the previous section, meaning that that blocks are allowed to wrap around, 
-and $l = \lceil n^{1/3} \rceil$.
+rates along with their 95\% confidence intervals from the 10000 replicates.
 
@@
 expected to match the nominal level. Because it is unlikely for the coverage to 
-exactly match the nominal level, we can construct a 95\% CI of the coverage rate 
+exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
+coverage rate 
 (which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
@@
 interval are above .95, the results suggest that the method is overestimating 
-the process' variability. \textbf{Figures~\ref{fig:mu}--\ref{fig:phi}} 
+the process' variability. \citet{brown2001interval} notes that the Wald-type 
+interval has poor coverage as the proportion approaches 0 or 1.
+\textbf{Figures~\ref{fig:mu1}--\ref{fig:phi1}} 
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu}
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
@@
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu}
+  \label{fig:mu1}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_sigma}
+  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
@@
     coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The 
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:sigma}
+  \label{fig:sigma1}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_phi}
+  \includegraphics[width=\textwidth]{figures/plot_norm_phi_1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
@@
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi}
+  \label{fig:phi1}
 \end{figure}
 
-For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
+For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
 that all methods eventually approach correct coverage of $\mu$ as sample size 
@@
 For estimating the standard deviation parameter~$\sigma_x$,
-\textbf{Figure~\ref{fig:sigma}} suggests that every method can reach nominal 
+\textbf{Figure~\ref{fig:sigma1}} suggests that every method can reach nominal 
 coverage of $\sigma_x$ if the sample is large enough, but for a given $n$ and 
@@
 For estimating the autocorrelation parameter~$\phi$, 
-\textbf{Figure~\ref{fig:phi}} suggests that while standard normal, Student's $t$, and 
+\textbf{Figure~\ref{fig:phi1}} suggests that while standard normal, Student's $t$, and 
 recentered percentile CIs do approach correct coverage as sample size increases, 
@@
 also investigate if there are types of block bootstrap interval construction 
-such as $ABC$ or bootstrap-t intervals, or alternatives to block bootstrap, such 
-as AR-Sieve bootstrap,\citep{kreiss1992bootstrap} that could more
-appropriately recover the parameters of a time series. In addition, as noted by
-\citet{buhlmann2002bootstraps}, there are some general drawbacks of block 
-bootstrap --- with respect to how reasonably it imitates the data-generating 
-process --- which may be investigated in a future study.
+such as $ABC$ or bootstrap-t intervals \citep{efron1993introduction} that could 
+more
+appropriately recover the parameters of a time series. We discussed some
+drawbacks of block bootstrap in the introduction, which could motivate a similar
+simulation study for alternatives to block bootstrap, such 
+as AR-Sieve bootstrap, \citep{kreiss1992bootstrap} which 
+\citet{buhlmann2002bootstraps} finds to be the best for linear time series. 
+Lastly, because of its exceptional performance in comparison to the other 
+CIs that are not based on bootstrap "tables", the proposed recentered percentile 
+CI would be
+an interesting method to study further with different bootstrap schemes.
 

### 2023-12-24 Manuscript/reply.tex
12/24 Notes

@@
 
-\mc{The Efron book refers to such tables as "confidence intervals based on 
-bootstrap 'tables'"}
+This terminology was used because, \citet{efron1993introduction} refers to such 
+CIs as 
+"confidence intervals based on 
+bootstrap 'tables'." We have changed these sentences as shown below:
+
+The standard CI is classified by \citet{efron1993introduction} 
+as a confidence interval based on bootstrap "tables".
+Like the standard normal interval, the
+Student's $t$ CI is classified by \citet{efron1993introduction} 
+as a confidence interval based on bootstrap "tables".
 
@@
 
-\mc{Maybe we can add this to future studies}
+We have added this comment to the discussion:
+Lastly, because of its exceptional performance in comparison to the other 
+CIs that are not based on bootstrap "tables", the proposed recentered percentile 
+CI would be
+an interesting method to study further with different bootstrap schemes.
 
@@
 
-\mc{It is a journal style choice}
+This is a journal style choice.
 
@@
 
-\mc{It is the Wald-type interval, should we just mention the undercoverage in
-the design section of simulation and cite a source?}
+We modified the Design section as below:
+
+If all values in the interval are below 0.95, the results would suggest 
+that the method either is providing inaccurate estimation, is underestimating 
+the process' variability, or a combination of both. If all values in the 
+interval are above .95, the results suggest that the method is overestimating 
+the process' variability. \citet{brown2001interval} notes that the Wald-type 
+interval has poor coverage as the proportion approaches 0 or 1.
 
@@
 
-\mc{Because of the deterioration, we found it hard to fix the limits on the 
-y-axis without making the other rows look bad}
+Because of the deterioration for $\phi$, we found it hard to fix the limits on 
+the 
+y-axis without hurting the visualization for the other rows. Below is an 
+example:
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/alt2plot_norm_phi_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard normal distribution with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:phi1}
+\end{figure}
 
@@
 
-\mc{addressed}
+The original sentence has been replaced with:
+Coverage rates are acceptable at smaller sample 
+sizes when phi is positive versus when phi is negative. In
+other words, a larger sample size is generally required to estimate a 
+parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the 
+same magnitude.
 
@@
 
+\citep{calhoun2018}
+
 \begin{comment}
@@
 
-\citep{ratick2009175}
+We have now repeated the same simulation study with block size as an 
+additional experimental factor. The optimal order of block size is 
+$\lceil n^{1/3} \rceil$, so we tried the same simulations using 
+$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$
 
@@
 
-\mc{For the higher positive autocorrelations, a very large sample size is
-required. We could try it for more extreme negative autocorrelations.}
+For practical purposes, it is in fact rare for autocorrelations to be stronger
+than 0.4. We have established the trend as the strength of the autocorrelation 
+increases, and how it varies depending on the sign of the autocorrelation and 
+the parameter of interest.
 
@@
 
-\citep[p.160]{efron1993introduction}
-\citep[p.188]{efron1993introduction}
+These intervals are discussed in \citep{efron1993introduction}. A citation
+is now provided in the last paragraph.
 
@@
 \end{comment}
+
+We have included this discussion of problems with block bootstrap in the
+introduction:
+
+\citet{lahiri1999theoretical} finds that moving block bootstrap has better 
+performance than non-overlapping block bootstrap. Additionally, moving block 
+bootstrap with nonrandom
+block sizes results in lower mean-squared errors than moving block bootstrap
+with random block sizes. \citet{buhlmann1999block} notes that a drawback of 
+block bootstrap is that it heavily depends on block size, which has to be chosen
+by the user of the method.
+Even when using the appropriate settings, as noted by
+\citet{buhlmann2002bootstraps} notes some general drawbacks of block 
+bootstrap --- with respect to how reasonably it imitates the data-generating 
+process. In addition, although block bootstrap is primarily used for stationary 
+time series, it can be outperformed by other bootstrap schemes for linear time
+series and categorical processes.
 

### 2023-12-24 Code/functions.R

@@ -144,3 +144,28 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
   ggsave(paste('../Manuscript/figures/alt_plot_', t, '.pdf', sep = ''), width = 10,
          height = 5.8)
 }
+
+alt_graph_bts2 <- function(t, width, data, trans = 'identity', level = .95)
+{
+  font_add_google("EB Garamond")
+  #  windows()
+  
+  showtext_auto()
+  
+  data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
+                    labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Recentered'))
+  
+  ggplot(data, aes(x = n, y = cov)) +
+    geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
+    geom_line(size = .2) +
+    geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width, size = .2) +
+    facet_grid(factor(CI) ~ factor(phi)) +
+    labs(x = 'Sample Size', y = 'Coverage Rate') +
+    scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
+            element_text(family = "EB Garamond", size = 10),
+          strip.text.y = element_text(angle = 270, hjust = 1)) +
+    scale_y_continuous(trans=trans)
+  ggsave(paste('../Manuscript/figures/alt2plot_', t, '.pdf', sep = ''), width = 10,
+         height = 5.8)
+}

### 2023-12-24 Code/plots.R

@@ -19,6 +19,7 @@ graph_bts(t, width, norm_sigma %>% filter(blksize == ceiling(n^(1/3))))
 t <- 'norm_phi_1'
 width <- .2
 graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
+alt_graph_bts2(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
 
 t <- 'norm_mu_2'
 width <- .2

### 2023-12-25 Manuscript/manuscript.tex
First Draft of Replies to Referee 2

@@
 $\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
-$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. The 
+$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. We only
+used serial dependences as strong as 0.4, because we only seek to 
+establish the 
+general trend as the strength of the autocorrelation 
+increases, and how it varies depending on the sign of the autocorrelation and 
+the parameter of interest. The 
 series $X_t$ has mean zero and variance 
@@
 interval has poor coverage as the proportion approaches 0 or 1.
-\textbf{Figures~\ref{fig:mu1}--\ref{fig:phi1}} 
+\textbf{Figures~\ref{fig:mu1}--\ref{fig:phi2}} 
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
@@
 
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu2}
+\end{figure}
+
+\begin{figure}[bp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
+    marginal standard normal distribution with AR 
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:sigma2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard normal distribution with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:phi2}
+\end{figure}
+
 For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
@@
 
+Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
+coverage 
+rates of $\mu$ appear to be lower when
+using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
+would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
+$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
+$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
+by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
+for smaller values of $n$.
+
+\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
+\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
+slightly lower
+especially for negative values of $\phi$, although Student's $t$ CIs are again
+not as influenced by this change in $l$. A larger sample size seems necessary
+when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.
+
+As shown in \textbf{Figure~\ref{fig:phi2}},
+recentered percentile and standard CIs have slightly lower coverage rates when
+estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
+Although it is still a problem, the coverage deterioration appears to be less 
+dramatic for BCA,
+BC, and percentile CIs.
+
+Aside from these differences, the overall changes
+in performance when other experimental factors are changed are the same.
+
 \begin{figure}[tbp]
@@
   \caption{50 replicate percentile, BC, and recentered percentile CIs for 
-    samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$. For 
+    samples of $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$)
+    for an AR(1) process with $\phi = 0.4$. For 
     each replicate, the lower and upper bounds of the CIs are displayed, as well 
@@
 estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
-perform noticeably better than the others. However, when estimating $\phi$, the 
+perform noticeably better than the others.
+However, when estimating $\phi$, the 
 choice of method is of utmost importance as to avoid coverage deterioration. 
+In addition, choice of block size is another important parameter, as
+$l = \lceil n^{1/3} \rceil$ results in better coverage than 
+$l = \lceil 2n^{1/3} \rceil$.
 Coverage rates are acceptable at smaller sample 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_mu}
+  \includegraphics[width=\textwidth]{figures/plot_exp_mu_1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
@@
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
     The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_mu}
+  \label{fig:exp_mu1}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
+  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
@@
     with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
     The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_sigma}
+  \label{fig:exp_sigma1}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_phi}
+  \includegraphics[width=\textwidth]{figures/plot_exp_phi_1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
@@
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
     The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi}
+  \label{fig:exp_phi1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_mu_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of a stationary series with marginal unit exponential
+    distribution obtained by transforming an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_mu2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
+    of a stationary series with 
+    marginal unit exponential distribution obtained by transforming an AR(1) process
+    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_sigma2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_phi_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient of a stationary series
+    with marginal unit exponential distribution obtained by transforming an AR(1) 
+    process with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_phi2}
 \end{figure}
@@
     obtained by transforming an AR(1) process with $\phi = 0.4$ with
-    sample size $n \in \{800, 1600\}$. For 
+    sample size $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$). For 
     each replicate, the lower and upper bounds of the CIs are displayed, as well 
@@
 confidence intervals of the real coverage are displayed in 
-\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
+\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi2}}. 
 Additionally, a set of 50 CIs are displayed for each of the percentile, 
@@
 methods. Performance continues to be more favorable when temporal dependence is
-negative rather than positive. Of particular significance, the percentile, BC,
+negative rather than positive. Altering the block size results in the same 
+changes in performance of different CIs. Of particular significance, the 
+percentile, BC,
 and BCA confidence intervals still display a decline in coverage accuracy for

### 2023-12-25 Manuscript/reply.tex
First Draft of Replies to Referee 2

@@
 
+Below is an example of what this would look like. We find that it is a little
+cluttered to make comparisons, so we will use the original format.
+
 \begin{figure}[tbp]
@@
 \end{figure}
-
-Here is an example of what this would look like. We find that it is a little
-cluttered to make comparisons, so we will use the original format.
 
@@
 We have added this comment to the discussion:
+
 Lastly, because of its exceptional performance in comparison to the other 
@@
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi1}
+  \label{fig:alt_phi1}
 \end{figure}
@@
 
-- When there is a positive correlation, effective sample size is lesser
-- When there is a negative correlation, effective sample size is larger, 
-meaning the coverage is better
+If a stationary series has a positive autocorrelation, the effective sample
+size is decreased, whereas is a series has a negative autocorrelation, the
+effective sample size is increased. Additionally, we expect this to have a 
+greater effect on the the estimation of the location parameter versus that
+of the scale parameter or temporal dependence parameter.
 
@@
 The original sentence has been replaced with:
+
 Coverage rates are acceptable at smaller sample 
@@
 $\lceil n^{1/3} \rceil$, so we tried the same simulations using 
-$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$
+$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
+the changed Results subsection below:
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu1}
+\end{figure}
+
+\begin{figure}[bp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
+    marginal standard normal distribution with AR 
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The 
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:sigma1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_phi_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard normal distribution with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:phi1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu2}
+\end{figure}
+
+\begin{figure}[bp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
+    marginal standard normal distribution with AR 
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:sigma2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard normal distribution with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:phi2}
+\end{figure}
+
+For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
+that all methods eventually approach correct coverage of $\mu$ as sample size 
+increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
+correct coverage, except for samples with strong negative dependence, in which 
+case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
+a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
+CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
+other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
+recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
+nominal level for all combinations of $n$ and $\phi$. All methods seem to 
+require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
+negative dependence versus positive dependence. For example, BC CIs recover 
+$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
+$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
+stronger, holding everything else equal, coverage increases, which lead to the 
+Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
+stronger, holding everything else equal, coverage decreases, and a larger sample 
+is necessary to recover~$\mu$.
+
+For estimating the standard deviation parameter~$\sigma_x$,
+\textbf{Figure~\ref{fig:sigma1}} suggests that every method can reach nominal 
+coverage of $\sigma_x$ if the sample is large enough, but for a given $n$ and 
+$\phi$, coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general.
+Like $\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample 
+sizes when compared to other methods. Unlike $\mu$, there is no over-coverage 
+issue for $\sigma_x$ when $\phi = -0.4$. Standard normal, percentile, BC, BCA, and 
+recentered percentile CIs again have similar performance. All methods seem to 
+have slightly higher coverage of $\sigma_x$ when $\phi$ is negative versus when 
+$\phi$ is positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as 
+the strength of the temporal dependence increases.
+
+For estimating the autocorrelation parameter~$\phi$, 
+\textbf{Figure~\ref{fig:phi1}} suggests that while standard normal, Student's $t$, and 
+recentered percentile CIs do approach correct coverage as sample size increases, 
+percentile, BC, and BCA CIs deteriorate as sample size increases, especially as 
+the strength of the temporal dependence increases. Because of this, only 
+standard normal, Student's $t$, and recentered percentile CIs should be considered as 
+effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
+again can achieve correct coverage with smaller sample sizes when compared to 
+standard and recentered percentile CIs which perform similarly. Student's $t$ 
+CIs can can recover $\phi$ at the nominal level for $n \geq 100$ when the 
+sample's temporal dependence is as strong as 0.4. Coverage appears to be higher 
+for all methods when the dependence is negative rather than positive. Whether or 
+not the dependence is negative or positive, coverage of $\phi$ seems to increase 
+slightly as the absolute value increases for standard normal, Student's $t$, and 
+recentered percentile CIs. For the values of $\phi$ observed, there are no 
+examples of over-coverage for standard normal, Student's $t$, BC, BCA, or recentered 
+percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
+sample sizes when $\phi = -0.2$ and when $\phi = 0$, indicating again that they 
+should not be used.
+
+Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
+coverage 
+rates of $\mu$ appear to be lower when
+using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
+would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
+$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
+$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
+by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
+for smaller values of $n$.
+
+\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
+\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
+slightly lower
+especially for negative values of $\phi$, although Student's $t$ CIs are again
+not as influenced by this change in $l$. A larger sample size seems necessary
+when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.
+
+As shown in \textbf{Figure~\ref{fig:phi2}},
+recentered percentile and standard CIs have slightly lower coverage rates when
+estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
+Although it is still a problem, the coverage deterioration appears to be less 
+dramatic for BCA,
+BC, and percentile CIs.
+
+Aside from these differences, the overall changes
+in performance when other experimental factors are changed are the same.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
+  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
+    samples of $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$)
+    for an AR(1) process with $\phi = 0.4$. For 
+    each replicate, the lower and upper bounds of the CIs are displayed, as well 
+    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
+  \label{fig:npi}
+\end{figure}
+
+The outcomes of the $\phi$ estimation raise a natural question about the 
+lackluster performance of certain methodologies. To delve into this inquiry, a
+set of 50 CIs was generated for each of the percentile, BC, and recentered
+percentile  approaches for samples of $n \in \{800, 1600\}$. Illustrated in 
+\textbf{Figure~\ref{fig:npi}}, it becomes evident that the percentile-based CIs 
+exhibit a notable bias, predominantly manifesting as a substantial 
+underestimation of $\phi$ with point estimator $\bar\theta_n^B$, that is, the 
+average of $B$ bootstrap point estimates. As the sample size increases from 800 
+to 1600, this bias does not vanish while the uncertainty reduces, which explains 
+why the coverage rates deteriorate. The bias in $\bar\theta_n^B$ also appears to 
+invalidate the bias-correction in the BC bootstrap, leading to the poor 
+performance of the BC intervals. The BCA intervals have the same problem as the 
+BC intervals in the bias-correction step. The root of the issue appears to be 
+that the autocorrelation in the block bootstrap samples is somehow smaller 
+compared to that in the original sample. On the other hand, the original point 
+estimator $\hat\theta_n$ is asymptotically unbiased. Since the width is based on 
+the uncertainty in the bootstrap point estimates $\hat\theta_n^{(b)}$, 
+$b = 1, \ldots, B$, the percentile CIs recentered at the original point estimate
+$\hat\theta_n$ provide desired coverage.
+
+To summarize, the performance of the CIs depends on the target parameter. When
+estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
+perform noticeably better than the others.
+However, when estimating $\phi$, the 
+choice of method is of utmost importance as to avoid coverage deterioration. 
+In addition, choice of block size is another important parameter, as
+$l = \lceil n^{1/3} \rceil$ results in better coverage than 
+$l = \lceil 2n^{1/3} \rceil$.
+Coverage rates are acceptable at smaller sample 
+sizes when phi is positive versus when phi is negative. In
+other words, a larger sample size is generally required to estimate a 
+parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the 
+same magnitude. In order 
+to know if coverage will increase as the strength of the temporal dependence 
+increases, one need to know what the parameter of interest is, and in the case 
+of $\mu$, the direction of the serial dependence. The BC approach does not seem 
+to be correcting bias appropriately when estimating $\phi$. Like the percentile 
+method, the recentered percentile method uses the spread from the bootstrap to 
+construct the width of the CI. However, the recentered approach, does not 
+correct from the original point estimate $\hat\theta_n$.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_mu_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of a stationary series with marginal unit exponential
+    distribution obtained by transforming an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_mu1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
+    of a stationary series with 
+    marginal unit exponential distribution obtained by transforming an AR(1) process
+    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_sigma1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_phi_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient of a stationary series
+    with marginal unit exponential distribution obtained by transforming an AR(1) 
+    process with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_phi1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_mu_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of a stationary series with marginal unit exponential
+    distribution obtained by transforming an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_mu2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
+    of a stationary series with 
+    marginal unit exponential distribution obtained by transforming an AR(1) process
+    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_sigma2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_phi_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient of a stationary series
+    with marginal unit exponential distribution obtained by transforming an AR(1) 
+    process with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_phi2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
+  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
+    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
+    of a stationary series with marginal exponential distribution
+    obtained by transforming an AR(1) process with $\phi = 0.4$ with
+    sample size $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$). For 
+    each replicate, the lower and upper bounds of the CIs are displayed, as well 
+    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
+  \label{fig:eri}
+\end{figure}
+
+For an exponential marginal distribution, the empirical coverage rates for 
+$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
+%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
+and 
+the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
+%it, we are not using $\phi$ in reference to the temporal dependence of the 
+%exponentially distributed series?}, 
+as well as 95\%
+confidence intervals of the real coverage are displayed in 
+\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi2}}. 
+Additionally, a set of 50 CIs are displayed for each of the percentile, 
+BC, and recentered percentile approaches for exponentially distributed
+samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
+($\phi = 0.4$) in Figure~\ref{fig:eri}.
+
+It appears that a greater sample size is generally required for the bootstrap
+CIs to cover the mean and standard deviation parameters in the exponential
+margin case than in the normal margin case. However, the trends and patterns
+discussed in the main text regarding the performance of various methods and
+diverse parameters remain consistent. For example, Student's $t$ confidence
+intervals still exhibit higher coverage rates in comparison to alternative
+methods. Performance continues to be more favorable when temporal dependence is
+negative rather than positive. Altering the block size results in the same 
+changes in performance of different CIs. Of particular significance, the 
+percentile, BC,
+and BCA confidence intervals still display a decline in coverage accuracy for
+the lag-1 autocorrelation coefficient as sample size increases as demonstrated
+in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
+manifesting the same bias issue. On the other hand, the recentered percentile
+confidence interval continues to be effective in estimating the temporal 
+dependence %\mc{replaced $\phi$ again here} 
+due to the
+inherent unbiasedness of the original point estimator. In sum, the findings for
+series that are marginally exponentially distributed closely mirror those
+attained for series that are marginally normally distributed.
 
@@
 
-For practical purposes, it is in fact rare for autocorrelations to be stronger
-than 0.4. We have established the trend as the strength of the autocorrelation 
+We have included this comment in the Design subsection:
+
+We only
+used serial dependences as strong as 0.4, because we only seek to 
+establish the 
+general trend as the strength of the autocorrelation 
 increases, and how it varies depending on the sign of the autocorrelation and 

### 2024-01-02 Manuscript/manuscript.tex
Included Effective Sample Size Bit in Paper, still need reference

@@
 stronger, holding everything else equal, coverage decreases, and a larger sample 
-is necessary to recover~$\mu$.
+is necessary to recover~$\mu$. A possible explanation for this is that if a 
+stationary series has a positive 
+autocorrelation, the effective sample
+size is decreased, whereas is a series has a negative autocorrelation, the
+effective sample size is increased. Additionally, this seems to have a 
+greater effect on the the estimation of the location parameter versus that
+of the scale parameter or temporal dependence parameter.
 

### 2024-01-02 Manuscript/reply.tex
Included Effective Sample Size Bit in Paper, still need reference

@@
 
-If a stationary series has a positive autocorrelation, the effective sample
+We have included this comment at the end of the paragraph on estimation of 
+$\mu$:
+
+A possible explanation for this is that if a 
+stationary series has a positive 
+autocorrelation, the effective sample
 size is decreased, whereas is a series has a negative autocorrelation, the
-effective sample size is increased. Additionally, we expect this to have a 
+effective sample size is increased. Additionally, this seems to have a 
 greater effect on the the estimation of the location parameter versus that
@@
 stronger, holding everything else equal, coverage decreases, and a larger sample 
-is necessary to recover~$\mu$.
+is necessary to recover~$\mu$.  A possible explanation for this is that if a 
+stationary series has a positive 
+autocorrelation, the effective sample
+size is decreased, whereas is a series has a negative autocorrelation, the
+effective sample size is increased. Additionally, this seems to have a 
+greater effect on the the estimation of the location parameter versus that
+of the scale parameter or temporal dependence parameter.
 

### 2024-01-02 Manuscript/reply.tex
Comment on Drawbacks in Discussion

@@
 
+We also added this comment in the Discussion section:
+
+We discussed some
+drawbacks of block bootstrap in the introduction, which could motivate a similar
+simulation study for alternatives to block bootstrap, such 
+as AR-Sieve bootstrap, \citep{kreiss1992bootstrap} which 
+\citet{buhlmann2002bootstraps} finds to be the best for linear time series.
+
 We are indebted to the reviewers for pointing out these vital discussion areas,

### 2024-01-02 Manuscript/manuscript.tex
initial feedback

@@
 series and categorical processes.
+\eds{If we include all these drawbacks here, we need to also provide some good 
+features of block bootstrap as well, otherwise, why do we care about their CI 
+performance?}
 
@@
 We propose a CI that is centered at the original point estimate and uses the 
-variation in the bootstrap estimates to construct the error bound. This interval 
+variation in the bootstrap estimates to construct the error bound. 
+\eds{The motivation behind proposing such an interval was based on the 
+simulation performance of the BC and BCA intervals, which will be discussed
+further in the Results section.} 
+This interval 
 requires
@@
 \subsection*{Design}
-We designed a simulation study to compare the performance of the different block 
-bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
+
+\eds{We compared the performance of the different block bootstrap CI methods 
+under two marginal distributions: normal and exponential.}
+
+\paragraph{Normal Marginal Distribution}
+%We designed a simulation study to compare the performance of the different block 
+%bootstrap CI methods. In particular, 
+We generated time series $X_t$ from a 1st 
 order autoregressive (AR(1)) process:
@@
 
+\paragraph{Exponential Marginal Distribution}
 Additionally, we evaluated the performance of block bootstrap when used to 
@@
 
+\paragraph{Normal Marginal Distribution}
 For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
@@
 
+\paragraph{Exponential Marginal Distribution}
 For an exponential marginal distribution, the empirical coverage rates for 

### 2024-01-02 Manuscript/reply.tex
initial feedback

@@
 
+\eds{Also added comment in the Recentered Percentile CI paragraph in the 
+BLOCK BOOTSTRAP CIS section. Please check and add a comment here if you like it.}
+
 After discussion of the flaws of percentile, BC, and BCA CIs at the end of the
@@
 
-The text from the Appendix has been moved to the Simulation Study section.
+The text from the Appendix has been moved to the Simulation Study 
+section.
+
+\eds{I also added subsubsections (paragraphs) for the Normal and Exponential 
+Marginal Distributions under Design and Results subsections.
+Is it possible to put to make the [Simulation Study] Design and 
+[Simulation Study] Results as two separate 
+sections instead of placing each as subsections of the Simulation Study section,
+or does the journal formatting prohibit this?  If you can change this, then the 
+Normal and Exponential Marginal subsubsections can be updated to subsections
+under the Simulation Study Design and Simulation Study Results sections.}
 
@@
 bootstrapped statistic, but we actually expect such CIs to work for different
-error structures.
+error structures. \eds{you will need to add more here.  This concerns the
+(asymptotic) distribution of the statistics, not the underlying error 
+structure.}
 
@@
 
-This terminology was used because, \citet{efron1993introduction} refers to such 
-CIs as 
+Thank you for the comment.  This terminology was used because 
+\citet{efron1993introduction} refers to such CIs as 
 "confidence intervals based on 
@@
 
-We have added this comment to the discussion:
+We agree. We have added this comment to the discussion:
 
@@
 
+\eds{I don't think this answers the question.  The reviewer is saying that 0.95 
+is close to the boundary of 1, so the undercoverage observed intervals
+(especially when phi -0.4) may be due, at least in part, to the flaws 
+of the asymptotic Wald interval you are using. 
+\@ Jun: do you think he should try exact Clopper-Pearson
+intervals for at least a few cases of undercoverage to verify it is not the Wald
+interval that is causing the undercoverage, then comment on this in at least the
+reply (and possibly also in the main paper)?}
+
 \begin{comment}
@@
 y-axis without hurting the visualization for the other rows. Below is an 
-example:
+example:  \eds{refer to the Figure label, and avoid using `below' and `above'
+terminology with latex because the figures are not always positioned as we may
+have intended.}
 
@@
 
-The original sentence has been replaced with:
+Thank you for pointing this out. The original sentence has been replaced 
+with:
 
@@
 
+\eds{I only saw this citation in the abstract, not the discussion.  
+Please remove this citation from the abstract and place in the discussion 
+section where the sentence in question appears. In general,
+try to avoid placing any citations in the abstract.}
+
 \begin{comment}
@@
 the changed Results subsection below:
+
+\eds{\@ Jun: what do you think about putting the $l = \lceil 2n^{1/3} \rceil$
+results in the Appendix, but keeping the conclusions regarding how the 
+$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$ simulations differ
+in the main text?}
 
@@
 
-We have included this comment in the Design subsection:
+Thank you for the comment. We have now included this comment in the Design 
+subsection:
 
@@
 
-These intervals are discussed in \citep{efron1993introduction}. A citation
-is now provided in the last paragraph.
+We apologize for the omission. These intervals are discussed in 
+\citep{efron1993introduction}. A citation is now provided in the last paragraph.
 
@@
 
-We have included this discussion of problems with block bootstrap in the
-introduction:
+Thank you for the comment. We have included this discussion of problems 
+with block bootstrap in the introduction:
 
@@
 by the user of the method.
-Even when using the appropriate settings, as noted by
+Even when using the appropriate settings, 
 \citet{buhlmann2002bootstraps} notes some general drawbacks of block 
@@
 series and categorical processes.
+
+\eds{If we include all these drawbacks in the intro, we need to also provide 
+some good features of block bootstrap as well, otherwise, why do we care about 
+their CI performance?}
 

### 2024-01-03 Manuscript/manuscript.tex
Addressed comments

@@
 should provide valid confidence intervals as the length of the time series goes
-to infinity. \citep{calhoun2018} In practice, however, it is necessary to know 
+to infinity. In practice, however, it is necessary to know 
 how large of a finite 
@@
 Even when using the appropriate settings, as noted by
-\citet{buhlmann2002bootstraps} notes some general drawbacks of block 
+\citet{buhlmann2002bootstraps} observes some general drawbacks of block 
 bootstrap --- with respect to how reasonably it imitates the data-generating 
@@
 time series, it can be outperformed by other bootstrap schemes for linear time
-series and categorical processes.
+series and categorical processes. Still, \citet{buhlmann2002bootstraps}
+emphasizes that a significant advantage of block bootstrap is its simplicity.
+To be more specific, the resampling step of block bootstrap is not 
+computationally more difficult than the resampling step of basic bootstrap.
+Furthermore, block bootstrap performs better than local bootstrap in terms of
+mimicking dependence structures.
+
 \eds{If we include all these drawbacks here, we need to also provide some good 
@@
 performance?}
+\mc{addressed}
 
@@
 variation in the bootstrap estimates to construct the error bound. 
-\eds{The motivation behind proposing such an interval was based on the 
+The motivation behind proposing such an interval was based on the 
 simulation performance of the BC and BCA intervals, which will be discussed
-further in the Results section.} 
+further in the Results section. 
 This interval 
@@
 
-\section*{simulation study}
-\label{sec:simu}
+\section*{simulation design}
+\label{sec:simdes}
 
-\subsection*{Design}
+%\subsection*{Design}
 
@@
 
-\paragraph{Normal Marginal Distribution}
+\subsection*{Normal Marginal Distribution}
 %We designed a simulation study to compare the performance of the different block 
@@
 
-\paragraph{Exponential Marginal Distribution}
+\subsection*{Exponential Marginal Distribution}
 Additionally, we evaluated the performance of block bootstrap when used to 
@@
 marginal distributions.
+
+It is important to note that we expect the CIs that are based on bootstrap 
+"tables" to depend on the 
+asymptotic distribution of the statistics, but we expect such CIs to 
+have similar performance for different error structures. For example, under the 
+Central
+Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
+approximately 
+normal for both marginal normal distributions and marginal exponential 
+distributions. Therefore, we do not expect CIs that are not based on bootstrap
+"tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
+non-normal error structures.
 
@@
 
-\subsection*{Results}
+\section*{simulation results}
+\label{sec:simres}
+
+%\subsection*{Results}
 
@@
 
-\paragraph{Normal Marginal Distribution}
+\subsection*{Normal Marginal Distribution}
 For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
@@
 
-\paragraph{Exponential Marginal Distribution}
+\subsection*{Exponential Marginal Distribution}
 For an exponential marginal distribution, the empirical coverage rates for 
@@
 parameter of a time series at the nominal level given an infinitely large 
-sample, so the goal for this study was to find the smallest finite sample length 
+sample, \citep{calhoun2018} so the goal for this study was to find the smallest 
+finite sample length 
 $n$ of a time series in order for the block bootstrap procedure to recover its 

### 2024-01-03 Manuscript/reply.tex
Addressed comments

@@
 BLOCK BOOTSTRAP CIS section. Please check and add a comment here if you like it.}
+\mc{looks good}
+
+We have added this comment to the Recentered Percentile CI paragraph:
+The motivation behind proposing such an interval was based on the 
+simulation performance of the BC and BCA intervals, which will be discussed
+further in the Results section.
 
@@
 under the Simulation Study Design and Simulation Study Results sections.}  
+\mc{addressed}
 
@@
 
-The formula for the "parametric" CIs concerns the distribution of the 
-bootstrapped statistic, but we actually expect such CIs to work for different
-error structures. \eds{you will need to add more here.  This concerns the
+We have included this comment in the Exponential Marginal Distribution 
+subsection of the Design section:
+
+It is important to note that we expect the CIs that are based on bootstrap 
+"tables" to depend on the 
+asymptotic distribution of the statistics, but we expect such CIs to 
+have similar performance for different error structures. For example, under the 
+Central
+Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
+approximately 
+normal for both marginal normal distributions and marginal exponential 
+distributions. Therefore, we do not expect CIs that are not based on bootstrap
+"tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
+non-normal error structures.
+\eds{you will need to add more here.  This concerns the
 (asymptotic) distribution of the statistics, not the underlying error 
 structure.}
+\mc{I changed it a bit... I'm not sure what to say for circumstances in which
+“non-parametric” CI 
+formulas would work better}
 
@@
 the 
-y-axis without hurting the visualization for the other rows. Below is an 
+y-axis without hurting the visualization for the other rows. 
+Figure~\ref{fig:alt_phi1} is an 
 example:  \eds{refer to the Figure label, and avoid using `below' and `above'
@@
 have intended.}
+\mc{addressed}
 
@@
 try to avoid placing any citations in the abstract.}
+\mc{addressed, sorry silly mistake}
 
@@
 by the user of the method.
-Even when using the appropriate settings, 
-\citet{buhlmann2002bootstraps} notes some general drawbacks of block 
+Even when using the appropriate settings, as noted by
+\citet{buhlmann2002bootstraps} observes some general drawbacks of block 
 bootstrap --- with respect to how reasonably it imitates the data-generating 
@@
 time series, it can be outperformed by other bootstrap schemes for linear time
-series and categorical processes.
+series and categorical processes. Still, \citet{buhlmann2002bootstraps}
+emphasizes that a significant advantage of block bootstrap is its simplicity.
+To be more specific, the resampling step of block bootstrap is not 
+computationally more difficult than the resampling step of basic bootstrap.
+Furthermore, block bootstrap performs better than local bootstrap in terms of
+mimicking dependence structures.
 
@@
 their CI performance?}
+\mc{addressed}
 

### 2024-01-04 Manuscript/reply.tex
Clopper Pearson Normal Mu

@@
 The text from the Appendix has been moved to the Simulation Study 
-section.
+section. The second reviewer suggested block size as an additional experimental
+factor, so the paragraphs for normal and exponential error structures have
+been adjusted accordingly.
 
@@
 
-If all values in the interval are below 0.95, the results would suggest 
+Because it is unlikely for the coverage to 
+exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
+coverage rate 
+(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
+is included in the interval, the block bootstrap method is likely performing 
+well. If all values in the interval are below 0.95, the results would suggest 
 that the method either is providing inaccurate estimation, is underestimating 
@@
 reply (and possibly also in the main paper)?}
+\mc{plot_norm_mu_1_cup.pdf (exact Clopper-Pearson) seems to have about the same 
+widths for high 
+proportions
+(especially for phi = -0.4) as plot_norm_mu_1.pdf (Wald-Type)}
 

### 2024-01-04 Code/norm_processing.R

@@ -11,10 +11,11 @@ grouped_matrices <- split(list_of_matrices, names(list_of_matrices))
 combined_matrices <- lapply(grouped_matrices, function(x) {
   Reduce(cbind, x)
 })
-df <- data.frame(phi = numeric(), n = numeric(), blksize = numeric(), 
+df <- data.frame(phi = numeric(), n = numeric(), blksize = numeric(),
                  CI = character(), 
                  target = character(), cov = numeric(),
-                 LB = numeric(), UB = numeric())
+                 LB = numeric(), UB = numeric(), CP_LB = numeric(), 
+                 CP_UB = numeric())
 for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
@@ -26,9 +27,13 @@ for(i in names(combined_matrices)) {
   target <- rep(parameters, length(cov) / length(parameters))
   LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
   UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
+  CP_LB <- 
+    sapply(cov, function(i) exactci(i*nrep, nrep, .95)$conf.int[1])
+  CP_UB <- 
+    sapply(cov, function(i) exactci(i*nrep, nrep, .95)$conf.int[2])
   new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), 
                          blksize = rep(blksize, length(cov)), CI, target, cov, 
-                         LB, UB)
+                         LB, UB, CP_LB, CP_UB)
   df <- rbind(df, new_rows)
 }
 

### 2024-01-04 Code/plots.R

@@ -63,3 +63,33 @@ graph_bts(t, width, exp_sigma %>% filter(blksize == ceiling(2*n^(1/3))))
 t <- 'exp_phi_2'
 width <- .2
 graph_bts(t, width, exp_phi %>% filter(blksize == ceiling(2*n^(1/3))))
+
+# Exact Clopper-Pearson CI
+
+t <- 'norm_mu_1_cp'
+width <- .2
+data <- norm_mu %>% filter(blksize == ceiling(n^(1/3)))
+trans = 'identity'
+level = .95
+
+font_add_google("EB Garamond")
+#  windows()
+
+showtext_auto()
+
+data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
+                  labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Recentered'))
+
+ggplot(data, aes(x = n, y = cov)) +
+  geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
+  geom_line(size = .2) +
+  geom_errorbar(aes(ymin=CP_LB, ymax = CP_UB), colour="black", width = width, size = .2) +
+  facet_grid(factor(CI) ~ factor(phi), scales = 'free') +
+  labs(x = 'Sample Size', y = 'Coverage Rate') +
+  scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
+          element_text(family = "EB Garamond", size = 10),
+        strip.text.y = element_text(angle = 270, hjust = 1)) +
+  scale_y_continuous(trans=trans)
+ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10,
+       height = 5.8)

### 2024-01-04 Manuscript/reply.tex
fixed compiling error caused by underscores

@@
 reply (and possibly also in the main paper)?}
-\mc{plot_norm_mu_1_cup.pdf (exact Clopper-Pearson) seems to have about the same 
+\mc{plot\_norm\_mu\_1\_cup.pdf (exact Clopper-Pearson) seems to have about the same 
 widths for high 
 proportions
-(especially for phi = -0.4) as plot_norm_mu_1.pdf (Wald-Type)}
+(especially for phi = -0.4) as {plot\_norm\_mu\_1.pdf} (Wald-Type)}
 

### 2024-01-05 Manuscript/manuscript.tex
Create Block Size Appendix

@@
 and we tried both $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$,
-keeping the order of the block size constant but varying the coefficient. 
+keeping the order of the block size constant but varying the coefficient. The
+results for $l = \lceil 2n^{1/3} \rceil$ are included in the Appendix.
 For each replicate, we constructed 
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu2}
-\end{figure}
-
-\begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
-    marginal standard normal distribution with AR 
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:sigma2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard normal distribution with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi2}
-\end{figure}
-
 \subsection*{Normal Marginal Distribution}
@@
 
-Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
-coverage 
-rates of $\mu$ appear to be lower when
-using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
-would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
-$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
-$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
-by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
-for smaller values of $n$.
-
-\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
-\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
-slightly lower
-especially for negative values of $\phi$, although Student's $t$ CIs are again
-not as influenced by this change in $l$. A larger sample size seems necessary
-when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.
-
-As shown in \textbf{Figure~\ref{fig:phi2}},
-recentered percentile and standard CIs have slightly lower coverage rates when
-estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
-Although it is still a problem, the coverage deterioration appears to be less 
-dramatic for BCA,
-BC, and percentile CIs.
-
-Aside from these differences, the overall changes
-in performance when other experimental factors are changed are the same.
-
 \begin{figure}[tbp]
@@
 choice of method is of utmost importance as to avoid coverage deterioration. 
-In addition, choice of block size is another important parameter, as
-$l = \lceil n^{1/3} \rceil$ results in better coverage than 
-$l = \lceil 2n^{1/3} \rceil$.
 Coverage rates are acceptable at smaller sample 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_mu_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a stationary series with marginal unit exponential
-    distribution obtained by transforming an AR(1) process with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_mu2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
-    of a stationary series with 
-    marginal unit exponential distribution obtained by transforming an AR(1) process
-    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_sigma2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_phi_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient of a stationary series
-    with marginal unit exponential distribution obtained by transforming an AR(1) 
-    process with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
   \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
@@
 methods. Performance continues to be more favorable when temporal dependence is
-negative rather than positive. Altering the block size results in the same 
-changes in performance of different CIs. Of particular significance, the 
+negative rather than positive. Of particular significance, the 
 percentile, BC,
@@
 
+\section*{Appendix: Simulation Study with $l = \lceil 2n^{1/3} \rceil$}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu2}
+\end{figure}
+
+\begin{figure}[bp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
+    marginal standard normal distribution with AR 
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:sigma2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard normal distribution with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:phi2}
+\end{figure}
+
+Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
+coverage 
+rates of $\mu$ appear to be lower when
+using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
+would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
+$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
+$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
+by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
+for smaller values of $n$.
+
+\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
+\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
+slightly lower
+especially for negative values of $\phi$, although Student's $t$ CIs are again
+not as influenced by this change in $l$. A larger sample size seems necessary
+when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.
+
+As shown in \textbf{Figure~\ref{fig:phi2}},
+recentered percentile and standard CIs have slightly lower coverage rates when
+estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
+Although it is still a problem, the coverage deterioration appears to be less 
+dramatic for BCA,
+BC, and percentile CIs.
+
+Aside from these differences, the overall changes
+in performance when other experimental factors are changed are the same as
+when $l = \lceil n^{1/3} \rceil$.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_mu_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of a stationary series with marginal unit exponential
+    distribution obtained by transforming an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_mu2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
+    of a stationary series with 
+    marginal unit exponential distribution obtained by transforming an AR(1) process
+    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_sigma2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_phi_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient of a stationary series
+    with marginal unit exponential distribution obtained by transforming an AR(1) 
+    process with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_phi2}
+\end{figure}
+
+For a stationary series with a marginal exponential distribution, altering the 
+block size results in the same 
+changes in performance of different CIs.
+
 \bibliographystyle{unsrtnat}

### 2024-01-05 Manuscript/reply.tex
Create Block Size Appendix

@@
 $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
-the changed Results subsection below:
+the Appendix detailing these results below (the 
+figures for 
+$l = \lceil n^{1/3} \rceil$ are included for comparison):
 
@@
 in the main text?}
+\mc{I moved everything to the Appendix. if you want to change it back you can 
+revert the commit}
+
+\section*{Appendix: Simulation Study with $l = \lceil 2n^{1/3} \rceil$}
 
@@
 \end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu2}
-\end{figure}
-
-\begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
-    marginal standard normal distribution with AR 
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:sigma2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard normal distribution with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi2}
-\end{figure}
-
-For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
-that all methods eventually approach correct coverage of $\mu$ as sample size 
-increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
-correct coverage, except for samples with strong negative dependence, in which 
-case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
-a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
-CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
-other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
-recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
-nominal level for all combinations of $n$ and $\phi$. All methods seem to 
-require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
-negative dependence versus positive dependence. For example, BC CIs recover 
-$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
-$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
-stronger, holding everything else equal, coverage increases, which lead to the 
-Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
-stronger, holding everything else equal, coverage decreases, and a larger sample 
-is necessary to recover~$\mu$.  A possible explanation for this is that if a 
-stationary series has a positive 
-autocorrelation, the effective sample
-size is decreased, whereas is a series has a negative autocorrelation, the
-effective sample size is increased. Additionally, this seems to have a 
-greater effect on the the estimation of the location parameter versus that
-of the scale parameter or temporal dependence parameter.
-
-For estimating the standard deviation parameter~$\sigma_x$,
-\textbf{Figure~\ref{fig:sigma1}} suggests that every method can reach nominal 
-coverage of $\sigma_x$ if the sample is large enough, but for a given $n$ and 
-$\phi$, coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general.
-Like $\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample 
-sizes when compared to other methods. Unlike $\mu$, there is no over-coverage 
-issue for $\sigma_x$ when $\phi = -0.4$. Standard normal, percentile, BC, BCA, and 
-recentered percentile CIs again have similar performance. All methods seem to 
-have slightly higher coverage of $\sigma_x$ when $\phi$ is negative versus when 
-$\phi$ is positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as 
-the strength of the temporal dependence increases.
-
-For estimating the autocorrelation parameter~$\phi$, 
-\textbf{Figure~\ref{fig:phi1}} suggests that while standard normal, Student's $t$, and 
-recentered percentile CIs do approach correct coverage as sample size increases, 
-percentile, BC, and BCA CIs deteriorate as sample size increases, especially as 
-the strength of the temporal dependence increases. Because of this, only 
-standard normal, Student's $t$, and recentered percentile CIs should be considered as 
-effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
-again can achieve correct coverage with smaller sample sizes when compared to 
-standard and recentered percentile CIs which perform similarly. Student's $t$ 
-CIs can can recover $\phi$ at the nominal level for $n \geq 100$ when the 
-sample's temporal dependence is as strong as 0.4. Coverage appears to be higher 
-for all methods when the dependence is negative rather than positive. Whether or 
-not the dependence is negative or positive, coverage of $\phi$ seems to increase 
-slightly as the absolute value increases for standard normal, Student's $t$, and 
-recentered percentile CIs. For the values of $\phi$ observed, there are no 
-examples of over-coverage for standard normal, Student's $t$, BC, BCA, or recentered 
-percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
-sample sizes when $\phi = -0.2$ and when $\phi = 0$, indicating again that they 
-should not be used.
-
-Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
-coverage 
-rates of $\mu$ appear to be lower when
-using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
-would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
-$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
-$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
-by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
-for smaller values of $n$.
-
-\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
-\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
-slightly lower
-especially for negative values of $\phi$, although Student's $t$ CIs are again
-not as influenced by this change in $l$. A larger sample size seems necessary
-when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.
-
-As shown in \textbf{Figure~\ref{fig:phi2}},
-recentered percentile and standard CIs have slightly lower coverage rates when
-estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
-Although it is still a problem, the coverage deterioration appears to be less 
-dramatic for BCA,
-BC, and percentile CIs.
-
-Aside from these differences, the overall changes
-in performance when other experimental factors are changed are the same.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
-  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
-    samples of $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$)
-    for an AR(1) process with $\phi = 0.4$. For 
-    each replicate, the lower and upper bounds of the CIs are displayed, as well 
-    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
-  \label{fig:npi}
-\end{figure}
-
-The outcomes of the $\phi$ estimation raise a natural question about the 
-lackluster performance of certain methodologies. To delve into this inquiry, a
-set of 50 CIs was generated for each of the percentile, BC, and recentered
-percentile  approaches for samples of $n \in \{800, 1600\}$. Illustrated in 
-\textbf{Figure~\ref{fig:npi}}, it becomes evident that the percentile-based CIs 
-exhibit a notable bias, predominantly manifesting as a substantial 
-underestimation of $\phi$ with point estimator $\bar\theta_n^B$, that is, the 
-average of $B$ bootstrap point estimates. As the sample size increases from 800 
-to 1600, this bias does not vanish while the uncertainty reduces, which explains 
-why the coverage rates deteriorate. The bias in $\bar\theta_n^B$ also appears to 
-invalidate the bias-correction in the BC bootstrap, leading to the poor 
-performance of the BC intervals. The BCA intervals have the same problem as the 
-BC intervals in the bias-correction step. The root of the issue appears to be 
-that the autocorrelation in the block bootstrap samples is somehow smaller 
-compared to that in the original sample. On the other hand, the original point 
-estimator $\hat\theta_n$ is asymptotically unbiased. Since the width is based on 
-the uncertainty in the bootstrap point estimates $\hat\theta_n^{(b)}$, 
-$b = 1, \ldots, B$, the percentile CIs recentered at the original point estimate
-$\hat\theta_n$ provide desired coverage.
-
-To summarize, the performance of the CIs depends on the target parameter. When
-estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
-perform noticeably better than the others.
-However, when estimating $\phi$, the 
-choice of method is of utmost importance as to avoid coverage deterioration. 
-In addition, choice of block size is another important parameter, as
-$l = \lceil n^{1/3} \rceil$ results in better coverage than 
-$l = \lceil 2n^{1/3} \rceil$.
-Coverage rates are acceptable at smaller sample 
-sizes when phi is positive versus when phi is negative. In
-other words, a larger sample size is generally required to estimate a 
-parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the 
-same magnitude. In order 
-to know if coverage will increase as the strength of the temporal dependence 
-increases, one need to know what the parameter of interest is, and in the case 
-of $\mu$, the direction of the serial dependence. The BC approach does not seem 
-to be correcting bias appropriately when estimating $\phi$. Like the percentile 
-method, the recentered percentile method uses the spread from the bootstrap to 
-construct the width of the CI. However, the recentered approach, does not 
-correct from the original point estimate $\hat\theta_n$.
 
@@
   \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu2}
+\end{figure}
+
+\begin{figure}[bp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
+    marginal standard normal distribution with AR 
+    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:sigma2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard normal distribution with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:phi2}
+\end{figure}
+
+Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
+coverage 
+rates of $\mu$ appear to be lower when
+using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
+would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
+$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
+$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
+by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
+for smaller values of $n$.
+
+\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
+\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
+slightly lower
+especially for negative values of $\phi$, although Student's $t$ CIs are again
+not as influenced by this change in $l$. A larger sample size seems necessary
+when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.
+
+As shown in \textbf{Figure~\ref{fig:phi2}},
+recentered percentile and standard CIs have slightly lower coverage rates when
+estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
+Although it is still a problem, the coverage deterioration appears to be less 
+dramatic for BCA,
+BC, and percentile CIs.
+
+Aside from these differences, the overall changes
+in performance when other experimental factors are changed are the same as
+when $l = \lceil n^{1/3} \rceil$.
+
+\begin{figure}[tbp]
+  \centering
   \includegraphics[width=\textwidth]{figures/plot_exp_mu_2}
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
-  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
-    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
-    of a stationary series with marginal exponential distribution
-    obtained by transforming an AR(1) process with $\phi = 0.4$ with
-    sample size $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$). For 
-    each replicate, the lower and upper bounds of the CIs are displayed, as well 
-    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
-  \label{fig:eri}
-\end{figure}
-
-For an exponential marginal distribution, the empirical coverage rates for 
-$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
-%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
-and 
-the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
-%it, we are not using $\phi$ in reference to the temporal dependence of the 
-%exponentially distributed series?}, 
-as well as 95\%
-confidence intervals of the real coverage are displayed in 
-\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi2}}. 
-Additionally, a set of 50 CIs are displayed for each of the percentile, 
-BC, and recentered percentile approaches for exponentially distributed
-samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
-($\phi = 0.4$) in Figure~\ref{fig:eri}.
-
-It appears that a greater sample size is generally required for the bootstrap
-CIs to cover the mean and standard deviation parameters in the exponential
-margin case than in the normal margin case. However, the trends and patterns
-discussed in the main text regarding the performance of various methods and
-diverse parameters remain consistent. For example, Student's $t$ confidence
-intervals still exhibit higher coverage rates in comparison to alternative
-methods. Performance continues to be more favorable when temporal dependence is
-negative rather than positive. Altering the block size results in the same 
-changes in performance of different CIs. Of particular significance, the 
-percentile, BC,
-and BCA confidence intervals still display a decline in coverage accuracy for
-the lag-1 autocorrelation coefficient as sample size increases as demonstrated
-in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
-manifesting the same bias issue. On the other hand, the recentered percentile
-confidence interval continues to be effective in estimating the temporal 
-dependence %\mc{replaced $\phi$ again here} 
-due to the
-inherent unbiasedness of the original point estimator. In sum, the findings for
-series that are marginally exponentially distributed closely mirror those
-attained for series that are marginally normally distributed.
+For a stationary series with a marginal exponential distribution, altering the 
+block size results in the same 
+changes in performance of different CIs.
 

### 2024-01-05 Manuscript/manuscript.tex
Clopper-Pearson in reply and Manuscript

@@
 interval has poor coverage as the proportion approaches 0 or 1.
-\textbf{Figures~\ref{fig:mu1}--\ref{fig:phi2}} 
+\textbf{Figures~\ref{fig:mu1}--\ref{fig:phi1}} 
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a standard normal marginal distribution, generated using the 
+real coverage for a standard normal marginal distribution using block bootstrap
+with $l = \lceil n^{1/3} \rceil$, generated using the 
 R \textsl{ggplot2} package.\citep{ggplot2}
@@
 autocorrelation coefficients are $\{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.
+
+\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi1}} 
+summarizes the empirical coverage rates and the 95\% confidence intervals of the 
+real coverage for a exponential marginal distribution using block bootstrap
+with $l = \lceil n^{1/3} \rceil$.
 
@@
 
+CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
+as stated before, the Wald-type CI is known to have undercoverage in such 
+situations.
+Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
+Clopper-Pearson intervals to verify that it is the choice of Wald interval
+does not cause undercoverage of the coverage rate. Indeed, the widths of the
+exact proportion CIs do not seem to differ heavily from the Wald-type CIs.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1_cp}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs 
+    for
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
+    error bars represent 95\% exact CIs of the real coverage rates.}
+  \label{fig:norm_mu_1_cp}
+\end{figure}
+
 For estimating the standard deviation parameter~$\sigma_x$,
@@
 
+\textbf{Figures~\ref{fig:mu2}--\ref{fig:phi2}} 
+summarizes the empirical coverage rates and the 95\% confidence intervals of the 
+real coverage for a standard normal marginal distribution using block bootstrap
+with $l = \lceil 2n^{1/3} \rceil$.
+
 \begin{figure}[tbp]
@@
 
+\textbf{Figures~\ref{fig:exp_mu2}--\ref{fig:exp_phi2}} 
+summarizes the empirical coverage rates and the 95\% confidence intervals of the 
+real coverage for a exponential marginal distribution using block bootstrap
+with $l = \lceil 2n^{1/3} \rceil$.
+
 \begin{figure}[tbp]

### 2024-01-05 Manuscript/reply.tex
Clopper-Pearson in reply and Manuscript

@@
 
+We have also included these comments and a figure in the Results section which 
+uses exact 
+Clopper-Pearson CIs:
+
+CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
+as stated before, the Wald-type CI is known to have undercoverage in such 
+situations.
+Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
+Clopper-Pearson intervals to verify that it is the choice of Wald interval
+does not cause undercoverage of the coverage rate. Indeed, the widths of the
+exact proportion CIs do not seem to differ heavily from the Wald-type CIs.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1_cp}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs 
+    for
+    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
+    error bars represent 95\% exact CIs of the real coverage rates.}
+  \label{fig:norm_mu_1_cp}
+\end{figure}
+
 \begin{comment}
@@
 
-\section*{Appendix: Simulation Study with $l = \lceil 2n^{1/3} \rceil$}
-
 \begin{figure}[tbp]
@@
 
+\section*{Appendix: Simulation Study with $l = \lceil 2n^{1/3} \rceil$}
+
+\textbf{Figures~\ref{fig:mu2}--\ref{fig:phi2}} 
+summarizes the empirical coverage rates and the 95\% confidence intervals of the 
+real coverage for a standard normal marginal distribution using block bootstrap
+with $l = \lceil 2n^{1/3} \rceil$.
+
 \begin{figure}[tbp]
@@
 when $l = \lceil n^{1/3} \rceil$.
+
+\textbf{Figures~\ref{fig:exp_mu2}--\ref{fig:exp_phi2}} 
+summarizes the empirical coverage rates and the 95\% confidence intervals of the 
+real coverage for a exponential marginal distribution using block bootstrap
+with $l = \lceil 2n^{1/3} \rceil$.
 

### 2024-01-05 Code/exp_processing.R

@@ -15,7 +15,8 @@ combined_matrices <- lapply(grouped_matrices, function(x) {
 df <- data.frame(rho = numeric(), n = numeric(), blksize = numeric(),
                  CI = character(), 
                  target = character(), cov = numeric(),
-                 LB = numeric(), UB = numeric())
+                 LB = numeric(), UB = numeric(), CP_LB = numeric(), 
+                 CP_UB = numeric())
 for(i in names(combined_matrices)) {
   phi <- as.numeric(strsplit(i, '_')[[1]][1])
   n <- as.integer(strsplit(i, '_')[[1]][2])
@@ -35,9 +36,13 @@ for(i in names(combined_matrices)) {
   target <- rep(parameters, length(cov) / length(parameters))
   LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
   UB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])
+  CP_LB <- 
+    sapply(cov, function(i) exactci(i*nrep, nrep, .95)$conf.int[1])
+  CP_UB <- 
+    sapply(cov, function(i) exactci(i*nrep, nrep, .95)$conf.int[2])
   new_rows <- data.frame(phi = rep(phi, length(cov)), n = rep(n, length(cov)), 
                          blksize = rep(blksize, length(cov)), CI, target, cov, 
-                         LB, UB)
+                         LB, UB, CP_LB, CP_UB)
   df <- rbind(df, new_rows)
 }
 

### 2024-01-05 Code/plots.R

@@ -93,3 +93,32 @@ ggplot(data, aes(x = n, y = cov)) +
   scale_y_continuous(trans=trans)
 ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10,
        height = 5.8)
+
+
+t <- 'exp_phi_1_cp'
+width <- .2
+data <- exp_phi %>% filter(blksize == ceiling(n^(1/3)))
+trans = 'identity'
+level = .95
+
+font_add_google("EB Garamond")
+#  windows()
+
+showtext_auto()
+
+data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
+                  labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Recentered'))
+
+ggplot(data, aes(x = n, y = cov)) +
+  geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
+  geom_line(size = .2) +
+  geom_errorbar(aes(ymin=CP_LB, ymax = CP_UB), colour="black", width = width, size = .2) +
+  facet_grid(factor(CI) ~ factor(phi), scales = 'free') +
+  labs(x = 'Sample Size', y = 'Coverage Rate') +
+  scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
+          element_text(family = "EB Garamond", size = 10),
+        strip.text.y = element_text(angle = 270, hjust = 1)) +
+  scale_y_continuous(trans=trans)
+ggsave(paste('../Manuscript/figures/plot_', t, '.pdf', sep = ''), width = 10,
+       height = 5.8)

### 2024-01-05 Manuscript/reply.tex
comments on the reply

@@
 % \jy{Spell check!}
+
+\jy{For each comment, response first and at the end of each response,
+  state what was done in the text. I usually don't quote text because
+  if you make changes, you need to synchronize at two locations. Learn
+  from the first version (which is a real reply letter for a paper).}
 
@@
 
-Below is an example of what this would look like. We find that it is a little
+\jy{never use ``below'' because tables/figures are floats.}
+
+Figure~\ref{fig:mu} is an example of what this would look like. We find that it is a little
 cluttered to make comparisons, so we will use the original format.
+
+\jy{1. Reduce the heights; put legend at the bottom; put the
+  confidence intervals side by side for each sample size (see this
+  paper for example plot:
+  \url{https://iopscience.iop.org/article/10.1088/1748-9326/ac14ee/meta}.}
 
@@
 
+\jy{Left quote: `` (below the ESC key)}
+
 \begin{comment}
@@
 
-Because of the style constraints for AJUR, we have removed page numbers in 
+Because of the bib style constraints for AJUR, we have removed page numbers in 
 citations.
@@
 (especially for phi = -0.4) as {plot\_norm\_mu\_1.pdf} (Wald-Type)}
+\jy{I thought the CP interval is for binomial proportions. How was it
+  done here?}
 
@@
 
+\jy{No  need to duplicate the figures if they are already in the paper.}
 \begin{figure}[tbp]
@@
 $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$ simulations differ
-in the main text?}
+in the main text?} \jy{I agree. Mention the results in the text and
+refer to the appendix.}
 \mc{I moved everything to the Appendix. if you want to change it back you can 

### 2024-01-06 Manuscript/reply.tex
Responded to Few Comments have to Address others
Addressed comment about plot

@@
 
-Figure~\ref{fig:mu} is an example of what this would look like. We find that it is a little
+Figure~\ref{fig:mu} is an example of what this would look like. We find that it 
+is a little
 cluttered to make comparisons, so we will use the original format.
@@
   \url{https://iopscience.iop.org/article/10.1088/1748-9326/ac14ee/meta}.}
+\mc{addressed}
 
@@
   done here?}
+\mc{this is the interval for the coverage rate, which is a proportion}
 
@@
 
-CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
-as stated before, the Wald-type CI is known to have undercoverage in such 
-situations.
-Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
-Clopper-Pearson intervals to verify that it is the choice of Wald interval
-does not cause undercoverage of the coverage rate. Indeed, the widths of the
-exact proportion CIs do not seem to differ heavily from the Wald-type CIs.
+%CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
+%as stated before, the Wald-type CI is known to have undercoverage in such 
+%situations.
+%Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
+%Clopper-Pearson intervals to verify that it is the choice of Wald interval
+%does not cause undercoverage of the coverage rate. Indeed, the widths of the
+%exact proportion CIs do not seem to differ heavily from the Wald-type CIs.
 
 \jy{No  need to duplicate the figures if they are already in the paper.}
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1_cp}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs 
-    for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
-    error bars represent 95\% exact CIs of the real coverage rates.}
-  \label{fig:norm_mu_1_cp}
-\end{figure}
+\mc{addressed}
 

### 2024-01-06 Code/functions.R

@@ -132,17 +132,19 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
   
   ggplot(data, aes(x = n, y = cov, color = CI)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
-    geom_line(size = .2) +
-    geom_errorbar(aes(ymin=LB, ymax = UB, color = CI), width = width, size = .2) +
+    geom_line(size = .2, position = position_dodge(width = 0.5)) +
+    geom_errorbar(aes(ymin=LB, ymax = UB, color = CI), width = width, size = .2,
+                  position = position_dodge(width = 0.5)) +
     facet_grid(. ~ factor(phi), scales = 'free') +
     labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
             element_text(family = "EB Garamond", size = 10),
-          strip.text.y = element_text(angle = 270, hjust = 1)) +
+          strip.text.y = element_text(angle = 270, hjust = 1),
+          legend.position = "bottom") +
     scale_y_continuous(trans=trans)
   ggsave(paste('../Manuscript/figures/alt_plot_', t, '.pdf', sep = ''), width = 10,
-         height = 5.8)
+         height = 3)
 }
 
 alt_graph_bts2 <- function(t, width, data, trans = 'identity', level = .95)

### 2024-01-06 Manuscript/manuscript.tex
Fixed Quotes and removed below

@@
 symmetric. The standard CI is classified by \citet{efron1993introduction} 
-as a confidence interval based on bootstrap "tables". Its 
+as a confidence interval based on bootstrap ``tables". Its 
 validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
@@
 Student's $t$ CI is classified by \citet{efron1993introduction} 
-as a confidence interval based on bootstrap "tables". In this case, its 
+as a confidence interval based on bootstrap ``tables". In this case, its 
 validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
@@
 It is important to note that we expect the CIs that are based on bootstrap 
-"tables" to depend on the 
+``tables" to depend on the 
 asymptotic distribution of the statistics, but we expect such CIs to 
@@
 distributions. Therefore, we do not expect CIs that are not based on bootstrap
-"tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
+``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
 non-normal error structures.
@@
 Lastly, because of its exceptional performance in comparison to the other 
-CIs that are not based on bootstrap "tables", the proposed recentered percentile 
+CIs that are not based on bootstrap ``tables", the proposed recentered percentile 
 CI would be

### 2024-01-06 Manuscript/reply.tex
Fixed Quotes and removed below

@@
 \jy{Left quote: `` (below the ESC key)}
+\mc{addressed in reply and manuscript}
 
@@
 \citet{efron1993introduction} refers to such CIs as 
-"confidence intervals based on 
-bootstrap 'tables'." We have changed these sentences as shown below:
+``confidence intervals based on 
+bootstrap `tables'." We have replaced all instances of the phrase 
+``table-based bootstrap CIs" to ``confidence intervals based on bootstrap 
+`tables'" for the sake of clarity.
 
-The standard CI is classified by \citet{efron1993introduction} 
-as a confidence interval based on bootstrap "tables".
-Like the standard normal interval, the
-Student's $t$ CI is classified by \citet{efron1993introduction} 
-as a confidence interval based on bootstrap "tables".
+%The standard CI is classified by \citet{efron1993introduction} 
+%as a confidence interval based on bootstrap ``tables".
+%Like the standard normal interval, the
+%Student's $t$ CI is classified by \citet{efron1993introduction} 
+%as a confidence interval based on bootstrap ``tables".
 
@@
 
-We modified the Design section as below:
+Thank you for pointing this out. We modified the Design section to include a 
+specification of the interval type for the coverage rate:
 
@@
 $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
-the Appendix detailing these results below (the 
-figures for 
-$l = \lceil n^{1/3} \rceil$ are included for comparison):
+an Appendix detailing these results:
 

### 2024-01-06 Manuscript/reply.tex
Removed quoted text

@@
   from the first version (which is a real reply letter for a paper).}
+\mc{addressed}
 
@@
 
-We have added this comment to the Recentered Percentile CI paragraph:
-The motivation behind proposing such an interval was based on the 
+Thank you for this suggestion. The motivation behind proposing such an interval 
+was based on the 
 simulation performance of the BC and BCA intervals, which will be discussed
-further in the Results section.
-
-After discussion of the flaws of percentile, BC, and BCA CIs at the end of the
-first paragraph of Discussion, we have included these additional comments on
-why the proposed CI performs well:
-
-The uncertainty measure from bootstrap, which is used to determine the width of
-the percentile CI, is quite consistent in comparison to that used for BC and 
-BCA CIs. However, for a percentile CI, the center seems
-to be at the wrong location but is corrected when $\hat\theta_n$ is used as the
-center. This is most likely the reason why the proposed recentered percentile CI
-perfoms so much better than percentile, BC, and BCA CIs.
+further in the Results section. This has now been stated in the Recentered
+Percentile CI pargarph.
 
@@
 \jy{never use ``below'' because tables/figures are floats.}
+\mc{addressed}
 
-Figure~\ref{fig:mu} is an example of what this would look like. We find that it 
-is a little
-cluttered to make comparisons, so we will use the original format.
-
+Thank you for this idea. We have provided Figure~\ref{fig:mu} as an 
+example of what this suggested figure
+would look like. 
 \jy{1. Reduce the heights; put legend at the bottom; put the
@@
 
+We find that this format
+is a little
+cluttered to make comparisons, so we have elected to remain with the original 
+format.
+
 \begin{comment}
@@
 
-The text from the Appendix has been moved to the Simulation Study 
-section. The second reviewer suggested block size as an additional experimental
-factor, so the paragraphs for normal and exponential error structures have
-been adjusted accordingly.
+You are correct. To remedy this, the text highlighting the simulation study with 
+an exponential marginal 
+distribution from the Appendix has been moved to the Simulation Study 
+section.
 
@@
 
-We have included this comment in the Exponential Marginal Distribution 
-subsection of the Design section:
-
-It is important to note that we expect the CIs that are based on bootstrap 
+Thank you for the comment. We expect the CIs that 
+are based on bootstrap 
 ``tables" to depend on the 
@@
 distributions. Therefore, we do not expect CIs that are not based on bootstrap
-``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
-non-normal error structures.
+``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better 
+under
+non-normal error structures. We have called attention to this in the Exponential
+Marginal Distribution subsection of the Design section.
+
 \eds{you will need to add more here.  This concerns the
@@
 
-We agree. We have added this comment to the discussion:
-
-Lastly, because of its exceptional performance in comparison to the other 
-CIs that are not based on bootstrap ``tables", the proposed recentered percentile 
-CI would be
-an interesting method to study further with different bootstrap schemes.
+We agree. We have added a comment in the Discussion underlining this CI's
+potential for future investigations.
 
@@
 Thank you for pointing this out. We modified the Design section to include a 
-specification of the interval type for the coverage rate:
-
-Because it is unlikely for the coverage to 
-exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
-coverage rate 
-(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
-is included in the interval, the block bootstrap method is likely performing 
-well. If all values in the interval are below 0.95, the results would suggest 
-that the method either is providing inaccurate estimation, is underestimating 
-the process' variability, or a combination of both. If all values in the 
-interval are above .95, the results suggest that the method is overestimating 
-the process' variability. \citet{brown2001interval} notes that the Wald-type 
-interval has poor coverage as the proportion approaches 0 or 1.
+specification of the interval type for the coverage rate, as well as an 
+acknowledgement of its flaw.
 
@@
 
-We have also included these comments and a figure in the Results section which 
+We have also included a figure in the Results section which 
 uses exact 
-Clopper-Pearson CIs:
+Clopper-Pearson CIs to verify that the choice of interval
+for the binomial proportion did not cause undercoverage in this case.
 
@@
 
-Because of the deterioration for $\phi$, we found it hard to fix the limits on 
+Thank you for the suggestion. However, because of the deterioration for $\phi$, 
+we found it hard to fix the limits on 
 the 
 y-axis without hurting the visualization for the other rows. 
-Figure~\ref{fig:alt_phi1} is an 
+Figure~\ref{fig:alt_phi1} is provided as an 
 example:  \eds{refer to the Figure label, and avoid using `below' and `above'
@@
 
-We have included this comment at the end of the paragraph on estimation of 
-$\mu$:
-
+Thank you for this comment.
 A possible explanation for this is that if a 
@@
 greater effect on the the estimation of the location parameter versus that
-of the scale parameter or temporal dependence parameter.
+of the scale parameter or temporal dependence parameter. We have included a 
+similar
+comment at the end of the paragraph on estimation of 
+$\mu$.
 
@@
 
-Thank you for pointing this out. The original sentence has been replaced 
-with:
-
-Coverage rates are acceptable at smaller sample 
-sizes when phi is positive versus when phi is negative. In
-other words, a larger sample size is generally required to estimate a 
-parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the 
-same magnitude.
+Thank you for pointing this out. The original sentence has been reworded as you
+suggested to make it more clear.
 
@@
 
-\citep{calhoun2018}
+Thank you for drawing this to our attention. A citation \citep{calhoun2018} has
+now been provided for that comment.
 
@@
 
-We have now repeated the same simulation study with block size as an 
+Thank you for the comment. We have now repeated the same simulation study with 
+block size as an 
 additional experimental factor. The optimal order of block size is 
@@
 $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
-an Appendix detailing these results:
-
-\eds{\@ Jun: what do you think about putting the $l = \lceil 2n^{1/3} \rceil$
-results in the Appendix, but keeping the conclusions regarding how the 
-$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$ simulations differ
-in the main text?} \jy{I agree. Mention the results in the text and
-refer to the appendix.}
-\mc{I moved everything to the Appendix. if you want to change it back you can 
-revert the commit}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu1}
-\end{figure}
-
-\begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
-    marginal standard normal distribution with AR 
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. The 
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:sigma1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_phi_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard normal distribution with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_mu_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a stationary series with marginal unit exponential
-    distribution obtained by transforming an AR(1) process with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_mu1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
-    of a stationary series with 
-    marginal unit exponential distribution obtained by transforming an AR(1) process
-    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_sigma1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_phi_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient of a stationary series
-    with marginal unit exponential distribution obtained by transforming an AR(1) 
-    process with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi1}
-\end{figure}
-
-\section*{Appendix: Simulation Study with $l = \lceil 2n^{1/3} \rceil$}
-
-\textbf{Figures~\ref{fig:mu2}--\ref{fig:phi2}} 
-summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a standard normal marginal distribution using block bootstrap
-with $l = \lceil 2n^{1/3} \rceil$.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu2}
-\end{figure}
-
-\begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
-    marginal standard normal distribution with AR 
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:sigma2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard normal distribution with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi2}
-\end{figure}
-
-Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
-coverage 
-rates of $\mu$ appear to be lower when
-using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
-would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
-$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
-$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
-by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
-for smaller values of $n$.
-
-\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
-\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
-slightly lower
-especially for negative values of $\phi$, although Student's $t$ CIs are again
-not as influenced by this change in $l$. A larger sample size seems necessary
-when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.
-
-As shown in \textbf{Figure~\ref{fig:phi2}},
-recentered percentile and standard CIs have slightly lower coverage rates when
-estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
-Although it is still a problem, the coverage deterioration appears to be less 
-dramatic for BCA,
-BC, and percentile CIs.
-
-Aside from these differences, the overall changes
-in performance when other experimental factors are changed are the same as
-when $l = \lceil n^{1/3} \rceil$.
-
-\textbf{Figures~\ref{fig:exp_mu2}--\ref{fig:exp_phi2}} 
-summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a exponential marginal distribution using block bootstrap
-with $l = \lceil 2n^{1/3} \rceil$.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_mu_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a stationary series with marginal unit exponential
-    distribution obtained by transforming an AR(1) process with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_mu2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
-    of a stationary series with 
-    marginal unit exponential distribution obtained by transforming an AR(1) process
-    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_sigma2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_phi_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient of a stationary series
-    with marginal unit exponential distribution obtained by transforming an AR(1) 
-    process with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi2}
-\end{figure}
-
-For a stationary series with a marginal exponential distribution, altering the 
-block size results in the same 
-changes in performance of different CIs.
+an Appendix detailing these results.
 
@@
 
-Thank you for the comment. We have now included this comment in the Design 
-subsection:
-
-We only
+Thank you for the comment. We only
 used serial dependences as strong as 0.4, because we only seek to 
@@
 increases, and how it varies depending on the sign of the autocorrelation and 
-the parameter of interest.
+the parameter of interest. This justification has been added to the Design 
+section.
 
@@
 
-Thank you for the comment. We have included this discussion of problems 
-with block bootstrap in the introduction:
-
-\citet{lahiri1999theoretical} finds that moving block bootstrap has better 
-performance than non-overlapping block bootstrap. Additionally, moving block 
-bootstrap with nonrandom
-block sizes results in lower mean-squared errors than moving block bootstrap
-with random block sizes. \citet{buhlmann1999block} notes that a drawback of 
-block bootstrap is that it heavily depends on block size, which has to be chosen
-by the user of the method.
-Even when using the appropriate settings, as noted by
-\citet{buhlmann2002bootstraps} observes some general drawbacks of block 
-bootstrap --- with respect to how reasonably it imitates the data-generating 
-process. In addition, although block bootstrap is primarily used for stationary 
-time series, it can be outperformed by other bootstrap schemes for linear time
-series and categorical processes. Still, \citet{buhlmann2002bootstraps}
-emphasizes that a significant advantage of block bootstrap is its simplicity.
-To be more specific, the resampling step of block bootstrap is not 
-computationally more difficult than the resampling step of basic bootstrap.
-Furthermore, block bootstrap performs better than local bootstrap in terms of
-mimicking dependence structures.
-
-\eds{If we include all these drawbacks in the intro, we need to also provide 
-some good features of block bootstrap as well, otherwise, why do we care about 
-their CI performance?}
-\mc{addressed}
-
-We also added this comment in the Discussion section:
-
-We discussed some
-drawbacks of block bootstrap in the introduction, which could motivate a similar
-simulation study for alternatives to block bootstrap, such 
-as AR-Sieve bootstrap, \citep{kreiss1992bootstrap} which 
-\citet{buhlmann2002bootstraps} finds to be the best for linear time series.
+Thank you for the comment. We have included a discussion of problems 
+with block bootstrap in the introduction, while also highlighting its advantages
+which motivated this investigation into their CI performance.
 

### 2024-01-06 Manuscript/reply.tex
Summary filled in

@@
 \begin{enumerate}
-\item 
-  \begin{enumerate}
-    \item 
-    \item 
-    \item 
-    \item 
-    \end{enumerate}
-\item 
-  \begin{enumerate}
-  \item 
-  \item 
-  \item 
-  \item 
-  \end{enumerate}
+\item Added clarifications of rationals for decisions regarding the experimental
+design;
+\item Reorganization of paragraphs on the Simulation Study, including moving the
+Appendix on the Exponential Marginal Distribution Study to the main text;
+\item Further discussion of the justification, advantages, and implications of
+the Recentered Percentile CI;
+\item Clarified wording and additional citations;
+\item More detailed xxamination of limitations of study and block bootstrap 
+in general
+\item An Appendix on simulation study using block size 
+$l = \lceil 2n^{1/3} \rceil$
 \end{enumerate}

### 2024-01-07 Manuscript/reply.tex
comments on replies

@@
 
-% \jy{Spell check!}
+We thank the editor and the AE for the opportunity to revise the manuscript. and
+the two referees for their constructive comments.
+We are indebted to the reviewers for pointing out these vital discussion areas,
+which have not only enriched the current paper but also charted a clear course
+for our subsequent research endeavors.
 
-\jy{For each comment, response first and at the end of each response,
-  state what was done in the text. I usually don't quote text because
-  if you make changes, you need to synchronize at two locations. Learn
-  from the first version (which is a real reply letter for a paper).}
-\mc{addressed}
+The manuscript has been
+revised accordingly with the following notable changes:
+\jy{Be selective here for ``notable''. I'd not include items like `wording
+  clarification'; your could put all the clarifications as one
+  item. Keep this list short for the reviewers to have a  
+  quick idea about the major changes (e.g., additional simulation studies).}
 
-\subsection*{Summary}
-
-We thank the editor and the AE for the opportunity to revise the manuscript and
-the two referees for their constructive comments. The manuscript has been
-revised accordingly with the following notable changes:
 \begin{enumerate}
@@
 
-Thank you for this suggestion. The motivation behind proposing such an interval 
-was based on the 
-simulation performance of the BC and BCA intervals, which will be discussed
-further in the Results section. This has now been stated in the Recentered
-Percentile CI pargarph.
+Thank you for this suggestion. The motivation behind the proposed
+recentered CI is that. for the autocorrelation parameter in the
+simulation studies, the centers of the existing CIs appeared to be a
+biased estimator of the target while the spreadness of the CIs still
+provide good uncertainty measures. This has now been added in the
+Recentered Percentile CI pargarph.
 
@@
 
-\jy{never use ``below'' because tables/figures are floats.}
-\mc{addressed}
-
 Thank you for this idea. We have provided Figure~\ref{fig:mu} as an 
@@
 would look like.
-\jy{1. Reduce the heights; put legend at the bottom; put the
-  confidence intervals side by side for each sample size (see this
-  paper for example plot:
-  \url{https://iopscience.iop.org/article/10.1088/1748-9326/ac14ee/meta}.}
-\mc{addressed}
+
+\jy{put the legend on one line.}
+
+\jy{This plot seems fine to me. Could you make it for the other
+  parameters too? Then we can make a decision. If we use this, the
+  number of figures would be greatly reduced.}
 
@@
 
-\jy{Left quote: `` (below the ESC key)}
-\mc{addressed in reply and manuscript}
-
 \begin{comment}
@@
 are based on bootstrap
+\jy{Need to explain ``table'' methods better in the manuscript.}
 ``tables" to depend on the 
@@
 \citet{efron1993introduction} refers to such CIs as
+\jy{This is still not clear. I think they mean CIs based on asymptotic
+  distributions with estimated asymptotic variances. This is in
+  contrast to percentile based CIs.}
 ``confidence intervals based on 
@@
 (especially for phi = -0.4) as {plot\_norm\_mu\_1.pdf} (Wald-Type)}
-\jy{I thought the CP interval is for binomial proportions. How was it
-  done here?}
-\mc{this is the interval for the coverage rate, which is a proportion}
+
+\jy{Are there big differences? We could report the CP CIs in the paper.}
 
@@
 
-\jy{No  need to duplicate the figures if they are already in the paper.}
-\mc{addressed}
-
 \begin{comment}
@@
 Thank you for the suggestion. However, because of the deterioration for $\phi$, 
-we found it hard to fix the limits on 
-the 
+we found it hard to fix the limits on the 
 y-axis without hurting the visualization for the other rows. 
-Figure~\ref{fig:alt_phi1} is provided as an 
-example:  \eds{refer to the Figure label, and avoid using `below' and `above'
-terminology with latex because the figures are not always positioned as we may
-have intended.}
-\mc{addressed}
+Figure~\ref{fig:alt_phi1} is provided as an example:
 
@@
 \end{figure}
+
+\jy{I'm interested in seeing the figures overlaid as in
+  Figure~\ref{fig:mu}.}
 
@@
 
-\eds{I only saw this citation in the abstract, not the discussion.  
-Please remove this citation from the abstract and place in the discussion 
-section where the sentence in question appears. In general,
-try to avoid placing any citations in the abstract.}
-\mc{addressed, sorry silly mistake}
-
 \begin{comment}
@@
 the parameter of interest. This justification has been added to the Design 
-section.
+section. \jy{Add a comment in the discussion about what'd be expected
+  with higher dependence levels.}
 
@@
 
-We are indebted to the reviewers for pointing out these vital discussion areas,
-which have not only enriched the current paper but also charted a clear course
-for our subsequent research endeavors.
-
 \bibliographystyle{chicago}

### 2024-01-08 Manuscript/reply.tex
Overlaid Plots for Phi and Sigma

@@
   quick idea about the major changes (e.g., additional simulation studies).}
+\mc{addressed}
 
 \begin{enumerate}
-\item Added clarifications of rationals for decisions regarding the experimental
-design;
+\item Added clarifications of design and more detail examination of results;
 \item Reorganization of paragraphs on the Simulation Study, including moving the
@@
 the Recentered Percentile CI;
-\item Clarified wording and additional citations;
-\item More detailed xxamination of limitations of study and block bootstrap 
-in general
 \item An Appendix on simulation study using block size 
@@
 \jy{put the legend on one line.}
+\mc{addressed}
 
@@
   number of figures would be greatly reduced.}
+\mc{addressed}
 
@@
     the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/alt_plot_norm_sigma_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\sigma$ of an AR(1) process with a marginal standard 
+    normal distribution with AR coefficient
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
+    error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:mu}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/alt_plot_norm_phi_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\phi$ of an AR(1) process with a marginal standard 
     normal distribution with AR coefficient
@@
 \jy{Are there big differences? We could report the CP CIs in the paper.}
+\mc{I included it in the paper but they do not seem too different}
 
@@
   Figure~\ref{fig:mu}.}
+\mc{addressed}
 

### 2024-01-08 Code/functions.R

@@ -142,7 +142,8 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
             element_text(family = "EB Garamond", size = 10),
           strip.text.y = element_text(angle = 270, hjust = 1),
           legend.position = "bottom") +
-    scale_y_continuous(trans=trans)
+    scale_y_continuous(trans=trans) +
+    guides(colour = guide_legend(nrow = 1))
   ggsave(paste('../Manuscript/figures/alt_plot_', t, '.pdf', sep = ''), width = 10,
          height = 3)
 }

### 2024-01-08 Code/plots.R

@@ -15,11 +15,13 @@ alt_graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(n^(1/3))))
 t <- 'norm_sigma_1'
 width <- .2
 graph_bts(t, width, norm_sigma %>% filter(blksize == ceiling(n^(1/3))))
+alt_graph_bts(t, width, norm_sigma %>% filter(blksize == ceiling(n^(1/3))))
 
 t <- 'norm_phi_1'
 width <- .2
 graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
 alt_graph_bts2(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
+alt_graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
 
 t <- 'norm_mu_2'
 width <- .2

### 2024-01-08 Manuscript/manuscript.tex
Responded to Some More Comments

@@
 symmetric. The standard CI is classified by \citet{efron1993introduction} 
-as a confidence interval based on bootstrap ``tables". Its 
+as a confidence interval based on bootstrap ``tables", which essentially means 
+it is based on an asymptotic 
+distribution with an estimated asymptotic variance (standard error). Its 
 validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
@@
 normal for both marginal normal distributions and marginal exponential 
-distributions. Therefore, we do not expect CIs that are not based on bootstrap
-``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
+distributions. Therefore, we do not expect CIs that are percentile-based
+(Percentile, BC, BCA, Recentered Percentile CI) to perform better under
 non-normal error structures.
@@
 Lastly, because of its exceptional performance in comparison to the other 
-CIs that are not based on bootstrap ``tables", the proposed recentered percentile 
+percentile-based CIs, the proposed recentered percentile 
 CI would be

### 2024-01-08 Manuscript/reply.tex
Responded to Some More Comments

@@
 \jy{Need to explain ``table'' methods better in the manuscript.}
+\mc{I gave it a try}
 ``tables" to depend on the 
@@
 normal for both marginal normal distributions and marginal exponential 
-distributions. Therefore, we do not expect CIs that are not based on bootstrap
-``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better 
+distributions. Therefore, we do not expect percentile-based CIs (Percentile, BC, BCA, Recentered Percentile CI) to perform better 
 under
@@
   contrast to percentile based CIs.}
+\mc{I tried to make it more clear in the manuscript, I used ``percentile-based"
+in the manuscript instead of CIs that are not based on tables}
 ``confidence intervals based on 
-bootstrap `tables'." We have replaced all instances of the phrase 
+bootstrap `tables'", which essentially means CIs based on asymptotic 
+distributions with estimated asymptotic variances (standard error), as opposed
+to CIs that are based on empirical percentiles.
+We have replaced all instances of the phrase 
 ``table-based bootstrap CIs" to ``confidence intervals based on bootstrap 
@@
 the parameter of interest. This justification has been added to the Design 
-section. \jy{Add a comment in the discussion about what'd be expected
+section. We have also added a comment in the discussion regarding what would
+be expected for higher dependence levels. \jy{Add a comment in the discussion about what'd be expected
   with higher dependence levels.}

### 2024-01-08 Manuscript/manuscript.tex
Responded to last comment

@@
 Student's $t$ should still be used if $\phi$ is unknown. Lastly, to estimate 
-$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Further
-investigation may be necessary to see if there are other interval corrections
+$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Although
+we have only used serial dependences as strong as 0.4, we have established the 
+trend. When estimating $\mu$, we expect coverage rates to decrease as
+$\phi$ approaches 1 - as $\phi$ approaches -1, we may observe increased 
+over-coverage. When estimating $\sigma$, we expect a larger sample size to
+be necessary as $|\phi|$ gets closer to 1. Lastly, when estimating $\phi$ for
+a marginal normal distribution, we 
+expect a larger sample size to be necessary as $|\phi|$ approaches 0. However, 
+for a marginal exponential distribution, we expect coverage rates of $\phi$ to 
+respond
+to stronger dependences similarly to coverage rates of $\mu$. Further
+investigation may be necessary to see if there are other percentile-based 
+interval corrections
 that fix the coverage deterioration problem for $\phi$.
@@
 $l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
-by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
+by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
 for smaller values of $n$.

### 2024-01-08 Manuscript/manuscript.tex
Comment about Exponential Difference

@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_mu_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a stationary series with marginal unit exponential
-    distribution obtained by transforming an AR(1) process with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_mu1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
-    of a stationary series with 
-    marginal unit exponential distribution obtained by transforming an AR(1) process
-    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_sigma1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_phi_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient of a stationary series
-    with marginal unit exponential distribution obtained by transforming an AR(1) 
-    process with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
-  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
-    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
-    of a stationary series with marginal exponential distribution
-    obtained by transforming an AR(1) process with $\phi = 0.4$ with
-    sample size $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$). For 
-    each replicate, the lower and upper bounds of the CIs are displayed, as well 
-    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
-  \label{fig:eri}
-\end{figure}
-
 \subsection*{Exponential Marginal Distribution}
@@
 confidence intervals of the real coverage are displayed in 
-\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi2}}. 
+\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi1}}. 
 Additionally, a set of 50 CIs are displayed for each of the percentile, 
@@
 
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_mu_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$ of a stationary series with marginal unit exponential
+    distribution obtained by transforming an AR(1) process with
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_mu1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
+    of a stationary series with 
+    marginal unit exponential distribution obtained by transforming an AR(1) process
+    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_sigma1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/plot_exp_phi_1}
+  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
+    the first-order autocorrelation coefficient of a stationary series
+    with marginal unit exponential distribution obtained by transforming an AR(1) 
+    process with 
+    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
+    replicates of
+    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
+    The error bars represent 95\% CIs of the real coverage rates.}
+  \label{fig:exp_phi1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
+  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
+    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
+    of a stationary series with marginal exponential distribution
+    obtained by transforming an AR(1) process with $\phi = 0.4$ with
+    sample size $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$). For 
+    each replicate, the lower and upper bounds of the CIs are displayed, as well 
+    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
+  \label{fig:eri}
+\end{figure}
+
 It appears that a greater sample size is generally required for the bootstrap
 CIs to cover the mean and standard deviation parameters in the exponential
-margin case than in the normal margin case. However, the trends and patterns
+margin case than in the normal margin case. In contrast to the marginal normal
+distribution, where coverage rates of were greater for stronger dependences 
+regardless of the sign, coverage rates seem to be greater only for stronger 
+negative
+dependencies and lesser for stronger positive dependences. 
+\mc{What could be an explanation for this?}
+However, the other 
+trends 
+and patterns
 discussed in the main text regarding the performance of various methods and
@@
 confidence interval continues to be effective in estimating the temporal 
-dependence %\mc{replaced $\phi$ again here} 
+dependence 
 due to the
-inherent unbiasedness of the original point estimator. In sum, the findings for
+inherent unbiasedness of the original point estimator. In sum, 
+for the most part, the findings for
 series that are marginally exponentially distributed closely mirror those
@@
 Student's $t$ should still be used if $\phi$ is unknown. Lastly, to estimate 
-$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Although
+$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Further
+investigation may be necessary to see if there are other percentile-based 
+interval corrections
+that fix the coverage deterioration problem for $\phi$.
+
+Although
 we have only used serial dependences as strong as 0.4, we have established the 
-trend. When estimating $\mu$, we expect coverage rates to decrease as
+trends as $|\phi|$ gets larger. When estimating $\mu$, we expect coverage rates 
+to decrease as
 $\phi$ approaches 1 - as $\phi$ approaches -1, we may observe increased 
@@
 expect a larger sample size to be necessary as $|\phi|$ approaches 0. However, 
-for a marginal exponential distribution, we expect coverage rates of $\phi$ to 
+for a marginal exponential distribution, we expect coverage rates of the 
+first-order autocorrelation to 
 respond
-to stronger dependences similarly to coverage rates of $\mu$. Further
-investigation may be necessary to see if there are other percentile-based 
-interval corrections
-that fix the coverage deterioration problem for $\phi$.
+to stronger dependences in a trend similar to that of coverage rates of $\mu$.
 

### 2024-01-08 Manuscript/manuscript.tex
fixed differences between distributions and block sizes

@@
 
-\subsection*{Normal Marginal Distribution}
+\subsection*{Marginal Standard Normal Distribution}
 %We designed a simulation study to compare the performance of the different block 
@@
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a standard normal marginal distribution using block bootstrap
+real coverage for a marginal standard normal distribution using block bootstrap
 with $l = \lceil n^{1/3} \rceil$, generated using the 
@@
 
-\subsection*{Exponential Marginal Distribution}
+\subsection*{Marginal Unit Exponential Distribution}
 Additionally, we evaluated the performance of block bootstrap when used to 
@@
 the mean, standard deviation, and the lag-1 autocorrelation coefficient of a
-stationary series with an exponential marginal distribution. The motivation of
+stationary series with a marginal exponential distribution. The motivation of
 for this study was to investigate if the results are robust to nonnormal
@@
 
-\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi1}} 
-summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a exponential marginal distribution using block bootstrap
-with $l = \lceil n^{1/3} \rceil$.
+For a marginal exponential  distribution, the empirical coverage rates for 
+$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
+%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
+and 
+the lag-1 autocorrelation coefficient using block bootstrap
+with $l = \lceil n^{1/3} \rceil$, %\mc{replaced $\phi$ here, as I understand
+%it, we are not using $\phi$ in reference to the temporal dependence of the 
+%exponentially distributed series?}, 
+as well as 95\%
+confidence intervals of the real coverage are displayed in 
+\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi1}}.
 
@@
 %\subsection*{Results}
+
+\subsection*{Marginal Standard Normal Distribution}
 
@@
 
-\subsection*{Normal Marginal Distribution}
 For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
@@
 
-\subsection*{Exponential Marginal Distribution}
-For an exponential marginal distribution, the empirical coverage rates for 
-$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
-%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
-and 
-the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
-%it, we are not using $\phi$ in reference to the temporal dependence of the 
-%exponentially distributed series?}, 
-as well as 95\%
-confidence intervals of the real coverage are displayed in 
-\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi1}}. 
-Additionally, a set of 50 CIs are displayed for each of the percentile, 
-BC, and recentered percentile approaches for exponentially distributed
-samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
-($\phi = 0.4$) in Figure~\ref{fig:eri}.
+\subsection*{Marginal Unit Exponential Distribution}
 
@@
 \end{figure}
+
+Additionally, a set of 50 CIs are displayed for each of the percentile, 
+BC, and recentered percentile approaches for exponentially distributed
+samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
+($\phi = 0.4$) in Figure~\ref{fig:eri}.
 
@@
 necessary sample sizes when using block bootstrap to estimate parameters of 
-serially dependent data. When using Student's $t$ intervals and $\phi$ is 
-unknown, the results of this study suggest that an $n \geq 800$ may be necessary 
-for common practice to estimate simpler parameters like $\mu$ or $\sigma_x$. If 
-$\phi$ is already known, a lesser $n$ may be adequate to estimate these 
+serially dependent data. When using Student's $t$ intervals and the marginal
+distribution and temporal dependence is 
+unknown, the results of this study suggest that $n \geq 1600$ may be necessary 
+for common practice to estimate $\mu$, whereas $n > 3200$ may be necessary
+to estimate the standard deviation. If 
+the dependences tructure or the marginal distribution is already known, a 
+lesser $n$ may be 
+adequate to estimate these 
 parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
-when estimating $\sigma_x$. For negative values of $\phi$, coverage of all 
-parameters is higher in general. In fact, Student's $t$ seems to over-cover 
-$\mu$ for $\phi = - 0.4$ when using smaller sample sizes, meaning that if $\phi$ 
+when estimating the standard deviation. For negative values of $\phi$, coverage of all 
+parameters is higher in general. Under a marginal standard normal distribution, 
+Student's $t$ seems to over-cover 
+$\mu$ for $\phi = - 0.4$  when 
+using smaller sample sizes, meaning that if $\phi$ 
 is known to have a very negative value, another CI may be required. However, in 
 real world applications, $\phi$ is more commonly found to be positive, so 
-Student's $t$ should still be used if $\phi$ is unknown. Lastly, to estimate 
-$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Further
+Student's $t$ should still be used if $\phi$ is unknown. 
+Lastly, to estimate 
+$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient under
+a marginal standard normal distribution, whereas $n \geq 1600$ may be required
+under under a marginal exponential distribution. Further
 investigation may be necessary to see if there are other percentile-based 
@@
 $\phi$ approaches 1 - as $\phi$ approaches -1, we may observe increased 
-over-coverage. When estimating $\sigma$, we expect a larger sample size to
+over-coverage. When estimating the standard deviation, we expect a larger sample 
+size to
 be necessary as $|\phi|$ gets closer to 1. Lastly, when estimating $\phi$ for
@@
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a standard normal marginal distribution using block bootstrap
+real coverage for a marginal standard normal distribution using block bootstrap
 with $l = \lceil 2n^{1/3} \rceil$.
@@
 \textbf{Figure~\ref{fig:sigma2}} looks very similar to 
-\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma$ do look 
+\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma_x$ do look 
 slightly lower
@@
 not as influenced by this change in $l$. A larger sample size seems necessary
-when using other CIs to estimate $\sigma$ for $l = \lceil 2n^{1/3} \rceil$.
+when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.
 
@@
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a exponential marginal distribution using block bootstrap
+real coverage for a marginal exponential distribution using block bootstrap
 with $l = \lceil 2n^{1/3} \rceil$.
@@
 
-For a stationary series with a marginal exponential distribution, altering the 
+For a stationary series with a marginal unit exponential distribution, altering 
+the 
 block size results in the same 

### 2024-01-08 Manuscript/manuscript.tex
comments/edits on reply/manuscript

@@
 interval corrections
-that fix the coverage deterioration problem for $\phi$.
-
+that fix the coverage deterioration problem for~$\phi$.
+\jy{add tilde to avoid line break where you are sure you don't want a
+  line break.}
+
+\jy{This is for our method. Some percentile-based CIs may have coverage
+  approaching zero, right?}
 Although
@@
 to decrease as
-$\phi$ approaches 1 - as $\phi$ approaches -1, we may observe increased 
+$\phi$ approaches 1 --- as $\phi$ approaches -1, we may observe increased 
 over-coverage. When estimating the standard deviation, we expect a larger sample 
@@
 respond
-to stronger dependences in a trend similar to that of coverage rates of $\mu$.
+to stronger dependences in a trend similar to that of coverage rates of~$\mu$.
 
@@
 \citet{buhlmann2002bootstraps} finds to be the best for linear time series.
-Lastly, because of its exceptional performance in comparison to the other 
-percentile-based CIs, the proposed recentered percentile 
-CI would be
-an interesting method to study further with different bootstrap schemes.
+Finally, there is a need for a more in-depth exploration to comprehend
+the reasons behind the subpar performance of existing percentile-based
+CIs when estimating the autocorrelation parameter. It is crucial to
+conduct a thorough investigation into the specific scenarios where the
+proposed CI demonstrates superior performance and the conditions under
+which it should be recommended.
 

### 2024-01-08 Manuscript/reply.tex
Responded to last comment
comments/edits on reply/manuscript

@@
 revised accordingly with the following notable changes:
-\jy{Be selective here for ``notable''. I'd not include items like `wording
-  clarification'; your could put all the clarifications as one
-  item. Keep this list short for the reviewers to have a  
-  quick idea about the major changes (e.g., additional simulation studies).}
-\mc{addressed}
-
 \begin{enumerate}
-\item Added clarifications of design and more detail examination of results;
+\item Clarifications of design and more detail examination of results;
 \item Reorganization of paragraphs on the Simulation Study, including moving the
@@
 the Recentered Percentile CI;
-\item An Appendix on simulation study using block size 
-$l = \lceil 2n^{1/3} \rceil$
+\item Additional simulation study using block size 
+$l = \lceil 2n^{1/3} \rceil$ in the Appendix.
 \end{enumerate}
@@
 Point-by-point responses to the comments are as follows, with the
-comments quoted in \emph{\color{darkblue} italic}.
+comments quoted in \emph{\color{darkblue} italic and blue}.
 
@@
 
-\jy{put the legend on one line.}
-\mc{addressed}
-
-\jy{This plot seems fine to me. Could you make it for the other
-  parameters too? Then we can make a decision. If we use this, the
-  number of figures would be greatly reduced.}
-\mc{addressed}
+\jy{Could you put the three plots in one? Perhaps use facet grid: phi
+  by parameter (mu, sigma, phi). Then we just need one caption.}
 
@@
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu}
+  \label{fig:sigma}
 \end{figure}
@@
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu}
+  \label{fig:phi}
 \end{figure}
@@
 Thank you for the comment. We expect the CIs that 
-are based on bootstrap
-\jy{Need to explain ``table'' methods better in the manuscript.}
-\mc{I gave it a try}
-``tables" to depend on the 
+are based on bootstrap ``tables" to depend on the 
 asymptotic distribution of the statistics, but we expect such CIs to 
@@
 \citet{efron1993introduction} refers to such CIs as
-\jy{This is still not clear. I think they mean CIs based on asymptotic
-  distributions with estimated asymptotic variances. This is in
-  contrast to percentile based CIs.}
-\mc{I tried to make it more clear in the manuscript, I used ``percentile-based"
-in the manuscript instead of CIs that are not based on tables}
 ``confidence intervals based on 
@@
 \begin{comment}
-3. The sections are numbered, which makes it awkward when the authors refer back 
+3. The sections are unnumbered, which makes it awkward when the
+authors refer back
 to a section.  For instance, they refer to “...procedures described in Block 
@@
 
-This is a journal style choice.
+We found unnumbered sections inconvenient too, but unfortunately, 
+this is a journal style choice.
 
@@
   Figure~\ref{fig:mu}.}
-\mc{addressed}
+\mc{addressed}\jy{Put them overlaid; three plots in one with facet
+  grid as the last one.}
 
@@
 similar
-comment at the end of the paragraph on estimation of 
-$\mu$.
+comment at the end of the paragraph on estimation of~$\mu$.
 
@@
 
+\jy{Add a discussion in the results section, referring to detailed
+  results in the appendix. Point out the location of this discussion
+  in this reply.}
+
 \begin{comment}
@@
 section. We have also added a comment in the discussion regarding what would
-be expected for higher dependence levels. \jy{Add a comment in the discussion about what'd be expected
-  with higher dependence levels.}
+be expected for higher dependence levels.
+\jy{give the location of the paragraph in the text.}
 
@@
 We apologize for the omission. These intervals are discussed in 
-\citep{efron1993introduction}. A citation is now provided in the last paragraph.
+\citet{efron1993introduction}. A citation is now provided in the last paragraph.
 
@@
 with block bootstrap in the introduction, while also highlighting its advantages
-which motivated this investigation into their CI performance.
+which motivated this investigation into their CI performance. This
+last sentences of the manuscript has also been rewritten to call for
+understanding of the subpar performance of the existing
+percentile-based CIs for the autocorrelation parameter and situations
+where the proposed CI should be recommended.
 

### 2024-01-08 Manuscript/manuscript.tex
faceted overlaid graphs

@@
   line break.}
+\mc{addressed}
 
@@
 by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
-for smaller values of $n$.
+for smaller values of~$n$.
 
@@
 especially for negative values of $\phi$, although Student's $t$ CIs are again
-not as influenced by this change in $l$. A larger sample size seems necessary
+not as influenced by this change in~$l$. A larger sample size seems necessary
 when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.

### 2024-01-08 Manuscript/reply.tex
faceted overlaid graphs

@@
 
-Thank you for this idea. We have provided Figure~\ref{fig:mu} as an 
+Thank you for this idea. We have provided Figure~\ref{fig:norm1} as an 
 example of what this suggested figure
@@
   by parameter (mu, sigma, phi). Then we just need one caption.}
+\mc{I think it looks good, only problem is I'm not sure how friendly it is for
+colorblind people. I used a palette which is supposed to be more colorblind
+friendly}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/alt_plot_norm_mu_1}
+  \includegraphics[width=\textwidth]{figures/alt_plot_norm1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard 
     normal distribution with AR coefficient
@@
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu}
+  \label{fig:norm1}
 \end{figure}
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/alt_plot_norm_sigma_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\sigma$ of an AR(1) process with a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:sigma}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/alt_plot_norm_phi_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\phi$ of an AR(1) process with a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi}
-\end{figure}
-
-We find that this format
-is a little
-cluttered to make comparisons, so we have elected to remain with the original 
-format.
+%We find that this format
+%is a little
+%cluttered to make comparisons, so we have elected to remain with the original 
+%format.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/alt2plot_norm_phi_1}
+  \includegraphics[width=\textwidth]{figures/alt2_plot_norm1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
+    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
     the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard normal distribution with 
+    a marginal standard 
+    normal distribution with AR coefficient
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:alt_phi1}
+  \label{fig:alt2_norm1}
 \end{figure}
@@
   grid as the last one.}
+  \mc{addressed. I think the last one looks better}
 

### 2024-01-08 Code/functions.R

@@ -122,6 +122,8 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 
 alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 {
+  cbPalette <- 
+    c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
   font_add_google("EB Garamond")
   #  windows()
   
@@ -135,7 +137,7 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
     geom_line(size = .2, position = position_dodge(width = 0.5)) +
     geom_errorbar(aes(ymin=LB, ymax = UB, color = CI), width = width, size = .2,
                   position = position_dodge(width = 0.5)) +
-    facet_grid(. ~ factor(phi), scales = 'free') +
+    facet_grid(factor(target) ~ factor(phi), scales = 'free') +
     labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
@@ -143,13 +145,16 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
           strip.text.y = element_text(angle = 270, hjust = 1),
           legend.position = "bottom") +
     scale_y_continuous(trans=trans) +
-    guides(colour = guide_legend(nrow = 1))
+    guides(colour = guide_legend(nrow = 1)) +
+    scale_colour_manual(values=cbPalette)
   ggsave(paste('../Manuscript/figures/alt_plot_', t, '.pdf', sep = ''), width = 10,
-         height = 3)
+         height = 6)
 }
 
 alt_graph_bts2 <- function(t, width, data, trans = 'identity', level = .95)
 {
+  cbPalette <- 
+    c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
   font_add_google("EB Garamond")
   #  windows()
   
@@ -158,17 +163,21 @@ alt_graph_bts2 <- function(t, width, data, trans = 'identity', level = .95)
   data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
[…]

### 2024-01-08 Code/plots.R

@@ -23,6 +23,26 @@ graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
 alt_graph_bts2(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
 alt_graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
 
+t <- 'norm1'
+width <- .2
+alt_graph_bts(t, 
+              width, 
+              rbind(
+              norm_mu %>% filter(blksize == ceiling(n^(1/3))),
+              norm_sigma %>% filter(blksize == ceiling(n^(1/3))),
+              norm_phi %>% filter(blksize == ceiling(n^(1/3)))))
+
+t <- 'norm1'
+width <- .2
+alt_graph_bts2(t, 
+              width, 
+              rbind(
+                norm_mu %>% filter(blksize == ceiling(n^(1/3))),
+                norm_sigma %>% filter(blksize == ceiling(n^(1/3))),
+                norm_phi %>% filter(blksize == ceiling(n^(1/3)))))
+
+
+
 t <- 'norm_mu_2'
 width <- .2
 graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(2*n^(1/3))))

### 2024-01-08 Manuscript/manuscript.tex
addressed comment on manuscript

@@
 margin case than in the normal margin case. In contrast to the marginal normal
-distribution, where coverage rates of were greater for stronger dependences 
-regardless of the sign, coverage rates seem to be greater only for stronger 
+distribution, where standard normal, Student's $t$, and 
+recentered percentile CI coverage rates were greater for stronger dependences 
+regardless of the sign, coverage rates for these CIs seem to be greater only for 
+stronger 
 negative
@@
   approaching zero, right?}
+\mc{addressed}
+
 Although
@@
 a marginal normal distribution, we 
-expect a larger sample size to be necessary as $|\phi|$ approaches 0. However, 
-for a marginal exponential distribution, we expect coverage rates of the 
-first-order autocorrelation to 
+expect a larger sample size to be necessary as $|\phi|$ approaches 0, assuming
+standard normal, Student's $t$, or 
+recentered percentile CIs are used. However, 
+when estimating the first-order autocorrelation of a marginal exponential 
+distribution using the same methods, we expect coverage rates to 
 respond
 to stronger dependences in a trend similar to that of coverage rates of~$\mu$. 
+We expect other percentile-based CIs, which are already inadequate for 
+relatively weak
+dependence structures, to perform even worse as $|\phi|$ approaches 1.
 

### 2024-01-08 Manuscript/manuscript.tex
discussion of appendix

@@
 and we tried both $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$,
-keeping the order of the block size constant but varying the coefficient. The
-results for $l = \lceil 2n^{1/3} \rceil$ are included in the Appendix.
+keeping the order of the block size constant but varying the coefficient. 
 For each replicate, we constructed 
@@
 correct from the original point estimate $\hat\theta_n$.
+
+The
+plot and results for $l = \lceil 2n^{1/3} \rceil$ are included in the Appendix.
+Performance generally seems to be better for $l = \lceil n^{1/3} \rceil$, but
+importantly, the changes in performance when varying other parameters do not
+change when a different block size is used.
 

### 2024-01-08 Manuscript/reply.tex
discussion of appendix

@@
 $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
-an Appendix detailing these results.
+an Appendix detailing these results, as well as a discussion referring to these
+results at the end of the Simulation Study Results section.
 
@@
   in this reply.}
+\mc{addressed}
 
@@
 the parameter of interest. This justification has been added to the Design 
-section. We have also added a comment in the discussion regarding what would
+section. We have also added a deliberation (third paragraph in the Discussion) 
+regarding what would
 be expected for higher dependence levels.
 \jy{give the location of the paragraph in the text.}
+\mc{addressed}
 

### 2024-01-08 Manuscript/reply.tex
Fixed pdf compile
quick comments

@@
 simulation studies, the centers of the existing CIs appeared to be a
-biased estimator of the target while the spreadness of the CIs still
+biased estimator of the target while the spreads of the CIs still
 provide good uncertainty measures. This has now been added in the
-Recentered Percentile CI pargarph.
+Recentered Percentile CI paragraph.
 
@@
 
-\jy{Could you put the three plots in one? Perhaps use facet grid: phi
-  by parameter (mu, sigma, phi). Then we just need one caption.}
-\mc{I think it looks good, only problem is I'm not sure how friendly it is for
-colorblind people. I used a palette which is supposed to be more colorblind
-friendly}
+\jy{Lets use the new graph in the paper too. You may also use
+  different line types to distinguish them.}
+
+\jy{Use latex symbols for mu, sigma, phi in the plots.}
 
@@
 
-%We find that this format
-%is a little
-%cluttered to make comparisons, so we have elected to remain with the original 
-%format.
-
 \begin{comment}
@@
 
-You are correct. To remedy this, the text highlighting the simulation study with 
-an exponential marginal 
+Agreed. The text highlighting the simulation study with an exponential marginal
 distribution from the Appendix has been moved to the Simulation Study 
@@
 \mc{I included it in the paper but they do not seem too different}
+\jy{Point out the location of the changes in the text.}
 
@@
 for the binomial proportion did not cause undercoverage in this case.
-
-%CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
-%as stated before, the Wald-type CI is known to have undercoverage in such 
-%situations.
-%Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
-%Clopper-Pearson intervals to verify that it is the choice of Wald interval
-%does not cause undercoverage of the coverage rate. Indeed, the widths of the
-%exact proportion CIs do not seem to differ heavily from the Wald-type CIs.
 
@@
 y-axis without hurting the visualization for the other rows. 
-Figure~\ref{fig:alt_phi1} is provided as an example:
+Figure~\ref{fig:alt2_norm1} is provided as an example:
 
@@
 
-\jy{I'm interested in seeing the figures overlaid as in
-  Figure~\ref{fig:mu}.}
+%\jy{I'm interested in seeing the figures overlaid as in
+%  Figure~\ref{fig:mu}.}
 \mc{addressed}\jy{Put them overlaid; three plots in one with facet

### 2024-01-08 Code/functions.R
1/8 Notes varied linetype for graph, need to figure out how to use greek letters in facet labels

@@ -123,7 +123,7 @@ graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 {
   cbPalette <- 
-    c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+    c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
   font_add_google("EB Garamond")
   #  windows()
   
@@ -132,12 +132,14 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
   data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
                     labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Recentered'))
   
-  ggplot(data, aes(x = n, y = cov, color = CI)) +
+  
+  ggplot(data, aes(x = n, y = cov, color = CI, linetype = CI)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
     geom_line(size = .2, position = position_dodge(width = 0.5)) +
     geom_errorbar(aes(ymin=LB, ymax = UB, color = CI), width = width, size = .2,
                   position = position_dodge(width = 0.5)) +
-    facet_grid(factor(target) ~ factor(phi), scales = 'free') +
+    facet_grid(factor(target) ~ factor(phi), scales = 'free',
+               labeller = labeller(target = as_labeller(target.labs))) +
     labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
@@ -154,7 +156,7 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
 alt_graph_bts2 <- function(t, width, data, trans = 'identity', level = .95)
 {
   cbPalette <- 
-    c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+    c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
   font_add_google("EB Garamond")
   #  windows()
   

### 2024-01-08 Code/plots.R

@@ -1,27 +1,13 @@
 library(tidyverse)
 source("functions.R")
 norm_mu <- read.csv("../Data/norm_mu.csv") %>% 
-  filter(CI != 'ctrCI')
+  filter(CI != 'ctrCI') %>% 
+  mutate(facet_target <- c('mu')[target])
 norm_sigma <- read.csv("../Data/norm_sigma.csv") %>% 
   filter(CI != 'ctrCI')
 norm_phi <- read.csv("../Data/norm_phi.csv") %>% 
   filter(CI != 'ctrCI')
 
-t <- 'norm_mu_1'
-width <- .2
-graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(n^(1/3))))
-alt_graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(n^(1/3))))
-
-t <- 'norm_sigma_1'
-width <- .2
-graph_bts(t, width, norm_sigma %>% filter(blksize == ceiling(n^(1/3))))
-alt_graph_bts(t, width, norm_sigma %>% filter(blksize == ceiling(n^(1/3))))
-
-t <- 'norm_phi_1'
-width <- .2
-graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
-alt_graph_bts2(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
-alt_graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(n^(1/3))))
 
 t <- 'norm1'
 width <- .2

### 2024-01-08 Manuscript/manuscript.tex
added plots to manuscript (greek letters included, still need to change text accordingly

@@
 interval has poor coverage as the proportion approaches 0 or 1.
-\textbf{Figures~\ref{fig:mu1}--\ref{fig:phi1}} 
+\textbf{Figure~\ref{fig:norm1}} 
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
@@
 confidence intervals of the real coverage are displayed in 
-\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi1}}.
+\textbf{Figure~\ref{fig:exp1}}.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1}
+  \includegraphics[width=\textwidth]{figures/alt_plot_norm1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard 
     normal distribution with AR coefficient
     $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
+    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates
+    of
     block bootstrap with $l = \lceil n^{1/3} \rceil$. The
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu1}
+  \label{fig:norm1}
 \end{figure}
 
-\begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
-    marginal standard normal distribution with AR 
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. The 
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:sigma1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_phi_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard normal distribution with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi1}
-\end{figure}
-
-For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
+For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:norm1}} suggests 
 that all methods eventually approach correct coverage of $\mu$ as sample size 
@@
 
-CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
-as stated before, the Wald-type CI is known to have undercoverage in such 
-situations.
-Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
-Clopper-Pearson intervals to verify that it is the choice of Wald interval
-does not cause undercoverage of the coverage rate. Indeed, the widths of the
-exact proportion CIs do not seem to differ heavily from the Wald-type CIs.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1_cp}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs 
-    for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
-    error bars represent 95\% exact CIs of the real coverage rates.}
-  \label{fig:norm_mu_1_cp}
-\end{figure}
+%CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
+%as stated before, the Wald-type CI is known to have undercoverage in such 
+%situations.
+%Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
+%Clopper-Pearson intervals to verify that it is the choice of Wald interval
+%does not cause undercoverage of the coverage rate. Indeed, the widths of the
+%exact proportion CIs do not seem to differ heavily from the Wald-type CIs.
 
 For estimating the standard deviation parameter~$\sigma_x$,
-\textbf{Figure~\ref{fig:sigma1}} suggests that every method can reach nominal 
+\textbf{Figure~\ref{fig:norm1}} suggests that every method can reach nominal 
 coverage of $\sigma_x$ if the sample is large enough, but for a given $n$ and 
@@
 For estimating the autocorrelation parameter~$\phi$, 
-\textbf{Figure~\ref{fig:phi1}} suggests that while standard normal, Student's $t$, and 
+\textbf{Figure~\ref{fig:norm1}} suggests that while standard normal, Student's $t$, and 
 recentered percentile CIs do approach correct coverage as sample size increases, 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_mu_1}
+  \includegraphics[width=\textwidth]{figures/alt_plot_exp1}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a stationary series with marginal unit exponential
-    distribution obtained by transforming an AR(1) process with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_mu1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
-    of a stationary series with 
-    marginal unit exponential distribution obtained by transforming an AR(1) process
+    the marginal mean $\mu$, the marginal standard deviation $\sigma_w$, and
+    the first-order autocorrelation coefficient $\rho$ of a stationary series 
+    with 
+    marginal unit exponential distribution obtained by transforming an AR(1) 
+    process
     with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
@@
     The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_sigma1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_phi_1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient of a stationary series
-    with marginal unit exponential distribution obtained by transforming an AR(1) 
-    process with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi1}
+  \label{fig:exp1}
 \end{figure}
@@
 
-\textbf{Figures~\ref{fig:mu2}--\ref{fig:phi2}} 
+\textbf{Figure~\ref{fig:norm2}} 
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_mu_2}
+  \includegraphics[width=\textwidth]{figures/alt_plot_norm2}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
+    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
+    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
+    a marginal standard 
     normal distribution with AR coefficient
@@
     error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:mu2}
+  \label{fig:norm2}
 \end{figure}
 
-\begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_sigma_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_x$ of an AR(1) process with a
-    marginal standard normal distribution with AR 
-    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The 
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:sigma2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_norm_phi_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard normal distribution with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:phi2}
-\end{figure}
-
-Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
+Based on \textbf{Figure~\ref{fig:norm2}}, for negative autocorrelations, the 
 coverage 
@@
 
-\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
-\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma_x$ do look 
+The results for $\sigma_x$ with $l = \lceil 2n^{1/3} \rceil$ look very similar 
+to 
+those the results for $\sigma_x$ with $l = \lceil n^{1/3} \rceil$, but coverage 
+rates of $\sigma_x$ do 
+look 
 slightly lower
@@
 
-As shown in \textbf{Figure~\ref{fig:phi2}},
+As shown in \textbf{Figure~\ref{fig:norm2}},
 recentered percentile and standard CIs have slightly lower coverage rates when
@@
 
-\textbf{Figures~\ref{fig:exp_mu2}--\ref{fig:exp_phi2}} 
+\textbf{Figure~\ref{fig:exp2}} 
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_mu_2}
+  \includegraphics[width=\textwidth]{figures/alt_plot_exp2}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$ of a stationary series with marginal unit exponential
-    distribution obtained by transforming an AR(1) process with
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_mu2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_sigma_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
-    of a stationary series with 
-    marginal unit exponential distribution obtained by transforming an AR(1) process
+    the marginal mean $\mu$, the marginal standard deviation $\sigma_w$, and
+    the first-order autocorrelation coefficient $\rho$ of a stationary series 
+    with 
+    marginal unit exponential distribution obtained by transforming an AR(1) 
+    process
     with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
@@
     The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_sigma2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/plot_exp_phi_2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
-    the first-order autocorrelation coefficient of a stationary series
-    with marginal unit exponential distribution obtained by transforming an AR(1) 
-    process with 
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp_phi2}
+  \label{fig:exp2}
 \end{figure}

### 2024-01-08 Manuscript/reply.tex
1/8 Notes varied linetype for graph, need to figure out how to use greek letters in facet labels
added plots to manuscript (greek letters included, still need to change text accordingly

@@
 
-Thank you for this idea. We have provided Figure~\ref{fig:norm1} as an 
-example of what this suggested figure
-would look like.
+Thank you for this idea. We have reformatted all of our coverage rate plots 
+accordingly, which has saved a lot of space!
 
@@
   different line types to distinguish them.}
+\mc{addressed}
 
 \jy{Use latex symbols for mu, sigma, phi in the plots.}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/alt_plot_norm1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:norm1}
-\end{figure}
+\mc{for exponential, the first-order autocorrelation coefficient
+is not the same as $\phi$, should I define $\rho$ as the first-order 
+autocorrelation coefficient in the manuscript so that I can use the greek letter
+in the plot}
 

### 2024-01-08 Code/functions.R

@@ -132,20 +132,22 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
   data$CI <- factor(data$CI, levels = c('stdCI', 'stuCI', 'pctCI', 'bcCI', 'bcaCI', 'propCI'), 
                     labels = c('Standard', 'Student\'s t', 'Percentile', 'BC', 'BCA', 'Recentered'))
   
+  data$target <- factor(data$target, levels = c('mu', 'sigma', 'phi', 'rho'))
   
   ggplot(data, aes(x = n, y = cov, color = CI, linetype = CI)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
-    geom_line(size = .2, position = position_dodge(width = 0.5)) +
+    geom_line(linewidth = .2, position = position_dodge(width = 0.5)) +
     geom_errorbar(aes(ymin=LB, ymax = UB, color = CI), width = width, size = .2,
                   position = position_dodge(width = 0.5)) +
     facet_grid(factor(target) ~ factor(phi), scales = 'free',
-               labeller = labeller(target = as_labeller(target.labs))) +
+               labeller = label_parsed) +
     labs(x = 'Sample Size', y = 'Coverage Rate') +
     scale_x_continuous(breaks = c(100, 200, 400, 800, 1600, 3200), trans='log2') +
     theme(axis.text.x = element_text(angle = 45, hjust = 1), text =
             element_text(family = "EB Garamond", size = 10),
           strip.text.y = element_text(angle = 270, hjust = 1),
-          legend.position = "bottom") +
+          legend.position = "bottom",
+          strip.text.y.right = element_text(angle = 0)) +
     scale_y_continuous(trans=trans) +
     guides(colour = guide_legend(nrow = 1)) +
     scale_colour_manual(values=cbPalette)

### 2024-01-08 Code/plots.R

@@ -1,13 +1,11 @@
 library(tidyverse)
 source("functions.R")
 norm_mu <- read.csv("../Data/norm_mu.csv") %>% 
-  filter(CI != 'ctrCI') %>% 
-  mutate(facet_target <- c('mu')[target])
+  filter(CI != 'ctrCI')
 norm_sigma <- read.csv("../Data/norm_sigma.csv") %>% 
   filter(CI != 'ctrCI')
 norm_phi <- read.csv("../Data/norm_phi.csv") %>% 
   filter(CI != 'ctrCI')
-
 
 t <- 'norm1'
 width <- .2
@@ -27,19 +25,14 @@ alt_graph_bts2(t,
                 norm_sigma %>% filter(blksize == ceiling(n^(1/3))),
                 norm_phi %>% filter(blksize == ceiling(n^(1/3)))))
 
-
-
-t <- 'norm_mu_2'
+t <- 'norm2'
 width <- .2
-graph_bts(t, width, norm_mu %>% filter(blksize == ceiling(2*n^(1/3))))
-
-t <- 'norm_sigma_2'
-width <- .2
-graph_bts(t, width, norm_sigma %>% filter(blksize == ceiling(2*n^(1/3))))
-
-t <- 'norm_phi_2'
-width <- .2
-graph_bts(t, width, norm_phi %>% filter(blksize == ceiling(2*n^(1/3))))
+alt_graph_bts(t, 
+              width, 
+              rbind(
+                norm_mu %>% filter(blksize == ceiling(2*n^(1/3))),
+                norm_sigma %>% filter(blksize == ceiling(2*n^(1/3))),
+                norm_phi %>% filter(blksize == ceiling(2*n^(1/3)))))
 
 exp_mu <- read.csv("../Data/exp_mu.csv") %>% 
   filter(CI != 'ctrCI')
@@ -48,29 +41,23 @@ exp_sigma <- read.csv("../Data/exp_sigma.csv") %>%
 exp_phi <- read.csv("../Data/exp_phi.csv") %>% 
   filter(CI != 'ctrCI')
 
-t <- 'exp_mu_1'
+t <- 'exp1'
 width <- .2
-graph_bts(t, width, exp_mu %>% filter(blksize == ceiling(n^(1/3))))
+alt_graph_bts(t, 
+              width, 
+              rbind(
+                exp_mu %>% filter(blksize == ceiling(n^(1/3))),
[…]

### 2024-01-09 Manuscript/manuscript.tex
further comments and edits

@@
 % control floats
-%% \renewcommand\floatpagefraction{.9}
-%% \renewcommand\topfraction{.9}
-%% \renewcommand\bottomfraction{.9}
-%% \renewcommand\textfraction{.2}
-%% \setcounter{totalnumber}{50}
-%% \setcounter{topnumber}{50}
-%% \setcounter{bottomnumber}{50}
+\renewcommand\floatpagefraction{.9}
+\renewcommand\topfraction{.9}
+\renewcommand\bottomfraction{.9}
+\renewcommand\textfraction{.2}
+\setcounter{totalnumber}{50}
+\setcounter{topnumber}{50}
+\setcounter{bottomnumber}{50}
 
@@
 
-\section*{introduction}
+\section*{Introduction}
 
@@
 the desired coverage rates.
-%\eds{I think the superscript citations need to go before the punctuation.  
-%Please check in other AJUR papers and adjust throughout the paper if needed.}
-%\mc{from the style guide: "Please bold and superscript the numbers for 
-%references in the text.1 Separate superscripted numbers by comma and space,1, 2 
-%they should be separated by an en-dash if the consecutive list of more than two 
-%numbers is used.1–3 List them AFTER punctuation (be it comma or period) with no 
-%space.2} 
-%\eds{thank you for checking!}
 
@@
 mimicking dependence structures.
-
-\eds{If we include all these drawbacks here, we need to also provide some good 
-features of block bootstrap as well, otherwise, why do we care about their CI 
-performance?}
-\mc{addressed}
 
@@
 six variants of block bootstrap CIs from the 
-literature:\citep{diciccio1996bootstrap, rice2006mathematical} a standard normal 
-CI, a 
+literature:\citep{diciccio1996bootstrap, rice2006mathematical}
+a standard normal CI, a 
 Student's $t$ CI, a percentile CI, a bias-corrected CI, a bias-corrected and 
@@
 
-\section*{block bootstrap cis}
+\section*{Block Bootstrap CIs}
 \label{sec:bbci}
@@
 \]
-%\eds{If $z_{(\alpha)}$ is the upper quantile, then $z_{(\alpha/2)}$ will be 
-%positive and $z_{(1-\alpha/2)}$ will be negative for small $\alpha$ values; with
-%the subtraction of the quantiles, the smaller CI endpoint would appear to
-%be listed first.  Please check this notation, and the notation for Student's $t$ 
-%CI, and other intervals which use the $z_{(\alpha)}$ upper standard normal 
-%quantile.} 
-%\mc{Replaced upper quantile with quantile function}
-
 This CI is centered by the original point estimate $\hat\theta_n$ and is 
@@
 \]
-%\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
 where $k$ is the number of blocks. This CI is centered by the original point 
@@
 \]
-%\eds{the $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ may need to be switched now in 
-%$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$ -- 
-%please check.} 
-%\mc{yes they had to be switched}
 
@@
 \end{equation*}
-%\eds{please check $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ in 
-%$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$} 
-%\mc{this one is okay}
 A $(1 - \alpha)100\%$ ~BCA CI is
@@
 
-\section*{simulation design}
+\section*{Simulation Design}
 \label{sec:simdes}
 
-%\subsection*{Design}
-
-\eds{We compared the performance of the different block bootstrap CI methods 
-under two marginal distributions: normal and exponential.}
+We compared the performance of the different block bootstrap CI methods
+under two marginal distributions: normal and exponential.
 
 \subsection*{Marginal Standard Normal Distribution}
-%We designed a simulation study to compare the performance of the different block 
-%bootstrap CI methods. In particular, 
+
 We generated time series $X_t$ from a 1st 
@@
 $n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
-10000 replicates. The 
+10,000 replicates. The 
 block bootstrap sampling step was done with function \texttt{tsboot} from R 
@@
 CIs for each parameter as described in the last section with $B = 1000$. We can
-estimate $\mu$, 
-$\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
+estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean,
+sample standard deviation, 
 and lag-1 autocorrelation, respectively, of each bootstrap sample. Then we can 
@@
 Then we estimated their actual coverage 
-rates along with their 95\% confidence intervals from the 10000 replicates.
+rates along with their 95\% confidence intervals from the 10,000 replicates.
 
@@
 coverage rate 
-(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
+(which is an estimate of a proportion with $R = 10,000$). If the proportion 0.95 
 is included in the interval, the block bootstrap method is likely performing 
@@
 \subsection*{Marginal Unit Exponential Distribution}
-Additionally, we evaluated the performance of block bootstrap when used to 
-estimate
-the mean, standard deviation, and the lag-1 autocorrelation coefficient of a
-stationary series with a marginal exponential distribution. The motivation of
-for this study was to investigate if the results are robust to nonnormal
-marginal distributions.
-
-It is important to note that we expect the CIs that are based on bootstrap 
-``tables" to depend on the 
-asymptotic distribution of the statistics, but we expect such CIs to 
-have similar performance for different error structures. For example, under the 
-Central
-Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
-approximately 
-normal for both marginal normal distributions and marginal exponential 
-distributions. Therefore, we do not expect CIs that are percentile-based
-(Percentile, BC, BCA, Recentered Percentile CI) to perform better under
-non-normal error structures.
+Additionally, to investigate if the results are robust to nonnormal
+marginal distributions, we evaluated the performance of block
+bootstrap for a time series with a non-normal marginal
+distribution. Specifically, we estimated the mean, standard deviation,
+and the lag-1 autocorrelation coefficient of a stationary series with
+marginal unit exponential distribution. Note that we expect the CIs
+that are based on bootstrap ``tables" to depend on the 
+asymptotic distribution of the estimator.  This asymptotic
+distribution depends more on the sample size than on the marginal
+distribution of the time series. So we expect such CIs to 
+have similar performance for different marginal distributions when the
+sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
+Recentered Percentile CI) are not necessatily expected to perform
+better under non-normal marginal distributions. The student's t and
+and normal-based CIs are only noticeably different when the number of
+blocks is smaller than 20.
 
 The series were generated by marginally transforming the
-AR(1) series $X_t$ in the simulation study by
+AR(1) series $X_t$ in the first simulation study by
 \begin{equation*}
@@
 distribution. The true mean ($\mu$) and standard deviation ($\sigma_w$) 
-parameters 
-of $W_t$ are~1. The 
-lag-1
+parameters of $W_t$ are~1. The lag-1
 autocorrelation coefficient is not invariant to the
-transformation, \citep{hofert2018elements} but its value can be obtained by
+transformation,\citep{hofert2018elements} but its value can be obtained by
 \begin{equation*}
@@
 $\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
-autocorrelation coefficients are $\{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.
+autocorrelation coefficients are
+$\rho \in \{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.
 
 For a marginal exponential  distribution, the empirical coverage rates for 
-$\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
-%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
-and 
-the lag-1 autocorrelation coefficient using block bootstrap
-with $l = \lceil n^{1/3} \rceil$, %\mc{replaced $\phi$ here, as I understand
-%it, we are not using $\phi$ in reference to the temporal dependence of the 
-%exponentially distributed series?}, 
-as well as 95\%
+$\mu$, $\sigma_w$, and 
+the lag-1 autocorrelation coefficient $\rho$ using block bootstrap
+with $l = \lceil n^{1/3} \rceil$, as well as 95\%
 confidence intervals of the real coverage are displayed in 
@@
 
-\section*{simulation results}
+\section*{Simulation Results}
 \label{sec:simres}
-
-%\subsection*{Results}
 
@@
 autocorrelation, the effective sample
-size is decreased, whereas is a series has a negative autocorrelation, the
+size is decreased, whereas if a series has a negative autocorrelation, the
 effective sample size is increased. Additionally, this seems to have a 
@@
 of the scale parameter or temporal dependence parameter.
+
+\jy{Are we reporting the C-P intervals? Clarify the desciption and
+  cite the reference.}
 
@@
 regardless of the sign, coverage rates for these CIs seem to be greater only for 
-stronger 
-negative
-dependencies and lesser for stronger positive dependences. 
+stronger negative dependencies and lesser for stronger positive dependences. 
 \mc{What could be an explanation for this?}
+\jy{I don't follow this. Are you talking about mu only? Even for mu,
+  the statement does not look right.}
+\jy{This would invalidate our explanation using the effective sample
+  size. Let's tune it down or remove it.}
 However, the other 
@@
 methods. Performance continues to be more favorable when temporal dependence is
-negative rather than positive. Of particular significance, the 
-percentile, BC,
+negative rather than positive. Of particular significance, the percentile, BC,
 and BCA confidence intervals still display a decline in coverage accuracy for
@@
 confidence interval continues to be effective in estimating the temporal 
-dependence 
-due to the
+dependence due to the
 inherent unbiasedness of the original point estimator. In sum, 
@@
 
-\section*{discussion}
+\section*{Discussion}
 \label{sec:disc}
@@
 parameter of a time series at the nominal level given an infinitely large 
-sample, \citep{calhoun2018} so the goal for this study was to find the smallest 
+sample,\citep{calhoun2018} so the goal for this study was to find the smallest 
 finite sample length 
@@
 underestimates $\phi$, the coverage decreases. The BC CI seems to correct the 
-bias, but the width of the CI seems to be inconsistent. The acceleration factor 
-of the BCA CI seems to fail, as the width of the CI seems to be inconsistent.
+bias, but the width of the CI seems to be too short. The acceleration factor 
+of the BCA CI seems to fail, as the width of the CI seems to be too
+short.
+\jy{Inconsistent means not consistent and consistency is a desired
+  property of an estimator. When we talk about width of a CI, what
+  does consistency mean? Do an throughout check, please.}
 
 One of the goals of this study was to provide some practical recommendations for
-necessary sample sizes when using block bootstrap to estimate parameters of 
-serially dependent data. When using Student's $t$ intervals and the marginal
+necessary sample sizes when using block bootstrap to estimate the parameters of
+serially dependent data. When using Student's $t$ intervals and the
+marginal
+\jy{Recall that t is not different from normal when sample size is
+  large. So the recommendation is to do t always since it performs
+  better for small samples.}
 distribution and temporal dependence is 
@@
 to estimate the standard deviation. If
+\jy{Don't discuss these. The recommended method is regardless of what
+  the dependence struture and marginald istribution are. That's why we
+  did the study. Just gave recommendations based on both
+  scenarios. Rewrite this paragraph.}
 the dependences tructure or the marginal distribution is already known, a 
@@
 using smaller sample sizes, meaning that if $\phi$
+\jy{These statements are not to the point. Let's not discuss the case
+  where phi is know or not. They are not known. We want the method to
+  be robust to phi and the true marginal distribution.}
 is known to have a very negative value, another CI may be required. However, in 
@@
 that fix the coverage deterioration problem for~$\phi$.
-\jy{add tilde to avoid line break where you are sure you don't want a
-  line break.}
-\mc{addressed}
-
-\jy{This is for our method. Some percentile-based CIs may have coverage
-  approaching zero, right?}
-\mc{addressed}
 
@@
 simulation study for alternatives to block bootstrap, such 
-as AR-Sieve bootstrap, \citep{kreiss1992bootstrap} which 
+as AR-Sieve bootstrap,\citep{kreiss1992bootstrap} which 
 \citet{buhlmann2002bootstraps} finds to be the best for linear time series.
@@
 
+\jy{Put the small paragraphs into a bigger one.}
+
 As shown in \textbf{Figure~\ref{fig:norm2}},

### 2024-01-09 Manuscript/reply.tex
further comments and edits

@@
 
-Thank you for this idea. We have reformatted all of our coverage rate plots 
+Thank you for the suggestion idea. We have reformatted all of our coverage rate plots 
 accordingly, which has saved a lot of space!
 
-\jy{Lets use the new graph in the paper too. You may also use
-  different line types to distinguish them.}
-\mc{addressed}
-
-\jy{Use latex symbols for mu, sigma, phi in the plots.}
 \mc{for exponential, the first-order autocorrelation coefficient
@@
 in the plot}
+\jy{Yes.}
 
@@
 
-\eds{I also added subsubsections (paragraphs) for the Normal and Exponential 
-Marginal Distributions under Design and Results subsections.
-Is it possible to put to make the [Simulation Study] Design and 
-[Simulation Study] Results as two separate 
-sections instead of placing each as subsections of the Simulation Study section,
-or does the journal formatting prohibit this?  If you can change this, then the 
-Normal and Exponential Marginal subsubsections can be updated to subsections
-under the Simulation Study Design and Simulation Study Results sections.}  
-\mc{addressed}
-
 \begin{comment}
@@
 are based on bootstrap ``tables" to depend on the 
-asymptotic distribution of the statistics, but we expect such CIs to 
-have similar performance for different error structures. For example, under the 
-Central
-Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
-approximately 
-normal for both marginal normal distributions and marginal exponential 
-distributions. Therefore, we do not expect percentile-based CIs (Percentile, BC, BCA, Recentered Percentile CI) to perform better 
-under
-non-normal error structures. We have called attention to this in the Exponential
-Marginal Distribution subsection of the Design section.
-
-\eds{you will need to add more here.  This concerns the
-(asymptotic) distribution of the statistics, not the underlying error 
-structure.}
-\mc{I changed it a bit... I'm not sure what to say for circumstances in which
-“non-parametric” CI 
-formulas would work better}
+asymptotic distribution of the point estimator. This asymptotic
+distribution depends more on the sample size than on the marginal
+distribution of the time series. So we expect such CIs to 
+have similar performance for different marginal distributions when the
+sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
+Recentered Percentile CI) are not necessatily expected to perform
+better under non-normal marginal distributions. The student's t and
+and normal-based CIs are only noticeably different when the number of
+blocks is smaller than 20. We have added a discussion on this point in
+the first paragraph of the subsection of Marginal Unit Exponential
+Distribution.
 

### 2024-01-09 Manuscript/manuscript.tex
Switched to Clopper-Pearson

--- 2024-01-08 Manuscript/manuscript.tex
@@
 
-\eds{We compared the performance of the different block bootstrap CI methods 
-under two marginal distributions: normal and exponential.}
+We compared the performance of the different block bootstrap CI methods 
+under two marginal distributions: standard normal and unit exponential.
 
@@
 expected to match the nominal level. Because it is unlikely for the coverage to 
-exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
+exactly match the nominal level, we can construct a 95\% Clopper-Pearson
+exact CI of the 
 coverage rate 
-(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
+(which is an estimate of a proportion with $R = 10000$). The choice of
+Clopper-Pearson was motivated by the Wald 
+interval's poor coverage as the proportion approaches 0 or 1, as noted by
+\citet{brown2001interval}, although when we tried Wald intervals, the coverage
+rate intervals
+did not appear to have large differences. If the 
+proportion 0.95 
 is included in the interval, the block bootstrap method is likely performing 
@@
 interval are above .95, the results suggest that the method is overestimating 
-the process' variability. \citet{brown2001interval} notes that the Wald-type 
-interval has poor coverage as the proportion approaches 0 or 1.
+the process' variability. 
 \textbf{Figure~\ref{fig:norm1}} 
@@
 size is decreased, whereas is a series has a negative autocorrelation, the
-effective sample size is increased. Additionally, this seems to have a 
+effective sample size is increased. \citep{geyer2011introduction} Additionally, 
+this seems to have a 
 greater effect on the the estimation of the location parameter versus that
@@
 
-%CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
-%as stated before, the Wald-type CI is known to have undercoverage in such 
 %situations.
@@
 to estimate the standard deviation. If 
-the dependences tructure or the marginal distribution is already known, a 
+the dependence structure or the marginal distribution is already known, a 
 lesser $n$ may be 

### 2024-01-09 Manuscript/reply.tex
Switched to Clopper-Pearson

--- 2024-01-08 Manuscript/reply.tex
@@
 
-\eds{Also added comment in the Recentered Percentile CI paragraph in the 
-BLOCK BOOTSTRAP CIS section. Please check and add a comment here if you like it.}
-\mc{looks good}
-
 Thank you for this suggestion. The motivation behind the proposed
@@
 section.
-
-\eds{I also added subsubsections (paragraphs) for the Normal and Exponential 
-Marginal Distributions under Design and Results subsections.
-Is it possible to put to make the [Simulation Study] Design and 
-[Simulation Study] Results as two separate 
-sections instead of placing each as subsections of the Simulation Study section,
-or does the journal formatting prohibit this?  If you can change this, then the 
-Normal and Exponential Marginal subsubsections can be updated to subsections
-under the Simulation Study Design and Simulation Study Results sections.}  
-\mc{addressed}
 
@@
 similar
-comment at the end of the paragraph on estimation of~$\mu$.
+comment at the end of the paragraph on estimation of~$\mu$, and we provided a 
+reference for effective sample size \citep{geyer2011introduction}.
 

### 2024-01-09 Code/functions.R

@@ -137,7 +137,7 @@ alt_graph_bts <- function(t, width, data, trans = 'identity', level = .95)
   ggplot(data, aes(x = n, y = cov, color = CI, linetype = CI)) +
     geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
     geom_line(linewidth = .2, position = position_dodge(width = 0.5)) +
-    geom_errorbar(aes(ymin=LB, ymax = UB, color = CI), width = width, size = .2,
+    geom_errorbar(aes(ymin=CP_LB, ymax = CP_UB, color = CI), width = width, size = .2,
                   position = position_dodge(width = 0.5)) +
     facet_grid(factor(target) ~ factor(phi), scales = 'free',
                labeller = label_parsed) +

### 2024-01-09 Manuscript/reply.tex

--- 2024-01-09 Manuscript/reply.tex
@@
 \end{comment}
-
-\eds{Also added comment in the Recentered Percentile CI paragraph in the 
-BLOCK BOOTSTRAP CIS section. Please check and add a comment here if you like it.}
-\mc{looks good}
 

### 2024-01-09 Manuscript/manuscript.tex
Reference for Clopper-Pearson

--- 2024-01-09 Manuscript/manuscript.tex
@@
 
+%\subsection*{Design}
+
 We compared the performance of the different block bootstrap CI methods 
-under two marginal distributions: normal and exponential.
+under two marginal distributions: standard normal and unit exponential.
 
@@
 expected to match the nominal level. Because it is unlikely for the coverage to 
-exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
-coverage rate 
-(which is an estimate of a proportion with $R = 10,000$). If the proportion 0.95 
+exactly match the nominal level, we can construct a 95\% Clopper-Pearson
+exact CI of the 
+coverage rate,\citep{clopper1934use}
+which is an estimate of a proportion with $R = 10,000$. We used the
+R \textsl{PropCIs} package to achieve this.\citep{PropCIs}
+The choice of
+Clopper-Pearson was motivated by the Wald 
+interval's poor coverage as the proportion approaches 0 or 1, as noted by 
+\citet{brown2001interval}, although when we tried Wald intervals, the coverage
+rate intervals
+did not appear to have large differences. 
+If the 
+proportion 0.95 
 is included in the interval, the block bootstrap method is likely performing 
@@
 parameters of $W_t$ are~1. The lag-1
-autocorrelation coefficient is not invariant to the
+autocorrelation coefficient ($\rho$) is not invariant to the
 transformation,\citep{hofert2018elements} but its value can be obtained by
@@
 size is decreased, whereas if a series has a negative autocorrelation, the
-effective sample size is increased. Additionally, this seems to have a 
+effective sample size is increased. \citep{geyer2011introduction} Additionally, 
+this seems to have a 
 greater effect on the the estimation of the location parameter versus that
@@
 distribution, where standard normal, Student's $t$, and 
-recentered percentile CI coverage rates were greater for stronger dependences 
-regardless of the sign, coverage rates for these CIs seem to be greater only for 
+recentered percentile CI $\phi$ coverage rates were greater for stronger 
+dependences 
+regardless of the sign, $\rho$ coverage rates for these CIs seem to be greater 
+only for 
 stronger negative dependencies and lesser for stronger positive dependences. 
@@
 \jy{I don't follow this. Are you talking about mu only? Even for mu,
-  the statement does not look right.}
+  the statement does not look right.} \mc{for lag-1 autocorrelation}
 \jy{This would invalidate our explanation using the effective sample
@@
   does consistency mean? Do an throughout check, please.}
+\mc{I was basically trying to say that the widths of the CI vary more 
+for BC CIs than for percentile or recentered CIs, I think it may be simpler to
+just say that they are shorter}
 
@@
   scenarios. Rewrite this paragraph.}
-the dependences tructure or the marginal distribution is already known, a 
+the dependence structure or the marginal distribution is already known, a 
 lesser $n$ may be 

### 2024-01-09 Manuscript/manuscript.tex
attempted to fix paragraphs

@@
   cite the reference.}
+\mc{addressed}
 
@@
   size. Let's tune it down or remove it.}
+\mc{this observation was for lag-1 autocorrelation. does it still invalidate 
+our effective sample size explanation?}
 However, the other 
@@
   large. So the recommendation is to do t always since it performs
-  better for small samples.}
+  better for small samples.} \mc{addressed}
 distribution and temporal dependence is 
@@
 for common practice to estimate $\mu$, whereas $n > 3200$ may be necessary
-to estimate the standard deviation. If
+to estimate the standard deviation. Student's $t$ is always preferable to
+Standard Normal CIs
+as they performs better for smaller sample sizes and performs as good or better
+for larger sample sizes.
 \jy{Don't discuss these. The recommended method is regardless of what
@@
   scenarios. Rewrite this paragraph.}
-the dependence structure or the marginal distribution is already known, a 
-lesser $n$ may be 
-adequate to estimate these 
-parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
-when estimating the standard deviation. For negative values of $\phi$, coverage of all 
-parameters is higher in general. Under a marginal standard normal distribution, 
-Student's $t$ seems to over-cover 
-$\mu$ for $\phi = - 0.4$  when 
-using smaller sample sizes, meaning that if $\phi$
+\mc{addressed}
 \jy{These statements are not to the point. Let's not discuss the case
@@
   be robust to phi and the true marginal distribution.}
-is known to have a very negative value, another CI may be required. However, in 
-real world applications, $\phi$ is more commonly found to be positive, so 
-Student's $t$ should still be used if $\phi$ is unknown. 
+\mc{addressed}
 Lastly, to estimate 
@@
 by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
-for smaller values of~$n$.
-
-The results for $\sigma_x$ with $l = \lceil 2n^{1/3} \rceil$ look very similar 
+for smaller values of~$n$. The results for $\sigma_x$ with $l = \lceil 2n^{1/3} 
+\rceil$ look very similar 
 to 
@@
 when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.
-
-\jy{Put the small paragraphs into a bigger one.}
-
-As shown in \textbf{Figure~\ref{fig:norm2}},
-recentered percentile and standard CIs have slightly lower coverage rates when
+\jy{Put the small paragraphs into a bigger one.}\mc{addressed}
+Recentered percentile and standard CIs have slightly lower coverage rates when
 estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
@@
 dramatic for BCA,
-BC, and percentile CIs.
-
-Aside from these differences, the overall changes
+BC, and percentile CIs. Aside from these differences, the overall changes
 in performance when other experimental factors are changed are the same as

### 2024-01-09 Manuscript/reply.tex
Reference for Clopper-Pearson
attempted to fix paragraphs

@@
 \jy{Yes.}
+\mc{addressed}
 
@@
 
-Thank you for pointing this out. We modified the Design section to include a 
-specification of the interval type for the coverage rate, as well as an 
-acknowledgement of its flaw.
+Thank you for pointing this out. We tried both Wald intervals and exact 
+Clopper-Pearson intervals. Although we did not find a major difference between
+the two, we have switched to Clopper-Pearson intervals to avoid the potential
+undercoverage.
 
@@
 \jy{Point out the location of the changes in the text.}
+\mc{addressed}
 
-We have also included a figure in the Results section which 
-uses exact 
-Clopper-Pearson CIs to verify that the choice of interval
-for the binomial proportion did not cause undercoverage in this case.
+We have discussed this in the third paragraph of the Marginal Standard Normal 
+Distribution subsection of the Design section, and we have provided a reference
+for Clopper-Pearson intervals \citep{clopper1934use} as well as the package we 
+used \citep{PropCIs}.
 

### 2024-01-09 Manuscript/manuscript.tex
Small Edits in Reply

@@
 sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
-Recentered Percentile CI) are not necessatily expected to perform
+Recentered Percentile) are not necessarily expected to perform
 better under non-normal marginal distributions. The student's t and

### 2024-01-09 Manuscript/reply.tex
Small Edits in Reply

@@
 Thank you for this suggestion. The motivation behind the proposed
-recentered CI is that. for the autocorrelation parameter in the
+recentered CI is that for the autocorrelation parameter in the
 simulation studies, the centers of the existing CIs appeared to be a
@@
 
-Thank you for the suggestion idea. We have reformatted all of our coverage rate plots 
+Thank you for the suggested idea. We have reformatted all of our coverage rate 
+plots 
 accordingly, which has saved a lot of space!
@@
 blocks is smaller than 20. We have added a discussion on this point in
-the first paragraph of the subsection of Marginal Unit Exponential
-Distribution.
+the first paragraph of the Marginal Unit Exponential
+Distribution subsection.
 
@@
 the two, we have switched to Clopper-Pearson intervals to avoid the potential
-undercoverage.
+undercoverage. We have discussed this in the third paragraph of the Marginal 
+Standard Normal 
+Distribution subsection of the Design section, and we have provided a reference
+for Clopper-Pearson intervals \citep{clopper1934use} as well as the package we 
+used \citep{PropCIs}.
 
@@
 
-We have discussed this in the third paragraph of the Marginal Standard Normal 
-Distribution subsection of the Design section, and we have provided a reference
-for Clopper-Pearson intervals \citep{clopper1934use} as well as the package we 
-used \citep{PropCIs}.
-
 \begin{comment}
@@
 we found it hard to fix the limits on the 
-y-axis without hurting the visualization for the other rows. 
-Figure~\ref{fig:alt2_norm1} is provided as an example:
+y-axis without hurting the visualization for the other rows. The other reviewer
+suggested that we put the 6 figures in a column in 
+a single plot.
+Figure~\ref{fig:alt2_norm1} is provided as an example of this with fixed limits:
 
@@
 of the scale parameter or temporal dependence parameter. We have included a 
-similar
 comment at the end of the paragraph on estimation of~$\mu$, and we provided a 
@@
 increases, and how it varies depending on the sign of the autocorrelation and 
-the parameter of interest. This justification has been added to the Design 
+the parameter of interest. This justification has been added to the first
+paragraph of the Normal section of the Design 
 section. We have also added a deliberation (third paragraph in the Discussion) 
@@
 Thank you for the comment. We have included a discussion of problems 
-with block bootstrap in the introduction, while also highlighting its advantages
+with block bootstrap as the second paragraph in the introduction, while also 
+highlighting its advantages
 which motivated this investigation into their CI performance. This
-last sentences of the manuscript has also been rewritten to call for
+last few sentences of the manuscript have also been rewritten to call for
 understanding of the subpar performance of the existing

### 2024-01-09 Manuscript/manuscript.tex
final smoothing

@@
 $r \in \{1, \ldots, R\}$, where $R$ is the number of replicates. Then
-$cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$, for
-$r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
+the empirical coverage rate is
+$ \sum_{r=1}^{R} I\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r}
+\}/R$, where $I(\cdot)$ in the indicator function.
+If a CI method is valid, then the coverage rate is
 expected to match the nominal level. Because it is unlikely for the coverage to 
 exactly match the nominal level, we can construct a 95\% Clopper-Pearson
-exact CI of the 
-coverage rate,\citep{clopper1934use}
+exact CI of the coverage rate,\citep{clopper1934use}
 which is an estimate of a proportion with $R = 10,000$. We used the
 R \textsl{PropCIs} package to achieve this.\citep{PropCIs}
-The choice of
-Clopper-Pearson was motivated by the Wald 
-interval's poor coverage as the proportion approaches 0 or 1, as noted by 
-\citet{brown2001interval}, although when we tried Wald intervals, the coverage
-rate intervals
-did not appear to have large differences. 
-If the 
-proportion 0.95 
+The choice of Clopper-Pearson was motivated by the Wald 
+interval's poor coverage as the proportion approaches 0
+or~1,\citep{brown2001interval}
+although when we tried Wald intervals, the coverage
+rate intervals did not appear to have large differences. If the proportion 0.95
 is included in the interval, the block bootstrap method is likely performing 
@@
 interval are above .95, the results suggest that the method is overestimating 
-the process' variability. 
-\textbf{Figure~\ref{fig:norm1}} 
+the process' variability. \textbf{Figure~\ref{fig:norm1}} 
 summarizes the empirical coverage rates and the 95\% confidence intervals of the 
@@
 $\rho \in \{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.
-
-For a marginal exponential  distribution, the empirical coverage rates for 
-$\mu$, $\sigma_w$, and 
-the lag-1 autocorrelation coefficient $\rho$ using block bootstrap
-with $l = \lceil n^{1/3} \rceil$, as well as 95\%
-confidence intervals of the real coverage are displayed in 
-\textbf{Figure~\ref{fig:exp1}}.
 
@@
 
-\jy{Are we reporting the C-P intervals? Clarify the desciption and
-  cite the reference.}
-\mc{addressed}
-
-%situations.
-%Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
-%Clopper-Pearson intervals to verify that it is the choice of Wald interval
-%does not cause undercoverage of the coverage rate. Indeed, the widths of the
-%exact proportion CIs do not seem to differ heavily from the Wald-type CIs.
-
 For estimating the standard deviation parameter~$\sigma_x$,
@@
   \caption{50 replicate percentile, BC, and recentered percentile CIs for 
-    samples of $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$)
-    for an AR(1) process with $\phi = 0.4$. For 
+    samples of size $n \in \{800, 1600\}$ ($l = \lceil n^{1/3} \rceil$)
+    for the lag-1 autocorrelation of an AR(1) process with $\phi = 0.4$. For 
     each replicate, the lower and upper bounds of the CIs are displayed, as well 
@@
 
-The
-plot and results for $l = \lceil 2n^{1/3} \rceil$ are included in the Appendix.
+The results for $l = \lceil 2n^{1/3} \rceil$ are reported in the Appendix.
 Performance generally seems to be better for $l = \lceil n^{1/3} \rceil$, but
-importantly, the changes in performance when varying other parameters do not
-change when a different block size is used.
+importantly, the patterns in performance when varying other parameters
+appear to be robust to the different block size.
 
@@
 
+For the scenario of marginal exponential distribution, the empirical
+coverage rates for $\mu$, $\sigma_w$, and 
+the lag-1 autocorrelation coefficient $\rho$ using block bootstrap
+with $l = \lceil n^{1/3} \rceil$, as well as 95\%
+confidence intervals of the real coverage are displayed in 
+\textbf{Figure~\ref{fig:exp1}}. 
 Additionally, a set of 50 CIs are displayed for each of the percentile, 
@@
 samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
-($\phi = 0.4$) in Figure~\ref{fig:eri}.
+($\phi = 0.4$) in \textbf{Figure~\ref{fig:eri}}.
 
@@
   \caption{50 replicate percentile, BC, and recentered percentile CIs for the
-    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
+    lag-1 autocorrelation coefficient $\rho = 0.355$ ($\phi = 0.4$)
     of a stationary series with marginal exponential distribution
@@
 CIs to cover the mean and standard deviation parameters in the exponential
-margin case than in the normal margin case. In contrast to the marginal normal
-distribution, where standard normal, Student's $t$, and 
-recentered percentile CI $\phi$ coverage rates were greater for stronger 
-dependences 
-regardless of the sign, $\rho$ coverage rates for these CIs seem to be greater 
-only for 
-stronger negative dependencies and lesser for stronger positive dependences. 
-\mc{What could be an explanation for this?}
-\jy{I don't follow this. Are you talking about mu only? Even for mu,
-  the statement does not look right.} \mc{for lag-1 autocorrelation}
-\jy{This would invalidate our explanation using the effective sample
-  size. Let's tune it down or remove it.}
-\mc{this observation was for lag-1 autocorrelation. does it still invalidate 
-our effective sample size explanation?}
-However, the other 
-trends 
-and patterns
-discussed in the main text regarding the performance of various methods and
-diverse parameters remain consistent. For example, Student's $t$ confidence
+margin case than in the normal margin case. However, the other trends 
+and patterns discussed regarding the performance of various methods and
+diverse parameters remain unchanged. For example, Student's $t$ confidence
 intervals still exhibit higher coverage rates in comparison to alternative
@@
 sample,\citep{calhoun2018} so the goal for this study was to find the smallest 
-finite sample length 
-$n$ of a time series in order for the block bootstrap procedure to recover its 
+finite sample length~$n$
+of a time series in order for the block bootstrap procedure to recover its 
 associated parameters at an acceptable rate. Our analysis relies on the 
@@
 short.
-\jy{Inconsistent means not consistent and consistency is a desired
-  property of an estimator. When we talk about width of a CI, what
-  does consistency mean? Do an throughout check, please.}
-\mc{I was basically trying to say that the widths of the CI vary more 
-for BC CIs than for percentile or recentered CIs, I think it may be simpler to
-just say that they are shorter}
 
@@
 serially dependent data. When using Student's $t$ intervals and the
-marginal
-\jy{Recall that t is not different from normal when sample size is
-  large. So the recommendation is to do t always since it performs
-  better for small samples.} \mc{addressed}
-distribution and temporal dependence is 
+marginal distribution and temporal dependence is 
 unknown, the results of this study suggest that $n \geq 1600$ may be necessary 
@@
 as they performs better for smaller sample sizes and performs as good or better
-for larger sample sizes.
-\jy{Don't discuss these. The recommended method is regardless of what
-  the dependence struture and marginald istribution are. That's why we
-  did the study. Just gave recommendations based on both
-  scenarios. Rewrite this paragraph.}
-\mc{addressed}
-\jy{These statements are not to the point. Let's not discuss the case
-  where phi is know or not. They are not known. We want the method to
-  be robust to phi and the true marginal distribution.}
-\mc{addressed}
-Lastly, to estimate 
-$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient under
+for larger sample sizes. Lastly, to estimate lag-1 autocorrelation,
+$n \geq 100$ using the Student's $t$ method may be sufficient under
 a marginal standard normal distribution, whereas $n \geq 1600$ may be required
@@
 investigation may be necessary to see if there are other percentile-based 
-interval corrections
-that fix the coverage deterioration problem for~$\phi$.
+interval corrections that fix the coverage deterioration problem for~$\phi$.
 
@@
 for smaller values of~$n$. The results for $\sigma_x$ with $l = \lceil 2n^{1/3} 
-\rceil$ look very similar 
-to 
+\rceil$ look very similar to 
 those the results for $\sigma_x$ with $l = \lceil n^{1/3} \rceil$, but coverage 
-rates of $\sigma_x$ do 
-look 
-slightly lower
+rates of $\sigma_x$ do look slightly lower
 especially for negative values of $\phi$, although Student's $t$ CIs are again
@@
 when $l = \lceil n^{1/3} \rceil$.
-
-\textbf{Figure~\ref{fig:exp2}} 
-summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a marginal exponential distribution using block bootstrap
-with $l = \lceil 2n^{1/3} \rceil$.
 
@@
 
-For a stationary series with a marginal unit exponential distribution, altering 
-the 
-block size results in the same 
-changes in performance of different CIs.
+\textbf{Figure~\ref{fig:exp2}} 
+summarizes the empirical coverage rates and the 95\% confidence intervals of the 
+real coverage for a marginal exponential distribution using block bootstrap
+with $l = \lceil 2n^{1/3} \rceil$. Again, altering the block size results in the same
+changes in performance of different CIs as those in the scenario of
+marginal normal distribution.
 

### 2024-01-09 Manuscript/reply.tex
final smoothing

@@
 
-\usepackage{color}
+\usepackage[dvipsnames]{color}
 \definecolor{darkblue}{rgb}{0.1, 0.2, 0.6}
-\usepackage{xcolor}
+
 \newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
@@
 Thank you for the suggested idea. We have reformatted all of our coverage rate 
-plots 
-accordingly, which has saved a lot of space!
-
-\mc{for exponential, the first-order autocorrelation coefficient
-is not the same as $\phi$, should I define $\rho$ as the first-order 
-autocorrelation coefficient in the manuscript so that I can use the greek letter
-in the plot}
-\jy{Yes.}
-\mc{addressed}
+plots accordingly, which has saved a lot of space!
 
@@
 Thank you for pointing this out. We tried both Wald intervals and exact 
-Clopper-Pearson intervals. Although we did not find a major difference between
-the two, we have switched to Clopper-Pearson intervals to avoid the potential
-undercoverage. We have discussed this in the third paragraph of the Marginal 
+Clopper-Pearson intervals \citep{clopper1934use}, the latter of which
+as implemented in the R package \texttt{PropCIs}.\citep{PropCIs}
+No major difference between the two was found, which is expected as we
+have a large number replication (10,000). Nonetheless, we have
+switched to reporting Clopper-Pearson intervals to avoid the potential
+undercoverage and discussed this in the third paragraph of the Marginal 
 Standard Normal 
-Distribution subsection of the Design section, and we have provided a reference
-for Clopper-Pearson intervals \citep{clopper1934use} as well as the package we 
-used \citep{PropCIs}.
-
-\eds{I don't think this answers the question.  The reviewer is saying that 0.95 
-is close to the boundary of 1, so the undercoverage observed intervals
-(especially when phi -0.4) may be due, at least in part, to the flaws 
-of the asymptotic Wald interval you are using. 
-\@ Jun: do you think he should try exact Clopper-Pearson
-intervals for at least a few cases of undercoverage to verify it is not the Wald
-interval that is causing the undercoverage, then comment on this in at least the
-reply (and possibly also in the main paper)?}
-\mc{plot\_norm\_mu\_1\_cup.pdf (exact Clopper-Pearson) seems to have about the same 
-widths for high 
-proportions
-(especially for phi = -0.4) as {plot\_norm\_mu\_1.pdf} (Wald-Type)}
-
-\jy{Are there big differences? We could report the CP CIs in the paper.}
-\mc{I included it in the paper but they do not seem too different}
-\jy{Point out the location of the changes in the text.}
-\mc{addressed}
+Distribution subsection of the Design section.
+\jy{Quanlity control the bib entries.}
 
@@
 
-Thank you for the suggestion. However, because of the deterioration for $\phi$, 
-we found it hard to fix the limits on the 
-y-axis without hurting the visualization for the other rows. The other reviewer
-suggested that we put the 6 figures in a column in 
-a single plot.
-Figure~\ref{fig:alt2_norm1} is provided as an example of this with fixed limits:
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/alt2_plot_norm1}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:alt2_norm1}
-\end{figure}
-
-%\jy{I'm interested in seeing the figures overlaid as in
-%  Figure~\ref{fig:mu}.}
-\mc{addressed}\jy{Put them overlaid; three plots in one with facet
-  grid as the last one.}
-  \mc{addressed. I think the last one looks better}
+As suggested by the other reviewer, we now overlay the comparison of 6
+CIs within the same panels. Each row reports the results for one
+parameter, with a shared scale on the y-axis. The number of figures
+have been greatly reduced and the comparison made easier.
 
@@
 Thank you for this comment.
-A possible explanation for this is that if a 
-stationary series has a positive 
-autocorrelation, the effective sample
-size is decreased, whereas is a series has a negative autocorrelation, the
-effective sample size is increased. Additionally, this seems to have a 
+A possible explanation for this is that if a stationary series has a positive
+autocorrelation, the effective sample size is decreased, whereas is a
+series has a negative autocorrelation, theeffective sample size is
+increased.\citep{geyer2011introduction}
+Additionally, this seems to have a 
 greater effect on the the estimation of the location parameter versus that
 of the scale parameter or temporal dependence parameter. We have included a 
-comment at the end of the paragraph on estimation of~$\mu$, and we provided a 
-reference for effective sample size \citep{geyer2011introduction}.
+comment at the end of the paragraph on estimation of~$\mu$.
 
@@
 
-Thank you for pointing this out. The original sentence has been reworded as you
-suggested to make it more clear.
+Thank you for pointing this out. The sentence has been rewphrased as
+suggested.
 
@@
 
-\jy{Add a discussion in the results section, referring to detailed
-  results in the appendix. Point out the location of this discussion
-  in this reply.}
-\mc{addressed}
-
 \begin{comment}
@@
 section. We have also added a deliberation (third paragraph in the Discussion) 
-regarding what would
-be expected for higher dependence levels.
-\jy{give the location of the paragraph in the text.}
-\mc{addressed}
+regarding what would be expected for higher dependence levels.
 

### 2024-01-09 Manuscript/manuscript.tex
touch up

@@
 size is decreased, whereas if a series has a negative autocorrelation, the
-effective sample size is increased. \citep{geyer2011introduction} Additionally, 
-this seems to have a 
+effective sample size is increased.\citep{geyer2011introduction}
+Additionally,  this seems to have a 
 greater effect on the the estimation of the location parameter versus that
@@
 parameter of a time series at the nominal level given an infinitely large
+\jy{Also cite Calhoun in the introduction}
 sample,\citep{calhoun2018} so the goal for this study was to find the smallest 

### 2024-01-09 Manuscript/manuscript.tex
replied to minor comments

@@
 to produce CIs with coverage rates matching their nominal levels as the sample 
-size grows. However, when dealing with finite sample sizes, an important 
+size grows.\citep{calhoun2018} However, when dealing with finite sample sizes, 
+an important 
 question is how large the sample size must be for block bootstrap CIs to have 
@@
 parameter of a time series at the nominal level given an infinitely large
-\jy{Also cite Calhoun in the introduction}
+%\jy{Also cite Calhoun in the introduction}\mc{addressed}
 sample,\citep{calhoun2018} so the goal for this study was to find the smallest 
@@
 when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.
-\jy{Put the small paragraphs into a bigger one.}\mc{addressed}
+%\jy{Put the small paragraphs into a bigger one.}\mc{addressed}
 Recentered percentile and standard CIs have slightly lower coverage rates when

### 2024-01-09 Code/exp_processing.R

@@ -1,5 +1,6 @@
 source("functions.R")
 library(copula)
+library(PropCIs)
 setwd("../Data")
 nrep <- 10000
 file_names <- list.files(pattern = "^exp_results")

### 2024-01-09 Code/norm_processing.R

@@ -1,4 +1,5 @@
 source("functions.R")
+library(PropCIs)
 setwd("../Data")
 nrep <- 10000
 file_names <- list.files(pattern = "^norm_results")

### 2024-01-09 Manuscript/reply.tex
replied to minor comments
Fixed typo in summary
opening paragraph in reply rephased

@@
 
-We thank the editor and the AE for the opportunity to revise the manuscript. and
-the two referees for their constructive comments.
-We are indebted to the reviewers for pointing out these vital discussion areas,
-which have not only enriched the current paper but also charted a clear course
-for our subsequent research endeavors.
+We extend our gratitude to the editor and the Associate Editor for
+granting us the opportunity to revise this manuscript. We also want to
+express our appreciation to the two referees for their valuable and
+constructive comments. The reviewers have highlighted crucial
+discussion areas that have not only enhanced the quality of this paper
+but have also set a clear direction for our future research
+endeavors.
 
@@
 \begin{enumerate}
-\item Clarifications of design and more detail examination of results;
+\item Clarifications of design and more detailed examination of results;
 \item Reorganization of paragraphs on the Simulation Study, including moving the
@@
 Distribution subsection of the Design section.
-\jy{Quanlity control the bib entries.}
+%\jy{Quanlity control the bib entries.}\mc{addressed}
 

### 2024-01-10 Manuscript/manuscript.tex
citation for R

@@
 block bootstrap sampling step was done with function \texttt{tsboot} from R 
+\citep{R}
 package \textsl{boot},\citep{boot} with block size $\lceil n / l \rceil$. This 

### 2024-01-10 Manuscript/manuscript.tex
allow breaks

@@
 $\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
-$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. We only
+$\phi$, which was set to five levels: $\{-0.4, -0.2, \allowbreak 0.0, 0.2, 0.4\}$. 
+We only
 used serial dependences as strong as 0.4, because we only seek to 
@@
 autocorrelation coefficients are
-$\rho \in \{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.
+$\rho \in \{-0.298, \allowbreak -0.156, 0, 0.170, 0.355\}$.
 

### 2024-01-10 Manuscript/manuscript.tex
removed superscript for affiliations

@@
 \author{
-Mathew Chandy*$^{a}$, Elizabeth D. Schifano$^{a}$, Jun Yan$^{a}$ \\ \medskip 
-$^{a}$Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
+Mathew Chandy*, Elizabeth D. Schifano, Jun Yan \\ \medskip 
+Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
 Student: mathew.chandy@uconn.edu* \\

### 2024-01-16 Manuscript/manuscript.tex
removed space before my name
about student author and press summary

@@
 % several affiliations need to be noted.
-\author{
-Mathew Chandy*, Elizabeth D. Schifano, Jun Yan \\ \medskip 
+\author{Mathew Chandy*, Elizabeth D. Schifano, Jun Yan \\ \medskip 
 Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
@@
 
+\section*{About Student Author}
+\label{sec:asa}
+Mathew Chandy is a senior majoring in both Statistics and Statistical Data Science, 
+and he plans to graduate in the spring of 2024.
+
+\section*{Press Summary}
+\label{sec:press}
+This simulation study evaluates the sample size necessary to estimate the mean,
+standard deviation, and lag-1 autocorrelation of a stationary time series using
+different block bootstrap confidence interval types. The results showed that 
+percentile-based confidence intervals for the lag-1 autocorrelation may suffer 
+from coverage deterioration as 
+sample size is increased, motivating the authors to propose a new recentered percentile 
+confidence interval which does not deteriorate in performance for greater sample sizes.
+The results also suggest that when using Student's $t$ bootstrap confidence intervals, 
+a sample size of at least 1600 may be sufficient to estimate the mean, 
+whereas a sample size larger than 3200 may be necessary to estimate 
+the standard deviation. Finally, to estimate the lag-1 autocorrelation, using
+Student's $t$ bootstrap confidence intervals demands a sample size of at least 100 
+when the marginal distribution is standard normal and a sample size of at least 1600 when
+the marginal distribution is unit exponential.
+
 \end{document}

### 2024-01-17 Manuscript/manuscript.tex
small change in press summary

@@
 whereas a sample size larger than 3200 may be necessary to estimate 
-the standard deviation. Finally, to estimate the lag-1 autocorrelation, using
-Student's $t$ bootstrap confidence intervals demands a sample size of at least 100 
-when the marginal distribution is standard normal and a sample size of at least 1600 when
-the marginal distribution is unit exponential.
+the standard deviation. The results additionally indicate that 
+estimation of the lag-1 autocorrelation - using
+Student's $t$ bootstrap confidence intervals - demands a sample size of at least 100 
+when the marginal distribution is standard normal and a sample size of at least 1600 
+when the marginal distribution is unit exponential.
 

### 2024-03-26 Code/copula.R
ajur style

@@ -18,11 +18,11 @@ cor(z[,1], z[,2])
 
 
 rho2phi <- function(rho) {
-    mymvd <- copula::mvdc(copula::normalCopula(rho), margins = "exp",
-                          paramMargins = list(rate=1), marginsIdentical = TRUE)
+    mymvd <- copula::mvdc(copula::normalCopula(rho), margins = "gamma",
+                          paramMargins = list(list(shape = 8, rate = 1)), marginsIdentical = TRUE)
     EXY <- pracma::dblquad(function(x, y) x * y * copula::dMvdc(cbind(x, y), mymvd),
                            0, 20, 0, 20)
-    phi <- (EXY - 1) / 1
+    phi <- (EXY - 64) / 8
     phi
 }
 

### 2024-03-29 Manuscript/citation.tex
reference fix

\begin{thebibliography}{30}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Efron(1979)]{efron1979bootstrap}
Efron, B. (1979) Bootstrap methods: Another look at the jackknife.
\newblock \textit{The Annals of Statistics} 7(1), 1--26.
\newblock \emph{https://doi.org/10.1007/978-1-4612-4380-9\_41}

\bibitem[Hall(1985)]{hall1985resampling}
Hall, P. (1985) Resampling a coverage pattern.
\newblock \textit{Stochastic Processes and their Applications} 20(2), 231--246.
\newblock \emph{https://doi.org/10.1016/0304-4149(85)90212-1}

\bibitem[Carlstein(1986)]{carlstein1986use}
Carlstein, E. (1986) The use of subseries values for estimating the variance of
  a general statistic from a stationary sequence.
\newblock \textit{The Annals of Statistics} 14(3), 1171--1179.
\newblock \emph{https://doi.org/10.1214/aos/1176350057}

\bibitem[Kunsch(1989)]{kunsch1989jackknife}
Kunsch, H.~R. (1989) The jackknife and the bootstrap for general stationary
  observations.
\newblock \textit{The Annals of Statistics} 17(3), 1217--1241.
\newblock \emph{https://doi.org/10.1214/aos/1176347265}

\bibitem[MacKinnon(2006)]{mackinnon2006bootstrap}
MacKinnon, J.~G. (2006) Bootstrap methods in econometrics.
\newblock \textit{The Economic Record} 82(1), 2--18.
\newblock \emph{https://doi.org/10.1111/j.1475-4932.2006.00328.x}

\bibitem[Varga and Zempl{\'e}ni(2017)]{varga2017generalised}
Varga, L., and Zempl{\'e}ni, A. (2017) Generalised block bootstrap and its use
  in meteorology.
\newblock \textit{Advances in Statistical Climatology, Meterology and
  Oceanography} 3(1), 55--66.
\newblock \emph{https://doi.org/10.5194/ascmo-3-55-2017}

\bibitem[Calhoun(2018)]{calhoun2018}
Calhoun, G. (2018) Block bootstrap consistency under weak assumptions.
\newblock \textit{Econometric Theory} 34(6), 1383--1406.
\newblock \emph{https://doi.org/10.1017/S0266466617000500}

\bibitem[Lahiri(1999)]{lahiri1999theoretical}
Lahiri, S.~N. (1999) Theoretical comparisons of block bootstrap methods.
\newblock \textit{The Annals of Statistics} 27(1), 386--404.
\newblock \emph{https://doi.org/10.1214/aos/1018031117}

\bibitem[Buhlmann and K{\"u}nsch(1999)]{buhlmann1999block}
B{\"u}hlmann, P., and K{\"u}nsch, H.~R. (1999) Block length selection in the
  bootstrap for time series.
\newblock \textit{Computational Statistics \& Data Analysis} 31(3), 295--310.
\newblock \emph{https://doi.org/10.1016/S0167-9473(99)00014-6}

\bibitem[Buhlmann(2002)]{buhlmann2002bootstraps}
B{\"u}hlmann, P. (2002) Bootstraps for time series.
\newblock \textit{Statistical Science} 52--72.
\newblock \emph{https://doi.org/10.1214/ss/1023798998}

\bibitem[Hesterberg(2015)]{hesterberg2015teachers}
Hesterberg, T.~C. (2015) What teachers should know about the bootstrap:
  {R}esampling in the undergraduate statistics curriculum.
\newblock \textit{The American Statistician} 69(4), 371--386.
\newblock \emph{https://doi.org/10.1080/00031305.2015.1089789}

\bibitem[Chernick and Labudde(2009)]{chernick2009revisiting}
Chernick, M.~R., and Labudde, R.~A. (2009) Revisiting qualms about bootstrap
  confidence intervals.
\newblock \textit{American Journal of Mathematical and Management Sciences}
  29(3-4), 437--456.
\newblock \emph{https://doi.org/10.1080/01966324.2009.10737767}

\bibitem[Nevitt and Hancock(2001)]{nevitt2001performance}
Nevitt, J., and Hancock, G.~R. (2001) Performance of bootstrapping approaches
  to model test statistics and parameter standard error estimation in
  structural equation modeling.
\newblock \textit{Structural Equation Modeling} 8(3), 353--377.
\newblock \emph{https://doi.org/10.1207/S15328007SEM0803\_2}

\bibitem[Burch(2012)]{burch2012nonparametric}
Burch, B.~D. (2012) Nonparametric bootstrap confidence intervals for variance
  components applied to interlaboratory comparisons.
\newblock \textit{Journal of Agricultural, Biological, and Environmental
  Statistics} 17(2), 228--245.
\newblock \emph{https://doi.org/10.1007/s13253-012-0087-9}

\bibitem[Puth et al.(2015)]{puth2015variety}
Puth, M.-T., Neuh{\"a}user, M., and Ruxton, G.~D. (2015) On the variety of
  methods for calculating confidence intervals by bootstrapping.
\newblock \textit{Journal of Animal Ecology} 84(4), 892--897.
\newblock \emph{https://doi.org/10.1111/1365-2656.12382}

\bibitem[Goncalves and White(2005)]{goncalves2005bootstrap}
Gon{\c c}alves, S., and White, H. (2005) Bootstrap standard error estimates for
  linear regression.
\newblock \textit{Journal of the American Statistical Association} 100(471),
  970--979.
\newblock \emph{https://doi.org/10.1198/016214504000002087}

\bibitem[Diciccio and Efron(1996)]{diciccio1996bootstrap}
DiCiccio, T.~J., and Efron, B. (1996) Bootstrap confidence intervals.
\newblock \textit{Statistical Science} 11(3), 189--228.
\newblock \emph{https://doi.org/10.1214/ss/1032280214}

\bibitem[Rice(2006)]{rice2006mathematical}
Rice, J.~A. (2006) \textit{Mathematical Statistics and Data Analysis}.
\newblock Cengage Learning, Boston

\bibitem[Efron and Tibshirani(1993)]{efron1993introduction}
Efron, B., and Tibshirani, R. (1993) \textit{An Introduction to the Bootstrap}.
\newblock Chapman \& Hall/CRC, Boca Raton.
\newblock \emph{https://doi.org/10.1201/9780429246593}

\bibitem[Carpenter and Bithell(2000)]{carpenter2000bootstrap}
Carpenter, J., and Bithell, J. (2000) Bootstrap confidence intervals: {When},
  which, what? {A} practical guide for medical statisticians.
\newblock \textit{Statistics in Medicine} 19(9), 1141--1164.
\newblock
  \emph{https://doi.org/10.1002/(SICI)1097-0258(20000515)19:9<1141::AID-SIM479>3.0.CO;2-F}

\bibitem[Efron(1987)]{efron1987better}
Efron, B. (1987) Better bootstrap confidence intervals.
\newblock \textit{Journal of the American Statistical Association} 82(397),
  171--185.
\newblock \emph{https://doi.org/10.1080/01621459.1987.10478410}

\bibitem{R}
R Core Team. (2022) \textit{R: A Language and Environment for Statistical
  Computing}.
\newblock R Foundation for Statistical Computing, Vienna, Austria

\bibitem{boot}
Canty, A. (2022) \textit{boot: Bootstrap R (S-Plus) Functions}.
\newblock R package version 1.3-28.1

\bibitem[Clopper and Pearson(1934)]{clopper1934use}
Clopper, C.~J., and Pearson, E.~S. (1934) The use of confidence or fiducial
  limits illustrated in the case of the binomial.
\newblock \textit{Biometrika} 26(4), 404--413.
\newblock \emph{https://doi.org/10.2307/2331986}

\bibitem{PropCIs}
Scherer, R. (2018) \textit{{PropCIs}: {V}arious Confidence Interval Methods for
  Proportions}.
\newblock R package version 0.3-0

\bibitem[Brown et al.(2001)]{brown2001interval}
Brown, L.~D., Cai, T.~T., and DasGupta, A. (2001) Interval estimation for a
  binomial proportion.
\newblock \textit{Statistical Science} 16(2), 101--133.
\newblock \emph{https://doi.org/10.1214/ss/1009213286}

\bibitem{ggplot2}
Wickham, H. (2016) \textit{ggplot2: Elegant Graphics for Data Analysis}.
\newblock Springer-Verlag, New York
\newblock \emph{https://doi.org/10.1007/978-0-387-98141-3}

\bibitem[Hofert et al.(2018)]{hofert2018elements}
Hofert, M., Kojadinovic, I., M{\"a}chler, M., and Yan, J. (2018)
  \textit{Elements of Copula Modeling with R}.
\newblock Springer, New York.
\newblock \emph{https://doi.org/10.1007/978-3-319-89635-9}

\bibitem[Geyer(2011)]{geyer2011introduction}
Geyer, C.~J. (2011) Introduction to {M}arkov chain {M}onte {C}arlo.
\newblock In S.~Brooks, A.~Gelman, G.~L. Jones, and X.-L. Meng, editors,
  \textit{Handbook of {M}arkov chain {M}onte {C}arlo}, 3--48. CRC Press, Boca
  Raton
\newblock \emph{https://doi.org/10.1201/b10905}

\bibitem[Kreiss(1992)]{kreiss1992bootstrap}
Kreiss, J.-P. (1992) Bootstrap procedures for {AR} ($\infty$)---processes.
\newblock In \textit{Bootstrapping and Related Techniques: Proceedings of an
  International Conference, Held in Trier, FRG, June 4--8, 1990}, 107--113.
  Springer, New York.
\newblock \emph{https://doi.org/10.1007/978-3-642-48850-4\_14}

\end{thebibliography}

### 2024-03-29 Manuscript/manuscript.tex
ajur style
reference fix

@@
 \makeatletter
-\newcommand\sixteen{\@setfontsize\sixteen{17pt}{6}}
+\newcommand\sixteen{\@setfontsize\sixteen{16pt}{6}}
 \renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
@@
 % several affiliations need to be noted.
-\author{Mathew Chandy*, Elizabeth D. Schifano, Jun Yan \\ \medskip 
-Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
+\author{Mathew Chandy*, Elizabeth D. Schifano, \& Jun Yan \\ \medskip \medskip 
+Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip\medskip 
+https://doi.org/10.33697/ajur.2024.101\\ \medskip\medskip 
 Student: mathew.chandy@uconn.edu* \\
@@
 
-\section*{Block Bootstrap CIs}
+\section*{\textit{Block Bootstrap CIs}}
 \label{sec:bbci}
@@
 general trend as the strength of the autocorrelation 
-increases, and how it varies depending on the sign of the autocorrelation and 
+increases, and how it varies depending on the sign of the autocorrelation
+and 
 the parameter of interest. The 
 series $X_t$ has mean zero and variance 
-$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
-set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
+$\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
+$\phi$, 
+we 
+set $\sigma_{\epsilon}^2 = (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
 
@@
   \includegraphics[width=\textwidth]{figures/alt_plot_norm1}
+  \includegraphics[width=\textwidth]{figures/alt_plot_norm2}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
@@
     block bootstrap with $l = \lceil n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
+    error bars represent 95\% CIs of the real coverage rates.
+  Top: $l = \lceil n^{1/3} \rceil$. Bottom: $l = \lceil 2n^{1/3} \rceil$.}
   \label{fig:norm1}
@@
 
-For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:norm1}} suggests 
+For estimating the mean parameter~$\mu$, the top panel of
+\textbf{Figure~\ref{fig:norm1}} suggests 
 that all methods eventually approach correct coverage of $\mu$ as sample size 
@@
 
-The results for $l = \lceil 2n^{1/3} \rceil$ are reported in the Appendix.
-Performance generally seems to be better for $l = \lceil n^{1/3} \rceil$, but
+The results for $l = \lceil 2n^{1/3} \rceil$ are reported in the
+bottom panel of Figure~\ref{fig:norm1}. The performances generally
+seems to be inferior compared those with $l = \lceil n^{1/3}\rceil$, but
 importantly, the patterns in performance when varying other parameters
 appear to be robust to the different block size.
+For negative autocorrelations, the coverage 
+rates of $\mu$ appear to be lower when
+using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
+would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
+$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
+$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
+by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
+for smaller values of~$n$. The results for $\sigma_x$ with $l = \lceil 2n^{1/3} 
+\rceil$ look very similar to 
+those the results for $\sigma_x$ with $l = \lceil n^{1/3} \rceil$, but coverage 
+rates of $\sigma_x$ do look slightly lower
+especially for negative values of $\phi$, although Student's $t$ CIs are again
+not as influenced by this change in~$l$. A larger sample size seems necessary
+when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.
+Recentered percentile and standard CIs have slightly lower coverage rates when
+estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
+Although it is still a problem, the coverage deterioration appears to be less 
+dramatic for BCA,
+BC, and percentile CIs. Aside from these differences, the overall changes
+in performance when other experimental factors are changed are the same as
+when $l = \lceil n^{1/3} \rceil$.
 
@@
   \includegraphics[width=\textwidth]{figures/alt_plot_exp1}
+  \includegraphics[width=\textwidth]{figures/alt_plot_exp2}
   \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
@@
     block bootstrap with $l = \lceil n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
+    The error bars represent 95\% CIs of the real coverage rates.
+    Top: $l = \lceil n^{1/3} \rceil$. Bottom: $l = \lceil 2n^{1/3} \rceil$.}
   \label{fig:exp1}
@@
 the lag-1 autocorrelation coefficient $\rho$ using block bootstrap
-with $l = \lceil n^{1/3} \rceil$, as well as 95\%
+with $l  \in \{\lceil n^{1/3} \rceil, \lceil 2n^{1/3} \rceil$, as well as 95\%
 confidence intervals of the real coverage are displayed in 
@@
 methods. Performance continues to be more favorable when temporal dependence is
-negative rather than positive. Of particular significance, the percentile, BC,
+negative rather than positive. Again, altering the block size results
+in the same changes in performance of different CIs as those in the
+scenario of  marginal normal distribution.
+Of particular significance, the percentile, BC,
 and BCA confidence intervals still display a decline in coverage accuracy for
@@
 parameter of a time series at the nominal level given an infinitely large
-%\jy{Also cite Calhoun in the introduction}\mc{addressed}
 sample,\citep{calhoun2018} so the goal for this study was to find the smallest 
@@
 
-\section*{Appendix: Simulation Study with $l = \lceil 2n^{1/3} \rceil$}
-
-\textbf{Figure~\ref{fig:norm2}} 
-summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a marginal standard normal distribution using block bootstrap
-with $l = \lceil 2n^{1/3} \rceil$.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/alt_plot_norm2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
-    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
-    a marginal standard 
-    normal distribution with AR coefficient
-    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. The
-    error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:norm2}
-\end{figure}
-
-Based on \textbf{Figure~\ref{fig:norm2}}, for negative autocorrelations, the 
-coverage 
-rates of $\mu$ appear to be lower when
-using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
-would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
-$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
-$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
-by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
-for smaller values of~$n$. The results for $\sigma_x$ with $l = \lceil 2n^{1/3} 
-\rceil$ look very similar to 
-those the results for $\sigma_x$ with $l = \lceil n^{1/3} \rceil$, but coverage 
-rates of $\sigma_x$ do look slightly lower
-especially for negative values of $\phi$, although Student's $t$ CIs are again
-not as influenced by this change in~$l$. A larger sample size seems necessary
-when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.
-%\jy{Put the small paragraphs into a bigger one.}\mc{addressed}
-Recentered percentile and standard CIs have slightly lower coverage rates when
-estimating negative values of $\phi$ with $l = \lceil 2n^{1/3} \rceil$. 
-Although it is still a problem, the coverage deterioration appears to be less 
-dramatic for BCA,
-BC, and percentile CIs. Aside from these differences, the overall changes
-in performance when other experimental factors are changed are the same as
-when $l = \lceil n^{1/3} \rceil$.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/alt_plot_exp2}
-  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
-    the marginal mean $\mu$, the marginal standard deviation $\sigma_w$, and
-    the first-order autocorrelation coefficient $\rho$ of a stationary series 
-    with 
-    marginal unit exponential distribution obtained by transforming an AR(1) 
-    process
-    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
-    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates 
-    replicates of
-    block bootstrap with $l = \lceil 2n^{1/3} \rceil$. 
-    The error bars represent 95\% CIs of the real coverage rates.}
-  \label{fig:exp2}
-\end{figure}
-
-\textbf{Figure~\ref{fig:exp2}} 
-summarizes the empirical coverage rates and the 95\% confidence intervals of the 
-real coverage for a marginal exponential distribution using block bootstrap
-with $l = \lceil 2n^{1/3} \rceil$. Again, altering the block size results in the same
-changes in performance of different CIs as those in the scenario of
-marginal normal distribution.
-
-\bibliographystyle{unsrtnat}
-\bibliography{citations}
+\bibliographystyle{ajur}
+\input{citation}
 
@@
 Mathew Chandy is a senior majoring in both Statistics and Statistical Data Science, 
-and he plans to graduate in the spring of 2024.
+and he plans to graduate in the Spring of 2024.
 
